### 2017-11-06 paper/generalities.tex
paper: add Masuda comments

\subsection{Analytic Preliminaries}
\label{sec:analytic_preliminaries}

Define the occurrence rate density, $\Gamma$,
as the expected number of planets per star per natural logarithmic bin 
of planetary and stellar phase space:
\begin{equation}
\Gamma(\vec{x}) = \frac{d^n\Lambda}{\prod_{i=1}^{n} {\rm d} \ln x_i  }.
\label{eq:rate_density_defn}
\end{equation}
$\vec{x}$ is an $n$-dimensional list of the continuous physical properties 
that might affect the occurrence rate density. 
For example,
$\vec{x}=(r,P,R)$ where $r$ is the planet radius, $P$ is its orbital period, 
and $R$ is the host star radius.
The occurrence rate $\Lambda$ is found by integrating the rate density over a 
specified volume of phase space (e.g., Youdin 2011).

The previous definition implicitly marginalizes the rate density over stellar 
multiplicity.
For simplicity, this work only considers single and binary star systems.
Then for a selected population of stars and planets the rate density can be 
written\footnote{
    Eq.~\ref{eq:rate_density_marginalized} follows by writing the $i^{\rm 
        th}$ system type's rate density as some normalization multiplied by a 
    probability density:
    $\Gamma_i(\vec{x}) = \mathcal{Z}_i p_i(\vec{x})$.
    For Eq.~\ref{eq:rate_density_defn} to hold, we must have $\mathcal{Z}_i = 
    \Lambda_i$.
}
\begin{equation}
\Gamma(\vec{x})
= \sum_{i=0}^{2} w_i \Gamma_i(\vec{x})
= \sum_i w_i \Lambda_i p_i(\vec{x})
\label{eq:rate_density_marginalized}
\end{equation}
where $i=0$ corresponds to single star systems, $i=1$ primaries of binaries, 
and $i=2$ secondaries of binaries.
$\Lambda_i$ is the occurrence rate integrated over all possible phase space  
for the $i^{\rm th}$ system type, and $p_i(\vec{x})$ is the joint 
probability density function so that $\Gamma_i(\vec{x}) = \Lambda_i 
p_i(\vec{x})$.
The weights are given by 
\begin{equation}
w_i = N_i/N_{\rm tot},
\end{equation}
for $N_{\rm tot} = \sum_i N_i$ the total number of selected stars, and 
$N_0,N_1,N_2$ the number of selected single stars, primaries, and 
secondaries respectively.
Both $N_1$ and $N_2$ are equal to the number of selected points on 
the sky which are in fact binary systems.
The relationship between the rate $\Lambda$ over a desired volume of 
phase space $\Omega_{\rm desired}$ and $\Lambda_i$ is
\begin{equation}
\Lambda = \sum_i
\left(
w_i \Lambda_i \int_{\Omega_{\rm desired}} p_i(\vec{x}) \,{\rm d}\Omega
\right),
\label{eq:occ_rate}
\end{equation}
where $p_i(\vec{x})$ is assumed to be normalized to unity.

A transit survey will have a rate density of detected planets $\hat{\Gamma}$, 
which for each system type will be the product of the rate density and the 
detection efficiency $Q_i(\vec{x})$:
\begin{equation}
\hat{\Gamma}(\vec{x}) = \sum_i Q_i(\vec{x}) \Gamma_i(\vec{x}) 
\equiv \sum_i \hat{\Gamma}_i(\vec{x}),
\label{eq:detected_rate_density}
\end{equation}
where again the index $i$ is over each type of system (singles, primaries, 
and secondaries).
The detection efficiency includes the geometric transit probability, as well 
as any incompleteness effects.
Foreman-Mackey et al. (2014) discuss how this 
is calculated in practice.

### 2017-11-06 paper/introduction.tex
paper: add Masuda comments

\section{Introduction}

An astronomer who does not believe in stellar multiplicity wants to measure the
mean number of planets of a certain type per star of a certain type.
They perform a signal-to-noise limited transit survey and detect $N_{\rm det}$ 
transit signals that appear to be from planets of the desired type.  They 
calculate the apparent number of searchable stars, $N_\star$.  ``Searchable 
stars'' are the stars for which 
planets are observed with 100\% detection efficiency. 
Correcting for the geometric 
transit probability $f_{\rm g}$, they compute an apparent occurrence rate 
$\Lambda_{\rm a}$:

\begin{equation}
\Lambda_{\rm a} = \frac{N_{\rm det}}{N_\star} \times \frac{1}{f_g}.
\end{equation}

There are many potential pitfalls.  Some genuine transit signals can be missed
by the detection pipeline.  Some apparent transit signals are spurious, from
noise fluctuations, failures of `detrending', or instrumental effects.  Stars
and planets can be misclassified due to statistical and systematic errors in
the measurements of their properties.  Poor angular resolution causes false
positives due to blends with background eclipsing binaries. {\it Et cetera}.

Here we focus on problems that arise from the fact that many stars exist in 
multiple star systems.
For simplicity, we only consider binaries, and we assume that they are all 
spatially unresolved.

An immediate complication is that, due to dynamical stability or some 
aspect of planet formation, the occurrence rate of planets may differ 
between binary and single-star systems.
If ``occurrence rate'' is defined purely as the mean number of planets within 
set radius and period bounds per star in a given mass interval, it must 
implicitly marginalize over stellar multiplicity.
This means marginalizing over ``occurrence rates in single star systems'', 
``occurrence rates about primaries'', and
``occurrence rates about secondaries'' (see {\it e.g.,} Wang et al., 
2015).

Outside of astrophysical differences, there are observational biases.
A given apparently-searchable star may truly be a single star of the desired 
type. If it is binary, it may contain two, one, or no searchable stars of the 
desired type, which affects $N_\star$.
There may be systematic errors in stellar parameter estimates of such 
systems, which in this work we neglect.
One might also imagine an apparently-searchable star which in no stellar 
component is of the desired type. We will not consider errors of this type.  
We will assume that all the apparently-searchable stars are either single 
stars of the desired type, or binaries in which either the primary or else 
both components are of the desired type.

When counting the detected signals from planets of the desired 
type, $N_{\rm det}$, ignoring binarity leads to errors in planet radius 
classification, and the assumed survey completeness.
Detected planets in binary systems will have underestimated radii because of 
the diluting flux from the companions, and possibly because they are assumed 
to orbit the wrong star ({\it e.g.}, Furlan et al. 2017).
The number of selected stars should change dependent on the planet radius 
and period for which the rate measurement is desired, and on the survey's 
achieved photometric precision.
This means our naive astronomer assumes the fraction of their selected stars 
which are searchable is 1 (this is their ``assumed completeness'').
Binarity confuses this, because the ability to search for planets 
in binary systems depends on which stellar component hosts the planet, and on 
how much dilution affects the measurement.

\paragraph{How Has Binarity Been Considered in Occurrence Rate Measurements?}
Many authors have reported planet occurrence rates from transit 
survey data\footnote{
    An online list of occurrence rate papers is maintained at 
    \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
}.
With regard to binarity, the typical approach has been to ignore the 
issue\footnote{Deacon et al., 2015 are an exception to the rule.}.
For instance, in a laudable study by Burke et al. (2015), they
\begin{quote}
``treat the pipeline completeness as having no uncertainty 
due to the incomplete understanding of the stellar parameters, eccentricity, 
and stellar binarity.''
\end{quote}
Though they do ``explore sensitivity in the derived planet occurrence rates 
to alternative assumptions for the stellar parameters and non-zero 
eccentricities'', they do not for binarity.

Of course, on a system-by-system level stellar multiplicity affects the 
interpretation of planet candidates. High resolution imaging 
campaigns have consequently been undertaken to measure the multiplicity of 
almost all {\it Kepler}\ Objects of Interest 
(Howell et al. 2011; Adams et al. 2012, 2013; Horch et al. 2012, 2014; 
Lillo-Box et al. 2012, 2014; Dressing et al. 2014; Law et al. 2014; Cartier et 
al. 2015; Everett et al. 2015; Gilliland et al. 2015; Wang et al. 2015a, 
2015b; Baranec et al. 2016).
The results of these programs have been collected by Furlan et al. 
(2017), and they represent an important advance in understanding the KOI 
sample's multiplicity statistics.
In particular, they can be immediately applied to rectify binarity's influence 
on the mass-radius diagram (Furlan \& Howell 2017).

For {\it Kepler}-derived occurrence rates, the high resolution imaging 
campaigns have not yet come full circle to observe a comparison sample of 
non-KOI host stars.
The most recent rate studies have thus used Furlan et al. (2017)'s 
catalog to test the effects of removing KOI hosts with known companions, which 
is an important step towards reducing contamination in the ``numerator'' of 
the occurrence rate (Fulton et al. 2017).
However, without an understanding of the multiplicity statistics of the 
non-KOI hosting stars that are assumed to be searchable, the 
true completeness, the true number of searchable stars, and thus the true 
occurrence rates will remain uncertain.

\paragraph{The Hot Jupiter Rate Discrepancy}
There is at least one context in which measurement of absolute 
occurrence rates may already be showing the signatures of binarity.
Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
marginally lower than those found by radial velocity surveys ($\approx 1\%$; 
see Table~\ref{tab:hj_rates}).
Though the discrepancy is of weak statistical significance ($<3\sigma$),
one plausible explanation for the difference is that the populations have 
distinct metallicities.
As originally argued by Gould et al. (2006), the RV sample is biased towards 
metal-rich stars, which have been measured by RV surveys to preferentially 
host more giant planets (Santos et al 2004, Fischer and Valenti 2005).
The {\it Kepler}\ sample specifically has been measured to be more metal poor 
than the local neighborhood, with a mean metallicity of $[{\rm M/H}]_{\rm 
mean}\approx -0.05$ (Dong et al., 2014; Guo et al., 2017).
Studying the problem in detail, Guo et al. recently argued that the 
metallicity difference could account for a $\approx 0.1\%$ difference in the 
measured rates between the CKS and {\it Kepler}\ samples~--~not a $\approx 
0.5\%$ difference.
Guo et al. concluded that ``other factors, such as binary contamination and 
imperfect stellar properties'' must also be at play.

Aside from surveying stars of varying metallicities, radial velocity and 
transit surveys differ in how they treat binarity.
Radial velocity surveys typically reject both visual and spectroscopic binaries
({\it e.g.}, Wright et al. 2012).
Transit surveys typically observe binaries, but the question of whether they 
were searchable to begin with is usually left for later interpretation.
In spectroscopic follow-up of candidate transiting planets, the prevalence of 
astrophysical false-positives may also lead to a bias against confirmation of 
transiting planets in binary systems.

Ignoring these complications, in this work we focus on whether
binarity might intrinsically bias transit survey occurrence rates, simply 
through its effects on the number of searchable stars and the apparent radii 
of detected planets.

To progressively gain intuition, we study the following idealized transit 
surveys:
\begin{itemize}
    \item Model \#1: fixed stars, fixed planets, twin binaries;
    \item Model \#2: fixed planets and primaries, varying secondaries;
    \item Model \#3: fixed primaries, varying planets and secondaries.
\end{itemize}
In Sec.~\ref{sec:numerical_methods}, we introduce our numerical approach 
to the problem, and in Sec.~\ref{sec:analytic_preliminaries} we clarify our 
terminology.
We present the analytic and numerical results in 
Secs.~\ref{sec:model_1}-\ref{sec:model_3}, where each subsection corresponds 
to each model above.
We interpret these calculations throughout, and in 
Sec.~\ref{sec:discussion} discuss their relevance to various questions in 
the interpretation of transit survey occurrence rates.

### 2017-11-06 paper/model_1.tex
paper: add Masuda comments

\subsection{Model \#1: fixed stars, fixed planets, twin binaries}
\label{sec:model_1}

Consider a universe in which all planets are identical, and all stars are 
either single or twin stars with otherwise identical physical properties.
The occurrence rate density at a planet radius $r$, stellar radius $R$, and 
semimajor axis $a$ for this model is
\begin{equation}
\Gamma(r,R,a) = \sum_i w_i \Lambda_i \delta^3(r_p,R_\star,a_p),
\label{eq:model1_occ_rate_density}
\end{equation}
for $r_p$ and $R_\star$ some fixed planet and stellar radii, $a_p$ a fixed 
semi-major axis, and $\delta$ the Dirac delta function, whose compact
form will be used for brevity.
The occurrence rate over any interval that includes $r_p$, $R_\star$, and 
$a_p$ is
\begin{equation}
\Lambda = \sum_i w_i \Lambda_i = \frac{ \sum_i N_i \Lambda_i }{N_{\rm tot}}.
\end{equation}
The rate is zero over intervals that do not.

To express the rate density of detected planets, $\hat{\Gamma} = \sum 
Q_i\Gamma_i$, we need the detection efficiencies for each system type, which 
are products of the geometric and selection probabilities:
\begin{align}
Q_i(\vec{x}) &= Q_{g,i}(\vec{x}) Q_{c,i}(\vec{x}),\quad {\rm where}\ 
\vec{x}=(r,R,a).
\label{eq:general_detection_efficiency}
\end{align}
Similar to Pepper et al. (2003), but in a new context, we take $Q_c$ as the 
ratio of the number of stars that were searchable to the number of stars that 
were selected.
Assuming a homogeneous distribution of stars, this gives
\begin{equation}
Q_{c,i}(\vec{x}) = \left(
\frac{d_{{\rm det},i}(\vec{x})}{d_{\rm sel}(\vec{x})}
\right)^3,
\end{equation}
for $d_{\rm sel}$ the maximum distance to which surveyed stars are selected, 
and $d_{{\rm det},i}$ the maximum distance to which planets can actually be 
detected about the $i^{\rm th}$ system type.
Note that $d_{\rm sel} \geq d_{{\rm det},i}$.
In a signal-to-noise limited transit survey in which the observer does not 
know which stars are binaries, 
\begin{equation}
d_{\rm sel} \propto (r/R)^2 (L_{\rm sys} T_{\rm dur} A N_{\rm tra})^{1/2},
\end{equation}
for $L_{\rm sys}=L_1(1+\ell)$ the system luminosity, $T_{\rm dur}$ the 
transit duration, $A$ the detector area, and $N_{\rm tra}$ 
the number of observed transits.
However,
\begin{equation}
d_{{\rm det},i} \propto \mathcal{D}_i(r/R)^2 (L_{\rm sys} T_{\rm dur} A N_{\rm 
tra})^{1/2},
\label{eq:d_det_i}
\end{equation}
for the dilution $\mathcal{D}_i$ given by
\begin{align}
\mathcal{D}_i
&=
\left.
\begin{cases}
1 & \text{for } i=0,\ {\rm single} \\
L_1 / L_{\rm sys} = (1+\ell)^{-1}, & \text{for } i=1,\ {\rm primary} \\
\ell L_1 / L_{\rm sys} = (1 + \ell^{-1})^{-1}, & 
    \text{for } i=2,\ {\rm secondary},
\end{cases}
\right.
\label{eq:dilution}
\end{align}
where the light ratio $\ell$ of a given binary is defined as the ratio of 
the luminosity of the secondary to the primary.

The maximum detectable distance to single stars is assumed to be known, and so 
$d_{{\rm sel},0} = d_{{\rm det},0}$.
For binary systems there is a necessary incompleteness, and combining 
Eqs.~\ref{eq:general_detection_efficiency} through~\ref{eq:dilution} yields
\begin{align}
Q_0 &= Q_{g,0}Q_{c,0} = Q_{g,0} \label{eq:detection_efficiency_0}\\
Q_1 &= Q_{g,1}Q_{c,1} = Q_{g,0} (1+q^\alpha)^{-3} \\
Q_2 &= Q_{g,2}Q_{c,2} = Q_{g,0} q^{2/3} (1+q^{-\alpha})^{-3} q^{-5}, 
\label{eq:detection_efficiency_2}
\end{align}
for $Q_{g,0}=R/a$, the transit probability in single star systems.
In Eq.~\ref{eq:detection_efficiency_2}, we have assumed a stellar 
mass-luminosity-radius relation: $R\propto M \propto L^{1/\alpha}$.
The geometric transit probability is $Q_{g,2} = Q_{g,0}q^{2/3}$, and the 
completeness is the latter term of Eq.~\ref{eq:detection_efficiency_2}.
For $q=1$, the $q^{2/3}$ and $q^{-5}$ evaluate to unity, but they will later 
become relevant.

Summarizing, we have written the rate density for each system type
(Eq.~\ref{eq:model1_occ_rate_density}) and the detection efficiency for each 
system type 
(Eq.~\ref{eq:detection_efficiency_0}-\ref{eq:detection_efficiency_2}),
and so have fully specified the rate density of detected planets, 
in addition to the true rate density.

\paragraph{What does an observer ignoring binarity infer?} 
An observer who ignores binarity assumes a detection efficiency 
$\tilde{Q}=Q_0$,
measures a detected planet rate density $\tilde{\Gamma}$, 
and infers an apparent rate density $\Gamma_a$.
Analogous to Eq.~\ref{eq:detected_rate_density},
\begin{equation}
\tilde{\Gamma} = \Gamma_a \tilde{Q}.
\end{equation}
Accounting for dilution, and assuming $q=1$, the apparent rate density is
\begin{equation}
\Gamma_a = 
w_a \Lambda_0 \delta^3(r_p, R_\star, a_p) +
w_b (\Lambda_1 Q_{c,1} + \Lambda_2 Q_{c,2}) 
				\delta^3(r_p/\sqrt{2}, R_\star, a_p),
\end{equation}
for $w_a = N_0/(N_0+N_1)$, and $w_b = N_1/(N_0+N_1)$.
This observer miscounts the number of total searched stars, does not correct 
for incompleteness, and misclassifies the planetary radii because of dilution.

\paragraph{Correction to inferred rate density and inferred rate}

Define a rate density correction factor, $X_\Gamma$, as the ratio of the 
apparent to true rate densities:
\begin{equation}
X_\Gamma \equiv \frac{\Gamma_a}{\Gamma}.
\end{equation}
This factor can be a function of whatever parameters $\Gamma_a$ and $\Gamma$ 
depend on; in this study, the planet radius is most relevant.
For the twin-binaries model,
\begin{equation}
X_\Gamma(r)
=
\frac{w_a \Lambda_0\delta^3(r_p) + 
	w_b(\Lambda_1 Q_{c,1} + \Lambda_2 Q_{c,2}) \delta^3(r_p/\sqrt{2})  }
	{(w_0\Lambda_0 + w_1\Lambda_1 + w_2\Lambda_2)\delta^3(r_p)}
	\label{eq:model1_correction}
	\end{equation}
where $\delta^3(r_p)$ is shorthand for $\delta^3(r-r_p,R-R_\star,a-a_p)$.

If we take the rates $\Lambda_i$ to be equal, applying the definitions of 
the weights gives a rate density correction factor at $r=r_p$ of
$X_\Gamma(r_p) = (1+\mu)^{-1}$, where 
\begin{align}
\mu \equiv \frac{N_1}{N_0} &=
\frac{n_b}{n_s} \left(\frac{d_{\rm sel,b}}{d_{\rm sel,s}}\right)^3 = 
\frac{{\rm BF}}{1-{\rm BF}} (1+\ell)^{3/2},
\label{eq:mu_definition}
\end{align}
for $n_b$ and $n_s$ the number density of binaries and singles in a 
volume limited sample.
Using Raghavan et al. (2010)'s $0.7-1.3M_\odot$ multiplicity fraction as our 
binary fraction\footnote{
The binary fraction is the fraction of systems in a volume-limited sample that 
are binary. It is equivalent to the multiplicity fraction if there are no 
triple, quadruple, or higher order multiples. In that case, ${\rm BF} = n_b / 
(n_s+n_b)$.
}, we set ${\rm BF}=0.44$.
The resulting correction to the rate density is $X_\Gamma(r_p) \approx 0.31$. 
The correction at $r_p/\sqrt{2}$ is infinite.
The numerical realization of this model agrees with these analytic values, and 
its output is shown in Fig~\ref{fig:errcases_model_1}.
%beta = 2.2223355980148636
If instead we assume that $\Lambda_0 = \Lambda_1$, but that $\Lambda_2=0$, we 
find 
$X_\Gamma(r_p) = (1+2\mu)/(1+\mu)^2$.
Taking the same binary fraction, this evaluates to $X_\Gamma(r_p)\approx 0.53$.
Since the correction to the rate is equal to that of rate density, at 
$r=r_p$, the occurrence rate is underestimated by a factor of roughly 2 to 3.

%Note that a correction to the inferred rate, $X_\Lambda$, can be 
%defined analogously:
%\begin{equation}
%X_\Lambda \equiv \frac{\Lambda_a}{\Lambda}.
%\end{equation}
%For this twin binary model, the correction to the rate is the same as that to 
%the rate density.

### 2017-11-06 paper/model_2.tex
paper: add Masuda comments

\subsection{Model \#2: fixed planets and primaries, varying secondaries}
\label{sec:model_2}

The main use of our binary-twin model is to help develop intuition.
We now let the light ratio $\ell = L_2/L_1$ vary across the binary 
population.
It does so because the underlying mass ratio $q=M_2/M_1$ varies.
We keep the primary mass fixed as $M_1$, which is also the mass of all single 
stars.

We parametrize the distribution of binary mass ratios in a volume-limited 
sample as a power law: $p(q)\propto q^\beta$.
For binaries with solar-type primaries\footnote{
Duchene and Kraus (2013), fitting all the multiple systems of Raghavan et al. 
(2010)'s Fig 16, find $\beta = 0.28\pm0.05$ for $0.7<M_\star/M_\odot<1.3$.
Examining only the binary systems of Rhagavan et al 2010, Fig 16, the 
distribution seems roughly uniform, $\beta \approx 0$, except for a claimed 
excess of twin binaries with $q\approx 1$, and an obvious lack of $q<0.1$ 
stellar companions.
}, $\beta$ is probably between 0 and 0.3.
Since we assume stars are a one-parameter family, $R \propto M \propto 
L^{1/\alpha}$, a drawn value of $q$ determines everything about a secondary.

The rate density in this model, $\Gamma(\vec{x})$, is the sum over system 
types of $w_i \Lambda_i p_i(\vec{x})$:
\begin{equation}
\Gamma(\vec{x})
=
\delta^4(r_p,R_\star,a_p,P_p)(w_0 \Lambda_0 + w_1 \Lambda_1)
+ w_2 \Lambda_2 \delta^3(r_p, P_p, a_p) p_2(q),
\label{eq:model2_rate_density}
\end{equation}
where the semimajor axis of the planet must be such that its period is $P_p$, 
and $p_2(q)$ is expressed in terms of the mass ratio instead of the secondary 
star's radius for convenience ($q$ and $R_2$ are interchangeable).
The probability that a secondary hosts a planet, as a function of the mass 
ratio, is
\begin{align}
p_2(q) &= p({\rm has\ planet}\,|\,{\rm secondary\ with\ }q) \times
          p({\rm secondary\ with\ }q)
          \\
p_2(q) &\propto q^{\gamma + \beta} (1+q^\alpha)^{3/2}.
\label{eq:model_2_p_2}
\end{align}
We take first term, $p({\rm has\ planet}\,|\,{\rm secondary\ with\ }q)$, as a 
power law of $q$ with exponent $\gamma$.
For the second term, since the selected sample at a given $(r,P,a)$ is
magnitude-limited, $p({\rm secondary\ with\ }q)$ 
is the product of the volume limited probability, $q^\beta$, and a 
Malmquist-like bias, $(1+q^\alpha)^{3/2}$.
We note that various authors (probably ourselves included) have incorrectly 
drawn from volume-limited binary distributions in Monte Carlo simulations of 
transit surveys (Sullivan et al 2015, Bakos et al 2012, Guenther et al 
2017, Bouma et al 2017).
The correct distribution for a magnitude-limited selection is shown in 
Fig.~\ref{fig:q_distribn_mag_limited}.

The occurrence rate corresponding to Eq.~\ref{eq:model2_rate_density}'s rate 
density for a desired volume of phase space $\Omega_{\rm desired}$ is given by 
Eq.~\ref{eq:occ_rate}.
Specifying the desired mass ratios of interest as $q_{\rm min} < q < q_{\rm 
max}$, this simplifies to
\begin{equation}
\Lambda = 
\frac{N_0 \Lambda_0 + N_1 \Lambda_1 + N_2 \Lambda_2 f_2}
{N_{\rm tot}},
\end{equation}
for
\begin{equation}
f_2 \equiv
\left(
\int_{q_{\rm min}}^{q_{\rm max}} p_2(q) \,{\rm d}q
\right)
\cdot
\left(
\int_{0}^{1} p_2(q) \,{\rm d}q
\right)^{-1}.
\end{equation}

The detected rate density, $\hat{\Gamma} = \sum_i Q_i \Gamma_i$, will be 
specified by the detection efficiencies for each type of system.
These are identical to 
Eqs.~\ref{eq:detection_efficiency_0}-\ref{eq:detection_efficiency_2}.
The detection efficiency for secondaries (Eq.~\ref{eq:detection_efficiency_2}) 
includes the transit probability from the smaller stellar radius, and combines 
dilution, the transit duration, and stellar radius for the completeness
probability.

\paragraph{What does an observer ignoring binarity infer?}
As a reminder, the apparent rate density is found by correcting the detected 
apparent rate density for the transit probability:
$\Gamma_a = \tilde{\Gamma} Q_{g,0}^{-1}$.
The observer's errors are as follows:
\begin{enumerate}
    \item The true planetary radii $r$ are interpreted as apparent radii $r_a$.
    The apparent radii depend on the system type:
    \begin{align}
    r_a
    &=
    \left.
    \begin{cases}
    r_p (1+q^\alpha)^{-1/2} & \text{for } i=1,\ {\rm primary} \\
    r_p (1+q^{-\alpha})^{-1/2} q^{-1}, & \text{for } i=2,\ {\rm secondary}.
    \end{cases}
    \right.
    \label{eq:model2_ra}
    \end{align}
    The factor of $q^{-1}$ for the secondary case accounts for the observer 
    assuming that the host star is the primary.
    \item The completeness fraction is miscalculated for any stars in binary 
    systems.
    \item The selected and searchable stars are miscounted.
\end{enumerate}

To write the apparent rate density as a function of the apparent 
radius $r_a$, we marginalize out the planet period, semimajor axis, and 
stellar radius (or equivalently the mass ratio, for binaries):
\begin{equation}
\Gamma_a(r_a) =
w_a \Lambda_0 \delta(r_p)
+
w_b \Lambda_1 I_1(r_a)
+
w_b \Lambda_2 I_2(r_a),
\label{eq:model2_Gamma_a}
\end{equation}
where the detection efficiencies are given in 
Eqs.~\ref{eq:detection_efficiency_0}-\ref{eq:detection_efficiency_2}, and as 
in the first model, $w_a=N_0/(N_0+N_1)$, $w_b=N_1/(N_0+N_1)$. The ratio of 
primaries to singles, $\mu$, is now less than that of Model \#1 (cf. 
Eq.~\ref{eq:mu_definition}). This is because a distribution of light ratios 
$\ell$ leads to a distribution of maximum selected distances. Integrating over 
the mass ratios, one finds
\begin{equation}
\mu \equiv \frac{N_1}{N_0} = \frac{\rm BF}{1 - {\rm BF}} \left(2^{3/2} - 
\int_{1}^{\sqrt{2}} u^2 (u^2 -1)^{1/\alpha} \,{\rm d}u\right).
\label{eq:mu_model_2}
\end{equation}

This fully specifies the weights in Eq.~\ref{eq:model2_Gamma_a}.
The $I_1(r_a)$ and $I_2(r_a)$ terms are found by marginalizing over the joint 
distribution of apparent radius and mass ratio:
\begin{align}
I_i(r_a) &= 
\int_0^1 p({\rm has\ detected\ planet}, r_a, q | {\rm star\ is\ type\ }i)
    \,{\rm d}q,
\quad
{\rm for}\ i\in\{1, 2\}, \\
&=
\int_0^1 
    p({\rm has\ detected\ planet} | r_a, q, {\rm star\ is\ type\ }i) 
    \nonumber\\
    &\quad\quad\quad\quad\times p(r_a | q, {\rm star\ is\ type\ }i)
    \,p(q | {\rm star\ is\ type\ }i)
\,{\rm d}q.
\end{align}
The first term is the detection efficiency; the second is a $\delta$-function 
of the apparent radius; the last is the mass ratio distribution given by 
Eq.~\ref{eq:model_2_p_2}.
The analytic solution for $i=1$ is
\begin{equation}
I_1(r_a) = \frac{1}{\mathcal{N}_1} \left(\frac{r_p}{r_a}\right)^{-3}
\left( \left(\frac{r_p}{r_a}\right)^2 -1  
    \right)^{\frac{\gamma+\beta}{\alpha}},
\quad {\rm for}\ r_p/\sqrt{2} < r_a < r_p,
\end{equation}
where $\mathcal{N}_1$ is the normalization term of the binary mass ratio 
distribution (Eq.~\ref{eq:model_2_p_2}): $\mathcal{N}_1 = \int_0^1 
q^{\gamma+\beta} (1+q^\alpha)^{3/2} {\rm d}q$.

For $i=2$, there is no analytic solution, because evaluating the integral 
requires imposing the constraint that $r_a  = r_p 
(1+q^{-\alpha})^{-1/2}q^{-1}$. This equation can be re-written
\begin{equation}
\left(\frac{r_p}{r_a}\right)^2 = q^2 + q^{-\alpha + 2},
\end{equation}
which has no analytic solution except for special values of $\alpha$, the 
mass-luminosity exponent.
For $\alpha=3.5$, our nominal case, semianalytic solutions could be found.
However, since our main interest is in understanding the qualitative behavior 
of the solutions, we focus on a few limiting cases, and proceed numerically.

\paragraph{Correction to inferred rate density}
Recall that the rate density correction factor, $X_\Gamma$, is the ratio of 
the apparent to true rate densities.
We consider a ``nominal model'' in which the stellar population is similar to 
Sun-like stars in the local neighborhood:
${\rm BF}=0.44$, $\alpha=3.5$, $\beta=0$.
Our default assumption is also that the occurrence of planets is independent 
of stellar mass ($\gamma=0$), so secondaries have the same occurrence rate as 
primaries and single stars.
Under these assumptions, the planetary rate density is
\begin{equation}
\Gamma(r) \approx \delta(r_p) \left( \Lambda_0 + \Lambda_1 + 
\Lambda_2 \right) / 3,
\label{eq:model2_Gamma_r}
\end{equation}
where the coefficients of $1/3$ are accurate to within one percent of the true 
coefficients.
Ignoring binarity, the observer finds an apparent rate density
\begin{equation}
\Gamma_a(r) = c_0 \Lambda_0 \delta(r_p)
             +c_1 \Lambda_1 I_1(r_a)
             +c_2 \Lambda_2 I_2(r_a),
\label{eq:model2_Gamma_a_r}
\end{equation}
for $c_0\approx 0.49$, $c_1\approx 0.32$, $c_2\approx 0.03$.
%171011_integrals.nb
Evaluating the correction term at $r=r_p$, since $\lim_{q\rightarrow0} 
p_i(r_a)=0$ for $i\in\{1,2\}$,
\begin{equation}
X_\Gamma(r=r_p) \approx \frac{3c_0 \Lambda_0}{\Lambda_0+\Lambda_1+\Lambda_2}.
\end{equation}
If all the rates are equal, $X_\Gamma(r=r_p)\approx0.49$.
If there are no planets around the secondaries, $X_\Gamma(r=r_p)\approx0.74$.

We also run this model in our numerical simulation.
The results are shown in Figs.~\ref{fig:errcases_model_2_linear} 
and~\ref{fig:errcases_model_2_log}.
They produce the same correction factors as predicted analytically.
They also show a peak in the inferred rate at $r_p/\sqrt{2}$ from 
secondaries.
This effect requires the observer to incorrectly estimate the host star's 
radius; if they somehow knew the host star's radius, but did not correct for 
binary dilution, the peak would instead be at an apparent radius of 0.

To summarize, dilution produces a spectrum of apparent planetary radii. In 
this model, this produces overestimated rates everywhere except where there 
are actually planets, where the rate is underestimated by a factor of 2.

### 2017-11-06 paper/model_3.tex
paper: add Masuda comments

\subsection{Model \#3: Fixed primaries, varying planets and secondaries}
\label{sec:model_3}

In this model, as in the previous one, all single and primary stars have 
identical properties.
Only the secondaries have masses, radii, and luminosities that vary between 
systems: $M\propto R \propto L^{1/\alpha}$.
The radii of planets are assigned independently of any host system
property, and are sampled from an intrinsic radius distribution, which we take 
as
\begin{align}
p_r(r)
&\propto
\left.
\begin{cases}
r^\delta & \text{for } r\geq 2r_\oplus \\
{\rm constant} & \text{for } r\leq2r_\oplus.
\end{cases}
\right.
\label{eq:model3_radius_distribution}
\end{align}
Following Howard et al. (2012)'s measurement, we take $\delta = -2.92$.
Our ``nominal model'' remains the same: the binary fraction is 0.44, 
$\alpha=3.5$, $\beta=\gamma=0$.
We take $\Lambda_i$, the occurrence rate integrated over all possible phase 
space for the $i^{\rm th}$ system type, to be equal for singles, primaries, 
and secondaries.

For this model, we forgo analytic development and focus only on numerics 
(Sec.~\ref{sec:numerical_methods}).
The nominal results are shown in Fig.~\ref{fig:errcases_model_3_log}.
For the assumed planetary and stellar distributions, the inferred rate is 
underestimated over all radii.

\paragraph{Hot Jupiter Occurrence Rates}
Taking Fig.~\ref{fig:errcases_model_3_log} and counting the number of planets 
per star with $r>8r_\oplus$, we can compare the true and inferred hot Jupiter 
occurrence rates.
Under the above assumptions, the true rate is 9.1 hot Jupiters 
per thousand stars.
The inferred rate is 6.9 per thousand stars.
This means that the inferred rate underestimates the true rate by a 
multiplicative factor of $\sim\!1.3$.

However, this result only applies under the assumption that $\Lambda_0 = 
\Lambda_1 = \Lambda_2$.
If hot Jupiters are less common around lower mass stars, it would be more 
sensible to consider $\Lambda_2<\Lambda_0$, while letting single stars and 
primaries host planets at the same rate.
Therefore in Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues} we let 
$\Lambda_2$ vary, and show the resulting inferred and true hot Jupiter 
($r>8r_\oplus$) rates.
The result is that the inferred rate is nearly independent of 
$\Lambda_2$~--~this is because most ($<1/10$) secondaries are not searchable, 
and so their completeness fraction is much smaller than that of primaries or 
single stars.
This means far fewer detected hot Jupiters orbit secondaries, and so they 
hardly affect the inferred rate.
While the ``true rate'' across the entire population is highly dependent on 
$\Lambda_2$, as one would expect from Eq.~\ref{eq:occ_rate}, the rate around 
singles and primaries (green line) is independent of that around secondaries.
Assuming that RV surveys are measuring the true rate around single stars (or 
primaries), this suggests that binarity might contributes to the 
HJ rate discrepancy at the $\sim 0.2\%$ level, independent of the HJ rate 
around secondaries.

\paragraph{The Rate of Earth Analogs}
The rate (density) of Earth-like planets orbiting Sun-like stars has 
been independently measured by Youdin, Petigura, Dong \& Zhu, 
Foreman-Mackey et al., and Burke et al., (2011, 2013, 2013, 2014, and 2015 
respectively).
These efforts have found that the one-year terrestrial planet occurrence rate 
varies between $\approx 0.03$ and $\approx 1$ per Sun-like star, depending on 
assumptions that are made when retrieving the rate (Burke et al. 2015's 
Fig.~17).

Our model does not explicitly include the rate density's period-dependence, 
because stellar binarity does not appreciably bias the period-dependence of 
occurrence rates measured by transit surveys\footnote{
    Note that stellar binarity does bias the {\it intrinsic} planet 
    occurrence as a function of planetary and binary periods. This is expected 
    from dynamical stability limits in $\geq$3 body systems, and has been 
    observationally confirmed (theory by Holman \& Wiegert 1999, and others 
    including Gongjie; confirmation from Wang et al 2014a, 2014b, Kraus et al 
    2014). 
    However our statement is that inferred rates as a function of planet     
    period should be negligibly affected by this, given the geometric bias 
    against long-period transit detections, and the fact that the period 
    distribution of solar-type binaries peaks at $\approx 100\,{\rm years}$ 
    (Raghavan et al 2010, Fig.~13).
}.
Instead, it allows us to evaluate the difference in the apparent and true rate 
as a function of radius 
(Fig.~\ref{fig:errcases_model_3_log}).
At Earth's radius, the result is that the inferred rate is $0.84\times$ the 
true rate around single stars, assuming that the $\Lambda_i$'s are equal.
Similar to the above case of the hot Jupiters, if we vary the true $\Lambda_2$ 
while keeping $\Lambda_0 = \Lambda_1$, the ratio of the inferred to true rate 
around single stars hardly 
changes; $(\Lambda_{\rm inferred}/\Lambda_1)_{r=r_\oplus} \approx 0.135$, to 
within a few percent, independent of $\Lambda_2$ (shown in 
Fig.~\ref{fig:earth_inputrate_vs_etaearthratevalues}).
The ratio of the inferred to the true rate, $(\Lambda_{\rm 
inferred}/\Lambda)_{r=r_\oplus}$ varies substantially, but by at most $50\%$ 
in the (unrealistic) limiting case that secondaries do not host planets.

### 2017-11-06 paper/main.tex
update authors

\documentclass[12pt,modern]{aastex61}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{comment}

\shortauthors{Bouma, Winn, Masuda}
\shorttitle{Binarity and Occurrence Rates}

\begin{document}

\title{ The effects of binarity on planet occurrence rates measured by transit 
surveys}

\author{
L. G. Bouma, J. N. Winn, K. Masuda
}

\begin{abstract}

This work aims to clarify the biases that stellar binarity introduces
to occurrence rates inferred from transit surveys.
In general, stellar multiplicity leads to diluted planetary 
radii, overestimated detection efficiencies, and an undercounted number of 
selected stars (though possibly an overcounted number of searched stars).
These effects skew occurrence rate measurements in different directions, and 
we develop simple models that allow us to understand the crucial effects.
For models in which all stellar systems are either single or twin binaries, 
and all planets are identical, we find that ignoring binarity leads to a
two-to-threefold underestimate of the occurrence at the true radius.
We believe this represents an upper bound on binarity's effects.
Using more realistic models for the stellar population and planetary 
radii, we find that ignoring binarity leads to a $10$\,-\,$30\%$ 
underestimate of the number of planets per star, depending on planet radii.
For the occurrence of Earth-sized planets, in our most realistic model the 
underestimate is by $\approx 15\%$~--~at present far smaller than 
systematic uncertainties on real measurements of this number.
For hot Jupiters, we find that the inferred occurrence rate is 
$\approx 1.3\times$ smaller than the true rate around single stars.
We suggest that this latter effect contributes to the discrepant hot Jupiter 
rates measured by {\it Kepler}\ and the California group's respective surveys.
\end{abstract}

\input{introduction}
\input{methods}
\input{results}
\input{discussion}
\input{conclusion}

%\acknowledgements
%It was a pleasure to share discussions with Kento Masuda, who pointed us in 
%this direction, and helped clarify that something like this was worth studying.

\input{figures.tex}
\input{hj_rates.tex}

\end{document}

### 2017-11-09 paper/figures.tex
add fig to visualize volumes

\newpage
\begin{figure}
    \begin{center}
        \includegraphics[width=\textwidth]{figures/visualize_volumes.pdf}
    \end{center}
    \caption{
    Cartoon of the different selected and searchable volumes for single 
    stars (left column), and twin binaries (right column).
    This model (\#1) assumes all stars have equal mass and luminosity.
    Since the observer does not recognize the brighter binaries, they select 
    them out to a larger distance, $\sqrt{2}\times$ that of single stars.
    However, dilution causes the twin binaries to only be searchable in one 
    eighth of their selected volume.
    }
    \label{fig:model_1_volumes}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics[width=\textwidth]{figures/errcases_rate_density_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \caption{
    Inferred planet occurrence rates as a function of planet radius in Model 
    \#1.
    This model has fixed stars, fixed planets, and twin binaries.
    If the true planet radius is $r_p$, all planets 
    detected in binaries will have apparent radii $r_a = r_p/\sqrt{2}$.
    Only 1 in 8 selected binaries is actually searchable (see 
    Sec.~\ref{sec:model_1}).
    To help illustrate the individual effects of errors, we 
    separated them:
    ``only wrong $N_\star$'' means the only error is an incorrectly assumed 
    number of selected stars;
    ``only wrong $Q$'' means the only error is an incorrectly assumed 
    detection efficiency (including both miscalculated transit probabilities 
    and 
    fraction of selected stars that are searchable);
    ``only wrong $r_a$'' means the only error is misinterpretation of 
    planetary radii, due to both transit depth dilution and also wrongly 
    assumed host star radii.
    }
    \label{fig:errcases_model_1}
\end{figure}

\begin{figure}[!tb]
    \centering
    \includegraphics[width=\textwidth]{figures/q_distribn_mag_limited.pdf}
    \caption{
    The distribution of the mass ratio for a magnitude limited sample of 
    binary stars. The underlying mass ratios are drawn from a uniform 
    distribution in a volume-limited sample, quite similar to that of Raghavan 
    et al. (2010)'s Fig. 13.
    The entire bias can be understood analytically (Eq.~\ref{eq:model_2_p_2},
    with $\gamma=0$).
    The numerical comparison uses a realistic empirical mass-luminosity 
    relation rather than $L=M^{3.5}$, found by fitting main sequence dwarf 
    mass luminosity data compiled from Torres et al. [2009] and Benedict et 
    al. [2016].
    }
    \label{fig:q_distribn_mag_limited}
\end{figure}

\begin{figure}[!tb]
    \centering
    \includegraphics[width=.7\textwidth]{figures/errcases_rate_density_vs_radius_model_2.pdf}
    \caption{
    Inferred planet occurrence rates as a function of planet radius in Model 
    \#2.
    This model has fixed planets and primaries, but varying secondaries.
    }
    \label{fig:errcases_model_2_linear}
\end{figure}

\begin{figure}[!tb]
    \centering
    \includegraphics[width=.7\textwidth]{figures/errcases_rate_density_vs_radius_logs_model_2.pdf}
    \caption{
    Same as Fig.~\ref{fig:errcases_model_2_linear}, but with logarithmic 
    $y$-axis, and different $x$ scale.
    }
    \label{fig:errcases_model_2_log}
\end{figure}

\begin{figure}[!tb]
    \centering
    \includegraphics[width=\textwidth]{figures/errcases_rate_density_vs_radius_logs_model_3.pdf}
    \caption{
    Inferred planet occurrence rates as a function of planet radius in Model 
    \#3.
    This model has fixed primaries and single stars, but varying 
    secondaries.
    The true planet radius distribution is a power law with exponent $-2.92$ 
    above $2R_\oplus$, below which it is uniform (e.g., Howard et al., 
    2012).
    }
    \label{fig:errcases_model_3_log}
\end{figure}

\begin{figure}[!tb]
    \centering
    \includegraphics[width=.9\textwidth]{figures/HJ_correction_inputrate_vs_HJratevalues.pdf}
    \caption{
    $\Lambda_i$ is the occurrence rate integrated over all possible phase 
    space for the $i^{\rm th}$ system type. $\Lambda_2/\Lambda_0=1$ 
    corresponds to an equal number of planets per secondary as per single star;
    $\Lambda_2/\Lambda_0=0$ corresponds to secondaries not having any planets.
    In our Model \#3, though the true HJ occurrence rate 
    (Eq.~\ref{eq:occ_rate}) is highly dependent on $\Lambda_2$, 
    the inferred rate hardly depends on whether secondaries have HJs.
    This means that the ``correction factor'' between the inferred rate and 
    the true rate around single stars is underestimated by a multiplicative 
    factor of $\approx1.3$, independent of the HJ rate around secondaries.
    The ``HJ rate'' is the summed rate from     
    Fig.~\ref{fig:errcases_model_3_log} above $8r_\oplus$.
    }
    \label{fig:HJ_correction_inputrate_vs_HJratevalues}
\end{figure}

\begin{figure}[!tb]
    \centering
    \includegraphics[width=.9\textwidth]{figures/earth_inputrate_vs_etaearthratevalues.pdf}
    \caption{
        Same as Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues}, but 
        for Earth-sized planets.
        The absolute values given on the $y$-axis found by summing the rate 
        from Fig.~\ref{fig:errcases_model_3_log} for planetary radii from 
        $0.5$ to $1.5r_\oplus$ (this is a toy model, and they do not reflect 
        an actual determination of $\eta_\oplus$).
        The relative values show that the inferred rate for Earths is roughly 
        independent of the occurrence rate (integrated over all radii) around 
        secondaries.
        However, it is systematically lower than the true rate around single 
        and primary stars, by $\approx 20\%$.
    }
    \label{fig:earth_inputrate_vs_etaearthratevalues}
\end{figure}

%\begin{figure}[!b]
%    \begin{center}
%        \includegraphics[width=.9\textwidth]{figures/prob_r_a.pdf}
%    \end{center}
%    \caption{Model \#2 (Sec.~\ref{sec:model_2}): 
%    probability of observing an apparent radius $r_a$ given a 
%    planet orbiting the primary, $p_1(r_a)$, or the secondary, $p_2(r_a)$ of 
%    a 
%    binary system.
%    The true planet radius is fixed~--~a delta function centered on ``1''.
%    This plot takes $\alpha=3.5, \beta=0$, for $\alpha$ the exponent in 
%    the mass-luminosity relation $L \propto M^\alpha$, and $\beta$ the 
%    exponent in the distribution of mass ratios in a volume-limited sample.
%    Each distribution is separately normalized.
%    }
%    \label{fig:model2_prob_r_a}
%\end{figure}

### 2017-11-09 src/plot_visualize_volumes.py

@@ -1,0 +1,102 @@
+'''
+visualize the selected and searchable volumes for single stars and twin
+binaries.
+'''
+# -*- coding: utf-8 -*-
+from __future__ import division, print_function
+from matplotlib import rc
+rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('text', usetex=True)
+
+from mpl_toolkits.mplot3d import Axes3D
+import matplotlib.pyplot as plt
+import numpy as np
+from mpl_toolkits.mplot3d import proj3d
+
+def make_sphere(radius, txt, ax, ind):
+    # radius: float
+    # txt: what you want annotation to say
+    # ax: Axes3D instance
+    # ind: deals w/ obnoxious text placement
+
+    # Make data
+    u = np.linspace(-np.pi, np.pi, 500)
+    v = np.linspace(0, np.pi, 500)
+    x = radius * np.outer(np.cos(u), np.sin(v))
+    y = radius * np.outer(np.sin(u), np.sin(v))
+    z = radius * np.outer(np.ones(np.size(u)), np.cos(v))
+
+    # Plot the surface
+    surf = ax.plot_surface(x, y, z, color='skyblue', alpha=0.3, linewidth=0,
+            zorder=1)
+    # Make sure it's rasterized to prevent bloated figures. NB. matplotlib
+    # throws an error saying that this is ignored, but it's clearly not, b/c it
+    # slims the output plot by a factor of 10.
+    surf.set_rasterized(True)
+
+    ax.plot(radius*np.cos(u), radius*np.abs(np.sin(u)), 0, color='k', alpha=0.9,
+            zorder=2)
+
+    _x, _y = np.linspace(0,radius,100), np.linspace(0,radius,100)
+    ax.plot(-np.sqrt(_x**2+_y**2)/2, np.sqrt(_x**2+_y**2)/2, np.zeros_like(_x),
+            color='k', linestyle=':', zorder=3)
+
+    minbound, maxbound = -1, 1
+    ax.auto_scale_xyz(
+            [minbound, maxbound], [minbound, maxbound], [minbound, maxbound])
+
+    ax.view_init(30, 90)
+
+    #######################
+    # MAKE THE ANNOTATION #
+    #######################
+    #end of arrow
+    x1, y1, _ = proj3d.proj_transform(-2**(-3/2)*radius, 2**(-3/2)*radius, 0,
[…]

### 2017-11-09 src/hj_rate.py
add HJ rate stats calcn

@@ -1,0 +1,70 @@
+'''
+each Monte Carlo iteration asks the Q: how many HJs get detected?
+
+then we ask: what is the probability of getting at least 10 detected HJs if you
+survey a sample of 836 stars, given a rate drawn from the stated bounds of
+Petigura et al (in prep)?
+
+Made by pythonizing Josh Winn's IDL code asking the same question.
+'''
+from __future__ import division
+import numpy as np
+
+n_stars = 836 # number of stars in Wright et al (2012)
+n_HJ = 10 # number of HJs in Wright et al (2012)
+
+m = int(1e5)  # number of monte carlo iterations
+  
+eta = 5.7e-3 # Petigura+ in prep's reported HJ rate
+eta_unc = 1.3e-3
+  
+####################
+ndet = np.zeros((m))
+
+seed = 42
+
+for i in range(m):
+    np.random.seed(seed+i)
+    Lambda = eta + eta_unc*np.random.normal()
+    ndet[i] = np.random.poisson(n_stars*Lambda)
+
+q = ndet >= n_HJ
+
+print('p means fraction of MC trials with at least {:d} HJs'.
+        format(n_HJ))
+print('without taking Z or binaries into account, p = {:.2f}'.format(
+    np.sum(q)/m 
+    ))
+
+  
+####################
+eta *= 1.2
+ndet = np.zeros((m))
+
+seed = 42
+
+for i in range(m):
+    np.random.seed(seed+i)
+    Lambda = eta + eta_unc*np.random.normal()
+    ndet[i] = np.random.poisson(n_stars*Lambda)
+
+q = ndet >= n_HJ
+print('taking Z into account, p = {:.2f}'.format(
+    np.sum(q)/m 
+    ))
+
+####################
+eta *= 1.3
+ndet = np.zeros((m))
+
+seed = 42
+
+for i in range(m):
+    np.random.seed(seed+i)
+    Lambda = eta + eta_unc*np.random.normal()
+    ndet[i] = np.random.poisson(n_stars*Lambda)
+
+q = ndet >= n_HJ
+print('taking Z and binaries into account, p = {:.2f}'.format(
+    np.sum(q)/m 
+    ))

### 2017-11-09 paper/figures.tex
fig1: update caption

@@
     \caption{
-    Cartoon of the different selected and searchable volumes for single 
-    stars (left column), and twin binaries (right column).
-    This model (\#1) assumes all stars have equal mass and luminosity.
-    Since the observer does not recognize the brighter binaries, they select 
-    them out to a larger distance, $\sqrt{2}\times$ that of single stars.
-    However, dilution causes the twin binaries to only be searchable in one 
-    eighth of their selected volume.
+    In Model \#1, we assume all stars have equal mass and luminosity, and that 
+    the observer cannot resolve binary systems.
+    For single stars (left), at fixed planet size and period, the 
+    selected and searchable volumes are then identical.
+    Twin binaries (right) are twice as luminous, and so are selected 
+    out to a maximum distance $\sqrt{2}\times$ that of single stars 
+    (Eq.~\ref{eq:d_sel}).
+    However, the diluting light from the twin companion lowers the maximum 
+    distance at which a planet can be detected, relative to single stars, by 
+    $1/\sqrt{2}$ (Eq.~\ref{eq:d_det_i}).
     }

### 2017-11-10 src/plot_errcases_rate_densities_vs_radius.py
update errcases plot paths

@@ -46,7 +46,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
         ax=bigax
 
     if isinstance(Λ_2,float) or isinstance(Λ_2,int):
-        fname = '../data/numerics/results_model_{:d}_Lambda2_{:.1f}.out'.format(
+        fname = '../data/numerics/results_model_{:d}_Lambda2_{:.2f}.out'.format(
                 model_number, Λ_2)
     else:
         fname = '../data/results_model_'+repr(model_number)+'.out'
@@ -69,7 +69,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
     for error_case_number in [1,2,3]:
 
         if isinstance(Λ_2,float) or isinstance(Λ_2,int):
-            fname = '../data/results_model_{:d}_error_case_{:d}_Lambda2_{:.1f}.out'.format(
+            fname = '../data/numerics/results_model_{:d}_error_case_{:d}_Lambda2_{:.2f}.out'.format(
                     model_number, error_case_number, Λ_2)
         else:
             fname = '../data/results_model_{:d}_error_case_{:d}.out'.format(
@@ -110,7 +110,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
     else:
         ax.legend(loc='best',fontsize='medium')
 
-    ax.set_xlabel('planet radius, $r$ [$R_\oplus$]', fontsize='large')
+    ax.set_xlabel('planet radius, $r$ [$r_\oplus$]', fontsize='large')
 
     ax.set_ylabel('planets per star, $\Lambda$', fontsize='large')
 
@@ -142,7 +142,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
         #Howard 2012 boundary #1 and boundary #2:
         for lower_bound in [5.6,8]:
             if isinstance(Λ_2,float) or isinstance(Λ_2,int):
-                fname = '../data/results_model_{:d}_Lambda2_{:.1f}.out'.format(
+                fname = '../data/numerics/results_model_{:d}_Lambda2_{:.2f}.out'.format(
                         model_number, Λ_2)
             else:
                 fname = '../data/results_model_{:d}.out'.format(
@@ -159,7 +159,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
             for error_case_number in [1,2,3]:
 
                 if isinstance(Λ_2,float) or isinstance(Λ_2,int):
[…]

### 2017-11-10 paper/discussion.tex
paper WIP commit

--- 2017-11-06 paper/introduction.tex
@@
-\section{Introduction}
-
-An astronomer who does not believe in stellar multiplicity wants to measure the
-mean number of planets of a certain type per star of a certain type.
-They perform a signal-to-noise limited transit survey and detect $N_{\rm det}$ 
-transit signals that appear to be from planets of the desired type.  They 
-calculate the apparent number of searchable stars, $N_\star$.  ``Searchable 
-stars'' are the stars for which 
-planets are observed with 100\% detection efficiency. 
-Correcting for the geometric 
-transit probability $f_{\rm g}$, they compute an apparent occurrence rate 
-$\Lambda_{\rm a}$:
-
-\begin{equation}
-\Lambda_{\rm a} = \frac{N_{\rm det}}{N_\star} \times \frac{1}{f_g}.
-\end{equation}
-
-There are many potential pitfalls.  Some genuine transit signals can be missed
-by the detection pipeline.  Some apparent transit signals are spurious, from
-noise fluctuations, failures of `detrending', or instrumental effects.  Stars
-and planets can be misclassified due to statistical and systematic errors in
-the measurements of their properties.  Poor angular resolution causes false
-positives due to blends with background eclipsing binaries. {\it Et cetera}.
-
-Here we focus on problems that arise from the fact that many stars exist in 
-multiple star systems.
-For simplicity, we only consider binaries, and we assume that they are all 
-spatially unresolved.
-
-An immediate complication is that, due to dynamical stability or some 
-aspect of planet formation, the occurrence rate of planets may differ 
-between binary and single-star systems.
-If ``occurrence rate'' is defined purely as the mean number of planets within 
-set radius and period bounds per star in a given mass interval, it must 
-implicitly marginalize over stellar multiplicity.
-This means marginalizing over ``occurrence rates in single star systems'', 
-``occurrence rates about primaries'', and
-``occurrence rates about secondaries'' (see {\it e.g.,} Wang et al., 
-2015).
-
-Outside of astrophysical differences, there are observational biases.
-A given apparently-searchable star may truly be a single star of the desired 
-type. If it is binary, it may contain two, one, or no searchable stars of the 
-desired type, which affects $N_\star$.
-There may be systematic errors in stellar parameter estimates of such 
-systems, which in this work we neglect.
-One might also imagine an apparently-searchable star which in no stellar 
-component is of the desired type. We will not consider errors of this type.  
-We will assume that all the apparently-searchable stars are either single 
-stars of the desired type, or binaries in which either the primary or else 
-both components are of the desired type.
-
-When counting the detected signals from planets of the desired 
-type, $N_{\rm det}$, ignoring binarity leads to errors in planet radius 
-classification, and the assumed survey completeness.
-Detected planets in binary systems will have underestimated radii because of 
-the diluting flux from the companions, and possibly because they are assumed 
-to orbit the wrong star ({\it e.g.}, Furlan et al. 2017).
-The number of selected stars should change dependent on the planet radius 
-and period for which the rate measurement is desired, and on the survey's 
-achieved photometric precision.
-This means our naive astronomer assumes the fraction of their selected stars 
-which are searchable is 1 (this is their ``assumed completeness'').
-Binarity confuses this, because the ability to search for planets 
-in binary systems depends on which stellar component hosts the planet, and on 
-how much dilution affects the measurement.
+\section{Discussion}
+\label{sec:discussion}
 
 \paragraph{How Has Binarity Been Considered in Occurrence Rate Measurements?}
-Many authors have reported planet occurrence rates from transit 
+Many authors have computed planet occurrence rates using transit 
 survey data\footnote{
@@
 }.
-With regard to binarity, the typical approach has been to ignore the 
-issue\footnote{Deacon et al., 2015 are an exception to the rule.}.
-For instance, in a laudable study by Burke et al. (2015), they
-\begin{quote}
-``treat the pipeline completeness as having no uncertainty 
-due to the incomplete understanding of the stellar parameters, eccentricity, 
-and stellar binarity.''
-\end{quote}
-Though they do ``explore sensitivity in the derived planet occurrence rates 
-to alternative assumptions for the stellar parameters and non-zero 
-eccentricities'', they do not for binarity.
+Notable studies using {\it Kepler}\ data include those by Howard et al. 2012, 
+Fressin et al., 2013, Foreman-Mackey et al., 2014, Dressing \& Charbonneau 
+2015, and Burke et al. 2015.
+Mostly if not entirely, these studies have ignored stellar multiplicity.
+However, binarity certainly introduces a level of systematic uncertainty to 
+pipeline completeness, as well as to star and planet counts.
+No one has yet carefully studied the magnitude of this issue for 
+{\it Kepler} occurrence rates, and the present work does not resolve this 
+problem.
+%NOTE: the above might be better in a "discussion" section?
 
@@
 on the mass-radius diagram (Furlan \& Howell 2017).
+
+%TODO: talk about N. R. Deacon et al 2015, Pan-STARRS1 here
 
@@
 
-To progressively gain intuition, we study the following idealized transit 
-surveys:
-\begin{itemize}
-    \item Model \#1: fixed stars, fixed planets, twin binaries;
-    \item Model \#2: fixed planets and primaries, varying secondaries;
-    \item Model \#3: fixed primaries, varying planets and secondaries.
-\end{itemize}
-In Sec.~\ref{sec:numerical_methods}, we introduce our numerical approach 
-to the problem, and in Sec.~\ref{sec:analytic_preliminaries} we clarify our 
-terminology.
-We present the analytic and numerical results in 
-Secs.~\ref{sec:model_1}-\ref{sec:model_3}, where each subsection corresponds 
-to each model above.
-We interpret these calculations throughout, and in 
-Sec.~\ref{sec:discussion} discuss their relevance to various questions in 
-the interpretation of transit survey occurrence rates.
+\paragraph{Does a detected planet orbit the primary or secondary?}
+Ciardi et al. (2015) studied the effects of stellar multiplicity on the 
+planet radii derived from transit surveys.
+They modeled the problem for {\it Kepler}\ objects of interest by matching a 
+population of binary and tertiary companions to KOI stars, 
+under the assumption that the KIC-listed stars were the primaries.
+They then computed planet radius correction factors assuming that {\it 
+Kepler}-detected planets orbited the primary or companion stars
+with equal probability (their Sec. 5).
+Under these assumptions, they found that any given planet's radius is on 
+average underestimated by a multiplicative factor of 1.5.
+
+Our models show that assuming a detected planet has equal probability of 
+orbiting the primary or secondary leads to an overstatement of
+binarity's population-level effects.
+A planet orbiting the secondary does lead to extreme corrections, but these 
+cases are rare outliers, because the searchable volume for secondaries is so 
+much smaller than that for primaries.
+Phrased in terms of the completeness, in our Model \#3 only $\sim 6\%$ of 
+selected secondaries are searchable, compared to $\sim 60\%$ of selected 
+primaries.
+This means that when high-resolution imaging discovers a binary companion in 
+system that hosts a detected transiting planet, the planet is much
+more likely to orbit the primary.
+This statement is independent of the fact that planets are often confirmed to 
+orbit the primary by inferring the stellar density from the transit duration.
+
+\paragraph{On the utility for future occurrence rate measurements}
+Though they will be difficult to distinguish from false positives, {\it TESS}\ 
+is expected to discover over $10^4$ giant planets (Sullivan et al. 2015).
+One possible use of this overwhelmingly large sample will to measure an
+occurrence rate of short-period giant planets.
+Our work indicates that if this measurement is to be more precise than $\sim 
+30\%$, binarity cannot be neglected.
+
+\paragraph{What about {\it Kepler}?}
+Barclay \& Collaborator (in preparation) have performed the exercise 
+of taking stars selected by the {\it Kepler}\ team, pairing them with a 
+population of secondaries, injecting a realistic distribution of planet radii, 
+and then comparing the inferred occurrence rates with the true ones.
+In their model, they find that binarity leads to an inferred rate of 
+Earth-sized planets $\approx 10\%$ less than the true rate.
+In our Model \#3, if all $\Lambda_i$'s are equal (a plausible assumption in 
+the lack of evidence to the contrary), the underestimate is by 16\%.

### 2017-11-10 paper/generalities.tex
paper WIP commit

@@
-\subsection{Analytic Preliminaries}
-\label{sec:analytic_preliminaries}
-
-Define the occurrence rate density, $\Gamma$,
-as the expected number of planets per star per natural logarithmic bin 
-of planetary and stellar phase space:
+We define the occurrence rate density, $\Gamma$, as the expected number of 
+planets per star per bin of planetary or stellar phase space.
+Since we will mainly be concerned with the rate density's dependence on 
+planetary radii $r$, we write
 \begin{equation}
-\Gamma(\vec{x}) = \frac{d^n\Lambda}{\prod_{i=1}^{n} {\rm d} \ln x_i  }.
+\Gamma(r) = \frac{{\rm d}\Lambda}{{\rm d}r},
 \label{eq:rate_density_defn}
 \end{equation}
-$\vec{x}$ is an $n$-dimensional list of the continuous physical properties 
-that might affect the occurrence rate density. 
-For example,
-$\vec{x}=(r,P,R)$ where $r$ is the planet radius, $P$ is its orbital period, 
-and $R$ is the host star radius.
-The occurrence rate $\Lambda$ is found by integrating the rate density over a 
-specified volume of phase space (e.g., Youdin 2011).
+where $\Lambda$ is the occurrence rate.
+In this notation, ``the occurrence rate of planets of a particular size'' 
+translates to an integral of Eq.~\ref{eq:rate_density_defn}, evaluated over a 
+radius interval.
 
-The previous definition implicitly marginalizes the rate density over stellar 
+The above definition implicitly marginalizes the rate density over stellar 
 multiplicity.
-For simplicity, this work only considers single and binary star systems.
-Then for a selected population of stars and planets the rate density can be 
-written\footnote{
-    Eq.~\ref{eq:rate_density_marginalized} follows by writing the $i^{\rm 
-        th}$ system type's rate density as some normalization multiplied by a 
-    probability density:
-    $\Gamma_i(\vec{x}) = \mathcal{Z}_i p_i(\vec{x})$.
-    For Eq.~\ref{eq:rate_density_defn} to hold, we must have $\mathcal{Z}_i = 
-    \Lambda_i$.
-}
+In this study we only consider single and binary star systems.
+For a selected population of stars and planets, the rate density is then 
+the weighted sum of rate densities for each system type:
 \begin{equation}
-\Gamma(\vec{x})
-= \sum_{i=0}^{2} w_i \Gamma_i(\vec{x})
-= \sum_i w_i \Lambda_i p_i(\vec{x})
+N_{\rm tot} \Gamma(r) =
+N_0 \Gamma_0(r) +
+N_1 \Gamma_1(r) +
+N_2 \Gamma_2(r),
 \label{eq:rate_density_marginalized}
 \end{equation}
-where $i=0$ corresponds to single star systems, $i=1$ primaries of binaries, 
-and $i=2$ secondaries of binaries.
-$\Lambda_i$ is the occurrence rate integrated over all possible phase space  
-for the $i^{\rm th}$ system type, and $p_i(\vec{x})$ is the joint 
-probability density function so that $\Gamma_i(\vec{x}) = \Lambda_i 
-p_i(\vec{x})$.
-The weights are given by 
+where $i=0$ corresponds to single stars, $i=1$ to primaries of 
+binaries, and $i=2$ to secondaries of binaries.
+$N_{\rm tot} = \sum_i N_i$ is the total number of selected stars, and 
+$N_0,N_1,N_2$ are the number of selected single stars, primaries, and 
+secondaries.
+Since each selected binary system contributes both a 
+primary and secondary star, $N_1=N_2$.
+This redundancy in our notation will later prove its use.
+
+Finally, it is useful to write 
+$\Gamma_i(r)$, the rate density for each type of star, as the product of a 
+shape function and a constant:
 \begin{equation}
-w_i = N_i/N_{\rm tot},
+\Gamma_i(r) = \frac{{\rm d}\Lambda_i}{{\rm d}r} = Z_i p_i(r),
+\quad {\rm for}\ i\in\{0,1,2\}.
+\label{eq:rate_density_shape}
 \end{equation}
-for $N_{\rm tot} = \sum_i N_i$ the total number of selected stars, and 
-$N_0,N_1,N_2$ the number of selected single stars, primaries, and 
-secondaries respectively.
+The shape function is normalized to unity.
+The $Z_i$'s can be interpreted as each system type's occurrence rate 
+$\Lambda_i$, integrated over all planetary radii.
+They are equivalent to the number of planets per single star, primary, or 
+secondary.
+
+\begin{comment}
 Both $N_1$ and $N_2$ are equal to the number of selected points on 
@@
 is calculated in practice.
+\end{comment}

### 2017-11-10 paper/introduction.tex
paper WIP commit

@@
 
-An astronomer who does not believe in stellar multiplicity wants to measure the
-mean number of planets of a certain type per star of a certain type.
-They perform a signal-to-noise limited transit survey and detect $N_{\rm det}$ 
-transit signals that appear to be from planets of the desired type.  They 
-calculate the apparent number of searchable stars, $N_\star$.  ``Searchable 
-stars'' are the stars for which 
-planets are observed with 100\% detection efficiency. 
-Correcting for the geometric 
-transit probability $f_{\rm g}$, they compute an apparent occurrence rate 
-$\Lambda_{\rm a}$:
-
+A group of astronomers wants to measure the mean number of planets of a 
+certain type per star of a certain type.
+Ignoring stellar multiplicity, they perform a signal-to-noise limited transit 
+survey and detect $N_{\rm det}$ signals that seem to be from the desired 
+class of planet.
+They count the apparent number of selected stars, $N_\star$.
+Assuming their survey is limited by Poisson noise, our astronomers compute 
+their detection efficiency $p_{\rm det}$ as a function of planetary and 
+stellar properties, in order to know which of the selected stars were
+searchable.
+Correcting for the geometric transit probability $p_{\rm tra}$, they report an 
+apparent occurrence rate $\Lambda_{\rm a}$:
 \begin{equation}
-\Lambda_{\rm a} = \frac{N_{\rm det}}{N_\star} \times \frac{1}{f_g}.
+\Lambda_{\rm a} = \frac{N_{\rm det}}{N_\star} \times \frac{1}{p_{\rm tra}}
+								  \times \frac{1}{p_{\rm det}}.
+\label{eq:wouldnt_it_be_nice}
 \end{equation}
@@
 multiple star systems.
-For simplicity, we only consider binaries, and we assume that they are all 
+For simplicity, we consider only binaries, and we assume that they are all 
 spatially unresolved.
@@
 An immediate complication is that, due to dynamical stability or some 
-aspect of planet formation, the occurrence rate of planets may differ 
+aspect of planet formation, the occurrence rate of planets might differ 
 between binary and single-star systems.
-If ``occurrence rate'' is defined purely as the mean number of planets within 
+If ``occurrence rate'' is defined as the mean number of planets within 
 set radius and period bounds per star in a given mass interval, it must 
@@
 
-Outside of astrophysical differences, there are observational biases.
-A given apparently-searchable star may truly be a single star of the desired 
-type. If it is binary, it may contain two, one, or no searchable stars of the 
-desired type, which affects $N_\star$.
-There may be systematic errors in stellar parameter estimates of such 
-systems, which in this work we neglect.
-One might also imagine an apparently-searchable star which in no stellar 
-component is of the desired type. We will not consider errors of this type.  
-We will assume that all the apparently-searchable stars are either single 
-stars of the desired type, or binaries in which either the primary or else 
-both components are of the desired type.
+Outside of astrophysical differences, there are observational biases for every 
+term in Eq.~\ref{eq:wouldnt_it_be_nice}.
+There are errors in $N_{\rm det}$ due to planet radius misclassification.
+There are errors in $N_\star$ because a given selected star might in fact be 
+two stars.
+There are errors in $p_{\rm tra}$ because stars in binaries may have different 
+masses and radii than assumed in the single-star case.
+Finally, there are errors in $p_{\rm det}$ because the detection efficiencies 
+of planets that orbit single stars, primaries, and secondaries are all 
+different.
 
-When counting the detected signals from planets of the desired 
-type, $N_{\rm det}$, ignoring binarity leads to errors in planet radius 
-classification, and the assumed survey completeness.
-Detected planets in binary systems will have underestimated radii because of 
-the diluting flux from the companions, and possibly because they are assumed 
-to orbit the wrong star ({\it e.g.}, Furlan et al. 2017).
-The number of selected stars should change dependent on the planet radius 
-and period for which the rate measurement is desired, and on the survey's 
-achieved photometric precision.
-This means our naive astronomer assumes the fraction of their selected stars 
-which are searchable is 1 (this is their ``assumed completeness'').
-Binarity confuses this, because the ability to search for planets 
-in binary systems depends on which stellar component hosts the planet, and on 
-how much dilution affects the measurement.
+Correcting for binarity's observational biases is non-trivial.
+For instance, in counting the number of selected stars, even after realizing 
+that binaries count as two stars, one must note that the multiplicity 
+fraction of {\it selected} stars is greater than that of a volume limited 
+sample.
+This is the familiar Malmquist bias: binaries are selected out to larger 
+distances than single stars because they are more luminous.
+As a separate challenge, finding the correct number of detected planets in a 
+radius bin, $N_{\rm det}$, requires knowledge of the true planetary radii.
+Observers deduce apparent radii.
+In binaries, the apparent and true radii differ because of diluting flux, 
+and possibly because the planet is assumed to orbit the wrong star ({\it 
+e.g.}, Furlan et al. 2017).
+%Finally, the detection efficiency $p_{\rm det}$ is different for selected 
+%stars in binary systems than it is in single systems.
 
-\paragraph{How Has Binarity Been Considered in Occurrence Rate Measurements?}
-Many authors have reported planet occurrence rates from transit 
-survey data\footnote{
-    An online list of occurrence rate papers is maintained at 
-    \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
-}.
-With regard to binarity, the typical approach has been to ignore the 
-issue\footnote{Deacon et al., 2015 are an exception to the rule.}.
-For instance, in a laudable study by Burke et al. (2015), they
-\begin{quote}
-``treat the pipeline completeness as having no uncertainty 
-due to the incomplete understanding of the stellar parameters, eccentricity, 
-and stellar binarity.''
-\end{quote}
-Though they do ``explore sensitivity in the derived planet occurrence rates 
-to alternative assumptions for the stellar parameters and non-zero 
-eccentricities'', they do not for binarity.
-
-Of course, on a system-by-system level stellar multiplicity affects the 
-interpretation of planet candidates. High resolution imaging 
-campaigns have consequently been undertaken to measure the multiplicity of 
-almost all {\it Kepler}\ Objects of Interest 
-(Howell et al. 2011; Adams et al. 2012, 2013; Horch et al. 2012, 2014; 
-Lillo-Box et al. 2012, 2014; Dressing et al. 2014; Law et al. 2014; Cartier et 
-al. 2015; Everett et al. 2015; Gilliland et al. 2015; Wang et al. 2015a, 
-2015b; Baranec et al. 2016).
-The results of these programs have been collected by Furlan et al. 
-(2017), and they represent an important advance in understanding the KOI 
-sample's multiplicity statistics.
-In particular, they can be immediately applied to rectify binarity's influence 
-on the mass-radius diagram (Furlan \& Howell 2017).
-
-For {\it Kepler}-derived occurrence rates, the high resolution imaging 
-campaigns have not yet come full circle to observe a comparison sample of 
-non-KOI host stars.
-The most recent rate studies have thus used Furlan et al. (2017)'s 
-catalog to test the effects of removing KOI hosts with known companions, which 
-is an important step towards reducing contamination in the ``numerator'' of 
-the occurrence rate (Fulton et al. 2017).
-However, without an understanding of the multiplicity statistics of the 
-non-KOI hosting stars that are assumed to be searchable, the 
-true completeness, the true number of searchable stars, and thus the true 
-occurrence rates will remain uncertain.
-
-\paragraph{The Hot Jupiter Rate Discrepancy}
-There is at least one context in which measurement of absolute 
-occurrence rates may already be showing the signatures of binarity.
-Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
-marginally lower than those found by radial velocity surveys ($\approx 1\%$; 
-see Table~\ref{tab:hj_rates}).
-Though the discrepancy is of weak statistical significance ($<3\sigma$),
-one plausible explanation for the difference is that the populations have 
-distinct metallicities.
-As originally argued by Gould et al. (2006), the RV sample is biased towards 
-metal-rich stars, which have been measured by RV surveys to preferentially 
-host more giant planets (Santos et al 2004, Fischer and Valenti 2005).
-The {\it Kepler}\ sample specifically has been measured to be more metal poor 
-than the local neighborhood, with a mean metallicity of $[{\rm M/H}]_{\rm 
-mean}\approx -0.05$ (Dong et al., 2014; Guo et al., 2017).
-Studying the problem in detail, Guo et al. recently argued that the 
-metallicity difference could account for a $\approx 0.1\%$ difference in the 
-measured rates between the CKS and {\it Kepler}\ samples~--~not a $\approx 
-0.5\%$ difference.
-Guo et al. concluded that ``other factors, such as binary contamination and 
-imperfect stellar properties'' must also be at play.
-
-Aside from surveying stars of varying metallicities, radial velocity and 
-transit surveys differ in how they treat binarity.
-Radial velocity surveys typically reject both visual and spectroscopic binaries
-({\it e.g.}, Wright et al. 2012).
-Transit surveys typically observe binaries, but the question of whether they 
-were searchable to begin with is usually left for later interpretation.
-In spectroscopic follow-up of candidate transiting planets, the prevalence of 
-astrophysical false-positives may also lead to a bias against confirmation of 
-transiting planets in binary systems.
-
-Ignoring these complications, in this work we focus on whether
-binarity might intrinsically bias transit survey occurrence rates, simply 
-through its effects on the number of searchable stars and the apparent radii 
-of detected planets.
-
-To progressively gain intuition, we study the following idealized transit 
-surveys:
+To gain intuition for the many observational biases at play,
+we study the following idealized transit surveys:
 \begin{itemize}
@@
 We interpret these calculations throughout, and in 
-Sec.~\ref{sec:discussion} discuss their relevance to various questions in 
+Sec.~\ref{sec:discussion} discuss their relevance to topical questions in 
 the interpretation of transit survey occurrence rates.
+In particular, we mention the ``hot Jupiter rate discrepancy'', the relevance 
+towards measurements of $\eta_\oplus$, and the significance for the dearth of 
+planets recently discovered by Fulton et al. (2017).

### 2017-11-10 paper/main.tex
paper WIP commit

@@
 radii, overestimated detection efficiencies, and an undercounted number of 
-selected stars (though possibly an overcounted number of searched stars).
+selected stars (but possibly an overcounted number of searched stars).
 These effects skew occurrence rate measurements in different directions, and 
@@
 radii, we find that ignoring binarity leads to a $10$\,-\,$30\%$ 
-underestimate of the number of planets per star, depending on planet radii.
+underestimate of the number of planets per star, depending on the true radius 
+distribution.
 For the occurrence of Earth-sized planets, in our most realistic model the 
@@
 \input{methods}
+\input{simplest_effects}
 \input{results}

### 2017-11-10 paper/model_1.tex
fig1: update caption
paper WIP commit

@@
 
-Consider a universe in which all planets are identical, and all stars are 
-either single or twin stars with otherwise identical physical properties.
+Since the effects of binarity are most pronounced when the two components are 
+similar, we begin by considering a universe in which all planets are 
+identical, and all stars are either single or twin stars with otherwise 
+identical physical properties.
 The occurrence rate density at a planet radius $r$, stellar radius $R$, and 
@@
 $d_{{\rm sel},0} = d_{{\rm det},0}$.
+This means our naive astronomer assumes the fraction of their selected stars 
+which are searchable is 1 (this is their ``assumed completeness'').
 For binary systems there is a necessary incompleteness, and combining 

### 2017-11-10 paper/simplest_effects.tex
paper WIP commit

--- 2017-11-10 paper/model_1.tex
@@
+\section{Idealized Models of Transit Surveys}
+
 \subsection{Model \#1: fixed stars, fixed planets, twin binaries}
@@
 similar, we begin by considering a universe in which all planets are 
-identical, and all stars are either single or twin stars with otherwise 
-identical physical properties.
-The occurrence rate density at a planet radius $r$, stellar radius $R$, and 
-semimajor axis $a$ for this model is
+identical, and all stars are identical except that some fraction of them exist 
+in binaries.
+
+Expressed mathematically, from Eqs.~\ref{eq:rate_density_marginalized}
+and~\ref{eq:rate_density_shape} the occurrence rate density at a planet radius 
+$r$ can be written
 \begin{equation}
-\Gamma(r,R,a) = \sum_i w_i \Lambda_i \delta^3(r_p,R_\star,a_p),
-\label{eq:model1_occ_rate_density}
+\Gamma(r) = \delta(r_p) \times
+\frac{
+    N_0 Z_0 +
+    N_1 Z_1 +
+    N_2 Z_2
+}{N_{\rm tot}},
+\label{eq:model_1_rate_density}
 \end{equation}
-for $r_p$ and $R_\star$ some fixed planet and stellar radii, $a_p$ a fixed 
-semi-major axis, and $\delta$ the Dirac delta function, whose compact
-form will be used for brevity.
-The occurrence rate over any interval that includes $r_p$, $R_\star$, and 
-$a_p$ is
+where $\delta(r_p)$ is the Dirac delta function, zero except at the true 
+planet radius, $r_p$.
+The occurrence rate over any interval that includes $r_p$ is then
 \begin{equation}
-\Lambda = \sum_i w_i \Lambda_i = \frac{ \sum_i N_i \Lambda_i }{N_{\rm tot}}.
+\Lambda|_{r_p} = \frac{
+    N_0 Z_0 +
+    N_1 Z_1 +
+    N_2 Z_2 
+}{N_{\rm tot}},
+\label{eq:model_1_rate}
 \end{equation}
-The rate is zero over intervals that do not.
+and the rate is zero over intervals that do not include $r_p$.
+
+We return to our group of binarity-ignoring astronomers. They do 
+not know the true planet population~--~they would like to discover it!
+In their signal-to-noise limited transit survey, they select stars 
+that they think can yield transit detections.
+Since the noise is Poissonian, they assume
+\begin{equation}
+\frac{{\rm signal}}{{\rm noise}}
+\propto \frac{(r/R)^2}{F^{-1/2}}
+\propto F^{1/2}
+\propto L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm incorrectly\ assumed})
+\end{equation}
+for $R$ the (constant) stellar radius, $F$ the photon flux, $L_{\rm sys}$ the 
+luminosity of a system, and $d$ its distance from us.
+At fixed planet radius, semimajor axis, stellar radius, and stellar luminosity,
+a constant signal-to-noise floor yields a maximum detectable 
+distance (Pepper et al 2003, Pepper and Gaudi 2005).
+The maximum distance out to which our binarity-ignoring astronomers 
+select stars, $d_{\rm sel}$, thus scales as $L_{\rm sys}^{1/2}$.
+
+The single stars have luminosity $L_1$, and the twin binaries have luminosity 
+$2L_1$.
+Thus the twin binaries are selected out to a distance $\sqrt{2}$ times 
+that of single stars.
+This is a bad move; in reality the transit signal for any planet in a 
+twin binary will be diluted by a factor of two:
+\begin{equation}
+\frac{{\rm signal}}{{\rm noise}}
+\propto \frac{\mathcal{D} (r/R)^2}{F^{-1/2}}
+\propto \mathcal{D} F^{1/2}
+\propto \mathcal{D} L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm true})
+\end{equation}
+where the dilution is $\mathcal{D} \equiv L_{\rm host}/L_{\rm sys}$, for 
+$L_{\rm host}$ the the planet host's luminosity.
+This means that the actual maximum searchable distance for binaries is 
+$1/\sqrt{2}\times$ that of single stars.
+The situation is illustrated in Fig.~\ref{fig:model_1_volumes}: only one in 
+eight selected stars in binaries are truly searchable.
+
+\paragraph{What do the observers ignoring binarity infer?} 
+The binarity-ignoring observers assume that every point on the sky with flux 
+above some minimum are searchable.
+They measure a detected planet rate density, and infer an apparent rate 
+density by correcting for $p_{\rm tra}$.
+The apparent rate density is
+\begin{equation}
+\Gamma_a(r) = 
+\delta(r_p) Z_0 \frac{N_0}{N_0+N_1}  +
+\delta\left(\frac{r_p}{\sqrt{2}}\right) 
+(Z_1 p_{{\rm det},1} + Z_2 p_{{\rm det},2}) \frac{N_1}{N_0+N_1},
+\label{eq:model_1_apparent_rate_density}
+\end{equation}
+where $p_{{\rm det},1}$ ($p_{{\rm det},2}$) is the probability that a selected 
+primary (secondary) is searchable.
+For this example, $p_{{\rm det},1}=p_{{\rm det},2}=1/8$.
+
+The true rate density (Eq.~\ref{eq:model_1_rate_density}) and the
+apparent rate density (Eq.~\ref{eq:model_1_apparent_rate_density})
+differ in that
+\begin{enumerate}
+\item The total number of selected stars, $N_{\rm tot} = N_0+N_1+N_2$, was 
+miscounted.
+%
+\item The detection efficiency was incorrectly assumed to be $1$ for all 
+selected stars. In reality, only one in eight binaries were searchable.
+%
+\item The inferred radii in binary systems are all $\sqrt{2}$ too small.
+\end{enumerate}
+
+We show the resulting occurrence rates over bins in planet radius in 
+Fig.~\ref{fig:errcases_model_1}.
+
+%NOTE: YOU CAN BUTCHER THE FUCK OUT OF THIS SECTION. JNW WANTS EACH CASE TO BE 
+%EXPLAINED, INDIVIDUALLY. DROP ALL THE "i" SUBSCRIPTS B/C THEY ARE APPARENTLY 
+%CONFUSING.
 
@@
 
-\paragraph{What does an observer ignoring binarity infer?} 
-An observer who ignores binarity assumes a detection efficiency 
-$\tilde{Q}=Q_0$,
-measures a detected planet rate density $\tilde{\Gamma}$, 
-and infers an apparent rate density $\Gamma_a$.
-Analogous to Eq.~\ref{eq:detected_rate_density},
-\begin{equation}
-\tilde{\Gamma} = \Gamma_a \tilde{Q}.
-\end{equation}
-Accounting for dilution, and assuming $q=1$, the apparent rate density is
-\begin{equation}
-\Gamma_a = 
-w_a \Lambda_0 \delta^3(r_p, R_\star, a_p) +
-w_b (\Lambda_1 Q_{c,1} + \Lambda_2 Q_{c,2}) 
-				\delta^3(r_p/\sqrt{2}, R_\star, a_p),
-\end{equation}
-for $w_a = N_0/(N_0+N_1)$, and $w_b = N_1/(N_0+N_1)$.
-This observer miscounts the number of total searched stars, does not correct 
-for incompleteness, and misclassifies the planetary radii because of dilution.
-
 \paragraph{Correction to inferred rate density and inferred rate}
@@
 binary fraction\footnote{
-The binary fraction is the fraction of systems in a volume-limited sample that 
+    The binary fraction is the fraction of systems in a volume-limited sample 
+    that 
     are binary. It is equivalent to the multiplicity fraction if there are no 
-triple, quadruple, or higher order multiples. In that case, ${\rm BF} = n_b / 
+    triple, quadruple, or higher order multiples. In that case, ${\rm BF} = 
+    n_b / 
     (n_s+n_b)$.

### 2017-11-12 paper/discussion.tex
paper JNW comments round 1

@@
 Mostly if not entirely, these studies have ignored stellar multiplicity.
-However, binarity certainly introduces a level of systematic uncertainty to 
+However, binarity clearly introduces a level of systematic uncertainty to 
 pipeline completeness, as well as to star and planet counts.
 No one has yet carefully studied the magnitude of this issue for 
-{\it Kepler} occurrence rates, and the present work does not resolve this 
-problem.
+{\it Kepler} occurrence rates.
+While the present work does not resolve this problem, it suggests the 
+approximate order of magnitude for the necessary correction factors.
 %NOTE: the above might be better in a "discussion" section?
@@
 interpretation of planet candidates. High resolution imaging 
-campaigns have consequently been undertaken to measure the multiplicity of 
+campaigns have been undertaken to measure the multiplicity of 
 almost all {\it Kepler}\ Objects of Interest 
@@
 
-For {\it Kepler}-derived occurrence rates, the high resolution imaging 
-campaigns have not yet come full circle to observe a comparison sample of 
-non-KOI host stars.
+To help clarify {\it Kepler}-derived occurrence rates, the high resolution 
+imaging campaigns have not yet come full circle by observing a comparison 
+sample of non-KOI host stars.
 The most recent rate studies have thus used Furlan et al. (2017)'s 
@@
 \paragraph{The Hot Jupiter Rate Discrepancy}
-There is at least one context in which measurement of absolute 
+There is at least one context in which measurement of 
 occurrence rates may already be showing the signatures of binarity.
@@
 see Table~\ref{tab:hj_rates}).
-Though the discrepancy is of weak statistical significance ($<3\sigma$),
-one plausible explanation for the difference is that the populations have 
-distinct metallicities.
-As originally argued by Gould et al. (2006), the RV sample is biased towards 
+The discrepancy has weak statistical significance ($<3\sigma$).
+That said, one reason to expect a difference is that the corresponding stellar 
+populations have distinct metallicities.
+As argued by Gould et al. (2006), the RV sample is biased towards 
 metal-rich stars, which have been measured by RV surveys to preferentially 
@@
 
-Ignoring these complications, in this work we focus on whether
-binarity might intrinsically bias transit survey occurrence rates, simply 
-through its effects on the number of searchable stars and the apparent radii 
-of detected planets.
+Ignoring these complications, in this work we showed that
+binarity does bias transit survey occurrence rates, simply through its 
+effects on the number of searchable stars and the apparent radii of detected 
+planets.
+Specifically, our results from Sec.~\ref{sec:model_3} indicate that binarity 
+might lead to underestimate HJ rates by a multiplicative factor of $\approx 
+1.3$.
+
+We assess the effect this might have towards resolving the hot Jupiter rate 
+discrepancy by asking:
+what is the probability of Wright et al. (2012)'s result, given a rate drawn 
+from the stated bounds of Petigura et al. (in prep)? (See 
+Table~\ref{tab:hj_rates}).
+In other words, we first take the true HJ rate as $\Lambda_{\rm HJ} = 5.7 \pm 
+1.3$, with Gaussian uncertainties, and then drawing from a Poisson 
+distribution compute the probability of detecting at least 10 hot Jupiters in 
+a sample of 836 stars.
+Without accounting for binarity or metallicity, only 4\% of RV surveys would 
+detect at least 10 hot Jupiters.
+If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account for Guo et al. 
+(2017)'s measured metallicity difference between the {\it Kepler}\ field and 
+the local solar neighborhood, 9\% of RV surveys would detect at least 10 hot 
+Jupiters.
+If we then multiply again by $1.3$ to account for binarity's bias, we find that
+23\% of RV surveys would detect at least 10 hot Jupiters, and any discrepancy 
+would be quite teneous.
+We emphasize that this result is only suggestive~--~a true resolution of the 
+rate discrepancy would likely require a detailed understanding of the {\it 
+Kepler}\ field's multiplicity statistics.
 

### 2017-11-12 paper/figures.tex
paper WIP commit
paper JNW comments round 1

--- 2017-11-09 paper/figures.tex
@@
 \newpage
-\begin{figure}
-    \begin{center}
-        \includegraphics[width=\textwidth]{figures/visualize_volumes.pdf}
-    \end{center}
-    \caption{
-    Cartoon of the different selected and searchable volumes for single 
-    stars (left column), and twin binaries (right column).
-    This model (\#1) assumes all stars have equal mass and luminosity.
-    Since the observer does not recognize the brighter binaries, they select 
-    them out to a larger distance, $\sqrt{2}\times$ that of single stars.
-    However, dilution causes the twin binaries to only be searchable in one 
-    eighth of their selected volume.
-    }
-    \label{fig:model_1_volumes}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-        \includegraphics[width=\textwidth]{figures/errcases_rate_density_vs_radius_model_1_brokenx.pdf}
-    \end{center}
-    \caption{
-    Inferred planet occurrence rates as a function of planet radius in Model 
-    \#1.
-    This model has fixed stars, fixed planets, and twin binaries.
-    If the true planet radius is $r_p$, all planets 
-    detected in binaries will have apparent radii $r_a = r_p/\sqrt{2}$.
-    Only 1 in 8 selected binaries is actually searchable (see 
-    Sec.~\ref{sec:model_1}).
-    To help illustrate the individual effects of errors, we 
-    separated them:
-    ``only wrong $N_\star$'' means the only error is an incorrectly assumed 
-    number of selected stars;
-    ``only wrong $Q$'' means the only error is an incorrectly assumed 
-    detection efficiency (including both miscalculated transit probabilities 
-    and 
-    fraction of selected stars that are searchable);
-    ``only wrong $r_a$'' means the only error is misinterpretation of 
-    planetary radii, due to both transit depth dilution and also wrongly 
-    assumed host star radii.
-    }
-    \label{fig:errcases_model_1}
-\end{figure}
-
-\begin{figure}[!tb]
-    \centering
-    \includegraphics[width=\textwidth]{figures/q_distribn_mag_limited.pdf}
-    \caption{
-    The distribution of the mass ratio for a magnitude limited sample of 
-    binary stars. The underlying mass ratios are drawn from a uniform 
-    distribution in a volume-limited sample, quite similar to that of Raghavan 
-    et al. (2010)'s Fig. 13.
-    The entire bias can be understood analytically (Eq.~\ref{eq:model_2_p_2},
-    with $\gamma=0$).
-    The numerical comparison uses a realistic empirical mass-luminosity 
-    relation rather than $L=M^{3.5}$, found by fitting main sequence dwarf 
-    mass luminosity data compiled from Torres et al. [2009] and Benedict et 
-    al. [2016].
-    }
-    \label{fig:q_distribn_mag_limited}
-\end{figure}
-
-\begin{figure}[!tb]
-    \centering
-    \includegraphics[width=.7\textwidth]{figures/errcases_rate_density_vs_radius_model_2.pdf}
-    \caption{
-    Inferred planet occurrence rates as a function of planet radius in Model 
-    \#2.
-    This model has fixed planets and primaries, but varying secondaries.
-    }
-    \label{fig:errcases_model_2_linear}
-\end{figure}
-
-\begin{figure}[!tb]
-    \centering
-    \includegraphics[width=.7\textwidth]{figures/errcases_rate_density_vs_radius_logs_model_2.pdf}
-    \caption{
-    Same as Fig.~\ref{fig:errcases_model_2_linear}, but with logarithmic 
-    $y$-axis, and different $x$ scale.
-    }
-    \label{fig:errcases_model_2_log}
-\end{figure}
-
-\begin{figure}[!tb]
-    \centering
-    \includegraphics[width=\textwidth]{figures/errcases_rate_density_vs_radius_logs_model_3.pdf}
-    \caption{
-    Inferred planet occurrence rates as a function of planet radius in Model 
-    \#3.
-    This model has fixed primaries and single stars, but varying 
-    secondaries.
-    The true planet radius distribution is a power law with exponent $-2.92$ 
-    above $2R_\oplus$, below which it is uniform (e.g., Howard et al., 
-    2012).
-    }
-    \label{fig:errcases_model_3_log}
-\end{figure}
-
-\begin{figure}[!tb]
-    \centering
-    \includegraphics[width=.9\textwidth]{figures/HJ_correction_inputrate_vs_HJratevalues.pdf}
-    \caption{
-    $\Lambda_i$ is the occurrence rate integrated over all possible phase 
-    space for the $i^{\rm th}$ system type. $\Lambda_2/\Lambda_0=1$ 
-    corresponds to an equal number of planets per secondary as per single star;
-    $\Lambda_2/\Lambda_0=0$ corresponds to secondaries not having any planets.
-    In our Model \#3, though the true HJ occurrence rate 
-    (Eq.~\ref{eq:occ_rate}) is highly dependent on $\Lambda_2$, 
-    the inferred rate hardly depends on whether secondaries have HJs.
-    This means that the ``correction factor'' between the inferred rate and 
-    the true rate around single stars is underestimated by a multiplicative 
-    factor of $\approx1.3$, independent of the HJ rate around secondaries.
-    The ``HJ rate'' is the summed rate from     
-    Fig.~\ref{fig:errcases_model_3_log} above $8r_\oplus$.
-    }
-    \label{fig:HJ_correction_inputrate_vs_HJratevalues}
-\end{figure}
-
-\begin{figure}[!tb]
-    \centering
-    \includegraphics[width=.9\textwidth]{figures/earth_inputrate_vs_etaearthratevalues.pdf}
-    \caption{
-        Same as Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues}, but 
-        for Earth-sized planets.
-        The absolute values given on the $y$-axis found by summing the rate 
-        from Fig.~\ref{fig:errcases_model_3_log} for planetary radii from 
-        $0.5$ to $1.5r_\oplus$ (this is a toy model, and they do not reflect 
-        an actual determination of $\eta_\oplus$).
-        The relative values show that the inferred rate for Earths is roughly 
-        independent of the occurrence rate (integrated over all radii) around 
-        secondaries.
-        However, it is systematically lower than the true rate around single 
-        and primary stars, by $\approx 20\%$.
-    }
-    \label{fig:earth_inputrate_vs_etaearthratevalues}
-\end{figure}
 

### 2017-11-12 paper/generalities.tex
paper JNW comments round 1

@@
 For a selected population of stars and planets, the rate density is then 
-the weighted sum of rate densities for each system type:
+a weighted sum of rate densities for each system type:
 \begin{equation}
@@
 
-Finally, it is useful to write 
+Finally, it is helpful to write 
 $\Gamma_i(r)$, the rate density for each type of star, as the product of a 

### 2017-11-12 paper/introduction.tex
paper JNW comments round 1

@@
 masses and radii than assumed in the single-star case.
-Finally, there are errors in $p_{\rm det}$ because the detection efficiencies 
-of planets that orbit single stars, primaries, and secondaries are all 
+Finally, there are errors in $p_{\rm det}$ because detection efficiencies 
+for planets orbiting single stars, primaries, and secondaries are all 
 different.
@@
 To gain intuition for the many observational biases at play,
-we study the following idealized transit surveys:
+we consider the following idealized transit surveys:
 \begin{itemize}
@@
 \end{itemize}
-In Sec.~\ref{sec:numerical_methods}, we introduce our numerical approach 
-to the problem, and in Sec.~\ref{sec:analytic_preliminaries} we clarify our 
-terminology.
-We present the analytic and numerical results in 
-Secs.~\ref{sec:model_1}-\ref{sec:model_3}, where each subsection corresponds 
-to each model above.
+We define our terminology in Sec.~\ref{sec:definitions}, and present
+our transit survey models in Secs.~\ref{sec:model_1}-\ref{sec:model_3}, where 
+subsequent subsections correspond to the models above.
 We interpret these calculations throughout, and in 
@@
 planets recently discovered by Fulton et al. (2017).
+We conclude in Sec.~\ref{sec:conclusion}

### 2017-11-12 paper/main.tex
paper JNW comments round 1

@@
 we develop simple models that allow us to understand the crucial effects.
-For models in which all stellar systems are either single or twin binaries, 
-and all planets are identical, we find that ignoring binarity leads to a
-two-to-threefold underestimate of the occurrence at the true radius.
-We believe this represents an upper bound on binarity's effects.
+For a model in which all stellar systems are either single or twin binaries, 
+and all planets are identical, we find that ignoring binarity leads to an 
+underestimate of the occurrence at the true radius by a multiplicative factor 
+of $0.8$ (assuming a 10\% twin binary fraction).
 Using more realistic models for the stellar population and planetary 
@@
 underestimate is by $\approx 15\%$~--~at present far smaller than 
-systematic uncertainties on real measurements of this number.
+systematic uncertainties on real $\eta_\oplus$ measurements.
 For hot Jupiters, we find that the inferred occurrence rate is 
@@
 \input{methods}
-\input{simplest_effects}
 \input{results}
@@
 
-\input{figures.tex}
 \input{hj_rates.tex}

### 2017-11-12 paper/model_2.tex
paper JNW comments round 1

@@
 
-The main use of our binary-twin model is to help develop intuition.
-We now let the light ratio $\ell = L_2/L_1$ vary across the binary 
-population.
+Our binary-twin model provides a simple estimate of binarity's systematic 
+effects, but perhaps it is too simple.
+We begin introducing realism by first letting the light ratio $\ell = L_2/L_1$ 
+vary across the binary population.
 It does so because the underlying mass ratio $q=M_2/M_1$ varies.
@@
 }, $\beta$ is probably between 0 and 0.3.
-Since we assume stars are a one-parameter family, $R \propto M \propto 
-L^{1/\alpha}$, a drawn value of $q$ determines everything about a secondary.
+We further assume that stars are a one-parameter family, $R \propto M \propto 
+L^{1/\alpha}$, so that a drawn value of $q$ determines everything about a 
+secondary.
 
-The rate density in this model, $\Gamma(\vec{x})$, is the sum over system 
-types of $w_i \Lambda_i p_i(\vec{x})$:
+The rate density in this model, $\Gamma(r,q)$, is the sum of the rate 
+densities for each system type:
 \begin{equation}
-\Gamma(\vec{x})
+\Gamma(r,q)
 =
-\delta^4(r_p,R_\star,a_p,P_p)(w_0 \Lambda_0 + w_1 \Lambda_1)
-+ w_2 \Lambda_2 \delta^3(r_p, P_p, a_p) p_2(q),
+\delta(r_p) \times 
+\frac{N_0 Z_0 + N_1 Z_1 + N_2 Z_2 p_2(q)}{N_{\rm tot}}
 \label{eq:model2_rate_density}
 \end{equation}
-where the semimajor axis of the planet must be such that its period is $P_p$, 
-and $p_2(q)$ is expressed in terms of the mass ratio instead of the secondary 
-star's radius for convenience ($q$ and $R_2$ are interchangeable).
+where $p_2(q)$ is expressed in terms of the mass ratio instead of the 
+secondary star's radius for convenience ($q$ and $R_2$ are interchangeable).
 The probability that a secondary hosts a planet, as a function of the mass 
@@
 power law of $q$ with exponent $\gamma$.
-For the second term, since the selected sample at a given $(r,P,a)$ is
-magnitude-limited, $p({\rm secondary\ with\ }q)$ 
+The second term, $p({\rm secondary\ with\ }q)$, 
 is the product of the volume limited probability, $q^\beta$, and a 
 Malmquist-like bias, $(1+q^\alpha)^{3/2}$.
-We note that various authors (probably ourselves included) have incorrectly 
-drawn from volume-limited binary distributions in Monte Carlo simulations of 
-transit surveys (Sullivan et al 2015, Bakos et al 2012, Guenther et al 
-2017, Bouma et al 2017).
-The correct distribution for a magnitude-limited selection is shown in 
-Fig.~\ref{fig:q_distribn_mag_limited}.
+This is because the selected sample at a fixed planet radius and period is 
+magnitude-limited.
+We show the magnitude-limited mass ratio distribution for the $\beta=0$ case 
+in Fig.~\ref{fig:q_distribn_mag_limited}.
+We emphasize that in any Monte Carlo simulation of a transit survey, it is 
+important to draw binaries from the correctly biased mass-ratio distribution 
+(e.g., Bakos et al 2012, Sullivan et al 2015, Guenther et al 2017).
 
 The occurrence rate corresponding to Eq.~\ref{eq:model2_rate_density}'s rate 
-density for a desired volume of phase space $\Omega_{\rm desired}$ is given by 
-Eq.~\ref{eq:occ_rate}.
-Specifying the desired mass ratios of interest as $q_{\rm min} < q < q_{\rm 
-max}$, this simplifies to
+density for specific mass ratios of interest $q_{\rm min} < q < q_{\rm 
+max}$ is
 \begin{equation}
-\Lambda = 
-\frac{N_0 \Lambda_0 + N_1 \Lambda_1 + N_2 \Lambda_2 f_2}
+\Lambda|_{r_p,q_{\rm min},q_{\rm max}} = 
+\frac{N_0 Z_0 + N_1 Z_1 + N_2 Z_2 f_2}
 {N_{\rm tot}},
@@
 f_2 \equiv
-\left(
-\int_{q_{\rm min}}^{q_{\rm max}} p_2(q) \,{\rm d}q
-\right)
-\cdot
-\left(
-\int_{0}^{1} p_2(q) \,{\rm d}q
-\right)^{-1}.
+\int_{q_{\rm min}}^{q_{\rm max}} p_2(q) \,{\rm d}q,
 \end{equation}
+where $p_2(q)$ is given by Eq.~\ref{eq:model_2_p_2}, and must be normalized to 
+unity.
 
-The detected rate density, $\hat{\Gamma} = \sum_i Q_i \Gamma_i$, will be 
-specified by the detection efficiencies for each type of system.
-These are identical to 
-Eqs.~\ref{eq:detection_efficiency_0}-\ref{eq:detection_efficiency_2}.
-The detection efficiency for secondaries (Eq.~\ref{eq:detection_efficiency_2}) 
-includes the transit probability from the smaller stellar radius, and combines 
-dilution, the transit duration, and stellar radius for the completeness
-probability.
+\begin{figure}[!tb]
+    \centering
+    \includegraphics[width=0.6\textwidth]{figures/q_distribn_mag_limited.pdf}
+    \caption{
+        The distribution of the mass ratio for a magnitude limited sample of 
+        binary stars. The underlying mass ratios are drawn from a uniform 
+        distribution in a volume-limited sample, quite similar to that of 
+        Raghavan 
+        et al. (2010)'s Fig. 13.
+        The entire bias can be understood analytically 
+        (Eq.~\ref{eq:model_2_p_2},
+        with $\gamma=0$).
+        The numerical comparison uses a realistic empirical mass-luminosity 
+        relation rather than $L=M^{3.5}$, found by fitting main sequence dwarf 
+        mass luminosity data compiled from Torres et al. [2009] and Benedict 
+        et 
+        al. [2016].
+    }
+    \label{fig:q_distribn_mag_limited}
+\end{figure}
 
-\paragraph{What does an observer ignoring binarity infer?}
-As a reminder, the apparent rate density is found by correcting the detected 
-apparent rate density for the transit probability:
-$\Gamma_a = \tilde{\Gamma} Q_{g,0}^{-1}$.
-The observer's errors are as follows:
+\paragraph{What does the observers ignoring binarity infer?}
+As a reminder, the observers compute an apparent rate density by correcting 
+the number of detections per star for the transit probability and the 
+detection efficiency.
+In this process, the binarity-ignoring observers make the following errors:
 \begin{enumerate}
+\item They assume that they have selected $N_0+N_1$ stars, while they have 
+actually selected $N_0+N_1+N_2$.
+%
+\item They assume that every star within the maximum selected distance is 
+searchable.
+This is true for single stars.
+For binaries, the actual detection efficiency is the ratio of the number of 
+searchable stars to the number of selected stars.
+For primaries,
+\begin{equation}
+p_{\rm det,1} = \left(\frac{d_{\rm det,1}}{d_{\rm sel}}\right)^3
+= \mathcal{D}_1^3 = (1+q^\alpha)^{-3},
+\label{eq:model_2_p_det_1}
+\end{equation}
+where we have assumed that all single stars and primaries have the same 
+properties, and have used $\ell = q^\alpha$.
+For secondaries,
+\begin{equation}
+p_{\rm det,2} = \left(\frac{d_{\rm det,2}}{d_{\rm sel}}\right)^3
+= \mathcal{D}_2^3 \left(\frac{R_1}{R_2}\right)^6
+    \left(\frac{T_{\rm dur,2}}{T_{\rm dur,1}}\right)^{3/2} 
+= (1+q^{-\alpha})^{-3} q^{-5},
+\label{eq:model_2_p_det_2}
+\end{equation}
+where subscripts `1' and `2' correspond to primaries and secondaries, and we 
+used the scaling relation $T_{\rm dur}\propto \rho_\star^{-1/3} \propto 
+R_\star^{2/3}$.
+%
+\item They assume the transit probability for all stars to be $R_\star/a$. 
+For planets orbiting secondaries at fixed period, the true transit probability 
+is $q^{2/3} R_\star/a$, since the secondaries have smaller radii and masses.
+%
 \item The true planetary radii $r$ are interpreted as apparent radii $r_a$.
-    The apparent radii depend on the system type:
+In binaries, the apparent radii depend on whether the host is the primary or 
+secondary:
     \begin{align}
@@
     The factor of $q^{-1}$ for the secondary case accounts for the observer 
-    assuming that the host star is the primary.
-    \item The completeness fraction is miscalculated for any stars in binary 
-    systems.
-    \item The selected and searchable stars are miscounted.
+    assuming all transit signals come from stars of fixed size.
 \end{enumerate}
@@
 \Gamma_a(r_a) =
-w_a \Lambda_0 \delta(r_p)
+\frac{N_0}{N_0+N_1} Z_0 \delta(r_p)
 +
-w_b \Lambda_1 I_1(r_a)
+\frac{N_1}{N_0+N_1} \left( Z_1 I_1(r_a)
 +
-w_b \Lambda_2 I_2(r_a),
+Z_2 I_2(r_a) \right).
 \label{eq:model2_Gamma_a}
 \end{equation}
-where the detection efficiencies are given in 
-Eqs.~\ref{eq:detection_efficiency_0}-\ref{eq:detection_efficiency_2}, and as 
-in the first model, $w_a=N_0/(N_0+N_1)$, $w_b=N_1/(N_0+N_1)$. The ratio of 
-primaries to singles, $\mu$, is now less than that of Model \#1 (cf. 
-Eq.~\ref{eq:mu_definition}). This is because a distribution of light ratios 
-$\ell$ leads to a distribution of maximum selected distances. Integrating over 
-the mass ratios, one finds
+The ratio of primaries to singles, $\mu=N_1/N_0$, is now less than 
+that of Model \#1 (cf. Eq.~\ref{eq:mu_definition}). This is because a 
+distribution of light 
+ratios $\ell$ leads to a distribution of maximum selected distances. 
+Integrating over the mass ratios from $q=0$ to $1$, one finds a
+dimensionless integral
 \begin{equation}
@@
 
-This fully specifies the weights in Eq.~\ref{eq:model2_Gamma_a}.
+Given a binary fraction, Eq.~\ref{eq:mu_model_2} fully specifies the 
+``weights'' in Eq.~\ref{eq:model2_Gamma_a}.
 The $I_1(r_a)$ and $I_2(r_a)$ terms are found by marginalizing over the joint 
@@
 \end{equation}
-which has no analytic solution except for special values of $\alpha$, the 
-mass-luminosity exponent.
+which has no analytic solution for $q(r_a)$ except for special values of 
+$\alpha$, the mass-luminosity exponent.
 For $\alpha=3.5$, our nominal case, semianalytic solutions could be found.
 However, since our main interest is in understanding the qualitative behavior 
-of the solutions, we focus on a few limiting cases, and proceed numerically.
+of the solutions, we derive a few limiting cases, and then proceed 
+numerically.
 
-\paragraph{Correction to inferred rate density}
+\paragraph{Limiting cases of rate density correction}
 Recall that the rate density correction factor, $X_\Gamma$, is the ratio of 
@@
 primaries and single stars.
-Under these assumptions, the planetary rate density is
+Under these assumptions, the true rate density is
 \begin{equation}
-\Gamma(r) \approx \delta(r_p) \left( \Lambda_0 + \Lambda_1 + 
-\Lambda_2 \right) / 3,
+\Gamma(r) \approx \delta(r_p) \left( Z_0 + Z_1 + 
+Z_2 \right) / 3,
 \label{eq:model2_Gamma_r}
@@
 \begin{equation}
-\Gamma_a(r) = c_0 \Lambda_0 \delta(r_p)
-             +c_1 \Lambda_1 I_1(r_a)
-             +c_2 \Lambda_2 I_2(r_a),
+\Gamma_a(r) = c_0 Z_0 \delta(r_p)
+             +c_1 Z_1 I_1(r_a)
+             +c_2 Z_2 I_2(r_a),
 \label{eq:model2_Gamma_a_r}
 \end{equation}
-for $c_0\approx 0.49$, $c_1\approx 0.32$, $c_2\approx 0.03$.
+for $c_0\approx 0.49$, $c_1\approx 0.32$, and $c_2$ unknown.
 %171011_integrals.nb
@@
 \end{equation}
-If all the rates are equal, $X_\Gamma(r=r_p)\approx0.49$.
+If all the $Z_i$'s are equal, $X_\Gamma(r=r_p)\approx0.49$.
 If there are no planets around the secondaries, $X_\Gamma(r=r_p)\approx0.74$.
 
-We also run this model in our numerical simulation.
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_model_2.pdf}
+    \caption{
+        Inferred planet occurrence rates as a function of planet radius in 
+        Model 
+        \#2.
+        This model has fixed planets and primaries, but varying secondaries.
+    }
+    \label{fig:errcases_model_2_linear}
+\end{figure}
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_logs_model_2.pdf}
+    \caption{
+        Same as Fig.~\ref{fig:errcases_model_2_linear}, but with logarithmic 
+        $y$-axis, and different $x$ scale.
+    }
+    \label{fig:errcases_model_2_log}
+\end{figure}
+
+\paragraph{Numerical approach}
+To maintain simplicity, we develop a Monte Carlo program to simulate our 
+toy transit surveys.
+The program generates a stellar population, assigns planets to the stars, and 
+then calculates which planets are detectable.
+It then computes the apparent and true planet occurrence rates as a function 
+of planet radius.
+This is discussed in detail below, and our implementation is available 
+online\footnote{\url{https://github.com/lgbouma/binary_biases}}.
+
+First, the user must specify the free parameters that describe the 
+stellar and planetary population. These values include the binary fraction, 
+and the true planet occurrence rates around single stars, primaries, and 
+secondaries (the $Z_i$'s; recall Eq.~\ref{eq:rate_density_shape}).
+There is also an arbitrary absolute number of selected stars.
+
+Once the free parameters are specified, the population of selected stars is 
+constructed.
+Each selected star is assigned a type (single, primary, secondary), a 
+binary mass ratio (if it is not single), and the property of whether it is 
+``searchable''.
+The relative number of binaries to primaries is set by 
+Eq.~\ref{eq:mu_model_2}.
+The mass ratios are drawn from the appropriate magnitude-limited distribution 
+(Eq.~\ref{eq:model_2_p_2}).
+If it is single, a selected star is assumed to be searchable.
+If it is a primary or secondary, its searchability is determined by a uniform 
+draw from either Eq.~\ref{eq:model_2_p_det_1} or Eq.~\ref{eq:model_2_p_det_2}, 
+as appropriate.
+
+Assigning planets, each selected star receives a planet at the rate $Z_i$, 
+according to its type.
+The radii of planets are assigned independently of any host system property, 
+and can be sampled for an arbitrary distribution ({\it e.g.}, power law; delta 
+function).
+The absolute transit probability, $p_{\rm tra}$ is set arbitrarily, and the 
+probability of a planet transiting a secondary is set as $q^{2/3}\times p_{\rm 
+tra}$.
+A planet is ``detected'' when a) it transits, and b) its host star is 
+searchable.
+For detected planets, apparent radii are computed according to analytic 
+formulae that account for both dilution and the misclassification of stellar 
+radii (Eq.~\ref{eq:model2_ra}).
+We assume that the observers think that all transits are around single stars.
+
+We then compute rates in bins of true planet radius and apparent planet radius.
+In a given radius bin, the true rate is found by counting the number of planets
+that exist around selected stars of all types (singles, primaries,
+secondaries), and dividing by the total number of these stars.
+The apparent rates are found by counting the number of detected planets that
+were found in an apparent radius bin, dividing by the geometric transit
+probability for single stars, and dividing by the apparent total number of
+stars.
+
+\paragraph{Numerical results for Model \#2}
+We first validate our model by ensuring it produces the analytically-predicted 
+results for Model \#1, and the limiting cases of Model \#2 described above.
+Following validation, assuming ${\rm BF}=0.44$, $\alpha=3.5$, 
+$\beta=\gamma=0$, and taking $Z_0=Z_1=Z_2$, we compute the true and apparent 
+occurrence rates over bins in planet radius.
 The results are shown in Figs.~\ref{fig:errcases_model_2_linear} 
 and~\ref{fig:errcases_model_2_log}.
-They produce the same correction factors as predicted analytically.
-They also show a peak in the inferred rate at $r_p/\sqrt{2}$ from 
-secondaries.
-This effect requires the observer to incorrectly estimate the host star's 
-radius; if they somehow knew the host star's radius, but did not correct for 
-binary dilution, the peak would instead be at an apparent radius of 0.
-
-To summarize, dilution produces a spectrum of apparent planetary radii. In 
-this model, this produces overestimated rates everywhere except where there 
-are actually planets, where the rate is underestimated by a factor of 2.
+Evidently, dilution produces a spectrum of apparent planetary radii. This 
+leads to overestimated rates everywhere except where there 
+are actually planets, where the rate is underestimated by a factor of two.

### 2017-11-12 paper/model_3.tex
paper JNW comments round 1

@@
 $\alpha=3.5$, $\beta=\gamma=0$.
-We take $\Lambda_i$, the occurrence rate integrated over all possible phase 
-space for the $i^{\rm th}$ system type, to be equal for singles, primaries, 
+We take $Z_i$, the occurrence rate integrated over all planet radii for the 
+$i^{\rm th}$ system type, to be equal for singles, primaries, 
 and secondaries.
 
-For this model, we forgo analytic development and focus only on numerics 
-(Sec.~\ref{sec:numerical_methods}).
-The nominal results are shown in Fig.~\ref{fig:errcases_model_3_log}.
+For this model, we forgo analytic development and focus only on numerics.
+The occurrence rates are shown as a function of planet radius in 
+Fig.~\ref{fig:errcases_model_3_log}.
 For the assumed planetary and stellar distributions, the inferred rate is 
 underestimated over all radii.
+
+\begin{figure}[!tb]
+    \centering
+    \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_logs_model_3.pdf}
+    \caption{
+        Inferred planet occurrence rates as a function of planet radius in 
+        Model 
+        \#3.
+        This model has fixed primaries and single stars, but varying 
+        secondaries.
+        The true planet radius distribution is a power law with exponent 
+        $-2.92$ 
+        above $2R_\oplus$, below which it is uniform (e.g., Howard et al., 
+        2012).
+    }
+    \label{fig:errcases_model_3_log}
+\end{figure}
 
@@
 
-However, this result only applies under the assumption that $\Lambda_0 = 
-\Lambda_1 = \Lambda_2$.
+However, this result only applies under the assumption that $Z_0 = 
+Z_1 = Z_2$.
 If hot Jupiters are less common around lower mass stars, it would be more 
-sensible to consider $\Lambda_2<\Lambda_0$, while letting single stars and 
+sensible to consider $Z_2<Z_0$, while letting single stars and 
 primaries host planets at the same rate.
 Therefore in Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues} we let 
-$\Lambda_2$ vary, and show the resulting inferred and true hot Jupiter 
+$Z_2$ vary, and show the resulting inferred and true hot Jupiter 
 ($r>8r_\oplus$) rates.
 The result is that the inferred rate is nearly independent of 
-$\Lambda_2$~--~this is because most ($<1/10$) secondaries are not searchable, 
+$Z_2$~--~this is because most ($<1/10$) secondaries are not searchable, 
 and so their completeness fraction is much smaller than that of primaries or 
@@
 hardly affect the inferred rate.
-While the ``true rate'' across the entire population is highly dependent on 
-$\Lambda_2$, as one would expect from Eq.~\ref{eq:occ_rate}, the rate around 
+While the ``true rate'' across the entire population is linearly dependent on 
+$Z_2$, the rate around 
 singles and primaries (green line) is independent of that around secondaries.
@@
 around secondaries.
+
+\begin{figure}[!tb]
+    \centering
+    \includegraphics[width=.6\textwidth]{figures/HJ_correction_inputrate_vs_HJratevalues.pdf}
+    \caption{
+        $X_i$ is the occurrence rate integrated over all possible phase 
+        space for the $i^{\rm th}$ system type. $Z_2/Z_0=1$ 
+        corresponds to an equal number of planets per secondary as per single 
+        star;
+        $Z_2/Z_0=0$ corresponds to secondaries not having any 
+        planets.
+        In our Model \#3, though the true HJ occurrence rate 
+        is highly dependent on $Z_2$, 
+        the inferred rate hardly depends on whether secondaries have HJs.
+        This means that the ``correction factor'' between the inferred rate 
+        and the true rate around single stars is underestimated by a 
+        multiplicative 
+        factor of $\approx1.3$, independent of the HJ rate around secondaries.
+        The ``HJ rate'' is the summed rate from     
+        Fig.~\ref{fig:errcases_model_3_log} above $8r_\oplus$.
+    }
+    \label{fig:HJ_correction_inputrate_vs_HJratevalues}
+\end{figure}
 
@@
 At Earth's radius, the result is that the inferred rate is $0.84\times$ the 
-true rate around single stars, assuming that the $\Lambda_i$'s are equal.
-Similar to the above case of the hot Jupiters, if we vary the true $\Lambda_2$ 
-while keeping $\Lambda_0 = \Lambda_1$, the ratio of the inferred to true rate 
+true rate around single stars, assuming that the $Z_i$'s are equal.
+Similar to the above case of the hot Jupiters, if we vary the true $Z_2$ 
+while keeping $Z_0 = Z_1$, the ratio of the inferred to true rate 
 around single stars hardly 
-changes; $(\Lambda_{\rm inferred}/\Lambda_1)_{r=r_\oplus} \approx 0.135$, to 
-within a few percent, independent of $\Lambda_2$ (shown in 
+changes by only a few percent (shown in 
 Fig.~\ref{fig:earth_inputrate_vs_etaearthratevalues}).
@@
 in the (unrealistic) limiting case that secondaries do not host planets.
+
+\begin{figure}[!tb]
+    \centering
+    \includegraphics[width=.6\textwidth]{figures/earth_inputrate_vs_etaearthratevalues.pdf}
+    \caption{
+        Same as Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues}, but 
+        for Earth-sized planets.
+        The absolute values given on the $y$-axis found by summing the rate 
+        from Fig.~\ref{fig:errcases_model_3_log} for planetary radii from 
+        $0.5$ to $1.5r_\oplus$ (this is a toy model, and they do not reflect 
+        an actual determination of $\eta_\oplus$).
+        The relative values show that the inferred rate for Earths is roughly 
+        independent of the occurrence rate (integrated over all radii) around 
+        secondaries.
+        However, it is systematically lower than the true rate around single 
+        and primary stars, by $\approx 20\%$.
+    }
+    \label{fig:earth_inputrate_vs_etaearthratevalues}
+\end{figure}

### 2017-11-12 paper/simplest_effects.tex
paper JNW comments round 1

@@
-\section{Idealized Models of Transit Surveys}
-
 \subsection{Model \#1: fixed stars, fixed planets, twin binaries}
@@
 We return to our group of binarity-ignoring astronomers. They do 
-not know the true planet population~--~they would like to discover it!
+not know the true rate density~--~they would like to discover it!
 In their signal-to-noise limited transit survey, they select stars 
@@
 \end{equation}
-for $R$ the (constant) stellar radius, $F$ the photon flux, $L_{\rm sys}$ the 
+for $R$ the constant stellar radius, $F$ the photon flux, $L_{\rm sys}$ the 
 luminosity of a system, and $d$ its distance from us.
@@
 that of single stars.
-This is a bad move; in reality the transit signal for any planet in a 
+This is a bad move, because the transit signal for any planet in a 
 twin binary will be diluted by a factor of two:
@@
 $L_{\rm host}$ the the planet host's luminosity.
-This means that the actual maximum searchable distance for binaries is 
-$1/\sqrt{2}\times$ that of single stars.
+This means that the actual maximum searchable distance for binaries, $d_{\rm 
+det}$, is $1/\sqrt{2}$ times that of single stars.
 The situation is illustrated in Fig.~\ref{fig:model_1_volumes}: only one in 
@@
 
+\begin{figure}[!tb]
+    \begin{center}
+        \includegraphics[width=0.6\textwidth]{figures/visualize_volumes.pdf}
+    \end{center}
+    \caption{
+        Cartoon of the different selected and searchable volumes for single 
+        stars (left column), and twin binaries (right column).
+        This model (\#1) assumes all stars have equal mass and luminosity.
+        Since the observer does not recognize the brighter binaries, they 
+        select 
+        them out to a larger distance, $\sqrt{2}\times$ that of single stars.
+        However, dilution causes the twin binaries to only be searchable in 
+        one 
+        eighth of their selected volume.
+    }
+    \label{fig:model_1_volumes}
+\end{figure}
+
 \paragraph{What do the observers ignoring binarity infer?} 
-The binarity-ignoring observers assume that every point on the sky with flux 
+The binarity-ignoring observers assume that all points on the sky with flux 
 above some minimum are searchable.
-They measure a detected planet rate density, and infer an apparent rate 
-density by correcting for $p_{\rm tra}$.
-The apparent rate density is
+They measure a detected planet rate density, and infer a rate 
+density by correcting for the transit probability.
+As a function of apparent radius, the apparent rate density is
 \begin{equation}
-\Gamma_a(r) = 
+\Gamma_a(r_a) = 
 \delta(r_p) Z_0 \frac{N_0}{N_0+N_1}  +
@@
 primary (secondary) is searchable.
-For this example, $p_{{\rm det},1}=p_{{\rm det},2}=1/8$.
+In this example, $p_{{\rm det},1}=p_{{\rm det},2}=1/8$; the detection 
+efficiency is the ratio of the searchable to selected volumes.
 
@@
 \end{enumerate}
+By making an assumption about the true number of planets per single, primary, 
+and secondary star ($Z_0,Z_1,$ and $Z_2$), we can assess the severity of 
+these errors.
+Taking $Z_0=Z_1=Z_2$, we plot the resulting occurrence rates over bins 
+in planet radius in Fig.~\ref{fig:errcases_model_1}.
+Though it is impossible for an observer to isolate any one of the above 
+errors without also addressing the others, mathematically it is simply a 
+matter of modifying the appropriate terms in 
+Eq.~\ref{eq:model_1_apparent_rate_density}.
+The resulting rates are also shown in 
+Fig.~\ref{fig:errcases_model_1}, and demonstrate how each 
+error individually affects the overall inferred rate.
 
-We show the resulting occurrence rates over bins in planet radius in 
-Fig.~\ref{fig:errcases_model_1}.
-
-%NOTE: YOU CAN BUTCHER THE FUCK OUT OF THIS SECTION. JNW WANTS EACH CASE TO BE 
-%EXPLAINED, INDIVIDUALLY. DROP ALL THE "i" SUBSCRIPTS B/C THEY ARE APPARENTLY 
-%CONFUSING.
-
-To express the rate density of detected planets, $\hat{\Gamma} = \sum 
-Q_i\Gamma_i$, we need the detection efficiencies for each system type, which 
-are products of the geometric and selection probabilities:
-\begin{align}
-Q_i(\vec{x}) &= Q_{g,i}(\vec{x}) Q_{c,i}(\vec{x}),\quad {\rm where}\ 
-\vec{x}=(r,R,a).
-\label{eq:general_detection_efficiency}
-\end{align}
-Similar to Pepper et al. (2003), but in a new context, we take $Q_c$ as the 
-ratio of the number of stars that were searchable to the number of stars that 
-were selected.
-Assuming a homogeneous distribution of stars, this gives
-\begin{equation}
-Q_{c,i}(\vec{x}) = \left(
-\frac{d_{{\rm det},i}(\vec{x})}{d_{\rm sel}(\vec{x})}
-\right)^3,
-\end{equation}
-for $d_{\rm sel}$ the maximum distance to which surveyed stars are selected, 
-and $d_{{\rm det},i}$ the maximum distance to which planets can actually be 
-detected about the $i^{\rm th}$ system type.
-Note that $d_{\rm sel} \geq d_{{\rm det},i}$.
-In a signal-to-noise limited transit survey in which the observer does not 
-know which stars are binaries, 
-\begin{equation}
-d_{\rm sel} \propto (r/R)^2 (L_{\rm sys} T_{\rm dur} A N_{\rm tra})^{1/2},
-\end{equation}
-for $L_{\rm sys}=L_1(1+\ell)$ the system luminosity, $T_{\rm dur}$ the 
-transit duration, $A$ the detector area, and $N_{\rm tra}$ 
-the number of observed transits.
-However,
-\begin{equation}
-d_{{\rm det},i} \propto \mathcal{D}_i(r/R)^2 (L_{\rm sys} T_{\rm dur} A N_{\rm 
-    tra})^{1/2},
-\label{eq:d_det_i}
-\end{equation}
-for the dilution $\mathcal{D}_i$ given by
-\begin{align}
-\mathcal{D}_i
-&=
-\left.
-\begin{cases}
-1 & \text{for } i=0,\ {\rm single} \\
-L_1 / L_{\rm sys} = (1+\ell)^{-1}, & \text{for } i=1,\ {\rm primary} \\
-\ell L_1 / L_{\rm sys} = (1 + \ell^{-1})^{-1}, & 
-\text{for } i=2,\ {\rm secondary},
-\end{cases}
-\right.
-\label{eq:dilution}
-\end{align}
-where the light ratio $\ell$ of a given binary is defined as the ratio of 
-the luminosity of the secondary to the primary.
-
-The maximum detectable distance to single stars is assumed to be known, and so 
-$d_{{\rm sel},0} = d_{{\rm det},0}$.
-This means our naive astronomer assumes the fraction of their selected stars 
-which are searchable is 1 (this is their ``assumed completeness'').
-For binary systems there is a necessary incompleteness, and combining 
-Eqs.~\ref{eq:general_detection_efficiency} through~\ref{eq:dilution} yields
-\begin{align}
-Q_0 &= Q_{g,0}Q_{c,0} = Q_{g,0} \label{eq:detection_efficiency_0}\\
-Q_1 &= Q_{g,1}Q_{c,1} = Q_{g,0} (1+q^\alpha)^{-3} \\
-Q_2 &= Q_{g,2}Q_{c,2} = Q_{g,0} q^{2/3} (1+q^{-\alpha})^{-3} q^{-5}, 
-\label{eq:detection_efficiency_2}
-\end{align}
-for $Q_{g,0}=R/a$, the transit probability in single star systems.
-In Eq.~\ref{eq:detection_efficiency_2}, we have assumed a stellar 
-mass-luminosity-radius relation: $R\propto M \propto L^{1/\alpha}$.
-The geometric transit probability is $Q_{g,2} = Q_{g,0}q^{2/3}$, and the 
-completeness is the latter term of Eq.~\ref{eq:detection_efficiency_2}.
-For $q=1$, the $q^{2/3}$ and $q^{-5}$ evaluate to unity, but they will later 
-become relevant.
-
-Summarizing, we have written the rate density for each system type
-(Eq.~\ref{eq:model1_occ_rate_density}) and the detection efficiency for each 
-system type 
-(Eq.~\ref{eq:detection_efficiency_0}-\ref{eq:detection_efficiency_2}),
-and so have fully specified the rate density of detected planets, 
-in addition to the true rate density.
+\begin{figure}[!tb]
+    \begin{center}
+        \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_model_1_brokenx.pdf}
+    \end{center}
+    \vspace{-0.5cm}
+    \caption{
+        Inferred planet occurrence rates over $0.01r_\oplus$ bins in planet 
+        radius,
+        for Model \#1.
+        This model has fixed stars, fixed planets, and twin binaries.
+        If the true planet radius is $r_p$, all planets 
+        detected in binaries will have apparent radii $r_a = r_p/\sqrt{2}$.
+        To illustrate the individual biases, we 
+        separated them:
+        ``only wrong $N_\star$'' means the only error is an incorrectly 
+        assumed 
+        number of selected stars;
+        ``only wrong $Q$'' means the only error is an incorrectly assumed 
+        detection efficiency (including both miscalculated transit 
+        probabilities 
+        and 
+        fraction of selected stars that are searchable);
+        ``only wrong $r_a$'' means the only error is misinterpretation of 
+        planetary radii, due to both transit depth dilution and also wrongly 
+        assumed host star radii.
+    }
+    \label{fig:errcases_model_1}
+\end{figure}
 
@@
 
-Define a rate density correction factor, $X_\Gamma$, as the ratio of the 
+We define a rate density correction factor, $X_\Gamma$, as the ratio of the 
 apparent to true rate densities:
@@
 \end{equation}
-This factor can be a function of whatever parameters $\Gamma_a$ and $\Gamma$ 
-depend on; in this study, the planet radius is most relevant.
-For the twin-binaries model,
+This correction factor can be a function of whatever parameters $\Gamma_a$ and 
+$\Gamma$ depend on; in this study, the planet radius is most relevant.
+
+Still assuming that the number of planets per single, primary, and 
+secondary star are equal ($Z_0=Z_1=Z_2$), we find a rate density correction 
+factor at the true planet radius of
 \begin{equation}
-X_\Gamma(r)
-=
-\frac{w_a \Lambda_0\delta^3(r_p) + 
-    w_b(\Lambda_1 Q_{c,1} + \Lambda_2 Q_{c,2}) \delta^3(r_p/\sqrt{2})  }
-{(w_0\Lambda_0 + w_1\Lambda_1 + w_2\Lambda_2)\delta^3(r_p)}
-\label{eq:model1_correction}
+X_\Gamma(r_p) = (1+\mu)^{-1},
+\label{eq:Z_eq_model_1_correction}
 \end{equation}
-where $\delta^3(r_p)$ is shorthand for $\delta^3(r-r_p,R-R_\star,a-a_p)$.
-
-If we take the rates $\Lambda_i$ to be equal, applying the definitions of 
-the weights gives a rate density correction factor at $r=r_p$ of
-$X_\Gamma(r_p) = (1+\mu)^{-1}$, where 
+where 
 \begin{align}
@@
 \frac{n_b}{n_s} \left(\frac{d_{\rm sel,b}}{d_{\rm sel,s}}\right)^3 = 
-\frac{{\rm BF}}{1-{\rm BF}} (1+\ell)^{3/2},
+\frac{{\rm BF}}{1-{\rm BF}} (1+\ell)^{3/2}.
 \label{eq:mu_definition}
 \end{align}
-for $n_b$ and $n_s$ the number density of binaries and singles in a 
-volume limited sample.
-Using Raghavan et al. (2010)'s $0.7-1.3M_\odot$ multiplicity fraction as our 
-binary fraction\footnote{
+In Eq.~\ref{eq:mu_definition}, $n_b$ and $n_s$ are the number density of 
+binaries and singles in a volume limited sample, and the maximum selected 
+distance for binary and single systems are $d_{\rm sel,b}$ and $d_{\rm sel,s}$.
+The light ratio $\ell$ is defined relative to the primary, so that
+$L_{\rm sys} = L_1(1+\ell)$.
+The binary fraction in a volume limited sample is ``{\rm BF}''.
+For instance, Raghavan et al., (2010) found a multiplicity fraction\footnote{
     The binary fraction is the fraction of systems in a volume-limited sample 
-    that 
-    are binary. It is equivalent to the multiplicity fraction if there are no 
-    triple, quadruple, or higher order multiples. In that case, ${\rm BF} = 
-    n_b / 
-    (n_s+n_b)$.
-}, we set ${\rm BF}=0.44$.
-The resulting correction to the rate density is $X_\Gamma(r_p) \approx 0.31$. 
-The correction at $r_p/\sqrt{2}$ is infinite.
-The numerical realization of this model agrees with these analytic values, and 
-its output is shown in Fig~\ref{fig:errcases_model_1}.
-%beta = 2.2223355980148636
-If instead we assume that $\Lambda_0 = \Lambda_1$, but that $\Lambda_2=0$, we 
-find 
-$X_\Gamma(r_p) = (1+2\mu)/(1+\mu)^2$.
-Taking the same binary fraction, this evaluates to $X_\Gamma(r_p)\approx 0.53$.
-Since the correction to the rate is equal to that of rate density, at 
-$r=r_p$, the occurrence rate is underestimated by a factor of roughly 2 to 3.
+    that are binary. It is equivalent to the multiplicity fraction if there 
+    are no triple, quadruple, or higher order multiples. In that case, ${\rm 
+    BF} = n_b / (n_s+n_b)$.
+}
+for primaries with masses $0.7-1.3M_\odot$ of 0.44. 
+``Twin binaries'' are perhaps 10-20\% of the binaries in a volume-limited 
+sample, depending on how ``twin'' is defined.
+Thus a representative twin binary fraction to use in
+Eq.~\ref{eq:Z_eq_model_1_correction} would be ${\rm BF}\approx 
+0.05$-$0.1$. This yields a rate density correction $X_\Gamma(r_p)$ of 0.79 if 
+${\rm BF}=0.1$, and 0.88 if ${\rm BF}=0.05$.
+Rephrasing the result, the apparent rate would be half the true rate 
+if the twin binary fraction were $(2^{3/2}+1)^{-1}\approx 0.26$.
+Fortunately, in most contexts it is not that high.
 
-%Note that a correction to the inferred rate, $X_\Lambda$, can be 
-%defined analogously:
-%\begin{equation}
-%X_\Lambda \equiv \frac{\Lambda_a}{\Lambda}.
-%\end{equation}
-%For this twin binary model, the correction to the rate is the same as that to 
-%the rate density.
+An alternative assumption is that secondaries do not host planets. In this 
+case, $Z_0=Z_1$, and $Z_2=0$. The correction to the rate density at the true 
+planet radius becomes
+\begin{equation}
+X_\Gamma(r_p) = (1+2\mu)/(1+\mu)^2.
+\end{equation}
+This evaluates to 0.95 if ${\rm BF}=0.1$, and 0.99 if ${\rm BF}=0.05$.
+While it is hard to justify the assumption that secondaries are planet-less, 
+it is worth noting that $\Gamma_a/\Gamma$ is sensitive to the relative number 
+of planets per single, primary, and secondary.

### 2017-11-12 src/hj_rate.py

@@ -14,10 +14,10 @@ n_stars = 836 # number of stars in Wright et al (2012)
 n_HJ = 10 # number of HJs in Wright et al (2012)
 
 m = int(1e5)  # number of monte carlo iterations
-  
+
 eta = 5.7e-3 # Petigura+ in prep's reported HJ rate
 eta_unc = 1.3e-3
-  
+
 ####################
 ndet = np.zeros((m))
 
@@ -32,11 +32,11 @@ q = ndet >= n_HJ
 
 print('p means fraction of MC trials with at least {:d} HJs'.
         format(n_HJ))
-print('without taking Z or binaries into account, p = {:.2f}'.format(
-    np.sum(q)/m 
+print('without taking Z or binaries into account, p = {:.3f}'.format(
+    np.sum(q)/m
     ))
 
-  
+
 ####################
 eta *= 1.2
 ndet = np.zeros((m))
@@ -49,8 +49,8 @@ for i in range(m):
     ndet[i] = np.random.poisson(n_stars*Lambda)
 
 q = ndet >= n_HJ
-print('taking Z into account, p = {:.2f}'.format(
-    np.sum(q)/m 
+print('taking Z into account, p = {:.3f}'.format(
+    np.sum(q)/m
     ))
 
 ####################
@@ -65,6 +65,6 @@ for i in range(m):
     ndet[i] = np.random.poisson(n_stars*Lambda)
 
 q = ndet >= n_HJ
-print('taking Z and binaries into account, p = {:.2f}'.format(
-    np.sum(q)/m 
+print('taking Z and binaries into account, p = {:.3f}'.format(
+    np.sum(q)/m
     ))

### 2017-11-12 src/plot_HJ_correction_vs_Ztwo.py

@@ -72,7 +72,7 @@ if __name__ == '__main__':
 
     ax.legend(loc='best',fontsize='medium')
 
-    ax.set_xlabel('$\Lambda_2/\Lambda_0$', fontsize='large')
+    ax.set_xlabel('$Z_2/Z_0$', fontsize='large')
     ax.set_ylabel('HJ rate (planets per thousand stars)', fontsize='large')
 
     outname = '../results/HJ_correction_inputrate_vs_HJratevalues'

### 2017-11-12 src/plot_print_earth_rate_analog.py

@@ -90,7 +90,7 @@ if __name__ == '__main__':
 
     ax.legend(loc='best',fontsize='medium')
 
-    ax.set_xlabel('$\Lambda_2/\Lambda_0$', fontsize='large')
+    ax.set_xlabel('$Z_2/Z_0$', fontsize='large')
     ax.set_ylabel('Earth rate (planets per hundred stars)', fontsize='large')
 
     outname = '../results/earth_inputrate_vs_etaearthratevalues'

### 2017-11-12 paper/conclusion.tex
paper: wordsmithing

\section{Conclusion}
\label{sec:conclusion}

This study presented three simple models for the effects of binarity on 
occurrence rates measured by transit surveys.
The most realistic of these models (Model \#3) suggests that binarity does 
lead to underestimates in transit survey occurrence rates, but with less than 
$30\%$ relative error.
The model further suggests that hot Jupiter rates measured by transit surveys 
are biased to infer $\approx 1.3\times$ fewer hot Jupiters per star than 
surveys that only measure occurrence rates about single stars ({\it 
i.e..,} radial velocity surveys).
It also indicates that binarity's effects on the measured 
occurrence rates of Earth-sized planets are far smaller than current 
systematic uncertainties.
Though our models are simplistic, their agreement with Barclay \& 
Collaborator's recent detailed simulations indicate that they may capture the 
essential ingredients.

### 2017-11-12 paper/discussion.tex
paper: wordsmithing

@@
 Specifically, our results from Sec.~\ref{sec:model_3} indicate that binarity 
-might lead to underestimate HJ rates by a multiplicative factor of $\approx 
+could lead to underestimated HJ rates by a multiplicative factor of $\approx 
 1.3$.
@@
 23\% of RV surveys would detect at least 10 hot Jupiters, and any discrepancy 
-would be quite teneous.
+would be quite tenuous
 We emphasize that this result is only suggestive~--~a true resolution of the 

### 2017-11-14 paper/introduction.tex
paper: improved clarity; corrected eqn error

@@
 They count the apparent number of selected stars, $N_\star$.
-Assuming their survey is limited by Poisson noise, our astronomers compute 
+Assuming their survey is limited by Poisson noise, the group computes
 their detection efficiency $p_{\rm det}$ as a function of planetary and 
@@
 To gain intuition for the many observational biases at play,
-we consider the following idealized transit surveys:
+we consider a set of idealized transit surveys:
 \begin{itemize}
@@
 our transit survey models in Secs.~\ref{sec:model_1}-\ref{sec:model_3}, where 
-subsequent subsections correspond to the models above.
+each subsection corresponds to a model listed above.
 We interpret these calculations throughout, and in 
-Sec.~\ref{sec:discussion} discuss their relevance to topical questions in 
+Sec.~\ref{sec:discussion} connect them to topical questions in 
 the interpretation of transit survey occurrence rates.

### 2017-11-14 paper/main.tex
paper: improved clarity; corrected eqn error

@@
 For the occurrence of Earth-sized planets, in our most realistic model the 
-underestimate is by $\approx 15\%$~--~at present far smaller than 
+rate is underestimated by $\approx 15\%$~--~at present far smaller than 
 systematic uncertainties on real $\eta_\oplus$ measurements.

### 2017-11-14 paper/model_2.tex
paper: improved clarity; corrected eqn error

@@
 \label{sec:model_2}
+
+\begin{figure}[!tb]
+    \centering
+    \includegraphics[width=0.6\textwidth]{figures/q_distribn_mag_limited.pdf}
+    \caption{
+        The distribution of the mass ratio for a magnitude limited sample of 
+        binary stars. The underlying mass ratios are drawn from a uniform 
+        distribution in a volume-limited sample, quite similar to that of 
+        Raghavan 
+        et al. (2010)'s Fig. 13.
+        The entire bias can be understood analytically 
+        (Eq.~\ref{eq:Malmquist_bias}).
+        {\bf todo: make y axis label p(secondary with q).}
+    }
+    \label{fig:q_distribn_mag_limited}
+\end{figure}
 
@@
 \end{equation}
-where $p_2(q)$ is expressed in terms of the mass ratio instead of the 
-secondary star's radius for convenience ($q$ and $R_2$ are interchangeable).
-The probability that a secondary hosts a planet, as a function of the mass 
-ratio, is
-\begin{align}
-p_2(q) &= p({\rm has\ planet}\,|\,{\rm secondary\ with\ }q) \times
-          p({\rm secondary\ with\ }q)
-          \\
-p_2(q) &\propto q^{\gamma + \beta} (1+q^\alpha)^{3/2}.
-\label{eq:model_2_p_2}
-\end{align}
-We take first term, $p({\rm has\ planet}\,|\,{\rm secondary\ with\ }q)$, as a 
-power law of $q$ with exponent $\gamma$.
-The second term, $p({\rm secondary\ with\ }q)$, 
-is the product of the volume limited probability, $q^\beta$, and a 
-Malmquist-like bias, $(1+q^\alpha)^{3/2}$.
+where $p_2(q)$ is mass-ratio dependent shape function in secondaries. A fully 
+general approach would parametrize $p_2(q)$ as a power law, $p_2(q) \propto 
+q^\gamma$. For simplicity we will always take $\gamma=0$, the uniform case.
+%We have written $\Gamma$ in terms of the mass ratio instead of the 
+%secondary star's radius for convenience ($q$ and $R_2$ are interchangeable).
+The interpretation of $Z_i$ is still ``the number of planets per star of 
+type $i$'', but now for secondaries this must include a marginalization 
+over both the mass ratio and the planet radius.
+
+There is also a Malmquist bias in Eq.~\ref{eq:model2_rate_density}, hidden 
+away in the numbers of selected stars.
 This is because the selected sample at a fixed planet radius and period is 
 magnitude-limited.
+Given a binary, the probability of drawing a mass ratio $q$ in a 
+magnitude-limited sample scales as
+\begin{equation}
+p({\rm draw\ }q | {\rm system\ is\ binary}) \propto q^\beta (1+q^\alpha)^{3/2}
+\label{eq:Malmquist_bias}
+\end{equation}
+where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
+ratio $q$, and the latter term is the Malmquist bias.
 We show the magnitude-limited mass ratio distribution for the $\beta=0$ case 
 in Fig.~\ref{fig:q_distribn_mag_limited}.
-We emphasize that in any Monte Carlo simulation of a transit survey, it is 
+We emphasize that in Monte Carlo simulations of transit surveys, it is 
 important to draw binaries from the correctly biased mass-ratio distribution 
@@
 density for specific mass ratios of interest $q_{\rm min} < q < q_{\rm 
-max}$ is
+max}$ is then
 \begin{equation}
@@
 \end{equation}
-where $p_2(q)$ is given by Eq.~\ref{eq:model_2_p_2}, and must be normalized to 
-unity.
+where $p_2(q)\propto q^\gamma$, and must be normalized to unity.
 
-\begin{figure}[!tb]
-    \centering
-    \includegraphics[width=0.6\textwidth]{figures/q_distribn_mag_limited.pdf}
-    \caption{
-        The distribution of the mass ratio for a magnitude limited sample of 
-        binary stars. The underlying mass ratios are drawn from a uniform 
-        distribution in a volume-limited sample, quite similar to that of 
-        Raghavan 
-        et al. (2010)'s Fig. 13.
-        The entire bias can be understood analytically 
-        (Eq.~\ref{eq:model_2_p_2},
-        with $\gamma=0$).
-        The numerical comparison uses a realistic empirical mass-luminosity 
-        relation rather than $L=M^{3.5}$, found by fitting main sequence dwarf 
-        mass luminosity data compiled from Torres et al. [2009] and Benedict 
-        et 
-        al. [2016].
-    }
-    \label{fig:q_distribn_mag_limited}
-\end{figure}
-
-\paragraph{What does the observers ignoring binarity infer?}
-As a reminder, the observers compute an apparent rate density by correcting 
-the number of detections per star for the transit probability and the 
-detection efficiency.
-In this process, the binarity-ignoring observers make the following errors:
+\paragraph{What do the observers ignoring binarity infer?}
+As a reminder, the binary-ignoring observers compute an apparent rate density 
+by correcting the number of detections per star for the transit probability 
+and the detection efficiency.
+In this process, they make the following errors:
 \begin{enumerate}
@@
 %
-\item They assume the transit probability for all stars to be $R_\star/a$. 
+\item They assume a transit probability for all stars of $p_{\rm tra} = 
+R_\star/a$. 
 For planets orbiting secondaries at fixed period, the true transit probability 
-is $q^{2/3} R_\star/a$, since the secondaries have smaller radii and masses.
+is $q^{2/3} p_{\rm tra}$, since the secondaries have smaller radii and masses.
 %
@@
 of the apparent radius; the last is the mass ratio distribution given by 
-Eq.~\ref{eq:model_2_p_2}.
-The analytic solution for $i=1$ is
+Eq.~\ref{eq:Malmquist_bias}.
+An analytic solution can be found for $i=1$.
+For $i=2$ there is no analytic solution, because evaluating the integral 
+requires imposing the constraint that $r_a  = r_p 
+(1+q^{-\alpha})^{-1/2}q^{-1}$. This equation can be re-written
+\begin{equation}
+\left(\frac{r_p}{r_a}\right)^2 = q^2 + q^{-\alpha + 2},
+\end{equation}
+which has no analytic solution for $q(r_a)$ except for special values of 
+$\alpha$, the mass-luminosity exponent.
+For $\alpha=3.5$, our nominal case, semianalytic solutions do exist.
+However, since our main interest is in understanding the qualitative behavior 
+of the solutions, we derive a limiting case, and then proceed 
+numerically.
+
+\begin{comment}
+The analytic solution for $i=1$ is something like
 \begin{equation}
@@
 q^{\gamma+\beta} (1+q^\alpha)^{3/2} {\rm d}q$.
+\end{comment}
 
-For $i=2$, there is no analytic solution, because evaluating the integral 
-requires imposing the constraint that $r_a  = r_p 
-(1+q^{-\alpha})^{-1/2}q^{-1}$. This equation can be re-written
-\begin{equation}
-\left(\frac{r_p}{r_a}\right)^2 = q^2 + q^{-\alpha + 2},
-\end{equation}
-which has no analytic solution for $q(r_a)$ except for special values of 
-$\alpha$, the mass-luminosity exponent.
-For $\alpha=3.5$, our nominal case, semianalytic solutions could be found.
-However, since our main interest is in understanding the qualitative behavior 
-of the solutions, we derive a few limiting cases, and then proceed 
-numerically.
-
-\paragraph{Limiting cases of rate density correction}
+\paragraph{Limiting case of rate density correction}
 Recall that the rate density correction factor, $X_\Gamma$, is the ratio of 
@@
 \end{equation}
-for $c_0\approx 0.49$, $c_1\approx 0.32$, and $c_2$ unknown.
-%171011_integrals.nb
-Evaluating the correction term at $r=r_p$, since $\lim_{q\rightarrow0} 
-p_i(r_a)=0$ for $i\in\{1,2\}$,
+for $c_0\approx 0.49$, and the coefficients $c_1, c_2$ unknown.
+%171011_integrals.nb $c_1\approx 0.32$
+We can evaluate the correction term at $r=r_p$, since $\lim_{r_a\rightarrow 
+r_p} I_i(r_a)=0$ for $i\in\{1,2\}$:
 \begin{equation}
@@
 
-Once the free parameters are specified, the population of selected stars is 
-constructed.
+Once the user specifies the free parameters, the program constructs a 
+population of selected stars.
 Each selected star is assigned a type (single, primary, secondary), a 
@@
 The mass ratios are drawn from the appropriate magnitude-limited distribution 
-(Eq.~\ref{eq:model_2_p_2}).
+(Eq.~\ref{eq:Malmquist_bias}).
 If it is single, a selected star is assumed to be searchable.
@@
 We first validate our model by ensuring it produces the analytically-predicted 
-results for Model \#1, and the limiting cases of Model \#2 described above.
+results for Model \#1, and the limiting case of Model \#2 described above.
 Following validation, assuming ${\rm BF}=0.44$, $\alpha=3.5$, 
-$\beta=\gamma=0$, and taking $Z_0=Z_1=Z_2$, we compute the true and apparent 
-occurrence rates over bins in planet radius.
+$\beta=\gamma=0$, and taking $Z_0=Z_1=Z_2=0.5$, we compute the true and 
+apparent occurrence rates over bins in planet radius.
 The results are shown in Figs.~\ref{fig:errcases_model_2_linear} 

### 2017-11-14 paper/simplest_effects.tex
paper: improved clarity; corrected eqn error

@@
 $L_{\rm host}$ the the planet host's luminosity.
-This means that the actual maximum searchable distance for binaries, $d_{\rm 
+This means that the true maximum searchable distance for binaries, $d_{\rm 
 det}$, is $1/\sqrt{2}$ times that of single stars.
@@
 above some minimum are searchable.
-They measure a detected planet rate density, and infer a rate 
-density by correcting for the transit probability.
-As a function of apparent radius, the apparent rate density is
+They correct their assumed number of searchable stars for the transit 
+probability.
+As a function of apparent radius, they then report an apparent rate density of
 \begin{equation}
@@
 \end{enumerate}
-By making an assumption about the true number of planets per single, primary, 
-and secondary star ($Z_0,Z_1,$ and $Z_2$), we can assess the severity of 
-these errors.
-Taking $Z_0=Z_1=Z_2$, we plot the resulting occurrence rates over bins 
-in planet radius in Fig.~\ref{fig:errcases_model_1}.
-Though it is impossible for an observer to isolate any one of the above 
-errors without also addressing the others, mathematically it is simply a 
+
+To assess the severity of these errors, we need to make assumptions about the 
+stellar and planetary populations.
+The important quantity for the stellar population is $N_1/N_0$, the ratio of 
+selected primaries (or binaries) to singles. We can define
+\begin{align}
+\mu \equiv \frac{N_1}{N_0} &=
+\frac{n_b}{n_s} \left(\frac{d_{\rm sel,b}}{d_{\rm sel,s}}\right)^3 = 
+\frac{{\rm BF}}{1-{\rm BF}} (1+\ell)^{3/2},
+\label{eq:mu_definition}
+\end{align}
+where $n_b$ and $n_s$ are the number density of binaries and singles in a 
+volume limited sample, and the maximum selected distance for binary and single 
+systems are $d_{\rm sel,b}$ and $d_{\rm sel,s}$.
+The light ratio $\ell$ is defined relative to the primary, so that
+$L_{\rm sys} = L_1(1+\ell)$.
+The binary fraction in a volume limited sample is ``{\rm BF}''.
+For instance, Raghavan et al., (2010) found a multiplicity fraction\footnote{
+    The binary fraction is the fraction of systems in a volume-limited sample 
+    that are binary. It is equivalent to the multiplicity fraction if there 
+    are no triple, quadruple, or higher order multiples. In that case, ${\rm 
+        BF} = n_b / (n_s+n_b)$.
+} of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$. 
+``Twin binaries'' are perhaps 10-20\% of the binaries in a volume-limited 
+sample, depending on how ``twin'' is defined.
+Thus a representative twin binary fraction for this model is ${\rm BF}\approx 
+0.05$-$0.1$.
+
+Further, we need to assume knowledge of the true number of planets per 
+single, primary, and secondary star ($Z_0,Z_1,$ and $Z_2$).
+Taking $Z_0=Z_1=Z_2=1/2$, we plot the resulting occurrence rates as a function 
+of planet radius in Fig.~\ref{fig:errcases_model_1}.
+Though it is impossible for an observer to isolate any one of binarity's 
+biases without also addressing the others, mathematically it is simply a 
 matter of modifying the appropriate terms in 
@@
         To illustrate the individual biases, we 
-        separated them:
+        separated them.
+        On this and future plots,
         ``only wrong $N_\star$'' means the only error is an incorrectly 
@@
         ``only wrong $Q$'' means the only error is an incorrectly assumed 
-        detection efficiency (including both miscalculated transit 
-        probabilities 
-        and 
-        fraction of selected stars that are searchable);
-        ``only wrong $r_a$'' means the only error is misinterpretation of 
+        completeness (including both miscalculated $p_{\rm tra}$ 
+        and fraction of selected stars that are searchable, $p_{\rm det}$);
+        ``only wrong $r_a$'' means the only error is in miscalculated        
         planetary radii, due to both transit depth dilution and also wrongly 
@@
 
-Still assuming that the number of planets per single, primary, and 
+If we continue assuming that the number of planets per single, primary, and 
 secondary star are equal ($Z_0=Z_1=Z_2$), we find a rate density correction 
@@
 \begin{equation}
-X_\Gamma(r_p) = (1+\mu)^{-1},
+X_\Gamma(r_p) = \frac{1}{1+\mu},
 \label{eq:Z_eq_model_1_correction}
 \end{equation}
-where 
-\begin{align}
-\mu \equiv \frac{N_1}{N_0} &=
-\frac{n_b}{n_s} \left(\frac{d_{\rm sel,b}}{d_{\rm sel,s}}\right)^3 = 
-\frac{{\rm BF}}{1-{\rm BF}} (1+\ell)^{3/2}.
-\label{eq:mu_definition}
-\end{align}
-In Eq.~\ref{eq:mu_definition}, $n_b$ and $n_s$ are the number density of 
-binaries and singles in a volume limited sample, and the maximum selected 
-distance for binary and single systems are $d_{\rm sel,b}$ and $d_{\rm sel,s}$.
-The light ratio $\ell$ is defined relative to the primary, so that
-$L_{\rm sys} = L_1(1+\ell)$.
-The binary fraction in a volume limited sample is ``{\rm BF}''.
-For instance, Raghavan et al., (2010) found a multiplicity fraction\footnote{
-    The binary fraction is the fraction of systems in a volume-limited sample 
-    that are binary. It is equivalent to the multiplicity fraction if there 
-    are no triple, quadruple, or higher order multiples. In that case, ${\rm 
-    BF} = n_b / (n_s+n_b)$.
-}
-for primaries with masses $0.7-1.3M_\odot$ of 0.44. 
-``Twin binaries'' are perhaps 10-20\% of the binaries in a volume-limited 
-sample, depending on how ``twin'' is defined.
-Thus a representative twin binary fraction to use in
-Eq.~\ref{eq:Z_eq_model_1_correction} would be ${\rm BF}\approx 
-0.05$-$0.1$. This yields a rate density correction $X_\Gamma(r_p)$ of 0.79 if 
-${\rm BF}=0.1$, and 0.88 if ${\rm BF}=0.05$.
-Rephrasing the result, the apparent rate would be half the true rate 
-if the twin binary fraction were $(2^{3/2}+1)^{-1}\approx 0.26$.
-Fortunately, in most contexts it is not that high.
+This yields a correction of 0.79 if ${\rm BF}=0.1$, and 0.88 if ${\rm 
+BF}=0.05$.
+Rephrasing the result, if the twin binary fraction were 
+$(2^{3/2}+1)^{-1}\approx 0.26$, then the apparent rate would be half the true 
+rate.
+Fortunately, in most contexts the twin binary fraction is not that high.
 
-An alternative assumption is that secondaries do not host planets. In this 
+An alternative assumption is that secondaries do not host planets. In that 
 case, $Z_0=Z_1$, and $Z_2=0$. The correction to the rate density at the true 
@@
 \begin{equation}
-X_\Gamma(r_p) = (1+2\mu)/(1+\mu)^2.
+X_\Gamma(r_p) = \frac{1+2\mu}{(1+\mu)^2}.
 \end{equation}

### 2017-11-14 paper/main.tex
remake model 1 Fig w/ smaller BF

@@
 underestimate of the occurrence at the true radius by a multiplicative factor 
-of $0.8$ (assuming a 10\% twin binary fraction).
+of $0.76$ (assuming a 10\% twin binary fraction).
 Using more realistic models for the stellar population and planetary 

### 2017-11-14 paper/simplest_effects.tex
remake model 1 Fig w/ smaller BF

@@
         This model has fixed stars, fixed planets, and twin binaries. 
+        It assumes a twin binary fraction of ${\rm BF}=0.1$.
         If the true planet radius is $r_p$, all planets 
         detected in binaries will have apparent radii $r_a = r_p/\sqrt{2}$.
-        To illustrate the individual biases, we 
-        separated them.
+        We illustrate the individual biases by separating them.
         On this and future plots,
@@
 \end{equation}
-This yields a correction of 0.79 if ${\rm BF}=0.1$, and 0.88 if ${\rm 
+This yields a correction of 0.76 if ${\rm BF}=0.1$, and 0.87 if ${\rm 
 BF}=0.05$.

### 2017-11-14 src/plot_errcases_rate_densities_vs_radius.py

@@ -213,7 +213,7 @@ if __name__ == '__main__':
 
         make_plot(model_number)
 
-    make_plot(1, brokenx=True)
+    make_plot(1, brokenx=True, Λ_2=0.5)
     make_plot(2, logy=True)
     make_plot(3, logy=True)
     make_plot(3, withtext=True, stdout=True)

### 2017-11-14 results/make_merged.sh
cleanup results dir
Model #1's different BFs broke my easy merging scripts :(

@@ -1,6 +1,5 @@
 #!/usr/bin/env bash
 pdftk \
-  errcases_rate_density_vs_radius_model_1.pdf \
   errcases_rate_density_vs_radius_model_1_brokenx.pdf \
   errcases_rate_density_vs_radius_model_2.pdf \
   errcases_rate_density_vs_radius_logs_model_2.pdf \
@@ -10,7 +9,6 @@ pdftk \
   output errcases_merged.pdf
 
 pdftk \
-  rate_density_vs_radius_model_1.pdf \
   rate_density_vs_radius_model_1_brokenx.pdf \
   rate_density_vs_radius_model_2.pdf \
   rate_density_vs_radius_logs_model_2.pdf \

### 2017-11-14 src/plot_rate_densities_vs_radius.py
complete results directory cleanup
Running
`src/plot_rate_densities_vs_radius.py`
and
`src/plot_errcases_rate_densities_vs_radius.py`

now produces a slew of plots, which, when merged with
`results/make_merged.sh`, gives pdfs that you can read without being
overly confused.

@@ -33,7 +33,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
 
     # Make summary plot
     if isinstance(Λ_2,float) or isinstance(Λ_2,int):
-        fname = '../data/numerics/results_model_{:d}_Lambda2_{:.1f}.out'.format(
+        fname = '../data/numerics/results_model_{:d}_Lambda2_{:.2f}.out'.format(
                 model_number, Λ_2)
     else:
         fname = '../data/results_model_'+repr(model_number)+'.out'
@@ -154,7 +154,7 @@ if __name__ == '__main__':
 
         make_plot(model_number)
 
-    make_plot(1, brokenx=True)
+    make_plot(1, brokenx=True, Λ_2=0.5)
     make_plot(2, logy=True)
     make_plot(3, logy=True)
     make_plot(3, withtext=True, stdout=True)

### 2017-11-14 paper/model_2.tex
improved mass ratio distribution plot

@@
     \centering
-    \includegraphics[width=0.6\textwidth]{figures/q_distribn_mag_limited.pdf}
+    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
     \caption{
-        The distribution of the mass ratio for a magnitude limited sample of 
-        binary stars. The underlying mass ratios are drawn from a uniform 
-        distribution in a volume-limited sample, quite similar to that of 
-        Raghavan 
-        et al. (2010)'s Fig. 13.
+        The mass ratio distribution for a magnitude-limited sample of 
+        binary stars, in which the underlying volume-limited distribution is 
+        uniform (quite similar to {\it e.g.}, Raghavan et al. (2010)'s 
+        Fig.~16).
         The entire bias can be understood analytically 
         (Eq.~\ref{eq:Malmquist_bias}).
-        {\bf todo: make y axis label p(secondary with q).}
     }
@@
 \begin{equation}
-p({\rm draw\ }q | {\rm system\ is\ binary}) \propto q^\beta (1+q^\alpha)^{3/2}
+p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto q^\beta 
+(1+q^\alpha)^{3/2}
 \label{eq:Malmquist_bias}

### 2017-11-14 src/plot_HJ_correction_vs_Ztwo.py

@@ -1,3 +1,4 @@
+# -*- coding: utf-8 -*-
 '''
 Given that hot Jupiters are thought to be less common around less-massive
 stars, it would be more sensible to consider Λ_2 < Λ_0 , while letting single
@@ -5,7 +6,6 @@ stars and primaries host planets at the same rate.
 
 This plots the rates as a function of Λ_2 /Λ_0.
 '''
-# -*- coding: utf-8 -*-
 from __future__ import division, print_function
 import matplotlib as mpl
 mpl.use('pgf')

### 2017-11-14 src/plot_mass_ratio_distribution.py

@@ -1,0 +1,37 @@
+'''
+plot the mass ratio distribution for a volume-limited sample, and a
+magnitude-limited sample.
+'''
+# -*- coding: utf-8 -*-
+from __future__ import division, print_function
+from matplotlib import rc
+rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('text', usetex=True)
+
+import matplotlib.pyplot as plt
+import numpy as np
+from scipy.integrate import trapz
+
+f,ax = plt.subplots(figsize=(4,4))
+
+q = np.arange(-0.1,1.1+1e-3,1e-3)
+β = 0
+α = 3.5
+
+yvals = q**β * (1+q**α)**(3/2)
+yvals[(q>1)|(q<0)] = 0
+ax.plot(q, yvals/trapz(yvals, q), label='magnitude-limited', zorder=2)
+
+yvals = np.ones_like(q)
+yvals[(q>1)|(q<0)] = 0
+ax.plot(q, yvals, label='volume-limited', zorder=1)
+
+ax.legend(loc='best',fontsize='medium')
+
+ax.set_xlabel('$q=M_2/M_1$', fontsize='large')
+ax.set_ylabel('$p(\mathrm{draw\ }q\,|\,\mathrm{system\ is\ binary})$', fontsize='large')
+ax.set_ylim([-0.1,2.3])
+ax.set_xlim([-0.05,1.05])
+
+outname = '../results/mass_ratio_distribution'
+f.savefig(outname+'.pdf', bbox_inches='tight')

### 2017-11-14 paper/model_2.tex
merge model 2 figs; add aastex cmds

@@
 
+\begin{figure}
+\centering
+\epsscale{1.3}
+\plottwo{figures/errcases_rate_density_vs_radius_model_2.pdf}{figures/errcases_rate_density_vs_radius_logs_model_2.pdf}
+\caption{
+Inferred planet occurrence rates as a function of planet radius in Model \#2 
+({\it top:} linear, {\it bottom:} logarithmic).
+This model has fixed planets and primaries, and varying secondary masses, 
+radii, and luminosities.
+The latter three lines are described in Fig.~\ref{fig:errcases_model_1}.
+\label{fig:errcases_model_2}}
+\end{figure}
+
+\begin{comment}
 \begin{figure}[!t]
@@
 \end{figure}
+\end{comment}
 
@@
 apparent occurrence rates over bins in planet radius.
-The results are shown in Figs.~\ref{fig:errcases_model_2_linear} 
-and~\ref{fig:errcases_model_2_log}.
+The results are shown in Fig.~\ref{fig:errcases_model_2}.
 Evidently, dilution produces a spectrum of apparent planetary radii. This 

### 2017-11-14 paper/model_2.tex
wordsmithing

@@
 \end{equation}
-where $p_2(q)\propto q^\gamma$, and must be normalized to unity.
+where $p_2(q)\propto q^\gamma$, and is normalized to unity.
 
@@
 results for Model \#1, and the limiting case of Model \#2 described above.
-Following validation, assuming ${\rm BF}=0.44$, $\alpha=3.5$, 
-$\beta=\gamma=0$, and taking $Z_0=Z_1=Z_2=0.5$, we compute the true and 
+Following validation, we assume ${\rm BF}=0.44$, $\alpha=3.5$, 
+$\beta=\gamma=0$, and take $Z_0=Z_1=Z_2=0.5$. We then compute the true and 
 apparent occurrence rates over bins in planet radius.
@@
 Evidently, dilution produces a spectrum of apparent planetary radii. This 
-leads to overestimated rates everywhere except where there 
-are actually planets, where the rate is underestimated by a factor of two.
+leads to overestimated rates everywhere except where at the true planet 
+radius, where the rate is underestimated by a factor of two.
+Compared to Model \#1 (Fig.~\ref{fig:errcases_model_1}), the general picture 
+is that the apparent radius distribution is ``blurred'' by the varying 
+secondary light ratios.

### 2017-11-14 paper/conclusion.tex
add improvements to text

@@
 occurrence rates measured by transit surveys.
+The simplest of these models (Model \#1) provides an order-of-magnitude 
+estimate of how much binarity biases occurrence rates.
 The most realistic of these models (Model \#3) suggests that binarity does 
@@
 It also indicates that binarity's effects on the measured 
-occurrence rates of Earth-sized planets are far smaller than current 
+rates of Earth-sized planets are far smaller than current 
 systematic uncertainties.
-Though our models are simplistic, their agreement with Barclay \& 
-Collaborator's recent detailed simulations indicate that they may capture the 
-essential ingredients.
+Though our models are simplistic, their agreement with T. Barclay's recent 
+independent simulations indicate that they capture the essential 
+ingredients.

### 2017-11-14 paper/discussion.tex
paper: improved clarity; corrected eqn error
add improvements to text

--- 2017-11-12 paper/discussion.tex
@@
 
-\paragraph{How Has Binarity Been Considered in Occurrence Rate Measurements?}
-Many authors have computed planet occurrence rates using transit 
-survey data\footnote{
+\paragraph{How has binarity been considered in occurrence rate measurements?}
+Binarity introduces systematic uncertainty to star and planet counts, and also 
+to estimates of pipeline completeness.
+In spite of this fact, stellar multiplicity has mostly been ignored in 
+calculations of planet occurrence rates using transit survey data\footnote{
     An online list of occurrence rate papers is maintained at 
     \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
-}.
-Notable studies using {\it Kepler}\ data include those by Howard et al. 2012, 
-Fressin et al., 2013, Foreman-Mackey et al., 2014, Dressing \& Charbonneau 
-2015, and Burke et al. 2015.
-Mostly if not entirely, these studies have ignored stellar multiplicity.
-However, binarity clearly introduces a level of systematic uncertainty to 
-pipeline completeness, as well as to star and planet counts.
-No one has yet carefully studied the magnitude of this issue for 
-{\it Kepler} occurrence rates.
-While the present work does not resolve this problem, it suggests the 
-approximate order of magnitude for the necessary correction factors.
-%NOTE: the above might be better in a "discussion" section?
+}~({\it 
+e.g.}, Howard et al. 2012, Fressin et al., 2013, Foreman-Mackey et 
+al., 2014, Dressing \& Charbonneau 2015, and Burke et al. 2015).
+For {\it Kepler} occurrence rates specifically, it seems that no one has yet 
+carefully assessed the magnitude of the issue.
+While we do not resolve the problem, we do suggest
+the approximate scale of the necessary corrections in a survey-independent 
+manner.
 
@@
 interpretation of planet candidates. High resolution imaging 
-campaigns have been undertaken to measure the multiplicity of 
-almost all {\it Kepler}\ Objects of Interest 
+campaigns have measured the multiplicity of almost all {\it Kepler}\ Objects 
+of Interest 
 (Howell et al. 2011; Adams et al. 2012, 2013; Horch et al. 2012, 2014; 
@@
 sample's multiplicity statistics.
-In particular, they can be immediately applied to rectify binarity's influence 
+In particular, they can be immediately applied to rectify binarity's effects 
 on the mass-radius diagram (Furlan \& Howell 2017).
 
-%TODO: talk about N. R. Deacon et al 2015, Pan-STARRS1 here
+The high resolution imaging campaign is also beginning to connect with
+occurrence rate calculations.
+The most recent rate studies have used Furlan et al. (2017)'s 
+catalog to test the effects of removing KOI hosts with known companions, which 
+helps reduce contamination in the ``numerator'' of 
+the occurrence rate (Fulton et al. 2017, Petigura et al., in prep).
+However, without an understanding of the multiplicity statistics of the 
+non-KOI stars, the true completeness, and thus the true 
+occurrence rates, will remain biased.
+The first-order correction that we suggest, given the impracticality of 
+performing high-resolution imaging of every selected star in a transit survey,
+is to model the detection pipeline's efficiency while accounting for 
+binarity.
+%Simply put~--~do not assume binarity can be ignored, and take the relevant 
+%systematic uncertainties about the selected stars into account.
+For {\it Kepler}, this would require high resolution imaging of a
+comparison sample of non-KOI host stars. If the associated multiplicity 
+statistics are then included in a model of the pipeline's detection 
+efficiency, and the number of selected stars is appropriately counted, it 
+would correct most of binarity's biases.
 
-To help clarify {\it Kepler}-derived occurrence rates, the high resolution 
-imaging campaigns have not yet come full circle by observing a comparison 
-sample of non-KOI host stars.
-The most recent rate studies have thus used Furlan et al. (2017)'s 
-catalog to test the effects of removing KOI hosts with known companions, which 
-is an important step towards reducing contamination in the ``numerator'' of 
-the occurrence rate (Fulton et al. 2017).
-However, without an understanding of the multiplicity statistics of the 
-non-KOI hosting stars that are assumed to be searchable, the 
-true completeness, the true number of searchable stars, and thus the true 
-occurrence rates will remain uncertain.
-
-\paragraph{The Hot Jupiter Rate Discrepancy}
-There is at least one context in which measurement of 
-occurrence rates may already be showing the signatures of binarity.
+\paragraph{The hot Jupiter rate discrepancy}
+There is at least one context in which ignoring binarity may already be 
+leading to discrepant measurements.
 Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
@@
 The discrepancy has weak statistical significance ($<3\sigma$).
-That said, one reason to expect a difference is that the corresponding stellar 
+One reason to expect a difference is that the corresponding stellar 
 populations have distinct metallicities.
@@
 Transit surveys typically observe binaries, but the question of whether they 
-were searchable to begin with is usually left for later interpretation.
+were searchable to begin with is left for later interpretation.
 In spectroscopic follow-up of candidate transiting planets, the prevalence of 
@@
 Ignoring these complications, in this work we showed that
-binarity does bias transit survey occurrence rates, simply through its 
-effects on the number of searchable stars and the apparent radii of detected 
-planets.
+binarity biases transit survey occurrence rates through its effects on 
+completeness, star counts, and the apparent radii of detected planets.
 Specifically, our results from Sec.~\ref{sec:model_3} indicate that binarity 
-might lead to underestimate HJ rates by a multiplicative factor of $\approx 
+could lead to underestimated HJ rates by a multiplicative factor of $\approx 
 1.3$.
 
-We assess the effect this might have towards resolving the hot Jupiter rate 
-discrepancy by asking:
+To assess the effect this might have towards resolving the hot Jupiter rate 
+discrepancy we ask:
 what is the probability of Wright et al. (2012)'s result, given a rate drawn 
@@
 Table~\ref{tab:hj_rates}).
-In other words, we first take the true HJ rate as $\Lambda_{\rm HJ} = 5.7 \pm 
-1.3$, with Gaussian uncertainties, and then drawing from a Poisson 
-distribution compute the probability of detecting at least 10 hot Jupiters in 
-a sample of 836 stars.
+In other words, we first take the true HJ rate per thousand stars as 
+$\Lambda_{\rm HJ} = 5.7 \pm 1.3$, with Gaussian uncertainties. 
+We then draw from a Poisson distribution and compute the probability of 
+detecting at least 10 hot Jupiters in a sample of 836 stars.
 Without accounting for binarity or metallicity, only 4\% of RV surveys would 
@@
 Jupiters.
-If we then multiply again by $1.3$ to account for binarity's bias, we find that
+If we multiply once more by $1.3$ to account for binarity's bias, we find that
 23\% of RV surveys would detect at least 10 hot Jupiters, and any discrepancy 
-would be quite teneous.
+would be rather tenuous.
 We emphasize that this result is only suggestive~--~a true resolution of the 
@@
 Kepler}\ field's multiplicity statistics.
+
+\paragraph{The rate of Earth analogs}
+Per {\it Kepler}'s primary science objective, the rate of Earth-like planets 
+orbiting Sun-like stars has been independently measured by Youdin, Petigura, 
+Dong \& Zhu, Foreman-Mackey et al., and Burke et al. (2011, 2013, 2013, 2014, 
+and 2015 respectively).
+These efforts have found that the one-year terrestrial planet occurrence rate 
+varies between $\approx 0.03$ and $\approx 1$ per Sun-like star, depending on 
+assumptions that are made when retrieving the rate (Burke et al. 2015's 
+Fig.~17).
+In our Model \#3, the inferred rate is $\approx 0.84\times$ the true rate 
+around single stars.
+This bias is quite small compared to the other systematic factors that 
+currently dominate the dispersion in $\eta_\oplus$ measurements.
+If a future transit survey measures an absolute value of $\eta_\oplus$ to 
+better than a factor of two, binarity might merit closer attention.
+
+\paragraph{The CKS radius gap}
+By improving the stellar radii... {\bf TODO}
+%TODO DO THESE CALCULATIONS
 
@@
 This means that when high-resolution imaging discovers a binary companion in 
-system that hosts a detected transiting planet, the planet is much
+a system that hosts a detected transiting planet, the planet is much
 more likely to orbit the primary.
@@
 \paragraph{On the utility for future occurrence rate measurements}
-Though they will be difficult to distinguish from false positives, {\it TESS}\ 
-is expected to discover over $10^4$ giant planets (Sullivan et al. 2015).
-One possible use of this overwhelmingly large sample will to measure an
+{\it TESS}\ is expected to discover over $10^4$ giant planets (Sullivan 
+et al. 2015).
+Though they will be difficult to distinguish from false positives, one 
+possible use of this overwhelmingly large sample will to measure an
 occurrence rate of short-period giant planets.
-Our work indicates that if this measurement is to be more precise than $\sim 
+Our work indicates that if this measurement is to be more accurate than $\sim 
 30\%$, binarity cannot be neglected.
 
-\paragraph{What about {\it Kepler}?}
-Barclay \& Collaborator (in preparation) have performed the exercise 
-of taking stars selected by the {\it Kepler}\ team, pairing them with a 
-population of secondaries, injecting a realistic distribution of planet radii, 
+\paragraph{Independent approaches for estimating binarity's effects}
+T. Barclay et al. (in prep) have performed the exercise of taking stars 
+selected by the {\it Kepler}\ team, pairing them with a population of 
+secondaries, injecting a realistic distribution of planet radii, 
 and then comparing the inferred occurrence rates with the true ones.
@@
 Earth-sized planets $\approx 10\%$ less than the true rate.
-In our Model \#3, if all $\Lambda_i$'s are equal (a plausible assumption in 
-the lack of evidence to the contrary), the underestimate is by 16\%.
+In our Model \#3, if all $Z_i$'s are equal (a plausible assumption in 
+the lack of evidence to the contrary), the underestimate is by a comparable 
+16\%.

### 2017-11-14 paper/model_3.tex
add improvements to text

@@
 
-In this model, as in the previous one, all single and primary stars have 
+As in the previous model, all single and primary stars in this model have 
 identical properties.
-Only the secondaries have masses, radii, and luminosities that vary between 
+The secondaries have masses, radii, and luminosities that vary between 
 systems: $M\propto R \propto L^{1/\alpha}$.
-The radii of planets are assigned independently of any host system
-property, and are sampled from an intrinsic radius distribution, which we take 
-as
+The only addition is that we now let the radii of planets vary: they are 
+assigned independently of any host system property, and are sampled from the 
+true radius distribution, which we take as
 \begin{align}
@@
 $\alpha=3.5$, $\beta=\gamma=0$.
-We take $Z_i$, the occurrence rate integrated over all planet radii for the 
-$i^{\rm th}$ system type, to be equal for singles, primaries, 
-and secondaries.
+We take $Z_i$, the number of planets per single, primary, and secondary, to be 
+equal.
 
-For this model, we forgo analytic development and focus only on numerics.
-The occurrence rates are shown as a function of planet radius in 
+For this model, we forgo analytic development and simply run our Monte Carlo 
+program.
+The resulting occurrence rates are shown in 
 Fig.~\ref{fig:errcases_model_3_log}.
@@
         $-2.92$ 
-        above $2R_\oplus$, below which it is uniform (e.g., Howard et al., 
+        above $2r_\oplus$, below which it is uniform ({\it e.g.}, Howard et 
+        al., 
         2012).
@@
 
-\paragraph{Hot Jupiter Occurrence Rates}
+\paragraph{Hot Jupiter occurrence rates}
 Taking Fig.~\ref{fig:errcases_model_3_log} and counting the number of planets 
@@
 $Z_2$, the rate around 
-singles and primaries (green line) is independent of that around secondaries.
-Assuming that RV surveys are measuring the true rate around single stars (or 
-primaries), this suggests that binarity might contributes to the 
-HJ rate discrepancy at the $\sim 0.2\%$ level, independent of the HJ rate 
-around secondaries.
+singles and primaries (Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues} 
+green line) is independent of that around secondaries.
 
@@
     \caption{
-        $X_i$ is the occurrence rate integrated over all possible phase 
+        $Z_i$ is the occurrence rate integrated over all possible phase 
         space for the $i^{\rm th}$ system type. $Z_2/Z_0=1$ 
@@
 
-\paragraph{The Rate of Earth Analogs}
-The rate (density) of Earth-like planets orbiting Sun-like stars has 
-been independently measured by Youdin, Petigura, Dong \& Zhu, 
-Foreman-Mackey et al., and Burke et al., (2011, 2013, 2013, 2014, and 2015 
-respectively).
-These efforts have found that the one-year terrestrial planet occurrence rate 
-varies between $\approx 0.03$ and $\approx 1$ per Sun-like star, depending on 
-assumptions that are made when retrieving the rate (Burke et al. 2015's 
-Fig.~17).
-
+\paragraph{The rate of Earth analogs}
 Our model does not explicitly include the rate density's period-dependence, 
@@
 while keeping $Z_0 = Z_1$, the ratio of the inferred to true rate 
-around single stars hardly 
-changes by only a few percent (shown in 
+around single stars changes by only a few percent (shown in 
 Fig.~\ref{fig:earth_inputrate_vs_etaearthratevalues}).

### 2017-11-14 src/numerical_models.py
add model #4 fulton+ 17 gap experiment

@@ -6,6 +6,9 @@ Example usage:
 >>> python numerical_models.py --quickrun --modelnumber 3 --LambdaTwo 0.5
 
 Alternatively, use a wrapper like `run_numerical_models.py`.
+
+Models #1-#3 are as-discussed in the text.
+Model #4 is a version of the Fulton+ (2017) gap.
 '''
 
 from __future__ import division, print_function
@@ -69,6 +72,9 @@ def numerical_transit_survey(
         # File names assume 2 digits of precision for Λ_2.
         raise NotImplementedError
 
+    if model_number > 4:
+        raise NotImplementedError
+
     ######################
     # STELLAR POPULATION #
     ######################
@@ -90,7 +96,7 @@ def numerical_transit_survey(
         q = 1
         μ = B * (1 + q**α)**(3/2)
         N_1 = int(N_0 * μ) # number of selected primaries
-    elif model_number == 2 or model_number == 3:
+    elif model_number == 2 or model_number == 3 or model_number == 4:
         integral = 0.484174086070513 # 17/10/14.2 analytic result
         N_d = N_0 * B * (2**(3/2) - 3*integral)
         N_1 = int(N_d) # number of primaries = number of double star systems
@@ -109,7 +115,7 @@ def numerical_transit_survey(
         df.loc[df['star_type'] == 'single', 'q'] = np.nan
         q = np.ones(N_1)
 
-    elif model_number == 2 or model_number == 3:
+    elif model_number == 2 or model_number == 3 or model_number == 4:
         df['q'] = np.nan
 
         # Inverse transform sampling to get samples of q
@@ -171,7 +177,7 @@ def numerical_transit_survey(
             assert np.isclose(_1, 1/8, rtol=1e-2) \
                    and \
                    np.isclose(_2, 1/8, rtol=1e-2)
-    elif model_number == 2 or model_number == 3:
+    elif model_number == 2 or model_number == 3 or model_number == 4:
         # primaries should be more complete than 1/8
         np.testing.assert_array_less(
                 1/8, #smaller
@@ -218,6 +224,24 @@ def numerical_transit_survey(
 
         df['r'] = r_samples
         df.loc[df['has_planet'] == False, 'r'] = np.nan
+
+    elif model_number == 4:
+        r_pl, r_pu = 2, 22.5 # [Rearth]. Lower and upper bound for truncation.
+
[…]

### 2017-11-14 src/plot_errcases_rate_densities_vs_radius.py

@@ -29,7 +29,7 @@ import numpy as np
 from brokenaxes import brokenaxes
 
 def make_plot(model_number, logx=None, logy=None, withtext=None,
-        stdout=False, brokenx=False, Λ_2=None):
+        stdout=False, brokenx=None, Λ_2=None, xcut=None):
 
     # Make summary plot
     if not brokenx:
@@ -53,7 +53,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
 
     df = pd.read_csv(fname)
 
-    if model_number == 3:
+    if model_number == 3 or model_number == 4:
         xvals = np.append(0, df['bin_left'])
         ytrue = np.append(0, df['true_Λ'])
         yinferred = np.append(0, df['inferred_Λ'])
@@ -76,7 +76,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
                     model_number, error_case_number)
         df = pd.read_csv(fname)
 
-        if error_case_number == 3:
+        if error_case_number == 3 or model_number == 4:
             try:
                 np.testing.assert_almost_equal(
                         np.sum(df['inferred_Λ']),
@@ -87,7 +87,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
                 print(model_number, error_case_number)
                 print('assert failed')
 
-        if model_number == 3:
+        if model_number == 3 or model_number == 4:
             xvals = np.append(0, df['bin_left'])
             ytrue = np.append(0, df['true_Λ'])
             yinferred = np.append(0, df['inferred_Λ'])
@@ -133,6 +133,9 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
             ax.set_xlim([0.5,1.02])
         elif (model_number == 1 or model_number == 2) and (logx or logy):
             ax.set_xlim([-0.02,1.02])
+
+    if xcut:
+        ax.set_xlim([-0.3,5.3])
 
     if model_number == 3:
 
@@ -203,6 +206,9 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
         if isinstance(Λ_2,float) or isinstance(Λ_2,int):
             outname += '_Lambda2_{:.1f}'.format(Λ_2)
 
+    if xcut:
+        outname += '_xcut'
+
     f.savefig(outname+'.pdf', bbox_inches='tight')
 
 
[…]

### 2017-11-14 src/plot_rate_densities_vs_radius.py

@@ -29,7 +29,7 @@ import numpy as np
 from brokenaxes import brokenaxes
 
 def make_plot(model_number, logx=None, logy=None, withtext=None,
-        stdout=False, brokenx=None, Λ_2=None):
+        stdout=False, brokenx=None, Λ_2=None, xcut=None):
 
     # Make summary plot
     if isinstance(Λ_2,float) or isinstance(Λ_2,int):
@@ -53,7 +53,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
                 despine=True)
         ax=bigax
 
-    if model_number == 3:
+    if model_number == 3 or model_number == 4:
         xvals = np.append(0, df['bin_left'])
         ytrue = np.append(0, df['true_Λ'])
         yinferred = np.append(0, df['inferred_Λ'])
@@ -62,7 +62,10 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
         ytrue = np.append(df['true_Λ'],[0,0])
         yinferred = np.append(df['inferred_Λ'],[0,0])
 
-    ax.step(xvals, ytrue, where='post', label='true')
+    try:
+        ax.step(xvals, ytrue, where='post', label='true')
+    except:
+        import IPython; IPython.embed()
 
     ax.step(xvals, yinferred, where='post', label='inferred')
 
@@ -94,6 +97,9 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
             ax.set_xlim([0.5,1.02])
         elif (model_number == 1 or model_number == 2) and (logx or logy):
             ax.set_xlim([-0.02,1.02])
+
+    if xcut:
+        ax.set_xlim([-0.3,5.3])
 
     if model_number == 3:
         # Assess HJ rate difference.
@@ -144,6 +150,9 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
         if isinstance(Λ_2,float) or isinstance(Λ_2,int):
             outname += '_Lambda2_{:.1f}'.format(Λ_2)
 
+    if xcut:
+        outname += '_xcut'
+
     f.savefig(outname+'.pdf', bbox_inches='tight')
 
 
@@ -162,3 +171,6 @@ if __name__ == '__main__':
     make_plot(3, Λ_2=0)
     make_plot(3, logy=True, Λ_2=0)
     make_plot(3, withtext=True, stdout=True, Λ_2=0)
+
+    make_plot(4, Λ_2=0.5)
+    make_plot(4, xcut=True, Λ_2=0.5)

### 2017-11-14 src/numerical_models.py
update binning of model #4 plot
(this is why you should never version-control pdfs. ugh.)

@@ -304,8 +304,11 @@ def numerical_transit_survey(
         Δr = 0.01
         radius_bins = np.arange(0, 1+Δr, Δr)
         r_pu = 1
-    elif model_number == 3 or model_number == 4:
+    elif model_number == 3:
         Δr = 0.5
+        radius_bins = np.arange(0, r_pu+Δr, Δr)
+    elif model_number == 4:
+        Δr = 0.25
         radius_bins = np.arange(0, r_pu+Δr, Δr)
         #radius_bins = np.logspace(-2,4/3,21) # thought about it, opted against
 

### 2017-11-15 paper/discussion.tex
add bibtex citations; update model #4 figure

@@
 calculations of planet occurrence rates using transit survey data\footnote{
-    An online list of occurrence rate papers is maintained at 
+    A list of occurrence rate papers is maintained at 
     \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
-}~({\it 
-e.g.}, Howard et al. 2012, Fressin et al., 2013, Foreman-Mackey et 
-al., 2014, Dressing \& Charbonneau 2015, and Burke et al. 2015).
+}~
+\citep[\textit{e.g.},][]{howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,dressing_occurrence_2015,burke_terrestrial_2015}.
 For {\it Kepler} occurrence rates specifically, it seems that no one has yet 
-carefully assessed the magnitude of the issue.
+carefully assessed binarity's importance, or lack thereof.
 While we do not resolve the problem, we do suggest
@@
 of Interest 
-(Howell et al. 2011; Adams et al. 2012, 2013; Horch et al. 2012, 2014; 
-Lillo-Box et al. 2012, 2014; Dressing et al. 2014; Law et al. 2014; Cartier et 
-al. 2015; Everett et al. 2015; Gilliland et al. 2015; Wang et al. 2015a, 
-2015b; Baranec et al. 2016).
-The results of these programs have been collected by Furlan et al. 
-(2017), and they represent an important advance in understanding the KOI 
+\citep{howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
+    horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
+    law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
+    wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016}.
+The results of these programs have been collected 
+by~\citet{furlan_kepler_2017}, and they represent an important advance in 
+understanding the KOI 
 sample's multiplicity statistics.
 In particular, they can be immediately applied to rectify binarity's effects 
-on the mass-radius diagram (Furlan \& Howell 2017).
+on the mass-radius diagram~\citep{furlan_densities_2017}.
 
@@
 occurrence rate calculations.
-The most recent rate studies have used Furlan et al. (2017)'s 
+The most recent rate studies have used~\citet{furlan_kepler_2017}'s 
 catalog to test the effects of removing KOI hosts with known companions, which 
 helps reduce contamination in the ``numerator'' of 
-the occurrence rate (Fulton et al. 2017, Petigura et al., in prep).
+the occurrence rate (\citealt{fulton_california-_2017}; Petigura et al.\! 2018,
+in preparation).
 However, without an understanding of the multiplicity statistics of the 
@@
 populations have distinct metallicities.
-As argued by Gould et al. (2006), the RV sample is biased towards 
+As argued by \citet{gould_frequency_2006}, the RV sample is biased towards 
 metal-rich stars, which have been measured by RV surveys to preferentially 
-host more giant planets (Santos et al 2004, Fischer and Valenti 2005).
+host more giant 
+planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005}.
 The {\it Kepler}\ sample specifically has been measured to be more metal poor 
 than the local neighborhood, with a mean metallicity of $[{\rm M/H}]_{\rm 
-    mean}\approx -0.05$ (Dong et al., 2014; Guo et al., 2017).
-Studying the problem in detail, Guo et al. recently argued that the 
-metallicity difference could account for a $\approx 0.1\%$ difference in the 
-measured rates between the CKS and {\it Kepler}\ samples~--~not a $\approx 
-0.5\%$ difference.
-Guo et al. concluded that ``other factors, such as binary contamination and 
-imperfect stellar properties'' must also be at play.
+    mean}\approx -0.05$~\citep{dong_metallicities_2014,guo_metallicity_2017}.
+Studying the problem in detail, \citeauthor{guo_metallicity_2017}\! recently 
+argued that the metallicity difference could account for a $\approx 20\%$ 
+relative difference in the measured rates between the CKS and {\it Kepler}\ 
+samples~--~not a factor of two.
+\citeauthor{guo_metallicity_2017}\! concluded that ``other factors, such as 
+binary contamination and imperfect stellar properties'' must also be at play.
 
@@
 Radial velocity surveys typically reject both visual and spectroscopic binaries
-({\it e.g.}, Wright et al. 2012).
+\citep[\textit{e.g.},][]{wright_frequency_2012}.
 Transit surveys typically observe binaries, but the question of whether they 
@@
 discrepancy we ask:
-what is the probability of Wright et al. (2012)'s result, given a rate drawn 
-from the stated bounds of Petigura et al. (in prep)? (See 
-Table~\ref{tab:hj_rates}).
+what is the probability of \citet{wright_frequency_2012}'s result, given a 
+rate drawn from the stated bounds of Petigura et al.~(2018, in preparation)?
 In other words, we first take the true HJ rate per thousand stars as 
@@
 detect at least 10 hot Jupiters.
-If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account for Guo et al. 
-(2017)'s measured metallicity difference between the {\it Kepler}\ field and 
-the local solar neighborhood, 9\% of RV surveys would detect at least 10 hot 
-Jupiters.
+If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account for 
+~\citet{guo_metallicity_2017}'s measured metallicity difference between the 
+{\it Kepler}\ field and the local solar neighborhood, 9\% of RV surveys would 
+detect at least 10 hot Jupiters.
 If we multiply once more by $1.3$ to account for binarity's bias, we find that
@@
 Per {\it Kepler}'s primary science objective, the rate of Earth-like planets 
-orbiting Sun-like stars has been independently measured by Youdin, Petigura, 
-Dong \& Zhu, Foreman-Mackey et al., and Burke et al. (2011, 2013, 2013, 2014, 
-and 2015 respectively).
+orbiting Sun-like stars has been independently measured by 
+\citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
+    foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
 These efforts have found that the one-year terrestrial planet occurrence rate 
 varies between $\approx 0.03$ and $\approx 1$ per Sun-like star, depending on 
-assumptions that are made when retrieving the rate (Burke et al. 2015's 
-Fig.~17).
+assumptions that are made when retrieving the rate 
+(\citet{burke_terrestrial_2015}'s Fig.~17).
 In our Model \#3, the inferred rate is $\approx 0.84\times$ the true rate 
@@
 currently dominate the dispersion in $\eta_\oplus$ measurements.
-If a future transit survey measures an absolute value of $\eta_\oplus$ to 
+If a future analyses determine absolute values of $\eta_\oplus$ to 
 better than a factor of two, binarity might merit closer attention.
 
-\paragraph{The CKS radius gap}
-By improving the stellar radii... {\bf TODO}
-%TODO DO THESE CALCULATIONS
+One relevant caveat to our assessment of binarity's importance for 
+$\eta_\oplus$ measurements is that none of our models 
+included the rate density's period-dependence. However, close binaries usually
+provoke dynamical instabilities, leading to fewer long-period planets per 
+star~\citep[\textit{e.g.},][]{holman_long-term_1999,wang_influence_2014,
+    kraus_impact_2016}.
+This effect might further bias transit survey measurements of $\eta_\oplus$
+beyond our rough estimate.
+
+\paragraph{Precise features of the radius valley}
+\begin{figure}[!tb]
+    \centering
+    \includegraphics[width=.6\textwidth]{figures/rate_density_vs_radius_model_4_xcut.pdf}
+    \caption{
+        Inferred planet occurrence rates as a function of planet radius in 
+        a model with a radius gap (Eq.~\ref{eq:model4_radius_distribution}).
+        Similar to Model \#3, this model has fixed primaries and single stars, 
+        but varying secondaries.
+    }
+    \label{fig:model_4}
+\end{figure}
+Using improved stellar parameters measured by the California-{\it Kepler} 
+survey,~\citet{fulton_california-_2017} recently reported a ``gap'' in 
+the radius-period 
+plane~\citep{petigura_california-kepler_2017,johnson_california-kepler_2017}.
+The existence of the gap has been independently corroborated using 
+asteroseismically-determined stellar 
+parameters~\citep{van_eylen_asteroseismic_2017}.
+Precise measurement of the gap's features, in particular its width, 
+depth, and shape, requires accurate occurrence rates.
+To illustrate binarity's role in the issue, we make identical assumptions as 
+in Model \#3, but instead assume an intrinsic radius distribution
+\begin{align}
+p_r(r)
+&\propto
+\left.
+\begin{cases}
+r^\delta & \text{for } r\geq 2r_\oplus, \\
+0 & \text{for } 1.5r_\oplus < r < 2r_\oplus, \\
+{\rm constant} & \text{for } r\leq1.5r_\oplus.
+\end{cases}
+\right.
+\label{eq:model4_radius_distribution}
+\end{align}
+The resulting true and inferred rates are shown in Fig.~\ref{fig:model_4}.
+If left uncorrected, binarity makes the gap more shallow, and flattens 
+the step-function edges.
+At present though, binarity seems less important than other effects that would 
+``blur'' the gap in the planet radius dimension. 
+In particular, the valley's period-dependence is almost certainly not flat
+\citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.
+This means that any study assessing its width, depth, etc. only in the planet 
+radius dimension must first account for the blurring that comes from 
+marginalizing over the periods.
 
 \paragraph{Does a detected planet orbit the primary or secondary?}
-Ciardi et al. (2015) studied the effects of stellar multiplicity on the 
-planet radii derived from transit surveys.
+\citet{ciardi_understanding_2015} studied the effects of stellar multiplicity 
+on the planet radii derived from transit surveys.
 They modeled the problem for {\it Kepler}\ objects of interest by matching a 
@@
 Our models show that assuming a detected planet has equal probability of 
-orbiting the primary or secondary leads to an overstatement of
+orbiting the primary or secondary leads to an overestimate of
 binarity's population-level effects.
@@
 \paragraph{On the utility for future occurrence rate measurements}
-{\it TESS}\ is expected to discover over $10^4$ giant planets (Sullivan 
-et al. 2015).
+{\it TESS}\ is expected to discover over $10^4$ giant 
+planets~\citep{sullivan_transiting_2015}.
 Though they will be difficult to distinguish from false positives, one 
@@
 \paragraph{Independent approaches for estimating binarity's effects}
-T. Barclay et al. (in prep) have performed the exercise of taking stars 
-selected by the {\it Kepler}\ team, pairing them with a population of 
+T. Barclay et al.\! (in preparation) have performed the exercise of taking 
+stars selected by the {\it Kepler}\ team, pairing them with a population of 
 secondaries, injecting a realistic distribution of planet radii, 

### 2017-11-15 paper/introduction.tex
add bibtex citations; update model #4 figure

@@
 ``occurrence rates about primaries'', and
-``occurrence rates about secondaries'' (see {\it e.g.,} Wang et al., 
-2015).
+``occurrence rates about secondaries''
+\citep[see][]{wang_occurrence_2015}.
 
@@
 In binaries, the apparent and true radii differ because of diluting flux, 
-and possibly because the planet is assumed to orbit the wrong star ({\it 
-e.g.}, Furlan et al. 2017).
-%Finally, the detection efficiency $p_{\rm det}$ is different for selected 
-%stars in binary systems than it is in single systems.
+and possibly because the planet is assumed to orbit the wrong star
+\citep[\textit{e.g.},][]{furlan_kepler_2017}.
 
@@
 In particular, we mention the ``hot Jupiter rate discrepancy'', the relevance 
-towards measurements of $\eta_\oplus$, and the significance for the dearth of 
-planets recently discovered by Fulton et al. (2017).
+towards measurements of $\eta_\oplus$, and the implications for detailed 
+study of \citet{fulton_california-_2017}'s recently discovered ``valley''.
 We conclude in Sec.~\ref{sec:conclusion}

### 2017-11-15 paper/model_2.tex
add bibtex citations; update model #4 figure

@@
         binary stars, in which the underlying volume-limited distribution is 
-        uniform (quite similar to {\it e.g.}, Raghavan et al. (2010)'s 
-        Fig.~16).
+        uniform (qualitatively similar to {\it 
+        e.g.},~\citet{raghavan_survey_2010}'s Fig.~16).
         The entire bias can be understood analytically 
@@
 For binaries with solar-type primaries\footnote{
-Duchene and Kraus (2013), fitting all the multiple systems of Raghavan et al. 
-(2010)'s Fig 16, find $\beta = 0.28\pm0.05$ for $0.7<M_\star/M_\odot<1.3$.
-Examining only the binary systems of Rhagavan et al 2010, Fig 16, the 
-distribution seems roughly uniform, $\beta \approx 0$, except for a claimed 
-excess of twin binaries with $q\approx 1$, and an obvious lack of $q<0.1$ 
-stellar companions.
+\citet{duchene_stellar_2013}, fitting all the multiple systems of 
+\citet{raghavan_survey_2010}'s Fig 16, find $\beta = 0.28\pm0.05$ for 
+$0.7<M_\star/M_\odot<1.3$.
+Examining only the binary systems of \citeauthor{raghavan_survey_2010}'s Fig 
+16, the distribution seems (by eye) to be roughly uniform, $\beta \approx 0$, 
+except for an excess of twin binaries with $q\approx 1$, and an obvious 
+lack of $q<0.1$ stellar companions.
 }, $\beta$ is probably between 0 and 0.3.
@@
 important to draw binaries from the correctly biased mass-ratio distribution 
-(e.g., Bakos et al 2012, Sullivan et al 2015, Guenther et al 2017).
+\citep[\textit{e.g.},][]{bakos_hatsouth:_2013,sullivan_transiting_2015,
+    gunther_new_2017}.
 

### 2017-11-15 paper/model_3.tex
add bibtex citations; update model #4 figure

@@
 \end{align}
-Following Howard et al. (2012)'s measurement, we take $\delta = -2.92$.
+Following~\citet{howard_planet_2012}'s measurement, we take $\delta = -2.92$.
 Our ``nominal model'' remains the same: the binary fraction is 0.44, 
@@
         $-2.92$ 
-        above $2r_\oplus$, below which it is uniform ({\it e.g.}, Howard et 
-        al., 
-        2012).
+        above $2r_\oplus$, below which it is uniform \citep[similar 
+        to][]{howard_planet_2012}.
     }
@@
 \paragraph{The rate of Earth analogs}
-Our model does not explicitly include the rate density's period-dependence, 
-because stellar binarity does not appreciably bias the period-dependence of 
-occurrence rates measured by transit surveys\footnote{
-    Note that stellar binarity does bias the {\it intrinsic} planet 
-    occurrence as a function of planetary and binary periods. This is expected 
-    from dynamical stability limits in $\geq$3 body systems, and has been 
-    observationally confirmed (theory by Holman \& Wiegert 1999, and others 
-    including Gongjie; confirmation from Wang et al 2014a, 2014b, Kraus et al 
-    2014). 
-    However our statement is that inferred rates as a function of planet     
-    period should be negligibly affected by this, given the geometric bias 
-    against long-period transit detections, and the fact that the period 
-    distribution of solar-type binaries peaks at $\approx 100\,{\rm years}$ 
-    (Raghavan et al 2010, Fig.~13).
-}.
-Instead, it allows us to evaluate the difference in the apparent and true rate 
-as a function of radius 
-(Fig.~\ref{fig:errcases_model_3_log}).
+This model provides an estimate of the apparent and true 
+rates as a function of radius (Fig.~\ref{fig:errcases_model_3_log}).
 At Earth's radius, the result is that the inferred rate is $0.84\times$ the 
@@
 The ratio of the inferred to the true rate, $(\Lambda_{\rm 
-inferred}/\Lambda)_{r=r_\oplus}$ varies substantially, but by at most $50\%$ 
+    inferred}/\Lambda)_{r=r_\oplus}$ varies substantially, but by at most 
+    $50\%$ 
 in the (unrealistic) limiting case that secondaries do not host planets.

### 2017-11-15 paper/simplest_effects.tex
fix typos
add bibtex citations; update model #4 figure

@@
 a constant signal-to-noise floor yields a maximum detectable 
-distance (Pepper et al 2003, Pepper and Gaudi 2005).
+distance~\citep{pepper_using_2003,pepper_searching_2005}.
 The maximum distance out to which our binarity-ignoring astronomers 
@@
 The binary fraction in a volume limited sample is ``{\rm BF}''.
-For instance, Raghavan et al., (2010) found a multiplicity fraction\footnote{
+For instance, \citet{raghavan_survey_2010} found a multiplicity 
+fraction\footnote{
     The binary fraction is the fraction of systems in a volume-limited sample 
@@
 \end{equation}
-This evaluates to 0.95 if ${\rm BF}=0.1$, and 0.99 if ${\rm BF}=0.05$.
+This evaluates to 0.94 if ${\rm BF}=0.1$, and 0.98 if ${\rm BF}=0.05$.
 While it is hard to justify the assumption that secondaries are planet-less, 

### 2017-11-17 paper/discussion.tex
add footnote addressing planet radius scaling Q

@@
 plane~\citep{petigura_california-kepler_2017,johnson_california-kepler_2017}.
-The existence of the gap has been independently corroborated using 
-asteroseismically-determined stellar 
+The existence of the gap has been independently corroborated from a sample of 
+KOIs with asteroseismically-determined stellar 
 parameters~\citep{van_eylen_asteroseismic_2017}.
 Precise measurement of the gap's features, in particular its width, 
-depth, and shape, requires accurate occurrence rates.
+depth, and shape, will require more accurate occurrence rates.
 To illustrate binarity's role in the issue, we make identical assumptions as 
@@
 The resulting true and inferred rates are shown in Fig.~\ref{fig:model_4}.
-If left uncorrected, binarity makes the gap more shallow, and flattens 
+If left uncorrected, binarity makes the gap appear more shallow, and flattens 
 the step-function edges.

### 2017-11-17 paper/model_3.tex
add footnote addressing planet radius scaling Q

@@
 For this model, we forgo analytic development and simply run our Monte Carlo 
-program.
+program\footnote{
+One might worry that our Monte Carlo program does not increase the number of 
+selected stars as the square of the planet radius (Eq.~\ref{eq:snr_true}).
+We can omit this dependence because in our model $N_1/N_0$ is independent of 
+desired planet radius, and all other terms in the rate densities ({\it e.g.}, 
+Eqs.~\ref{eq:model2_rate_density} and~\ref{eq:model2_Gamma_a}) are independent 
+of the number of selected stars.
+}.
 The resulting occurrence rates are shown in 

### 2017-11-20 paper/discussion.tex
make Guo+2017 reference more precise

@@
 see Table~\ref{tab:hj_rates}).
-The discrepancy has weak statistical significance ($<3\sigma$).
-One reason to expect a difference is that the corresponding stellar 
+Though the discrepancy has weak statistical significance ($<3\sigma$),
+one reason to expect a difference is that the corresponding stellar 
 populations have distinct metallicities.
@@
 planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005}.
-The {\it Kepler}\ sample specifically has been measured to be more metal poor 
-than the local neighborhood, with a mean metallicity of $[{\rm M/H}]_{\rm 
-    mean}\approx -0.05$~\citep{dong_metallicities_2014,guo_metallicity_2017}.
-Studying the problem in detail, \citeauthor{guo_metallicity_2017}\! recently 
-argued that the metallicity difference could account for a $\approx 20\%$ 
+Investigating the discrepancy from the metallicty 
+angle,~\citet{guo_metallicity_2017} measured the
+{\it Kepler} field's mean metallicity to be $[{\rm M/H}]_{\rm Kepler}= 
+-0.045\pm0.009$, which is lower than the California Planet Search's mean of 
+$[{\rm M/H}]_{\rm CPS}= -0.005\pm0.006$.
+The former value agrees with that measured by \citet{dong_metallicities_2014}.
+Based on their measurements, \citeauthor{guo_metallicity_2017}\! 
+then argued that the metallicity difference could account for a $\approx 20\%$ 
 relative difference in the measured rates between the CKS and {\it Kepler}\ 

### 2017-11-27 sandbox/note_km.tex
adding KM note

\documentclass[12pt,modern]{aastex61}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{comment}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
%\received{July 1, 2016}
%\revised{September 27, 2016}
%\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{AAS journals.}

\shortauthors{Bouma et al.}
\shorttitle{Binarity and Occurrence Rates}

\begin{document}

\title{ The effects of binarity on planet occurrence rates measured by transit 
surveys}
%
\correspondingauthor{L. Bouma}
\email{luke@astro.princeton.edu}
%
\author{L. G. Bouma}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{J. N. Winn}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{K. Masuda}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
%
%
\begin{abstract}
%
This derives the equations of the paper.

%
\end{abstract}
%
\keywords{
    methods: data analysis ---
    planets and satellites: detection ---
    surveys}
%
%

\newcommand{\pt}{\theta}
\newcommand{\pa}{\theta_{\rm a}}
\newcommand{\pn}{\theta_0}

\newcommand{\pp}{\mathcal{P}}
\newcommand{\ps}{\mathcal{S}}
\renewcommand{\a}{_{\rm a}}
\newcommand{\s}{_{\rm s}}

\section{Preliminaries}

\subsection{Searchable Distance}

We can detect a signal if 
\begin{equation}
	{\text{signal}\over\text{noise}}\sim
    {\delta_{\rm obs}\over(L/d^2)^{-1/2}},
	\quad \delta_{\rm obs}:\text{observed depth}
\end{equation}
is above some threshold (it would probably make more sense to include the 
duration information, but that would anyway be a trivial extension and so we 
omit it here for brevity). Thus, the maximum searchable distance scales as
\begin{equation}
	d(\delta_{\rm obs}, L_{\rm sys}) \propto \delta_{\rm obs} \cdot L_{\rm 
	sys}^{1/2}.
\end{equation}
We assume that the signal is detected if and only if a given star is searchable.

Using this distance, the number of searchable stars $N\s$ is given by
\begin{equation}
	N\s(\delta_{\rm obs}, L_{\rm sys})=n_0 \delta_{\rm obs}^3 L_{\rm 
	sys}^{3/2},
\end{equation}
where $n_0$ is a normalization constant proportional to the volume density of the systems with a certain type of interest (e.g. single star, binary).
We neglect the dependence of the normalization $n_0$ on the stellar type.

\subsection{Relation between Apparent and Actual Stellar Properties}

We assume that the apparent property of an unresolved binary is the same as that of the primary:
\begin{equation}
	M\a=M_1, \quad R\a=R_1, ...
\end{equation}
We also assume the stellar radius and luminosity is uniquely related to the stellar mass.

Given these assumptions, the total luminosity of the system is
%This assumption, along with a given $L$--$M$ relation, leads to
\begin{equation}
	L_{\rm sys}=L_1+L_2=L(M\a)+L(qM\a),
\end{equation}
where $q=M_2/M_1$. Note that $L_{\rm sys}$ is the true value (because $M\a$ is 
the true primary mass), while the system luminosity estimated by an observer 
would be $L(M\a)$, which based on the apparent stellar parameters (unless the 
observer has a priori knowledge on the distance to a given system).

\subsection{Apparent Number of Searchable Stars}

Given the apparent signal $\delta_{\rm obs}$ and stellar mass $M\a$, the 
maximum searchable distance for singles and binaries are proportional to 
$\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm obs}\cdot 
[L(M\a)+L(qM\a)]^{1/2}$. Thus, 
the apparent number of searchable stars (i.e. points in the sky), which will 
be selected by an ignorant observer, is 
\begin{align}
	\notag
	N_{\rm s,a}(\delta_{\rm obs}, M\a)
	%&=n_{\rm s,0}\delta_{\rm obs}^3L(M\a)^{3/2} + n_{\rm b,0}\delta_{\rm 
	%obs}^3 \cdot [L(M\a)+L(qM\a)]^{3/2}\\
	&=n_{\rm s}\delta_{\rm obs}^3 L(M\a)^{3/2}\left\{1+\int \mathrm{d}q\,f(q) 
	{\mathrm{BF}\over{1-\mathrm{BF}}}\left[1+{L(qM\a) \over 
	L(M\a)}\right]^{3/2}\right\}\\
	&\equiv N\s^0(\delta_{\rm obs}, L(M\a)) \left[1+\mu(\mathrm{BF}, 
	M\a)\right],
\end{align}
where $N\s^0$ is the number of searchable singles (this agrees with the actual value), $f(q)$ is the binary mass ratio distribution, and $\mathrm{BF}=n_{\rm b}/(n_{\rm s}+n_{\rm b})$ is the binary fraction in a volume-limited sample.

\section{Apparent Occurrence Rate --- General Formula}

A group of astronomers wants to measure the mean number of planets of a 
certain type per star of a certain type.
They simply observe a set points on the sky selected in a magnitude-limited way (or whatever, actually?) and detect $n$ planets of a desired class. Then they compute the occurrence as
\begin{equation}
\Lambda(\pp, \ps) = \frac{n(\pp, \ps)}{N_{\rm s}(\pp, \ps)} \times \frac{1}{p_{\rm tra}(\pp, \ps)}.
\end{equation}
Here $N_{\rm s}$ is the number of stars (among those initially selected) around which the planets of interest are searchable; $p_{\rm tra}$ is the transit probability.

Let's see how the binary modifies this. The occurrence is computed based on the apparent planetary/stellar parameters $\pp\a$, $\ps\a$:
\begin{equation}
\Lambda\a(\pp\a, \ps\a) = \frac{n(\pp\a, \ps\a)}{N_{\rm s,a}(\pp\a, \ps\a)} \times \frac{1}{p_{\rm tra}(\pp\a, \ps\a)}.
\end{equation}
Here, $N_{\rm s}$ and $p_{\rm tra}$ are computed for the apparent parameter $\pp\a$ and $\ps\a$. In the presence of dilution, planets with $(\pp\a, \ps\a)$ are associated with systems of many different planetary and stellar properties, so $n_{\rm a}$ is given by the convolution of the true occurrence, $\Lambda(\pp, \ps)$, and number of searchable stars that give $(\pp\a, \ps\a)$ when the true system actually has $(\pp, \ps)$, $\mathcal{N}(\pp\a, \ps\a; \pp, \ps)$:
\begin{equation}
	n(\pp\a, \ps\a)=\sum_i n^i(\pp\a, \ps\a)
	=\sum_i \int \mathrm{d}\pp\mathrm{d}\ps\,
	%\mathcal{P}_{\rm tra}(\pp\a, \ps\a; \pt)
	\mathcal{N}_{\rm s}^i(\pp\a,\ps\a; \pp, \ps)
	\cdot\Lambda^i(\pp, \ps)\cdot p_{\rm tra}(\pp, \ps),
\end{equation}
where $i$ specifies the type of true host stars (0: single, 1: primary, 2: secondary).
%where $b_i=1-\mathrm{BF}$ for $i=0$ (singles) and $b_i=\mathrm{BF}$ for $i=1,2$. In fact, the $b_i$ factor appears when we count the number of searchable systems $\mathcal{N}$; what matters here is the number density of binaries and singles, so $\mathrm{BF}$ is the binary fraction in a volume-limited sample. Here we factor it out just to simplify(?) the notation.

So the problem essentially reduces to the evaluation of
\begin{equation}
	\mathcal{N}_{\rm s}(\pp\a,\ps\a; \pp, \ps)
\end{equation}
for planets around single stars, primaries in binaries, and secondaries in binaries.

\section{Evaluation of $\mathcal{N}$}

Let us explicitly write $\pp=r$ and $\ps=M$; $R$ and $L$ are uniquely determined from the assumed mass--radius--luminosity relation. We neglect the $P$ dependence.

\subsection{Single Stars}

For $i=0$, 
\begin{equation}
	\mathcal{N}_{\rm s}^0(\pp\a,\ps\a; \pp, \ps)
	=\delta(\pp\a-\pp)\delta(\ps\a-\ps) N\s^0(\pp,\ps),
	%=\delta(r'-r)\delta(M'-M)\delta(R'-R) N\s((r/R)^2, L(M))
\end{equation}
so
\begin{equation}
	n^0(\pp\a, \ps\a)=N\s^0(\pp\a,\ps\a)\cdot \Lambda^0(\pp\a, \ps\a) \cdot p_{\rm tra}(\pp\a, \ps\a).
\end{equation}
If all the stars are singles, this yields
\begin{equation}
	\Lambda\a(\pp\a, \ps\a)=\Lambda^0(\pp\a, \ps\a),
\end{equation}
as expected (now $\mu=0$ and $N_{\rm s,a}=N\s^0$) --- the true occurrence is recovered.

\subsection{Primaries in Binaries}

Since we assume $\ps\a=\ps_1$,
\begin{equation}
	\mathcal{N}_{\rm s}^1(r', M'; r, M) \propto \delta(M'-M).
	%=\mathcal{N}_{\rm s}^1(r', M', R'; r, M', R').
\end{equation}
In this case, $\mathcal{N}_{\rm s}^1$ is non-zero only at $r'=R'\sqrt{D'}$, where
\begin{equation}
	D' %= \delta \times {L_1 \over L_{\rm sys}} 
	= \left[{r\over R(M')}\right]^2\times {L(M') \over L_{\rm sys}(M', q)}
\end{equation}
and the normalization is given by the number of searchable binaries (for signal $D'$):
\begin{equation}
	%N_{\rm s}(D', L_{\rm sys})
	n_{\rm b}D'^3 L_{\rm sys}^{3/2}=N_{\rm s}^0(D', L(M'))\cdot\mu(\mathrm{BF},M').
	%=N_{\rm s}(D', L(M')) \times \left[L_{\rm sys}(M', q) \over L(M') 
	%\right]^{3/2}.
\end{equation}
Thus,
\begin{equation}
	\mathcal{N}_{\rm s}^1(r', M'; r, M)
	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r', M'; r, M; q),
\end{equation}
where $f(q)$ is the binary mass ratio distribution and
\begin{align}
	\notag
	\mathcal{N}_{{\rm s}, q}^1(r', M'; r, M; q)
	%&=N_{\rm s}(D', L(M')) \left[L_{\rm sys}(M', q) \over L(M') 
	%\right]^{3/2}\\
	&=N_{\rm s}^0(D', L(M'))\cdot\mu(\mathrm{BF},M')\\
	&\times\delta \left(r'-r\sqrt{{L(M') \over L_{\rm sys}(M', 
	q)}}\right)\delta(M'-M).
\end{align}

\subsection{Secondaries in Binaries}

In this case, $M=qM_1=qM'$, so
\begin{equation}
	\mathcal{N}_{\rm s}^2(r', M'; r, M)
	\propto \delta\left(M'-{M\over q}\right).
	%=\mathcal{N}_{\rm s}^2(r', M', R'; r, qM', R(qM')).
\end{equation}
Again $\mathcal{N}_{\rm s}^2$ is non-zero only at $r'=R'\sqrt{D'}$, but this time
\begin{equation}
	D' = \left[{r\over R(qM')}\right]^2 \times {L(qM') 
	\over L_{\rm sys}(M', q)}.
\end{equation}
The normalization remains the same as the previous case (we are counting the searchable stars at a given observed depth $D'$, total luminosity of the binary is the same).
Thus,
\begin{equation}
	\mathcal{N}_{\rm s}^2(r', M'; r, M)
	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r', M'; r, M; q),
\end{equation}
where
\begin{align}
	\notag
	\mathcal{N}_{\rm s}^2(r', M'; r, M; q)
	%&=N_{\rm s}(D', L(M')) \left[L_{\rm sys}(M', q) \over L(M') 
	%\right]^{3/2}\\
	&=N_{\rm s}^0(D', L(M'))\cdot\mu(\mathrm{BF},M')\\
	&\times \delta \left(r'-r\sqrt{ \left[{R(M')\over R(qM')}\right]^2 {L(qM') 
	\over L_{\rm sys}(M', q)} }\right)\delta\left(M'-{M\over q}\right).
\end{align}

\section{Result}

\subsection{Marginalization over the True Properties}

Let's integrate out $\pp$ and $\ps$.

\begin{align}
	n^0(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^0(r\a, M\a; r, M)
	\cdot\Lambda^0(r, M) \cdot p_{\rm tra}(M)\\
	&=\int\mathrm{d}r\mathrm{d}M\, N\s^0(\delta_{\rm obs}, 
	L(M\a))\delta(r\a-r)\delta(M\a-M)
	\cdot\Lambda^0(r, M) \cdot p_{\rm tra}(M)\\
	&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot\Lambda^0(r\a, M\a) \cdot p_{\rm 
	tra}(M\a).
\end{align}

\begin{align}
	n^1(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^1(r\a, M\a; r, M)
	\cdot\Lambda^1(r, M) \cdot p_{\rm tra}(M)\\
	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, q}^1(r\a, M\a; r, M; q)\cdot\Lambda^1(r, M) \cdot p_{\rm tra}(M)\\
	&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
	\mu(\mathrm{BF}, M\a) \int {\mathrm{d}q \over \alpha}\,f(q)\,\Lambda^1(r^*, M\a),
	%\left[L_{\rm sys}(M', q) \over L(M') \right]^{3/2},
\end{align}
where $r^*=r\a/\alpha$ and 
\begin{equation}
	\alpha(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}.
\end{equation}

Finally,
\begin{align}
	n^2(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^2(r\a, M\a; r, M)
	\cdot\Lambda^2(r, M) \cdot p_{\rm tra}(M)\\
	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, q}^2(r\a, M\a; r, M; q)\cdot\Lambda^2(r, M) \cdot p_{\rm tra}(M)\\
	&=%N_{\rm s}(D', L(M')
	N\s^0(\delta_{\rm obs}, L(M\a))\cdot\mu(\mathrm{BF}, M\a)
	\int {q \mathrm{d}q \over \beta}\,f(q)\,\Lambda^2(r^{**}, qM\a)\,p_{\rm tra}(qM\a),
	%\left[L_{\rm sys}(M', q) \over L(M') \right]^{3/2},
\end{align}
where $r^{**}=r\a/\beta$ and 
\begin{equation}
	\beta(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm sys}(M\a, q)} }.
\end{equation}

\subsection{Final Formula}

Note again that the denominators of $\Lambda\a$ are the same for singles, 
primaries, and secondaries: $N_{\rm s,a}(\delta_{\rm obs}, M\a)$ and $p_{\rm 
tra}(M\a)$. This is because we are calculating the occurrence at the same 
apparent planet/star properties, and the observer can never distinguish 
binaries from singles (and adopt the primary properties for binaries).
Using the results above, the apparent occurrence is thus given by
\begin{align}
	&\Lambda\a(r\a, M\a)={1\over 1+\mu(\mathrm{BF}, M\a)}\times\\
	%&=(1-\mathrm{BF})\cdot
	&\left\{ \Lambda^0(r\a, M\a)+ \mu(\mathrm{BF}, M\a) \left[
	\int {\mathrm{d}q \over A}\,f(q)\,\Lambda^1\left({r\a\over A}, M\a\right)\,
	+\int {q \mathrm{d}q \over B}\,f(q)\,\Lambda^2\left({r\a\over B}, qM\a\right)\,
	{R(qM\a) \over R(M\a)}
	q^{-1/3} \right]
	\right\},
	 %\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2}
	 %\\
	%&+\mathrm{BF}\cdot
	%\int {q \mathrm{d}q \over B}\,f(q)\,\Lambda^2\left({r\a\over B}, qM\a\right)\,
	%{R(qM\a) \over R(M\a)}q^{-1/3}
	%\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2},
\end{align}
where
\begin{equation}
	A=\left[1+{L(qM\a) \over L(M\a)}\right]^{-1/2}, \quad
	B={R(M\a)\over R(qM\a)}\left[1+{L(M\a) \over L(qM\a)}\right]^{-1/2}.
\end{equation}

\section{Examples}

\subsection{Twin Binary}

We have $f(q)=\delta(q-1)$. Thus
\begin{align}
	\Lambda\a(r\a, M\a)
	={1\over 1+\mu(\mathrm{BF}, M\a)}
	\left\{\Lambda^0(r\a, M\a)
	%+\mathrm{BF}\cdot 2^{3/2}\sqrt{2}\left[\Lambda^1(\sqrt{2}\,r\a, M\a)+\Lambda^2(\sqrt{2}\,r\a, M\a)\right].
	+\mu(\mathrm{BF}, M\a)\cdot\sqrt{2}\left[\Lambda^1(\sqrt{2}\,r\a, M\a)+\Lambda^2(\sqrt{2}\,r\a, M\a)\right]
	\right\},
\end{align}
where
\begin{equation}
	\mu(\mathrm{BF}, M\a)=\int \mathrm{d}q\,f(q) {\mathrm{BF}\over{1-\mathrm{BF}}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2}
	=2^{3/2}\cdot{\mathrm{BF}\over{1-\mathrm{BF}}}.
\end{equation}

\subsubsection{Same Planets}

If $\Lambda^i(r, M)=Z^i\cdot\delta(r-r_0)$ (all the planets have the same radius),
\begin{align}
	\Lambda\a(r\a, M\a)
	%=\Lambda_0\left[(1-\mathrm{BF})\cdot\delta(r\a-r_0)
	%+2\mathrm{BF}\cdot 2^{3/2}\cdot\delta\left(r\a-{r_0\over\sqrt{2}}\right)\right].
	={1 \over 1+\mu(\mathrm{BF})}
	\left[Z^0 \cdot \delta(r\a-r_0)+(Z^1+Z^2)\cdot \mu(\mathrm{BF})\cdot \delta\left(r\a-{r_0\over\sqrt{2}}\right)\right].
\end{align}
This reproduces Eq.(9) of the draft, after correcting for the smaller number of apparently searchable stars for the diluted planets (factor of $(1/2)^3$). In the limit of $\mathrm{BF}\to1$ ($\mu\to\infty$), the above formula yields $\Lambda\a=(Z^1+Z^2)\,\delta(r\a-{r_0/\sqrt{2}})$.

\subsection{Power Law World}

If we assume 
\begin{equation}
	L(M) \sim M^\alpha \sim R^\alpha,
\end{equation}
we find
\begin{align}
	A=(1+q^\alpha)^{-1/2}, \quad 
	B=q^{-1}(1+q^{-\alpha})^{-1/2},
\end{align}
so
\begin{align}
	\Lambda\a(r\a, M\a)=...
	%&=(1-\mathrm{BF})\cdot\Lambda^0(r\a, M\a)\\
	%&+\mathrm{BF}\cdot 
	%\int \mathrm{d}q\,f(q)
	%(1+q^\alpha)^2 \cdot \Lambda^1\left( r\a\sqrt{1+q^\alpha}, M\a\right)\\
	%&+\mathrm{BF}\cdot
	%\int {\mathrm{d}q}\,f(q)q^{8/3}
	%\sqrt{1+q^{-\alpha}}(1+q^\alpha)^{3/2}
	%\cdot\Lambda^2\left(r\a q\sqrt{1+q^{-\alpha}}, qM\a\right).
\end{align}
We may further assume
\begin{equation}
	f(q)\sim q^\beta, \quad \Lambda(r) \sim r^\gamma
\end{equation}
and keep calculating...

%\acknowledgements
%It was a pleasure to share discussions with Kento Masuda, who pointed us in 
%this direction, and helped clarify that something like this was worth 
%studying.
%It was a pleasure discussing this work with F. Dai and T. Barclay.

\newpage
\bibliographystyle{yahapj}                            
\bibliography{bibliography}

\end{document}

### 2017-11-27 sandbox/note_km.tex
update KM note

@@
 
-Using this distance, the number of searchable stars $N\s$ is given by
+Assuming that stars are uniformly distributed in space, the number of 
+searchable stars $N\s$ is then proportional to
 \begin{equation}
-	N\s(\delta_{\rm obs}, L_{\rm sys})=n_0 \delta_{\rm obs}^3 L_{\rm 
+	N\s(\delta_{\rm obs}, L_{\rm sys}) \propto n \delta_{\rm obs}^3 L_{\rm 
 	sys}^{3/2},
 \end{equation}
-where $n_0$ is a normalization constant proportional to the volume density of the systems with a certain type of interest (e.g. single star, binary).
-We neglect the dependence of the normalization $n_0$ on the stellar type.
+where $n$ is the volume density of {\it e.g.}, single star, or binary systems.
+We neglect the dependence of $n$ on stellar type.
 
@@
 
-We assume that the apparent property of an unresolved binary is the same as that of the primary:
+We assume that the apparent properties of an unresolved binary are the same as 
+those of the primary:
 \begin{equation}
@@
 \end{equation}
-We also assume the stellar radius and luminosity is uniquely related to the stellar mass.
+We also assume the stellar radius and luminosity is uniquely related to the 
+stellar mass.
 
-Given these assumptions, the total luminosity of the system is
-%This assumption, along with a given $L$--$M$ relation, leads to
+Given these assumptions, the total luminosity of a system is
 \begin{equation}
@@
 where $q=M_2/M_1$. Note that $L_{\rm sys}$ is the true value (because $M\a$ is 
-the true primary mass), while the system luminosity estimated by an observer 
-would be $L(M\a)$, which based on the apparent stellar parameters (unless the 
-observer has a priori knowledge on the distance to a given system).
+the true primary mass), while an observer would estimate a system luminosity 
+of $L(M\a)$, based on the apparent stellar parameters. We presume the 
+observer has no a priori knowledge of the distance to a given system~--~they 
+only measure a flux, assume a stellar mass $M_a$, and use relations for 
+$L(M_a)$ and $R(M_a)$ to estimate system properties.
 
@@
 the apparent number of searchable stars (i.e. points in the sky), which will 
-be selected by an ignorant observer, is 
+be selected by an ignorant observer, can be written 
 \begin{align}
@@
 	%obs}^3 \cdot [L(M\a)+L(qM\a)]^{3/2}\\
-	&=n_{\rm s}\delta_{\rm obs}^3 L(M\a)^{3/2}\left\{1+\int \mathrm{d}q\,f(q) 
-	{\mathrm{BF}\over{1-\mathrm{BF}}}\left[1+{L(qM\a) \over 
-	L(M\a)}\right]^{3/2}\right\}\\
+	&\propto n_{\rm s}\delta_{\rm obs}^3 L(M\a)^{3/2}\left[ 1+\int 
+	\mathrm{d}q\,f(q) 
+	{\mathrm{BF}\over{1-\mathrm{BF}}}\left(1+{L(qM\a) \over 
+	L(M\a)}\right)^{3/2}\right]\\
+	N_{\rm s,a}(\delta_{\rm obs}, M\a)
     &\equiv N\s^0(\delta_{\rm obs}, L(M\a)) \left[1+\mu(\mathrm{BF}, 
@@
 \end{align}
-where $N\s^0$ is the number of searchable singles (this agrees with the actual value), $f(q)$ is the binary mass ratio distribution, and $\mathrm{BF}=n_{\rm b}/(n_{\rm s}+n_{\rm b})$ is the binary fraction in a volume-limited sample.
+where $N\s^0$ is the number of searchable singles (this agrees with the actual 
+value), $f(q)$ is the binary mass ratio distribution, $\mathrm{BF}=n_{\rm 
+b}/(n_{\rm s}+n_{\rm b})$ is the binary fraction in a volume-limited sample, 
+and $n_s$ is the number density of singles in a volume-limited sample.
+Proportionality constants subsumed into the definition of $N_s^0$ include 
+{\it e.g.}, the telescope area and the survey duration.
 
@@
 certain type per star of a certain type.
-They simply observe a set points on the sky selected in a magnitude-limited way (or whatever, actually?) and detect $n$ planets of a desired class. Then they compute the occurrence as
+They observe a set points on the sky and detect $N_{\rm det}$ planets that 
+appear to be of the desired class.
+They then choose the stars (among those initially selected) around which the 
+planets of interest appeared to be searchable.
+Finally they compute the apparent occurrence,
 \begin{equation}
-\Lambda(\pp, \ps) = \frac{n(\pp, \ps)}{N_{\rm s}(\pp, \ps)} \times \frac{1}{p_{\rm tra}(\pp, \ps)}.
+\Lambda\a(\pp\a, \ps\a) = \frac{N_{\rm det}(\pp\a, \ps\a)}{N_{\rm s,a}(\pp\a, 
+    \ps\a)} \times \frac{1}{p_{\rm tra}(\pp\a, \ps\a)}.
 \end{equation}
-Here $N_{\rm s}$ is the number of stars (among those initially selected) around which the planets of interest are searchable; $p_{\rm tra}$ is the transit probability.
+where $\pp\a$, $\ps\a$ are the apparent planetary/stellar parameters.
 
-Let's see how the binary modifies this. The occurrence is computed based on the apparent planetary/stellar parameters $\pp\a$, $\ps\a$:
+In the presence of dilution, planets with $(\pp\a, \ps\a)$ are associated with 
+systems of many different planetary and stellar properties, so $N_{\rm 
+det}(\pp\a, \ps\a)$ is 
+given by the convolution of the true occurrence, $\Lambda(\pp, \ps)$, and 
+number of searchable stars that give $(\pp\a, \ps\a)$ when the true system 
+actually has $(\pp, \ps)$, $\mathcal{N}(\pp\a, \ps\a; \pp, \ps)$:
 \begin{equation}
-\Lambda\a(\pp\a, \ps\a) = \frac{n(\pp\a, \ps\a)}{N_{\rm s,a}(\pp\a, \ps\a)} \times \frac{1}{p_{\rm tra}(\pp\a, \ps\a)}.
-\end{equation}
-Here, $N_{\rm s}$ and $p_{\rm tra}$ are computed for the apparent parameter $\pp\a$ and $\ps\a$.
-In the presence of dilution, planets with $(\pp\a, \ps\a)$ are associated with systems of many different planetary and stellar properties, so $n_{\rm a}$ is given by the convolution of the true occurrence, $\Lambda(\pp, \ps)$, and number of searchable stars that give $(\pp\a, \ps\a)$ when the true system actually has $(\pp, \ps)$, $\mathcal{N}(\pp\a, \ps\a; \pp, \ps)$:
-\begin{equation}
-	n(\pp\a, \ps\a)=\sum_i n^i(\pp\a, \ps\a)
+	N_{\rm det}(\pp\a, \ps\a)=\sum_i N_{\rm det}^i(\pp\a, \ps\a)
 	=\sum_i \int \mathrm{d}\pp\mathrm{d}\ps\,
@@
 \end{equation}
-where $i$ specifies the type of true host stars (0: single, 1: primary, 2: secondary).
-%where $b_i=1-\mathrm{BF}$ for $i=0$ (singles) and $b_i=\mathrm{BF}$ for $i=1,2$.
-In fact, the $b_i$ factor appears when we count the number of searchable systems $\mathcal{N}$; what matters here is the number density of binaries and singles, so $\mathrm{BF}$ is the binary fraction in a volume-limited sample.
-Here we factor it out just to simplify(?) the notation.
+where $i$ specifies the type of true host stars (0: single, 1: primary, 2: 
+secondary).
 
-So the problem essentially reduces to the evaluation of
+So the problem reduces to the evaluation of
 \begin{equation}
-	\mathcal{N}_{\rm s}(\pp\a,\ps\a; \pp, \ps)
+	\mathcal{N}_{\rm s}^i(\pp\a,\ps\a; \pp, \ps)
 \end{equation}
@@
 
-\section{Evaluation of $\mathcal{N}$}
+\section{Evaluation of 
+    $\mathcal{N}_{\rm \MakeLowercase{s}}^{\MakeLowercase{i}}$}
 
-Let us explicitly write $\pp=r$ and $\ps=M$; $R$ and $L$ are uniquely determined from the assumed mass--radius--luminosity relation. We neglect the $P$ dependence.
+Let us explicitly write $\pp=r$ and $\ps=M$; $R$ and $L$ are uniquely 
+determined from the assumed mass--radius--luminosity relation. We neglect the 
+dependence on planetary orbital period.
+We proceed by evaluating
+\begin{align}
+N_{\rm det}(r_a, M_a) &=
+\sum_i N_{\rm det}^i(r_a, M_a) \\
+N_{\rm det}(r_a, M_a)
+&=
+\sum_i \int \mathrm{d}r \mathrm{d}M \,
+\mathcal{N}_{\rm s}^i(r_a,M_a; r,M)
+\cdot\Lambda^i(r,M) \cdot p_{\rm tra}(r,M),
+\end{align}
+term by term.
 
@@
 \begin{equation}
-	\mathcal{N}_{\rm s}^0(\pp\a,\ps\a; \pp, \ps)
-	=\delta(\pp\a-\pp)\delta(\ps\a-\ps) N\s^0(\pp,\ps),
-	%=\delta(r'-r)\delta(M'-M)\delta(R'-R) N\s((r/R)^2, L(M))
+	\mathcal{N}_{\rm s}^0(r\a,M\a; r,M)
+	=\delta(r\a-r)\delta(M\a-M) N\s^0(r,M),
 \end{equation}
@@
 \begin{equation}
-	n^0(\pp\a, \ps\a)=N\s^0(\pp\a,\ps\a)\cdot \Lambda^0(\pp\a, \ps\a) \cdot p_{\rm tra}(\pp\a, \ps\a).
+	N_{\rm det}^0(r\a, M\a)=N\s^0(r\a,M\a)\cdot \Lambda^0(r\a, 
+	M\a) \cdot p_{\rm tra}(r\a, M\a).
 \end{equation}
@@
 \begin{equation}
-	\Lambda\a(\pp\a, \ps\a)=\Lambda^0(\pp\a, \ps\a),
+	\Lambda\a(r\a, M\a)=\Lambda^0(r\a, M\a),
 \end{equation}
-as expected (now $\mu=0$ and $N_{\rm s,a}=N\s^0$) --- the true occurrence is recovered.
+as expected (now $\mu=0$ and $N_{\rm s,a}=N\s^0$) --- the true occurrence is 
+recovered.
+
+%TODO: PROCEED FROM HERE
 
@@
 \begin{equation}
-	\mathcal{N}_{\rm s}^1(r', M'; r, M) \propto \delta(M'-M).
-	%=\mathcal{N}_{\rm s}^1(r', M', R'; r, M', R').
+	\mathcal{N}_{\rm s}^1(r_a, M_a; r, M) \propto \delta(M_a-M).
 \end{equation}
-In this case, $\mathcal{N}_{\rm s}^1$ is non-zero only at $r'=R'\sqrt{D'}$, where
+In this case, $\mathcal{N}_{\rm s}^1$ is non-zero only at 
+$r_a=R_a\sqrt{\delta_{\rm obs}}$, 
+and the observed depth is
 \begin{equation}
-	D' %= \delta \times {L_1 \over L_{\rm sys}} 
-	= \left[{r\over R(M')}\right]^2\times {L(M') \over L_{\rm sys}(M', q)}
+	\delta_{\rm obs}
+	= \left[{r\over R(M_a)}\right]^2\times {L(M_a) \over L_{\rm sys}(M_a, q)}.
+   \label{eq:delta_obs_primaries} 
 \end{equation}
-and the normalization is given by the number of searchable binaries (for signal $D'$):
+The normalization of $\mathcal{N}_{\rm s}^1$ is given by the number of 
+binaries that are searchable for a signal $\delta_{\rm obs}$:
 \begin{equation}
-	%N_{\rm s}(D', L_{\rm sys})
-	n_{\rm b}D'^3 L_{\rm sys}^{3/2}=N_{\rm s}^0(D', L(M'))\cdot\mu(\mathrm{BF},M').
-	%=N_{\rm s}(D', L(M')) \times \left[L_{\rm sys}(M', q) \over L(M') 
-	%\right]^{3/2}.
+	N_{\rm s}^0(\delta_{\rm obs}, 
+	L(M_a))\cdot\mu(\mathrm{BF},M_a).
 \end{equation}
-Thus,
+Thus, the number of primaries with apparent parameters $(r_a,M_a)$ given the 
+true parameters $(r,M)$ is
 \begin{equation}
-	\mathcal{N}_{\rm s}^1(r', M'; r, M)
-	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r', M'; r, M; q),
+	\mathcal{N}_{\rm s}^1(r_a, M_a; r, M)
+	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r_a, M_a; r, M; q),
 \end{equation}
@@
 	\notag
-	\mathcal{N}_{{\rm s}, q}^1(r', M'; r, M; q)
-	%&=N_{\rm s}(D', L(M')) \left[L_{\rm sys}(M', q) \over L(M') 
-	%\right]^{3/2}\\
-	&=N_{\rm s}^0(D', L(M'))\cdot\mu(\mathrm{BF},M')\\
-	&\times\delta \left(r'-r\sqrt{{L(M') \over L_{\rm sys}(M', 
-	q)}}\right)\delta(M'-M).
+	\mathcal{N}_{{\rm s}, q}^1(r_a, M_a; r, M; q)
+	&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))\cdot\mu(\mathrm{BF},M_a)\\
+	&\times\delta \left(r_a-r\sqrt{{L(M_a) \over L_{\rm sys}(M_a, 
+	q)}}\right)\delta(M_a-M).
+\label{eq:N_s_1}
 \end{align}
+Note that while the observed depth is a function of the true parameters 
+(Eq.~\ref{eq:delta_obs_primaries}), since we are counting 
+detected planets of a given {\it apparent} size, we will not need to worry 
+about this dependence.
 
@@
 
-In this case, $M=qM_1=qM'$, so
+In this case, $M=qM_1=qM_a$, so
 \begin{equation}
-	\mathcal{N}_{\rm s}^2(r', M'; r, M)
-	\propto \delta\left(M'-{M\over q}\right).
-	%=\mathcal{N}_{\rm s}^2(r', M', R'; r, qM', R(qM')).
+	\mathcal{N}_{\rm s}^2(r_a, M_a; r, M)
+	\propto \delta\left(M_a-{M\over q}\right).
+	%=\mathcal{N}_{\rm s}^2(r_a, M_a, R_a; r, qM_a, R(qM_a)).
 \end{equation}
-Again $\mathcal{N}_{\rm s}^2$ is non-zero only at $r'=R'\sqrt{D'}$, but this time
+Again $\mathcal{N}_{\rm s}^2$ is non-zero only at $r_a=R_a\sqrt{\delta_{\rm 
+obs}}$, but this 
+time
 \begin{equation}
-	D' = \left[{r\over R(qM')}\right]^2 \times {L(qM') 
-	\over L_{\rm sys}(M', q)}.
+	\delta_{\rm obs} = \left[{r\over R(qM_a)}\right]^2 \times {L(qM_a) 
+	\over L_{\rm sys}(M_a, q)}.
 \end{equation}
-The normalization remains the same as the previous case (we are counting the searchable stars at a given observed depth $D'$, total luminosity of the binary is the same).
+The normalization remains the same as the previous case (we are counting the 
+searchable stars at a given observed depth $\delta_{\rm obs}$, total 
+luminosity of the binary is the same).
 Thus,
 \begin{equation}
-	\mathcal{N}_{\rm s}^2(r', M'; r, M)
-	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r', M'; r, M; q),
+	\mathcal{N}_{\rm s}^2(r_a, M_a; r, M)
+	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r_a, M_a; r, M; q),
 \end{equation}
@@
 	\notag
-	\mathcal{N}_{\rm s}^2(r', M'; r, M; q)
-	%&=N_{\rm s}(D', L(M')) \left[L_{\rm sys}(M', q) \over L(M') 
+	\mathcal{N}_{\rm s}^2(r_a, M_a; r, M; q)
+	%&=N_{\rm s}(\delta_{\rm obs}, L(M_a)) \left[L_{\rm sys}(M_a, q) \over 
+	%L(M_a) 
 	%\right]^{3/2}\\
-	&=N_{\rm s}^0(D', L(M'))\cdot\mu(\mathrm{BF},M')\\
-	&\times \delta \left(r'-r\sqrt{ \left[{R(M')\over R(qM')}\right]^2 {L(qM') 
-	\over L_{\rm sys}(M', q)} }\right)\delta\left(M'-{M\over q}\right).
+	&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))\cdot\mu(\mathrm{BF},M_a)\\
+	&\times \delta \left(r_a-r\sqrt{ \left[{R(M_a)\over R(qM_a)}\right]^2 
+	{L(qM_a) 
+	\over L_{\rm sys}(M_a, q)} }\right)\delta\left(M_a-{M\over q}\right).
 \end{align}
@@
 \begin{align}
-	n^0(r\a, M\a)
+	N_{\rm det}^0(r\a, M\a)
 	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^0(r\a, M\a; r, M)
@@
 \begin{align}
-	n^1(r\a, M\a)
+	N_{\rm det}^1(r\a, M\a)
 	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^1(r\a, M\a; r, M)
@@
 	&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
-	\mu(\mathrm{BF}, M\a) \int {\mathrm{d}q \over \alpha}\,f(q)\,\Lambda^1(r^*, M\a),
-	%\left[L_{\rm sys}(M', q) \over L(M') \right]^{3/2},
+	\mu(\mathrm{BF}, M\a) \int {\mathrm{d}q \over 
+	\alpha}\,f(q)\,\Lambda^1(r_a/\alpha, M\a),
+	%\left[L_{\rm sys}(M_a, q) \over L(M_a) \right]^{3/2},
 \end{align}
-where $r^*=r\a/\alpha$ and 
+where
 \begin{equation}
@@
 \begin{align}
-	n^2(r\a, M\a)
+	N_{\rm det}^2(r\a, M\a)
 	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^2(r\a, M\a; r, M)
-	\cdot\Lambda^2(r, M) \cdot p_{\rm tra}(M)\\
-	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, q}^2(r\a, M\a; r, M; q)\cdot\Lambda^2(r, M) \cdot p_{\rm tra}(M)\\
-	&=%N_{\rm s}(D', L(M')
+	\cdot\Lambda^2(r, M) \cdot p_{\rm tra}(M)
+    \\
+	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, 
+	q}^2(r\a, M\a; r, M; q)\cdot\Lambda^2(r, M) \cdot p_{\rm tra}(M)
+    \\
+    &= N\s^0(\delta_{\rm obs},L(M\a)) \mu({\rm BF},M\a)
+    \int {\rm d}r{\rm d}q\, q f(q) \delta(r_a - r\beta) \Lambda^2(r,qM\a) 
+    p_{\rm tra}(qM\a) \\
+	&=%N_{\rm s}(\delta_{\rm obs}, L(M_a)
 	N\s^0(\delta_{\rm obs}, L(M\a))\cdot\mu(\mathrm{BF}, M\a)
-	\int {q \mathrm{d}q \over \beta}\,f(q)\,\Lambda^2(r^{**}, qM\a)\,p_{\rm tra}(qM\a),
-	%\left[L_{\rm sys}(M', q) \over L(M') \right]^{3/2},
+	\int {q \mathrm{d}q \over \beta}\,f(q)\,\Lambda^2(r_a/\beta, qM\a)\,p_{\rm 
+	tra}(qM\a),
+	%\left[L_{\rm sys}(M_a, q) \over L(M_a) \right]^{3/2},
 \end{align}
-where $r^{**}=r\a/\beta$ and 
+where
 \begin{equation}
@@
 binaries from singles (and adopt the primary properties for binaries).
-Using the results above, the apparent occurrence is thus given by
+Using the results above, the apparent occurrence,
 \begin{align}
-	&\Lambda\a(r\a, M\a)={1\over 1+\mu(\mathrm{BF}, M\a)}\times\\
-	%&=(1-\mathrm{BF})\cdot
-	&\left\{ \Lambda^0(r\a, M\a)+ \mu(\mathrm{BF}, M\a) \left[
-	\int {\mathrm{d}q \over A}\,f(q)\,\Lambda^1\left({r\a\over A}, M\a\right)\,
-	+\int {q \mathrm{d}q \over B}\,f(q)\,\Lambda^2\left({r\a\over B}, qM\a\right)\,
+\Lambda\a(r\a,M\a) &= 
+    \frac{1}{N_{\rm s,a}(r\a,M\a) p_{\rm tra}(r\a,M\a)} \times
+    \sum_i N_{\rm det}^i (r\a,M\a),
+\end{align}
+evaluates to
+\begin{align}
+\notag
+\Lambda\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
+   \left\{ \Lambda^0(r\a, M\a)+ 
+\mu(\mathrm{BF}, M\a)
+\left[ \int {\mathrm{d}q \over \alpha}\,f(q)\,\Lambda^1\left({r\a\over 
+    \alpha}, 
+M\a\right)\,
+\right.   
+   \right. \\
+& \quad\quad\quad\quad\quad \left.\left.
++\int {q \mathrm{d}q \over \beta}\,f(q)\,\Lambda^2\left({r\a\over \beta}, 
+qM\a\right)\,
 {R(qM\a) \over R(M\a)}
-	q^{-1/3} \right]
-	\right\},
-	 %\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2}
-	 %\\
-	%&+\mathrm{BF}\cdot
-	%\int {q \mathrm{d}q \over B}\,f(q)\,\Lambda^2\left({r\a\over B}, qM\a\right)\,
-	%{R(qM\a) \over R(M\a)}q^{-1/3}
-	%\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2},
+q^{-1/3} \right]	\right\}.  
 \end{align}
-where
-\begin{equation}
-	A=\left[1+{L(qM\a) \over L(M\a)}\right]^{-1/2}, \quad
-	B={R(M\a)\over R(qM\a)}\left[1+{L(M\a) \over L(qM\a)}\right]^{-1/2}.
-\end{equation}
 

### 2017-11-28 sandbox/note_km.tex
km note: notation improvement, technical kvetching

@@
 	\mu(\mathrm{BF}, M\a) \int {\mathrm{d}q \over 
-	\alpha}\,f(q)\,\Lambda^1(r_a/\alpha, M\a),
+	\mathcal{A}}\,f(q)\,\Lambda^1(r_a/\mathcal{A}, M\a),
 	%\left[L_{\rm sys}(M_a, q) \over L(M_a) \right]^{3/2},
@@
 \begin{equation}
-	\alpha(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}.
+	\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}.
 \end{equation}
@@
     &= N\s^0(\delta_{\rm obs},L(M\a)) \mu({\rm BF},M\a)
-    \int {\rm d}r{\rm d}q\, q f(q) \delta(r_a - r\beta) \Lambda^2(r,qM\a) 
+    \int {\rm d}r{\rm d}q\, q f(q) \delta(r_a - r\mathcal{B}) 
+    \Lambda^2(r,qM\a) 
     p_{\rm tra}(qM\a) \\
@@
 	N\s^0(\delta_{\rm obs}, L(M\a))\cdot\mu(\mathrm{BF}, M\a)
-	\int {q \mathrm{d}q \over \beta}\,f(q)\,\Lambda^2(r_a/\beta, qM\a)\,p_{\rm 
+	\int {q \mathrm{d}q \over \mathcal{B}}\,f(q)\,\Lambda^2(r_a/\mathcal{B}, 
+	qM\a)\,p_{\rm 
 	tra}(qM\a),
@@
 \begin{equation}
-	\beta(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm sys}(M\a, q)} }.
+	\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
+	sys}(M\a, q)} }.
 \end{equation}
@@
 binaries from singles (and adopt the primary properties for binaries).
-Using the results above, the apparent occurrence,
+Using the results above, the apparent occurrence rate,
 \begin{align}
@@
 \mu(\mathrm{BF}, M\a)
-\left[ \int {\mathrm{d}q \over \alpha}\,f(q)\,\Lambda^1\left({r\a\over 
-    \alpha}, 
+\left[ \int {\mathrm{d}q \over \mathcal{A}}\,f(q)\,\Lambda^1\left({r\a\over 
+    \mathcal{A}}, 
 M\a\right)\,
@@
 & \quad\quad\quad\quad\quad \left.\left.
-+\int {q \mathrm{d}q \over \beta}\,f(q)\,\Lambda^2\left({r\a\over \beta}, 
++\int {q \mathrm{d}q \over \mathcal{B}}\,f(q)\,\Lambda^2\left({r\a\over 
+\mathcal{B}}, 
 qM\a\right)\,
@@
 
+\subsubsection{Simplifying above general result}
+To simplify, drop the explicit $M_a$ and BF 
+dependences, and assume $R\propto M$, so $R(qM_a)/R(M_a) = q$.
+Also, move all superscript numbers to subscripts.
+Then the apparent occurrence rate is
+\begin{equation}
+\Lambda\a(r\a) = \frac{1}{1+\mu}
+\left(
+    \Lambda_0(r\a) +
+    \mu \left[
+        \int \frac{{\rm d}q}{\mathcal{A}(q)} f(q) 
+        \Lambda_1\left( \frac{r\a}{\mathcal{A}(q)} \right)
+        +
+        \int \frac{q {\rm d}q}{\mathcal{B}(q)} f(q)
+        \Lambda_2\left(\frac{r\a}{\mathcal{B}(q)}\right) q^{2/3}
+    \right]
+\right).
+\end{equation}
+For the power law case when $L\sim M^\alpha$,
+\begin{equation}
+\mathcal{A}(q)
+=(1+q^\alpha)^{-1/2},
+\quad
+\mathcal{B}(q)
+=q^{-1}(1+q^{-\alpha})^{-1/2}
+\end{equation}
+
 \section{Examples}
@@
 
-We have $f(q)=\delta(q-1)$. Thus
+We have $f(q)=\delta(q-1)$. The apparent rate is
 \begin{align}
-	\Lambda\a(r\a, M\a)
-	={1\over 1+\mu(\mathrm{BF}, M\a)}
-	\left\{\Lambda^0(r\a, M\a)
-	%+\mathrm{BF}\cdot 2^{3/2}\sqrt{2}\left[\Lambda^1(\sqrt{2}\,r\a, M\a)+\Lambda^2(\sqrt{2}\,r\a, M\a)\right].
-	+\mu(\mathrm{BF}, M\a)\cdot\sqrt{2}\left[\Lambda^1(\sqrt{2}\,r\a, M\a)+\Lambda^2(\sqrt{2}\,r\a, M\a)\right]
+\Lambda\a(r\a)
+={1\over 1+\mu(\mathrm{BF})}
+\left\{\Lambda_0(r\a)
++\mu(\mathrm{BF})\cdot \sqrt{2}\cdot\left[\Lambda_1(\sqrt{2}\,r\a)
++\Lambda_2(\sqrt{2}\,r\a)\right]
 \right\},
@@
 \begin{equation}
-	\mu(\mathrm{BF}, M\a)=\int \mathrm{d}q\,f(q) {\mathrm{BF}\over{1-\mathrm{BF}}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2}
+	\mu(\mathrm{BF})=\int \mathrm{d}q\,f(q) 
+	{\mathrm{BF}\over{1-\mathrm{BF}}}\left[1+{L(qM\a) \over 
+	L(M\a)}\right]^{3/2}
 	=2^{3/2}\cdot{\mathrm{BF}\over{1-\mathrm{BF}}}.
@@
 
-If $\Lambda^i(r, M)=Z^i\cdot\delta(r-r_0)$ (all the planets have the same radius),
+If $\Lambda_i(r, M)=Z_i\cdot\delta(r-r_0)$ (all the planets have the same 
+radius), by using the identity $\delta(ax+b)=\delta(x+b/a)/|a|$,
 \begin{align}
-	\Lambda\a(r\a, M\a)
-	%=\Lambda_0\left[(1-\mathrm{BF})\cdot\delta(r\a-r_0)
-	%+2\mathrm{BF}\cdot 2^{3/2}\cdot\delta\left(r\a-{r_0\over\sqrt{2}}\right)\right].
+	\Lambda\a(r\a)
 	={1 \over 1+\mu(\mathrm{BF})}
-	\left[Z^0 \cdot \delta(r\a-r_0)+(Z^1+Z^2)\cdot \mu(\mathrm{BF})\cdot \delta\left(r\a-{r_0\over\sqrt{2}}\right)\right].
+	\left[Z_0 \cdot \delta(r\a-r_0)+(Z_1+Z_2)\cdot \sqrt{2} 
+	\mu(\mathrm{BF})\cdot 
+	\delta\left(r\a-\frac{r_0}{\sqrt{2}}\right)\right].
+    \label{eq:model1_apparent_rate}
 \end{align}
-This reproduces Eq.(9) of the draft, after correcting for the smaller number of apparently searchable stars for the diluted planets (factor of $(1/2)^3$).
-In the limit of $\mathrm{BF}\to1$ ($\mu\to\infty$), the above formula yields $\Lambda\a=(Z^1+Z^2)\,\delta(r\a-{r_0/\sqrt{2}})$.
+This reproduces Eq.(9) of the draft (after removing the $p_{\rm det}$ terms).
+In the limit of $\mathrm{BF}\to1$ ($\mu\to\infty$), the above formula yields 
+$\Gamma\a=(Z^1+Z^2)\,\delta(r\a-{r_0/\sqrt{2}})$.
+
+Eq.~\ref{eq:model1_apparent_rate} is technically abusing notation, because 
+$\Lambda$ must be dimensionless, and $\delta(r-r_0)$ has units 
+of inverse length.
+Since the equation is meant to convey the idea: ``at a given apparent radius, 
+the apparent number of planets per star is $x$'', and the delta function is 
+more succinct than listing out discrete cases, we leave it as-is.
 
@@
 	%\int \mathrm{d}q\,f(q)
-	%(1+q^\alpha)^2 \cdot \Lambda^1\left( r\a\sqrt{1+q^\alpha}, M\a\right)\\
+	%(1+q^\mathcal{A})^2 \cdot \Lambda^1\left( r\a\sqrt{1+q^\mathcal{A}}, 
+	%M\a\right)\\
 	%&+\mathrm{BF}\cdot
 	%\int {\mathrm{d}q}\,f(q)q^{8/3}
-	%\sqrt{1+q^{-\alpha}}(1+q^\alpha)^{3/2}
-	%\cdot\Lambda^2\left(r\a q\sqrt{1+q^{-\alpha}}, qM\a\right).
+	%\sqrt{1+q^{-\mathcal{A}}}(1+q^\mathcal{A})^{3/2}
+	%\cdot\Lambda^2\left(r\a q\sqrt{1+q^{-\mathcal{A}}}, qM\a\right).
 \end{align}

### 2017-11-28 sandbox/note_km.tex
km note: changed mu defn. Wrote Model 2.

@@
 %
-This derives the equations of the paper.
+This note formally derives a general equation for the apparent occurrence rate 
+used in the paper.
 
@@
 	\quad \delta_{\rm obs}:\text{observed depth}
+    \label{eq:snr_limited}
 \end{equation}
@@
 the apparent number of searchable stars (i.e. points in the sky), which will 
-be selected by an ignorant observer, can be written 
+be selected by an ignorant observer, is proportional to
 \begin{align}
@@
 N_{\rm s,a}(\delta_{\rm obs}, M\a)
-	%&=n_{\rm s,0}\delta_{\rm obs}^3L(M\a)^{3/2} + n_{\rm b,0}\delta_{\rm 
-	%obs}^3 \cdot [L(M\a)+L(qM\a)]^{3/2}\\
-	&\propto n_{\rm s}\delta_{\rm obs}^3 L(M\a)^{3/2}\left[ 1+\int 
-	\mathrm{d}q\,f(q) 
-	{\mathrm{BF}\over{1-\mathrm{BF}}}\left(1+{L(qM\a) \over 
-	L(M\a)}\right)^{3/2}\right]\\
+&\propto n_{\rm s}\delta_{\rm obs}^3 L(M\a)^{3/2}\left[1+\mu(\mathrm{BF}, 
+M\a)\right],
+\end{align}
+and we can define
+\begin{align}
 	N_{\rm s,a}(\delta_{\rm obs}, M\a)
@@
 	M\a)\right],
+    \label{eq:N_selected}
 \end{align}
 where $N\s^0$ is the number of searchable singles (this agrees with the actual 
-value), $f(q)$ is the binary mass ratio distribution, $\mathrm{BF}=n_{\rm 
-b}/(n_{\rm s}+n_{\rm b})$ is the binary fraction in a volume-limited sample, 
+value), $\mathrm{BF}=n_{\rm b}/(n_{\rm s}+n_{\rm b})$ 
+is the binary fraction in a volume-limited sample, 
 and $n_s$ is the number density of singles in a volume-limited sample.
@@
 {\it e.g.}, the telescope area and the survey duration.
+
+\subsubsection{What is $\mu$?}
+In Eq.~\ref{eq:N_selected}, $\mu$ is the ratio of the number of single to 
+double star systems (that are searchable for an observed signal $\delta_{\rm 
+obs}$).
+If we make various simplifying assumptions, it turns out that this number 
+depends only on the binary fraction and the 
+binary mass ratio distribution in a volume-limited sample.
+The proof is as follows.
+
+In a shell of thickness ${\rm d}r$, there are $n_d(r) 4\pi r^2 {\rm d}r$ 
+searchable double star systems.
+The number density of searchable double star systems $n_d(r)$ is constant up 
+to the maximum searchable distance for singles, $d_0$. At greater distances, 
+$n_d(r)$ decreases, because only some binaries have sufficient flux to make 
+the SNR cut.
+Specifically,
+\begin{equation}
+n_d(r) = 
+\begin{cases}
+n_b,	\quad r\leq d_0\\
+n_b \int_{q_{\rm min}(r)}^1 {\rm d}q\, f(q), \quad d_0 < r < \sqrt{2}d_0 \\
+\end{cases}
+\end{equation}
+where $f(q)$ is the mass ratio distribution in a volume-limited sample, 
+$q_{\rm min}(r)$ is the minimum mass ratio required to provide sufficient flux 
+for searchability.
+Assuming $L\propto M^\alpha$,
+\begin{equation}
+q_{\rm min}(r) =
+\left(
+    \left( \frac{r}{d_0}\right)^2
+    - 1
+\right)^{\frac{1}{\alpha}}.
+\end{equation}
+Using the common parametrization $f(q) \sim q^\beta$, and setting $\beta=0$,
+\begin{equation}
+n_d(r) = 
+\begin{cases}
+n_b,	\quad r\leq d_0\\
+n_b (1-q_{\rm min}(r)), \quad d_0 < r < \sqrt{2}d_0. \\
+\end{cases}
+\end{equation}
+Integrating,
+\begin{align}
+N_d = \int {\rm d} N_d &= \int n_d(r) 4\pi r^2 {\rm d}r \\
+&=
+4\pi n_b \left(
+    \frac{d_0^3}{3} +
+    \left[\frac{r^3}{3}\right]^{\sqrt{2 d_0}}_{d_0}
+    -
+    \int_{d_0}^{\sqrt{2}d_0} \left(
+    \left(\frac{r}{d_0}\right)^2 -1
+    \right)^{\frac{1}{\alpha}}
+    r^2 \,{\rm d}r
+\right) \\
+&=
+\frac{4 \pi n_b}{3} d_0^3 \left(
+2^{3/2} -
+3 \int_{1}^{\sqrt{2}} {\rm d}u\, u^2 (u^2 - 1)^{1/\alpha}
+\right), \label{eq:dimensionless_integral}
+\\
+&\equiv
+\frac{4 \pi n_b}{3} d_0^3 \left(
+2^{3/2} - 3 I
+\right),
+\end{align}
+where the penultimate line substituted $u=r/d_0$.
+For the common case $\alpha=3.5$, the dimensionless integral $I$ evaluates to 
+$\approx 0.484174$.
+
+Thus
+\begin{equation}
+\mu \equiv \frac{N_d}{N_s^0}
+= \frac{n_b}{n_s} \left(2^{3/2} - 3 I\right)
+= \frac{{\rm BF}}{1 - {\rm BF}} \left(2^{3/2} - 3 I\right).
+\label{eq:mu_final}
+\end{equation}
+For the twin binary case, $I=0$, and for the power law volume-limited 
+distribution, $I$ takes the form given in Eq.~\ref{eq:dimensionless_integral}.
 
@@
 \end{equation}
-where $f(q)$ is the binary mass ratio distribution and
+where $f(q)$ is the binary mass ratio distribution in the SNR-limited sample 
+and
 \begin{align}
@@
 about this dependence.
+As discussed in the main text, we have $f(q) \sim q^\beta (1+q^\alpha)^{3/2}$.
 
@@
 \right).
+\label{eq:simple_apparent_occ_rate}
 \end{equation}
@@
 =q^{-1}(1+q^{-\alpha})^{-1/2}
+\label{eq:powerlaw_A_B}
 \end{equation}
@@
 
-\subsubsection{Same Planets}
+\subsubsection{Same Planets (Model \# 1)}
 
@@
 	={1 \over 1+\mu(\mathrm{BF})}
-	\left[Z_0 \cdot \delta(r\a-r_0)+(Z_1+Z_2)\cdot \sqrt{2} 
+	\left[Z_0 \cdot \delta(r\a-r_0)+(Z_1+Z_2)\cdot 
 	\mu(\mathrm{BF})\cdot 
@@
 In the limit of $\mathrm{BF}\to1$ ($\mu\to\infty$), the above formula yields 
-$\Gamma\a=(Z^1+Z^2)\,\delta(r\a-{r_0/\sqrt{2}})$.
+$\Lambda\a=(Z^1+Z^2)\,\delta(r\a-{r_0/\sqrt{2}})$.
 
@@
 we find 
+\begin{equation}
+\mathcal{A}(q)
+=(1+q^\alpha)^{-1/2},
+\quad
+\mathcal{B}(q)
+=q^{-1}(1+q^{-\alpha})^{-1/2}.
+\end{equation}
+
+This gives a value of $\mu({\rm BF})$ stated in Eq.~\ref{eq:mu_final}.
+Now recall Eq.~\ref{eq:simple_apparent_occ_rate} for the apparent occurrence 
+rate. We restate it here:
+\begin{equation}
+\Lambda\a(r\a) = \frac{1}{1+\mu}
+\left(
+\Lambda_0(r\a) +
+\mu \left[
+\int \frac{{\rm d}q}{\mathcal{A}(q)} f(q) 
+\Lambda_1\left( \frac{r\a}{\mathcal{A}(q)} \right)
++
+\int \frac{q {\rm d}q}{\mathcal{B}(q)} f(q)
+\Lambda_2\left(\frac{r\a}{\mathcal{B}(q)}\right) q^{2/3}
+\right]
+\right).
+\end{equation}
+
+\subsubsection{Same Planets (Model \# 2)}
+For our ``Model \#2'', we again want $\Lambda_i(r) = Z_i \cdot \delta(r-r_0)$.
+To achieve this, write
+\begin{equation}
+f(q) = \frac{q^\beta (1+q^\alpha)^{3/2}}{\mathcal{N}_q},
+\end{equation}
+for $\mathcal{N}_q$ the normalization.
+For $i=1$, call the integral on the left the $[\ldots]$ ``$I_1$''.
+Then
 \begin{align}
-	A=(1+q^\alpha)^{-1/2}, \quad 
-	B=q^{-1}(1+q^{-\alpha})^{-1/2},
+I_1(r_a) &\equiv \int \frac{{\rm d}q}{\mathcal{A}(q)} f(q) 
+    \Lambda_1\left( \frac{r\a}{\mathcal{A}(q)} \right)
+    \\
+&= \frac{1}{\mathcal{N}_q} \int {\rm d}q\, q^\beta (1+q^\alpha)^2
+    \Lambda_1(r_a (1+q^\alpha)^{1/2})
+    \\
+&= \frac{Z_1}{\mathcal{N}_q} \int {\rm d}q\, q^\beta (1+q^\alpha)^2
+    \delta(r_a (1+q^\alpha)^{1/2} - r_0) \\
+&= \frac{Z_1}{\mathcal{N}_q}
+    \left( \left(\frac{r_0}{r_a}\right)^2 - 1  \right)^{\beta/\alpha}
+    \left( \frac{r_0}{r_a}\right)^4.
+    \label{eq:model_2_i_1}
 \end{align}
-so
+The penultimate line used the fact that $r_a(1+q^\alpha)^{1/2}=r_0$ has only 
+one root:
+\begin{equation}
+q(r_a) = \left(\left(\frac{r_0}{r_a}\right)^2 - 1\right)^{1/\alpha}.
+\end{equation}
+Eq.~\ref{eq:model_2_i_1} should be used as a sanity check on any 
+Monte Carlo numerics.
+
+Attempting the same thing for $i=2$,
 \begin{align}
-	\Lambda\a(r\a, M\a)=...
-	%&=(1-\mathrm{BF})\cdot\Lambda^0(r\a, M\a)\\
-	%&+\mathrm{BF}\cdot 
-	%\int \mathrm{d}q\,f(q)
-	%(1+q^\mathcal{A})^2 \cdot \Lambda^1\left( r\a\sqrt{1+q^\mathcal{A}}, 
-	%M\a\right)\\
-	%&+\mathrm{BF}\cdot
-	%\int {\mathrm{d}q}\,f(q)q^{8/3}
-	%\sqrt{1+q^{-\mathcal{A}}}(1+q^\mathcal{A})^{3/2}
-	%\cdot\Lambda^2\left(r\a q\sqrt{1+q^{-\mathcal{A}}}, qM\a\right).
+I_2(r_a) &\equiv \int \frac{q {\rm d}q}{\mathcal{B}(q)} f(q)
+\Lambda_2\left(\frac{r\a}{\mathcal{B}(q)}\right) q^{2/3}
+\\
+&= \frac{Z_2}{\mathcal{N}_q} \int {\rm d}q\,
+    q^{\beta+\frac{8}{3}} 
+    (1+q^\alpha)^{3/2}
+    (1+q^{-\alpha})^{1/2}
+    \delta(r_a q (1+q^{-\alpha})^{1/2} - r_0).
 \end{align}
-We may further assume
+Unfortunately, analytic roots of $r_a q (1+q^{-\alpha})^{1/2} = r_0$ do not 
+exist.
+Schematically, since for any function $g(x)$,
 \begin{equation}
-	f(q)\sim q^\beta, \quad \Lambda(r) \sim r^\gamma
+\delta(g(x)) = \sum_{x_i \in \{{\rm roots}\}} \frac{\delta(x-x_i)}{|g'(x_i)|},
+\end{equation}
+if the roots are found numerically then
+\begin{equation}
+I_2(r_a) = \frac{Z_2}{\mathcal{N}_q}
+    \sum_{q_i \in \{{\rm roots}\}}
+q_i^{\beta+\frac{8}{3}} 
+(1+q_i^\alpha)^{3/2}
+(1+q_i^{-\alpha})^{1/2}.
+\end{equation}
+But this doesn't really give much insight.
+
+\subsubsection{Power law planets (Model \# 3)}
+
+Assume now that
+\begin{equation}
+    \Lambda(r) \sim r^\delta
 \end{equation}
 and keep calculating...
-
-%\acknowledgements
-%It was a pleasure to share discussions with Kento Masuda, who pointed us in 
-%this direction, and helped clarify that something like this was worth 
-%studying.
-%It was a pleasure discussing this work with F. Dai and T. Barclay.
 

### 2017-11-28 results/make_merged.sh
update code, for no p_det

@@ -3,16 +3,16 @@ pdftk \
   errcases_rate_density_vs_radius_model_1_brokenx.pdf \
   errcases_rate_density_vs_radius_model_2.pdf \
   errcases_rate_density_vs_radius_logs_model_2.pdf \
-  errcases_rate_density_vs_radius_model_3.pdf \
-  errcases_rate_density_vs_radius_logs_model_3.pdf \
-  errcases_rate_density_vs_radius_model_3_withtext.pdf \
+  errcases_rate_density_vs_radius_model_3_Lambda2_0.5.pdf \
+  errcases_rate_density_vs_radius_logs_model_3_Lambda2_0.5.pdf \
+  errcases_rate_density_vs_radius_model_3_withtext_Lambda2_0.5.pdf \
   output errcases_merged.pdf
 
 pdftk \
   rate_density_vs_radius_model_1_brokenx.pdf \
   rate_density_vs_radius_model_2.pdf \
   rate_density_vs_radius_logs_model_2.pdf \
-  rate_density_vs_radius_model_3.pdf \
-  rate_density_vs_radius_logs_model_3.pdf \
-  rate_density_vs_radius_model_3_withtext.pdf \
+  rate_density_vs_radius_model_3_Lambda2_0.5.pdf \
+  rate_density_vs_radius_logs_model_3_Lambda2_0.5.pdf \
+  rate_density_vs_radius_model_3_withtext_Lambda2_0.5.pdf \
   output rates_merged.pdf

### 2017-11-28 src/numerical_models.py

@@ -9,6 +9,8 @@ Alternatively, use a wrapper like `run_numerical_models.py`.
 
 Models #1-#3 are as-discussed in the text.
 Model #4 is a version of the Fulton+ (2017) gap.
+
+NB: running Model #1 requires hard-changing BF in `numerical_transit_survey`.
 '''
 
 from __future__ import division, print_function
@@ -24,7 +26,7 @@ def numerical_transit_survey(
         quickrun,
         model_number,
         Λ_2,
-        BF=0.44,
+        BF=0.1,
         α=3.5,
         β=0,
         γ=0,
@@ -150,10 +152,16 @@ def numerical_transit_survey(
     Q_c0 = 1
     single_is_searchable = np.ones(N_0).astype(bool)
 
-    Q_c1 = (1+q**α)**(-3)
+    # NOTE: the inclusion of this "searchability" draw is outdated. (In drafts
+    # before mid-November 2017, I made an error in counting searchable
+    # binaries -- I thought that e.g., 1 in 8 selected twin binaries would be
+    # searchable. However, a star is selected based on its flux and the
+    # planet's *apparent* radius, rather than the planet's true radius. Thus
+    # all selected twin binaries are searchable. (Per KM's 2017/11/21 note).
+    Q_c1 = 1 #(1+q**α)**(-3)
     primary_is_searchable = ( np.random.rand((N_1)) < Q_c1 )
 
-    Q_c2 = (1+q**(-α))**(-3) * q**(-5)
+    Q_c2 = 1 #(1+q**(-α))**(-3) * q**(-5)
     secondary_is_searchable = ( np.random.rand((N_2)) < Q_c2 )
 
     is_searchable = np.concatenate(
@@ -170,24 +178,6 @@ def numerical_transit_survey(
             len(df[df['star_type']=='secondary'])
     print("population's completeness fraction for secondaries: {:.3g}".
             format(_2))
-
-    if model_number == 1:
-        if slowrun and N_0>=1e6:
-            # we know that the completeness in model 1 should be 1/8.
-            assert np.isclose(_1, 1/8, rtol=1e-2) \
-                   and \
-                   np.isclose(_2, 1/8, rtol=1e-2)
-    elif model_number == 2 or model_number == 3 or model_number == 4:
-        # primaries should be more complete than 1/8
[…]

### 2017-11-28 src/plot_errcases_rate_densities_vs_radius.py

@@ -217,12 +217,12 @@ if __name__ == '__main__':
 
     for model_number in [1,2,3]:
 
-        make_plot(model_number)
+        make_plot(model_number, Λ_2=0.5)
 
     make_plot(1, brokenx=True, Λ_2=0.5)
-    make_plot(2, logy=True)
-    make_plot(3, logy=True)
-    make_plot(3, withtext=True, stdout=True)
+    make_plot(2, logy=True, Λ_2=0.5)
+    make_plot(3, logy=True, Λ_2=0.5)
+    make_plot(3, withtext=True, stdout=True, Λ_2=0.5)
 
     make_plot(3, Λ_2=0)
     make_plot(3, logy=True, Λ_2=0)

### 2017-11-28 src/plot_rate_densities_vs_radius.py

@@ -1,5 +1,5 @@
 '''
-first, for models 1,2, 3:
+first, for models 1,2,3,4:
 >>> python numerical_models.py
 then:
 >>> python plot_rate_densities_vs_radius.py
@@ -161,12 +161,12 @@ if __name__ == '__main__':
 
     for model_number in [1,2,3]:
 
-        make_plot(model_number)
+        make_plot(model_number, Λ_2=0.5)
 
     make_plot(1, brokenx=True, Λ_2=0.5)
-    make_plot(2, logy=True)
-    make_plot(3, logy=True)
-    make_plot(3, withtext=True, stdout=True)
+    make_plot(2, logy=True, Λ_2=0.5)
+    make_plot(3, logy=True, Λ_2=0.5)
+    make_plot(3, withtext=True, stdout=True, Λ_2=0.5)
 
     make_plot(3, Λ_2=0)
     make_plot(3, logy=True, Λ_2=0)

### 2017-11-29 sandbox/note_km.tex
add twin binary, planet distrbn case

@@
 \right\},
+\label{eq:apparent_rate_twin_binary}
 \end{align}
@@
 more succinct than listing out discrete cases, we leave it as-is.
+
+\subsubsection{Power Law Distribution of Planets}
+
+Imagine instead that we took $\Lambda_i(r,M) = Z_i r^\delta$.
+From Eq.~\ref{eq:apparent_rate_twin_binary}, we get an apparent rate
+\begin{equation}
+\Lambda_a(r_a) = r_a^\delta \left[
+\frac{Z_0}{1+\mu({\rm BF})}
++
+2^{\frac{\delta}{2} + 1 } \frac{\mu({\rm BF})}{1+\mu({\rm BF})} \left(
+Z_1 + Z_2
+\right)
+\right].
+\end{equation}
+
+Consider the case when the $Z_i$'s are identical. If we compare 
+$\Lambda_a(r_a)$ with $\Lambda(r)$, we must impose that $r_a$ and $r$ are 
+indistinguishable (i.e.: the observer cannot tell them apart).
+Note that the true rate is
+\begin{equation}
+\Lambda(r) = r^\delta \left[
+\frac{Z_0}{1+2\mu} + \frac{\mu}{1+2\mu} (Z_1+Z_2)
+\right]
+\end{equation}
+We then get a correction factor
+\begin{equation}
+X_\Lambda \equiv \left. \frac{\Lambda_a(r_a)}{\Lambda(r)} 
+\right|_{r_a\rightarrow r}
+=
+\frac{2^{\frac{\delta}{2}+2}\mu + 1}{\mu + 1}.
+\end{equation}
+
+For the case of ${\rm BF}=0.1$, $\mu\approx 0.153$. Taking $\delta=-2.92$ from 
+Howard et al. (2012),  we get a correction factor $X_\Lambda = 
+\Lambda_a/\Lambda = 1.06$.
+In other words, the apparent rate is an {\it over}estimate of the true rate, 
+with a relative error of 6\%.
 

### 2017-11-30 sandbox/note_km.tex
corrected math error in I_1(r_a) model 2

@@
 given by the convolution of the true occurrence, $\Lambda(\pp, \ps)$, and 
-number of searchable stars that give $(\pp\a, \ps\a)$ when the true system 
-actually has $(\pp, \ps)$, $\mathcal{N}(\pp\a, \ps\a; \pp, \ps)$:
+$\mathcal{N}(\pp\a, \ps\a; \pp, \ps)$, the number of searchable stars that 
+give $(\pp\a, \ps\a)$ when the true system actually has $(\pp, \ps)$:
 \begin{equation}
@@
 
-Imagine instead that we took $\Lambda_i(r,M) = Z_i r^\delta$.
+Imagine instead that we took $\Lambda_i(r,M) = Z_i f(r) = Z_i 
+r^\delta/\mathcal{N}_r$, for $f(r)$ the radius shape function, 
+$\mathcal{N}_r$ the shape function's normalization, and $Z_i$ the number of 
+planets per star.
 From Eq.~\ref{eq:apparent_rate_twin_binary}, we get an apparent rate
 \begin{equation}
-\Lambda_a(r_a) = r_a^\delta \left[
+\Lambda_a(r_a) = \frac{r_a^\delta}{\mathcal{N}_r} \left[
 \frac{Z_0}{1+\mu({\rm BF})}
 +
-2^{\frac{\delta}{2} + 1 } \frac{\mu({\rm BF})}{1+\mu({\rm BF})} \left(
-Z_1 + Z_2
+2^{\frac{\delta+1}{2} } \frac{\mu({\rm BF})}{1+\mu({\rm BF})} \left(Z_1 + Z_2
 \right)
@@
 \begin{equation}
-\Lambda(r) = r^\delta \left[
+\Lambda(r) = \frac{r^\delta}{\mathcal{N}_r} \left[
 \frac{Z_0}{1+2\mu} + \frac{\mu}{1+2\mu} (Z_1+Z_2)
@@
 with a relative error of 6\%.
+
+As a side-note, this particular model (twin binaries, power law planet 
+distribution) is a good unit test for the numerics. As of git commit 
+\texttt{9b8f55c}, the two agree.
 
@@
     \delta(r_a (1+q^\alpha)^{1/2} - r_0) \\
-&= \frac{Z_1}{\mathcal{N}_q}
-    \left( \left(\frac{r_0}{r_a}\right)^2 - 1  \right)^{\beta/\alpha}
+&= \frac{Z_1}{\mathcal{N}_q} \frac{2}{\alpha} \frac{r_0}{r_a^2} 
+   \left(\left(\frac{r_0}{r_a}\right)^2 -1
+       \right)^{\frac{1-\alpha}{\alpha}}
+   \int {\rm d}q\, q^\beta (1+q^\alpha)^2 
+       \delta\left( q - \left( \left(\frac{r_0}{r_a}\right)^2 -1
+       \right)^{\frac{1}{\alpha}} \right) \\
+&= \frac{Z_1}{\mathcal{N}_q} \frac{2}{\alpha} \frac{r_0}{r_a^2}
+    \left( \left(\frac{r_0}{r_a}\right)^2 - 1  
+    \right)^{\frac{\beta-\alpha+1}{\alpha}}
     \left( \frac{r_0}{r_a}\right)^4.
@@
 \begin{equation}
-q(r_a) = \left(\left(\frac{r_0}{r_a}\right)^2 - 1\right)^{1/\alpha}.
+q(r_a) = \left(\left(\frac{r_0}{r_a}\right)^2 - 1\right)^{1/\alpha},
 \end{equation}
-Eq.~\ref{eq:model_2_i_1} should be used as a sanity check on any 
-Monte Carlo numerics.
+and for any function $f(q)$ with a single root $q_i$,
+\begin{equation}
+\delta(f(q)) = \frac{\delta(q-q_i)}{|f'(q_i)|}.
+\end{equation}
+Eq.~\ref{eq:model_2_i_1} is a good unit test for Monte Carlo numerics.
 
@@
 exist.
-Schematically, since for any function $g(x)$,
-\begin{equation}
-\delta(g(x)) = \sum_{x_i \in \{{\rm roots}\}} \frac{\delta(x-x_i)}{|g'(x_i)|},
-\end{equation}
-if the roots are found numerically then
+If the roots are found numerically then
 \begin{equation}
@@
 (1+q_i^\alpha)^{3/2}
-(1+q_i^{-\alpha})^{1/2}.
+(1+q_i^{-\alpha})^{1/2},
 \end{equation}
-But this doesn't really give much insight.
+but this doesn't really give much insight.
 

### 2017-11-30 sandbox/note_km.tex
did analytic model #3, which is now tractable

@@
 used in the paper.
+For some analytic cases, this lets us vet our Monte Carlo code.
 
@@
 \end{align}
-and we can define
+and can be {\it defined} as
 \begin{align}
@@
 n_b,	\quad r\leq d_0\\
-n_b \int_{q_{\rm min}(r)}^1 {\rm d}q\, f(q), \quad d_0 < r < \sqrt{2}d_0 \\
+n_b \int_{q_{\rm min}(r)}^1 {\rm d}q\, f_v(q), \quad d_0 < r < \sqrt{2}d_0 \\
 \end{cases}
 \end{equation}
-where $f(q)$ is the mass ratio distribution in a volume-limited sample, 
+where $f_v(q)$ is the mass ratio distribution in a volume-limited sample, 
 $q_{\rm min}(r)$ is the minimum mass ratio required to provide sufficient flux 
@@
 \end{equation}
-Using the common parametrization $f(q) \sim q^\beta$, and setting $\beta=0$,
+Using the common parametrization $f_v(q) \sim q^\beta$, and setting $\beta=0$,
 \begin{equation}
@@
 certain type per star of a certain type.
-They observe a set points on the sky and detect $N_{\rm det}$ planets that 
+They observe a set points on the sky and detect a set of planets that 
 appear to be of the desired class.
@@
 planets of interest appeared to be searchable.
-Finally they compute the apparent occurrence,
+Given these quantities, they compute the apparent rate density,
 \begin{equation}
-\Lambda\a(\pp\a, \ps\a) = \frac{N_{\rm det}(\pp\a, \ps\a)}{N_{\rm s,a}(\pp\a, 
+\Gamma\a(\pp\a, \ps\a) = \frac{N_{\rm det}(\pp\a, \ps\a)}{N_{\rm s,a}(\pp\a, 
     \ps\a)} \times \frac{1}{p_{\rm tra}(\pp\a, \ps\a)}.
@@
 where $\pp\a$, $\ps\a$ are the apparent planetary/stellar parameters.
+Here $N_{\rm det}(\pp\a, \ps\a)$ is the number of 
+detected planets with parameters $\pp\a,\ps\a$, {\it per unit} $\pp\a$ {\it 
+and} $\ps\a$. The quantity $N_{\rm s,a}(\pp\a, \ps\a)$ is the apparent number 
+of searchable stars.
+The apparent rate for a given class of planets is found by integrating the 
+rate density. For instance, if $\pp\a=r_a$ and $\ps\a=M_a$, the apparent rate 
+is
+\begin{equation}
+\int {\rm d}^2 \Lambda\a(r\a,M\a)
+=
+\int {\rm d}r\a {\rm d}M\a \, \Gamma_a(\pp\a,\ps\a)
+=
+\int {\rm d}r\a {\rm d}M\a
+    \frac{N_{\rm det}(r\a,M\a)}{N_{\rm s,a}(r\a,M\a)}
+    \times \frac{1}{p_{\rm tra}(r\a,M\a)}.
+\end{equation}
 
@@
 det}(\pp\a, \ps\a)$ is 
-given by the convolution of the true occurrence, $\Lambda(\pp, \ps)$, and 
-$\mathcal{N}(\pp\a, \ps\a; \pp, \ps)$, the number of searchable stars that 
-give $(\pp\a, \ps\a)$ when the true system actually has $(\pp, \ps)$:
-\begin{equation}
+given by the convolution of the true rate density, $\Gamma(\pp, \ps)$, and 
+$\mathcal{N}(\pp\a, \ps\a; \pp, \ps)$, the number (per unit $(\pp\a, \ps\a)$) 
+of searchable stars that give $(\pp\a, \ps\a)$  when the true system 
+actually has $(\pp, \ps)$:
+\begin{align}
 	N_{\rm det}(\pp\a, \ps\a)=\sum_i N_{\rm det}^i(\pp\a, \ps\a)
@@
 	\mathcal{N}_{\rm s}^i(\pp\a,\ps\a; \pp, \ps)
-	\cdot\Lambda^i(\pp, \ps)\cdot p_{\rm tra}(\pp, \ps),
-\end{equation}
+	\cdot\Gamma^i(\pp, \ps)\cdot p_{\rm tra}(\pp, \ps),
+\end{align}
 where $i$ specifies the type of true host stars (0: single, 1: primary, 2: 
@@
 \mathcal{N}_{\rm s}^i(r_a,M_a; r,M)
-\cdot\Lambda^i(r,M) \cdot p_{\rm tra}(r,M),
+\cdot\Gamma^i(r,M) \cdot p_{\rm tra}(r,M),
 \end{align}
@@
 \begin{equation}
-	N_{\rm det}^0(r\a, M\a)=N\s^0(r\a,M\a)\cdot \Lambda^0(r\a, 
+	N_{\rm det}^0(r\a, M\a)=N\s^0(r\a,M\a)\cdot \Gamma^0(r\a, 
 	M\a) \cdot p_{\rm tra}(r\a, M\a).
@@
 \begin{equation}
-	\Lambda\a(r\a, M\a)=\Lambda^0(r\a, M\a),
+	\Gamma\a(r\a, M\a)=\Gamma^0(r\a, M\a),
 \end{equation}
@@
 	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r_a, M_a; r, M; q),
+    \label{eq:fancyN_s_1}
 \end{equation}
@@
 about this dependence.
-As discussed in the main text, we have $f(q) \sim q^\beta (1+q^\alpha)^{3/2}$.
+As discussed in the main text, in Eq.~\ref{eq:fancyN_s_1} we will have $f(q) 
+\sim q^\beta (1+q^\alpha)^{3/2}$.
 
@@
 	\propto \delta\left(M_a-{M\over q}\right).
-	%=\mathcal{N}_{\rm s}^2(r_a, M_a, R_a; r, qM_a, R(qM_a)).
+    \label{eq:fancyN_s_2_prop}
 \end{equation}
@@
 
+One might worry in Eq.~\ref{eq:fancyN_s_2_prop} that we opt to write 
+$\mathcal{N}\s^2 \propto \delta(M_a - M/q)$, rather than $\propto \delta(M_a q 
+- M)$ or some other seemingly function with the same functional dependence, 
+but a different normalization once integrated.
+We do this because the delta function in Eq.~\ref{eq:fancyN_s_2_prop} is 
+defined with respect to the measure ${\rm d}M\a$, not ${\rm d}M$.
+This means that it should be unity when integrated over ${\rm d}M\a$.
+Ultimately, this is based on how we defined $\mathcal{N}\s^2$ as a number per 
+$r\a$, per $M\a$.
+
 \section{Result}
@@
 	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^0(r\a, M\a; r, M)
-	\cdot\Lambda^0(r, M) \cdot p_{\rm tra}(M)\\
+	\cdot\Gamma^0(r, M) \cdot p_{\rm tra}(M)\\
 	&=\int\mathrm{d}r\mathrm{d}M\, N\s^0(\delta_{\rm obs}, 
 	L(M\a))\delta(r\a-r)\delta(M\a-M)
-	\cdot\Lambda^0(r, M) \cdot p_{\rm tra}(M)\\
-	&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot\Lambda^0(r\a, M\a) \cdot p_{\rm 
+	\cdot\Gamma^0(r, M) \cdot p_{\rm tra}(M)\\
+	&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot\Gamma^0(r\a, M\a) \cdot p_{\rm 
 	tra}(M\a).
@@
 	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^1(r\a, M\a; r, M)
-	\cdot\Lambda^1(r, M) \cdot p_{\rm tra}(M)\\
-	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, q}^1(r\a, M\a; r, M; q)\cdot\Lambda^1(r, M) \cdot p_{\rm tra}(M)\\
+	\cdot\Gamma^1(r, M) \cdot p_{\rm tra}(M)\\
+	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, 
+	q}^1(r\a, M\a; r, M; q)\cdot\Gamma^1(r, M) \cdot p_{\rm tra}(M)\\
 	&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
 	\mu(\mathrm{BF}, M\a) \int {\mathrm{d}q \over 
-	\mathcal{A}}\,f(q)\,\Lambda^1(r_a/\mathcal{A}, M\a),
+	\mathcal{A}}\,f(q)\,\Gamma^1(r_a/\mathcal{A}, M\a),
 	%\left[L_{\rm sys}(M_a, q) \over L(M_a) \right]^{3/2},
@@
 	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^2(r\a, M\a; r, M)
-	\cdot\Lambda^2(r, M) \cdot p_{\rm tra}(M)
+	\cdot\Gamma^2(r, M) \cdot p_{\rm tra}(M)
     \\
 	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, 
-	q}^2(r\a, M\a; r, M; q)\cdot\Lambda^2(r, M) \cdot p_{\rm tra}(M)
+	q}^2(r\a, M\a; r, M; q)\cdot\Gamma^2(r, M) \cdot p_{\rm tra}(M)
     \\
@@
     \int {\rm d}r{\rm d}q\, q f(q) \delta(r_a - r\mathcal{B}) 
-    \Lambda^2(r,qM\a) 
+    \Gamma^2(r,qM\a) 
     p_{\rm tra}(qM\a) \\
@@
 	N\s^0(\delta_{\rm obs}, L(M\a))\cdot\mu(\mathrm{BF}, M\a)
-	\int {q \mathrm{d}q \over \mathcal{B}}\,f(q)\,\Lambda^2(r_a/\mathcal{B}, 
+	\int {q \mathrm{d}q \over \mathcal{B}}\,f(q)\,\Gamma^2(r_a/\mathcal{B}, 
 	qM\a)\,p_{\rm 
@@
 
-Note again that the denominators of $\Lambda\a$ are the same for singles, 
+Note again that the denominators of $\Gamma\a$ are the same for singles, 
 primaries, and secondaries: $N_{\rm s,a}(\delta_{\rm obs}, M\a)$ and $p_{\rm 
@@
 binaries from singles (and adopt the primary properties for binaries).
-Using the results above, the apparent occurrence rate,
+Using the results above, the apparent rate density,
 \begin{align}
-\Lambda\a(r\a,M\a) &= 
+\Gamma\a(r\a,M\a) &= 
     \frac{1}{N_{\rm s,a}(r\a,M\a) p_{\rm tra}(r\a,M\a)} \times
@@
 \notag
-\Lambda\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
-   \left\{ \Lambda^0(r\a, M\a)+ 
+\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
+   \left\{ \Gamma^0(r\a, M\a)+ 
 \mu(\mathrm{BF}, M\a)
-\left[ \int {\mathrm{d}q \over \mathcal{A}}\,f(q)\,\Lambda^1\left({r\a\over 
+\left[ \int {\mathrm{d}q \over \mathcal{A}}\,f(q)\,\Gamma^1\left({r\a\over 
     \mathcal{A}}, 
@@
 & \quad\quad\quad\quad\quad \left.\left.
-+\int {q \mathrm{d}q \over \mathcal{B}}\,f(q)\,\Lambda^2\left({r\a\over 
++\int {q \mathrm{d}q \over \mathcal{B}}\,f(q)\,\Gamma^2\left({r\a\over 
 \mathcal{B}}, 
@@
 Also, move all superscript numbers to subscripts.
-Then the apparent occurrence rate is
+Then the apparent rate density is
 \begin{equation}
-\Lambda\a(r\a) = \frac{1}{1+\mu}
+\Gamma\a(r\a) = \frac{1}{1+\mu}
 \left(
-    \Lambda_0(r\a) +
+    \Gamma_0(r\a) +
     \mu \left[
         \int \frac{{\rm d}q}{\mathcal{A}(q)} f(q) 
-        \Lambda_1\left( \frac{r\a}{\mathcal{A}(q)} \right)
+        \Gamma_1\left( \frac{r\a}{\mathcal{A}(q)} \right)
         +
         \int \frac{q {\rm d}q}{\mathcal{B}(q)} f(q)
-        \Lambda_2\left(\frac{r\a}{\mathcal{B}(q)}\right) q^{2/3}
+        \Gamma_2\left(\frac{r\a}{\mathcal{B}(q)}\right) q^{2/3}
     \right]
@@
 
-We have $f(q)=\delta(q-1)$. The apparent rate is
+We have $f(q)=\delta(q-1)$. The apparent rate density is
 \begin{align}
-\Lambda\a(r\a)
+\Gamma\a(r\a)
 ={1\over 1+\mu(\mathrm{BF})}
-\left\{\Lambda_0(r\a)
-+\mu(\mathrm{BF})\cdot \sqrt{2}\cdot\left[\Lambda_1(\sqrt{2}\,r\a)
-+\Lambda_2(\sqrt{2}\,r\a)\right]
+\left\{\Gamma_0(r\a)
++\mu(\mathrm{BF})\cdot \sqrt{2}\cdot\left[\Gamma_1(\sqrt{2}\,r\a)
++\Gamma_2(\sqrt{2}\,r\a)\right]
 \right\},
@@
 
-If $\Lambda_i(r, M)=Z_i\cdot\delta(r-r_0)$ (all the planets have the same 
+If $\Gamma_i(r, M)=Z_i\cdot\delta(r-r_0)$ (all the planets have the same 
 radius), by using the identity $\delta(ax+b)=\delta(x+b/a)/|a|$,
 \begin{align}
-	\Lambda\a(r\a)
+	\Gamma\a(r\a)
 	={1 \over 1+\mu(\mathrm{BF})}
@@
 \end{align}
-This reproduces Eq.(9) of the draft (after removing the $p_{\rm det}$ terms).
+This reproduces Eq.(9) of the draft (after removing the $p_{\rm det}$ 
+terms)\footnote{
+The above equation also follows by just thinking about the problem and 
+explicitly writing out the answer (cf. LB's handwritten notes 
+\texttt{2017/11/26.9}), though the formal derivation is a good check.
+}.
 In the limit of $\mathrm{BF}\to1$ ($\mu\to\infty$), the above formula yields 
-$\Lambda\a=(Z^1+Z^2)\,\delta(r\a-{r_0/\sqrt{2}})$.
-
-Eq.~\ref{eq:model1_apparent_rate} is technically abusing notation, because 
-$\Lambda$ must be dimensionless, and $\delta(r-r_0)$ has units 
-of inverse length.
-Since the equation is meant to convey the idea: ``at a given apparent radius, 
-the apparent number of planets per star is $x$'', and the delta function is 
-more succinct than listing out discrete cases, we leave it as-is.
+$\Gamma\a=(Z^1+Z^2)\,\delta(r\a-{r_0/\sqrt{2}})$.
 
@@
 
-Imagine instead that we took $\Lambda_i(r,M) = Z_i f(r) = Z_i 
+Imagine instead that we took $\Gamma_i(r,M) = Z_i f(r) = Z_i 
 r^\delta/\mathcal{N}_r$, for $f(r)$ the radius shape function, 
@@
 planets per star.
-From Eq.~\ref{eq:apparent_rate_twin_binary}, we get an apparent rate
+From Eq.~\ref{eq:apparent_rate_twin_binary}, we get an apparent rate density
 \begin{equation}
-\Lambda_a(r_a) = \frac{r_a^\delta}{\mathcal{N}_r} \left[
+\Gamma_a(r_a) = \frac{r_a^\delta}{\mathcal{N}_r} \left[
 \frac{Z_0}{1+\mu({\rm BF})}
@@
 \right].
+\label{eq:model5_apparent_rate_density}
 \end{equation}
@@
 Consider the case when the $Z_i$'s are identical. If we compare 
-$\Lambda_a(r_a)$ with $\Lambda(r)$, we must impose that $r_a$ and $r$ are 
+$\Gamma_a(r_a)$ with $\Gamma(r)$, we must impose that $r_a$ and $r$ are 
 indistinguishable (i.e.: the observer cannot tell them apart).
-Note that the true rate is
+Note that the true rate density is
 \begin{equation}
-\Lambda(r) = \frac{r^\delta}{\mathcal{N}_r} \left[
+\Gamma(r) = \frac{r^\delta}{\mathcal{N}_r} \left[
 \frac{Z_0}{1+2\mu} + \frac{\mu}{1+2\mu} (Z_1+Z_2)
@@
 \begin{equation}
-X_\Lambda \equiv \left. \frac{\Lambda_a(r_a)}{\Lambda(r)} 
+X_\Gamma \equiv \left. \frac{\Gamma_a(r_a)}{\Gamma(r)} 
 \right|_{r_a\rightarrow r}
@@
 For the case of ${\rm BF}=0.1$, $\mu\approx 0.153$. Taking $\delta=-2.92$ from 
-Howard et al. (2012),  we get a correction factor $X_\Lambda = 
-\Lambda_a/\Lambda = 1.06$.
-In other words, the apparent rate is an {\it over}estimate of the true rate, 
-with a relative error of 6\%.
+Howard et al. (2012),  we get a correction factor $X_\Gamma = 
+\Gamma_a/\Gamma = 1.06$.
+In other words, the apparent rate density is an {\it over}estimate of the true 
+rate density, with a relative error of 6\%.
 
 As a side-note, this particular model (twin binaries, power law planet 
-distribution) is a good unit test for the numerics. As of git commit 
-\texttt{9b8f55c}, the two agree.
+distribution) is a good unit test for the numerics.
+More realistically, we'll take a power law above some cutoff (to avoid the 
+divergence for $\delta<0$), but Eq.~\ref{eq:model5_apparent_rate_density} will 
+tell us the apparent rate density within the region of parameter space where 
+only the power law matters.
 
@@
 This gives a value of $\mu({\rm BF})$ stated in Eq.~\ref{eq:mu_final}.
-Now recall Eq.~\ref{eq:simple_apparent_occ_rate} for the apparent occurrence 
-rate. We restate it here:
+Now recall Eq.~\ref{eq:simple_apparent_occ_rate} for the apparent rate 
+density. We restate it here:
 \begin{equation}
-\Lambda\a(r\a) = \frac{1}{1+\mu}
+\Gamma\a(r\a) = \frac{1}{1+\mu}
 \left(
-\Lambda_0(r\a) +
+\Gamma_0(r\a) +
 \mu \left[
 \int \frac{{\rm d}q}{\mathcal{A}(q)} f(q) 
-\Lambda_1\left( \frac{r\a}{\mathcal{A}(q)} \right)
+\Gamma_1\left( \frac{r\a}{\mathcal{A}(q)} \right)
 +
 \int \frac{q {\rm d}q}{\mathcal{B}(q)} f(q)
-\Lambda_2\left(\frac{r\a}{\mathcal{B}(q)}\right) q^{2/3}
+\Gamma_2\left(\frac{r\a}{\mathcal{B}(q)}\right) q^{2/3}
 \right]
@@
 \subsubsection{Same Planets (Model \# 2)}
-For our ``Model \#2'', we again want $\Lambda_i(r) = Z_i \cdot \delta(r-r_0)$.
+For our ``Model \#2'', we again want $\Gamma_i(r) = Z_i \cdot \delta(r-r_0)$.
 To achieve this, write
@@
 I_1(r_a) &\equiv \int \frac{{\rm d}q}{\mathcal{A}(q)} f(q) 
-    \Lambda_1\left( \frac{r\a}{\mathcal{A}(q)} \right)
+    \Gamma_1\left( \frac{r\a}{\mathcal{A}(q)} \right)
+    \label{eq:defn_I1}
     \\
 &= \frac{1}{\mathcal{N}_q} \int {\rm d}q\, q^\beta (1+q^\alpha)^2
-    \Lambda_1(r_a (1+q^\alpha)^{1/2})
+    \Gamma_1(r_a (1+q^\alpha)^{1/2})
     \\
@@
 I_2(r_a) &\equiv \int \frac{q {\rm d}q}{\mathcal{B}(q)} f(q)
-\Lambda_2\left(\frac{r\a}{\mathcal{B}(q)}\right) q^{2/3}
+\Gamma_2\left(\frac{r\a}{\mathcal{B}(q)}\right) q^{2/3}
+\label{eq:defn_I2}
 \\
@@
 
-Assume now that
+Power law planets, a realistic mass ratio distribution.
+In other words, now assume
 \begin{equation}
-    \Lambda(r) \sim r^\delta
+    \Gamma_i(r,M) = Z_i f(r) = Z_i r^\delta / \mathcal{N}_r.
 \end{equation}
-and keep calculating...
+Surprisingly, this might give more insight than Model \#2.
+
+From Eq.~\ref{eq:simple_apparent_occ_rate}, we can write
+\begin{equation}
+\Gamma\a(r\a) = \frac{1}{1+\mu} \left(
+\Gamma_0(r\a) + \mu  \left[
+I_1(r_a) + I_2(r_a)
+\right]
+\right),
+\end{equation}
+where $I_1(r_a)$ and $I_2(r_a)$ are defined in the same way as in 
+Eqs.~\ref{eq:defn_I1} and~\ref{eq:defn_I2}.
+Doing the calculation, we find
+\begin{equation}
+I_1(r\a) = \frac{Z_1}{\mathcal{N}_q \mathcal{N}_r} r_a^\delta
+\int {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta}{2}+2}
+\end{equation}
+and
+\begin{equation}
+I_2(r\a) = \frac{Z_2}{\mathcal{N}_q \mathcal{N}_r} r_a^\delta
+\int {\rm d}q\,q^{\beta+\delta+\frac{8}{3}} 
+               (1+q^\alpha)^{\frac{3}{2}}
+               (1+q^{-\alpha})^{\frac{\delta+1}{2}}.
+\end{equation}
+The net effect of binarity is to just {\it scale} the overall distribution!
+
+Note that the true rate density is
+\begin{equation}
+\Gamma(r) = \frac{r^\delta}{\mathcal{N}_r} \left[
+\frac{Z_0}{1+2\mu} + \frac{\mu}{1+2\mu} (Z_1+Z_2)
+\right].
+\end{equation}
+The rate density correction factor, $X_\Gamma = \Gamma\a/\Gamma$, will be
+\begin{align}
+X_\Gamma &\equiv \left. \frac{\Gamma_a(r_a)}{\Gamma(r)} 
+\right|_{r_a\rightarrow r} \\
+&=
+\frac{1+2\mu}{3(1+\mu)}
+\left[1 + \mu
+\left(
+\int {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta}{2}+2} +
+\int {\rm d}q\,q^{\beta+\delta+\frac{8}{3}} 
+    (1+q^\alpha)^{\frac{3}{2}}
+    (1+q^{-\alpha})^{\frac{\delta+1}{2}}
+\right)\right].
+\end{align}
+
+For $\alpha = 3.5$, $\beta=0$, $\delta=-2.92$, the term in $(\ldots)\approx 
+1.41425 \approx \sqrt{2}$, where the latter surprising numerical fluke holds 
+to the first four decimal places.
+For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma = 1.28$, an apparent rate 
+which is {\it higher} than the true rate by 28\%!
+
+More realistically, we'll take a power law above some cutoff (to avoid the 
+divergence for $\delta<0$), but nonetheless the above indicates we're going to 
+need to write a different argument about whether binarity might explain the HJ 
+rate discrepancy (apparently, it goes the wrong way!)
 

### 2017-12-04 sandbox/note_km.tex
km note: update discussion of "true occ rate"

@@
 indistinguishable (i.e.: the observer cannot tell them apart).
-Note that the true rate density is
+Note that the true rate density for stars selected in the sample is
 \begin{equation}
-\Gamma(r) = \frac{r^\delta}{\mathcal{N}_r} \left[
+\Gamma_{\rm sel}(r) = \frac{r^\delta}{\mathcal{N}_r} \left[
 \frac{Z_0}{1+2\mu} + \frac{\mu}{1+2\mu} (Z_1+Z_2)
-\right]
+\right],
 \end{equation}
-We then get a correction factor
+while the true rate density for a volume-limited sample of stars is
 \begin{equation}
-X_\Gamma \equiv \left. \frac{\Gamma_a(r_a)}{\Gamma(r)} 
-\right|_{r_a\rightarrow r}
-=
-\frac{2^{\frac{\delta}{2}+2}\mu + 1}{\mu + 1}.
+\Gamma_{\rm vl}(r) = \frac{r^\delta}{\mathcal{N}_r} \left[
+\frac{Z_0}{1+2(n_b/n_s)} + \frac{(n_b/n_s)}{1+2(n_b/n_s)} (Z_1+Z_2)
+\right],
 \end{equation}
+for $n_b$ and $n_s$ the number density of binaries and singles in a 
+volume-limited sample.
 
+The stand-alone term ``true rate density'' is ill defined, and should probably 
+be avoided.
+In different contexts, it might refer to either a) 
+$\Gamma_{\rm sel}(r)$, b) $\Gamma_{\rm vl}(r)$, or even c) $\Gamma_0(r)$, the 
+rate around singles.
+The meaning that most people probably {\it want} true rate density to have is
+$\Gamma_0(r)$~---~simply ``I have a star that is single; how many planets are 
+there?''.
+This is also a sensible definition because it is {\it independent} of any 
+complications of planet formation that would make $Z_1$ or $Z_2$ different 
+from $Z_0$.
+One way to deal with this, rather than making the arbitrary choice, would be 
+to just plot out all the possible options.
+
+We could define a ``correction factor'' relative to $\Gamma_0$, or to 
+$\Gamma_{\rm sel}$, or to $\Gamma_{\rm vl}$.
+If the $Z_i$'s are equal, these are all identical:
+\begin{align}
+\notag
+X_\Gamma &\equiv 
+\left. \frac{\Gamma_a(r_a)}{\Gamma_0(r)} 
+\right|_{r_a\rightarrow r,\ Z_i{\rm 's}\ {\rm equal}} \\
+\notag&=
+\left. \frac{\Gamma_a(r_a)}{\Gamma_{\rm sel}(r)} 
+\right|_{r_a\rightarrow r,\ Z_i{\rm 's}\ {\rm equal}} \\
+\notag&=
+\left. \frac{\Gamma_a(r_a)}{\Gamma_{\rm vl}(r)} 
+\right|_{r_a\rightarrow r,\ Z_i{\rm 's}\ {\rm equal}} \\
+&=
+\frac{1 + 2^{\frac{\delta+3}{2}}\mu}{1 + \mu}.
+\end{align}
 For the case of ${\rm BF}=0.1$, $\mu\approx 0.153$. Taking $\delta=-2.92$ from 
 Howard et al. (2012),  we get a correction factor $X_\Gamma = 
-\Gamma_a/\Gamma = 1.06$.
-In other words, the apparent rate density is an {\it over}estimate of the true 
-rate density, with a relative error of 6\%.
+\Gamma_a/\Gamma = 1.004$.
+In other words, the apparent rate density is an {\it over}estimate of the rate 
+density of selected stars, with a relative error $\delta \Gamma = |\Gamma - 
+\Gamma\a | / \Gamma$ of 0.4\%.
 
@@
 
-Note that the true rate density is
+Note that the true rate density for the selected stars is
 \begin{equation}
-\Gamma(r) = \frac{r^\delta}{\mathcal{N}_r} \left[
+\Gamma_{\rm sel}(r) = \frac{r^\delta}{\mathcal{N}_r} \left[
 \frac{Z_0}{1+2\mu} + \frac{\mu}{1+2\mu} (Z_1+Z_2)
@@
 \end{equation}
-The rate density correction factor, $X_\Gamma = \Gamma\a/\Gamma$, will be
+The correction factor with respect to selected stars, $X_\Gamma = 
+\Gamma\a/\Gamma_{\rm sel}$, will be
 \begin{align}
-X_\Gamma &\equiv \left. \frac{\Gamma_a(r_a)}{\Gamma(r)} 
-\right|_{r_a\rightarrow r} \\
+X_\Gamma &\equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_{\rm sel}(r)} 
+\right|_{r_a\rightarrow r,\ Z_i{\rm 's\ equal}} \\
 &=
@@
 to the first four decimal places.
-For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma = 1.28$, an apparent rate 
-which is {\it higher} than the true rate by 28\%!
+For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma_{\rm sel} = 1.28$, an 
+apparent rate which is {\it higher} than the true rate by 28\%!
+Note that this result is the same as $\Gamma\a/\Gamma0$ and 
+$\Gamma\a/\Gamma_{\rm vl}$ in the limit where all the $Z_i$'s are equal.
 

### 2017-12-05 src/numerical_models.py
update comments

@@ -666,11 +666,11 @@ def run_unit_tests(
             print('\n'*10)
 
         # Compare the analytic and numeric (apparent) Λ_a(r_a) distributions,
-        # above r_a ~= 2r_\oplus and below r_pu/sqrt(2).  (I was too lazy to
-        # derive the analytic form from r_pu/sqrt(2) to r_pu, but you expect to
-        # see a drop in the numeric value because of those HJs being diluted,
-        # but it's a small effect and the resulting numerics look fine, CF. the
-        # "temp" test plots below).
+        # above r_a ~= 2r_\oplus and below r_pu/sqrt(2).  (I didn't derive the
+        # analytic form from r_pu/sqrt(2) to r_pu, but you expect to see a drop
+        # in the numeric value because of those HJs being diluted, but it's a
+        # small effect and the resulting numerics look fine, CF. the "temp"
+        # test plots below).
 
         del vals_num, vals_anal
         Λ_a_num = np.array(inferred_dict['Λ'])

### 2017-12-05 paper/introduction.tex
WIP paper commit

@@
 Ignoring stellar multiplicity, they perform a signal-to-noise limited transit 
-survey and detect $N_{\rm det}$ signals that seem to be from the desired 
-class of planet.
-They count the apparent number of selected stars, $N_\star$.
-Assuming their survey is limited by Poisson noise, the group computes
-their detection efficiency $p_{\rm det}$ as a function of planetary and 
-stellar properties, in order to know which of the selected stars were
-searchable.
+survey, and detect a set of planets that appear to be of the desired class.
+They then choose the stars (among those initially surveyed) around which the 
+planets of interest appeared to be searchable.
 Correcting for the geometric transit probability $p_{\rm tra}$, they report an 
-apparent occurrence rate $\Lambda_{\rm a}$:
+apparent rate density,
 \begin{equation}
-\Lambda_{\rm a} = \frac{N_{\rm det}}{N_\star} \times \frac{1}{p_{\rm tra}}
-								  \times \frac{1}{p_{\rm det}}.
+\Gamma\a(\pp\a, \ps\a) = \frac{N_{\rm det}(\pp\a, \ps\a)}{N_{\rm s,a}(\pp\a, 
+    \ps\a)} \times \frac{1}{p_{\rm tra}(\pp\a, \ps\a)}.
 \label{eq:wouldnt_it_be_nice}
 \end{equation}
+where $\pp\a$, $\ps\a$ are the apparent planetary and stellar parameters, 
+respectively.
+Here $N_{\rm det}(\pp\a, \ps\a)$ is the number of 
+detected planets with parameters $\pp\a,\ps\a$, per unit $\pp\a$ and $\ps\a$. 
+The quantity $N_{\rm s,a}(\pp\a, \ps\a)$ is the number of unresolved 
+point-sources on the sky the appear to be searchable.
 
@@
 term in Eq.~\ref{eq:wouldnt_it_be_nice}.
-There are errors in $N_{\rm det}$ due to planet radius misclassification.
-There are errors in $N_\star$ because a given selected star might in fact be 
-two stars.
-There are errors in $p_{\rm tra}$ because stars in binaries may have different 
-masses and radii than assumed in the single-star case.
+There are errors in $N_{\rm det}$ due to planet radius 
+misclassification.
+There are errors in $N_{{\rm s,a}}$ because a given point on the sky
+There are errors in $p_{\rm tra}(\pp\a,\ps\a)$ because stars in binaries may 
+have different masses and radii than assumed in the single-star case.
+Binarity might also affect the observers' ability to correctly select 
+searchable stars (but see Sec.~\ref{sec:model_1} for discussion of why this is 
+a second-order effect).
+
 Finally, there are errors in $p_{\rm det}$ because detection efficiencies 

### 2017-12-05 src/numerical_models.py
add code to let r_pu be tunable parameter

@@ -11,9 +11,9 @@ Model #5: twin binary, varying r
 
 Example usage, for each model type:
 >>> python numerical_models.py --modelnumber 1 --ZsubTwo 0.5 --binaryfrac 0.1
->>> python numerical_models.py --modelnumber 2 --ZsubTwo 0.5 --binaryfrac 0.44
->>> python numerical_models.py --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44
->>> python numerical_models.py --modelnumber 4 --ZsubTwo 0.5 --binaryfrac 0.44
+>>> python numerical_models.py --modelnumber 2 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
+>>> python numerical_models.py --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
+>>> python numerical_models.py --modelnumber 4 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
 >>> python numerical_models.py --modelnumber 5 --ZsubTwo 0.5 --binaryfrac 0.1
 
 Alternatively, use a wrapper like `run_numerical_models.py`.
@@ -29,7 +29,7 @@ from math import pi as π
 import os, argparse, decimal
 
 
-def check_inputs(γ, Z_2, model_number, BF):
+def check_inputs(γ, Z_2, model_number, BF, r_pu):
     '''
     Verify that input values are reasonable, otherwise raise errors.
     '''
@@ -46,6 +46,10 @@ def check_inputs(γ, Z_2, model_number, BF):
 
     if not (BF > 0):
         raise AssertionError
+
+    if model_number in [2,3,4]:
+        if not r_pu > 0:
+            raise AssertionError
 
 
 def make_stellar_population(quickrun, model_number, BF, α, β, γ, δ):
@@ -172,7 +176,7 @@ def make_stellar_population(quickrun, model_number, BF, α, β, γ, δ):
 
 
 def make_planet_population(model_number, df, q, is_searchable, Z_0, Z_1, Z_2,
-        N_0, N_1, N_2, δ, debugging=False):
+        N_0, N_1, N_2, δ, r_pu, debugging=False):
     '''
     Given the dataframe of stars, assign planets. Further, assign whether they
     transit, and whether they are detected.
[…]

### 2017-12-05 src/plot_rate_densities_vs_radius.py

@@ -29,14 +29,15 @@ import numpy as np
 from brokenaxes import brokenaxes
 
 def make_plot(model_number, logx=None, logy=None, withtext=None,
-        stdout=False, brokenx=None, Z_2=None, xcut=None):
+        stdout=False, brokenx=None, Z_2=None, xcut=None, r_pu=None):
+
+    assert Z_2 > -1
+
+    plt.close('all')
 
     # Make summary plot
-    if isinstance(Z_2,float) or isinstance(Z_2,int):
-        fname = '../data/numerics/results_model_{:d}_Zsub2_{:.2f}.out'.format(
-                model_number, Z_2)
-    else:
-        fname = '../data/results_model_'+repr(model_number)+'.out'
+    fname = '../data/numerics/results_model_{:d}_Zsub2_{:.2f}_rpu_{:.1f}.out'.format(
+            model_number, Z_2, r_pu)
 
     df = pd.read_csv(fname)
 
@@ -55,19 +56,21 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
 
     if model_number == 3 or model_number == 4:
         xvals = np.append(0, df['bin_left'])
-        ytrue = np.append(0, df['true_Λ'])
+        ytrueselected = np.append(0, df['true_Λ'])
+        ytruesingle = np.append(0, df['true_single_Λ'])
         yinferred = np.append(0, df['inferred_Λ'])
     elif model_number == 1 or model_number == 2:
         xvals = np.append(df['bin_left'],[1,1.1])
-        ytrue = np.append(df['true_Λ'],[0,0])
+        ytrueselected = np.append(df['true_Λ'],[0,0])
+        ytruesingle = np.append(df['true_single_Λ'],[0,0])
         yinferred = np.append(df['inferred_Λ'],[0,0])
 
-    try:
-        ax.step(xvals, ytrue, where='post', label='true')
-    except:
-        import IPython; IPython.embed()
-
     ax.step(xvals, yinferred, where='post', label='inferred')
+
+    ax.step(xvals, ytrueselected, where='post', label='true (selected)')
+
+    ax.step(xvals, ytruesingle, where='post', label='true (single)',
+            linestyle='--')
 
     if brokenx:
         ax.legend(loc='upper left',fontsize='medium')
[…]

### 2017-12-05 src/run_all_models.sh

@@ -1,5 +1,16 @@
+# "Nominal" models (this just means I arbitrarily decided Z_2 = 0.5)
 python numerical_models.py --modelnumber 1 --ZsubTwo 0.5 --binaryfrac 0.1
-python numerical_models.py --modelnumber 2 --ZsubTwo 0.5 --binaryfrac 0.44
-python numerical_models.py --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44
-python numerical_models.py --modelnumber 4 --ZsubTwo 0.5 --binaryfrac 0.44
-python numerical_models.py --modelnumber 5 --ZsubTwo 0.5 --binaryfrac 0.1
+python numerical_models.py --modelnumber 2 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
+python numerical_models.py --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
+python numerical_models.py --modelnumber 4 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
+python numerical_models.py --modelnumber 5 --ZsubTwo 0.5 --binaryfrac 0.1 --upperradiuscutoff 22.5
+
+# Check vs Z_2
+python numerical_models.py --modelnumber 3 --ZsubTwo 0.0 --binaryfrac 0.44 --upperradiuscutoff 22.5
+python numerical_models.py --modelnumber 3 --ZsubTwo 0.25 --binaryfrac 0.44 --upperradiuscutoff 22.5
+
+# Check vs upper radius cutoff
+python numerical_models.py --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 15.0
+python numerical_models.py --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 17.5
+python numerical_models.py --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 20.0
+python numerical_models.py --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 25.0

### 2017-12-05 results/make_merged.sh
results for r_pu and Z_2 variation study

@@ -4,9 +4,10 @@ pdftk \
   rate_density_vs_radius_model_1_brokenx.pdf \
   rate_density_vs_radius_model_2.pdf \
   rate_density_vs_radius_logs_model_2.pdf \
-  rate_density_vs_radius_model_3_Zsub2_0.5.pdf \
-  rate_density_vs_radius_logs_model_3_Zsub2_0.5.pdf \
-  rate_density_vs_radius_model_3_withtext_Zsub2_0.5.pdf \
+  rate_density_vs_radius_model_3_Zsub2_0.50_rpu_22.5.pdf \
+  rate_density_vs_radius_logs_model_3_Zsub2_0.50_rpu_22.5.pdf \
+  rate_density_vs_radius_model_3_withtext_Zsub2_0.50_rpu_22.5.pdf \
+  rate_density_vs_radius_model_4_xcut.pdf \
   output rates_merged.pdf
 
 # OUTDATED: "error cases" plots.
@@ -19,5 +20,3 @@ pdftk \
 #  errcases_rate_density_vs_radius_logs_model_3_Zsub2_0.5.pdf \
 #  errcases_rate_density_vs_radius_model_3_withtext_Zsub2_0.5.pdf \
 #  output errcases_merged.pdf
-
-

### 2017-12-05 results/model3_fn_of_Z2.sh

@@ -1,0 +1,11 @@
+#!/usr/bin/env bash
+
+pdftk \
+  rate_density_vs_radius_logs_model_3_Zsub2_0.00_rpu_22.5.pdf \
+  rate_density_vs_radius_logs_model_3_Zsub2_0.25_rpu_22.5.pdf \
+  rate_density_vs_radius_logs_model_3_Zsub2_0.50_rpu_22.5.pdf \
+  rate_density_vs_radius_model_3_withtext_Zsub2_0.00_rpu_22.5.pdf \
+  rate_density_vs_radius_model_3_withtext_Zsub2_0.25_rpu_22.5.pdf \
+  rate_density_vs_radius_model_3_withtext_Zsub2_0.50_rpu_22.5.pdf \
+  output rates_fn_of_Z2.pdf
+

### 2017-12-05 results/model3_fn_of_rpu.sh

@@ -1,0 +1,15 @@
+#!/usr/bin/env bash
+
+pdftk \
+  rate_density_vs_radius_logs_model_3_Zsub2_0.50_rpu_15.0.pdf \
+  rate_density_vs_radius_logs_model_3_Zsub2_0.50_rpu_17.5.pdf \
+  rate_density_vs_radius_logs_model_3_Zsub2_0.50_rpu_20.0.pdf \
+  rate_density_vs_radius_logs_model_3_Zsub2_0.50_rpu_22.5.pdf \
+  rate_density_vs_radius_logs_model_3_Zsub2_0.50_rpu_25.0.pdf \
+  rate_density_vs_radius_model_3_withtext_Zsub2_0.50_rpu_15.0.pdf \
+  rate_density_vs_radius_model_3_withtext_Zsub2_0.50_rpu_17.5.pdf \
+  rate_density_vs_radius_model_3_withtext_Zsub2_0.50_rpu_20.0.pdf \
+  rate_density_vs_radius_model_3_withtext_Zsub2_0.50_rpu_22.5.pdf \
+  rate_density_vs_radius_model_3_withtext_Zsub2_0.50_rpu_25.0.pdf \
+  output rates_fn_of_rpu.pdf
+

### 2017-12-11 sandbox/derivation.tex
kvetch over normalization. KM's and LB's agree.
Which is nice, because we approached it from two qualitatively different
directions.

--- 2017-12-04 sandbox/note_km.tex
@@
 n_b,	\quad r\leq d_0\\
-n_b \int_{q_{\rm min}(r)}^1 {\rm d}q\, f_v(q), \quad d_0 < r < \sqrt{2}d_0 \\
+n_b \int_{q_{\rm min}(r)}^1 {\rm d}q\, f_{\rm vl}(q), \quad d_0 < r < 
+\sqrt{2}d_0 \\
 \end{cases}
 \end{equation}
-where $f_v(q)$ is the mass ratio distribution in a volume-limited sample, 
-$q_{\rm min}(r)$ is the minimum mass ratio required to provide sufficient flux 
-for searchability.
+where $f_{\rm vl}(q)$ is the mass ratio distribution in a volume-limited 
+sample, $q_{\rm min}(r)$ is the minimum mass ratio required to provide 
+sufficient flux for searchability.
 Assuming $L\propto M^\alpha$,
@@
 distribution, $I$ takes the form given in Eq.~\ref{eq:dimensionless_integral}.
+
+\subsubsection{Alternative Derivation of $\mu$}
+
+For a given set of $(\delta_{\rm obs}, M\a)$  and $q$, the searchable distance for binaries is larger than singles by $\sqrt{1+L(qM\a)/L(M\a)}$. Thus,
+\begin{equation}
+	{N_d \over N_s^0}=\int_0^1 {n_b\over n_s}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} f(q)\mathrm{d}q
+	=\int_0^1 \frac{{\rm BF}}{1 - {\rm BF}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} f(q)\mathrm{d}q.
+\end{equation}
+If $\mathrm{BF}$ is independent of $q$, $L\sim M^\alpha$, and $f(q)\sim q^\beta$:
+\begin{equation}
+	{N_d \over N_s^0}
+	=\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 \left(1+q^\alpha\right)^{3/2} q^\beta\mathrm{d}q,
+\end{equation}
+which may be written in a closed form using the hypergeometric function. 
+Integrating by parts and using $u\equiv(1+q^\alpha)^{1/2}$, this reduces to
+\begin{align}
+	{N_d \over N_s^0}
+	\notag
+	&=\frac{{\rm BF}}{1 - {\rm BF}} \left(1\over{1+\beta}\right)^2
+	\left\{
+	\left[q^{\beta+1}\left(1+q^\alpha\right)^{3/2}\right]_0^1-{3\over2}\alpha \int_0^1 q^{\alpha+\beta}\left(1+q^\alpha\right)^{1/2} \mathrm{d}q \right\},\\
+	&=\frac{{\rm BF}}{1 - {\rm BF}} \left(1\over{1+\beta}\right)^2
+	\left[ 2^{3/2} - 3 \int_1^{\sqrt{2}} u^2(u^2-1)^{{1+\beta}\over\alpha}\mathrm{d}u \right].
+\end{align}
+For $\beta=0$, the last line is equivalent to Eq.(14).
 
@@
 
-%TODO: PROCEED FROM HERE
+\subsection{Primaries in Binaries}
 
-\subsection{Primaries in Binaries}
+The number of primaries with apparent parameters $(r_a,M_a)$ given the 
+true parameters $(r,M)$ is
+\begin{equation}
+	\mathcal{N}_{\rm s}^1(r_a, M_a; r, M)
+	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r_a, M_a, q; r, M),
+    \label{eq:fancyN_s_1}
+\end{equation}
+where $f(q)$ is the binary mass ratio distribution.
 
@@
 \begin{equation}
-	\mathcal{N}_{\rm s}^1(r_a, M_a; r, M) \propto \delta(M_a-M).
+	\mathcal{N}_{{\rm s},q}^1(r_a, M_a, q; r, M) \propto \delta(M_a-M).
 \end{equation}
-In this case, $\mathcal{N}_{\rm s}^1$ is non-zero only at 
+In this case, $\mathcal{N}_{{\rm s},q}^1$ is non-zero only at 
 $r_a=R_a\sqrt{\delta_{\rm obs}}$, 
@@
 	\delta_{\rm obs}
-	= \left[{r\over R(M_a)}\right]^2\times {L(M_a) \over L_{\rm sys}(M_a, q)}.
+	= \left[{r\over R(M_a)}\right]^2\times {L(M_a) \over L_{\rm sys}(M_a, q)}
+	\equiv \left[{r\over R(M_a)}\right]^2\times \mathcal{A}(q,M\a)^2
    \label{eq:delta_obs_primaries} 
 \end{equation}
-The normalization of $\mathcal{N}_{\rm s}^1$ is given by the number of 
-binaries that are searchable for a signal $\delta_{\rm obs}$:
+The normalization of $\mathcal{N}_{{\rm s},q}^1$ is given by the number of 
+binaries that are searchable for a signal $\delta_{\rm obs}$ and have the mass ratio $q$ (cf. 1.3.2):
 \begin{equation}
 	N_{\rm s}^0(\delta_{\rm obs}, 
-	L(M_a))\cdot\mu(\mathrm{BF},M_a).
+	L(M_a))\cdot
+	{n_b\over n_s}\left[L_{\rm sys}(M_a, q) \over L(M\a)\right]^{3/2}
+	=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))
+	\cdot \frac{{\rm BF}}{1 - {\rm BF}} \cdot {1 \over \mathcal{A}(q,M\a)^3}.
+    \label{eq:primary_normalization}
 \end{equation}
-Thus, the number of primaries with apparent parameters $(r_a,M_a)$ given the 
-true parameters $(r,M)$ is
-\begin{equation}
-	\mathcal{N}_{\rm s}^1(r_a, M_a; r, M)
-	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r_a, M_a; r, M; q),
-    \label{eq:fancyN_s_1}
-\end{equation}
-where $f(q)$ is the binary mass ratio distribution in the SNR-limited sample 
-and
+
+Thus,
 \begin{align}
 	\notag
-	\mathcal{N}_{{\rm s}, q}^1(r_a, M_a; r, M; q)
-	&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))\cdot\mu(\mathrm{BF},M_a)\\
-	&\times\delta \left(r_a-r\sqrt{{L(M_a) \over L_{\rm sys}(M_a, 
-	q)}}\right)\delta(M_a-M).
+	\mathcal{N}_{{\rm s}, q}^1(r_a, M_a, q; r, M)
+	&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))
+	\cdot \frac{{\rm BF}}{1 - {\rm BF}} \cdot {1 \over \mathcal{A}(q,M\a)^3}\\
+	&\times\delta \left[r_a-r\mathcal{A}(q,M\a)\right]\delta(M_a-M).
+	%&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))\cdot\mu(\mathrm{BF},M_a)\\
+	%&\times\delta \left(r_a-r\sqrt{{L(M_a) \over L_{\rm sys}(M_a, q)}}\right)\delta(M_a-M).
 \label{eq:N_s_1}
@@
 about this dependence.
-As discussed in the main text, in Eq.~\ref{eq:fancyN_s_1} we will have $f(q) 
-\sim q^\beta (1+q^\alpha)^{3/2}$.
+In Eq.~\ref{eq:fancyN_s_1}, we will have $f(q) \sim q^\beta $, the 
+volume-limited mass ratio distribution (Eq.~\ref{eq:primary_normalization} 
+accounts for the Malmquist bias).
 
@@
 \begin{equation}
-	\mathcal{N}_{\rm s}^2(r_a, M_a; r, M)
+	\mathcal{N}_{{\rm s},q}^2(r_a, M_a, q; r, M)
 	\propto \delta\left(M_a-{M\over q}\right).
@@
 	\mathcal{N}_{\rm s}^2(r_a, M_a; r, M)
-	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r_a, M_a; r, M; q),
+	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r_a, M_a, q; r, M),
 \end{equation}
@@
 	\mathcal{N}_{\rm s}^2(r_a, M_a; r, M; q)
-	%&=N_{\rm s}(\delta_{\rm obs}, L(M_a)) \left[L_{\rm sys}(M_a, q) \over 
-	%L(M_a) 
-	%\right]^{3/2}\\
-	&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))\cdot\mu(\mathrm{BF},M_a)\\
+	%&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))\cdot\mu(\mathrm{BF},M_a)\\
+	&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a)) \cdot \frac{{\rm BF}}{1 - {\rm BF}} \cdot {1 \over \mathcal{A}(q,M\a)^3}\\
 	&\times \delta \left(r_a-r\sqrt{ \left[{R(M_a)\over R(qM_a)}\right]^2 
@@
 	\over L_{\rm sys}(M_a, q)} }\right)\delta\left(M_a-{M\over q}\right).
+\label{eq:mathcal_N_s_2}
 \end{align}
@@
 $r\a$, per $M\a$.
+
+One might also worry because in Eq.~\ref{eq:mathcal_N_s_2}, it is hard to see 
+any explicit indication that secondaries are harder to search for planets of a 
+given true size than primaries (or singles).
+This piece of intuition is accounted in the delta functions.
+If one were to instead go through the exercise of saying ``how many searchable 
+secondaries are there in terms of the {\it true} parameters?'' you would get 
+exactly the same answer\footnote{LB did this, in his handwritten notes
+\texttt{2017/12/09.0-2017/12/11/.0}}.
 
@@
 	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, 
-	q}^1(r\a, M\a; r, M; q)\cdot\Gamma^1(r, M) \cdot p_{\rm tra}(M)\\
+	q}^1(r\a, M\a, q; r, M)\cdot\Gamma^1(r, M) \cdot p_{\rm tra}(M)\\
 	&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
-	\mu(\mathrm{BF}, M\a) \int {\mathrm{d}q \over 
-	\mathcal{A}}\,f(q)\,\Gamma^1(r_a/\mathcal{A}, M\a),
-	%\left[L_{\rm sys}(M_a, q) \over L(M_a) \right]^{3/2},
+	{\mathrm{BF}\over{1-\mathrm{BF}}} \int {\mathrm{d}q \over 
+	\mathcal{A}^4}\,f(q)\,\Gamma^1\left({r_a\over\mathcal{A}}, M\a\right),
 \end{align}
@@
 	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^2(r\a, M\a; r, M)
-	\cdot\Gamma^2(r, M) \cdot p_{\rm tra}(M)
-    \\
+	\cdot\Gamma^2(r, M) \cdot p_{\rm tra}(M)\\
 	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, 
-	q}^2(r\a, M\a; r, M; q)\cdot\Gamma^2(r, M) \cdot p_{\rm tra}(M)
-    \\
-    &= N\s^0(\delta_{\rm obs},L(M\a)) \mu({\rm BF},M\a)
-    \int {\rm d}r{\rm d}q\, q f(q) \delta(r_a - r\mathcal{B}) 
+	q}^2(r\a, M\a, q; r, M)\cdot\Gamma^2(r, M) \cdot p_{\rm tra}(M)\\
+    &= N\s^0(\delta_{\rm obs},L(M\a)) \cdot \frac{{\rm BF}}{1 - {\rm BF}}
+    \int {{\rm d}r{\rm d}q\over \mathcal{A}^3}\, q f(q) \delta(r_a - r\mathcal{B}) 
     \Gamma^2(r,qM\a) 
@@
 	&=%N_{\rm s}(\delta_{\rm obs}, L(M_a)
-	N\s^0(\delta_{\rm obs}, L(M\a))\cdot\mu(\mathrm{BF}, M\a)
-	\int {q \mathrm{d}q \over \mathcal{B}}\,f(q)\,\Gamma^2(r_a/\mathcal{B}, 
+	N\s^0(\delta_{\rm obs}, L(M\a))\cdot \frac{{\rm BF}}{1 - {\rm BF}}
+	\int {q \mathrm{d}q \over {\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma^2(r_a/\mathcal{B}, 
 	qM\a)\,p_{\rm 
@@
    \left\{ \Gamma^0(r\a, M\a)+ 
-\mu(\mathrm{BF}, M\a)
-\left[ \int {\mathrm{d}q \over \mathcal{A}}\,f(q)\,\Gamma^1\left({r\a\over 
+\frac{{\rm BF}}{1 - {\rm BF}}
+\left[ \int {\mathrm{d}q \over \mathcal{A}^4}\,f(q)\,\Gamma^1\left({r\a\over 
     \mathcal{A}}, 
@@
 & \quad\quad\quad\quad\quad \left.\left.
-+\int {q \mathrm{d}q \over \mathcal{B}}\,f(q)\,\Gamma^2\left({r\a\over 
++\int {q \mathrm{d}q \over {\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma^2\left({r\a\over 
 \mathcal{B}}, 
@@
 \end{align}
+
+\edit1{MODIFIED UP TO THIS POINT}
+
+\edit2{TODO: follow the above analytics to below limiting cases}
 

### 2017-12-11 sandbox/did_we_normalize_correctly.tex
kvetch over normalization. KM's and LB's agree.
Which is nice, because we approached it from two qualitatively different
directions.

\documentclass[12pt,modern]{aastex61}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{comment}

\begin{document}

\newcommand{\pt}{\theta}
\newcommand{\pa}{\theta_{\rm a}}
\newcommand{\pn}{\theta_0}

\newcommand{\pp}{\mathcal{P}}
\newcommand{\ps}{\mathcal{S}}
\renewcommand{\a}{_{\rm a}}
\newcommand{\s}{_{\rm s}}

\section{Did we normalize the number of searchable stars correctly?}

Recall how we evaluated
\begin{align}
N_{\rm det}(r\a, M\a) &=
\sum_i N_{\rm det}^i(r\a, M\a) \\
N_{\rm det}(r\a, M\a)
&=
\sum_i \int \mathrm{d}r \mathrm{d}M \,
\mathcal{N}_{\rm s}^i(r\a,M\a; r,M)
\cdot\Gamma^i(r,M) \cdot p_{\rm tra}(r,M).
\end{align}
The fancy-looking $\mathcal{N}_{\rm s}^i(r\a,M\a; r,M)$ term is supposed to 
mean ``the number of searchable stars of type $i$ (per unit $r\a,M\a$) that 
give $(r\a,M\a)$ when the true system actually has $(r,M)$''.

For $i=0$, we wrote
\begin{equation}
\mathcal{N}_{\rm s}^0(r\a,M\a; r,M)
=\delta(r\a-r)\delta(M\a-M) N\s^0(r,M),
\label{eq:simple}
\end{equation}
where $N\s^0(r,M)$ is the number of searchable singles with true parameters 
$(r,M)$.
Note that this $N\s^0(r,M)$ should indeed be written a function of the {\it 
true} parameters, and only once integrated will it give a function of apparent 
parameters.

We then get
\begin{align}
\notag
N_{\rm det}^0(r\a,M\a)
&= \int {\rm d}r{\rm d}M 
	\mathcal{N}_{\rm s}^0(r\a,M\a; r,M) \Gamma^0(r,M) p_{\rm tra}(r,M) \\
\notag
&= \int {\rm d}r{\rm d}M 
\delta(r\a-r)\delta(M\a-M) N\s^0(r,M) \Gamma^0(r,M) p_{\rm tra}(r,M) \\
&= N\s^0(r\a,M\a) \Gamma^0(r\a,M\a) p_{\rm tra}(M\a).
\end{align}

For $i=1$, by definition,
\begin{equation}
N_{\rm det}^1(r\a,M\a) =
\int \mathrm{d}r \mathrm{d}M \,
\mathcal{N}_{\rm s}^1(r\a,M\a; r,M)
\cdot\Gamma^i(r,M) \cdot p_{\rm tra}(r,M).
\end{equation}
Just as before, we must marginalize out the binary distribution:
\begin{equation}
\mathcal{N}_{\rm s}^1(r_a, M_a; r, M)
=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r_a, M_a; r, M; q).
\end{equation}
We can thus write (order of integration does not matter)
\begin{equation}
N_{\rm det}^1(r\a,M\a) =
\int \mathrm{d}r \mathrm{d}M \mathrm{d}q \,
f(q)
\mathcal{N}_{\rm s}^1(r\a,M\a; r,M; q)
\cdot\Gamma^i(r,M) \cdot p_{\rm tra}(r,M).
\label{eq:N_det_1}
\end{equation}
Now I'm pretty sure that we need to write
\begin{equation}
\mathcal{N}_{\rm s}^1(r\a,M\a; r,M; q)
=\delta(r\a-r\mathcal{A}(q))\delta(M\a-M) N\s^1(r,M;q),
\label{eq:less_simple}
\end{equation}
where $\mathcal{A}(q)$ is the necessary correction for dilution, defined 
identically as before, but now $N\s^1(r,M;q)$ is the number of primaries that 
are searchable for planets when the system has true parameters $(r,M,q)$.

This is immediately different from what we've done previously.
We previously wrote
\begin{equation}
	N\s^i(\delta_{\rm obs}, L_{\rm sys}) \propto n_i \delta_{\rm obs}^3 L_{\rm 
		sys}^{3/2},
\end{equation}
where $N\s^i(\delta_{\rm obs}, L_{\rm sys})$ is the number of searchable 
stars of type $i$, given {\it apparent} parameters.

Now, instead, when I write $N\s^1(r,M;q)$, I'm saying: {\it given true 
parameters}, how many searchable primaries are there? I'm pretty sure this 
latter question is the correct one to ask for purposes of determining 
$\mathcal{N}_{\rm s}^1(r\a,M\a; r,M; q)$.
{\bf If you disagree, then don't bother reading the rest}.
Assuming we're asking the right question, let's find out the effect on the 
$\mathcal{N}\s^1$ quantity. First, note
\begin{equation}
d_{\rm det}^1(r,R,M,q) \propto
\left(\frac{L(M\a)}{L(M\a)+L(qM\a)}\right)
\cdot \left(\frac{r}{R}\right)^2
\cdot \left(L(M\a)+L(qM\a)\right)^{1/2},
\end{equation}
where I ignored the $T_{\rm dur}$ dependence, and wrote the terms for 
dilution, geometric transit depth, and system luminosity.
Taking the cube,
\begin{equation}
N\s^1(r,R,M,q) \propto
n_b
\frac{L(M\a)^3}{(L(M\a) + L(qM\a))^{3/2}}
\left(\frac{r}{R}\right)^6.
\label{eq:N_s_real_parameters}
\end{equation}
This number of searchable stars, given the true system parameters, will be 
what goes into determining the number of detections (given apparent 
parameters).

I think this also means $f(q)$ in Eq.~\ref{eq:N_det_1} should be $f_{\rm 
vl}(q)$~---~the volume limited binary distribution.
Before, we (I) said it would be magnitude limited.
The reasoning for why it must be volume-limited will become clear in 
Eq.~\ref{eq:mag_limit_becomes_clear}, where it will be evident that doing 
otherwise would be erroneously accounting for the Malmquist bias twice.

Let's compute the contribution of primaries to the overall rate density,
\begin{equation}
\Gamma\a^1(r\a,M\a) = \frac{N_{\rm det}^1(r\a,M\a)}{N_{\rm s,a}(r\a,M\a)} 
\frac{1}{p_{\rm tra}(r\a,M\a)}.
\label{eq:Gamma_a_1}
\end{equation}
As before, we have
\begin{equation}
N_{\rm s,a}(r\a,M\a) = N\s^0(r\a,M\a)(1+\mu),
\end{equation}
where $\mu \equiv N_d/N_s^0$ is, as we've agreed before, a number that 
is determined by the binary mass ratio distribution, the binary fraction, and 
nothing else.

From Eq.~\ref{eq:N_det_1} and Eq.~\ref{eq:less_simple}, we now get
\begin{equation}
N_{\rm det}^1(r\a,M\a) =
p_{\rm tra}(M\a)
\int \frac{{\rm d}q\,f_{\rm vl}(q)}{\mathcal{A}(q)}
N\s^1\left(r=\frac{r\a}{\mathcal{A}(q)},M=M\a, q=q\right)
\Gamma^1\left(\frac{r\a}{\mathcal{A}(q)},M\a\right),
\end{equation}
where I'm keeping the explicit $N\s^1(r,M,q)$ dependence to indicate I am 
referring to Eq.~\ref{eq:N_s_real_parameters}, the number of searchable 
primaries given real parameters.
Plugging into Eq.~\ref{eq:Gamma_a_1},
\begin{align}
\Gamma\a^1(r\a,M\a) &=
\frac{1}{1+\mu}
\int \frac{{\rm d}q\,f_{\rm vl}(q)}{\mathcal{A}(q)}
\frac{N\s^1\left(r=\frac{r\a}{\mathcal{A}(q)},M=M\a, q=q\right)}
{N\s^0(r\a,M\a)}
\Gamma^1\left(\frac{r\a}{\mathcal{A}(q)},M\a\right) \\
&=
\frac{(n_b/n_s)}{1+\mu}
\int \frac{{\rm d}q\,f_{\rm vl}(q)}{\mathcal{A}(q)}
\left(\frac{L(M\a)}{L(M\a)+L(qM\a)}\right)^{3/2}
\mathcal{A}(q)^{-6}
\Gamma^1\left(\frac{r\a}{\mathcal{A}(q)},M\a\right) 
\label{eq:mag_limit_becomes_clear}\\
&=
\frac{(n_b/n_s)}{1+\mu}
\int {\rm d}q\,f_{\rm vl}(q)
\mathcal{A}(q)^{-4}
\Gamma^1\left(\frac{r\a}{\mathcal{A}(q)},M\a\right).
\end{align}

If you compute out the various limiting cases, it turns out for $f_{\rm 
vl}(q)=\delta(q-1)$, the above is exactly the same as what we had before.
However, if $f_{\rm vl}(q)=q^\beta / \mathcal{N}_q$, it is slightly different.

\end{document}

### 2017-12-11 sandbox/derivation.tex
propagate normalization fix until derivation end

@@
 \begin{equation}
-	{N_d \over N_s^0}
+	\mu = {N_d \over N_s^0}
 	=\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 \left(1+q^\alpha\right)^{3/2} q^\beta\mathrm{d}q,
@@
 \begin{align}
-	{N_d \over N_s^0}
+	\mu = {N_d \over N_s^0}
 	\notag
@@
 
-\edit1{MODIFIED UP TO THIS POINT}
-
-\edit2{TODO: follow the above analytics to below limiting cases}
-
 \subsubsection{Simplifying above general result}
-To simplify, drop the explicit $M_a$ and BF 
-dependences, and assume $R\propto M$, so $R(qM_a)/R(M_a) = q$.
-Also, move all superscript numbers to subscripts.
+To simplify, drop the explicit BF dependences, and assume $R\propto M$, so 
+$R(qM_a)/R(M_a) = q$. Also, move all superscript numbers to subscripts.
 Then the apparent rate density is
-\begin{equation}
-\Gamma\a(r\a) = \frac{1}{1+\mu}
-\left(
-    \Gamma_0(r\a) +
-    \mu \left[
-        \int \frac{{\rm d}q}{\mathcal{A}(q)} f(q) 
-        \Gamma_1\left( \frac{r\a}{\mathcal{A}(q)} \right)
-        +
-        \int \frac{q {\rm d}q}{\mathcal{B}(q)} f(q)
-        \Gamma_2\left(\frac{r\a}{\mathcal{B}(q)}\right) q^{2/3}
-    \right]
-\right).
+\begin{align}
+\notag
+\Gamma\a(r\a,M\a) &= {1\over 1+\mu}\times
+\left\{ \Gamma^0(r\a, M\a)+ 
+\frac{{\rm BF}}{1 - {\rm BF}}
+\left[ \int {\mathrm{d}q \over \mathcal{A}^4}\,f(q)\,\Gamma^1\left({r\a\over 
+    \mathcal{A}}, 
+M\a\right)\,
+\right.   
+\right. \\
+& \quad\quad\quad\quad\quad \left.\left.
++\int {q \mathrm{d}q \over 
+{\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma^2\left({r\a\over 
+    \mathcal{B}}, 
+qM\a\right)\,
+q^{2/3} \right]	\right\}.  
 \label{eq:simple_apparent_occ_rate}
-\end{equation}
+\end{align}
 For the power law case when $L\sim M^\alpha$,
@@
 
-We have $f(q)=\delta(q-1)$. The apparent rate density is
+We have $f(q)=\delta(q-1)$. Since all stars have the exact same mass (both 
+true mass and apparent mass), we will drop the $M\a$ dependence.
+The apparent rate density is then
 \begin{align}
@@
 \begin{equation}
-	\mu(\mathrm{BF})=\int \mathrm{d}q\,f(q) 
-	{\mathrm{BF}\over{1-\mathrm{BF}}}\left[1+{L(qM\a) \over 
-	L(M\a)}\right]^{3/2}
+	\mu(\mathrm{BF})
+   	=\int_0^1 \frac{{\rm BF}}{1 - {\rm BF}}\left[1+{L(qM\a) \over 
+    L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q
 	=2^{3/2}\cdot{\mathrm{BF}\over{1-\mathrm{BF}}}.
@@
 
-If $\Gamma_i(r, M)=Z_i\cdot\delta(r-r_0)$ (all the planets have the same 
+If $\Gamma_i(r)=Z_i\cdot\delta(r-r_0)$ (all the planets have the same 
 radius), by using the identity $\delta(ax+b)=\delta(x+b/a)/|a|$,
@@
 
-Imagine instead that we took $\Gamma_i(r,M) = Z_i f(r) = Z_i 
+Imagine instead that we took $\Gamma_i(r) = Z_i f(r) = Z_i 
 r^\delta/\mathcal{N}_r$, for $f(r)$ the radius shape function, 
@@
 
-The stand-alone term ``true rate density'' is ill defined, and should probably 
+The stand-alone term ``true rate density'' is ill defined, and should 
 be avoided.
@@
 to just plot out all the possible options.
+In general though, we will give highest preference to $\Gamma_0(r)$, since it 
+can be compared with the results of other surveys.
 
@@
 
-If we assume 
+Now assume $f(q) = q^\beta/\mathcal{N}_q$, for $\mathcal{N}_q$ the 
+normalization.
+As previously noted, if we assume
 \begin{equation}
@@
 \end{equation}
-we find 
+we have 
 \begin{equation}
@@
 density. We restate it here:
-\begin{equation}
-\Gamma\a(r\a) = \frac{1}{1+\mu}
-\left(
-\Gamma_0(r\a) +
-\mu \left[
-\int \frac{{\rm d}q}{\mathcal{A}(q)} f(q) 
-\Gamma_1\left( \frac{r\a}{\mathcal{A}(q)} \right)
-+
-\int \frac{q {\rm d}q}{\mathcal{B}(q)} f(q)
-\Gamma_2\left(\frac{r\a}{\mathcal{B}(q)}\right) q^{2/3}
-\right]
-\right).
-\end{equation}
+\begin{align}
+\notag
+\Gamma\a(r\a,M\a) &= {1\over 1+\mu}\times
+\left\{ \Gamma^0(r\a, M\a)+ 
+\frac{{\rm BF}}{1 - {\rm BF}}
+\left[ \int {\mathrm{d}q \over \mathcal{A}^4}\,f(q)\,\Gamma^1\left({r\a\over 
+    \mathcal{A}}, 
+M\a\right)\,
+\right.   
+\right. \\
+& \quad\quad\quad\quad\quad \left.\left.
++\int {q \mathrm{d}q \over 
+    {\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma^2\left({r\a\over 
+    \mathcal{B}}, 
+qM\a\right)\,
+q^{2/3} \right]	\right\}.
+\end{align}
+
+Since in this model we will have stars with different masses, it makes more 
+sense to keep the explicit ``$M\a$'' dependence in our equations.
 
 \subsubsection{Same Planets (Model \# 2)}
-For our ``Model \#2'', we again want $\Gamma_i(r) = Z_i \cdot \delta(r-r_0)$.
-To achieve this, write
+For our ``Model \#2'', we assume
 \begin{equation}
-f(q) = \frac{q^\beta (1+q^\alpha)^{3/2}}{\mathcal{N}_q},
+\Gamma_i(r,M) = Z_i \cdot \delta(r-r_0) M^\gamma / \mathcal{N}_M,
 \end{equation}
-for $\mathcal{N}_q$ the normalization.
-For $i=1$, call the integral on the left the $[\ldots]$ ``$I_1$''.
+where $\mathcal{N}_M$ has the correct units to make $Z_i$ dimensionless.
+In most cases we'll take $\gamma=0$, but we'll carry it through the 
+calculations here.
+
+For $i=1$, call the integral on the left of the $[\ldots]$ ``$I_1$''.
 Then
 \begin{align}
-I_1(r_a) &\equiv \int \frac{{\rm d}q}{\mathcal{A}(q)} f(q) 
-    \Gamma_1\left( \frac{r\a}{\mathcal{A}(q)} \right)
+I_1(r\a,M\a) &\equiv \int \frac{{\rm d}q}{\mathcal{A}^4} f(q) 
+    \Gamma_1\left( \frac{r\a}{\mathcal{A}}, M\a \right)
     \label{eq:defn_I1}
@@
 &= \frac{1}{\mathcal{N}_q} \int {\rm d}q\, q^\beta (1+q^\alpha)^2
-    \Gamma_1(r_a (1+q^\alpha)^{1/2})
+    \Gamma_1(r_a (1+q^\alpha)^{1/2}, M\a)
     \\
-&= \frac{Z_1}{\mathcal{N}_q} \int {\rm d}q\, q^\beta (1+q^\alpha)^2
+&= \frac{Z_1 M\a^\gamma}{\mathcal{N}_q \mathcal{N}_M} \int {\rm d}q\, q^\beta 
+(1+q^\alpha)^2
     \delta(r_a (1+q^\alpha)^{1/2} - r_0) \\
-&= \frac{Z_1}{\mathcal{N}_q} \frac{2}{\alpha} \frac{r_0}{r_a^2} 
+&= \frac{Z_1 M\a^\gamma}{\mathcal{N}_q \mathcal{N}_M} \frac{2}{\alpha} 
+\frac{r_0}{r_a^2} 
    \left(\left(\frac{r_0}{r_a}\right)^2 -1
@@
        \right)^{\frac{1}{\alpha}} \right) \\
-&= \frac{Z_1}{\mathcal{N}_q} \frac{2}{\alpha} \frac{r_0}{r_a^2}
+&= \frac{Z_1 M\a^\gamma}{\mathcal{N}_q \mathcal{N}_M} \frac{2}{\alpha} 
+\frac{r_0}{r_a^2}
     \left( \left(\frac{r_0}{r_a}\right)^2 - 1  
@@
 \end{equation}
-Eq.~\ref{eq:model_2_i_1} is a good unit test for Monte Carlo numerics.
+Eq.~\ref{eq:model_2_i_1} is a good unit test for numerics.
 
@@
 \begin{align}
-I_2(r_a) &\equiv \int \frac{q {\rm d}q}{\mathcal{B}(q)} f(q)
-\Gamma_2\left(\frac{r\a}{\mathcal{B}(q)}\right) q^{2/3}
+I_2(r\a,M\a) &\equiv \int \frac{q {\rm d}q}{\mathcal{A}^3\mathcal{B}} f(q)
+\Gamma_2\left(\frac{r\a}{\mathcal{B}}, qM\a\right) q^{2/3}
 \label{eq:defn_I2}
 \\
-&= \frac{Z_2}{\mathcal{N}_q} \int {\rm d}q\,
-    q^{\beta+\frac{8}{3}} 
+&=
+Z_2 \int \frac{q {\rm d}q}{\mathcal{A}^3\mathcal{B}} f(q)
+\delta\left(\frac{r\a}{\mathcal{B}} - r_0\right)
+\frac{(qM\a)^{\gamma}}{\mathcal{N}_M}
+q^{2/3}
+\\
+&= \frac{Z_2 M\a^\gamma}{\mathcal{N}_q\mathcal{N}_M} \int {\rm d}q\,
+    q^{\beta+\gamma+\frac{8}{3}} 
     (1+q^\alpha)^{3/2}
@@
 \begin{equation}
-I_2(r_a) = \frac{Z_2}{\mathcal{N}_q}
+I_2(r\a,M\a) = \frac{Z_2}{\mathcal{N}_q}
     \sum_{q_i \in \{{\rm roots}\}}
-q_i^{\beta+\frac{8}{3}} 
+q_i^{\beta+\gamma+\frac{8}{3}} 
 (1+q_i^\alpha)^{3/2}
@@
 
-Power law planets, a realistic mass ratio distribution.
-In other words, now assume
+Power law planets are a slightly more realistic mass ratio distribution.
+If we now assume
 \begin{equation}
-    \Gamma_i(r,M) = Z_i f(r) = Z_i r^\delta / \mathcal{N}_r.
+    \Gamma_i(r,M) = Z_i \times \frac{r^\delta}{\mathcal{N}_r} \times
+    \frac{M^\gamma}{\mathcal{N}_M},
 \end{equation}
-Surprisingly, this might give more insight than Model \#2.
-
+where $Z_i$ is dimensionless, and the normalization constants carry 
+the units (each side has units $[r^{-1} M^{-1}]$).
 From Eq.~\ref{eq:simple_apparent_occ_rate}, we can write
 \begin{equation}
-\Gamma\a(r\a) = \frac{1}{1+\mu} \left(
-\Gamma_0(r\a) + \mu  \left[
-I_1(r_a) + I_2(r_a)
+\Gamma\a(r\a,M\a) = \frac{1}{1+\mu} \left(
+\Gamma_0(r\a,M\a) + \frac{{\rm BF}}{1-{\rm BF}} 
+\left[ I_1(r_a,M\a) + I_2(r_a,M\a)
 \right]
@@
 \end{equation}
-where $I_1(r_a)$ and $I_2(r_a)$ are defined in the same way as in 
+where $I_1(r\a,M\a)$ and $I_2(r\a,M\a)$ are defined in the same way as in 
 Eqs.~\ref{eq:defn_I1} and~\ref{eq:defn_I2}.
 Doing the calculation, we find
-\begin{equation}
-I_1(r\a) = \frac{Z_1}{\mathcal{N}_q \mathcal{N}_r} r_a^\delta
-\int {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta}{2}+2}
-\end{equation}
+\begin{align}
+I_1(r\a,M\a) &= 
+\int \frac{{\rm d}q}{\mathcal{A}} f(q)
+\Gamma^1 \left(\frac{r\a}{\mathcal{A}},M\a\right)
+\\
+&=
+\frac{Z_1}{\mathcal{N}_q \mathcal{N}_r \mathcal{N}_M} 
+r\a^\delta M\a^\gamma
+\int {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+1}{2}}
+\end{align}
 and
-\begin{equation}
-I_2(r\a) = \frac{Z_2}{\mathcal{N}_q \mathcal{N}_r} r_a^\delta
-\int {\rm d}q\,q^{\beta+\delta+\frac{8}{3}} 
+\begin{align}
+I_2(r\a,M\a) &=
+\int \frac{q\,{\rm d}q}{\mathcal{A}^3 \mathcal{B}} f(q)
+\Gamma^2 \left(\frac{r\a}{\mathcal{B}},qM\a\right)
+\\
+&= \frac{Z_2}{\mathcal{N}_q \mathcal{N}_r \mathcal{N}_M} 
+r\a^\delta M\a^\gamma
+\int {\rm d}q\,q^{\beta+\gamma+\delta+\frac{8}{3}} 
                (1+q^\alpha)^{\frac{3}{2}}
                (1+q^{-\alpha})^{\frac{\delta+1}{2}}.
-\end{equation}
+\end{align}
 The net effect of binarity is to just {\it scale} the overall distribution!
 
-Note that the true rate density for the selected stars is
-\begin{equation}
-\Gamma_{\rm sel}(r) = \frac{r^\delta}{\mathcal{N}_r} \left[
-\frac{Z_0}{1+2\mu} + \frac{\mu}{1+2\mu} (Z_1+Z_2)
-\right].
-\end{equation}
-The correction factor with respect to selected stars, $X_\Gamma = 
-\Gamma\a/\Gamma_{\rm sel}$, will be
+Note that the true rate density for a volume-limited sample is
 \begin{align}
-X_\Gamma &\equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_{\rm sel}(r)} 
-\right|_{r_a\rightarrow r,\ Z_i{\rm 's\ equal}} \\
+\Gamma_{\rm vl}(r,M) &= \frac{r^\delta M^\gamma}{\mathcal{N}_r\mathcal{N}_M} 
+\left[
+\frac{Z_0}{1+2(n_b/n_s)} + \frac{(n_b/n_s)}{1+2(n_b/n_s)} (Z_1+Z_2)
+\right] \\
+&= \frac{r^\delta M^\gamma Z_0}{\mathcal{N}_r\mathcal{N}_M}
+\quad\quad ({\rm assuming}\ Z_0=Z_1=Z_2),
+\end{align}
+which when $Z_0=Z_1=Z_2$ is equal to $\Gamma_0$, and $\Gamma_{\rm sel}$.
+The correction factor with respect to single stars, $X_\Gamma = 
+\Gamma\a/\Gamma_0$, is then
+\begin{align}
+X_\Gamma &\equiv \left. \frac{\Gamma\a(r\a,M\a)}{\Gamma_0(r,M)} 
+\right|_{r\a\rightarrow r,\ M\a\rightarrow M,\ Z_i{\rm 's\ equal}} \\
 &=
-\frac{1+2\mu}{3(1+\mu)}
-\left[1 + \mu
+\frac{1}{1+\mu}
+\left[1 + \frac{2}{\mathcal{N}_q} \frac{{\rm BF}}{1-{\rm BF}}
 \left(
-\int {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta}{2}+2} +
-\int {\rm d}q\,q^{\beta+\delta+\frac{8}{3}} 
+\int {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+1}{2}} +
+\int {\rm d}q\,q^{\beta+\gamma+\delta+\frac{8}{3}} 
     (1+q^\alpha)^{\frac{3}{2}}
@@
 
-For $\alpha = 3.5$, $\beta=0$, $\delta=-2.92$, the term in $(\ldots)\approx 
-1.41425 \approx \sqrt{2}$, where the latter surprising numerical fluke holds 
-to the first four decimal places.
-For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma_{\rm sel} = 1.28$, an 
-apparent rate which is {\it higher} than the true rate by 28\%!
-Note that this result is the same as $\Gamma\a/\Gamma0$ and 
+For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the sum of the 
+integrals in $(\ldots)\approx 1.16393$. %171211_model_integrals.nb
+For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.36$, an 
+apparent rate which is {\it higher} than the true rate by 36\%!
+Note that this result is the same as $\Gamma\a/\Gamma_{\rm sel}$ and 
 $\Gamma\a/\Gamma_{\rm vl}$ in the limit where all the $Z_i$'s are equal.

### 2017-12-12 sandbox/derivation.tex
improve precision
derivation: correct math errors

@@
 For the common case $\alpha=3.5$, the dimensionless integral $I$ evaluates to 
-$\approx 0.484174$.
+$\approx 0.4841741$.
 
@@
 I_1(r\a,M\a) &= 
-\int \frac{{\rm d}q}{\mathcal{A}} f(q)
+\int \frac{{\rm d}q}{\mathcal{A}^4} f(q)
 \Gamma^1 \left(\frac{r\a}{\mathcal{A}},M\a\right)
@@
 r\a^\delta M\a^\gamma
-\int {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+1}{2}}
+\int {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}}
 \end{align}
@@
 \frac{1}{1+\mu}
-\left[1 + \frac{2}{\mathcal{N}_q} \frac{{\rm BF}}{1-{\rm BF}}
+\left[1 + \frac{1}{\mathcal{N}_q} \frac{{\rm BF}}{1-{\rm BF}}
 \left(
-\int {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+1}{2}} +
+\int {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}} +
 \int {\rm d}q\,q^{\beta+\gamma+\delta+\frac{8}{3}} 
@@
 For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the sum of the 
-integrals in $(\ldots)\approx 1.16393$. %171211_model_integrals.nb
-For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.36$, an 
-apparent rate which is {\it higher} than the true rate by 36\%!
+integrals in $(\ldots)\approx 1.41425$. %171211_model_integrals.nb
+For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.01448$, an 
+apparent rate which is {\it higher} than the true rate by 1.4\%!
 Note that this result is the same as $\Gamma\a/\Gamma_{\rm sel}$ and 

### 2017-12-13 sandbox/derivation.tex
derivation: fix typo
derivation: add powerlaw+constant integrals

@@
 
-\subsubsection{Power law planets (Model \# 3)}
+\subsubsection{Power law planets (Model \# 6)}
 
@@
 \int {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}}
+\label{eq:I_1_powerlaw_r}
 \end{align}
@@
 \int \frac{q\,{\rm d}q}{\mathcal{A}^3 \mathcal{B}} f(q)
-\Gamma^2 \left(\frac{r\a}{\mathcal{B}},qM\a\right)
+\Gamma^2 \left(\frac{r\a}{\mathcal{B}},qM\a\right) q^{2/3}
 \\
@@
                (1+q^{-\alpha})^{\frac{\delta+1}{2}}.
+\label{eq:I_2_powerlaw_r}               
 \end{align}
@@
 
+\subsubsection{Constant rate density of planets}
+Combining a power law distribution with a constant below some minimum radius 
+would be reasonable (Model \#3).
+Here, we'll have
+\begin{align}
+\notag
+\Gamma_i(r,M) &= Z_i \times \frac{r^\delta}{\mathcal{N}_r} \times
+\frac{M^\gamma}{\mathcal{N}_M}\quad\quad (r>r_\ell),\\
+&= Z_i \times \frac{r_\ell^\delta}{\mathcal{N}_r} \times
+\frac{M^\gamma}{\mathcal{N}_M}\equiv c_\ell \quad\quad (r<r_\ell).
+\end{align}
+
+Once again,
+\begin{equation}
+\Gamma\a(r\a,M\a) = \frac{1}{1+\mu} \left(
+\Gamma_0(r\a,M\a) + \frac{{\rm BF}}{1-{\rm BF}} 
+\left[ I_1(r_a,M\a) + I_2(r_a,M\a)
+\right]
+\right).
+\end{equation}
+At $r\a>r_\ell$, the integrals $I_1(r\a,M\a)$ and $I_2(r\a,M\a)$ are given by 
+Eqs.~\ref{eq:I_1_powerlaw_r} and~\ref{eq:I_2_powerlaw_r} respectively.
+\paragraph{Case $i=1$:}
+At $r\a<r_\ell$, they can be evaluated as follows:
+\begin{align}
+I_1(r\a,M\a) &\equiv \int \frac{{\rm d}q}{\mathcal{A}^4} f(q) 
+\Gamma_1\left( \frac{r\a}{\mathcal{A}}, M\a \right) \\
+&=
+\int_{r\a/\mathcal{A}>r_\ell} \frac{{\rm d}q}{\mathcal{A}^4} f(q) 
+\Gamma_1\left( \frac{r\a}{\mathcal{A}}, M\a \right)
++
+\int_{r\a/\mathcal{A}<r_\ell} \frac{{\rm d}q}{\mathcal{A}^4} f(q) 
+\Gamma_1\left( \frac{r\a}{\mathcal{A}}, M\a \right) \\
+&=
+\int_{q_\ell(r\a)}^1 \frac{{\rm d}q}{\mathcal{A}^4} f(q) 
+\Gamma_1\left( \frac{r\a}{\mathcal{A}}, M\a \right)
++
+\int_{0}^{q_\ell(r\a)} \frac{{\rm d}q}{\mathcal{A}^4} f(q) 
+\Gamma_1\left( \frac{r\a}{\mathcal{A}}, M\a \right) \\
+&=
+\frac{Z_1 r\a^\delta M\a^\gamma}{\mathcal{N}_q \mathcal{N}_r \mathcal{N}_M} 
+\int_{q_\ell(r\a)}^1 {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}}
++ 
+\frac{Z_1 r_\ell^\delta M\a^\gamma}{\mathcal{N}_q \mathcal{N}_r \mathcal{N}_M} 
+\int_0^{q_\ell(r\a)} {\rm d}q\, 
+(1+q^\alpha)^2 q^\beta,
+\end{align}
+where $q_\ell(r\a)$ is found by inverting $r\a/\mathcal{A}=r_\ell$:
+\begin{equation}
+q_\ell(r\a) = \left(\left(\frac{r_\ell}{r\a}\right)^2 - 
+1\right)^{\frac{1}{\alpha}}.
+\end{equation}
+
+\paragraph{Case $i=2$:}
+For $i=2$, the situation is slightly more complicated. I will specify that 
+$\alpha=3.5$, or else the existence of different classes of minima in 
+$r\a/\mathcal{B}=r_\ell$ might confuse the matter.
+If so, then there are two subcases.
+\textit{For subcase \#1,} $\left(\frac{r_\ell}{r\a}\right)^2 > 2$. Then
+\begin{align}
+I_2(r\a,M\a) &=
+\int \frac{q^{5/3}\,{\rm d}q}{\mathcal{A}^3 \mathcal{B}} f(q)
+\Gamma^2 \left(\frac{r\a}{\mathcal{B}},qM\a\right) \\
+&=
+\int_0^{q_{\ell,1}(r\a)} (\ldots)
++
+\int_{q_{\ell,1}(r\a)}^{q_t} (\ldots)
++
+\int_{q_t}^{1} (\ldots)
+\label{eq:intermed_q}\\
+&=
+\int_0^{q_{\ell,1}(r\a)} (\ldots)
++
+\int_{q_{\ell,1}(r\a)}^{1} (\ldots),
+\end{align}
+where $(\ldots)$ indicates the same integrand as in the first line.
+Here, $q_t$ is the turning point of $q^2(1+q^{-\alpha})$ (see 
+Figs.~\ref{fig:func_of_q_0} and~\ref{fig:func_of_q_1}),
+and $q_{\ell,1}(r\a)$ is the sole root of
+\begin{equation}
+q^2 (1+q^{-\alpha}) = \left(\frac{r_\ell}{r\a}\right)^2,
+\end{equation} 
+which must be found numerically.
+In Eq~\ref{eq:intermed_q}, the left-most term has $r\a/\mathcal{B} > r_\ell$, 
+while the right two terms have $r\a/\mathcal{B} < r_\ell$ (and so they can be 
+safely merged).
+Simplifying,
+\begin{align}
+\notag
+I_2(r\a,M\a) &= 
+    \frac{1}{\mathcal{N}_q}
+    \int_0^{q_{\ell,1}(r\a)} 
+    {\rm d}q\, q^{8/3} (1+q^\alpha)^{3/2} q^\beta
+    \Gamma^2 \left(\frac{r\a}{\mathcal{B}},qM\a\right)
+    \\
+&\quad\quad\quad+
+\frac{1}{\mathcal{N}_q}
+\int_{q_{\ell,1}(r\a)}^{1}
+    {\rm d}q\, q^{8/3} (1+q^\alpha)^{3/2} q^\beta
+    \Gamma^2 \left(\frac{r\a}{\mathcal{B}},qM\a\right),
+\end{align}
+and plugging in the rate densities, we get
+\begin{align}
+\notag
+I_2(r\a,M\a) &= 
+\frac{Z_2 r\a^\delta M\a^\gamma}{\mathcal{N}_q \mathcal{N}_r \mathcal{N}_M}
+\int_0^{q_{\ell,1}(r\a)} 
+{\rm d}q\,
+q^{\beta+\gamma+\delta+\frac{8}{3}} 
+(1+q^\alpha)^{\frac{3}{2}}
+(1+q^{-\alpha})^{\frac{\delta+1}{2}}
+\\
+&\quad\quad\quad+
+\frac{Z_2 r_\ell^\delta M\a^\gamma}{\mathcal{N}_q \mathcal{N}_r \mathcal{N}_M}
+\int_{q_{\ell,1}(r\a)}^{1}
+{\rm d}q\, q^{\beta + \gamma + \frac{8}{3}} (1+q^\alpha)^{3/2} 
+(1+q^{-\alpha})^{\frac{1}{2}}.
+\quad\quad \left({\rm for}\ \left(\frac{r_\ell}{r\a}\right)^2 > 2\right)
+\end{align}
+
+\textit{For subcase \#2,} if $q_t^2 (1+q_t^{-\alpha}) < 
+\left(\frac{r_\ell}{r\a}\right)^2 < 2 $,
+then there are two roots, $q_{\ell,1}$ (which is $<q_t$) and $q_{\ell,2}$ 
+(which is $>q_t$). Each must be found 
+numerically. Their existence makes the integrals silly:
+\begin{align}
+I_2(r\a,M\a) &=
+\int \frac{q^{5/3}\,{\rm d}q}{\mathcal{A}^3 \mathcal{B}} f(q)
+\Gamma^2 \left(\frac{r\a}{\mathcal{B}},qM\a\right) \\
+&=
+\int_0^{q_{\ell,1}(r\a)} (\ldots)
++
+\int_{q_{\ell,1}(r\a)}^{q_t} (\ldots)
++
+\int_{q_t}^{q_{\ell,2}(r\a)} (\ldots)
++
+\int_{q_{\ell,2}(r\a)}^1 (\ldots)
+\\
+&=
+\int_0^{q_{\ell,1}(r\a)} (\ldots)
++
+\int_{q_{\ell,1}(r\a)}^{q_{\ell,2}(r\a)} (\ldots)
++
+\int_{q_{\ell,2}(r\a)}^1 (\ldots),
+\end{align}
+where the left and right-most terms have $r\a/\mathcal{B}>r_\ell$, and the 
+center term has $r\a/\mathcal{B}<r_\ell$.
+Numerically, $q_t = 0.9210924370$ and 
+$q_t^2(1+q^{-\alpha})=1.9796263301$.
+
+Plugging in the rate densities, we get
+\begin{align}
+\notag
+I_2(r\a,M\a) &=
+\frac{Z_2 r\a^\delta M\a^\gamma}{\mathcal{N}_q \mathcal{N}_r \mathcal{N}_M}
+\int_0^{q_{\ell,1}(r\a)} 
+{\rm d}q\,
+q^{\beta+\gamma+\delta+\frac{8}{3}} 
+(1+q^\alpha)^{\frac{3}{2}}
+(1+q^{-\alpha})^{\frac{\delta+1}{2}}
+\\
+\notag
+&\quad\quad\quad+
+\frac{Z_2 r_\ell^\delta M\a^\gamma}{\mathcal{N}_q \mathcal{N}_r \mathcal{N}_M}
+\int_{q_{\ell,1}(r\a)}^{q_{\ell,2}(r\a)}
+{\rm d}q\, q^{\beta + \gamma + \frac{8}{3}} (1+q^\alpha)^{3/2} 
+(1+q^{-\alpha})^{\frac{1}{2}}
+\\
+\notag
+&\quad\quad\quad+
+\frac{Z_2 r\a^\delta M\a^\gamma}{\mathcal{N}_q \mathcal{N}_r \mathcal{N}_M}
+\int_{q_{\ell,2}(r\a)}^1
+{\rm d}q\,
+q^{\beta+\gamma+\delta+\frac{8}{3}} 
+(1+q^\alpha)^{\frac{3}{2}}
+(1+q^{-\alpha})^{\frac{\delta+1}{2}}
+\\
+&\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
+\ldots\ {\rm for}\ q_t^2 
+(1+q_t^{-\alpha}) < 
+\left(\frac{r_\ell}{r\a}\right)^2 < 2.
+\end{align}
+
+This should actually be enough to integrate semi-analytically with a computer.
+
+\begin{figure}[!th]
+    \centering
+    \includegraphics[width=.7\textwidth]{funcq_of_q_0.png}
+    \caption{For $\alpha=3.5$, there is a single minimum of $q^2 
+    (1+q^{-\alpha})$.}
+    \label{fig:func_of_q_0}
+\end{figure}
+\begin{figure}[!th]
+    \centering
+    \includegraphics[width=.7\textwidth]{funcq_of_q_1.png}
+    \caption{For $\alpha=3.5$, there is a single minimum of $q^2 
+        (1+q^{-\alpha})$.}
+    \label{fig:func_of_q_1}
+\end{figure}
+
 \newpage

### 2017-12-14 src/integrate_for_apparent_rate_density.py
add option for higher resolution integration

@@ -455,7 +455,7 @@ def Gamma_a(r_a, M_a, f_q, q, A_q, B_q, μ, norm_r=None, norm_q=None,
     return Γ_a, Γ_0
 
 
-def get_apparent_radius_grid(model_number):
+def get_apparent_radius_grid(model_number, slowrun=False):
 
     if model_number == 1:
         r_a_grid = np.array([2**(-1/2),1])
@@ -464,10 +464,16 @@ def get_apparent_radius_grid(model_number):
         r_a_grid = np.arange(5e-3,1+5e-3,5e-3)
 
     elif model_number in [5]:
-        r_a_grid = np.arange(1e-2,r_pu+1e-2,1e-2)
+        if not slowrun:
+            r_a_grid = np.arange(1e-2,r_pu+1e-2,1e-2)
+        elif slowrun:
+            r_a_grid = np.arange(1e-2,r_pu+1e-2,1e-2)
 
     elif model_number in [3, 4, 6]:
-        r_a_grid = np.arange(1e-1,r_pu+1e-1,1e-1)
+        if not slowrun:
+            r_a_grid = np.arange(1e-1,r_pu+1e-1,1e-1)
+        elif slowrun:
+            r_a_grid = np.arange(2e-2,r_pu+2e-2,2e-2)
 
     return r_a_grid
 
@@ -554,6 +560,8 @@ if __name__ == '__main__':
         help='BF = n_b/(n_s+n_b), for n number density')
     parser.add_argument('-rpu', '--upperradiuscutoff', type=float, default=None,
         help='the maximum allowed planet radius in units of Rearth')
+    parser.add_argument('-sr', '--slowrun', action='store_true', default=False,
+        help='use --slowrun if you want models to run high-resoln models.')
 
     args = parser.parse_args()
 
@@ -565,7 +573,7 @@ if __name__ == '__main__':
 
     M_a_grid = np.array([1.0])
 
-    r_a_grid = get_apparent_radius_grid(model_number)
+    r_a_grid = get_apparent_radius_grid(model_number, args.slowrun)
 
     Γ_a, Γ_0 = get_apparent_rate_density(r_a_grid, M_a_grid, model_number)
 

### 2017-12-14 src/run_integrator.sh

@@ -20,3 +20,24 @@ python integrate_for_apparent_rate_density.py --modelnumber 3 --ZsubTwo 0.5 --bi
 # If you fine-tune both r_pu AND Z_2/Z_0 preferentially, how big of a "HJ
 # discrepancy" do you get?
 python integrate_for_apparent_rate_density.py --modelnumber 3 --ZsubTwo 0.0 --binaryfrac 0.44 --upperradiuscutoff 15.0
+
+# "Nominal" models (this just means I arbitrarily decided Z_2 = 0.5)
+#python integrate_for_apparent_rate_density.py --slowrun --modelnumber 1 --ZsubTwo 0.5 --binaryfrac 0.1 --upperradiuscutoff 1
+#python integrate_for_apparent_rate_density.py --slowrun --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
+#python integrate_for_apparent_rate_density.py --slowrun --modelnumber 4 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
+#python integrate_for_apparent_rate_density.py --slowrun --modelnumber 5 --ZsubTwo 0.5 --binaryfrac 0.1 --upperradiuscutoff 22.5
+#python integrate_for_apparent_rate_density.py --slowrun --modelnumber 6 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
+#
+## Check vs Z_2
+#python integrate_for_apparent_rate_density.py --slowrun --modelnumber 3 --ZsubTwo 0.0 --binaryfrac 0.44 --upperradiuscutoff 22.5
+#python integrate_for_apparent_rate_density.py --slowrun --modelnumber 3 --ZsubTwo 0.25 --binaryfrac 0.44 --upperradiuscutoff 22.5
+#
+## Check vs upper radius cutoff
+#python integrate_for_apparent_rate_density.py --slowrun --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 15.0
+#python integrate_for_apparent_rate_density.py --slowrun --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 17.5
[…]

### 2017-12-14 paper/simplest_effects.tex
add footnote addressing planet radius scaling Q
paper: update volume visualization and caption

@@
 \propto \mathcal{D} L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm true})
+\label{eq:snr_true}
 \end{equation}
@@
     \caption{
-        Cartoon of the different selected and searchable volumes for single 
-        stars (left column), and twin binaries (right column).
-        This model (\#1) assumes all stars have equal mass and luminosity.
-        Since the observer does not recognize the brighter binaries, they 
-        select 
-        them out to a larger distance, $\sqrt{2}\times$ that of single stars.
-        However, dilution causes the twin binaries to only be searchable in 
-        one 
-        eighth of their selected volume.
+        Cartoon of the searchable volumes for single stars ({\it left}), and 
+        twin binaries ({\it right}).
+        This model (\#1) assumes all stars have equal mass and luminosity, and 
+        all planets have the same true radius $r=r_p$.
+        {\it Top:} At an apparent radius $r\a=r_p$,
+        the observer selects twin binaries out to a larger         
+        distance, $\sqrt{2}\times$ that of single stars.
+        Because of dilution, there are no planets in twin binaries with 
+        $r\a=r_p$.
+        {\it Middle:} At an apparent radius $r\a=r_p/\sqrt{2}$, the 
+        searched volumes are half those at $r\a=r_p$. 
+        The only detected planets with $r\a=r_p/\sqrt{2}$ orbit twin binaries.
+        {\it Bottom:} Planets with a true radius $r=r_p$ are searchable to 
+        a maximum distance $d_0$ around singles, and $d_0/\sqrt{2}$ around 
+        twin binaries. These distances are the same as what an observer 
+        selects based on apparent radii.
     }

### 2017-12-14 results/make_merged.sh
clarify file names
the monte carlo code produces occ rates, not rate densities.

@@ -1,54 +1,0 @@
-#!/usr/bin/env bash
-
-pdftk \
-  rate_density_vs_radius_model_1_brokenx.pdf \
-  rate_density_vs_radius_model_2.pdf \
-  rate_density_vs_radius_logs_model_2.pdf \
-  rate_density_vs_radius_model_3_Zsub2_0.50_rpu_22.5.pdf \
-  rate_density_vs_radius_logs_model_3_Zsub2_0.50_rpu_22.5.pdf \
-  rate_density_vs_radius_model_3_withtext_Zsub2_0.50_rpu_22.5.pdf \
-  rate_density_vs_radius_model_4_xcut.pdf \
-  output rates_merged.pdf
-
-# As function of Z_2
-pdftk \
-  rate_density_vs_radius_logs_model_3_Zsub2_0.00_rpu_22.5.pdf \
-  rate_density_vs_radius_logs_model_3_Zsub2_0.25_rpu_22.5.pdf \
-  rate_density_vs_radius_logs_model_3_Zsub2_0.50_rpu_22.5.pdf \
-  rate_density_vs_radius_model_3_withtext_Zsub2_0.00_rpu_22.5.pdf \
-  rate_density_vs_radius_model_3_withtext_Zsub2_0.25_rpu_22.5.pdf \
-  rate_density_vs_radius_model_3_withtext_Zsub2_0.50_rpu_22.5.pdf \
-  output rates_fn_of_Z2.pdf
-
-pdftk \
-  rate_density_vs_radius_model_3_fraclines_Zsub2_0.00_rpu_22.5.pdf \
-  rate_density_vs_radius_model_3_fraclines_Zsub2_0.25_rpu_22.5.pdf \
-  rate_density_vs_radius_model_3_fraclines_Zsub2_0.50_rpu_22.5.pdf \
-  output rates_fn_of_Z2_fraclines.pdf
-
-# As function of r_pu
-pdftk \
-  rate_density_vs_radius_logs_model_3_Zsub2_0.50_rpu_15.0.pdf \
-  rate_density_vs_radius_logs_model_3_Zsub2_0.50_rpu_17.5.pdf \
-  rate_density_vs_radius_logs_model_3_Zsub2_0.50_rpu_20.0.pdf \
-  rate_density_vs_radius_logs_model_3_Zsub2_0.50_rpu_22.5.pdf \
-  rate_density_vs_radius_logs_model_3_Zsub2_0.50_rpu_25.0.pdf \
[…]

### 2017-12-14 results/make_monte_carlo_merged.sh

@@ -1,0 +1,54 @@
+#!/usr/bin/env bash
+
+pdftk \
+  occ_rate_vs_radius_model_1_brokenx.pdf \
+  occ_rate_vs_radius_model_2.pdf \
+  occ_rate_vs_radius_logs_model_2.pdf \
+  occ_rate_vs_radius_model_3_Zsub2_0.50_rpu_22.5.pdf \
+  occ_rate_vs_radius_logs_model_3_Zsub2_0.50_rpu_22.5.pdf \
+  occ_rate_vs_radius_model_3_withtext_Zsub2_0.50_rpu_22.5.pdf \
+  occ_rate_vs_radius_model_4_xcut.pdf \
+  output rates_monte_carlo_merged.pdf
+
+# As function of Z_2
+pdftk \
+  occ_rate_vs_radius_logs_model_3_Zsub2_0.00_rpu_22.5.pdf \
+  occ_rate_vs_radius_logs_model_3_Zsub2_0.25_rpu_22.5.pdf \
+  occ_rate_vs_radius_logs_model_3_Zsub2_0.50_rpu_22.5.pdf \
+  occ_rate_vs_radius_model_3_withtext_Zsub2_0.00_rpu_22.5.pdf \
+  occ_rate_vs_radius_model_3_withtext_Zsub2_0.25_rpu_22.5.pdf \
+  occ_rate_vs_radius_model_3_withtext_Zsub2_0.50_rpu_22.5.pdf \
+  output rates_monte_carlo_fn_of_Z2.pdf
+
+pdftk \
+  occ_rate_vs_radius_model_3_fraclines_Zsub2_0.00_rpu_22.5.pdf \
+  occ_rate_vs_radius_model_3_fraclines_Zsub2_0.25_rpu_22.5.pdf \
+  occ_rate_vs_radius_model_3_fraclines_Zsub2_0.50_rpu_22.5.pdf \
+  output rates_monte_carlo_fn_of_Z2_fraclines.pdf
+
+# As function of r_pu
+pdftk \
+  occ_rate_vs_radius_logs_model_3_Zsub2_0.50_rpu_15.0.pdf \
+  occ_rate_vs_radius_logs_model_3_Zsub2_0.50_rpu_17.5.pdf \
+  occ_rate_vs_radius_logs_model_3_Zsub2_0.50_rpu_20.0.pdf \
+  occ_rate_vs_radius_logs_model_3_Zsub2_0.50_rpu_22.5.pdf \
[…]

### 2017-12-14 src/plot_occrates_vs_radius.py

@@ -121,10 +121,10 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
         ax.set_yscale('log')
 
     if logx or logy:
-        outname = '../results/rate_density_vs_radius_logs_model_'+\
+        outname = '../results/occ_rate_vs_radius_logs_model_'+\
                  repr(model_number)
     else:
-        outname = '../results/rate_density_vs_radius_model_'+\
+        outname = '../results/occ_rate_vs_radius_model_'+\
                  repr(model_number)
     if brokenx:
         outname += '_brokenx'

### 2017-12-15 src/integrate_for_apparent_rate_density.py
add model #7 for HJ study

@@ -14,6 +14,7 @@ XModel #2: varying q, same planet (WARNING: not implemented)
 /Model #4: varying q, r with a gap
 /Model #5: twin binary, powerlaw r
 /Model #6: varying q, powerlaw r
+/Model #7: varying q, r ~ gaussian(14re, 2re)
 
 Example usage, for each model type:
 >>> python integrate_for_apparent_rate_density.py --modelnumber 1 --ZsubTwo 0.5 --binaryfrac 0.1 --upperradiuscutoff 1
@@ -22,6 +23,7 @@ Example usage, for each model type:
 >>> python integrate_for_apparent_rate_density.py --modelnumber 4 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
 >>> python integrate_for_apparent_rate_density.py --modelnumber 5 --ZsubTwo 0.5 --binaryfrac 0.1 --upperradiuscutoff 22.5
 >>> python integrate_for_apparent_rate_density.py --modelnumber 6 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
+>>> python integrate_for_apparent_rate_density.py --modelnumber 7 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
 
 '''
 from __future__ import division, print_function
@@ -42,7 +44,7 @@ global BF, model_number, r_pu, r_pl
 r_pl = 2 # [Rearth]. Lower bound for truncation.
 
 
-def Gamma_0(r, M, Z_0, model_number, norm_r=None):
+def Gamma_0(r, M, Z_0, model_number, norm_r=None, gaussianparams=None):
     '''
     occ rate density around singles
     '''
@@ -64,10 +66,16 @@ def Gamma_0(r, M, Z_0, model_number, norm_r=None):
         f_r = 0 if (r > 1.5) & (r < 2) else min( r**δ, r_pl**δ )
         Γ_0 = Z_0 * f_r / norm_r
 
+    elif model_number == 7:
+        mean, sigma = gaussianparams[0], gaussianparams[1]
+        f_r = np.exp(- (r-mean)**2 / (2 * sigma**2) )
+        Γ_0 = Z_0 * f_r / norm_r
+
     return Γ_0
 
 
-def Gamma_1(r, M, Z_1, model_number, prefactor=None, norm_r=None, q_grid=None):
[…]

### 2017-12-15 src/plot_integrated_occrates_vs_radius.py

@@ -15,7 +15,7 @@ pgf_with_custom_preamble = {
 mpl.rcParams.update(pgf_with_custom_preamble)
 
 import matplotlib.pyplot as plt, pandas as pd, numpy as np
-from scipy import integrate
+from scipy.integrate import trapz
 
 from brokenaxes import brokenaxes
 
@@ -65,7 +65,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
         yinferred = np.array(df['Γ_a'])
         xsingle = np.append(xvals,1)
         ytruesingle = np.append(np.array(df['Γ_0']), 0)
-    elif model_number in [3,4,5,6]:
+    elif model_number in [3,4,5,6,7]:
         xvals = np.array(df['r'])
         yinferred = np.array(df['Γ_a'])
         xsingle = xvals
@@ -79,10 +79,10 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
         for bin_pair in bin_pairs:
             inds = (xvals > bin_pair[0]) & (xvals < bin_pair[1])
             Λinferred = np.append(
-                        Λinferred, integrate.trapz(yinferred[inds], xvals[inds])
+                        Λinferred, trapz(yinferred[inds], xvals[inds])
                         )
             Λtruesingle = np.append(
-                        Λtruesingle, integrate.trapz(ytruesingle[inds], xvals[inds])
+                        Λtruesingle, trapz(ytruesingle[inds], xvals[inds])
                         )
 
         yinferred = Λinferred
@@ -117,7 +117,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
             for bin_pair in bin_pairs:
                 inds = (xvals > bin_pair[0]) & (xvals < bin_pair[1])
                 Λinferred = np.append(
-                            Λinferred, integrate.trapz(yinferred[inds], xvals[inds])
+                            Λinferred, trapz(yinferred[inds], xvals[inds])
                             )
 
             yinferred = Λinferred
[…]

### 2017-12-15 src/plot_integrated_rate_densities_vs_radius.py

@@ -65,7 +65,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
         yinferred = np.array(df['Γ_a'])
         xsingle = np.append(xvals,1)
         ytruesingle = np.append(np.array(df['Γ_0']), 0)
-    elif model_number in [3,4,5,6]:
+    elif model_number in [3,4,5,6,7]:
         xvals = np.array(df['r'])
         yinferred = np.array(df['Γ_a'])
         xsingle = xvals
@@ -102,7 +102,10 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
         ax.plot(xsingle, ytruesingle, label='true (singles)', linestyle='-',
                 c=colors[1])
 
-    ax.legend(loc='best',fontsize='medium')
+    if model_number != 7:
+        ax.legend(loc='best',fontsize='medium')
+    else:
+        ax.legend(loc='upper left',fontsize='small')
 
     ax.set_xlabel('planet radius, $r$ [$r_\oplus$]', fontsize='large')
 
@@ -140,7 +143,12 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
     if xcut:
         ax.set_xlim([-0.3,5.3])
 
-    if model_number == 3:
+    if model_number == 3 or model_number==7:
+        Z_2 = 0.0
+        fname = '../data/numerics/integrate_model_{:d}_Zsub2_{:.2f}_rpu_{:.2f}.out'.format(
+                model_number, Z_2, r_pu)
+        df = pd.read_csv(fname)
+
         # Assess HJ rate difference.
         #Howard 2012 boundary #1 and boundary #2:
         for lower_bound in [5.6,8]:
@@ -186,17 +194,17 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
                     transform=ax.transAxes, fontsize='x-small')
             outname += '_withtext'
 
-        else:
+        elif model_number==3:
             txt = '$Z_2/Z_0 =\ ${:.1f}'.format(Z_2/Z_0)
             ax.text(0.96,0.5,txt,horizontalalignment='right',
[…]

### 2017-12-15 src/run_integrator.sh

@@ -26,6 +26,10 @@
 ## If you fine-tune both r_pu AND Z_2/Z_0 preferentially, how big of a "HJ
 ## discrepancy" do you get?
 #python integrate_for_apparent_rate_density.py --modelnumber 3 --ZsubTwo 0.0 --binaryfrac 0.44 --upperradiuscutoff 15.0
+## Model #7, HJ study
+#python integrate_for_apparent_rate_density.py --modelnumber 7 --ZsubTwo 0.0 --binaryfrac 0.44 --upperradiuscutoff 22.5
+#python integrate_for_apparent_rate_density.py --modelnumber 7 --ZsubTwo 0.25 --binaryfrac 0.44 --upperradiuscutoff 22.5
+#python integrate_for_apparent_rate_density.py --modelnumber 7 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
 
 ##########################
 # SLOW (HIGH RESOLUTION) #
@@ -53,3 +57,8 @@ python integrate_for_apparent_rate_density.py --slowrun --modelnumber 3 --ZsubTw
 # If you fine-tune both r_pu AND Z_2/Z_0 preferentially, how big of a "HJ
 # discrepancy" do you get?
 python integrate_for_apparent_rate_density.py --slowrun --modelnumber 3 --ZsubTwo 0.0 --binaryfrac 0.44 --upperradiuscutoff 15.0
+
+# Model #7, HJ study
+python integrate_for_apparent_rate_density.py --slowrun --modelnumber 7 --ZsubTwo 0.0 --binaryfrac 0.44 --upperradiuscutoff 22.5
+python integrate_for_apparent_rate_density.py --slowrun --modelnumber 7 --ZsubTwo 0.25 --binaryfrac 0.44 --upperradiuscutoff 22.5
+python integrate_for_apparent_rate_density.py --slowrun --modelnumber 7 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5

### 2017-12-15 src/plot_integrated_occrates_vs_radius.py
bugfix plot scripts

@@ -230,7 +230,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
                     transform=ax.transAxes, fontsize='x-small')
             outname += '_withtext'
 
-        elif model_number==3:
+        elif model_number==3 and not many_Zs:
             txt = '$Z_2/Z_0 =\ ${:.1f}'.format(Z_2/Z_0)
             ax.text(0.96,0.5,txt,horizontalalignment='right',
                     verticalalignment='center',
@@ -256,36 +256,36 @@ if __name__ == '__main__':
     #note: not running
     #make_plot(2, logy=True, Z_2=0.5, r_pu=1)
 
-    #make_plot(5, logx=True, logy=True, Z_2=0.5, r_pu=22.5)
-    #make_plot(6, logx=True, logy=True, Z_2=0.5, r_pu=22.5)
+    make_plot(5, logx=True, logy=True, Z_2=0.5, r_pu=22.5)
+    make_plot(6, logx=True, logy=True, Z_2=0.5, r_pu=22.5)
 
-    #make_plot(3, Z_2=0.5, r_pu=22.5)
-    #make_plot(3, withtext=True, Z_2=0.5, r_pu=22.5)
-    #make_plot(3, logx=False, logy=True, Z_2=0.5, r_pu=22.5)
-    #make_plot(3, logx=True, logy=True, Z_2=0.5, r_pu=22.5)
+    make_plot(3, Z_2=0.5, r_pu=22.5)
+    make_plot(3, withtext=True, Z_2=0.5, r_pu=22.5)
+    make_plot(3, logx=False, logy=True, Z_2=0.5, r_pu=22.5)
+    make_plot(3, logx=True, logy=True, Z_2=0.5, r_pu=22.5)
 
-    #make_plot(4, Z_2=0.5, xcut=True, r_pu=22.5)
-    #make_plot(4, logy=True, Z_2=0.5, xcut=True, r_pu=22.5)
+    make_plot(4, Z_2=0.5, xcut=True, r_pu=22.5)
+    make_plot(4, logy=True, Z_2=0.5, xcut=True, r_pu=22.5)
 
-    ## Change as a function of Z_2/Z_0
-    #for Z_2 in [0, 0.25]:
-    #    make_plot(3, Z_2=Z_2, r_pu=22.5)
-    #    make_plot(3, logy=True, Z_2=Z_2, r_pu=22.5)
[…]

### 2017-12-15 src/plot_integrated_rate_densities_vs_radius.py

@@ -144,7 +144,8 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
         ax.set_xlim([-0.3,5.3])
 
     if model_number == 3 or model_number==7:
-        Z_2 = 0.0
+
+        Z_2 = 0.5
         fname = '../data/numerics/integrate_model_{:d}_Zsub2_{:.2f}_rpu_{:.2f}.out'.format(
                 model_number, Z_2, r_pu)
         df = pd.read_csv(fname)
@@ -194,7 +195,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
                     transform=ax.transAxes, fontsize='x-small')
             outname += '_withtext'
 
-        elif model_number==3:
+        elif model_number==3 and not many_Zs:
             txt = '$Z_2/Z_0 =\ ${:.1f}'.format(Z_2/Z_0)
             ax.text(0.96,0.5,txt,horizontalalignment='right',
                     verticalalignment='center',
@@ -220,36 +221,36 @@ if __name__ == '__main__':
     #note: not running
     #make_plot(2, logy=True, Z_2=0.5, r_pu=1)
 
-    #make_plot(5, logx=True, logy=True, Z_2=0.5, r_pu=22.5)
-    #make_plot(6, logx=True, logy=True, Z_2=0.5, r_pu=22.5)
+    make_plot(5, logx=True, logy=True, Z_2=0.5, r_pu=22.5)
+    make_plot(6, logx=True, logy=True, Z_2=0.5, r_pu=22.5)
 
-    #make_plot(3, Z_2=0.5, r_pu=22.5)
-    #make_plot(3, withtext=True, Z_2=0.5, r_pu=22.5)
-    #make_plot(3, logx=False, logy=True, Z_2=0.5, r_pu=22.5)
-    #make_plot(3, logx=True, logy=True, Z_2=0.5, r_pu=22.5)
+    make_plot(3, Z_2=0.5, r_pu=22.5)
+    make_plot(3, withtext=True, Z_2=0.5, r_pu=22.5)
+    make_plot(3, logx=False, logy=True, Z_2=0.5, r_pu=22.5)
+    make_plot(3, logx=True, logy=True, Z_2=0.5, r_pu=22.5)
 
[…]

### 2017-12-15 paper/main.tex
merge model 2 figs; add aastex cmds
add improvements to text
add bibtex citations; update model #4 figure
add footnote addressing planet radius scaling Q
WIP paper commit
paper: update volume visualization and caption
paper: update figures and captions.

@@
 \usepackage{comment}
+\usepackage{grffile} % checks for multiple dots in figure filenames
 
-\shortauthors{Bouma, Winn, Masuda}
+%% Reintroduced the \received and \accepted commands from AASTeX v5.2
+%\received{July 1, 2016}
+%\revised{September 27, 2016}
+%\accepted{\today}
+%% Command to document which AAS Journal the manuscript was submitted to.
+%% Adds "Submitted to " the arguement.
+\submitjournal{AAS journals.}
+
+\shortauthors{Bouma et al.}
 \shorttitle{Binarity and Occurrence Rates}
 
+\newcommand{\pp}{\mathcal{P}}
+\newcommand{\ps}{\mathcal{S}}
+\renewcommand{\a}{_{\rm a}}
+\newcommand{\s}{_{\rm s}}
 \begin{document}
@@
 surveys}
-
-\author{
-L. G. Bouma, J. N. Winn, K. Masuda
-}
-
+%
+\correspondingauthor{L. Bouma}
+\email{luke@astro.princeton.edu}
+%
+\author{L. G. Bouma}
+\affiliation{
+    Department of Astrophysical Sciences,
+    Princeton University,
+    4 Ivy Lane, Princeton, NJ 08540, USA}
+\author{J. N. Winn}
+\affiliation{
+    Department of Astrophysical Sciences,
+    Princeton University,
+    4 Ivy Lane, Princeton, NJ 08540, USA}
+\author{K. Masuda}
+\affiliation{
+    Department of Astrophysical Sciences,
+    Princeton University,
+    4 Ivy Lane, Princeton, NJ 08540, USA}
+%
+%
 \begin{abstract}
-
+%
 This work aims to clarify the biases that stellar binarity introduces
@@
 rates measured by {\it Kepler}\ and the California group's respective surveys.
+%
 \end{abstract}
+%
+\keywords{
+    methods: data analysis ---
+    planets and satellites: detection ---
+    surveys}
+%
+%
 
-\input{introduction}
-\input{methods}
-\input{results}
-\input{discussion}
-\input{conclusion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\input{introduction}
+
+\section{Introduction}
+
+A group of astronomers wants to measure the mean number of planets of a 
+certain type per star of a certain type.
+Ignoring stellar multiplicity, they perform a signal-to-noise limited transit 
+survey, and detect a set of planets that appear to be of the desired class.
+They then choose the stars (among those initially surveyed) around which the 
+planets of interest appeared to be searchable.
+Correcting for the geometric transit probability $p_{\rm tra}$, they report an 
+apparent rate density,
+\begin{equation}
+\Gamma\a(\pp\a, \ps\a) = \frac{N_{\rm det}(\pp\a, \ps\a)}{N_{\rm s,a}(\pp\a, 
+    \ps\a)} \times \frac{1}{p_{\rm tra}(\pp\a, \ps\a)}.
+\label{eq:wouldnt_it_be_nice}
+\end{equation}
+where $\pp\a$, $\ps\a$ are the apparent planetary and stellar parameters, 
+respectively.
+Here $N_{\rm det}(\pp\a, \ps\a)$ is the number of 
+detected planets with parameters $\pp\a,\ps\a$, per unit $\pp\a$ and $\ps\a$. 
+The quantity $N_{\rm s,a}(\pp\a, \ps\a)$ is the number of unresolved 
+point-sources on the sky the appear to be searchable.
+
+There are many potential pitfalls.  Some genuine transit signals can be missed
+by the detection pipeline.  Some apparent transit signals are spurious, from
+noise fluctuations, failures of `detrending', or instrumental effects.  Stars
+and planets can be misclassified due to statistical and systematic errors in
+the measurements of their properties.  Poor angular resolution causes false
+positives due to blends with background eclipsing binaries. {\it Et cetera}.
+
+Here we focus on problems that arise from the fact that many stars exist in 
+multiple star systems.
+For simplicity, we consider only binaries, and we assume that they are all 
+spatially unresolved.
+
+An immediate complication is that, due to dynamical stability or some 
+aspect of planet formation, the occurrence rate of planets might differ 
+between binary and single-star systems.
+If ``occurrence rate'' is defined as the mean number of planets within 
+set radius and period bounds per star in a given mass interval, it must 
+implicitly marginalize over stellar multiplicity.
+This means marginalizing over ``occurrence rates in single star systems'', 
+``occurrence rates about primaries'', and
+``occurrence rates about secondaries''
+\citep[see][]{wang_occurrence_2015}.
+
+Outside of astrophysical differences, there are observational biases for every 
+term in Eq.~\ref{eq:wouldnt_it_be_nice}.
+There are errors in $N_{\rm det}$ due to planet radius 
+misclassification.
+There are errors in $N_{{\rm s,a}}$ because a given point on the sky
+There are errors in $p_{\rm tra}(\pp\a,\ps\a)$ because stars in binaries may 
+have different masses and radii than assumed in the single-star case.
+Binarity might also affect the observers' ability to correctly select 
+searchable stars (but see Sec.~\ref{sec:model_1} for discussion of why this is 
+a second-order effect).
+
+Finally, there are errors in $p_{\rm det}$ because detection efficiencies 
+for planets orbiting single stars, primaries, and secondaries are all 
+different.
+
+Correcting for binarity's observational biases is non-trivial.
+For instance, in counting the number of selected stars, even after realizing 
+that binaries count as two stars, one must note that the multiplicity 
+fraction of {\it selected} stars is greater than that of a volume limited 
+sample.
+This is the familiar Malmquist bias: binaries are selected out to larger 
+distances than single stars because they are more luminous.
+As a separate challenge, finding the correct number of detected planets in a 
+radius bin, $N_{\rm det}$, requires knowledge of the true planetary radii.
+Observers deduce apparent radii.
+In binaries, the apparent and true radii differ because of diluting flux, 
+and possibly because the planet is assumed to orbit the wrong star
+\citep[\textit{e.g.},][]{furlan_kepler_2017}.
+
+To gain intuition for the many observational biases at play,
+we consider a set of idealized transit surveys:
+\begin{itemize}
+    \item Model \#1: fixed stars, fixed planets, twin binaries;
+    \item Model \#2: fixed planets and primaries, varying secondaries;
+    \item Model \#3: fixed primaries, varying planets and secondaries.
+\end{itemize}
+We define our terminology in Sec.~\ref{sec:definitions}, and present
+our transit survey models in Secs.~\ref{sec:model_1}-\ref{sec:model_3}, where 
+each subsection corresponds to a model listed above.
+We interpret these calculations throughout, and in 
+Sec.~\ref{sec:discussion} connect them to topical questions in 
+the interpretation of transit survey occurrence rates.
+In particular, we mention the ``hot Jupiter rate discrepancy'', the relevance 
+towards measurements of $\eta_\oplus$, and the implications for detailed 
+study of \citet{fulton_california-_2017}'s recently discovered ``valley''.
+We conclude in Sec.~\ref{sec:conclusion}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\input{methods}
+
+\section{Definitions}
+\label{sec:definitions}
+We define the occurrence rate density, $\Gamma$, as the expected number of 
+planets per star per bin of planetary or stellar phase space.
+Since we will mainly be concerned with the rate density's dependence on 
+planetary radii $r$, we write
+\begin{equation}
+\Gamma(r) = \frac{{\rm d}\Lambda}{{\rm d}r},
+\label{eq:rate_density_defn}
+\end{equation}
+where $\Lambda$ is the occurrence rate.
+In this notation, ``the occurrence rate of planets of a particular size'' 
+translates to an integral of Eq.~\ref{eq:rate_density_defn}, evaluated over a 
+radius interval.
+
+The above definition implicitly marginalizes the rate density over stellar 
+multiplicity.
+In this study we only consider single and binary star systems.
+For a selected population of stars and planets, the rate density is then 
+a weighted sum of rate densities for each system type:
+\begin{equation}
+N_{\rm tot} \Gamma(r) =
+N_0 \Gamma_0(r) +
+N_1 \Gamma_1(r) +
+N_2 \Gamma_2(r),
+\label{eq:rate_density_marginalized}
+\end{equation}
+where $i=0$ corresponds to single stars, $i=1$ to primaries of 
+binaries, and $i=2$ to secondaries of binaries.
+$N_{\rm tot} = \sum_i N_i$ is the total number of selected stars, and 
+$N_0,N_1,N_2$ are the number of selected single stars, primaries, and 
+secondaries.
+Since each selected binary system contributes both a 
+primary and secondary star, $N_1=N_2$.
+This redundancy in our notation will later prove its use.
+
+Finally, it is helpful to write 
+$\Gamma_i(r)$, the rate density for each type of star, as the product of a 
+shape function and a constant:
+\begin{equation}
+\Gamma_i(r) = \frac{{\rm d}\Lambda_i}{{\rm d}r} = Z_i p_i(r),
+\quad {\rm for}\ i\in\{0,1,2\}.
+\label{eq:rate_density_shape}
+\end{equation}
+The shape function is normalized to unity.
+The $Z_i$'s can be interpreted as each system type's occurrence rate 
+$\Lambda_i$, integrated over all planetary radii.
+They are equivalent to the number of planets per single star, primary, or 
+secondary.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\input{results}
+
+\section{Idealized Models of Transit Surveys}
+
+\subsection{Model \#1: fixed stars, fixed planets, twin binaries}
+\label{sec:model_1}
+
+Since the effects of binarity are most pronounced when the two components are 
+similar, we begin by considering a universe in which all planets are 
+identical, and all stars are identical except that some fraction of them exist 
+in binaries.
+
+Expressed mathematically, from Eqs.~\ref{eq:rate_density_marginalized}
+and~\ref{eq:rate_density_shape} the occurrence rate density at a planet radius 
+$r$ can be written
+\begin{equation}
+\Gamma(r) = \delta(r_p) \times
+\frac{
+    N_0 Z_0 +
+    N_1 Z_1 +
+    N_2 Z_2
+}{N_{\rm tot}},
+\label{eq:model_1_rate_density}
+\end{equation}
+where $\delta(r_p)$ is the Dirac delta function, zero except at the true 
+planet radius, $r_p$.
+The occurrence rate over any interval that includes $r_p$ is then
+\begin{equation}
+\Lambda|_{r_p} = \frac{
+    N_0 Z_0 +
+    N_1 Z_1 +
+    N_2 Z_2 
+}{N_{\rm tot}},
+\label{eq:model_1_rate}
+\end{equation}
+and the rate is zero over intervals that do not include $r_p$.
+
+We return to our group of binarity-ignoring astronomers. They do 
+not know the true rate density~--~they would like to discover it!
+In their signal-to-noise limited transit survey, they select stars 
+that they think can yield transit detections.
+Since the noise is Poissonian, they assume
+\begin{equation}
+\frac{{\rm signal}}{{\rm noise}}
+\propto \frac{(r/R)^2}{F^{-1/2}}
+\propto F^{1/2}
+\propto L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm incorrectly\ assumed})
+\end{equation}
+for $R$ the constant stellar radius, $F$ the photon flux, $L_{\rm sys}$ the 
+luminosity of a system, and $d$ its distance from us.
+At fixed planet radius, semimajor axis, stellar radius, and stellar luminosity,
+a constant signal-to-noise floor yields a maximum detectable 
+distance~\citep{pepper_using_2003,pepper_searching_2005}.
+The maximum distance out to which our binarity-ignoring astronomers 
+select stars, $d_{\rm sel}$, thus scales as $L_{\rm sys}^{1/2}$.
+
+The single stars have luminosity $L_1$, and the twin binaries have luminosity 
+$2L_1$.
+Thus the twin binaries are selected out to a distance $\sqrt{2}$ times 
+that of single stars.
+This is a bad move, because the transit signal for any planet in a 
+twin binary will be diluted by a factor of two:
+\begin{equation}
+\frac{{\rm signal}}{{\rm noise}}
+\propto \frac{\mathcal{D} (r/R)^2}{F^{-1/2}}
+\propto \mathcal{D} F^{1/2}
+\propto \mathcal{D} L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm true})
+\label{eq:snr_true}
+\end{equation}
+where the dilution is $\mathcal{D} \equiv L_{\rm host}/L_{\rm sys}$, for 
+$L_{\rm host}$ the the planet host's luminosity.
+This means that the true maximum searchable distance for binaries, $d_{\rm 
+    det}$, is $1/\sqrt{2}$ times that of single stars.
+The situation is illustrated in Fig.~\ref{fig:model_1_volumes}: only one in 
+eight selected stars in binaries are truly searchable.
+
+\begin{figure}[!tb]
+    \begin{center}
+        \includegraphics[width=0.6\textwidth]{figures/visualize_volumes.pdf}
+    \end{center}
+    \caption{
+        Cartoon of the searchable volumes for single stars ({\it left}), and 
+        twin binaries ({\it right}).
+        This model (\#1) assumes all stars have equal mass and luminosity, and 
+        all planets have the same true radius $r=r_p$.
+        {\it Top:} At an apparent radius $r\a=r_p$,
+        the observer selects twin binaries out to a larger         
+        distance, $\sqrt{2}\times$ that of single stars.
+        Because of dilution, there are no planets in twin binaries with 
+        $r\a=r_p$.
+        {\it Middle:} At an apparent radius $r\a=r_p/\sqrt{2}$, the 
+        searched volumes are half those at $r\a=r_p$. 
+        The only detected planets with $r\a=r_p/\sqrt{2}$ orbit twin binaries.
+        {\it Bottom:} Planets with a true radius $r=r_p$ are searchable to 
+        a maximum distance $d_0$ around singles, and $d_0/\sqrt{2}$ around 
+        twin binaries. These distances are the same as what an observer 
+        selects based on apparent radii.
+    }
+    \label{fig:model_1_volumes}
+\end{figure}
+
+\paragraph{What do the observers ignoring binarity infer?} 
+The binarity-ignoring observers assume that all points on the sky with flux 
+above some minimum are searchable.
+They correct their assumed number of searchable stars for the transit 
+probability.
+As a function of apparent radius, they then report an apparent rate density of
+\begin{equation}
+\Gamma_a(r_a) = 
+\delta(r_p) Z_0 \frac{N_0}{N_0+N_1}  +
+\delta\left(\frac{r_p}{\sqrt{2}}\right) 
+(Z_1 p_{{\rm det},1} + Z_2 p_{{\rm det},2}) \frac{N_1}{N_0+N_1},
+\label{eq:model_1_apparent_rate_density}
+\end{equation}
+where $p_{{\rm det},1}$ ($p_{{\rm det},2}$) is the probability that a selected 
+primary (secondary) is searchable.
+In this example, $p_{{\rm det},1}=p_{{\rm det},2}=1/8$; the detection 
+efficiency is the ratio of the searchable to selected volumes.
+
+The true rate density (Eq.~\ref{eq:model_1_rate_density}) and the
+apparent rate density (Eq.~\ref{eq:model_1_apparent_rate_density})
+differ in that
+\begin{enumerate}
+    \item The total number of selected stars, $N_{\rm tot} = N_0+N_1+N_2$, was 
+    miscounted.
+    %
+    \item The detection efficiency was incorrectly assumed to be $1$ for all 
+    selected stars. In reality, only one in eight binaries were searchable.
+    %
+    \item The inferred radii in binary systems are all $\sqrt{2}$ too small.
+\end{enumerate}
+
+To assess the severity of these errors, we need to make assumptions about the 
+stellar and planetary populations.
+The important quantity for the stellar population is $N_1/N_0$, the ratio of 
+selected primaries (or binaries) to singles. We can define
+\begin{align}
+\mu \equiv \frac{N_1}{N_0} &=
+\frac{n_b}{n_s} \left(\frac{d_{\rm sel,b}}{d_{\rm sel,s}}\right)^3 = 
+\frac{{\rm BF}}{1-{\rm BF}} (1+\ell)^{3/2},
+\label{eq:mu_definition}
+\end{align}
+where $n_b$ and $n_s$ are the number density of binaries and singles in a 
+volume limited sample, and the maximum selected distance for binary and single 
+systems are $d_{\rm sel,b}$ and $d_{\rm sel,s}$.
+The light ratio $\ell$ is defined relative to the primary, so that
+$L_{\rm sys} = L_1(1+\ell)$.
+The binary fraction in a volume limited sample is ``{\rm BF}''.
+For instance, \citet{raghavan_survey_2010} found a multiplicity 
+fraction\footnote{
+    The binary fraction is the fraction of systems in a volume-limited sample 
+    that are binary. It is equivalent to the multiplicity fraction if there 
+    are no triple, quadruple, or higher order multiples. In that case, ${\rm 
+        BF} = n_b / (n_s+n_b)$.
+} of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$. 
+``Twin binaries'' are perhaps 10-20\% of the binaries in a volume-limited 
+sample, depending on how ``twin'' is defined.
+Thus a representative twin binary fraction for this model is ${\rm BF}\approx 
+0.05$-$0.1$.
+
+Further, we need to assume knowledge of the true number of planets per 
+single, primary, and secondary star ($Z_0,Z_1,$ and $Z_2$).
+Taking $Z_0=Z_1=Z_2=1/2$, we plot the resulting occurrence rates as a function 
+of planet radius in Fig.~\ref{fig:occ_rate_model_1}.
+Though it is impossible for an observer to isolate any one of binarity's 
+biases without also addressing the others, mathematically it is simply a 
+matter of modifying the appropriate terms in 
+Eq.~\ref{eq:model_1_apparent_rate_density}.
+The resulting rates are also shown in 
+Fig.~\ref{fig:occ_rate_model_1}, and demonstrate how each 
+error individually affects the overall inferred rate.
+
+\begin{figure}[!tb]
+    \begin{center}
+        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
+    \end{center}
+    \vspace{-0.5cm}
+    \caption{
+        Inferred occurrence rates over $0.01r_\oplus$ bins in planet 
+        radius,for Model \#1.
+        This model has fixed stars, fixed planets, and twin binaries. 
+        Further, a twin binary fraction of ${\rm BF}=0.1$ is assumed, and all 
+        planets are {\bf TODO}.
+        If the true planet radius is $r_p$, all planets detected in binaries 
+        will have apparent radii $r_a = r_p/\sqrt{2}$.
+    }
+    \label{fig:occ_rate_model_1}
+\end{figure}
+
+\paragraph{Correction to inferred rate density and inferred rate}
+
+We define a rate density correction factor, $X_\Gamma$, as the ratio of the 
+apparent to true rate densities:
+\begin{equation}
+X_\Gamma \equiv \frac{\Gamma_a}{\Gamma}.
+\end{equation}
+This correction factor can be a function of whatever parameters $\Gamma_a$ and 
+$\Gamma$ depend on; in this study, the planet radius is most relevant.
+
+If we continue assuming that the number of planets per single, primary, and 
+secondary star are equal ($Z_0=Z_1=Z_2$), we find a rate density correction 
+factor at the true planet radius of
+\begin{equation}
+X_\Gamma(r_p) = \frac{1}{1+\mu},
+\label{eq:Z_eq_model_1_correction}
+\end{equation}
+This yields a correction of 0.76 if ${\rm BF}=0.1$, and 0.87 if ${\rm 
+    BF}=0.05$.
+Rephrasing the result, if the twin binary fraction were 
+$(2^{3/2}+1)^{-1}\approx 0.26$, then the apparent rate would be half the true 
+rate.
+Fortunately, in most contexts the twin binary fraction is not that high.
+
+An alternative assumption is that secondaries do not host planets. In that 
+case, $Z_0=Z_1$, and $Z_2=0$. The correction to the rate density at the true 
+planet radius becomes
+\begin{equation}
+X_\Gamma(r_p) = \frac{1+2\mu}{(1+\mu)^2}.
+\end{equation}
+This evaluates to 0.94 if ${\rm BF}=0.1$, and 0.98 if ${\rm BF}=0.05$.
+While it is hard to justify the assumption that secondaries are planet-less, 
+it is worth noting that $\Gamma_a/\Gamma$ is sensitive to the relative number 
+of planets per single, primary, and secondary.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Model \#2: fixed planets and primaries, varying secondaries}
+\label{sec:model_2}
+
+\begin{figure}[!tb]
+    \centering
+    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
+    \caption{
+        The mass ratio distribution for a magnitude-limited sample of 
+        binary stars, in which the underlying volume-limited distribution is 
+        uniform (qualitatively similar to {\it 
+            e.g.},~\citet{raghavan_survey_2010}'s Fig.~16).
+        The entire bias can be understood analytically 
+        (Eq.~\ref{eq:Malmquist_bias}).
+    }
+    \label{fig:q_distribn_mag_limited}
+\end{figure}
+
+Our binary-twin model provides a simple estimate of binarity's systematic 
+effects, but perhaps it is too simple.
+We begin introducing realism by first letting the light ratio $\ell = L_2/L_1$ 
+vary across the binary population.
+It does so because the underlying mass ratio $q=M_2/M_1$ varies.
+We keep the primary mass fixed as $M_1$, which is also the mass of all single 
+stars.
+
+We parametrize the distribution of binary mass ratios in a volume-limited 
+sample as a power law: $p(q)\propto q^\beta$.
+For binaries with solar-type primaries\footnote{
+    \citet{duchene_stellar_2013}, fitting all the multiple systems of 
+    \citet{raghavan_survey_2010}'s Fig 16, find $\beta = 0.28\pm0.05$ for 
+    $0.7<M_\star/M_\odot<1.3$.
+    Examining only the binary systems of \citeauthor{raghavan_survey_2010}'s 
+    Fig 
+    16, the distribution seems (by eye) to be roughly uniform, $\beta \approx 
+    0$, 
+    except for an excess of twin binaries with $q\approx 1$, and an obvious 
+    lack of $q<0.1$ stellar companions.
+}, $\beta$ is probably between 0 and 0.3.
+We further assume that stars are a one-parameter family, $R \propto M \propto 
+L^{1/\alpha}$, so that a drawn value of $q$ determines everything about a 
+secondary.
+
+The rate density in this model, $\Gamma(r,q)$, is the sum of the rate 
+densities for each system type:
+\begin{equation}
+\Gamma(r,q)
+=
+\delta(r_p) \times 
+\frac{N_0 Z_0 + N_1 Z_1 + N_2 Z_2 p_2(q)}{N_{\rm tot}}
+\label{eq:model2_rate_density}
+\end{equation}
+where $p_2(q)$ is mass-ratio dependent shape function in secondaries. A fully 
+general approach would parametrize $p_2(q)$ as a power law, $p_2(q) \propto 
+q^\gamma$. For simplicity we will always take $\gamma=0$, the uniform case.
+%We have written $\Gamma$ in terms of the mass ratio instead of the 
+%secondary star's radius for convenience ($q$ and $R_2$ are interchangeable).
+The interpretation of $Z_i$ is still ``the number of planets per star of 
+type $i$'', but now for secondaries this must include a marginalization 
+over both the mass ratio and the planet radius.
+
+There is also a Malmquist bias in Eq.~\ref{eq:model2_rate_density}, hidden 
+away in the numbers of selected stars.
+This is because the selected sample at a fixed planet radius and period is 
+magnitude-limited.
+Given a binary, the probability of drawing a mass ratio $q$ in a 
+magnitude-limited sample scales as
+\begin{equation}
+p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto q^\beta 
+(1+q^\alpha)^{3/2}
+\label{eq:Malmquist_bias}
+\end{equation}
+where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
+ratio $q$, and the latter term is the Malmquist bias.
+We show the magnitude-limited mass ratio distribution for the $\beta=0$ case 
+in Fig.~\ref{fig:q_distribn_mag_limited}.
+We emphasize that in Monte Carlo simulations of transit surveys, it is 
+important to draw binaries from the correctly biased mass-ratio distribution 
+\citep[\textit{e.g.},][]{bakos_hatsouth:_2013,sullivan_transiting_2015,
+    gunther_new_2017}.
+
+The occurrence rate corresponding to Eq.~\ref{eq:model2_rate_density}'s rate 
+density for specific mass ratios of interest $q_{\rm min} < q < q_{\rm 
+    max}$ is then
+\begin{equation}
+\Lambda|_{r_p,q_{\rm min},q_{\rm max}} = 
+\frac{N_0 Z_0 + N_1 Z_1 + N_2 Z_2 f_2}
+{N_{\rm tot}},
+\end{equation}
+for
+\begin{equation}
+f_2 \equiv
+\int_{q_{\rm min}}^{q_{\rm max}} p_2(q) \,{\rm d}q,
+\end{equation}
+where $p_2(q)\propto q^\gamma$, and is normalized to unity.
+
+\paragraph{What do the observers ignoring binarity infer?}
+As a reminder, the binary-ignoring observers compute an apparent rate density 
+by correcting the number of detections per star for the transit probability 
+and the detection efficiency.
+In this process, they make the following errors:
+\begin{enumerate}
+    \item They assume that they have selected $N_0+N_1$ stars, while they have 
+    actually selected $N_0+N_1+N_2$.
+    %
+    \item They assume that every star within the maximum selected distance is 
+    searchable.
+    This is true for single stars.
+    For binaries, the actual detection efficiency is the ratio of the number 
+    of 
+    searchable stars to the number of selected stars.
+    For primaries,
+    \begin{equation}
+    p_{\rm det,1} = \left(\frac{d_{\rm det,1}}{d_{\rm sel}}\right)^3
+    = \mathcal{D}_1^3 = (1+q^\alpha)^{-3},
+    \label{eq:model_2_p_det_1}
+    \end{equation}
+    where we have assumed that all single stars and primaries have the same 
+    properties, and have used $\ell = q^\alpha$.
+    For secondaries,
+    \begin{equation}
+    p_{\rm det,2} = \left(\frac{d_{\rm det,2}}{d_{\rm sel}}\right)^3
+    = \mathcal{D}_2^3 \left(\frac{R_1}{R_2}\right)^6
+    \left(\frac{T_{\rm dur,2}}{T_{\rm dur,1}}\right)^{3/2} 
+    = (1+q^{-\alpha})^{-3} q^{-5},
+    \label{eq:model_2_p_det_2}
+    \end{equation}
+    where subscripts `1' and `2' correspond to primaries and secondaries, and 
+    we 
+    used the scaling relation $T_{\rm dur}\propto \rho_\star^{-1/3} \propto 
+    R_\star^{2/3}$.
+    %
+    \item They assume a transit probability for all stars of $p_{\rm tra} = 
+    R_\star/a$. 
+    For planets orbiting secondaries at fixed period, the true transit 
+    probability 
+    is $q^{2/3} p_{\rm tra}$, since the secondaries have smaller radii and 
+    masses.
+    %
+    \item The true planetary radii $r$ are interpreted as apparent radii $r_a$.
+    In binaries, the apparent radii depend on whether the host is the primary 
+    or 
+    secondary:
+    \begin{align}
+    r_a
+    &=
+    \left.
+    \begin{cases}
+    r_p (1+q^\alpha)^{-1/2} & \text{for } i=1,\ {\rm primary} \\
+    r_p (1+q^{-\alpha})^{-1/2} q^{-1}, & \text{for } i=2,\ {\rm secondary}.
+    \end{cases}
+    \right.
+    \label{eq:model2_ra}
+    \end{align}
+    The factor of $q^{-1}$ for the secondary case accounts for the observer 
+    assuming all transit signals come from stars of fixed size.
+\end{enumerate}
+
+To write the apparent rate density as a function of the apparent 
+radius $r_a$, we marginalize out the planet period, semimajor axis, and 
+stellar radius (or equivalently the mass ratio, for binaries):
+\begin{equation}
+\Gamma_a(r_a) =
+\frac{N_0}{N_0+N_1} Z_0 \delta(r_p)
++
+\frac{N_1}{N_0+N_1} \left( Z_1 I_1(r_a)
++
+Z_2 I_2(r_a) \right).
+\label{eq:model2_Gamma_a}
+\end{equation}
+The ratio of primaries to singles, $\mu=N_1/N_0$, is now less than 
+that of Model \#1 (cf. Eq.~\ref{eq:mu_definition}). This is because a 
+distribution of light 
+ratios $\ell$ leads to a distribution of maximum selected distances. 
+Integrating over the mass ratios from $q=0$ to $1$, one finds a
+dimensionless integral
+\begin{equation}
+\mu \equiv \frac{N_1}{N_0} = \frac{\rm BF}{1 - {\rm BF}} \left(2^{3/2} - 
+\int_{1}^{\sqrt{2}} u^2 (u^2 -1)^{1/\alpha} \,{\rm d}u\right).
+\label{eq:mu_model_2}
+\end{equation}
+
+Given a binary fraction, Eq.~\ref{eq:mu_model_2} fully specifies the 
+``weights'' in Eq.~\ref{eq:model2_Gamma_a}.
+The $I_1(r_a)$ and $I_2(r_a)$ terms are found by marginalizing over the joint 
+distribution of apparent radius and mass ratio:
+\begin{align}
+I_i(r_a) &= 
+\int_0^1 p({\rm has\ detected\ planet}, r_a, q | {\rm star\ is\ type\ }i)
+\,{\rm d}q,
+\quad
+{\rm for}\ i\in\{1, 2\}, \\
+&=
+\int_0^1 
+p({\rm has\ detected\ planet} | r_a, q, {\rm star\ is\ type\ }i) 
+\nonumber\\
+&\quad\quad\quad\quad\times p(r_a | q, {\rm star\ is\ type\ }i)
+\,p(q | {\rm star\ is\ type\ }i)
+\,{\rm d}q.
+\end{align}
+The first term is the detection efficiency; the second is a $\delta$-function 
+of the apparent radius; the last is the mass ratio distribution given by 
+Eq.~\ref{eq:Malmquist_bias}.
+An analytic solution can be found for $i=1$.
+For $i=2$ there is no analytic solution, because evaluating the integral 
+requires imposing the constraint that $r_a  = r_p 
+(1+q^{-\alpha})^{-1/2}q^{-1}$. This equation can be re-written
+\begin{equation}
+\left(\frac{r_p}{r_a}\right)^2 = q^2 + q^{-\alpha + 2},
+\end{equation}
+which has no analytic solution for $q(r_a)$ except for special values of 
+$\alpha$, the mass-luminosity exponent.
+For $\alpha=3.5$, our nominal case, semianalytic solutions do exist.
+However, since our main interest is in understanding the qualitative behavior 
+of the solutions, we derive a limiting case, and then proceed 
+numerically.
+
+\begin{comment}
+The analytic solution for $i=1$ is something like
+\begin{equation}
+I_1(r_a) = \frac{1}{\mathcal{N}_1} \left(\frac{r_p}{r_a}\right)^{-3}
+\left( \left(\frac{r_p}{r_a}\right)^2 -1  
+\right)^{\frac{\gamma+\beta}{\alpha}},
+\quad {\rm for}\ r_p/\sqrt{2} < r_a < r_p,
+\end{equation}
+where $\mathcal{N}_1$ is the normalization term of the binary mass ratio 
+distribution (Eq.~\ref{eq:model_2_p_2}): $\mathcal{N}_1 = \int_0^1 
+q^{\gamma+\beta} (1+q^\alpha)^{3/2} {\rm d}q$.
+\end{comment}
+
+\paragraph{Limiting case of rate density correction}
+Recall that the rate density correction factor, $X_\Gamma$, is the ratio of 
+the apparent to true rate densities.
+We consider a ``nominal model'' in which the stellar population is similar to 
+Sun-like stars in the local neighborhood:
+${\rm BF}=0.44$, $\alpha=3.5$, $\beta=0$.
+Our default assumption is also that the occurrence of planets is independent 
+of stellar mass ($\gamma=0$), so secondaries have the same occurrence rate as 
+primaries and single stars.
+Under these assumptions, the true rate density is
+\begin{equation}
+\Gamma(r) \approx \delta(r_p) \left( Z_0 + Z_1 + 
+Z_2 \right) / 3,
+\label{eq:model2_Gamma_r}
+\end{equation}
+where the coefficients of $1/3$ are accurate to within one percent of the true 
+coefficients.
+Ignoring binarity, the observer finds an apparent rate density
+\begin{equation}
+\Gamma_a(r) = c_0 Z_0 \delta(r_p)
++c_1 Z_1 I_1(r_a)
++c_2 Z_2 I_2(r_a),
+\label{eq:model2_Gamma_a_r}
+\end{equation}
+for $c_0\approx 0.49$, and the coefficients $c_1, c_2$ unknown.
+%171011_integrals.nb $c_1\approx 0.32$
+We can evaluate the correction term at $r=r_p$, since $\lim_{r_a\rightarrow 
+    r_p} I_i(r_a)=0$ for $i\in\{1,2\}$:
+\begin{equation}
+X_\Gamma(r=r_p) \approx \frac{3c_0 \Lambda_0}{\Lambda_0+\Lambda_1+\Lambda_2}.
+\end{equation}
+If all the $Z_i$'s are equal, $X_\Gamma(r=r_p)\approx0.49$.
+If there are no planets around the secondaries, $X_\Gamma(r=r_p)\approx0.74$.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_logs_model_2.pdf}
+\caption{
+Inferred planet occurrence rates as a function of planet radius in Model \#2. 
+This model has fixed planets and primaries, and varying secondary masses, 
+radii, and luminosities.
+}
+\label{fig:occ_rate_model_2_log}
+\end{figure}
+
+\paragraph{Numerical approach}
+To maintain simplicity, we develop a Monte Carlo program to simulate our 
+toy transit surveys.
+The program generates a stellar population, assigns planets to the stars, and 
+then calculates which planets are detectable.
+It then computes the apparent and true planet occurrence rates as a function 
+of planet radius.
+We discuss the details below, and refer the interested reader to our online 
+implementation\footnote{\url{https://github.com/lgbouma/binary_biases}}.
+
+First, the user must specify the free parameters that describe the 
+stellar and planetary population. These values include the binary fraction, 
+and the true planet occurrence rates around single stars, primaries, and 
+secondaries (the $Z_i$'s; recall Eq.~\ref{eq:rate_density_shape}).
+There is also an arbitrary absolute number of selected stars.
+
+Once the user specifies the free parameters, the program constructs a 
+population of selected stars.
+Each selected star is assigned a type (single, primary, secondary), a 
+binary mass ratio (if it is not single), and the property of whether it is 
+``searchable''.
+The relative number of binaries to primaries is set by 
+Eq.~\ref{eq:mu_model_2}.
+The mass ratios are drawn from the appropriate magnitude-limited distribution 
+(Eq.~\ref{eq:Malmquist_bias}).
+If it is single, a selected star is assumed to be searchable.
+If it is a primary or secondary, its searchability is determined by a uniform 
+draw from either Eq.~\ref{eq:model_2_p_det_1} or Eq.~\ref{eq:model_2_p_det_2}, 
+as appropriate.
+
+Assigning planets, each selected star receives a planet at the rate $Z_i$, 
+according to its type.
+The radii of planets are assigned independently of any host system property, 
+and can be sampled for an arbitrary distribution ({\it e.g.}, power law; delta 
+function).
+The absolute transit probability, $p_{\rm tra}$ is set arbitrarily, and the 
+probability of a planet transiting a secondary is set as $q^{2/3}\times p_{\rm 
+    tra}$.
+A planet is ``detected'' when a) it transits, and b) its host star is 
+searchable.
+For detected planets, apparent radii are computed according to analytic 
+formulae that account for both dilution and the misclassification of stellar 
+radii (Eq.~\ref{eq:model2_ra}).
+We assume that the observers think that all transits are around single stars.
+
+We then compute rates in bins of true planet radius and apparent planet radius.
+In a given radius bin, the true rate is found by counting the number of planets
+that exist around selected stars of all types (singles, primaries,
+secondaries), and dividing by the total number of these stars.
+The apparent rates are found by counting the number of detected planets that
+were found in an apparent radius bin, dividing by the geometric transit
+probability for single stars, and dividing by the apparent total number of
+stars.
+
+\paragraph{Numerical results for Model \#2}
+We first validate our model by ensuring it produces the analytically-predicted 
+results for Model \#1, and the limiting case of Model \#2 described above.
+Following validation, we assume ${\rm BF}=0.44$, $\alpha=3.5$, 
+$\beta=\gamma=0$, and take $Z_0=Z_1=Z_2=0.5$. We then compute the true and 
+apparent occurrence rates over bins in planet radius.
+The results are shown in Fig.~\ref{fig:occ_rate_model_2}.
+Evidently, dilution produces a spectrum of apparent planetary radii. This 
+leads to overestimated rates everywhere except where at the true planet 
+radius, where the rate is underestimated by a factor of two.
+Compared to Model \#1 (Fig.~\ref{fig:occ_rate_model_1}), the general picture 
+is that the apparent radius distribution is ``blurred'' by the varying 
+secondary light ratios.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Model \#3: Fixed primaries, varying planets and secondaries}
+\label{sec:model_3}
+
+As in the previous model, all single and primary stars in this model have 
+identical properties.
+The secondaries have masses, radii, and luminosities that vary between 
+systems: $M\propto R \propto L^{1/\alpha}$.
+The only addition is that we now let the radii of planets vary: they are 
+assigned independently of any host system property, and are sampled from the 
+true radius distribution, which we take as
+\begin{align}
+p_r(r)
+&\propto
+\left.
+\begin{cases}
+r^\delta & \text{for } r\geq 2r_\oplus \\
+{\rm constant} & \text{for } r\leq2r_\oplus.
+\end{cases}
+\right.
+\label{eq:model3_radius_distribution}
+\end{align}
+Following~\citet{howard_planet_2012}'s measurement, we take $\delta = -2.92$.
+Our ``nominal model'' remains the same: the binary fraction is 0.44, 
+$\alpha=3.5$, $\beta=\gamma=0$.
+We take $Z_i$, the number of planets per single, primary, and secondary, to be 
+equal.
+
+For this model, we forgo analytic development and simply run our Monte Carlo 
+program\footnote{
+    One might worry that our Monte Carlo program does not increase the number 
+    of 
+    selected stars as the square of the planet radius (Eq.~\ref{eq:snr_true}).
+    We can omit this dependence because in our model $N_1/N_0$ is independent 
+    of 
+    desired planet radius, and all other terms in the rate densities ({\it 
+    e.g.}, 
+    Eqs.~\ref{eq:model2_rate_density} and~\ref{eq:model2_Gamma_a}) are 
+    independent 
+    of the number of selected stars.
+}.
+The resulting occurrence rates are shown in 
+Fig.~\ref{fig:occ_rate_model_3_log}.
+For the assumed planetary and stellar distributions, the inferred rate is 
+underestimated over all radii.
+
+\begin{figure}[!tb]
+\centering
+\epsscale{1.15}
+\plottwo{figures/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf}
+\caption{
+{\it Left:} rate density and {\it right:} rate as a 
+function of planet radius in Model \#3. This model has fixed primaries and 
+single stars, but varying secondaries. The true planet radius distribution is 
+a power law with exponent $-2.92$ above $2r_\oplus$, below which it is uniform 
+\citep[similar to][]{howard_planet_2012}.
+\label{fig:occ_rate_model_3_log}}
+\end{figure}
+
+\paragraph{Hot Jupiter occurrence rates}
+Taking Fig.~\ref{fig:occ_rate_model_3_log} and counting the number of planets 
+per star with $r>8r_\oplus$, we can compare the true and inferred hot Jupiter 
+occurrence rates.
+Under the above assumptions, the true rate is 9.1 hot Jupiters 
+per thousand stars.
+The inferred rate is 6.9 per thousand stars.
+This means that the inferred rate underestimates the true rate by a 
+multiplicative factor of $\sim\!1.3$.
+
+However, this result only applies under the assumption that $Z_0 = 
+Z_1 = Z_2$.
+If hot Jupiters are less common around lower mass stars, it would be more 
+sensible to consider $Z_2<Z_0$, while letting single stars and 
+primaries host planets at the same rate.
+Therefore in Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues} we let 
+$Z_2$ vary, and show the resulting inferred and true hot Jupiter 
+($r>8r_\oplus$) rates.
+The result is that the inferred rate is nearly independent of 
+$Z_2$~--~this is because most ($<1/10$) secondaries are not searchable, 
+and so their completeness fraction is much smaller than that of primaries or 
+single stars.
+This means far fewer detected hot Jupiters orbit secondaries, and so they 
+hardly affect the inferred rate.
+While the ``true rate'' across the entire population is linearly dependent on 
+$Z_2$, the rate around 
+singles and primaries (Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues} 
+green line) is independent of that around secondaries.
+
+\begin{figure}[!tb]
+    \centering
+    \includegraphics[width=.6\textwidth]{figures/HJ_correction_inputrate_vs_HJratevalues.pdf}
+    \caption{
+        $Z_i$ is the occurrence rate integrated over all possible phase 
+        space for the $i^{\rm th}$ system type. $Z_2/Z_0=1$ 
+        corresponds to an equal number of planets per secondary as per single 
+        star;
+        $Z_2/Z_0=0$ corresponds to secondaries not having any 
+        planets.
+        In our Model \#3, though the true HJ occurrence rate 
+        is highly dependent on $Z_2$, 
+        the inferred rate hardly depends on whether secondaries have HJs.
+        This means that the ``correction factor'' between the inferred rate 
+        and the true rate around single stars is underestimated by a 
+        multiplicative 
+        factor of $\approx1.3$, independent of the HJ rate around secondaries.
+        The ``HJ rate'' is the summed rate from     
+        Fig.~\ref{fig:occ_rate_model_3_log} above $8r_\oplus$.
+    }
+    \label{fig:HJ_correction_inputrate_vs_HJratevalues}
+\end{figure}
+
+\paragraph{The rate of Earth analogs}
+This model provides an estimate of the apparent and true 
+rates as a function of radius (Fig.~\ref{fig:occ_rate_model_3_log}).
+At Earth's radius, the result is that the inferred rate is $0.84\times$ the 
+true rate around single stars, assuming that the $Z_i$'s are equal.
+Similar to the above case of the hot Jupiters, if we vary the true $Z_2$ 
+while keeping $Z_0 = Z_1$, the ratio of the inferred to true rate 
+around single stars changes by only a few percent (shown in 
+Fig.~\ref{fig:earth_inputrate_vs_etaearthratevalues}).
+The ratio of the inferred to the true rate, $(\Lambda_{\rm 
+    inferred}/\Lambda)_{r=r_\oplus}$ varies substantially, but by at most 
+$50\%$ 
+in the (unrealistic) limiting case that secondaries do not host planets.
+
+\begin{figure}[!tb]
+    \centering
+    \includegraphics[width=.6\textwidth]{figures/earth_inputrate_vs_etaearthratevalues.pdf}
+    \caption{
+        Same as Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues}, but 
+        for Earth-sized planets.
+        The absolute values given on the $y$-axis found by summing the rate 
+        from Fig.~\ref{fig:occ_rate_model_3_log} for planetary radii from 
+        $0.5$ to $1.5r_\oplus$ (this is a toy model, and they do not reflect 
+        an actual determination of $\eta_\oplus$).
+        The relative values show that the inferred rate for Earths is roughly 
+        independent of the occurrence rate (integrated over all radii) around 
+        secondaries.
+        However, it is systematically lower than the true rate around single 
+        and primary stars, by $\approx 20\%$.
+    }
+    \label{fig:earth_inputrate_vs_etaearthratevalues}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\input{discussion}
+
+\section{Discussion}
+\label{sec:discussion}
+
+\paragraph{How has binarity been considered in occurrence rate measurements?}
+Binarity introduces systematic uncertainty to star and planet counts, and also 
+to estimates of pipeline completeness.
+In spite of this fact, stellar multiplicity has mostly been ignored in 
+calculations of planet occurrence rates using transit survey data\footnote{
+    A list of occurrence rate papers is maintained at 
+    \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
+}~
+\citep[\textit{e.g.},][]{howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,dressing_occurrence_2015,burke_terrestrial_2015}.
+For {\it Kepler} occurrence rates specifically, it seems that no one has yet 
+carefully assessed binarity's importance, or lack thereof.
+While we do not resolve the problem, we do suggest
+the approximate scale of the necessary corrections in a survey-independent 
+manner.
+
+Of course, on a system-by-system level stellar multiplicity affects the 
+interpretation of planet candidates. High resolution imaging 
+campaigns have measured the multiplicity of almost all {\it Kepler}\ Objects 
+of Interest 
+\citep{howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
+    horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
+    law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
+    wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016}.
+The results of these programs have been collected 
+by~\citet{furlan_kepler_2017}, and they represent an important advance in 
+understanding the KOI 
+sample's multiplicity statistics.
+In particular, they can be immediately applied to rectify binarity's effects 
+on the mass-radius diagram~\citep{furlan_densities_2017}.
+
+The high resolution imaging campaign is also beginning to connect with
+occurrence rate calculations.
+The most recent rate studies have used~\citet{furlan_kepler_2017}'s 
+catalog to test the effects of removing KOI hosts with known companions, which 
+helps reduce contamination in the ``numerator'' of 
+the occurrence rate (\citealt{fulton_california-_2017}; Petigura et al.\! 2018,
+in preparation).
+However, without an understanding of the multiplicity statistics of the 
+non-KOI stars, the true completeness, and thus the true 
+occurrence rates, will remain biased.
+The first-order correction that we suggest, given the impracticality of 
+performing high-resolution imaging of every selected star in a transit survey,
+is to model the detection pipeline's efficiency while accounting for 
+binarity.
+%Simply put~--~do not assume binarity can be ignored, and take the relevant 
+%systematic uncertainties about the selected stars into account.
+For {\it Kepler}, this would require high resolution imaging of a
+comparison sample of non-KOI host stars. If the associated multiplicity 
+statistics are then included in a model of the pipeline's detection 
+efficiency, and the number of selected stars is appropriately counted, it 
+would correct most of binarity's biases.
+
+\paragraph{The hot Jupiter rate discrepancy}
+\begin{figure}[!tb]
+    \centering
+    \includegraphics[width=.6\textwidth]{figures/int_rate_density_vs_radius_model_7_rpu_22.5_manyZs.pdf}
+    \caption{
+        HJ rate, if it were Gaussian.
+    }
+    \label{fig:gaussian_HJ}
+\end{figure}
+
+There is at least one context in which ignoring binarity may already be 
+leading to discrepant measurements.
+Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
+marginally lower than those found by radial velocity surveys ($\approx 1\%$; 
+see Table~\ref{tab:hj_rates}).
+Though the discrepancy has weak statistical significance ($<3\sigma$),
+one reason to expect a difference is that the corresponding stellar 
+populations have distinct metallicities.
+As argued by \citet{gould_frequency_2006}, the RV sample is biased towards 
+metal-rich stars, which have been measured by RV surveys to preferentially 
+host more giant 
+planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005}.
+Investigating the discrepancy from the metallicty 
+angle,~\citet{guo_metallicity_2017} measured the
+{\it Kepler} field's mean metallicity to be $[{\rm M/H}]_{\rm Kepler}= 
+-0.045\pm0.009$, which is lower than the California Planet Search's mean of 
+$[{\rm M/H}]_{\rm CPS}= -0.005\pm0.006$.
+The former value agrees with that measured by \citet{dong_metallicities_2014}.
+Based on their measurements, \citeauthor{guo_metallicity_2017}\! 
+then argued that the metallicity difference could account for a $\approx 20\%$ 
+relative difference in the measured rates between the CKS and {\it Kepler}\ 
+samples~--~not a factor of two.
+\citeauthor{guo_metallicity_2017}\! concluded that ``other factors, such as 
+binary contamination and imperfect stellar properties'' must also be at play.
+
+Aside from surveying stars of varying metallicities, radial velocity and 
+transit surveys differ in how they treat binarity.
+Radial velocity surveys typically reject both visual and spectroscopic binaries
+\citep[\textit{e.g.},][]{wright_frequency_2012}.
+Transit surveys typically observe binaries, but the question of whether they 
+were searchable to begin with is left for later interpretation.
+In spectroscopic follow-up of candidate transiting planets, the prevalence of 
+astrophysical false-positives may also lead to a bias against confirmation of 
+transiting planets in binary systems.
+
+Ignoring these complications, in this work we showed that
+binarity biases transit survey occurrence rates through its effects on 
+completeness, star counts, and the apparent radii of detected planets.
+Specifically, our results from Sec.~\ref{sec:model_3} indicate that binarity 
+could lead to underestimated HJ rates by a multiplicative factor of $\approx 
+1.3$.
+
+To assess the effect this might have towards resolving the hot Jupiter rate 
+discrepancy we ask:
+what is the probability of \citet{wright_frequency_2012}'s result, given a 
+rate drawn from the stated bounds of Petigura et al.~(2018, in preparation)?
+In other words, we first take the true HJ rate per thousand stars as 
+$\Lambda_{\rm HJ} = 5.7 \pm 1.3$, with Gaussian uncertainties. 
+We then draw from a Poisson distribution and compute the probability of 
+detecting at least 10 hot Jupiters in a sample of 836 stars.
+Without accounting for binarity or metallicity, only 4\% of RV surveys would 
+detect at least 10 hot Jupiters.
+If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account for 
+~\citet{guo_metallicity_2017}'s measured metallicity difference between the 
+{\it Kepler}\ field and the local solar neighborhood, 9\% of RV surveys would 
+detect at least 10 hot Jupiters.
+If we multiply once more by $1.3$ to account for binarity's bias, we find that
+23\% of RV surveys would detect at least 10 hot Jupiters, and any discrepancy 
+would be rather tenuous.
+We emphasize that this result is only suggestive~--~a true resolution of the 
+rate discrepancy would likely require a detailed understanding of the {\it 
+    Kepler}\ field's multiplicity statistics.
+
+\paragraph{The rate of Earth analogs}
+Per {\it Kepler}'s primary science objective, the rate of Earth-like planets 
+orbiting Sun-like stars has been independently measured by 
+\citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
+    foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
+These efforts have found that the one-year terrestrial planet occurrence rate 
+varies between $\approx 0.03$ and $\approx 1$ per Sun-like star, depending on 
+assumptions that are made when retrieving the rate 
+(\citet{burke_terrestrial_2015}'s Fig.~17).
+In our Model \#3, the inferred rate is $\approx 0.84\times$ the true rate 
+around single stars.
+This bias is quite small compared to the other systematic factors that 
+currently dominate the dispersion in $\eta_\oplus$ measurements.
+If a future analyses determine absolute values of $\eta_\oplus$ to 
+better than a factor of two, binarity might merit closer attention.
+
+One relevant caveat to our assessment of binarity's importance for 
+$\eta_\oplus$ measurements is that none of our models 
+included the rate density's period-dependence. However, close binaries usually
+provoke dynamical instabilities, leading to fewer long-period planets per 
+star~\citep[\textit{e.g.},][]{holman_long-term_1999,wang_influence_2014,
+    kraus_impact_2016}.
+This effect might further bias transit survey measurements of $\eta_\oplus$
+beyond our rough estimate.
+
+\paragraph{Precise features of the radius valley}
+
+\begin{figure}[!tb]
+    \centering
+    \epsscale{1.15}
+    \plottwo{figures/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf}
+    \caption{
+        {\it Left:} rate density and {\it right:} rate as a 
+        function of planet radius in a model with a radius gap 
+        (Eq.~\ref{eq:model4_radius_distribution}).
+        Similar to Model \#3, this model has fixed primaries and single stars, 
+        but varying secondaries.
+    }
+    \label{fig:model_4}
+\end{figure}
+
+Using improved stellar parameters measured by the California-{\it Kepler} 
+survey,~\citet{fulton_california-_2017} recently reported a ``gap'' in 
+the radius-period 
+plane~\citep{petigura_california-kepler_2017,johnson_california-kepler_2017}.
+The existence of the gap has been independently corroborated from a sample of 
+KOIs with asteroseismically-determined stellar 
+parameters~\citep{van_eylen_asteroseismic_2017}.
+Precise measurement of the gap's features, in particular its width, 
+depth, and shape, will require more accurate occurrence rates.
+To illustrate binarity's role in the issue, we make identical assumptions as 
+in Model \#3, but instead assume an intrinsic radius distribution
+\begin{align}
+p_r(r)
+&\propto
+\left.
+\begin{cases}
+r^\delta & \text{for } r\geq 2r_\oplus, \\
+0 & \text{for } 1.5r_\oplus < r < 2r_\oplus, \\
+{\rm constant} & \text{for } r\leq1.5r_\oplus.
+\end{cases}
+\right.
+\label{eq:model4_radius_distribution}
+\end{align}
+The resulting true and inferred rates are shown in Fig.~\ref{fig:model_4}.
+If left uncorrected, binarity makes the gap appear more shallow, and flattens 
+the step-function edges.
+At present though, binarity seems less important than other effects that would 
+``blur'' the gap in the planet radius dimension. 
+In particular, the valley's period-dependence is almost certainly not flat
+\citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.
+This means that any study assessing its width, depth, etc. only in the planet 
+radius dimension must first account for the blurring that comes from 
+marginalizing over the periods.
+
+\paragraph{Does a detected planet orbit the primary or secondary?}
+\citet{ciardi_understanding_2015} studied the effects of stellar multiplicity 
+on the planet radii derived from transit surveys.
+They modeled the problem for {\it Kepler}\ objects of interest by matching a 
+population of binary and tertiary companions to KOI stars, 
+under the assumption that the KIC-listed stars were the primaries.
+They then computed planet radius correction factors assuming that {\it 
+    Kepler}-detected planets orbited the primary or companion stars
+with equal probability (their Sec. 5).
+Under these assumptions, they found that any given planet's radius is on 
+average underestimated by a multiplicative factor of 1.5.
+
+Our models show that assuming a detected planet has equal probability of 
+orbiting the primary or secondary leads to an overestimate of
+binarity's population-level effects.
+A planet orbiting the secondary does lead to extreme corrections, but these 
+cases are rare outliers, because the searchable volume for secondaries is so 
+much smaller than that for primaries.
+Phrased in terms of the completeness, in our Model \#3 only $\sim 6\%$ of 
+selected secondaries are searchable, compared to $\sim 60\%$ of selected 
+primaries.
+This means that when high-resolution imaging discovers a binary companion in 
+a system that hosts a detected transiting planet, the planet is much
+more likely to orbit the primary.
+This statement is independent of the fact that planets are often confirmed to 
+orbit the primary by inferring the stellar density from the transit duration.
+
+\paragraph{On the utility for future occurrence rate measurements}
+{\it TESS}\ is expected to discover over $10^4$ giant 
+planets~\citep{sullivan_transiting_2015}.
+Though they will be difficult to distinguish from false positives, one 
+possible use of this overwhelmingly large sample will to measure an
+occurrence rate of short-period giant planets.
+Our work indicates that if this measurement is to be more accurate than $\sim 
+30\%$, binarity cannot be neglected.
+
+\paragraph{Independent approaches for estimating binarity's effects}
+T. Barclay et al.\! (in preparation) have performed the exercise of taking 
+stars selected by the {\it Kepler}\ team, pairing them with a population of 
+secondaries, injecting a realistic distribution of planet radii, 
+and then comparing the inferred occurrence rates with the true ones.
+In their model, they find that binarity leads to an inferred rate of 
+Earth-sized planets $\approx 10\%$ less than the true rate.
+In our Model \#3, if all $Z_i$'s are equal (a plausible assumption in 
+the lack of evidence to the contrary), the underestimate is by a comparable 
+16\%.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\input{conclusion}
+
+\section{Conclusion}
+\label{sec:conclusion}
+
+This study presented three simple models for the effects of binarity on 
+occurrence rates measured by transit surveys.
+The simplest of these models (Model \#1) provides an order-of-magnitude 
+estimate of how much binarity biases occurrence rates.
+The most realistic of these models (Model \#3) suggests that binarity does 
+lead to underestimates in transit survey occurrence rates, but with less than 
+$30\%$ relative error.
+The model further suggests that hot Jupiter rates measured by transit surveys 
+are biased to infer $\approx 1.3\times$ fewer hot Jupiters per star than 
+surveys that only measure occurrence rates about single stars ({\it 
+    i.e..,} radial velocity surveys).
+It also indicates that binarity's effects on the measured 
+rates of Earth-sized planets are far smaller than current 
+systematic uncertainties.
+Though our models are simplistic, their agreement with T. Barclay's recent 
+independent simulations indicate that they capture the essential 
+ingredients.
 
 %\acknowledgements
-%It was a pleasure to share discussions with Kento Masuda, who pointed us in 
-%this direction, and helped clarify that something like this was worth studying.
+%It was a pleasure discussing this work with F. Dai and T. Barclay.
 
+\newpage
 \input{hj_rates.tex}
 
+\newpage
+\bibliographystyle{yahapj}                            
+\bibliography{bibliography}
+
 \end{document}

### 2017-12-15 paper/simplest_effects.tex
paper: update figures and captions.

@@
     \begin{center}
-        \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_model_1_brokenx.pdf}
+        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
     \end{center}
@@
     \caption{
-        Inferred planet occurrence rates over $0.01r_\oplus$ bins in planet 
-        radius,
-        for Model \#1.
+        Inferred occurrence rates over $0.01r_\oplus$ bins in planet 
+        radius,for Model \#1.
         This model has fixed stars, fixed planets, and twin binaries. 
-        It assumes a twin binary fraction of ${\rm BF}=0.1$.
-        If the true planet radius is $r_p$, all planets 
-        detected in binaries will have apparent radii $r_a = r_p/\sqrt{2}$.
-        We illustrate the individual biases by separating them.
-        On this and future plots,
-        ``only wrong $N_\star$'' means the only error is an incorrectly 
-        assumed 
-        number of selected stars;
-        ``only wrong $Q$'' means the only error is an incorrectly assumed 
-        completeness (including both miscalculated $p_{\rm tra}$ 
-        and fraction of selected stars that are searchable, $p_{\rm det}$);
-        ``only wrong $r_a$'' means the only error is in miscalculated        
-        planetary radii, due to both transit depth dilution and also wrongly 
-        assumed host star radii.
+        Further, a twin binary fraction of ${\rm BF}=0.1$ is assumed, and all 
+        planets are {\bf TODO}.
+        If the true planet radius is $r_p$, all planets detected in binaries 
+        will have apparent radii $r_a = r_p/\sqrt{2}$.
     }

### 2017-12-16 paper/main.tex
paper: further figure edits
paper: updating text (WIP)

@@
 \newcommand{\s}{_{\rm s}}
+\renewcommand{\d}{_{\rm d}}
 \begin{document}
@@
 
-A group of astronomers wants to measure the mean number of planets of a 
-certain type per star of a certain type.
-Ignoring stellar multiplicity, they perform a signal-to-noise limited transit 
-survey, and detect a set of planets that appear to be of the desired class.
-They then choose the stars (among those initially surveyed) around which the 
+A group of binarity-ignoring astronomers wants to measure the mean number of 
+planets of a certain type per star of a certain type.
+They perform a wide-field photometric search for planets that transit, and 
+discover all for which
+\begin{equation}
+\left(\frac{{\rm S}}{{\rm N}}\right)
+= ({\rm const}) \cdot \delta_{\rm obs} L_{\rm sys}^{1/2} d^{-1}
+> \left(\frac{{\rm S}}{{\rm N}}\right)_{\rm floor}.
+\label{eq:S_N_thresh}
+\end{equation}
+The observed transit depth $\delta_{\rm obs}$ constitutes the signal, ${\rm 
+S}$. The survey is shot-noise dominated, and so the noise ${\rm N}$
+scales as the inverse root of the photon flux received from any stellar 
+system, ${\rm N} \propto (L_{\rm sys}/d^2)^{-1/2}$, for $L_{\rm sys}$ the 
+system luminosity and $d$ its distance.
+The solid angle coverage, telescope area, and survey duration are part of the 
+``const'' term of Eq.~\ref{eq:S_N_thresh}. The transit duration also 
+affects detectability, but we omit it in this work for brevity.
+
+To compute an occurrence, at every planetary and stellar property the 
+astronomers choose the stars (among those initially surveyed) around which the 
 planets of interest appeared to be searchable.
@@
 \begin{equation}
-\Gamma\a(\pp\a, \ps\a) = \frac{N_{\rm det}(\pp\a, \ps\a)}{N_{\rm s,a}(\pp\a, 
+\Gamma\a(\pp\a, \ps\a) = \frac{n_{\rm det}(\pp\a, \ps\a)}{N_{\rm s,a}(\pp\a, 
     \ps\a)} \times \frac{1}{p_{\rm tra}(\pp\a, \ps\a)}.
-\label{eq:wouldnt_it_be_nice}
-\end{equation}
-where $\pp\a$, $\ps\a$ are the apparent planetary and stellar parameters, 
-respectively.
-Here $N_{\rm det}(\pp\a, \ps\a)$ is the number of 
-detected planets with parameters $\pp\a,\ps\a$, per unit $\pp\a$ and $\ps\a$. 
+\label{eq:defn_apparent_rate_density}
+\end{equation}
+where $\pp\a$, $\ps\a$ are the apparent planetary and stellar parameters.
 The quantity $N_{\rm s,a}(\pp\a, \ps\a)$ is the number of unresolved 
-point-sources on the sky the appear to be searchable.
+point-sources on the sky that appear to be searchable, and
+$n_{\rm det}(\pp\a, \ps\a)$ is the number of detected planets, per unit 
+$\pp\a$ and $\ps\a$.
 
@@
 For simplicity, we consider only binaries, and we assume that they are all 
-spatially unresolved.
+bound and spatially unresolved.
 
@@
 
-Outside of astrophysical differences, there are observational biases for every 
-term in Eq.~\ref{eq:wouldnt_it_be_nice}.
-There are errors in $N_{\rm det}$ due to planet radius 
+Outside of astrophysical differences, every term in 
+Eq.~\ref{eq:defn_apparent_rate_density} is observationally-biased.
+There are errors in $n_{\rm det}(\pp\a,\ps\a)$ due to planet radius 
 misclassification.
-There are errors in $N_{{\rm s,a}}$ because a given point on the sky
+There are errors in $N_{{\rm s,a}}(\pp\a,\ps\a)$ because an apparently 
+searchable point on the sky might include two searchable stars.
 There are errors in $p_{\rm tra}(\pp\a,\ps\a)$ because stars in binaries may 
@@
 Binarity might also affect the observers' ability to correctly select 
-searchable stars (but see Sec.~\ref{sec:model_1} for discussion of why this is 
-a second-order effect).
-
-Finally, there are errors in $p_{\rm det}$ because detection efficiencies 
-for planets orbiting single stars, primaries, and secondaries are all 
-different.
+searchable stars (but see Sec.~\ref{sec:model_1} for discussion of this 
+issue).
 
@@
 For instance, in counting the number of selected stars, even after realizing 
-that binaries count as two stars, one must note that the multiplicity 
-fraction of {\it selected} stars is greater than that of a volume limited 
+that binaries count as two stars, one must note that the multiplicity fraction 
+of {\it selected} stars is greater than that of a volume limited 
 sample.
@@
 \end{itemize}
-We define our terminology in Sec.~\ref{sec:definitions}, and present
-our transit survey models in Secs.~\ref{sec:model_1}-\ref{sec:model_3}, where 
+In Sec.~\ref{sec:definitions}, we clarify our terminology and state
+assumptions that apply throughout this study.
+We then present our transit survey models in 
+Secs.~\ref{sec:model_1}-\ref{sec:model_3}, where 
 each subsection corresponds to a model listed above.
@@
 study of \citet{fulton_california-_2017}'s recently discovered ``valley''.
-We conclude in Sec.~\ref{sec:conclusion}
+We conclude in Sec.~\ref{sec:conclusion}.
 
@@
 
-\section{Definitions}
+\section{Definitions and Preliminaries}
 \label{sec:definitions}
-We define the occurrence rate density, $\Gamma$, as the expected number of 
-planets per star per bin of planetary or stellar phase space.
+
+\subsection{Occurrence rate, occurrence rate density}
+Define the occurrence rate density, $\Gamma$, as the expected number of 
+planets per star per unit of planetary and stellar phase space.
 Since we will mainly be concerned with the rate density's dependence on 
@@
 multiplicity.
-In this study we only consider single and binary star systems.
-For a selected population of stars and planets, the rate density is then 
-a weighted sum of rate densities for each system type:
-\begin{equation}
-N_{\rm tot} \Gamma(r) =
+Considering only single and binary systems, the rate density for any selected 
+sample of stars is a weighted sum of rate densities for each system type:
+\begin{equation}
+N_{\rm tot} \Gamma_{\rm sel}(r) =
 N_0 \Gamma_0(r) +
@@
 $N_0,N_1,N_2$ are the number of selected single stars, primaries, and 
-secondaries.
-Since each selected binary system contributes both a 
-primary and secondary star, $N_1=N_2$.
-This redundancy in our notation will later prove its use.
-
-Finally, it is helpful to write 
-$\Gamma_i(r)$, the rate density for each type of star, as the product of a 
-shape function and a constant:
-\begin{equation}
-\Gamma_i(r) = \frac{{\rm d}\Lambda_i}{{\rm d}r} = Z_i p_i(r),
+secondaries. For our purposes binary systems are not identifiable, and so 
+$N_1=N_2$.
+
+The rate density for each type of star, $\Gamma_i(r)$, can be written as 
+the product of a shape function and a constant:
+\begin{equation}
+\Gamma_i(r) = \frac{{\rm d}\Lambda_i}{{\rm d}r} = Z_i f_i(r),
 \quad {\rm for}\ i\in\{0,1,2\}.
@@
 
+\subsection{Searchable stars}
+For a given planet radius, semimajor axis, and stellar luminosity, a fixed 
+signal-to-noise floor yields a maximum searchable 
+distance~\citep{pepper_using_2003,pepper_searching_2005}.
+From Eq.~\ref{eq:S_N_thresh}, this maximum searchable distance scales as
+\begin{equation}
+d(\delta_{\rm obs}, L_{\rm sys}) \propto \delta_{\rm obs} \cdot L_{\rm 
+    sys}^{1/2}.
+\end{equation}
+Assuming that stars are uniformly distributed in space, the number 
+of searchable stars $N\s$ is then proportional to
+\begin{equation}
+N\s(\delta_{\rm obs}, L_{\rm sys}) \propto n \delta_{\rm obs}^3 L_{\rm 
+    sys}^{3/2},
+\label{eq:N_searchable_prop}
+\end{equation}
+where $n$ is the volume density of {\it e.g.}, single star, or binary systems.
+We neglect the dependence of $n$ on stellar type.
+
+\subsection{Relation between Apparent and Actual Stellar Properties}
+
+We assume that the apparent properties of an unresolved binary are identical to
+the true properties of the primary:
+\begin{equation}
+M\a=M_1, \quad R\a=R_1, ...
+\end{equation}
+We also take the stellar radius and luminosity to be uniquely related to the 
+stellar mass.
+Given these assumptions, the total luminosity of a system is
+\begin{equation}
+L_{\rm sys}=L_1+L_2=L(M\a)+L(qM\a),
+\end{equation}
+where $q=M_2/M_1$. Note that $L_{\rm sys}$ is the true value (because $M\a$ is 
+the true primary mass), while an observer with no a priori knowledge of the 
+distance to a system would measure a flux, assume a stellar mass $M_a$, and 
+estimate a system luminosity of $L(M\a)$.
+
+\subsection{Apparent number of searchable stars}
+\label{subsec:apparent_N_searchable}
+
+\begin{figure}[!tb]
+    \centering
+    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
+    \caption{
+        The mass ratio distribution for a magnitude-limited sample of 
+        binary stars, in which the underlying volume-limited distribution is 
+        uniform, qualitatively similar to {\it e.g.}, 
+        \citet{raghavan_survey_2010}'s Fig.~16.
+        At a given observed depth, the searchable binaries in a transit survey 
+        are magnitude-limited (see Sec.~\ref{subsec:apparent_N_searchable}).
+    }
+    \label{fig:q_distribn_mag_limited}
+\end{figure}
+
+Given the observed signal $\delta_{\rm obs}$ and apparent stellar mass $M\a$, 
+the maximum searchable distance for singles and binaries are proportional to 
+$\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm obs}\cdot 
+[L(M\a)+L(qM\a)]^{1/2}$.
+Thus, the apparent number of searchable stars (points in the sky), which 
+will be selected by an ignorant observer, can be written as
+\begin{align}
+N_{\rm s,a}(\delta_{\rm obs}, M\a)
+= N\s^0(\delta_{\rm obs}, L(M\a)) \left[1+\mu(\mathrm{BF}, 
+M\a)\right],
+\label{eq:N_selected}
+\end{align}
+where $N\s^0$ is the number of searchable singles (this agrees with the actual 
+value), $\mathrm{BF}=n_{\rm b}/(n_{\rm s}+n_{\rm b})$ 
+is the binary fraction in a volume-limited sample,
+$n_s$ ($n_b$) is the number density of single (binary) systems in a 
+volume-limited sample,
+and $\mu$ is the ratio of the number of double to single star 
+systems that are searchable for an observed signal $\delta_{\rm obs}$.
+Applying Eq.~\ref{eq:N_searchable_prop},
+\begin{equation}
+\mu({\rm BF},M\a) = 
+{N_{\rm d} \over N_s^0}=
+\int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
+f(q)\mathrm{d}q,
+\label{eq:mu_general}
+\end{equation}
+where $f(q)$ is the distribution of binary mass ratios in a volume-limited 
+sample.
+If $\mathrm{BF}$ is independent of $q$, $L \propto M^\alpha$, and $f(q) 
+\propto q^\beta$, this reduces to
+\begin{equation}
+\mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 
+\left(1+q^\alpha\right)^{3/2} q^\beta\mathrm{d}q,
+\end{equation}
+which may be written in a closed form using the hypergeometric function.
+
+This can be understood as a Malmquist bias: at fixed observed transit 
+depth, for singles and primaries with the same luminosity, binaries are 
+searchable to a greater distance.
+In particular, the sample of searchable binaries is magnitude-limited.
+Given a searchable binary, the probability of drawing a mass ratio $q$ will 
+scale as
+\begin{equation}
+p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto 
+(1+q^\alpha)^{3/2} q^\beta 
+\label{eq:Malmquist_bias}
+\end{equation}
+where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
+ratio $q$, and the first term is the Malmquist bias.
+We show this magnitude-limited mass ratio distribution for the $\beta=0$ case 
+in Fig.~\ref{fig:q_distribn_mag_limited}.
+In Monte Carlo simulations of transit surveys, it is 
+important to draw binaries from a correctly biased mass-ratio distribution 
+\citep[\textit{e.g.},][]{bakos_hatsouth:_2013,sullivan_transiting_2015,
+    gunther_new_2017}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:model_1}
-
-Since the effects of binarity are most pronounced when the two components are 
-similar, we begin by considering a universe in which all planets are 
-identical, and all stars are identical except that some fraction of them exist 
-in binaries.
-
-Expressed mathematically, from Eqs.~\ref{eq:rate_density_marginalized}
-and~\ref{eq:rate_density_shape} the occurrence rate density at a planet radius 
-$r$ can be written
-\begin{equation}
-\Gamma(r) = \delta(r_p) \times
-\frac{
-    N_0 Z_0 +
-    N_1 Z_1 +
-    N_2 Z_2
-}{N_{\rm tot}},
-\label{eq:model_1_rate_density}
-\end{equation}
-where $\delta(r_p)$ is the Dirac delta function, zero except at the true 
-planet radius, $r_p$.
-The occurrence rate over any interval that includes $r_p$ is then
-\begin{equation}
-\Lambda|_{r_p} = \frac{
-    N_0 Z_0 +
-    N_1 Z_1 +
-    N_2 Z_2 
-}{N_{\rm tot}},
-\label{eq:model_1_rate}
-\end{equation}
-and the rate is zero over intervals that do not include $r_p$.
-
-We return to our group of binarity-ignoring astronomers. They do 
-not know the true rate density~--~they would like to discover it!
-In their signal-to-noise limited transit survey, they select stars 
-that they think can yield transit detections.
-Since the noise is Poissonian, they assume
-\begin{equation}
-\frac{{\rm signal}}{{\rm noise}}
-\propto \frac{(r/R)^2}{F^{-1/2}}
-\propto F^{1/2}
-\propto L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm incorrectly\ assumed})
-\end{equation}
-for $R$ the constant stellar radius, $F$ the photon flux, $L_{\rm sys}$ the 
-luminosity of a system, and $d$ its distance from us.
-At fixed planet radius, semimajor axis, stellar radius, and stellar luminosity,
-a constant signal-to-noise floor yields a maximum detectable 
-distance~\citep{pepper_using_2003,pepper_searching_2005}.
-The maximum distance out to which our binarity-ignoring astronomers 
-select stars, $d_{\rm sel}$, thus scales as $L_{\rm sys}^{1/2}$.
-
-The single stars have luminosity $L_1$, and the twin binaries have luminosity 
-$2L_1$.
-Thus the twin binaries are selected out to a distance $\sqrt{2}$ times 
-that of single stars.
-This is a bad move, because the transit signal for any planet in a 
-twin binary will be diluted by a factor of two:
-\begin{equation}
-\frac{{\rm signal}}{{\rm noise}}
-\propto \frac{\mathcal{D} (r/R)^2}{F^{-1/2}}
-\propto \mathcal{D} F^{1/2}
-\propto \mathcal{D} L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm true})
-\label{eq:snr_true}
-\end{equation}
-where the dilution is $\mathcal{D} \equiv L_{\rm host}/L_{\rm sys}$, for 
-$L_{\rm host}$ the the planet host's luminosity.
-This means that the true maximum searchable distance for binaries, $d_{\rm 
-    det}$, is $1/\sqrt{2}$ times that of single stars.
-The situation is illustrated in Fig.~\ref{fig:model_1_volumes}: only one in 
-eight selected stars in binaries are truly searchable.
 
@@
 
-\paragraph{What do the observers ignoring binarity infer?} 
-The binarity-ignoring observers assume that all points on the sky with flux 
-above some minimum are searchable.
-They correct their assumed number of searchable stars for the transit 
-probability.
-As a function of apparent radius, they then report an apparent rate density of
-\begin{equation}
-\Gamma_a(r_a) = 
-\delta(r_p) Z_0 \frac{N_0}{N_0+N_1}  +
-\delta\left(\frac{r_p}{\sqrt{2}}\right) 
-(Z_1 p_{{\rm det},1} + Z_2 p_{{\rm det},2}) \frac{N_1}{N_0+N_1},
-\label{eq:model_1_apparent_rate_density}
-\end{equation}
-where $p_{{\rm det},1}$ ($p_{{\rm det},2}$) is the probability that a selected 
-primary (secondary) is searchable.
-In this example, $p_{{\rm det},1}=p_{{\rm det},2}=1/8$; the detection 
-efficiency is the ratio of the searchable to selected volumes.
-
-The true rate density (Eq.~\ref{eq:model_1_rate_density}) and the
-apparent rate density (Eq.~\ref{eq:model_1_apparent_rate_density})
-differ in that
-\begin{enumerate}
-    \item The total number of selected stars, $N_{\rm tot} = N_0+N_1+N_2$, was 
-    miscounted.
-    %
-    \item The detection efficiency was incorrectly assumed to be $1$ for all 
-    selected stars. In reality, only one in eight binaries were searchable.
-    %
-    \item The inferred radii in binary systems are all $\sqrt{2}$ too small.
-\end{enumerate}
-
-To assess the severity of these errors, we need to make assumptions about the 
-stellar and planetary populations.
-The important quantity for the stellar population is $N_1/N_0$, the ratio of 
-selected primaries (or binaries) to singles. We can define
-\begin{align}
-\mu \equiv \frac{N_1}{N_0} &=
-\frac{n_b}{n_s} \left(\frac{d_{\rm sel,b}}{d_{\rm sel,s}}\right)^3 = 
-\frac{{\rm BF}}{1-{\rm BF}} (1+\ell)^{3/2},
-\label{eq:mu_definition}
-\end{align}
-where $n_b$ and $n_s$ are the number density of binaries and singles in a 
-volume limited sample, and the maximum selected distance for binary and single 
-systems are $d_{\rm sel,b}$ and $d_{\rm sel,s}$.
-The light ratio $\ell$ is defined relative to the primary, so that
-$L_{\rm sys} = L_1(1+\ell)$.
-The binary fraction in a volume limited sample is ``{\rm BF}''.
-For instance, \citet{raghavan_survey_2010} found a multiplicity 
-fraction\footnote{
-    The binary fraction is the fraction of systems in a volume-limited sample 
-    that are binary. It is equivalent to the multiplicity fraction if there 
-    are no triple, quadruple, or higher order multiples. In that case, ${\rm 
-        BF} = n_b / (n_s+n_b)$.
-} of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$. 
-``Twin binaries'' are perhaps 10-20\% of the binaries in a volume-limited 
-sample, depending on how ``twin'' is defined.
-Thus a representative twin binary fraction for this model is ${\rm BF}\approx 
-0.05$-$0.1$.
-
-Further, we need to assume knowledge of the true number of planets per 
-single, primary, and secondary star ($Z_0,Z_1,$ and $Z_2$).
-Taking $Z_0=Z_1=Z_2=1/2$, we plot the resulting occurrence rates as a function 
-of planet radius in Fig.~\ref{fig:occ_rate_model_1}.
-Though it is impossible for an observer to isolate any one of binarity's 
-biases without also addressing the others, mathematically it is simply a 
-matter of modifying the appropriate terms in 
-Eq.~\ref{eq:model_1_apparent_rate_density}.
-The resulting rates are also shown in 
-Fig.~\ref{fig:occ_rate_model_1}, and demonstrate how each 
-error individually affects the overall inferred rate.
-
 \begin{figure}[!tb]
@@
         Inferred occurrence rates over $0.01r_\oplus$ bins in planet 
-        radius,for Model \#1.
+        radius, for Model \#1.
         This model has fixed stars, fixed planets, and twin binaries. 
-        Further, a twin binary fraction of ${\rm BF}=0.1$ is assumed, and all 
-        planets are {\bf TODO}.
+        We assume a twin binary fraction of ${\rm BF}=0.1$, and that all 
+        stars (single, primary, and secondary) host planets at equal 
+        rates.
         If the true planet radius is $r_p$, all planets detected in binaries 
-        will have apparent radii $r_a = r_p/\sqrt{2}$.
+        will have apparent radii $r\a = r_p/\sqrt{2}$.
     }
@@
 
+Since the effects of binarity are most pronounced when the two components are 
+similar, we first consider a universe in which all planets are 
+identical, and all stars are identical except that some fraction of them exist 
+in binaries.
+Expressed mathematically, from Eqs.~\ref{eq:rate_density_marginalized} 
+and~\ref{eq:rate_density_shape} the rate density for a selected sample of 
+stars at planet radius $r$ is
+\begin{equation}
+\Gamma_{\rm sel}(r) = \delta(r-r_p) \times
+\frac{
+    Z_0 +
+    \mu (Z_1 + Z_2)
+}{1+2\mu},
+\label{eq:model_1_rate_density}
+\end{equation}
+where $\mu$ is given by Eq.~\ref{eq:mu_general} with $f(q) = \delta(q-1)$,
+$\delta$ is the Dirac delta function, and the true planet radius is 
+$r_p$.
+We will generally write rate densities in terms of $\mu$'s, rather than 
+$N_i$'s, because $\mu$'s are independent of planet radius.
+
+We return to our group of binarity-ignoring astronomers. They select all the 
+points on-sky that they think are searchable: those that are above some flux 
+limit (at each $\delta_{\rm obs}$).
+The relevant stellar samples are illustrated in Fig.~\ref{fig:model_1_volumes}.
+At an apparent radius equal to the true radius ($r\a=r_p$), the observer 
+thinks all stars are singles, with $d<d_0$.
+In fact, binaries with $r\a=r_p$ are also searchable, out to $\sqrt{2}d_0$. 
+However, in this model no such systems exist; all planets in twin binaries 
+have true radii $r=r_p$, and so are observed with apparent radii 
+$r\a=r_p/\sqrt{2}$.
+This is because of ``radius dilution'':
+for an unresolved point-source... %TODO FIXME
+
+At an apparent radius of $r\a=r_p/\sqrt{2}$, there might also be planets with 
+true radii $r=r_p/\sqrt{2}$ orbiting a single~---~however none of these exist 
+in this model either.
+Following Eq.~\ref{eq:defn_apparent_rate_density}, the apparent rate density 
+computed without considering binarity is
+\begin{equation}
+\Gamma_a(r_a) = 
+\frac{1}{1+\mu} Z_0 \cdot
+\delta(r\a-r_p)  +
+\frac{\mu}{1+\mu} (Z_1 + Z_2) \cdot
+\delta\left(r\a-\frac{r_p}{\sqrt{2}} \right),
+\label{eq:model_1_apparent_rate_density}
+\end{equation}
+
+The rate density for selected stars (Eq.~\ref{eq:model_1_rate_density}) and the
+apparent rate density (Eq.~\ref{eq:model_1_apparent_rate_density}) differ in 
+that (A) the total number of selected stars, $N_{\rm tot} = N_0+N_1+N_2$, was 
+miscounted; and (B) the inferred radii in binary systems are all $\sqrt{2}$ 
+too small.
+
+To assess the severity of these errors, we need to assume a binary fraction, 
+and to know the true number of planets per single, primary, and secondary star 
+($Z_0,Z_1,$ and $Z_2$).
+For the former,
+\citet{raghavan_survey_2010} found a multiplicity 
+fraction\footnote{
+    The binary fraction is the fraction of systems in a volume-limited sample 
+    that are binary. It is equivalent to the multiplicity fraction if there 
+    are no triple, quadruple, or higher order multiples.
+} of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$. 
+``Twin binaries'' are perhaps 10-20\% of the binaries in a volume-limited 
+sample, depending on how ``twin'' is defined.
+Thus a representative twin binary fraction for this model is ${\rm BF}\approx 
+0.05$-$0.1$. 
+For the latter, taking $Z_0=Z_1=Z_2=1/2$, we plot the resulting occurrence 
+rates as a function of planet radius in Fig.~\ref{fig:occ_rate_model_1}.
+When the $Z_i$'s are equal, the rate density for singles, $\Gamma_0(r)$ 
+(dashed green line), is equal to the rate density for selected stars, 
+$\Gamma_{\rm sel}(r)$ (solid orange line).
+
 \paragraph{Correction to inferred rate density and inferred rate}
-
-We define a rate density correction factor, $X_\Gamma$, as the ratio of the 
-apparent to true rate densities:
-\begin{equation}
-X_\Gamma \equiv \frac{\Gamma_a}{\Gamma}.
-\end{equation}
-This correction factor can be a function of whatever parameters $\Gamma_a$ and 
-$\Gamma$ depend on; in this study, the planet radius is most relevant.
-
-If we continue assuming that the number of planets per single, primary, and 
-secondary star are equal ($Z_0=Z_1=Z_2$), we find a rate density correction 
-factor at the true planet radius of
-\begin{equation}
-X_\Gamma(r_p) = \frac{1}{1+\mu},
-\label{eq:Z_eq_model_1_correction}
-\end{equation}
+We can define a rate density ``correction factor'', $X_\Gamma$, as the ratio 
+of the apparent to single star rate density,
+\begin{equation}
+X_\Gamma(r) \equiv \left. \frac{\Gamma_a(r\a)}{\Gamma_0(r)} \right|_{r\a 
+\rightarrow r}.
+\end{equation}
+Continuing in the assumption that the number of planets per single, primary, 
+and secondary star are equal, we find a rate density 
+correction factor at the true planet radius of $1/(1+\mu)$.
 This yields a correction of 0.76 if ${\rm BF}=0.1$, and 0.87 if ${\rm 
-    BF}=0.05$.
-Rephrasing the result, if the twin binary fraction were 
+BF}=0.05$. Rephrasing the result, if the twin binary fraction were 
 $(2^{3/2}+1)^{-1}\approx 0.26$, then the apparent rate would be half the true 
-rate.
-Fortunately, in most contexts the twin binary fraction is not that high.
+rate. Fortunately, in most contexts the twin binary fraction is not that high.
 
@@
 case, $Z_0=Z_1$, and $Z_2=0$. The correction to the rate density at the true 
-planet radius becomes
-\begin{equation}
-X_\Gamma(r_p) = \frac{1+2\mu}{(1+\mu)^2}.
-\end{equation}
+planet radius becomes $(1+2\mu)/(1+\mu)^2$.
 This evaluates to 0.94 if ${\rm BF}=0.1$, and 0.98 if ${\rm BF}=0.05$.
-While it is hard to justify the assumption that secondaries are planet-less, 
+While it seems unlikely that secondaries are planet-less, 
 it is worth noting that $\Gamma_a/\Gamma$ is sensitive to the relative number 
@@
 
+\paragraph{On completeness}
+Our expressions for the apparent rate density 
+(Eqs.~\ref{eq:defn_apparent_rate_density} 
+and~\ref{eq:model_1_apparent_rate_density}) do not explicitly mention 
+detection efficiency.
+If we were to take a smooth detection probability in S/N, we would need to 
+include an explicit detection efficiency term in 
+Eq.~\ref{eq:defn_apparent_rate_density} is to inversely weight for planets 
+that had low probabilities of being detected.
+However, our ``detection probability'' is a step function in S/N 
+(Eq.~\ref{eq:S_N_thresh}).
+In our model, the maximum searchable distance is only a function of the 
+apparent depth and true system luminosity.
+Even though the observers are selecting stars based on what they think are 
+``true radii'' (bottom row of Fig.~\ref{fig:model_1_volumes}), the 
+actual searchability of a point-source is determined by apparent radius and 
+system luminosity (Eq.~\ref{eq:S_N_thresh}; top rows of 
+Fig.~\ref{fig:model_1_volumes}).
+Thus at a given apparent radius $r\a$, the stars (single or binary) that are 
+searchable are exactly the stars that are selected, since dilution affects the 
+apparent radius and the maximum searchable distance in equal and opposite 
+order.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Model \#2: Power law planets}
+\label{sec:model_2}
+
+\subsubsection{Twin binaries}
+Our binary-twin model provides a simple estimate of binarity's systematic 
+effects, but perhaps it is too simple.
+We begin introducing realism by keeping all binaries as twins, but letting the 
+radius distribution of planets vary.
+Specifically, we take
+\begin{equation}
+\Gamma_i(r) = Z_i f(r) = Z_i r^\delta/\mathcal{N}_r,
+\end{equation}
+for $f(r)$ the radius shape function, $\mathcal{N}_r$ the shape function's 
+normalization, and $Z_i$ the number of planets per star.
+It turns out that in this model, the apparent rate density is quite similar to 
+that written in Eq.~\ref{eq:model_1_apparent_rate_density}, except that the 
+radius dependence and normalization are slightly different:
+\begin{equation}
+\Gamma_a(r_a) = \frac{r_a^\delta}{\mathcal{N}_r} \left[
+\frac{Z_0}{1+\mu}
++
+2^{\frac{\delta+1}{2} } \frac{\mu}{1+\mu} \left(Z_1 + Z_2
+\right)
+\right].
+\label{eq:model5_apparent_rate_density}
+\end{equation}
+The details of this equation come from a more general form derived in the 
+Appendix (Eq.~\ref{eq:general_Gamma_a}).
+
+If the $Z_i$'s are equal, the ``correction factor'' relative to the rate 
+density for singles becomes quite simple:
+\begin{align}
+\left. \frac{\Gamma_a(r_a)}{\Gamma_0(r)} 
+\right|_{r_a\rightarrow r}
+&=
+\frac{1 + 2^{\frac{\delta+3}{2}}\mu}{1 + \mu}.
+\label{eq:power_law_correction}
+\end{align}
+For the case of ${\rm BF}=0.1$, $\mu\approx 0.153$. Taking $\delta=-2.92$ from 
+\citet{howard_planet_2012},  we get a correction factor $\Gamma\a/\Gamma_0 = 
+1.004$.
+In other words, the apparent rate density is an {\it over}estimate of the rate 
+density of selected stars, with a relative difference $\delta \Gamma_0 = 
+|\Gamma_0 - \Gamma\a | / \Gamma_0$ of 0.4\%.
+A power law radius distribution $f(r) \propto r^\delta$ diverges for 
+$\delta < 0$. From the work of \citet{howard_planet_2012}, this approximation 
+is applicable for $r\gtrsim 2r_\oplus$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Varying binaries}
+\label{sub:powerlaw_varying_binaries}
+
+To confirm the intuition that non-twin binaries do not affect 
+the above result, we now assume $f(q) = q^\beta/\mathcal{N}_q$, for 
+$\mathcal{N}_q$ the normalization.
+This changes $\mu$ (Eq.~\ref{eq:mu_general}).
+It may also affect the rate density, which could be a function of the stellar 
+mass, which now changes for secondaries (we assume that singles and primaries 
+have the same mass). Absorbing this dependence into a power law as well,
+\begin{equation}
+\Gamma_i(r,M) = Z_i \times \frac{r^\delta}{\mathcal{N}_r} \times
+\frac{M^\gamma}{\mathcal{N}_M},
+\end{equation}
+where $Z_i$ is dimensionless, and the normalization constants carry 
+the units (each side has units $[r^{-1} M^{-1}]$).
+We assume that stars are a one-parameter family, given by $R \propto M \propto 
+L^{\frac{1}{\alpha}}$, so that a given value of $q$ determines everything 
+about a secondary.
+
+Using Eq.~\ref{eq:general_Gamma_a}, we can show that when $Z_0=Z_1=Z_2$,
+\begin{align}
+X_\Gamma &\equiv \left. \frac{\Gamma\a(r\a,M\a)}{\Gamma_0(r,M)} 
+\right|_{r\a\rightarrow r,\ M\a\rightarrow M,\ Z_i{\rm 's\ equal}} \\
+&=
+\frac{1}{1+\mu}
+\left[1 + \frac{1}{\mathcal{N}_q} \frac{{\rm BF}}{1-{\rm BF}}
+\left(
+\int {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}} +
+\int {\rm d}q\,q^{\beta+\gamma+\delta+\frac{8}{3}} 
+(1+q^\alpha)^{\frac{3}{2}}
+(1+q^{-\alpha})^{\frac{\delta+1}{2}}
+\right)\right].
+\label{eq:powerlaw_vary_binary}
+\end{align}
+
+For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the 
+summed integrals in Eq.~\ref{eq:powerlaw_vary_binary} give $(\ldots)\approx 
+1.41425$. %171211_model_integrals.nb
+For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.014$; the
+apparent rate density is higher than the rate density around singles by 1.4\%.
+Although with slightly tedious algebra, the result that for power-law 
+radius distribution (at $r\gtrsim 2r_\oplus$), binarity influences derived 
+occurrence rates at the $\sim$few percent level seems robust for Sun-like 
+stars.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{comment}
 \subsection{Model \#2: fixed planets and primaries, varying secondaries}
@@
 
-\begin{figure}[!tb]
-    \centering
-    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
-    \caption{
-        The mass ratio distribution for a magnitude-limited sample of 
-        binary stars, in which the underlying volume-limited distribution is 
-        uniform (qualitatively similar to {\it 
-            e.g.},~\citet{raghavan_survey_2010}'s Fig.~16).
-        The entire bias can be understood analytically 
-        (Eq.~\ref{eq:Malmquist_bias}).
-    }
-    \label{fig:q_distribn_mag_limited}
-\end{figure}
-
 Our binary-twin model provides a simple estimate of binarity's systematic 
 effects, but perhaps it is too simple.
-We begin introducing realism by first letting the light ratio $\ell = L_2/L_1$ 
+We begin introducing realism by first letting the binary light ratio $L_2/L_1$ 
 vary across the binary population.
@@
 We further assume that stars are a one-parameter family, $R \propto M \propto 
-L^{1/\alpha}$, so that a drawn value of $q$ determines everything about a 
-secondary.
+L^{\frac{1}{\alpha}}$, so that a given value of $q$ determines everything 
+about a secondary.
 
@@
 over both the mass ratio and the planet radius.
-
-There is also a Malmquist bias in Eq.~\ref{eq:model2_rate_density}, hidden 
-away in the numbers of selected stars.
-This is because the selected sample at a fixed planet radius and period is 
-magnitude-limited.
-Given a binary, the probability of drawing a mass ratio $q$ in a 
-magnitude-limited sample scales as
-\begin{equation}
-p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto q^\beta 
-(1+q^\alpha)^{3/2}
-\label{eq:Malmquist_bias}
-\end{equation}
-where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
-ratio $q$, and the latter term is the Malmquist bias.
-We show the magnitude-limited mass ratio distribution for the $\beta=0$ case 
-in Fig.~\ref{fig:q_distribn_mag_limited}.
-We emphasize that in Monte Carlo simulations of transit surveys, it is 
-important to draw binaries from the correctly biased mass-ratio distribution 
-\citep[\textit{e.g.},][]{bakos_hatsouth:_2013,sullivan_transiting_2015,
-    gunther_new_2017}.
 
@@
 
-\begin{comment}
 The analytic solution for $i=1$ is something like
@@
 q^{\gamma+\beta} (1+q^\alpha)^{3/2} {\rm d}q$.
-\end{comment}
 
@@
 
+\end{comment}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Model \#3: Fixed primaries, varying planets and secondaries}
+\subsection{Model \#3: Fixed primaries, broken power-law planets and 
+secondaries}
 \label{sec:model_3}
 
-As in the previous model, all single and primary stars in this model have 
-identical properties.
-The secondaries have masses, radii, and luminosities that vary between 
-systems: $M\propto R \propto L^{1/\alpha}$.
-The only addition is that we now let the radii of planets vary: they are 
-assigned independently of any host system property, and are sampled from the 
-true radius distribution, which we take as
+\begin{figure}[!tb]
+    \centering
+    \epsscale{1.15}
+    \plottwo{figures/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf}
+    \caption{
+        {\it Left:} rate density and {\it right:} rate as a 
+        function of planet radius in Model \#3. This model has fixed primaries 
+        and 
+        single stars, but varying secondaries. The true planet radius 
+        distribution is 
+        a power law with exponent $-2.92$ above $2r_\oplus$, below which it is 
+        uniform 
+        \citep[similar to][]{howard_planet_2012}. We use an arbitrary 
+        normalization of 
+        $Z_0=0.5$ throughout.}
+    \label{fig:occ_rate_model_3_log}
+\end{figure}
+
+Though the details of the radius distribution $\Gamma_i(r)$ at $r<2r_\oplus$ 
+are still an active topic of research, we can consider how binarity effects
+this regime under various reasonable assumptions.
+For instance, we can assume that the true radius shape function is
 \begin{align}
-p_r(r)
+f(r)
 &\propto
@@
 \end{align}
-Following~\citet{howard_planet_2012}'s measurement, we take $\delta = -2.92$.
-Our ``nominal model'' remains the same: the binary fraction is 0.44, 
-$\alpha=3.5$, $\beta=\gamma=0$.
-We take $Z_i$, the number of planets per single, primary, and secondary, to be 
-equal.
-
-For this model, we forgo analytic development and simply run our Monte Carlo 
-program\footnote{
-    One might worry that our Monte Carlo program does not increase the number 
-    of 
-    selected stars as the square of the planet radius (Eq.~\ref{eq:snr_true}).
-    We can omit this dependence because in our model $N_1/N_0$ is independent 
-    of 
-    desired planet radius, and all other terms in the rate densities ({\it 
-    e.g.}, 
-    Eqs.~\ref{eq:model2_rate_density} and~\ref{eq:model2_Gamma_a}) are 
-    independent 
-    of the number of selected stars.
-}.
-The resulting occurrence rates are shown in 
+As before, all single and primary stars in this model have identical 
+properties. The secondaries have masses, radii, and luminosities that vary 
+between systems: $R \propto M \propto L^{\frac{1}{\alpha}}$.
+Our ``nominal model'' remains the same: 
+$\alpha=3.5$, $\beta=\gamma=0$, $\delta=-2.92$.
+
+At apparent radii $r\a > 2r_\oplus$, the results of this model are the same as 
+those from Sec.~\ref{sub:powerlaw_varying_binaries}.
+For $r\a < 2r_\oplus$, the equations are quite tedious, though still tractable.
+To compute $\Gamma\a(r\a)$, we simply insert 
+Eq.~\ref{eq:model3_radius_distribution} into Eq.~\ref{eq:general_Gamma_a}, and 
+integrate using a computer program.
+We refer the interested reader to our online 
+implementation\footnote{\url{https://github.com/lgbouma/binary_biases}}.
+The output is validated against analytic predictions in the $r\a > 
+2r_\oplus$ and the $r\a < 2r_\oplus/\sqrt{2}$ regimes, and is plotted in
 Fig.~\ref{fig:occ_rate_model_3_log}.
-For the assumed planetary and stellar distributions, the inferred rate is 
-underestimated over all radii.
-
-\begin{figure}[!tb]
-\centering
-\epsscale{1.15}
-\plottwo{figures/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf}
-\caption{
-{\it Left:} rate density and {\it right:} rate as a 
-function of planet radius in Model \#3. This model has fixed primaries and 
-single stars, but varying secondaries. The true planet radius distribution is 
-a power law with exponent $-2.92$ above $2r_\oplus$, below which it is uniform 
-\citep[similar to][]{howard_planet_2012}.
-\label{fig:occ_rate_model_3_log}}
-\end{figure}
+
+\paragraph{The rate of Earth analogs}
+The most immediately arresting result there is a ``bump'' in the apparent rate 
+density at $r\a < 2r_\oplus$.
+For the case in which secondaries host as many (half as many) planets as 
+single stars, this means an overestimate of the absolute occurrence rate by 
+$\approx 50\%$ ($\approx 25\%$).
+It remains even for the $Z_2/Z_0=0$ case as a $\approx 10\%$ effect.
 
 \paragraph{Hot Jupiter occurrence rates}
-Taking Fig.~\ref{fig:occ_rate_model_3_log} and counting the number of planets 
-per star with $r>8r_\oplus$, we can compare the true and inferred hot Jupiter 
-occurrence rates.
-Under the above assumptions, the true rate is 9.1 hot Jupiters 
-per thousand stars.
-The inferred rate is 6.9 per thousand stars.
-This means that the inferred rate underestimates the true rate by a 
-multiplicative factor of $\sim\!1.3$.
-
-However, this result only applies under the assumption that $Z_0 = 
-Z_1 = Z_2$.
-If hot Jupiters are less common around lower mass stars, it would be more 
-sensible to consider $Z_2<Z_0$, while letting single stars and 
-primaries host planets at the same rate.
-Therefore in Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues} we let 
-$Z_2$ vary, and show the resulting inferred and true hot Jupiter 
-($r>8r_\oplus$) rates.
-The result is that the inferred rate is nearly independent of 
-$Z_2$~--~this is because most ($<1/10$) secondaries are not searchable, 
-and so their completeness fraction is much smaller than that of primaries or 
-single stars.
-This means far fewer detected hot Jupiters orbit secondaries, and so they 
-hardly affect the inferred rate.
-While the ``true rate'' across the entire population is linearly dependent on 
-$Z_2$, the rate around 
-singles and primaries (Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues} 
-green line) is independent of that around secondaries.
-
+Taking Fig.~\ref{fig:occ_rate_model_3_log} and integrating the rate density
+for $r>8r_\oplus$, we can compare the apparent hot Jupiter 
+occurrence rate with the true rate for singles.
+In the most extreme case of $Z_2/Z_0=0$, we find that $\Lambda_{{\rm 
+HJ},0}/\Lambda_{\rm HJ,a} = 1.13$, where
+\begin{equation}
+\Lambda_{\rm HJ,a} = \int_{8r_\oplus}^{\infty} \Gamma\a(r)\,{\rm d}r,
+\end{equation}
+and similarly for $\Lambda_{\rm HJ,0}$.
+%occ_rate_vs_radius_model_3_withtext_Zsub2_0.00_rpu_22.5.pdf
+If $Z_2/Z_0>0$, binarity affects this value less: when $Z_2/Z_0=0.5$, 
+we find $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 1.06$
+
+%TODO: FIGURE OUT WHAT TO DO WITH THESE
+\begin{comment}
 \begin{figure}[!tb]
@@
 
-\paragraph{The rate of Earth analogs}
-This model provides an estimate of the apparent and true 
-rates as a function of radius (Fig.~\ref{fig:occ_rate_model_3_log}).
-At Earth's radius, the result is that the inferred rate is $0.84\times$ the 
-true rate around single stars, assuming that the $Z_i$'s are equal.
-Similar to the above case of the hot Jupiters, if we vary the true $Z_2$ 
-while keeping $Z_0 = Z_1$, the ratio of the inferred to true rate 
-around single stars changes by only a few percent (shown in 
-Fig.~\ref{fig:earth_inputrate_vs_etaearthratevalues}).
-The ratio of the inferred to the true rate, $(\Lambda_{\rm 
-    inferred}/\Lambda)_{r=r_\oplus}$ varies substantially, but by at most 
-$50\%$ 
-in the (unrealistic) limiting case that secondaries do not host planets.
-
 \begin{figure}[!tb]
@@
 \end{figure}
+\end{comment}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Further models: radius gaps, Gaussian HJ distributions}
+
+The radius distribution specified by Eq.~\ref{eq:model3_radius_distribution} 
+misses some important features recently reported by state of the art 
+occurrence rate studies.
+
+\paragraph{Precise features of the radius valley}
+
+\begin{figure}[!tb]
+    \centering
+    \epsscale{1.15}
+    \plottwo{figures/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf}
+    \caption{
+        {\it Left:} rate density and {\it right:} rate as a 
+        function of planet radius in a model with a radius gap 
+        (Eq.~\ref{eq:model4_radius_distribution}).
+        Similar to Model \#3, this model has fixed primaries and single stars, 
+        but varying secondaries.
+    }
+    \label{fig:model_4}
+\end{figure}
+
+In particular,~\citet{fulton_california-_2017} recently reported a ``gap'' in 
+the radius-period 
+plane~\citep{petigura_california-kepler_2017,johnson_california-kepler_2017}.
+The existence of the gap has been independently corroborated from a sample of 
+KOIs with asteroseismically-determined stellar 
+parameters~\citep{van_eylen_asteroseismic_2017}.
+Precise measurement of the gap's features, in particular its width, 
+depth, and shape, will require more accurate occurrence rates.
+To illustrate binarity's role in the issue, we make identical assumptions as 
+in Model \#3, but instead assume an intrinsic radius distribution
+\begin{align}
+f(r)
+&\propto
+\left.
+\begin{cases}
+r^\delta & \text{for } r\geq 2r_\oplus, \\
+0 & \text{for } 1.5r_\oplus < r < 2r_\oplus, \\
+{\rm constant} & \text{for } r\leq1.5r_\oplus.
+\end{cases}
+\right.
+\label{eq:model4_radius_distribution}
+\end{align}
+The resulting true and inferred rates are shown in Fig.~\ref{fig:model_4}.
+If left uncorrected, binarity makes the gap appear more shallow, and flattens 
+the step-function edges.
+Of course, other effects could also ``blur'' the gap in the planet radius 
+dimension. 
+In particular, the valley's period-dependence is almost certainly not flat
+\citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.
+This means that any study assessing its width, depth, etc. only in the planet 
+radius dimension must either account for the blurring that comes from 
+marginalizing over the periods, or else perform tests at fixed periods.
+
+\paragraph{Alternative models for the HJ distribution}
+
+\begin{figure}[!tb]
+    \centering
+    \includegraphics[width=.6\textwidth]{figures/int_rate_density_vs_radius_model_7_rpu_22.5_manyZs.pdf}
+    \caption{
+        Rate density for a population of planets with true radii $r$ drawn from
+        $\mathcal{N}(14r_\oplus,2r_\oplus)$.
+        This is similar to the hot Jupiter distribution presented 
+        by~\citet{petigura_CKS_2017}.
+    }
+    \label{fig:gaussian_HJ}
+\end{figure}
+
+In the recent work by~\citet{petigura_CKS_2017}, hot Jupiters appear as an 
+island in period-radius space, rather than as a continuous component of a 
+power law distribution.
+Consider instead the intrinsic radius shape function
+\begin{equation}
+f(r) \propto \exp \left( -\frac{(r-\bar{r})^2}{2\sigma^2} \right),
+\end{equation}
+with $\bar{r} = 14r_\oplus$ and $\sigma = 2r_\oplus$.
+As always, $\Gamma_i(r) = Z_i f(r)$.
+We then compute $\Gamma\a(r\a)$, and plot it in Fig.~\ref{fig:gaussian_HJ}.
+Integrating to find hot Jupiter rates,
+we find the opposite effect as from the power law model.
+For $Z_2/Z_0>0$, 
+the apparent HJ rate is {\it greater} than the true rate for singles.
+The effect is maximal when there are as many hot Jupiters orbiting secondaries 
+as singles, in which case
+$\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 0.84$
+For the case when no hot Jupiters orbit secondaries, $\Lambda_{{\rm HJ},0} 
+\approx \Lambda_{\rm HJ,a}$ to within one percent.
 
@@
 \paragraph{How has binarity been considered in occurrence rate measurements?}
-Binarity introduces systematic uncertainty to star and planet counts, and also 
-to estimates of pipeline completeness.
+This work has shown that binarity introduces substantial systematic 
+uncertainty to star and planet counts.
+To first order, it appears not to effect estimates of pipeline completeness...
+%TODO
 In spite of this fact, stellar multiplicity has mostly been ignored in 
@@
 \paragraph{The hot Jupiter rate discrepancy}
-\begin{figure}[!tb]
-    \centering
-    \includegraphics[width=.6\textwidth]{figures/int_rate_density_vs_radius_model_7_rpu_22.5_manyZs.pdf}
-    \caption{
-        HJ rate, if it were Gaussian.
-    }
-    \label{fig:gaussian_HJ}
-\end{figure}
 
@@
 
-\paragraph{Precise features of the radius valley}
-
-\begin{figure}[!tb]
-    \centering
-    \epsscale{1.15}
-    \plottwo{figures/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf}
-    \caption{
-        {\it Left:} rate density and {\it right:} rate as a 
-        function of planet radius in a model with a radius gap 
-        (Eq.~\ref{eq:model4_radius_distribution}).
-        Similar to Model \#3, this model has fixed primaries and single stars, 
-        but varying secondaries.
-    }
-    \label{fig:model_4}
-\end{figure}
-
-Using improved stellar parameters measured by the California-{\it Kepler} 
-survey,~\citet{fulton_california-_2017} recently reported a ``gap'' in 
-the radius-period 
-plane~\citep{petigura_california-kepler_2017,johnson_california-kepler_2017}.
-The existence of the gap has been independently corroborated from a sample of 
-KOIs with asteroseismically-determined stellar 
-parameters~\citep{van_eylen_asteroseismic_2017}.
-Precise measurement of the gap's features, in particular its width, 
-depth, and shape, will require more accurate occurrence rates.
-To illustrate binarity's role in the issue, we make identical assumptions as 
-in Model \#3, but instead assume an intrinsic radius distribution
-\begin{align}
-p_r(r)
-&\propto
-\left.
-\begin{cases}
-r^\delta & \text{for } r\geq 2r_\oplus, \\
-0 & \text{for } 1.5r_\oplus < r < 2r_\oplus, \\
-{\rm constant} & \text{for } r\leq1.5r_\oplus.
-\end{cases}
-\right.
-\label{eq:model4_radius_distribution}
-\end{align}
-The resulting true and inferred rates are shown in Fig.~\ref{fig:model_4}.
-If left uncorrected, binarity makes the gap appear more shallow, and flattens 
-the step-function edges.
-At present though, binarity seems less important than other effects that would 
-``blur'' the gap in the planet radius dimension. 
-In particular, the valley's period-dependence is almost certainly not flat
-\citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.
-This means that any study assessing its width, depth, etc. only in the planet 
-radius dimension must first account for the blurring that comes from 
-marginalizing over the periods.
-
 \paragraph{Does a detected planet orbit the primary or secondary?}
@@
 
+\software
+numpy, scipy, pandas, matplotlib
+
 %\acknowledgements
@@
 \input{hj_rates.tex}
+
+\newpage
+\appendix
+\section{Apparent occurrence rate~---~general formula}
+Recall our definition of apparent rate density 
+(Eq.~\ref{eq:defn_apparent_rate_density}).
+The planets with $(\pp\a, \ps\a)$ are associated with 
+systems of many different planetary and stellar properties, so $n_{\rm 
+det}(\pp\a, \ps\a)$ is given by the convolution of the true rate density, 
+$\Gamma(\pp, \ps)$, and $\mathcal{N}(\pp\a, \ps\a; \pp, \ps)$, the number (per 
+unit $(\pp\a, \ps\a)$) of searchable stars that give $(\pp\a, \ps\a)$  when 
+the true system actually has $(\pp, \ps)$:
+\begin{align}
+N_{\rm det}(\pp\a, \ps\a)=\sum_i N_{\rm det}^i(\pp\a, \ps\a)
+=\sum_i \int \mathrm{d}\pp\mathrm{d}\ps\,
+\mathcal{N}_{\rm s}^i(\pp\a,\ps\a; \pp, \ps)
+\cdot\Gamma^i(\pp, \ps)\cdot p_{\rm tra}(\pp, \ps),
+\end{align}
+where $i$ specifies the type of true host stars (0: single, 1: primary, 2: 
+secondary).
+The problem reduces to the evaluation of
+\begin{equation}
+\mathcal{N}_{\rm s}^i(\pp\a,\ps\a; \pp, \ps)
+\end{equation}
+for planets around single stars, primaries in binaries, and secondaries in 
+binaries.
+
+Using the results above, the apparent rate density,
+\begin{align}
+\Gamma\a(r\a,M\a) &= 
+\frac{1}{N_{\rm s,a}(r\a,M\a) p_{\rm tra}(r\a,M\a)} \times
+\sum_i N_{\rm det}^i (r\a,M\a),
+\end{align}
+evaluates to
+\begin{align}
+\notag
+\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
+\left\{ \Gamma^0(r\a, M\a)+ 
+\frac{{\rm BF}}{1 - {\rm BF}}
+\left[ \int {\mathrm{d}q \over \mathcal{A}^4}\,f(q)\,\Gamma^1\left({r\a\over 
+    \mathcal{A}}, 
+M\a\right)\,
+\right.   
+\right. \\
+& \quad\quad\quad\quad\quad \left.\left.
++\int {q \mathrm{d}q \over 
+{\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma^2\left({r\a\over 
+    \mathcal{B}}, 
+qM\a\right)\,
+{R(qM\a) \over R(M\a)}
+q^{-1/3} \right]	\right\}.
+\label{eq:general_Gamma_a}
+\end{align}
+This equation is used to derive Eq.~\ref{eq:model5_apparent_rate_density}.
 

### 2017-12-16 src/hj_rate.py
update hj rate calculation

@@ -54,7 +54,7 @@ print('taking Z into account, p = {:.3f}'.format(
     ))
 
 ####################
-eta *= 1.3
+eta *= 1.13
 ndet = np.zeros((m))
 
 seed = 42

### 2017-12-16 src/numerical_models.py

@@ -22,7 +22,6 @@ Alternatively, use a wrapper like `run_numerical_models.py`.
 from __future__ import division, print_function
 
 import numpy as np, pandas as pd, matplotlib.pyplot as plt
-from astropy import units as u, constants as c
 from scipy.integrate import trapz
 from scipy.interpolate import interp1d
 from math import pi as π

### 2017-12-16 paper/main.tex
paper: update text

@@
 %
-This work aims to clarify the biases that stellar binarity introduces
-to occurrence rates inferred from transit surveys.
-In general, stellar multiplicity leads to diluted planetary 
-radii, overestimated detection efficiencies, and an undercounted number of 
-selected stars (but possibly an overcounted number of searched stars).
-These effects skew occurrence rate measurements in different directions, and 
-we develop simple models that allow us to understand the crucial effects.
-For a model in which all stellar systems are either single or twin binaries, 
-and all planets are identical, we find that ignoring binarity leads to an 
-underestimate of the occurrence at the true radius by a multiplicative factor 
-of $0.76$ (assuming a 10\% twin binary fraction).
+This study develops simplified models of signal-to-noise limited transit 
+surveys, in order to clarify the biases that stellar binarity introduces
+to occurrence rate measurements.
+Particular attention is paid to dilution of observed planet radii, errors in 
+star counts, and detection efficiencies.
+Free parameters in our models include the true radius distribution of planets, 
+and the relative numbers of planets orbiting secondaries, primaries, and 
+single stars.
+In the simplest possible case, all stellar systems are either single or twin 
+binaries, and all planets are identical. If so, then we find that ignoring 
+binarity leads to an underestimate of the occurrence at the true radius by a 
+multiplicative factor of $0.76$ (assuming a 10\% twin binary fraction).
 Using more realistic models for the stellar population and planetary 
-radii, we find that ignoring binarity leads to a $10$\,-\,$30\%$ 
-underestimate of the number of planets per star, depending on the true radius 
-distribution.
-For the occurrence of Earth-sized planets, in our most realistic model the 
-rate is underestimated by $\approx 15\%$~--~at present far smaller than 
-systematic uncertainties on real $\eta_\oplus$ measurements.
-For hot Jupiters, we find that the inferred occurrence rate is 
-$\approx 1.3\times$ smaller than the true rate around single stars.
-We suggest that this latter effect contributes to the discrepant hot Jupiter 
-rates measured by {\it Kepler}\ and the California group's respective surveys.
+radii, we find that the occurrence of Earth-sized planets can be overestimated 
+by at most $\approx 50\%$ when ignoring binarity~--~at present far smaller 
+than systematic uncertainties on real $\eta_\oplus$ measurements.
+We quantify how gaps in the intrinsic planet radius distribution are filled 
+in when binarity is neglected.
+Our models suggest that for most of the observed radius distribution 
+($r>2r_\oplus$), ignoring binarity only leads to errors in inferred occurrence 
+rates at the $\lesssim 10\%$ level.
+One corollary is that binarity is unlikely to strongly influence the HJ rate 
+discrepancy.
 %
@@
 As a separate challenge, finding the correct number of detected planets in a 
-radius bin, $N_{\rm det}$, requires knowledge of the true planetary radii.
+radius bin requires knowledge of the true planetary radii.
 Observers deduce apparent radii.
@@
     \item Model \#1: fixed stars, fixed planets, twin binaries;
-    \item Model \#2: fixed planets and primaries, varying secondaries;
-    \item Model \#3: fixed primaries, varying planets and secondaries.
+    \item Model \#2: fixed primaries, power-law planets, varying secondaries;
+    \item Model \#3: fixed primaries, broken power-law planets and varying 
+    secondaries.
 \end{itemize}
@@
         {\it Top:} At an apparent radius $r\a=r_p$,
-        the observer selects twin binaries out to a larger         
+        the observer searched twin binaries out to a larger         
         distance, $\sqrt{2}\times$ that of single stars.
@@
 \begin{equation}
-\Gamma_{\rm sel}(r) = \delta(r-r_p) \times
+\Gamma_{\rm sel}(r) = \delta(r-r_p) \cdot
 \frac{
@@
 At an apparent radius equal to the true radius ($r\a=r_p$), the observer 
-thinks all stars are singles, with $d<d_0$.
+thinks all searchable stars are singles, with $d<d_0$.
 In fact, binaries with $r\a=r_p$ are also searchable, out to $\sqrt{2}d_0$. 
@@
 $r\a=r_p/\sqrt{2}$.
-This is because of ``radius dilution'':
-for an unresolved point-source... %TODO FIXME
-
+This is because they are ``diluted'':
+for an unresolved point-source,
+\begin{equation}
+\delta_{\rm obs}
+= \left({r\a \over R\a}\right)^2
+= \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over L_{\rm 
+sys}(M_a, q)}.
+\label{eq:delta_obs_general} 
+\end{equation}
 At an apparent radius of $r\a=r_p/\sqrt{2}$, there might also be planets with 
@@
 It may also affect the rate density, which could be a function of the stellar 
-mass, which now changes for secondaries (we assume that singles and primaries 
-have the same mass). Absorbing this dependence into a power law as well,
+mass, which is now varying for secondaries (we assume that singles and 
+primaries have the same mass).
+Absorbing this dependence into a power law as well,
 \begin{equation}
@@
 apparent rate density is higher than the rate density around singles by 1.4\%.
-Although with slightly tedious algebra, the result that for power-law 
-radius distribution (at $r\gtrsim 2r_\oplus$), binarity influences derived 
-occurrence rates at the $\sim$few percent level seems robust for Sun-like 
-stars.
+To summarize, this model suggests that for a power-law radius distribution 
+(applicable for $r\gtrsim 2r_\oplus$), binarity influences apparent planet
+occurrence rates around Sun-like stars at the $\sim$few percent level.
 
@@
 The most immediately arresting result there is a ``bump'' in the apparent rate 
-density at $r\a < 2r_\oplus$.
+density at $r\a < 2r_\oplus$: the true rate for singles is less than the 
+inferred rate.
 For the case in which secondaries host as many (half as many) planets as 
@@
 $\approx 50\%$ ($\approx 25\%$).
-It remains even for the $Z_2/Z_0=0$ case as a $\approx 10\%$ effect.
+The ``bump'' exists even for the $Z_2/Z_0=0$ case as a $\approx 10\%$ effect.
 
 \paragraph{Hot Jupiter occurrence rates}
-Taking Fig.~\ref{fig:occ_rate_model_3_log} and integrating the rate density
-for $r>8r_\oplus$, we can compare the apparent hot Jupiter 
+Taking Fig.~\ref{fig:occ_rate_model_3_log} and integrating the rate density, 
+we can compare the apparent hot Jupiter 
 occurrence rate with the true rate for singles.
@@
 \subsection{Further models: radius gaps, Gaussian HJ distributions}
+\label{sec:further_models}
 
@@
 Precise measurement of the gap's features, in particular its width, 
-depth, and shape, will require more accurate occurrence rates.
-To illustrate binarity's role in the issue, we make identical assumptions as 
-in Model \#3, but instead assume an intrinsic radius distribution
+depth, and shape, will require accurate occurrence rates.
+To illustrate binarity's role in this problem, we make identical assumptions 
+as in Sec.~\ref{sec:model_3}, but instead assume an intrinsic radius 
+distribution
 \begin{align}
@@
 \citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.
-This means that any study assessing its width, depth, etc. only in the planet 
-radius dimension must either account for the blurring that comes from 
-marginalizing over the periods, or else perform tests at fixed periods.
+This means that any study measuring the gap's width or depth in the face of 
+binarity must either perform tests at fixed orbital period, or else 
+marginalize over period and account for the associated blurring in the planet 
+radius dimension.
 
@@
 power law distribution.
-Consider instead the intrinsic radius shape function
+Consider instead a Gaussian radius shape function,
 \begin{equation}
@@
 Integrating to find hot Jupiter rates,
-we find the opposite effect as from the power law model.
+we find the opposite effect as in the power law model.
 For $Z_2/Z_0>0$, 
@@
 \paragraph{How has binarity been considered in occurrence rate measurements?}
-This work has shown that binarity introduces substantial systematic 
-uncertainty to star and planet counts.
-To first order, it appears not to effect estimates of pipeline completeness...
-%TODO
-In spite of this fact, stellar multiplicity has mostly been ignored in 
-calculations of planet occurrence rates using transit survey data\footnote{
+This study has shown that under a reasonable set of simplifying assumptions, 
+binarity can introduce systematic errors to star and planet counts in transit 
+surveys, which then bias derived occurrence rates.
+Thus far, real-world occurrence rate calculations\footnote{
     A list of occurrence rate papers is maintained at 
     \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
-}~
-\citep[\textit{e.g.},][]{howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,dressing_occurrence_2015,burke_terrestrial_2015}.
-For {\it Kepler} occurrence rates specifically, it seems that no one has yet 
-carefully assessed binarity's importance, or lack thereof.
-While we do not resolve the problem, we do suggest
-the approximate scale of the necessary corrections in a survey-independent 
-manner.
+} using transit survey data have mostly ignored stellar 
+multiplicity~\citep[\textit{e.g.},][]{howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,dressing_occurrence_2015,burke_terrestrial_2015}.
+For {\it Kepler} occurrence rates specifically, 
+it seems that no one has yet carefully assessed binarity's importance, or lack 
+thereof.
+While we do not resolve the problem, we do suggest the approximate scale of 
+the necessary corrections in a survey-independent manner.
 
@@
     law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
-    wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016}.
+    wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016,ziegler_robo-ao_2017}.
 The results of these programs have been collected 
@@
 helps reduce contamination in the ``numerator'' of 
-the occurrence rate (\citealt{fulton_california-_2017}; Petigura et al.\! 2018,
-in preparation).
+the occurrence rate (\citealt{fulton_california-_2017}; 
+\citealt{petigura_CKS_2017}).
 However, without an understanding of the multiplicity statistics of the 
-non-KOI stars, the true completeness, and thus the true 
+non-KOI stars, the true number of searchable stars, and thus the true 
 occurrence rates, will remain biased.
@@
 binarity.
-%Simply put~--~do not assume binarity can be ignored, and take the relevant 
-%systematic uncertainties about the selected stars into account.
 For {\it Kepler}, this would require high resolution imaging of a
@@
 efficiency, and the number of selected stars is appropriately counted, it 
-would correct most of binarity's biases.
+would correct many of binarity's biases.
+
+\paragraph{The rate of Earth analogs}
+Per {\it Kepler}'s primary science objective, the rate of Earth-like planets 
+orbiting Sun-like stars has been independently measured by 
+\citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
+    foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
+These efforts have found that the one-year terrestrial planet occurrence rate 
+varies between $\approx 0.03$ and $\approx 1$ per Sun-like star, depending on 
+assumptions that are made when retrieving the rate 
+(\citealt{burke_terrestrial_2015}'s Fig.~17).
+In our Model \#3, the inferred rate can be up to 50\% higher than the true 
+rate around single stars.
+Though this bias seems large, it is currently small compared to the other 
+systematic factors that dominate the dispersion in $\eta_\oplus$ 
+measurements.
+If a future analyses determine absolute values of $\eta_\oplus$ to 
+better than a factor of two, binarity might merit closer attention.
+
+One relevant caveat to our assessment of binarity's importance for 
+$\eta_\oplus$ measurements is that none of our models 
+included the rate density's period-dependence. However, close binaries usually
+provoke dynamical instabilities, leading to fewer long-period planets per 
+star~\citep[\textit{e.g.},][]{holman_long-term_1999,wang_influence_2014,
+    kraus_impact_2016}.
+This effect might further bias transit survey measurements of $\eta_\oplus$
+beyond our rough estimate.
 
 \paragraph{The hot Jupiter rate discrepancy}
-
-There is at least one context in which ignoring binarity may already be 
-leading to discrepant measurements.
+There is at least one context in which ignoring binarity has been suggested as 
+a possible source of discrepant occurrence rate measurements.
 Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
@@
 binarity biases transit survey occurrence rates through its effects on 
-completeness, star counts, and the apparent radii of detected planets.
-Specifically, our results from Sec.~\ref{sec:model_3} indicate that binarity 
-could lead to underestimated HJ rates by a multiplicative factor of $\approx 
-1.3$.
-
-To assess the effect this might have towards resolving the hot Jupiter rate 
-discrepancy we ask:
-what is the probability of \citet{wright_frequency_2012}'s result, given a 
-rate drawn from the stated bounds of Petigura et al.~(2018, in preparation)?
+star counts and the apparent radii of detected planets.
+Our results from Sec.~\ref{sec:model_3} indicate that binarity 
+could lead to underestimated HJ rates relative to singles by a multiplicative 
+factor of at most $\approx 1.13$ (assuming a power-law radius distribution, 
+and that no secondaries host HJs).
+We later pointed out in Sec.~\ref{sec:further_models} that this power-law 
+radius distribution is probably unrealistic. If we instead assumed a 
+Gaussian radius distribution~\citep[e.g.,][]{petigura_CKS_2017}, apparent HJ 
+rates are actually {\it greater} 
+than the true rate around singles.
+
+If we believe the assumed power-law radius distribution, we can ask whether 
+this ``correction factor'' might help resolve the discrepancy.
+Explicitly, we ask: what is the probability of \citet{wright_frequency_2012}'s 
+result, given a rate drawn from the stated bounds of~\citet{petigura_CKS_2017}?
 In other words, we first take the true HJ rate per thousand stars as 
@@
 detect at least 10 hot Jupiters.
-If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account for 
-~\citet{guo_metallicity_2017}'s measured metallicity difference between the 
+If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account 
+for~\citet{guo_metallicity_2017}'s measured metallicity difference between the 
 {\it Kepler}\ field and the local solar neighborhood, 9\% of RV surveys would 
 detect at least 10 hot Jupiters.
-If we multiply once more by $1.3$ to account for binarity's bias, we find that
-23\% of RV surveys would detect at least 10 hot Jupiters, and any discrepancy 
-would be rather tenuous.
-We emphasize that this result is only suggestive~--~a true resolution of the 
-rate discrepancy would likely require a detailed understanding of the {\it 
-    Kepler}\ field's multiplicity statistics.
-
-\paragraph{The rate of Earth analogs}
-Per {\it Kepler}'s primary science objective, the rate of Earth-like planets 
-orbiting Sun-like stars has been independently measured by 
-\citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
-    foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
-These efforts have found that the one-year terrestrial planet occurrence rate 
-varies between $\approx 0.03$ and $\approx 1$ per Sun-like star, depending on 
-assumptions that are made when retrieving the rate 
-(\citet{burke_terrestrial_2015}'s Fig.~17).
-In our Model \#3, the inferred rate is $\approx 0.84\times$ the true rate 
-around single stars.
-This bias is quite small compared to the other systematic factors that 
-currently dominate the dispersion in $\eta_\oplus$ measurements.
-If a future analyses determine absolute values of $\eta_\oplus$ to 
-better than a factor of two, binarity might merit closer attention.
-
-One relevant caveat to our assessment of binarity's importance for 
-$\eta_\oplus$ measurements is that none of our models 
-included the rate density's period-dependence. However, close binaries usually
-provoke dynamical instabilities, leading to fewer long-period planets per 
-star~\citep[\textit{e.g.},][]{holman_long-term_1999,wang_influence_2014,
-    kraus_impact_2016}.
-This effect might further bias transit survey measurements of $\eta_\oplus$
-beyond our rough estimate.
+If we multiply once more by $1.13$ to account for binarity's supposed bias, we 
+find that 14\% of RV surveys would detect at least 10 hot Jupiters, still 
+suggesting a weak discrepancy.
+
+This suggestion should be taken with caution, because it (likely incorrectly) 
+assumes a power-law radius distribution.
+Assuming a Gaussian similar to that reported by~\citet{petigura_CKS_2017},
+we find that binarity is unlikely to resolve the HJ rate discrepancy.
+Of course, such calculations can be at most suggestive~--~a true resolution 
+of binarity's effects may require a detailed understanding of the 
+{\it Kepler}\ field's multiplicity statistics, and the mission's completeness 
+(both for candidate detection and follow-up).
+For instance, if hot Jupiters are less likely to be confirmed in binary 
+systems, this might further bias the rates low.
 
@@
     Kepler}-detected planets orbited the primary or companion stars
-with equal probability (their Sec. 5).
+with equal probability (their Sec.~5).
 Under these assumptions, they found that any given planet's radius is on 
-average underestimated by a multiplicative factor of 1.5.
-
-Our models show that assuming a detected planet has equal probability of 
+average underestimated by a multiplicative factor of $\approx\! 1.5$.
+\citet{ziegler_robo-ao_2017} recently reported a similar value for the real
+population of systems observed by the Robo-AO KOI survey, under the same 
+assumption.
+
+Our models indicate that assuming a detected planet has equal probability of 
 orbiting the primary or secondary leads to an overestimate of
@@
 cases are rare outliers, because the searchable volume for secondaries is so 
-much smaller than that for primaries.
-Phrased in terms of the completeness, in our Model \#3 only $\sim 6\%$ of 
-selected secondaries are searchable, compared to $\sim 60\%$ of selected 
-primaries.
+much smaller than that for primaries (see~Fig.~\ref{fig:model_1_volumes}).
 This means that when high-resolution imaging discovers a binary companion in 
@@
 
-\paragraph{On the utility for future occurrence rate measurements}
+\paragraph{Utility in future occurrence rate measurements}
 {\it TESS}\ is expected to discover over $10^4$ giant 
-planets~\citep{sullivan_transiting_2015}.
+planets~\citep{ricker_transiting_2014,sullivan_transiting_2015}.
 Though they will be difficult to distinguish from false positives, one 
-possible use of this overwhelmingly large sample will to measure an
-occurrence rate of short-period giant planets.
-Our work indicates that if this measurement is to be more accurate than $\sim 
-30\%$, binarity cannot be neglected.
-
+possible use of this large sample will to measure an occurrence rate of 
+short-period giant planets with minimal error from counting statistics.
+Our models suggest that binarity will only become an appreciable fraction of 
+the error budget at the $\approx 10\%$ precision level.
+This should be sufficient for a rate measurement precise enough to indicate a 
+preference between $\approx 0.5\%$ and $\approx 1\%$ of Sun-like stars hosting 
+hot Jupiters.
+
+\begin{comment}
 \paragraph{Independent approaches for estimating binarity's effects}
@@
 16\%.
+\end{comment}
 
@@
 
-This study presented three simple models for the effects of binarity on 
-occurrence rates measured by transit surveys.
-The simplest of these models (Model \#1) provides an order-of-magnitude 
-estimate of how much binarity biases occurrence rates.
-The most realistic of these models (Model \#3) suggests that binarity does 
-lead to underestimates in transit survey occurrence rates, but with less than 
-$30\%$ relative error.
-The model further suggests that hot Jupiter rates measured by transit surveys 
-are biased to infer $\approx 1.3\times$ fewer hot Jupiters per star than 
-surveys that only measure occurrence rates about single stars ({\it 
-    i.e..,} radial velocity surveys).
-It also indicates that binarity's effects on the measured 
-rates of Earth-sized planets are far smaller than current 
-systematic uncertainties.
-Though our models are simplistic, their agreement with T. Barclay's recent 
-independent simulations indicate that they capture the essential 
-ingredients.
-
-\software
-numpy, scipy, pandas, matplotlib
-
-%\acknowledgements
-%It was a pleasure discussing this work with F. Dai and T. Barclay.
-
-\newpage
-\input{hj_rates.tex}
-
-\newpage
+This study presented simple models for the effects of binarity on occurrence 
+rates measured by transit surveys.
+The simplest of these models (Model \#1) provided an order-of-magnitude 
+estimate of how much binarity might affect occurrence rates.
+The most realistic of these models (Model \#3) suggests that binarity leads to 
+overestimates in transit survey occurrence rates at planetary radii 
+$<2r_\oplus$, with at most $\approx 50\%$ relative error.
+Although this is smaller than current systematic uncertainties on the 
+occurrence rates of Earth-sized planets, this means that binarity could
+eventually become an important component of the $\eta_\oplus$ error budget.
+Further, we showed that assuming a power-law radius distribution, 
+then hot Jupiter rates measured by transit surveys could be biased to infer 
+$\approx 1.13\times$ fewer hot Jupiters per star than surveys that only 
+measure occurrence rates about single stars ({\it i.e..,} radial velocity 
+surveys). However, assuming a more realistic Gaussian radius distribution 
+indicates that the effects of binarity on measured hot Jupiter rates are 
+either negligible, or else lead to {\it over}estimated rates.
+The overall result is that our models do not suggest that binarity can 
+resolve the HJ rate discrepancy.
+Finally, we also pointed out that binarity can substantially ``fill in'' 
+gaps in the apparent radius distribution (Fig.~\ref{fig:model_4}).
+This will likely become an important consideration for precise measurements of 
+the depth, width, and slope of \citet{fulton_california-_2017}'s radius gap.
+
+\acknowledgements{
+It was a pleasure discussing this work with F. Dai and T. Barclay.
+
+\software{\texttt{numpy}~\citep{walt_numpy_2011}, 
+\texttt{scipy}~\citep{jones_scipy_2001}, 
+\texttt{matplotlib}~\citep{hunter_matplotlib_2007}, 
+\texttt{pandas}~\citep{mckinney-proc-scipy-2010}
+}
+}
+
 \appendix
@@
 (Eq.~\ref{eq:defn_apparent_rate_density}).
-The planets with $(\pp\a, \ps\a)$ are associated with 
+Let us explicitly write $\pp=r$ and $\ps=M$; $R$ and $L$ are uniquely 
+determined from the assumed stellar mass--radius--luminosity relation. We 
+neglect the dependence on planetary orbital period.
+The planets with $(r\a, M\a)$ are associated with 
 systems of many different planetary and stellar properties, so $n_{\rm 
-det}(\pp\a, \ps\a)$ is given by the convolution of the true rate density, 
-$\Gamma(\pp, \ps)$, and $\mathcal{N}(\pp\a, \ps\a; \pp, \ps)$, the number (per 
-unit $(\pp\a, \ps\a)$) of searchable stars that give $(\pp\a, \ps\a)$  when 
-the true system actually has $(\pp, \ps)$:
+det}(r\a, M\a)$ is given by the convolution of the true rate density, 
+$\Gamma(r, M)$, and $\mathcal{N}(r\a, M\a; r, M)$, the number (per 
+unit $(r\a, M\a)$) of searchable stars that give $(r\a, M\a)$  when 
+the true system actually has $(r, M)$. Mathematically,
 \begin{align}
-N_{\rm det}(\pp\a, \ps\a)=\sum_i N_{\rm det}^i(\pp\a, \ps\a)
-=\sum_i \int \mathrm{d}\pp\mathrm{d}\ps\,
-\mathcal{N}_{\rm s}^i(\pp\a,\ps\a; \pp, \ps)
-\cdot\Gamma^i(\pp, \ps)\cdot p_{\rm tra}(\pp, \ps),
+n_{\rm det}(r_a, M_a) &=
+\sum_i n_{\rm det}^i(r_a, M_a) \\
+&=
+\sum_i \int \mathrm{d}r \mathrm{d}M \,
+\mathcal{N}_{\rm s}^i(r_a,M_a; r,M)
+\cdot\Gamma_i(r,M) \cdot p_{\rm tra}(r,M),
+\label{eq:n_det}
 \end{align}
@@
 
+\paragraph{Single stars} For $i=0$, 
+\begin{equation}
+\mathcal{N}_{\rm s}^0(r\a,M\a; r,M)
+=\delta(r\a-r)\delta(M\a-M) N\s^0(r,M),
+\end{equation}
+so
+\begin{equation}
+n_{\rm det}^0(r\a, M\a)=N\s^0(r\a,M\a)\cdot \Gamma_0(r\a, 
+M\a) \cdot p_{\rm tra}(r\a, M\a).
+\end{equation}
+
+\paragraph{Primaries in binaries}
+The number of primaries with apparent parameters $(r_a,M_a)$ given the 
+true parameters $(r,M)$ is
+\begin{equation}
+\mathcal{N}_{\rm s}^1(r_a, M_a; r, M)
+=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r_a, M_a, q; r, M),
+\label{eq:fancyN_s_1}
+\end{equation}
+where $f(q)$ is the volume-limited binary mass ratio distribution.
+
+Since we assume $\ps\a=\ps_1$,
+\begin{equation}
+\mathcal{N}_{{\rm s},q}^1(r_a, M_a, q; r, M) \propto \delta(M_a-M).
+\end{equation}
+In this case, $\mathcal{N}_{{\rm s},q}^1$ is non-zero only at 
+$r_a=R_a\sqrt{\delta_{\rm obs}}$, 
+and the observed depth is
+\begin{equation}
+\delta_{\rm obs}
+= \left[{r\over R(M_a)}\right]^2\times {L(M_a) \over L_{\rm sys}(M_a, q)}
+\equiv \left[{r\over R(M_a)}\right]^2\times \mathcal{A}(q,M\a)^2
+\label{eq:delta_obs_primaries} 
+\end{equation}
+The normalization of $\mathcal{N}_{{\rm s},q}^1$ is given by the number of 
+binaries that are searchable for a signal $\delta_{\rm obs}$ and that have the 
+mass ratio $q$:
+\begin{equation}
+N_{\rm s}^0(\delta_{\rm obs}, 
+L(M_a))\cdot
+{n_b\over n_s}\left[L_{\rm sys}(M_a, q) \over L(M\a)\right]^{3/2}
+=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))
+\cdot \frac{{\rm BF}}{1 - {\rm BF}} \cdot {1 \over \mathcal{A}(q,M\a)^3}.
+\label{eq:primary_normalization}
+\end{equation}
+
+Thus,
+\begin{align}
+\notag
+\mathcal{N}_{{\rm s}, q}^1(r_a, M_a, q; r, M)
+&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))
+\cdot \frac{{\rm BF}}{1 - {\rm BF}} \cdot {1 \over \mathcal{A}(q,M\a)^3}\\
+&\times\delta \left[r_a-r\mathcal{A}(q,M\a)\right]\delta(M_a-M).
+%&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))\cdot\mu(\mathrm{BF},M_a)\\
+%&\times\delta \left(r_a-r\sqrt{{L(M_a) \over L_{\rm sys}(M_a, 
+%q)}}\right)\delta(M_a-M).
+\label{eq:N_s_1}
+\end{align}
+
+\paragraph{Secondaries in binaries}
+In this case, $M=qM_1=qM_a$, so
+\begin{equation}
+\mathcal{N}_{{\rm s},q}^2(r_a, M_a, q; r, M)
+\propto \delta\left(M_a-{M\over q}\right).
+\label{eq:fancyN_s_2_prop}
+\end{equation}
+Again $\mathcal{N}_{\rm s}^2$ is non-zero only at $r_a=R_a\sqrt{\delta_{\rm 
+        obs}}$, but this 
+time
+\begin{equation}
+\delta_{\rm obs} = \left[{r\over R(qM_a)}\right]^2 \times {L(qM_a) 
+    \over L_{\rm sys}(M_a, q)}.
+\end{equation}
+The normalization remains the same as the previous case (we are counting the 
+searchable stars at a given observed depth $\delta_{\rm obs}$, total 
+luminosity of the binary is the same).
+Thus,
+\begin{equation}
+\mathcal{N}_{\rm s}^2(r_a, M_a; r, M)
+=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r_a, M_a, q; r, M),
+\end{equation}
+where
+\begin{align}
+\notag
+\mathcal{N}_{\rm s}^2(r_a, M_a; r, M; q)
+&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a)) \cdot \frac{{\rm BF}}{1 - {\rm BF}} 
+\cdot {1 \over \mathcal{A}(q,M\a)^3}\\
+&\times \delta \left(r_a-r\sqrt{ \left[{R(M_a)\over R(qM_a)}\right]^2 
+    {L(qM_a) 
+        \over L_{\rm sys}(M_a, q)} }\right)\delta\left(M_a-{M\over q}\right).
+\label{eq:mathcal_N_s_2}
+\end{align}
+
+One might worry in Eq.~\ref{eq:mathcal_N_s_2} that we opt to write 
+$\mathcal{N}\s^2 \propto \delta(M_a - M/q)$, rather than $\propto \delta(M_a q 
+- M)$ or some other delta function with the same functional dependence, 
+but a different normalization once integrated.
+We do this because the delta function in Eq.~\ref{eq:mathcal_N_s_2} is 
+defined with respect to the measure ${\rm d}M\a$, not ${\rm d}M$.
+This is because $\mathcal{N}\s^2$ is defined as a number per $r\a$, per $M\a$.
+
+\paragraph{Number of detected planets}
+Marginalizing per Eq.~\ref{eq:n_det}, we find
+\begin{align}
+\notag
+n_{\rm det}^0(r\a, M\a)
+&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^0(r\a, M\a; r, M)
+\cdot\Gamma^0(r, M) \cdot p_{\rm tra}(M)\\
+&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot\Gamma^0(r\a, M\a) \cdot p_{\rm 
+    tra}(M\a),
+\end{align}
+and
+\begin{align}
+\notag
+n_{\rm det}^1(r\a, M\a)
+&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^1(r\a, M\a; r, M)
+\cdot\Gamma^1(r, M) \cdot p_{\rm tra}(M)\\
+&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
+{\mathrm{BF}\over{1-\mathrm{BF}}} \int {\mathrm{d}q \over 
+    \mathcal{A}^4}\,f(q)\,\Gamma^1\left({r_a\over\mathcal{A}}, M\a\right),
+\end{align}
+where
+\begin{equation}
+\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}.
+\end{equation}
+Finally,
+\begin{align}
+n_{\rm det}^2(r\a, M\a)
+&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^2(r\a, M\a; r, M)
+\cdot\Gamma^2(r, M) \cdot p_{\rm tra}(M)\\
+&=
+N\s^0(\delta_{\rm obs}, L(M\a))\cdot \frac{{\rm BF}}{1 - {\rm BF}}
+\int {q \mathrm{d}q \over 
+{\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma^2(r_a/\mathcal{B}, 
+qM\a)\,p_{\rm 
+    tra}(qM\a),
+\end{align}
+where
+\begin{equation}
+\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
+            sys}(M\a, q)} }.
+\end{equation}
+
+\paragraph{General formula for apparent occurrence rate}
 Using the results above, the apparent rate density,
@@
 \frac{1}{N_{\rm s,a}(r\a,M\a) p_{\rm tra}(r\a,M\a)} \times
-\sum_i N_{\rm det}^i (r\a,M\a),
+\sum_i n_{\rm det}^i (r\a,M\a),
 \end{align}
@@
 \end{align}
-This equation is used to derive Eq.~\ref{eq:model5_apparent_rate_density}.
+This equation is used to derive Eqs.~\ref{eq:model5_apparent_rate_density} 
+and~\ref{eq:powerlaw_vary_binary}, and is numerically integrated to create 
+Figs.~\ref{fig:occ_rate_model_3_log},~\ref{fig:model_4}, 
+and~\ref{fig:gaussian_HJ}.
+It is validated in limits in which it is possible to write down the answer 
+(e.g., Eq.~\ref{eq:model_1_apparent_rate_density}), and also against a Monte 
+Carlo realization of the twin binary models (Secs.~\ref{sec:model_1} 
+and~\ref{sec:model_2}).
+
+\newpage
+\input{hj_rates.tex}
 

### 2017-12-16 paper/main.tex
paper: caption clarification

@@
     \caption{
-        {\it Left:} rate density and {\it right:} rate as a 
-        function of planet radius in Model \#3. This model has fixed primaries 
+        {\it Left:} rate density and {\it right:} rate (over $0.5r_\oplus$ 
+        bins) as a function of planet radius in Model \#3. This model has 
+        fixed primaries 
         and 
@@
     \caption{
-        {\it Left:} rate density and {\it right:} rate as a 
-        function of planet radius in a model with a radius gap 
+        {\it Left:} rate density and {\it right:} rate (over $0.25r_\oplus$ 
+        bins) as a function of planet radius in a model with a radius gap 
         (Eq.~\ref{eq:model4_radius_distribution}).

### 2017-12-18 paper/main.tex
paper: wordsmith, add box

@@
 \usepackage{grffile} % checks for multiple dots in figure filenames
+\usepackage{empheq} % for boxing equations
+\newcommand*\widefbox[1]{\fbox{\hspace{1em}#1\hspace{1em}}}
 
@@
 The observed transit depth $\delta_{\rm obs}$ constitutes the signal, ${\rm 
-S}$. The survey is shot-noise dominated, and so the noise ${\rm N}$
-scales as the inverse root of the photon flux received from any stellar 
-system, ${\rm N} \propto (L_{\rm sys}/d^2)^{-1/2}$, for $L_{\rm sys}$ the 
-system luminosity and $d$ its distance.
+S}$. The survey is shot-noise dominated, and the fractional photon noise 
+${\rm N}$ scales as the inverse root of the photon flux received from any 
+stellar system, ${\rm N} \propto (L_{\rm sys}/d^2)^{-1/2}$, for $L_{\rm sys}$ 
+the system luminosity and $d$ its distance.
 The solid angle coverage, telescope area, and survey duration are part of the 
@@
 include an explicit detection efficiency term in 
-Eq.~\ref{eq:defn_apparent_rate_density} is to inversely weight for planets 
+Eq.~\ref{eq:defn_apparent_rate_density} to inversely weight for planets 
 that had low probabilities of being detected.
@@
 evaluates to
-\begin{align}
+
+\begin{empheq}[box=\widefbox]{align}
 \notag
@@
 \label{eq:general_Gamma_a}
-\end{align}
+\end{empheq}
 This equation is used to derive Eqs.~\ref{eq:model5_apparent_rate_density} 

### 2017-12-19 paper/main.tex
paper: improve text for readability

@@
 \usepackage{empheq} % for boxing equations
-\newcommand*\widefbox[1]{\fbox{\hspace{1em}#1\hspace{1em}}}
+\newcommand*\widefbox[1]{\fbox{\hspace{0.2cm}#1\hspace{0.2cm}}}
 
@@
 \newcommand{\s}{_{\rm s}}
+\newcommand{\p}{_{\rm p}}
 \renewcommand{\d}{_{\rm d}}
@@
     4 Ivy Lane, Princeton, NJ 08540, USA}
-\author{J. N. Winn}
+\author{K. Masuda}
 \affiliation{
@@
     4 Ivy Lane, Princeton, NJ 08540, USA}
-\author{K. Masuda}
+\author{J. N. Winn}
 \affiliation{
@@
 To compute an occurrence, at every planetary and stellar property the 
-astronomers choose the stars (among those initially surveyed) around which the 
-planets of interest appeared to be searchable.
+astronomers choose the stars around which the planets of interest appeared to 
+be searchable.
 Correcting for the geometric transit probability $p_{\rm tra}$, they report an 
@@
 between binary and single-star systems.
-If ``occurrence rate'' is defined as the mean number of planets within 
-set radius and period bounds per star in a given mass interval, it must 
-implicitly marginalize over stellar multiplicity.
-This means marginalizing over ``occurrence rates in single star systems'', 
-``occurrence rates about primaries'', and
-``occurrence rates about secondaries''
-\citep[see][]{wang_occurrence_2015}.
+In an observed sample of stars that contains both singles and binaries, the 
+detected planets would then be drawn from different intrinsic 
+distributions for the occurrence rates in single star systems, 
+about primaries, and about secondaries~\citep[{\it 
+e.g},][]{wang_occurrence_2015}.
 
@@
 Eq.~\ref{eq:defn_apparent_rate_density} is observationally-biased.
-There are errors in $n_{\rm det}(\pp\a,\ps\a)$ due to planet radius 
-misclassification.
+There are errors in $n_{\rm det}(\pp\a,\ps\a)$ due to misclassification of 
+both planet radii and stellar properties.
 There are errors in $N_{{\rm s,a}}(\pp\a,\ps\a)$ because an apparently 
@@
 Binarity might also affect the observers' ability to correctly select 
-searchable stars (but see Sec.~\ref{sec:model_1} for discussion of this 
+searchable stars (but see Sec.~\ref{sec:discussion} for discussion of this 
 issue).
@@
 Correcting for binarity's observational biases is non-trivial.
-For instance, in counting the number of selected stars, even after realizing 
+For instance, in counting the number of searchable stars, even after realizing 
 that binaries count as two stars, one must note that the multiplicity fraction 
-of {\it selected} stars is greater than that of a volume limited 
-sample.
-This is the familiar Malmquist bias: binaries are selected out to larger 
-distances than single stars because they are more luminous.
-As a separate challenge, finding the correct number of detected planets in a 
-radius bin requires knowledge of the true planetary radii.
-Observers deduce apparent radii.
-In binaries, the apparent and true radii differ because of diluting flux, 
-and possibly because the planet is assumed to orbit the wrong star
-\citep[\textit{e.g.},][]{furlan_kepler_2017}.
+of stars that are searchable for a given observed transit depth is greater 
+than that the multiplicity fraction in a volume limited sample.
+This is the familiar Malmquist bias: at a fixed $\delta_{\rm obs}$, binaries 
+are searchable out to larger distances than single stars because they are more 
+luminous.
+While this is what biases detectability, separate effects bias interpretation:
+ignoring binarity, the (apparent) radii assigned to planets in binaries will 
+typically be smaller than the true radii.
+The apparent and true radii differ because of diluting flux, and possibly 
+because the planet is assumed to orbit the wrong 
+star.
 
 To gain intuition for the many observational biases at play,
-we consider a set of idealized transit surveys:
-\begin{itemize}
-    \item Model \#1: fixed stars, fixed planets, twin binaries;
-    \item Model \#2: fixed primaries, power-law planets, varying secondaries;
-    \item Model \#3: fixed primaries, broken power-law planets and varying 
-    secondaries.
-\end{itemize}
-In Sec.~\ref{sec:definitions}, we clarify our terminology and state
-assumptions that apply throughout this study.
-We then present our transit survey models in 
-Secs.~\ref{sec:model_1}-\ref{sec:model_3}, where 
-each subsection corresponds to a model listed above.
-We interpret these calculations throughout, and in 
-Sec.~\ref{sec:discussion} connect them to topical questions in 
-the interpretation of transit survey occurrence rates.
-In particular, we mention the ``hot Jupiter rate discrepancy'', the relevance 
-towards measurements of $\eta_\oplus$, and the implications for detailed 
-study of \citet{fulton_california-_2017}'s recently discovered ``valley''.
-We conclude in Sec.~\ref{sec:conclusion}.
+we consider a set of idealized transit surveys.
+First, we discuss the simplest possible cases (Sec.~\ref{sec:simplest}), in 
+which all planets have identical properties, and all stars have identical 
+properties except that some are in binaries.
+The straightforward thought-experiments of Sec.~\ref{sec:simplest} are then 
+generalized in Sec.~\ref{sec:general_formula} to allow for varying populations 
+of secondaries, and for varying intrinsic occurrence rate distributions.
+Sec.~\ref{sec:more_complicated} investigates questions of interest, 
+including (a) measurements of $\eta_\oplus$, (b) the ``hot Jupiter rate 
+discrepancy'', and (c) \citet{fulton_california-_2017}'s 
+recently discovered ``valley''.
+We discuss what our models suggest about binarity's biasing effects in 
+Sec.~\ref{sec:discussion}, and conclude in Sec.~\ref{sec:conclusion}.
 
@@
 
-\section{Definitions and Preliminaries}
-\label{sec:definitions}
-
-\subsection{Occurrence rate, occurrence rate density}
-Define the occurrence rate density, $\Gamma$, as the expected number of 
-planets per star per unit of planetary and stellar phase space.
-Since we will mainly be concerned with the rate density's dependence on 
-planetary radii $r$, we write
-\begin{equation}
-\Gamma(r) = \frac{{\rm d}\Lambda}{{\rm d}r},
-\label{eq:rate_density_defn}
-\end{equation}
-where $\Lambda$ is the occurrence rate.
-In this notation, ``the occurrence rate of planets of a particular size'' 
-translates to an integral of Eq.~\ref{eq:rate_density_defn}, evaluated over a 
-radius interval.
-
-The above definition implicitly marginalizes the rate density over stellar 
-multiplicity.
-Considering only single and binary systems, the rate density for any selected 
-sample of stars is a weighted sum of rate densities for each system type:
-\begin{equation}
-N_{\rm tot} \Gamma_{\rm sel}(r) =
-N_0 \Gamma_0(r) +
-N_1 \Gamma_1(r) +
-N_2 \Gamma_2(r),
-\label{eq:rate_density_marginalized}
-\end{equation}
-where $i=0$ corresponds to single stars, $i=1$ to primaries of 
-binaries, and $i=2$ to secondaries of binaries.
-$N_{\rm tot} = \sum_i N_i$ is the total number of selected stars, and 
-$N_0,N_1,N_2$ are the number of selected single stars, primaries, and 
-secondaries. For our purposes binary systems are not identifiable, and so 
-$N_1=N_2$.
-
-The rate density for each type of star, $\Gamma_i(r)$, can be written as 
-the product of a shape function and a constant:
-\begin{equation}
-\Gamma_i(r) = \frac{{\rm d}\Lambda_i}{{\rm d}r} = Z_i f_i(r),
-\quad {\rm for}\ i\in\{0,1,2\}.
-\label{eq:rate_density_shape}
-\end{equation}
-The shape function is normalized to unity.
-The $Z_i$'s can be interpreted as each system type's occurrence rate 
-$\Lambda_i$, integrated over all planetary radii.
-They are equivalent to the number of planets per single star, primary, or 
-secondary.
-
-\subsection{Searchable stars}
-For a given planet radius, semimajor axis, and stellar luminosity, a fixed 
-signal-to-noise floor yields a maximum searchable 
+\section{The simplest possible transit survey models}
+\label{sec:simplest}
+
+\subsection{Twin binaries, identical stars, identical planets}
+\label{sec:model_1}
+
+\begin{figure}[!tb]
+    \begin{center}
+        \includegraphics[width=0.6\textwidth]{figures/visualize_volumes.pdf}
+    \end{center}
+    \caption{
+        Cartoon of the searchable volumes for single stars ({\it left}), and 
+        twin binaries ({\it right}).
+        This model assumes all stars have equal mass and luminosity, and 
+        all planets have the same true radius $r=r\p$.
+        {\it Top:} At an apparent radius $r\a=r\p$,
+        the observer searched twin binaries out to a larger         
+        distance, $\sqrt{2}\times$ that of single stars.
+        Because of dilution, there are no planets in twin binaries with 
+        $r\a=r\p$.
+        {\it Middle:} At an apparent radius $r\a=r\p/\sqrt{2}$, the 
+        searched volumes are half those at $r\a=r\p$. 
+        The only detected planets with $r\a=r\p/\sqrt{2}$ orbit twin binaries.
+        {\it Bottom:} Planets with a true radius $r=r\p$ are searchable to 
+        a maximum distance $d_0$ around singles, and $d_0/\sqrt{2}$ around 
+        twin binaries.
+    }
+    \label{fig:model_1_volumes}
+\end{figure}
+
+Since the effects of binarity are most pronounced when the two components are 
+similar, we begin by considering a universe in which all planets are 
+identical, and all stars are identical except that some fraction of them exist 
+in binaries. The goal of this thought experiment is to compare the occurrence 
+inferred by observers ignoring binarity with the true occurrence in single 
+star systems.
+
+First, what are the possible apparent radii of detected planets?
+If the true planet radius is $r=r\p$, then planets in singles will be 
+detected with the identical apparent radii: $r\a = r\p$.
+Conversely, all detections in twin binaries will have apparent radii 
+$r\a=r\p/\sqrt{2}$, because they are diluted.
+For an unresolved point-source,
+\begin{equation}
+\delta_{\rm obs}
+= \left(\frac{r\a}{R\a}\right)^2
+= \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over L_{\rm 
+        sys}(M_1, q)},
+\label{eq:delta_obs_general} 
+\end{equation}
+where $R_{\rm host}$ ($L_{\rm host}$) is the planet-host's stellar radius 
+(luminosity), $R\a$ is the apparent stellar radius, $L_{\rm sys}=L_1+L_2 = 
+L(M_1) + L(qM_1)$ is the system luminosity, and $q=M_2/M_1$ is the binary mass 
+ratio.
+We assume that the stellar radius and luminosity are uniquely related to the 
+stellar mass.
+The observers, with no a priori knowledge of the distance to a system, would 
+measure a flux, assume a stellar mass $M\a=M_1$, and estimate both a stellar 
+radius $R\a = R(M\a)$ and an under-luminous system luminosity of $L_{\rm 
+sys,a}(M\a) = L(M\a)$.
+
+The planets will be detected if and only if their host stars are searchable.
+For a fixed signal-to-noise floor, there is a maximum searchable 
 distance~\citep{pepper_using_2003,pepper_searching_2005}.
@@
 \end{equation}
-where $n$ is the volume density of {\it e.g.}, single star, or binary systems.
+where $n$ is the number per unit volume of {\it e.g.}, single star, or binary 
+systems.
 We neglect the dependence of $n$ on stellar type.
 
-\subsection{Relation between Apparent and Actual Stellar Properties}
-
-We assume that the apparent properties of an unresolved binary are identical to
-the true properties of the primary:
-\begin{equation}
-M\a=M_1, \quad R\a=R_1, ...
-\end{equation}
-We also take the stellar radius and luminosity to be uniquely related to the 
-stellar mass.
-Given these assumptions, the total luminosity of a system is
-\begin{equation}
-L_{\rm sys}=L_1+L_2=L(M\a)+L(qM\a),
-\end{equation}
-where $q=M_2/M_1$. Note that $L_{\rm sys}$ is the true value (because $M\a$ is 
-the true primary mass), while an observer with no a priori knowledge of the 
-distance to a system would measure a flux, assume a stellar mass $M_a$, and 
-estimate a system luminosity of $L(M\a)$.
-
-\subsection{Apparent number of searchable stars}
-\label{subsec:apparent_N_searchable}
+The searchable volumes for our thought experiment are illustrated 
+in Fig.~\ref{fig:model_1_volumes}.
+At an apparent radius equal to the true radius ($r\a=r\p$), single stars 
+with $d<d_0$ are searchable.
+Binaries with $r\a=r\p$ are also searchable, out to $\sqrt{2}d_0$. 
+However, in this model no such systems exist; all planets in twin binaries 
+have true radii $r=r\p$, and so are observed with apparent radii 
+$r\a=r\p/\sqrt{2}$, out to $d_0/\sqrt{2}$.
+At an apparent radius of $r\a=r\p/\sqrt{2}$, there could also be planets with 
+true radii $r=r\p/\sqrt{2}$ orbiting singles~---~however none of these exist 
+in this model.
+
+How many planets are detected?
+If we assume that there are $N\s^0(r\a)$ singles that are searchable for 
+planets with $r\a$, and that there are $Z_0$ planets per single, then 
+single stars contribute
+\begin{equation}
+n_{\rm det}^0(r\a) = N\s^0(r\a) Z_0 p_{\rm tra} \cdot \delta(r\a - r_p)
+\end{equation}
+planet detections (per unit $r\a$), where $\delta$ is the Dirac delta function.
+
+We can write similar equations for the binaries.
+First though, we define a ratio $\mu \equiv N\s^{\rm b}(r\a) / N\s^0(r\a)$ 
+between the number of searchable binary systems and the number of searchable 
+singles at a given $r\a$.
+This quantity is useful because although $N\s^{\rm b}$ and $N\s^0$ vary
+as a function of the observed transit depth, $\mu$ remains fixed.
+Applying this definition, at $r\a=r\p/\sqrt{2}$, some detections will come 
+from primaries,
+\begin{equation}
+n_{\rm det}^1(r\a) =
+\mu N\s^0(r\a) Z_1 p_{\rm tra}
+\cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right),
+\end{equation}
+and some from secondaries,
+\begin{equation}
+n_{\rm det}^2(r\a) = 
+\mu N\s^0(r\a) Z_2 p_{\rm tra}
+\cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right),
+\end{equation}
+where $Z_1$ is the number of planets per primary, $Z_2$ is the number of 
+planets per secondary, and $p_{\rm tra}$ is the same for identical stars.
+In the case of twin binaries, Eq.~\ref{eq:N_searchable_prop} gives $\mu = 
+2^{3/2} n_{\rm b}/n_{\rm s} = 2^{3/2} {\rm BF}/(1-{\rm BF})$, for ${\rm BF}$ 
+the binary fraction\footnote{The binary fraction is the fraction of systems in 
+a volume-limited sample that are binary. It is equivalent to the multiplicity 
+fraction if there are no triple, quadruple, or higher order multiples.
+}.
+
+The last item we need to write down the apparent rate density $\Gamma\a(r\a)$ 
+is the number of unresolved point-sources on sky, $N_{\rm s,a}$.
+Assuming that the apparent stellar radius is fixed, then given the 
+apparent planet radius $r\a$,
+\begin{equation}
+N_{\rm s,a}(r\a) = N\s^0(r\a) \times (1 + \mu)
+\label{eq:apparentlysearchable_to_searchable}
+\end{equation}
+relates the number of apparently searchable point-sources to the number of 
+searchable singles.
+From the discussion above, it should be clear that there are in fact
+$N\s^0(r\a)\times (1 + 2\mu)$ searchable stars at any given $r\a$; the 
+observers are under-counting.
+
+Using Eq.~\ref{eq:defn_apparent_rate_density}, the apparent rate density 
+computed without considering binarity is
+\begin{align}
+\Gamma\a(r\a) = 
+\frac{1}{1+\mu} Z_0 \cdot
+\delta(r\a-r\p)  +
+\frac{\mu}{1+\mu} (Z_1 + Z_2) \cdot
+\delta\left(r\a-\frac{r\p}{\sqrt{2}} \right).
+\label{eq:model_1_apparent_rate_density}
+\end{align}
+The number of searchable singles at a given apparent radius, 
+$N\s^0(r\a)$, makes no appearance.
+The observer's errors in Eq.~\ref{eq:model_1_apparent_rate_density} are 
+(A) under-counting the number of searchable stars at any apparent radius;
+and
+(B) inferring radii in binary systems that are all $\sqrt{2}$ too small.
+
+\begin{figure}[!tb]
+    \begin{center}
+        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
+    \end{center}
+    \vspace{-0.5cm}
+    \caption{
+        Inferred occurrence rates over $0.01r_\oplus$ bins in planet 
+        radius, for a model with identical stars, identical planets, and twin 
+        binaries.
+        We assume a twin binary fraction of ${\rm BF}=0.1$, and that all 
+        stars (single, primary, and secondary) host planets at equal 
+        rates.
+        If the true planet radius is $r\p$, all planets detected in binaries 
+        will have apparent radii $r\a = r\p/\sqrt{2}$.
+    }
+    \label{fig:occ_rate_model_1}
+\end{figure}
+
+To assess the severity of these errors, we need to assume a binary fraction, 
+and to know the true number of planets per single, primary, and secondary star 
+($Z_0,Z_1,$ and $Z_2$).
+For the former,
+\citet{raghavan_survey_2010} found a multiplicity 
+fraction of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$, 
+which we take as a binary fraction. 
+``Twin binaries'' are perhaps 10-20\% of the binaries in a volume-limited 
+sample, depending on how ``twin'' is defined.
+Thus a representative twin binary fraction for this model is ${\rm BF}\approx 
+0.05$-$0.1$. 
+For the latter, we take $Z_0=Z_1=Z_2=0.5$, and plot the resulting occurrence 
+rates as a function of planet radius in Fig.~\ref{fig:occ_rate_model_1}.
+
+Our point for comparison is the rate density for single stars,
+\begin{equation}
+\Gamma_0(r) = Z_0 \cdot \delta(r-r\p).
+\end{equation}
+We can define a rate density ``correction factor'', $X_\Gamma$, as the ratio 
+of the apparent to single star rate density,
+\begin{equation}
+X_\Gamma(r) \equiv \left. \frac{\Gamma_a(r\a)}{\Gamma_0(r)} \right|_{r\a 
+    \rightarrow r}.
+\end{equation}
+Continuing in the assumption that the number of planets per single, primary, 
+and secondary star are equal, we find a rate density 
+correction factor at the true planet radius of $1/(1+\mu)$.
+This yields a correction of 0.76 if ${\rm BF}=0.1$, and 0.87 if ${\rm 
+    BF}=0.05$. Rephrasing the result, if the twin binary fraction were 
+$(2^{3/2}+1)^{-1}\approx 0.26$, then the apparent rate at $r\a=r\p$ would be 
+half the true rate at $r=r\p$.
+For most stellar types, the twin binary fraction is not that high.
+
+An alternative assumption is that secondaries do not host planets. In that 
+case, $Z_0=Z_1$, and $Z_2=0$. The correction to the rate density at the true 
+planet radius becomes $(1+2\mu)/(1+\mu)^2$.
+This evaluates to 0.94 if ${\rm BF}=0.1$, and 0.98 if ${\rm BF}=0.05$.
+While it seems unlikely that secondaries are planet-less, 
+it is worth noting that $\Gamma\a/\Gamma$ is sensitive to the relative number 
+of planets per single, primary, and secondary.
+
+\subsection{Twin binaries, identical stars, two planet sizes}
+
+A simple extension to the previous example will help us further distinguish 
+the detected populations.
+Consider now a universe that is the same in every respect to that of 
+Sec.~\ref{sec:model_1}, except now half of planets have radii $r\p$, while 
+the other half have $r\p/\sqrt{2}$.
+The true rate densities are
+\begin{equation}
+\Gamma_i(r) = \frac{Z_i}{2} \left[
+\delta(r-r\p) + \delta\left(r-\frac{r\p}{\sqrt{2}}\right)
+\right], \quad {\rm for}\  i \in \{ 0,1,2 \},
+\end{equation}
+where as always $i=0$ corresponds to singles, $i=1$ to primaries, and $i=2$ to 
+secondaries, and the $Z_i$'s are the number of planets per star of each type.
+
+Following an identical line of reasoning as before, the apparent rate density 
+can be written
+\begin{align}
+\notag
+\Gamma\a(r\a) &=
+\frac{1}{2(1+\mu)} \left[
+Z_0 \cdot \delta(r\a - r\p)
++
+\left[Z_0 + \mu (Z_1 + Z_2)
+\right] \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right) 
+\right. \\
+&\quad\quad\quad\quad\quad\quad\quad\quad+
+\left.
+\mu(Z_1 + Z_2) \cdot \delta\left(r\a - \frac{r\p}{2}\right)
+\right].
+\label{eq:two_radii_twins}
+\end{align}
+The important qualitative point of this equation is that at $r\a = 
+r\p/\sqrt{2}$, two populations contribute.
+The first population is singles with $r=r\p/\sqrt{2}$, and the second is twin 
+binaries with $r=r\p$.
+Both populations are detected out to the same maximum searchable distance.
+Just as with Eq.~\ref{eq:apparentlysearchable_to_searchable}, we will have a 
+cancellation of $N\s^0(r\a)$ terms, leaving only the $\mu$ weights.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{General formula for apparent occurrence rate}
+\label{sec:general_formula}
+
+To generalize the procedure of Sec.~\ref{sec:simplest}, we consider a S/N 
+limited transit survey in which all the primaries and single stars have 
+identical properties.
+For example, they might all be solar analogs, roughly similar to 
+the stars that {\it Kepler} surveyed~\citep{batalha_selection_2010}.
+We let the properties of the secondaries vary, and assume that there are some 
+functions $L(M)$ and $R(M)$ that specify a star's luminosity and radius in 
+terms of its mass.
+We then allow for an arbitrary volume-limited mass ratio distribution 
+$f(q)$, and also for arbitrary true rate densities for singles, primaries, 
+and doubles ($\Gamma_0, \Gamma_1, \Gamma_2$).
+Since the properties of the secondaries vary, we must consider not only the 
+dependence of the rate densities on planet radius, but also on stellar mass.
+We presume that the observers always take the properties of a binary system to 
+be those of the primary.
+
+Given this laundry-list of assumptions, a general formula for the apparent 
+rate density follows:
+\begin{align}
+\notag
+\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
+\left\{ \Gamma_0(r\a, M\a)+ 
+\frac{{\rm BF}}{1 - {\rm BF}}
+\left[ \int {\mathrm{d}q \over \mathcal{A}^4}\,f(q)\,\Gamma_1\left({r\a\over 
+    \mathcal{A}}, 
+M\a\right)\,
+\right.   
+\right. \\
+& \quad\quad\quad\quad\quad \left.\left.
++\int {q \mathrm{d}q \over 
+    {\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma_2\left({r\a\over 
+    \mathcal{B}}, 
+qM\a\right)\,
+{R(qM\a) \over R(M\a)}
+q^{-1/3} \right]	\right\},
+\label{eq:general_Gamma_a}
+\end{align}
+where 
+\begin{equation}
+\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}
+\end{equation}
+and
+\begin{equation}
+\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
+            sys}(M\a, q)} }
+\end{equation}
+are the dilution terms appropriate to primaries and secondaries, and as before 
+${\rm BF}$ is the volume-limited binary fraction.
+
+A derivation of Eq.~\ref{eq:general_Gamma_a} is given in the 
+\hyperref[sec:appendix]{Appendix}; here we highlight its qualitative 
+features.
+The terms inside the curly braces $\{ \ldots \}$ are the sum of 
+the apparent rate densities from singles, primaries, and secondaries.
+The contribution from singles is not affected by binarity.
+In the contributions from primaries and secondaries,
+planets with $(r\a, M\a)$ are associated with 
+systems of many different planetary and stellar properties.
+This means that $n_{\rm det}(r\a, M\a)$ is given by a convolution of the 
+true rate density, $\Gamma(r, M)$, and the number per unit $(r\a, M\a)$ of 
+searchable stars that give $(r\a, M\a)$  when the true system actually has 
+$(r, M)$.
+This convolution has been evaluated, leaving only a dependence on the mass 
+ratio distribution.
+Finally, the latter term in the apparent rate density of secondaries comes 
+from a correction for the overestimated transit probability.
+
+\paragraph{Ratio of searchable binaries to singles}
+We must also specify the exact form of $\mu({\rm BF},M\a)$, the ratio of 
+the number of searchable binary systems to singles.
+Given the observed signal $\delta_{\rm obs}$ and apparent stellar mass $M\a$, 
+recall that the maximum searchable distance for singles and binaries are 
+proportional to $\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm 
+obs}\cdot [L(M\a)+L(qM\a)]^{1/2}$.
+Applying Eq.~\ref{eq:N_searchable_prop},
+\begin{equation}
+\mu({\rm BF},M\a) = 
+\frac{N\s^{\rm b}(r_a)}{N_s^0(r\a)}=
+\int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
+f(q)\mathrm{d}q.
+\label{eq:mu_general}
+\end{equation}
+
+If $\mathrm{BF}$ is independent of $q$, $L \propto M^\alpha$, and $f(q) 
+\propto q^\beta$, this reduces to
+\begin{equation}
+\mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 
+\left(1+q^\alpha\right)^{3/2} q^\beta\mathrm{d}q,
+\label{eq:mu_power_laws}
+\end{equation}
+which may be written in a closed form using the hypergeometric function.
 
@@
         At a given observed depth, the searchable binaries in a transit survey 
-        are magnitude-limited (see Sec.~\ref{subsec:apparent_N_searchable}).
+        are magnitude-limited.
     }
@@
 \end{figure}
-
-Given the observed signal $\delta_{\rm obs}$ and apparent stellar mass $M\a$, 
-the maximum searchable distance for singles and binaries are proportional to 
-$\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm obs}\cdot 
-[L(M\a)+L(qM\a)]^{1/2}$.
-Thus, the apparent number of searchable stars (points in the sky), which 
-will be selected by an ignorant observer, can be written as
-\begin{align}
-N_{\rm s,a}(\delta_{\rm obs}, M\a)
-= N\s^0(\delta_{\rm obs}, L(M\a)) \left[1+\mu(\mathrm{BF}, 
-M\a)\right],
-\label{eq:N_selected}
-\end{align}
-where $N\s^0$ is the number of searchable singles (this agrees with the actual 
-value), $\mathrm{BF}=n_{\rm b}/(n_{\rm s}+n_{\rm b})$ 
-is the binary fraction in a volume-limited sample,
-$n_s$ ($n_b$) is the number density of single (binary) systems in a 
-volume-limited sample,
-and $\mu$ is the ratio of the number of double to single star 
-systems that are searchable for an observed signal $\delta_{\rm obs}$.
-Applying Eq.~\ref{eq:N_searchable_prop},
-\begin{equation}
-\mu({\rm BF},M\a) = 
-{N_{\rm d} \over N_s^0}=
-\int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
-f(q)\mathrm{d}q,
-\label{eq:mu_general}
-\end{equation}
-where $f(q)$ is the distribution of binary mass ratios in a volume-limited 
-sample.
-If $\mathrm{BF}$ is independent of $q$, $L \propto M^\alpha$, and $f(q) 
-\propto q^\beta$, this reduces to
-\begin{equation}
-\mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 
-\left(1+q^\alpha\right)^{3/2} q^\beta\mathrm{d}q,
-\end{equation}
-which may be written in a closed form using the hypergeometric function.
 
@@
 In particular, the sample of searchable binaries is magnitude-limited.
-Given a searchable binary, the probability of drawing a mass ratio $q$ will 
-scale as
+Given a searchable binary, the probability it having a mass ratio $q$ 
+scales as
 \begin{equation}
@@
 
-\section{Idealized Models of Transit Surveys}
-
-\subsection{Model \#1: fixed stars, fixed planets, twin binaries}
-\label{sec:model_1}
-
-\begin{figure}[!tb]
-    \begin{center}
-        \includegraphics[width=0.6\textwidth]{figures/visualize_volumes.pdf}
-    \end{center}
-    \caption{
-        Cartoon of the searchable volumes for single stars ({\it left}), and 
-        twin binaries ({\it right}).
-        This model (\#1) assumes all stars have equal mass and luminosity, and 
-        all planets have the same true radius $r=r_p$.
-        {\it Top:} At an apparent radius $r\a=r_p$,
-        the observer searched twin binaries out to a larger         
-        distance, $\sqrt{2}\times$ that of single stars.
-        Because of dilution, there are no planets in twin binaries with 
-        $r\a=r_p$.
-        {\it Middle:} At an apparent radius $r\a=r_p/\sqrt{2}$, the 
-        searched volumes are half those at $r\a=r_p$. 
-        The only detected planets with $r\a=r_p/\sqrt{2}$ orbit twin binaries.
-        {\it Bottom:} Planets with a true radius $r=r_p$ are searchable to 
-        a maximum distance $d_0$ around singles, and $d_0/\sqrt{2}$ around 
-        twin binaries. These distances are the same as what an observer 
-        selects based on apparent radii.
-    }
-    \label{fig:model_1_volumes}
-\end{figure}
-
-\begin{figure}[!tb]
-    \begin{center}
-        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
-    \end{center}
-    \vspace{-0.5cm}
-    \caption{
-        Inferred occurrence rates over $0.01r_\oplus$ bins in planet 
-        radius, for Model \#1.
-        This model has fixed stars, fixed planets, and twin binaries. 
-        We assume a twin binary fraction of ${\rm BF}=0.1$, and that all 
-        stars (single, primary, and secondary) host planets at equal 
-        rates.
-        If the true planet radius is $r_p$, all planets detected in binaries 
-        will have apparent radii $r\a = r_p/\sqrt{2}$.
-    }
-    \label{fig:occ_rate_model_1}
-\end{figure}
-
-Since the effects of binarity are most pronounced when the two components are 
-similar, we first consider a universe in which all planets are 
-identical, and all stars are identical except that some fraction of them exist 
-in binaries.
-Expressed mathematically, from Eqs.~\ref{eq:rate_density_marginalized} 
-and~\ref{eq:rate_density_shape} the rate density for a selected sample of 
-stars at planet radius $r$ is
-\begin{equation}
-\Gamma_{\rm sel}(r) = \delta(r-r_p) \cdot
-\frac{
-    Z_0 +
-    \mu (Z_1 + Z_2)
-}{1+2\mu},
-\label{eq:model_1_rate_density}
-\end{equation}
-where $\mu$ is given by Eq.~\ref{eq:mu_general} with $f(q) = \delta(q-1)$,
-$\delta$ is the Dirac delta function, and the true planet radius is 
-$r_p$.
-We will generally write rate densities in terms of $\mu$'s, rather than 
-$N_i$'s, because $\mu$'s are independent of planet radius.
-
-We return to our group of binarity-ignoring astronomers. They select all the 
-points on-sky that they think are searchable: those that are above some flux 
-limit (at each $\delta_{\rm obs}$).
-The relevant stellar samples are illustrated in Fig.~\ref{fig:model_1_volumes}.
-At an apparent radius equal to the true radius ($r\a=r_p$), the observer 
-thinks all searchable stars are singles, with $d<d_0$.
-In fact, binaries with $r\a=r_p$ are also searchable, out to $\sqrt{2}d_0$. 
-However, in this model no such systems exist; all planets in twin binaries 
-have true radii $r=r_p$, and so are observed with apparent radii 
-$r\a=r_p/\sqrt{2}$.
-This is because they are ``diluted'':
-for an unresolved point-source,
-\begin{equation}
-\delta_{\rm obs}
-= \left({r\a \over R\a}\right)^2
-= \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over L_{\rm 
-sys}(M_a, q)}.
-\label{eq:delta_obs_general} 
-\end{equation}
-At an apparent radius of $r\a=r_p/\sqrt{2}$, there might also be planets with 
-true radii $r=r_p/\sqrt{2}$ orbiting a single~---~however none of these exist 
-in this model either.
-Following Eq.~\ref{eq:defn_apparent_rate_density}, the apparent rate density 
-computed without considering binarity is
-\begin{equation}
-\Gamma_a(r_a) = 
-\frac{1}{1+\mu} Z_0 \cdot
-\delta(r\a-r_p)  +
-\frac{\mu}{1+\mu} (Z_1 + Z_2) \cdot
-\delta\left(r\a-\frac{r_p}{\sqrt{2}} \right),
-\label{eq:model_1_apparent_rate_density}
-\end{equation}
-
-The rate density for selected stars (Eq.~\ref{eq:model_1_rate_density}) and the
-apparent rate density (Eq.~\ref{eq:model_1_apparent_rate_density}) differ in 
-that (A) the total number of selected stars, $N_{\rm tot} = N_0+N_1+N_2$, was 
-miscounted; and (B) the inferred radii in binary systems are all $\sqrt{2}$ 
-too small.
-
-To assess the severity of these errors, we need to assume a binary fraction, 
-and to know the true number of planets per single, primary, and secondary star 
-($Z_0,Z_1,$ and $Z_2$).
-For the former,
-\citet{raghavan_survey_2010} found a multiplicity 
-fraction\footnote{
-    The binary fraction is the fraction of systems in a volume-limited sample 
-    that are binary. It is equivalent to the multiplicity fraction if there 
-    are no triple, quadruple, or higher order multiples.
-} of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$. 
-``Twin binaries'' are perhaps 10-20\% of the binaries in a volume-limited 
-sample, depending on how ``twin'' is defined.
-Thus a representative twin binary fraction for this model is ${\rm BF}\approx 
-0.05$-$0.1$. 
-For the latter, taking $Z_0=Z_1=Z_2=1/2$, we plot the resulting occurrence 
-rates as a function of planet radius in Fig.~\ref{fig:occ_rate_model_1}.
-When the $Z_i$'s are equal, the rate density for singles, $\Gamma_0(r)$ 
-(dashed green line), is equal to the rate density for selected stars, 
-$\Gamma_{\rm sel}(r)$ (solid orange line).
-
-\paragraph{Correction to inferred rate density and inferred rate}
-We can define a rate density ``correction factor'', $X_\Gamma$, as the ratio 
-of the apparent to single star rate density,
-\begin{equation}
-X_\Gamma(r) \equiv \left. \frac{\Gamma_a(r\a)}{\Gamma_0(r)} \right|_{r\a 
-\rightarrow r}.
-\end{equation}
-Continuing in the assumption that the number of planets per single, primary, 
-and secondary star are equal, we find a rate density 
-correction factor at the true planet radius of $1/(1+\mu)$.
-This yields a correction of 0.76 if ${\rm BF}=0.1$, and 0.87 if ${\rm 
-BF}=0.05$. Rephrasing the result, if the twin binary fraction were 
-$(2^{3/2}+1)^{-1}\approx 0.26$, then the apparent rate would be half the true 
-rate. Fortunately, in most contexts the twin binary fraction is not that high.
-
-An alternative assumption is that secondaries do not host planets. In that 
-case, $Z_0=Z_1$, and $Z_2=0$. The correction to the rate density at the true 
-planet radius becomes $(1+2\mu)/(1+\mu)^2$.
-This evaluates to 0.94 if ${\rm BF}=0.1$, and 0.98 if ${\rm BF}=0.05$.
-While it seems unlikely that secondaries are planet-less, 
-it is worth noting that $\Gamma_a/\Gamma$ is sensitive to the relative number 
-of planets per single, primary, and secondary.
-
-\paragraph{On completeness}
-Our expressions for the apparent rate density 
-(Eqs.~\ref{eq:defn_apparent_rate_density} 
-and~\ref{eq:model_1_apparent_rate_density}) do not explicitly mention 
-detection efficiency.
-If we were to take a smooth detection probability in S/N, we would need to 
-include an explicit detection efficiency term in 
-Eq.~\ref{eq:defn_apparent_rate_density} to inversely weight for planets 
-that had low probabilities of being detected.
-However, our ``detection probability'' is a step function in S/N 
-(Eq.~\ref{eq:S_N_thresh}).
-In our model, the maximum searchable distance is only a function of the 
-apparent depth and true system luminosity.
-Even though the observers are selecting stars based on what they think are 
-``true radii'' (bottom row of Fig.~\ref{fig:model_1_volumes}), the 
-actual searchability of a point-source is determined by apparent radius and 
-system luminosity (Eq.~\ref{eq:S_N_thresh}; top rows of 
-Fig.~\ref{fig:model_1_volumes}).
-Thus at a given apparent radius $r\a$, the stars (single or binary) that are 
-searchable are exactly the stars that are selected, since dilution affects the 
-apparent radius and the maximum searchable distance in equal and opposite 
-order.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Model \#2: Power law planets}
+\section{More complicated transit survey models}
+\label{sec:more_complicated}
+The following section applies our general equation for the apparent rate 
+density (Eq.~\ref{eq:general_Gamma_a}) to study binarity's effects in more 
+realistic regimes.
+In general, we will write the rate density for each type of star, 
+$\Gamma_i(r)$, as the product of a shape function and a constant:
+\begin{equation}
+\Gamma_i(r) = \frac{{\rm d}\Lambda_i}{{\rm d}r} = Z_i f_i(r),
+\quad {\rm for\ }i\in\{0,1,2\},
+\end{equation}
+where as awlays, $i=0$ corresponds to single stars, $i=1$ to primaries of 
+binaries, and $i=2$ to secondaries of binaries.
+The shape function is normalized to unity.
+The $Z_i$'s are each system type's occurrence rate $\Lambda_i$, integrated 
+over all planetary radii. In other words, they are number of planets per 
+single, primary, or secondary star.
+This section will consider the effects of varying both $f_i(r)$ and also the
+relative values of the $Z_i$'s.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Power law planet radius distributions}
 \label{sec:model_2}
@@
 \subsubsection{Twin binaries}
-Our binary-twin model provides a simple estimate of binarity's systematic 
-effects, but perhaps it is too simple.
 We begin introducing realism by keeping all binaries as twins, but letting the 
@@
 \end{equation}
-for $f(r)$ the radius shape function, $\mathcal{N}_r$ the shape function's 
-normalization, and $Z_i$ the number of planets per star.
-It turns out that in this model, the apparent rate density is quite similar to 
-that written in Eq.~\ref{eq:model_1_apparent_rate_density}, except that the 
-radius dependence and normalization are slightly different:
-\begin{equation}
-\Gamma_a(r_a) = \frac{r_a^\delta}{\mathcal{N}_r} \left[
+for $f(r)$ the radius shape function, and $\mathcal{N}_r$ the shape function's 
+normalization.
+The resulting apparent rate density is quite similar to that of the twin 
+binary, fixed-planet case (Eq.~\ref{eq:model_1_apparent_rate_density}), except 
+that the radius dependence and normalization are slightly different:
+\begin{equation}
+\Gamma\a(r\a) = \frac{r\a^\delta}{\mathcal{N}_r} \left[
 \frac{Z_0}{1+\mu}
@@
 \end{equation}
-The details of this equation come from a more general form derived in the 
-Appendix (Eq.~\ref{eq:general_Gamma_a}).
-
+As in Sec.~\ref{sec:model_1}, $\mu = 2^{3/2} {\rm BF}/(1-{\rm BF})$.
 If the $Z_i$'s are equal, the ``correction factor'' relative to the rate 
-density for singles becomes quite simple:
+density for singles then becomes quite simple:
 \begin{align}
-\left. \frac{\Gamma_a(r_a)}{\Gamma_0(r)} 
-\right|_{r_a\rightarrow r}
+\left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
+\right|_{r\a\rightarrow r}
 &=
@@
 1.004$.
-In other words, the apparent rate density is an {\it over}estimate of the rate 
-density of selected stars, with a relative difference $\delta \Gamma_0 = 
-|\Gamma_0 - \Gamma\a | / \Gamma_0$ of 0.4\%.
-A power law radius distribution $f(r) \propto r^\delta$ diverges for 
-$\delta < 0$. From the work of \citet{howard_planet_2012}, this approximation 
-is applicable for $r\gtrsim 2r_\oplus$.
+In other words, the apparent rate density is an {\it over}estimate compared to 
+the rate density of single stars, with a relative difference $\delta \Gamma_0 
+= |\Gamma_0 - \Gamma\a | / \Gamma_0$ of 0.4\%.
+This is quite a small effect!
+Note though that it could change if the $Z_i$'s are not equal.
+Also, a power law radius distribution $f(r) \propto r^\delta$ diverges for 
+$\delta < 0$; \citet{howard_planet_2012}'s results indicate that this
+approximation is good for $r\a\gtrsim 2r_\oplus$.
+Similarly, it is nonsensical for $f(r)$ to be finite above some upper radius 
+limit $r_u$, perhaps around $\approx 24r_\oplus$, based on the most inflated 
+hot Jupiters.
+An upper cut-off of $r_u$ would lead to smaller values of $\Gamma(r\a)$ 
+down to $r_u/\sqrt{2}$, compared to an intrinsic power law without the cut-off.
+We are not particularly interested in this effect; there are better 
+models for hot Jupiter occurrence rates that we will discuss in 
+Sec.~\ref{sec:further_models}.
+If the assumptions behind this model (listed in 
+Sec.~\ref{sec:general_formula}) are at all applicable in real transit surveys, 
+this suggests that for $2r_\oplus \lesssim r\a \lesssim 17r_\oplus$, 
+binarity's impact on derived occurrence rates is quite small.
 
@@
 $\mathcal{N}_q$ the normalization.
-This changes $\mu$ (Eq.~\ref{eq:mu_general}).
+This changes $\mu$ (Eq.~\ref{eq:mu_general} becomes 
+Eq.~\ref{eq:mu_power_laws}).
 It may also affect the rate density, which could be a function of the stellar 
@@
 X_\Gamma &\equiv \left. \frac{\Gamma\a(r\a,M\a)}{\Gamma_0(r,M)} 
-\right|_{r\a\rightarrow r,\ M\a\rightarrow M,\ Z_i{\rm 's\ equal}} \\
+\right|_{r\a\rightarrow r,\ M\a\rightarrow M} \\
 &=
+\notag
 \frac{1}{1+\mu}
-\left[1 + \frac{1}{\mathcal{N}_q} \frac{{\rm BF}}{1-{\rm BF}}
+\left[1 + \frac{1}{\mathcal{N}_q} \frac{{\rm BF}}{1-{\rm BF}}\times 
 \left(
 \int {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}} +
+\right.
+\right. \\
+&\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
+\left.\left.
 \int {\rm d}q\,q^{\beta+\gamma+\delta+\frac{8}{3}} 
@@
 To summarize, this model suggests that for a power-law radius distribution 
-(applicable for $r\gtrsim 2r_\oplus$), binarity influences apparent planet
-occurrence rates around Sun-like stars at the $\sim$few percent level.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{comment}
-\subsection{Model \#2: fixed planets and primaries, varying secondaries}
-\label{sec:model_2}
-
-Our binary-twin model provides a simple estimate of binarity's systematic 
-effects, but perhaps it is too simple.
-We begin introducing realism by first letting the binary light ratio $L_2/L_1$ 
-vary across the binary population.
-It does so because the underlying mass ratio $q=M_2/M_1$ varies.
-We keep the primary mass fixed as $M_1$, which is also the mass of all single 
-stars.
-
-We parametrize the distribution of binary mass ratios in a volume-limited 
-sample as a power law: $p(q)\propto q^\beta$.
-For binaries with solar-type primaries\footnote{
-    \citet{duchene_stellar_2013}, fitting all the multiple systems of 
-    \citet{raghavan_survey_2010}'s Fig 16, find $\beta = 0.28\pm0.05$ for 
-    $0.7<M_\star/M_\odot<1.3$.
-    Examining only the binary systems of \citeauthor{raghavan_survey_2010}'s 
-    Fig 
-    16, the distribution seems (by eye) to be roughly uniform, $\beta \approx 
-    0$, 
-    except for an excess of twin binaries with $q\approx 1$, and an obvious 
-    lack of $q<0.1$ stellar companions.
-}, $\beta$ is probably between 0 and 0.3.
-We further assume that stars are a one-parameter family, $R \propto M \propto 
-L^{\frac{1}{\alpha}}$, so that a given value of $q$ determines everything 
-about a secondary.
-
-The rate density in this model, $\Gamma(r,q)$, is the sum of the rate 
-densities for each system type:
-\begin{equation}
-\Gamma(r,q)
-=
-\delta(r_p) \times 
-\frac{N_0 Z_0 + N_1 Z_1 + N_2 Z_2 p_2(q)}{N_{\rm tot}}
-\label{eq:model2_rate_density}
-\end{equation}
-where $p_2(q)$ is mass-ratio dependent shape function in secondaries. A fully 
-general approach would parametrize $p_2(q)$ as a power law, $p_2(q) \propto 
-q^\gamma$. For simplicity we will always take $\gamma=0$, the uniform case.
-%We have written $\Gamma$ in terms of the mass ratio instead of the 
-%secondary star's radius for convenience ($q$ and $R_2$ are interchangeable).
-The interpretation of $Z_i$ is still ``the number of planets per star of 
-type $i$'', but now for secondaries this must include a marginalization 
-over both the mass ratio and the planet radius.
-
-The occurrence rate corresponding to Eq.~\ref{eq:model2_rate_density}'s rate 
-density for specific mass ratios of interest $q_{\rm min} < q < q_{\rm 
-    max}$ is then
-\begin{equation}
-\Lambda|_{r_p,q_{\rm min},q_{\rm max}} = 
-\frac{N_0 Z_0 + N_1 Z_1 + N_2 Z_2 f_2}
-{N_{\rm tot}},
-\end{equation}
-for
-\begin{equation}
-f_2 \equiv
-\int_{q_{\rm min}}^{q_{\rm max}} p_2(q) \,{\rm d}q,
-\end{equation}
-where $p_2(q)\propto q^\gamma$, and is normalized to unity.
-
-\paragraph{What do the observers ignoring binarity infer?}
-As a reminder, the binary-ignoring observers compute an apparent rate density 
-by correcting the number of detections per star for the transit probability 
-and the detection efficiency.
-In this process, they make the following errors:
-\begin{enumerate}
-    \item They assume that they have selected $N_0+N_1$ stars, while they have 
-    actually selected $N_0+N_1+N_2$.
-    %
-    \item They assume that every star within the maximum selected distance is 
-    searchable.
-    This is true for single stars.
-    For binaries, the actual detection efficiency is the ratio of the number 
-    of 
-    searchable stars to the number of selected stars.
-    For primaries,
-    \begin{equation}
-    p_{\rm det,1} = \left(\frac{d_{\rm det,1}}{d_{\rm sel}}\right)^3
-    = \mathcal{D}_1^3 = (1+q^\alpha)^{-3},
-    \label{eq:model_2_p_det_1}
-    \end{equation}
-    where we have assumed that all single stars and primaries have the same 
-    properties, and have used $\ell = q^\alpha$.
-    For secondaries,
-    \begin{equation}
-    p_{\rm det,2} = \left(\frac{d_{\rm det,2}}{d_{\rm sel}}\right)^3
-    = \mathcal{D}_2^3 \left(\frac{R_1}{R_2}\right)^6
-    \left(\frac{T_{\rm dur,2}}{T_{\rm dur,1}}\right)^{3/2} 
-    = (1+q^{-\alpha})^{-3} q^{-5},
-    \label{eq:model_2_p_det_2}
-    \end{equation}
-    where subscripts `1' and `2' correspond to primaries and secondaries, and 
-    we 
-    used the scaling relation $T_{\rm dur}\propto \rho_\star^{-1/3} \propto 
-    R_\star^{2/3}$.
-    %
-    \item They assume a transit probability for all stars of $p_{\rm tra} = 
-    R_\star/a$. 
-    For planets orbiting secondaries at fixed period, the true transit 
-    probability 
-    is $q^{2/3} p_{\rm tra}$, since the secondaries have smaller radii and 
-    masses.
-    %
-    \item The true planetary radii $r$ are interpreted as apparent radii $r_a$.
-    In binaries, the apparent radii depend on whether the host is the primary 
-    or 
-    secondary:
-    \begin{align}
-    r_a
-    &=
-    \left.
-    \begin{cases}
-    r_p (1+q^\alpha)^{-1/2} & \text{for } i=1,\ {\rm primary} \\
-    r_p (1+q^{-\alpha})^{-1/2} q^{-1}, & \text{for } i=2,\ {\rm secondary}.
-    \end{cases}
-    \right.
-    \label{eq:model2_ra}
-    \end{align}
-    The factor of $q^{-1}$ for the secondary case accounts for the observer 
-    assuming all transit signals come from stars of fixed size.
-\end{enumerate}
-
-To write the apparent rate density as a function of the apparent 
-radius $r_a$, we marginalize out the planet period, semimajor axis, and 
-stellar radius (or equivalently the mass ratio, for binaries):
-\begin{equation}
-\Gamma_a(r_a) =
-\frac{N_0}{N_0+N_1} Z_0 \delta(r_p)
-+
-\frac{N_1}{N_0+N_1} \left( Z_1 I_1(r_a)
-+
-Z_2 I_2(r_a) \right).
-\label{eq:model2_Gamma_a}
-\end{equation}
-The ratio of primaries to singles, $\mu=N_1/N_0$, is now less than 
-that of Model \#1 (cf. Eq.~\ref{eq:mu_definition}). This is because a 
-distribution of light 
-ratios $\ell$ leads to a distribution of maximum selected distances. 
-Integrating over the mass ratios from $q=0$ to $1$, one finds a
-dimensionless integral
-\begin{equation}
-\mu \equiv \frac{N_1}{N_0} = \frac{\rm BF}{1 - {\rm BF}} \left(2^{3/2} - 
-\int_{1}^{\sqrt{2}} u^2 (u^2 -1)^{1/\alpha} \,{\rm d}u\right).
-\label{eq:mu_model_2}
-\end{equation}
-
-Given a binary fraction, Eq.~\ref{eq:mu_model_2} fully specifies the 
-``weights'' in Eq.~\ref{eq:model2_Gamma_a}.
-The $I_1(r_a)$ and $I_2(r_a)$ terms are found by marginalizing over the joint 
-distribution of apparent radius and mass ratio:
-\begin{align}
-I_i(r_a) &= 
-\int_0^1 p({\rm has\ detected\ planet}, r_a, q | {\rm star\ is\ type\ }i)
-\,{\rm d}q,
-\quad
-{\rm for}\ i\in\{1, 2\}, \\
-&=
-\int_0^1 
-p({\rm has\ detected\ planet} | r_a, q, {\rm star\ is\ type\ }i) 
-\nonumber\\
-&\quad\quad\quad\quad\times p(r_a | q, {\rm star\ is\ type\ }i)
-\,p(q | {\rm star\ is\ type\ }i)
-\,{\rm d}q.
-\end{align}
-The first term is the detection efficiency; the second is a $\delta$-function 
-of the apparent radius; the last is the mass ratio distribution given by 
-Eq.~\ref{eq:Malmquist_bias}.
-An analytic solution can be found for $i=1$.
-For $i=2$ there is no analytic solution, because evaluating the integral 
-requires imposing the constraint that $r_a  = r_p 
-(1+q^{-\alpha})^{-1/2}q^{-1}$. This equation can be re-written
-\begin{equation}
-\left(\frac{r_p}{r_a}\right)^2 = q^2 + q^{-\alpha + 2},
-\end{equation}
-which has no analytic solution for $q(r_a)$ except for special values of 
-$\alpha$, the mass-luminosity exponent.
-For $\alpha=3.5$, our nominal case, semianalytic solutions do exist.
-However, since our main interest is in understanding the qualitative behavior 
-of the solutions, we derive a limiting case, and then proceed 
-numerically.
-
-The analytic solution for $i=1$ is something like
-\begin{equation}
-I_1(r_a) = \frac{1}{\mathcal{N}_1} \left(\frac{r_p}{r_a}\right)^{-3}
-\left( \left(\frac{r_p}{r_a}\right)^2 -1  
-\right)^{\frac{\gamma+\beta}{\alpha}},
-\quad {\rm for}\ r_p/\sqrt{2} < r_a < r_p,
-\end{equation}
-where $\mathcal{N}_1$ is the normalization term of the binary mass ratio 
-distribution (Eq.~\ref{eq:model_2_p_2}): $\mathcal{N}_1 = \int_0^1 
-q^{\gamma+\beta} (1+q^\alpha)^{3/2} {\rm d}q$.
-
-\paragraph{Limiting case of rate density correction}
-Recall that the rate density correction factor, $X_\Gamma$, is the ratio of 
-the apparent to true rate densities.
-We consider a ``nominal model'' in which the stellar population is similar to 
-Sun-like stars in the local neighborhood:
-${\rm BF}=0.44$, $\alpha=3.5$, $\beta=0$.
-Our default assumption is also that the occurrence of planets is independent 
-of stellar mass ($\gamma=0$), so secondaries have the same occurrence rate as 
-primaries and single stars.
-Under these assumptions, the true rate density is
-\begin{equation}
-\Gamma(r) \approx \delta(r_p) \left( Z_0 + Z_1 + 
-Z_2 \right) / 3,
-\label{eq:model2_Gamma_r}
-\end{equation}
-where the coefficients of $1/3$ are accurate to within one percent of the true 
-coefficients.
-Ignoring binarity, the observer finds an apparent rate density
-\begin{equation}
-\Gamma_a(r) = c_0 Z_0 \delta(r_p)
-+c_1 Z_1 I_1(r_a)
-+c_2 Z_2 I_2(r_a),
-\label{eq:model2_Gamma_a_r}
-\end{equation}
-for $c_0\approx 0.49$, and the coefficients $c_1, c_2$ unknown.
-%171011_integrals.nb $c_1\approx 0.32$
-We can evaluate the correction term at $r=r_p$, since $\lim_{r_a\rightarrow 
-    r_p} I_i(r_a)=0$ for $i\in\{1,2\}$:
-\begin{equation}
-X_\Gamma(r=r_p) \approx \frac{3c_0 \Lambda_0}{\Lambda_0+\Lambda_1+\Lambda_2}.
-\end{equation}
-If all the $Z_i$'s are equal, $X_\Gamma(r=r_p)\approx0.49$.
-If there are no planets around the secondaries, $X_\Gamma(r=r_p)\approx0.74$.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_logs_model_2.pdf}
-\caption{
-Inferred planet occurrence rates as a function of planet radius in Model \#2. 
-This model has fixed planets and primaries, and varying secondary masses, 
-radii, and luminosities.
-}
-\label{fig:occ_rate_model_2_log}
-\end{figure}
-
-\paragraph{Numerical approach}
-To maintain simplicity, we develop a Monte Carlo program to simulate our 
-toy transit surveys.
-The program generates a stellar population, assigns planets to the stars, and 
-then calculates which planets are detectable.
-It then computes the apparent and true planet occurrence rates as a function 
-of planet radius.
-We discuss the details below, and refer the interested reader to our online 
-implementation\footnote{\url{https://github.com/lgbouma/binary_biases}}.
-
-First, the user must specify the free parameters that describe the 
-stellar and planetary population. These values include the binary fraction, 
-and the true planet occurrence rates around single stars, primaries, and 
-secondaries (the $Z_i$'s; recall Eq.~\ref{eq:rate_density_shape}).
-There is also an arbitrary absolute number of selected stars.
-
-Once the user specifies the free parameters, the program constructs a 
-population of selected stars.
-Each selected star is assigned a type (single, primary, secondary), a 
-binary mass ratio (if it is not single), and the property of whether it is 
-``searchable''.
-The relative number of binaries to primaries is set by 
-Eq.~\ref{eq:mu_model_2}.
-The mass ratios are drawn from the appropriate magnitude-limited distribution 
-(Eq.~\ref{eq:Malmquist_bias}).
-If it is single, a selected star is assumed to be searchable.
-If it is a primary or secondary, its searchability is determined by a uniform 
-draw from either Eq.~\ref{eq:model_2_p_det_1} or Eq.~\ref{eq:model_2_p_det_2}, 
-as appropriate.
-
-Assigning planets, each selected star receives a planet at the rate $Z_i$, 
-according to its type.
-The radii of planets are assigned independently of any host system property, 
-and can be sampled for an arbitrary distribution ({\it e.g.}, power law; delta 
-function).
-The absolute transit probability, $p_{\rm tra}$ is set arbitrarily, and the 
-probability of a planet transiting a secondary is set as $q^{2/3}\times p_{\rm 
-    tra}$.
-A planet is ``detected'' when a) it transits, and b) its host star is 
-searchable.
-For detected planets, apparent radii are computed according to analytic 
-formulae that account for both dilution and the misclassification of stellar 
-radii (Eq.~\ref{eq:model2_ra}).
-We assume that the observers think that all transits are around single stars.
-
-We then compute rates in bins of true planet radius and apparent planet radius.
-In a given radius bin, the true rate is found by counting the number of planets
-that exist around selected stars of all types (singles, primaries,
-secondaries), and dividing by the total number of these stars.
-The apparent rates are found by counting the number of detected planets that
-were found in an apparent radius bin, dividing by the geometric transit
-probability for single stars, and dividing by the apparent total number of
-stars.
-
-\paragraph{Numerical results for Model \#2}
-We first validate our model by ensuring it produces the analytically-predicted 
-results for Model \#1, and the limiting case of Model \#2 described above.
-Following validation, we assume ${\rm BF}=0.44$, $\alpha=3.5$, 
-$\beta=\gamma=0$, and take $Z_0=Z_1=Z_2=0.5$. We then compute the true and 
-apparent occurrence rates over bins in planet radius.
-The results are shown in Fig.~\ref{fig:occ_rate_model_2}.
-Evidently, dilution produces a spectrum of apparent planetary radii. This 
-leads to overestimated rates everywhere except where at the true planet 
-radius, where the rate is underestimated by a factor of two.
-Compared to Model \#1 (Fig.~\ref{fig:occ_rate_model_1}), the general picture 
-is that the apparent radius distribution is ``blurred'' by the varying 
-secondary light ratios.
-
-\end{comment}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Model \#3: Fixed primaries, broken power-law planets and 
-secondaries}
+($2r_\oplus \lesssim r\a \lesssim 17r_\oplus$) in which there are the same 
+number of planets orbiting singles, primaries, and secondaries, binarity 
+influences apparent planet occurrence rates around Sun-like stars at the 
+$\sim$few percent level.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Fixed primaries, varying secondaries, broken power-law planets}
 \label{sec:model_3}
@@
         {\it Left:} rate density and {\it right:} rate (over $0.5r_\oplus$ 
-        bins) as a function of planet radius in Model \#3. This model has 
-        fixed primaries 
-        and 
-        single stars, but varying secondaries. The true planet radius 
-        distribution is 
-        a power law with exponent $-2.92$ above $2r_\oplus$, below which it is 
-        uniform 
-        \citep[similar to][]{howard_planet_2012}. We use an arbitrary 
-        normalization of 
-        $Z_0=0.5$ throughout.}
+        bins) as a function of planet radius for the distribution specified by 
+        Eq.~\ref{eq:model3_radius_distribution}. This model has identical 
+        primaries and single stars, and varying secondaries. We use an 
+        arbitrary normalization of $Z_0=0.5$ throughout.}
     \label{fig:occ_rate_model_3_log}
@@
 
-%TODO: FIGURE OUT WHAT TO DO WITH THESE
-\begin{comment}
-\begin{figure}[!tb]
-\centering
-\includegraphics[width=.6\textwidth]{figures/HJ_correction_inputrate_vs_HJratevalues.pdf}
-\caption{
-$Z_i$ is the occurrence rate integrated over all possible phase 
-space for the $i^{\rm th}$ system type. $Z_2/Z_0=1$ 
-corresponds to an equal number of planets per secondary as per single 
-star;
-$Z_2/Z_0=0$ corresponds to secondaries not having any 
-planets.
-In our Model \#3, though the true HJ occurrence rate 
-is highly dependent on $Z_2$, 
-the inferred rate hardly depends on whether secondaries have HJs.
-This means that the ``correction factor'' between the inferred rate 
-and the true rate around single stars is underestimated by a 
-multiplicative 
-factor of $\approx1.3$, independent of the HJ rate around secondaries.
-The ``HJ rate'' is the summed rate from     
-Fig.~\ref{fig:occ_rate_model_3_log} above $8r_\oplus$.
-}
-\label{fig:HJ_correction_inputrate_vs_HJratevalues}
-\end{figure}
-
-\begin{figure}[!tb]
-\centering
-\includegraphics[width=.6\textwidth]{figures/earth_inputrate_vs_etaearthratevalues.pdf}
-\caption{
-Same as Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues}, but 
-for Earth-sized planets.
-The absolute values given on the $y$-axis found by summing the rate 
-from Fig.~\ref{fig:occ_rate_model_3_log} for planetary radii from 
-$0.5$ to $1.5r_\oplus$ (this is a toy model, and they do not reflect 
-an actual determination of $\eta_\oplus$).
-The relative values show that the inferred rate for Earths is roughly 
-independent of the occurrence rate (integrated over all radii) around 
-secondaries.
-However, it is systematically lower than the true rate around single 
-and primary stars, by $\approx 20\%$.
-}
-\label{fig:earth_inputrate_vs_etaearthratevalues}
-\end{figure}
-\end{comment}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
         (Eq.~\ref{eq:model4_radius_distribution}).
-        Similar to Model \#3, this model has fixed primaries and single stars, 
-        but varying secondaries.
+        Similar to Fig.~\protect\ref{fig:occ_rate_model_3_log}, this model has 
+        fixed primaries and single stars, but varying secondaries.
     }
@@
 The first-order correction that we suggest, given the impracticality of 
-performing high-resolution imaging of every selected star in a transit survey,
-is to model the detection pipeline's efficiency while accounting for 
+performing high-resolution imaging of every star searched by a transit 
+survey, is to model the detection pipeline's efficiency while accounting for 
 binarity.
@@
 statistics are then included in a model of the pipeline's detection 
-efficiency, and the number of selected stars is appropriately counted, it 
-would correct many of binarity's biases.
+efficiency, and the number of searchable stars is appropriately counted (at a 
+given $\delta_{\rm obs}$), it would correct many of binarity's biases.
 
@@
 (\citealt{burke_terrestrial_2015}'s Fig.~17).
-In our Model \#3, the inferred rate can be up to 50\% higher than the true 
-rate around single stars.
+In the power law model of Sec.~\ref{sec:model_3}, the inferred rate can be up 
+to 50\% higher than the true rate around single stars.
 Though this bias seems large, it is currently small compared to the other 
@@
 The former value agrees with that measured by \citet{dong_metallicities_2014}.
-Based on their measurements, \citeauthor{guo_metallicity_2017}\! 
-then argued that the metallicity difference could account for a $\approx 20\%$ 
-relative difference in the measured rates between the CKS and {\it Kepler}\ 
-samples~--~not a factor of two.
+Refitting for the metallicity exponent in $\Lambda_{\rm HJ} \propto 10^{\beta 
+[{\rm M/H}] }$, \citeauthor{guo_metallicity_2017}\! found $\beta = 2.1\pm 
+0.7$, and noted that this would imply that the metallicity difference could 
+account for a $\approx 20\%$ relative difference in the measured rates between 
+the CKS and {\it Kepler}\ samples~--~not a factor of two\footnote{
+\citet{petigura_CKS_2017} recently found $\beta = 3.4^{0.9}_{-0.8}$.
+This gives an $\approx 25\%$ relative difference, indicating metallicity could 
+account for at least half of the ``hot Jupiter rate discrepancy''.
+}.
 \citeauthor{guo_metallicity_2017}\! concluded that ``other factors, such as 
@@
 and that no secondaries host HJs).
-We later pointed out in Sec.~\ref{sec:further_models} that this power-law 
-radius distribution is probably unrealistic. If we instead assumed a 
-Gaussian radius distribution~\citep[e.g.,][]{petigura_CKS_2017}, apparent HJ 
-rates are actually {\it greater} 
+We later pointed out in Sec.~\ref{sec:further_models} that assuming a 
+power-law radius distribution is probably wrong if one wishes to study the HJ 
+rate discrepancy. If we instead assumed a 
+Gaussian radius distribution~\citep[following][]{petigura_CKS_2017}, apparent 
+HJ rates are actually {\it greater} 
 than the true rate around singles.
-
+\begin{comment}
 If we believe the assumed power-law radius distribution, we can ask whether 
@@
 assumes a power-law radius distribution.
-Assuming a Gaussian similar to that reported by~\citet{petigura_CKS_2017},
-we find that binarity is unlikely to resolve the HJ rate discrepancy.
+\end{comment}
+This means that assuming a Gaussian similar to that reported 
+by~\citet{petigura_CKS_2017}, binarity is unlikely to resolve the HJ rate 
+discrepancy.
 Of course, such calculations can be at most suggestive~--~a true resolution 
@@
 For instance, if hot Jupiters are less likely to be confirmed in binary 
-systems, this might further bias the rates low.
+systems, this might bias the rates low.
 
@@
 
+\paragraph{On completeness}
+{\bf TODO THIS SECTION}
+This is if some fraction of stars you thought were searchable are not. There 
+are no such stars.
+
+Our expressions for the apparent rate density 
+(Eqs.~\ref{eq:defn_apparent_rate_density} 
+and~\ref{eq:model_1_apparent_rate_density}) do not explicitly mention 
+detection efficiency.
+If we were to take a smooth detection probability in S/N, we would need to 
+include an explicit detection efficiency term in 
+Eq.~\ref{eq:defn_apparent_rate_density} to inversely weight for planets 
+that had low probabilities of being detected.
+However, our ``detection probability'' is a step function in S/N 
+(Eq.~\ref{eq:S_N_thresh}).
+In our model, the maximum searchable distance is only a function of the 
+apparent depth and true system luminosity.
+Even though the observers are selecting stars based on what they think are 
+``true radii'' (bottom row of Fig.~\ref{fig:model_1_volumes}), the 
+actual searchability of a point-source is determined by apparent radius and 
+system luminosity (Eq.~\ref{eq:S_N_thresh}; top rows of 
+Fig.~\ref{fig:model_1_volumes}).
+Thus at a given apparent radius $r\a$, the stars (single or binary) that are 
+searchable are exactly the stars that are SEARCHED, since dilution affects the 
+apparent radius and the maximum searchable distance in equal and opposite 
+order.
+
 \paragraph{Utility in future occurrence rate measurements}
@@
 rates measured by transit surveys.
-The simplest of these models (Model \#1) provided an order-of-magnitude 
-estimate of how much binarity might affect occurrence rates.
-The most realistic of these models (Model \#3) suggests that binarity leads to 
-overestimates in transit survey occurrence rates at planetary radii 
-$<2r_\oplus$, with at most $\approx 50\%$ relative error.
+The simplest of these models (Sec.~\ref{sec:simplest}) provided an 
+order-of-magnitude estimate for how much binarity might affect occurrence 
+rates: by no more than $\sim$factors of two.
+
+We then gave a general formula for the apparent rate density inferred by an 
+observer ignoring binarity (Eq.~\ref{eq:general_Gamma_a}).
+As input, this equations requires a volume-limited mass ratio distribution 
+$f(q)$, and also the true rate densities for planets around singles, 
+primaries, and secondaries.
+The assumptions that make the model tractable are:
+\begin{enumerate}
+    \item the transit survey is S/N limited;
+    \item all the primaries and single stars have identical properties;
+    \item the properties of the secondaries can vary, but there are known 
+    functions $L(M)$ and $R(M)$ that specify a star's luminosity and radius in 
+    terms of its mass;
+    \item the binarity-ignoring observers assume that binaries have the same 
+    properties as the primaries.
+\end{enumerate}
+
+Allowing for these conditions, many results follow:
+\begin{itemize}
+%
+\item Assuming a power-law planet radius distribution, and that the same 
+number of planets orbit singles, primaries, and secondaries, binarity 
+influences apparent planet occurrence rates around Sun-like stars at the 
+$\sim$few percent level from radii $2r_\oplus \lesssim r\a \lesssim 
+17r_\oplus$ (Sec.~\ref{sec:model_2}).
+%
+\item Assuming a broken-power law planet radius distribution, with 
+\citet{howard_planet_2012}'s exponent at $r > 2r_\oplus$ and a constant 
+occurrence at $r < 2r_\oplus$, there is a ``bump'' in the apparent rate 
+density at $r\a < 2r_\oplus$, leading to a relative error $\delta \Gamma_0 = 
+|\Gamma_0 - \Gamma\a|/\Gamma_0$ of at most $\approx 50\%$ 
+(Fig.~\ref{fig:occ_rate_model_3_log}).
 Although this is smaller than current systematic uncertainties on the 
@@
 eventually become an important component of the $\eta_\oplus$ error budget.
-Further, we showed that assuming a power-law radius distribution, 
-then hot Jupiter rates measured by transit surveys could be biased to infer 
-$\approx 1.13\times$ fewer hot Jupiters per star than surveys that only 
-measure occurrence rates about single stars ({\it i.e..,} radial velocity 
-surveys). However, assuming a more realistic Gaussian radius distribution 
-indicates that the effects of binarity on measured hot Jupiter rates are 
-either negligible, or else lead to {\it over}estimated rates.
-The overall result is that our models do not suggest that binarity can 
-resolve the HJ rate discrepancy.
-Finally, we also pointed out that binarity can substantially ``fill in'' 
-gaps in the apparent radius distribution (Fig.~\ref{fig:model_4}).
+%
+\item Binarity ``fills in'' gaps in the radius distribution 
+(Fig.~\ref{fig:model_4}), by an amount that could affect precise measurements 
+of the depth, width, and slope of \citet{fulton_california-_2017}'s radius 
+gap, in the event that planets are not carefully vetted with high resolution 
+imaging.
 This will likely become an important consideration for precise measurements of 
-the depth, width, and slope of \citet{fulton_california-_2017}'s radius gap.
+the depth, width, and slope of .
+%
+\item Binarity does not lead to smaller apparent HJ occurrence rates 
+(Fig.~\ref{fig:gaussian_HJ}).
+This assumes a Gaussian planet radius distribution, similar to that reported 
+by~\citet{petigura_CKS_2017}.
+\end{itemize}
+
+All of these results should be understood as only being strictly applicable 
+when the assumptions listed above are met.
+Otherwise, they are only suggestive.
+{\bf TODO: finish}
 
@@
 
+\newpage
 \appendix
-\section{Apparent occurrence rate~---~general formula}
+\section{Derivation of general formula for apparent occurrence rate}
+\label{sec:appendix}
 Recall our definition of apparent rate density 
@@
 &=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^0(r\a, M\a; r, M)
-\cdot\Gamma^0(r, M) \cdot p_{\rm tra}(M)\\
-&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot\Gamma^0(r\a, M\a) \cdot p_{\rm 
+\cdot\Gamma_0(r, M) \cdot p_{\rm tra}(M)\\
+&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot\Gamma_0(r\a, M\a) \cdot p_{\rm 
     tra}(M\a),
@@
 &=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^1(r\a, M\a; r, M)
-\cdot\Gamma^1(r, M) \cdot p_{\rm tra}(M)\\
+\cdot\Gamma_1(r, M) \cdot p_{\rm tra}(M)\\
 &=N\s^0(\delta_{\rm obs}, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
 {\mathrm{BF}\over{1-\mathrm{BF}}} \int {\mathrm{d}q \over 
-    \mathcal{A}^4}\,f(q)\,\Gamma^1\left({r_a\over\mathcal{A}}, M\a\right),
+    \mathcal{A}^4}\,f(q)\,\Gamma_1\left({r_a\over\mathcal{A}}, M\a\right),
 \end{align}
@@
 &=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^2(r\a, M\a; r, M)
-\cdot\Gamma^2(r, M) \cdot p_{\rm tra}(M)\\
+\cdot\Gamma_2(r, M) \cdot p_{\rm tra}(M)\\
 &=
@@
 \int {q \mathrm{d}q \over 
-{\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma^2(r_a/\mathcal{B}, 
+{\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma_2(r_a/\mathcal{B}, 
 qM\a)\,p_{\rm 
@@
 
-\begin{empheq}[box=\widefbox]{align}
+\begin{align}
 \notag
 \Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
-\left\{ \Gamma^0(r\a, M\a)+ 
+\left\{ \Gamma_0(r\a, M\a)+ 
 \frac{{\rm BF}}{1 - {\rm BF}}
-\left[ \int {\mathrm{d}q \over \mathcal{A}^4}\,f(q)\,\Gamma^1\left({r\a\over 
+\left[ \int {\mathrm{d}q \over \mathcal{A}^4}\,f(q)\,\Gamma_1\left({r\a\over 
     \mathcal{A}}, 
@@
 +\int {q \mathrm{d}q \over 
-    {\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma^2\left({r\a\over 
+    {\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma_2\left({r\a\over 
     \mathcal{B}}, 
@@
 q^{-1/3} \right]	\right\}.
-\label{eq:general_Gamma_a}
-\end{empheq}
+\end{align}
 This equation is used to derive Eqs.~\ref{eq:model5_apparent_rate_density} 

### 2017-12-19 src/get_accurate_mu.py

@@ -1,14 +1,24 @@
+from __future__ import division
 import numpy as np
 from scipy.integrate import trapz
 
 α = 3.5
 β = 0
 
-q = np.arange(0,1+1e-8,1e-8)
+#q = np.arange(0,1+1e-8,1e-8)
+q = np.arange(0,1+1e-7,1e-7)
 
 # 2**(3/2) + 3I = this
-this = trapz( (1 + q**α)**(3/2), q )
+this = trapz( q**β * (1 + q**α)**(3/2), q )
 
 I = (this - 2**(3/2))/3
 
 print(-I)
+
+BF = 0.1
+mu = BF/(1-BF) * this
+print(mu)
+
+δ = -2.92
+print( 2**((δ+3)/2) )
+print( (1 + 2**((δ+3)/2) * mu)/(1 + mu))

### 2017-12-19 src/integrate_for_apparent_rate_density.py
save ndet_a from integrator

@@ -1,21 +1,39 @@
 '''
-We wrote a general equation for the apparent rate density, as a function of the
-apparent planet radius r_a and apparent mass M_a.
+----------
+usage: integrate_for_apparent_rate_density.py [-h] [-mn MODELNUMBER]
+	[-ztwo ZSUBTWO] [-bf BINARYFRAC] [-rpu UPPERRADIUSCUTOFF] [-sr]
 
-Here, we evaluate it for particular "true" (volume-limited) occurrence rate
-densities.
+Integrate the general equation for apparent rate density.
+
+optional arguments:
+  -h, --help            show this help message and exit
+
+  -mn MODELNUMBER, --modelnumber MODELNUMBER
+                        1 through 7.
+
+  -ztwo ZSUBTWO, --ZsubTwo ZSUBTWO
+                        integrated occ rate for secondaries
+
+  -bf BINARYFRAC, --binaryfrac BINARYFRAC
+                        BF = n_b/(n_s+n_b), for n number density
+
+  -rpu UPPERRADIUSCUTOFF, --upperradiuscutoff UPPERRADIUSCUTOFF
+                        the maximum allowed planet radius in units of Rearth
+
+  -sr, --slowrun        use --slowrun if you want models to run high-resoln
+                        models.
+----------
 
 The models are as follows:
 /Model #1: twin binary, same planet
-
 XModel #2: varying q, same planet (WARNING: not implemented)
-
 /Model #3: varying q, powerlaw+const r
 /Model #4: varying q, r with a gap
 /Model #5: twin binary, powerlaw r
 /Model #6: varying q, powerlaw r
 /Model #7: varying q, r ~ gaussian(14re, 2re)
 
+----------
 Example usage, for each model type:
 >>> python integrate_for_apparent_rate_density.py --modelnumber 1 --ZsubTwo 0.5 --binaryfrac 0.1 --upperradiuscutoff 1
 >>> python integrate_for_apparent_rate_density.py --modelnumber 2 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
@@ -24,7 +42,6 @@ Example usage, for each model type:
[…]

### 2017-12-19 src/plot_integrated_occrates_vs_radius.py
fix figure labels for paper

@@ -93,10 +93,11 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
     colors = ['#1f77b4', '#ff7f0e', '#2ca02c', '#d62728']
     c = ['#4ca8e8', '#85c5f2'] # shades of blue for vs function of Z_2
 
+    lambdastr = r'$\Lambda_{\mathrm{a}}(r_{\mathrm{a}})$'
     if not many_Zs:
-        ax.step(xvals, yinferred, label='inferred', c=colors[0], where='post')
+        ax.step(xvals, yinferred, label=lambdastr, c=colors[0], where='post')
     else:
-        ax.step(xvals, yinferred, label='inferred, $Z_2/Z_0$={:.1f}'.format(
+        ax.step(xvals, yinferred, label=lambdastr+', $Z_2/Z_0$={:.1f}'.format(
             Z_2/Z_0), c=colors[0], where='post')
 
     if many_Zs:
@@ -126,12 +127,12 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
             c = ['#4ca8e8', '#85c5f2'] # shades of blue for vs function of Z_2
             ls = ['--', ':'] # shades of blue for vs function of Z_2
 
-            ax.step(xvals, yinferred, label='inferred, $Z_2/Z_0$={:.1f}'.format(
+            ax.step(xvals, yinferred, label=lambdastr+', $Z_2/Z_0$={:.1f}'.format(
             Z_2/Z_0), c=c[ind], linestyle=ls[ind], where='post')
 
     if standardlines:
 
-        ax.step(xvals, ytruesingle, where='post', label='true (singles)',
+        ax.step(xvals, ytruesingle, where='post', label='$\Lambda_0(r)$',
                 linestyle='-', c=colors[1])
 
     if brokenx:
@@ -143,9 +144,9 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
             ax.legend(loc='upper left',fontsize='small')
 
 
-    ax.set_xlabel('planet radius, $r$ [$r_\oplus$]', fontsize='large')
+    ax.set_xlabel('planet radius [$r_\oplus$]', fontsize='large')
 
-    ax.set_ylabel('number of planets per star, $\Lambda$', fontsize='large')
+    ax.set_ylabel('number of planets per star', fontsize='large')
 
     if logx:
         ax.set_xscale('log')

### 2017-12-19 src/plot_integrated_rate_densities_vs_radius.py

@@ -74,10 +74,11 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
     colors = ['#1f77b4', '#ff7f0e', '#2ca02c', '#d62728']
     c = ['#4ca8e8', '#85c5f2'] # shades of blue for vs function of Z_2
 
+    gammastr = r'$\Gamma_{\mathrm{a}}(r_{\mathrm{a}})$'
     if not many_Zs:
-        ax.plot(xvals, yinferred, label='inferred', c=colors[0])
+        ax.plot(xvals, yinferred, label=gammastr, c=colors[0])
     else:
-        ax.plot(xvals, yinferred, label='inferred, $Z_2/Z_0$={:.1f}'.format(
+        ax.plot(xvals, yinferred, label=gammastr+', $Z_2/Z_0$={:.1f}'.format(
             Z_2/Z_0), c=colors[0])
 
     if many_Zs:
@@ -93,13 +94,13 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
             c = ['#4ca8e8', '#85c5f2'] # shades of blue for vs function of Z_2
             ls = ['--', ':'] # shades of blue for vs function of Z_2
 
-            ax.plot(xvals, yinferred, label='inferred, $Z_2/Z_0$={:.1f}'.format(
+            ax.plot(xvals, yinferred, label=gammastr+', $Z_2/Z_0$={:.1f}'.format(
             Z_2/Z_0), c=c[ind], linestyle=ls[ind])
 
 
     if standardlines:
 
-        ax.plot(xsingle, ytruesingle, label='true (singles)', linestyle='-',
+        ax.plot(xsingle, ytruesingle, label='$\Gamma_0(r)$', linestyle='-',
                 c=colors[1])
 
     if model_number != 7:
@@ -107,9 +108,9 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
     else:
         ax.legend(loc='upper left',fontsize='small')
 
-    ax.set_xlabel('planet radius, $r$ [$r_\oplus$]', fontsize='large')
+    ax.set_xlabel('planet radius [$r_\oplus$]', fontsize='large')
 
-    ax.set_ylabel('rate density, $\Gamma$ [$r_\oplus^{-1}$]', fontsize='large')
+    ax.set_ylabel('rate density [$r_\oplus^{-1}$]', fontsize='large')
 
     if logx:
         ax.set_xscale('log')

### 2017-12-19 src/plot_occrates_vs_radius.py

@@ -1,4 +1,6 @@
 '''
+This script plots the output of the Monte Carlo simulation.
+
 first, for models 1,2,3,4:
 >>> python numerical_models.py
 then:
@@ -82,15 +84,16 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
 
     colors = ['#1f77b4', '#ff7f0e', '#2ca02c', '#d62728']
 
-    ax.step(xvals, yinferred, where='post', label='inferred', c=colors[0])
+    lambdastr = r'$\Lambda_{\mathrm{a}}(r_{\mathrm{a}})$'
+    ax.step(xvals, yinferred, where='post', label=lambdastr, c=colors[0])
 
     if standardlines:
 
-        ax.step(xvals, ytrueselected, where='post', label='true (selected)',
-                c=colors[1])
+        #ax.step(xvals, ytrueselected, where='post', label='true (selected)',
+        #        c=colors[1])
 
-        ax.step(xvals, ytruesingle, where='post', label='true (single)',
-                linestyle='--', c=colors[2])
+        ax.step(xvals, ytruesingle, where='post', label='$\Lambda_0(r)$',
+                linestyle='-', c=colors[1])
 
     elif not standardlines:
 
@@ -112,9 +115,9 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
     else:
         ax.legend(loc='best',fontsize='medium')
 
-    ax.set_xlabel('planet radius, $r$ [$r_\oplus$]', fontsize='large')
+    ax.set_xlabel('planet radius [$r_\oplus$]', fontsize='large')
 
-    ax.set_ylabel('number of planets per star, $\Lambda$', fontsize='large')
+    ax.set_ylabel('number of planets per star', fontsize='large')
 
     if logx:
         ax.set_xscale('log')

### 2017-12-19 src/plot_ndet_apparent_vs_radius.py
add plotting script for n_det output

@@ -1,0 +1,276 @@
+# -*- coding: utf-8 -*-
+from __future__ import division, print_function
+import matplotlib as mpl
+mpl.use('pgf')
+pgf_with_custom_preamble = {
+    'pgf.texsystem': 'pdflatex', # xelatex is default; i don't have it
+    'font.family': 'serif', # use serif/main font for text elements
+    'text.usetex': True,    # use inline math for ticks
+    'pgf.rcfonts': False,   # don't setup fonts from rc parameters
+    'pgf.preamble': [
+        '\\usepackage{amsmath}',
+        '\\usepackage{amssymb}'
+        ]
+    }
+mpl.rcParams.update(pgf_with_custom_preamble)
+
+import matplotlib.pyplot as plt, pandas as pd, numpy as np
+from scipy.integrate import trapz
+
+from brokenaxes import brokenaxes
+
+def make_plot(model_number, logx=None, logy=None, withtext=None,
+        stdout=False, brokenx=None, Z_2=None, xcut=None, r_pu=None,
+        standardlines=True, many_Zs=False):
+    '''
+    withtext: includes summary text from integration on plot
+
+    stdout: write "withtext" text to stdout
+
+    xcut: mainly for model #1, overplotted over different axes
+
+    standardlines:
+        mainly for filenaming
+    '''
+
+    assert Z_2 > -1
+    Z_0 = 0.5
+
+    plt.close('all')
+
+    if not brokenx:
+        f, ax = plt.subplots(figsize=(4,4))
+    elif many_Zs:
+        f, ax = plt.subplots(figsize=(5,4))
+    else:
+        #cf https://github.com/bendichter/brokenaxes/blob/master/brokenaxes.py
+        f = plt.figure(figsize=(4,4))
+        bigax = brokenaxes(
+                xlims=((0.695, .715), (.985, 1.005)),
+                d=0.02,
+                tilt=85,
+                hspace=.05,
+                despine=True)
+        ax=bigax
+
+    # Make summary plot
+    fname = '../data/numerics/integrate_model_{:d}_Zsub2_{:.2f}_rpu_{:.2f}.out'.format(
+            model_number, Z_2, r_pu)
+
+    df = pd.read_csv(fname)
+
+    if model_number in [1,2]:
[…]

### 2017-12-20 src/plot_KOI_radii.py
check confirmed KOI radii

@@ -1,0 +1,10 @@
+import pandas as pd, numpy as np
+import matplotlib.pyplot as plt
+
+#from NASA exoplanet archive, only KOIs with "CONFIRMED" designation
+df = pd.read_csv('../data/confirmed_KOI_radii.csv', comment='#')
+
+plt.hist(np.log10(df['koi_prad']), bins=20)
+plt.savefig('../results/KOI_radii_log.pdf', bbox_inches='tight')
+
+print(len(df[df['koi_prad']>2])/len(df))

### 2017-12-20 paper/main.tex
update paper text and figures

@@
 Particular attention is paid to dilution of observed planet radii, errors in 
-star counts, and detection efficiencies.
-Free parameters in our models include the true radius distribution of planets, 
-and the relative numbers of planets orbiting secondaries, primaries, and 
-single stars.
-In the simplest possible case, all stellar systems are either single or twin 
-binaries, and all planets are identical. If so, then we find that ignoring 
-binarity leads to an underestimate of the occurrence at the true radius by a 
-multiplicative factor of $0.76$ (assuming a 10\% twin binary fraction).
-Using more realistic models for the stellar population and planetary 
-radii, we find that the occurrence of Earth-sized planets can be overestimated 
-by at most $\approx 50\%$ when ignoring binarity~--~at present far smaller 
-than systematic uncertainties on real $\eta_\oplus$ measurements.
-We quantify how gaps in the intrinsic planet radius distribution are filled 
-in when binarity is neglected.
-Our models suggest that for most of the observed radius distribution 
-($r>2r_\oplus$), ignoring binarity only leads to errors in inferred occurrence 
-rates at the $\lesssim 10\%$ level.
-One corollary is that binarity is unlikely to strongly influence the HJ rate 
-discrepancy.
+star counts, and treatment of detection efficiencies.
+Given a somewhat restrictive set of assumptions, we derive a general formula 
+for the apparent rate density, for which the free parameters include the true 
+radius distribution of planets, and also the relative numbers of planets 
+orbiting secondaries, primaries, and single stars.
+From this formalism, we suggest that for most of the observed radius 
+distribution (apparent planet radii $>2r_\oplus$), ignoring binarity only 
+leads to errors in inferred occurrence rates at the $\lesssim 10\%$ level.
+One corollary is that binarity seems unlikely to strongly influence the HJ 
+rate discrepancy.
+The errors created by ignoring binarity at smaller apparent radii might be 
+larger: for instance, the absolute occurrence of Earth-sized planets could be 
+overestimated by up to $\approx 50\%$.
+A final point is that our formalism provides a quantitative argument for why
+whenever high-resolution imaging follow-up discovers stellar neighbors of 
+detected planets, the planet is more likely to orbit primary. 
 %
@@
         If the true planet radius is $r\p$, all planets detected in binaries 
-        will have apparent radii $r\a = r\p/\sqrt{2}$.
+        will have apparent radii $r\a = r\p/\sqrt{2}$ (see 
+        Eq.~\ref{eq:model_1_apparent_rate_density}).
+        The rate and rate density are related by $\Lambda|_a^b = 
+        \int_{a}^{b}\Gamma\,{\rm d}r$.
     }
@@
 
-To generalize the procedure of Sec.~\ref{sec:simplest}, we consider a S/N 
+To generalize the procedure of Sec.~\ref{sec:simplest}, we consider a SNR 
 limited transit survey in which all the primaries and single stars have 
@@
 
-\begin{figure}[!tb]
+\begin{figure}[!t]
     \centering
@@
 
+\paragraph{Fraction of detected planets from a given source}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/ndet_vs_radius_logx_model_3_fraclines_rpu_22.5_manyZs.pdf}
+    \caption{
+        Fraction of detected planet at a given apparent planet radius coming 
+        from singles (solid lines), primaries (dashed lines), and secondaries 
+        (dotted lines).
+        Three different values for $Z_2/Z_0$ are selected: $1$ (blue), $0.5$ 
+        (orange), $0$ (green).
+        The assumed true planet radius distribution is a broken power-law
+        (Eq.~\ref{eq:model3_radius_distribution}; same as 
+        Fig.~\ref{fig:occ_rate_model_3_log}).
+    }
+    \label{fig:frac_model_3}
+\end{figure}
+
+It would be nice to get some intuition for how much the secondaries matter.
+From Fig.~\ref{fig:model_1_volumes}, we have the intuition that for a given 
+true planet radius, secondaries have a much smaller searchable volume than 
+primaries or singles.
+Does this necessarily imply that if we are given a detected planet with some 
+apparent radius $r\a$, which is then observed by high-resolution imaging to 
+exist in a binary, that the planet probably orbits the primary?
+
+We explore this quantitatively in Fig.~\ref{fig:frac_model_3}.
+The lines in this figure are computed using the expressions given in the 
+appendix for the number of detections coming from singles, primaries, and 
+secondaries (Eqs.~\ref{eq:n_det_0},~\ref{eq:n_det_1}, and~\ref{eq:n_det_2}).
+In the scenario that high-resolution imaging finds a system with $r\a > 
+2r_\oplus$ in a binary, of order $\sim 3\times$ more detected planets orbit 
+primaries than secondaries, for the $Z_2/Z_0=1$ case.
+For the $Z_2/Z_0=0.5$ case, of order $\sim 7\times$ more detected planet 
+planets orbit primaries than secondaries.
+At $r\a < 2r_\oplus$, the ratios are $\sim 1.6 \times$ and $\sim 3.1 \times$ 
+as many detected planets orbiting primaries than secondaries for the same 
+$Z_2/Z_0$ values.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \paragraph{Precise features of the radius valley}
-
-\begin{figure}[!tb]
-    \centering
-    \epsscale{1.15}
-    \plottwo{figures/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf}
-    \caption{
-        {\it Left:} rate density and {\it right:} rate (over $0.25r_\oplus$ 
-        bins) as a function of planet radius in a model with a radius gap 
-        (Eq.~\ref{eq:model4_radius_distribution}).
-        Similar to Fig.~\protect\ref{fig:occ_rate_model_3_log}, this model has 
-        fixed primaries and single stars, but varying secondaries.
-    }
-    \label{fig:model_4}
-\end{figure}
 
@@
 
+\begin{figure}[!t]
+    \centering
+    \epsscale{1.15}
+    \plottwo{figures/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf}
+    \caption{
+        {\it Left:} rate density and {\it right:} rate (over $0.25r_\oplus$ 
+        bins) as a function of planet radius in a model with a radius gap 
+        (Eq.~\ref{eq:model4_radius_distribution}).
+        Similar to Fig.~\protect\ref{fig:occ_rate_model_3_log}, this model has 
+        fixed primaries and single stars, but varying secondaries.
+    }
+    \label{fig:model_4}
+\end{figure}
+
 \paragraph{Alternative models for the HJ distribution}
-
-\begin{figure}[!tb]
-    \centering
-    \includegraphics[width=.6\textwidth]{figures/int_rate_density_vs_radius_model_7_rpu_22.5_manyZs.pdf}
-    \caption{
-        Rate density for a population of planets with true radii $r$ drawn from
-        $\mathcal{N}(14r_\oplus,2r_\oplus)$.
-        This is similar to the hot Jupiter distribution presented 
-        by~\citet{petigura_CKS_2017}.
-    }
-    \label{fig:gaussian_HJ}
-\end{figure}
 
@@
 
+\begin{figure}[!tb]
+    \centering
+    \includegraphics[width=.6\textwidth]{figures/int_rate_density_vs_radius_model_7_rpu_22.5_manyZs.pdf}
+    \caption{
+        Rate density for a population of planets with true radii $r$ drawn from
+        $\mathcal{N}(14r_\oplus,2r_\oplus)$.
+        This is similar to the hot Jupiter distribution presented 
+        by~\citet{petigura_CKS_2017}.
+    }
+    \label{fig:gaussian_HJ}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 This study has shown that under a reasonable set of simplifying assumptions, 
-binarity can introduce systematic errors to star and planet counts in transit 
-surveys, which then bias derived occurrence rates.
+ignoring binarity introduces systematic errors to star and planet counts in 
+transit surveys, which then bias derived occurrence rates.
 Thus far, real-world occurrence rate calculations\footnote{
@@
 While we do not resolve the problem, we do suggest the approximate scale of 
-the necessary corrections in a survey-independent manner.
+the possible errors in a survey-independent manner.
 
@@
 interpretation of planet candidates. High resolution imaging 
-campaigns have measured the multiplicity of almost all {\it Kepler}\ Objects 
+campaigns have measured the multiplicities of almost all {\it Kepler}\ Objects 
 of Interest 
@@
 
-The high resolution imaging campaign is also beginning to connect with
+This high resolution imaging campaign is also beginning to connect with
 occurrence rate calculations.
@@
 occurrence rates, will remain biased.
-The first-order correction that we suggest, given the impracticality of 
-performing high-resolution imaging of every star searched by a transit 
-survey, is to model the detection pipeline's efficiency while accounting for 
-binarity.
-For {\it Kepler}, this would require high resolution imaging of a
-comparison sample of non-KOI host stars. If the associated multiplicity 
-statistics are then included in a model of the pipeline's detection 
-efficiency, and the number of searchable stars is appropriately counted (at a 
-given $\delta_{\rm obs}$), it would correct many of binarity's biases.
+
+\paragraph{Practical effects: smooth detection efficiencies; finite SNR floors}
+To interpret whether the results of this study are of any help for removing 
+binarity's effects from the {\it Kepler}\ planet sample, a few practical 
+concerns become pressing.
+
+First, our calculations have ignored the fact that any given transit survey's 
+finite SNR floor might censor the apparent rate density.
+If the surveyed stars all have the same size, this is equivalent to 
+saying that there might be a cutoff in apparent planet radii, below which no 
+planets are detected.
+The effects on our main results (e.g., 
+Figs.~\ref{fig:occ_rate_model_3_log},~\ref{fig:frac_model_3}, 
+and~\ref{fig:gaussian_HJ}) would be that the apparent rate density 
+below the cutoff in apparent radius would simply drop to zero.
+
+A second assumption we used is that the detection efficiency is a 
+step function in SNR.
+The detection efficiencies of real transit surveys are smooth functions in 
+SNR; see for example the injection \& recovery simulations performed on {\it 
+    Kepler}\ data by~\citet{christiansen_measuring_2016}, and the resulting 
+smooth 
+functional form adopted by~\citet{fulton_california-_2017}.
+If we were to take a smooth detection probability in SNR, we would need to 
+include a detection efficiency term in 
+Eq.~\ref{eq:defn_apparent_rate_density} to inversely weight for planets 
+that had low probabilities of being detected.
+
+The simplest way to avoid the conceptual complications of accounting for 
+finite detection efficiency is to raise the SNR floor, to {\it e.g.,} 
+${\rm SNR} \approx 12$ in \citet{fulton_california-_2017}'s Fig 5.
+To a good approximation, this allows one to discuss stars that are 
+``searchable'' and ``not searchable'' for signals of an observed depth (at 
+fixed orbital period).
+For {\it Kepler} specifically, coupled with high resolution imaging of a
+comparison sample of non-KOI host stars, this would facilitate the process 
+of directly comparing the observed KOI distribution of apparent radii with the 
+distributions discussed in this study.
+
+If one insists on using a smooth detection efficiency, then life probably 
+becomes more complicated.
+It might then be necessary to model the detection pipeline's efficiency while 
+somehow marginalizing over binarity.
+Since the relative number of detections (at fixed $\delta_{\rm obs}$) coming 
+from singles, primaries, and secondaries changes as a function of the 
+intrinsic distribution of planet parameters (Fig.~\ref{fig:frac_model_3}), 
+some complicated deconvolution might be required.
 
@@
 (\citealt{burke_terrestrial_2015}'s Fig.~17).
-In the power law model of Sec.~\ref{sec:model_3}, the inferred rate can be up 
-to 50\% higher than the true rate around single stars.
+In the power law model of Sec.~\ref{sec:model_3}, we noted that the inferred 
+rate can be up to 50\% higher than the true rate around single stars.
 Though this bias seems large, it is currently small compared to the other 
@@
     kraus_impact_2016}.
-This effect might further bias transit survey measurements of $\eta_\oplus$
+This effect might further affect transit survey measurements of $\eta_\oplus$
 beyond our rough estimate.
@@
 This gives an $\approx 25\%$ relative difference, indicating metallicity could 
-account for at least half of the ``hot Jupiter rate discrepancy''.
+account for about half of the ``hot Jupiter rate discrepancy''.
 }.
@@
 average underestimated by a multiplicative factor of $\approx\! 1.5$.
-\citet{ziegler_robo-ao_2017} recently reported a similar value for the real
-population of systems observed by the Robo-AO KOI survey, under the same 
-assumption.
-
-Our models indicate that assuming a detected planet has equal probability of 
-orbiting the primary or secondary leads to an overestimate of
+\citet{ziegler_robo-ao_2017} recently reported a similar mean radius 
+correction factor for the multiple systems observed by the Robo-AO KOI survey, 
+using the same assumption that detected planets are as likely to orbit the 
+primary and the secondary.
+
+Assuming a broken power-law radius distribution, we showed in 
+Fig.~\ref{fig:frac_model_3} that assuming a detected planet has equal 
+probability of orbiting the primary or secondary leads to an overestimate of
 binarity's population-level effects.
-A planet orbiting the secondary does lead to extreme corrections, but these 
-cases are rare outliers, because the searchable volume for secondaries is so 
-much smaller than that for primaries (see~Fig.~\ref{fig:model_1_volumes}).
-This means that when high-resolution imaging discovers a binary companion in 
+A planet orbiting the secondary does lead to extreme corrections.
+However, at $r\a \gtrsim 2r_\oplus$, these cases are rare outliers.
+At $r\a \lesssim 2r_\oplus$, for all of the trial values of $Z_2/Z_0$ assumed 
+in Fig.~\ref{fig:frac_model_3}, a detected planet is always more likely to 
+orbit the primary than the secondary.
+
+Of course, our model's assumptions (see the list in Sec.~\ref{sec:conclusion}) 
+might not apply to the {\it Kepler}\ dataset.
+If they do, then for the $56\%$ of ``\texttt{CONFIRMED}'' 
+KOIs\footnote{Exoplanet Archive; \cite{akeson_nasa_2013}; 
+\url{exoplanetarchive.ipac.caltech.edu}} with 
+apparent radii $>2r_\oplus$, 
+whenever high-resolution imaging 
+discovers a binary companion in 
 a system that hosts a detected transiting planet, the planet is much
@@
 orbit the primary by inferring the stellar density from the transit duration.
-
-\paragraph{On completeness}
-{\bf TODO THIS SECTION}
-This is if some fraction of stars you thought were searchable are not. There 
-are no such stars.
-
-Our expressions for the apparent rate density 
-(Eqs.~\ref{eq:defn_apparent_rate_density} 
-and~\ref{eq:model_1_apparent_rate_density}) do not explicitly mention 
-detection efficiency.
-If we were to take a smooth detection probability in S/N, we would need to 
-include an explicit detection efficiency term in 
-Eq.~\ref{eq:defn_apparent_rate_density} to inversely weight for planets 
-that had low probabilities of being detected.
-However, our ``detection probability'' is a step function in S/N 
-(Eq.~\ref{eq:S_N_thresh}).
-In our model, the maximum searchable distance is only a function of the 
-apparent depth and true system luminosity.
-Even though the observers are selecting stars based on what they think are 
-``true radii'' (bottom row of Fig.~\ref{fig:model_1_volumes}), the 
-actual searchability of a point-source is determined by apparent radius and 
-system luminosity (Eq.~\ref{eq:S_N_thresh}; top rows of 
-Fig.~\ref{fig:model_1_volumes}).
-Thus at a given apparent radius $r\a$, the stars (single or binary) that are 
-searchable are exactly the stars that are SEARCHED, since dilution affects the 
-apparent radius and the maximum searchable distance in equal and opposite 
-order.
 
@@
 observer ignoring binarity (Eq.~\ref{eq:general_Gamma_a}).
-As input, this equations requires a volume-limited mass ratio distribution 
+As input, this equation requires a volume-limited mass ratio distribution 
 $f(q)$, and also the true rate densities for planets around singles, 
@@
 \begin{enumerate}
-    \item the transit survey is S/N limited;
+    \item the transit survey is SNR limited;
     \item all the primaries and single stars have identical properties;
@@
 when the assumptions listed above are met.
-Otherwise, they are only suggestive.
-{\bf TODO: finish}
+Otherwise, while it is only suggestive, our approach still provides 
+helpful hints at how stellar binarity influences transit survey occurrence 
+rates.
 
 \acknowledgements{
-It was a pleasure discussing this work with F. Dai and T. Barclay.
+It was a pleasure sharing discussions about this study with F. Dai and T. 
+Barclay.
+This work made use of NASA's Astrophysics Data System Bibliographic Services.
 
@@
     tra}(M\a),
+\label{eq:n_det_0}
 \end{align}
@@
     \mathcal{A}^4}\,f(q)\,\Gamma_1\left({r_a\over\mathcal{A}}, M\a\right),
+\label{eq:n_det_1}
 \end{align}
@@
     tra}(qM\a),
+\label{eq:n_det_2}
 \end{align}

### 2017-12-20 paper/main.tex
paper: correcting typos

@@
 for the apparent rate density, for which the free parameters include the true 
-radius distribution of planets, and also the relative numbers of planets 
+planet radius distribution, and also the relative numbers of planets 
 orbiting secondaries, primaries, and single stars.
@@
 whenever high-resolution imaging follow-up discovers stellar neighbors of 
-detected planets, the planet is more likely to orbit primary. 
+detected planets, the planet is more likely to orbit the primary. 
 %
@@
 \end{equation}
-The observed transit depth $\delta_{\rm obs}$ constitutes the signal, ${\rm 
-S}$. The survey is shot-noise dominated, and the fractional photon noise 
+The observed transit depth per unit stellar flux $\delta_{\rm obs}$ 
+constitutes the signal, ${\rm S}$.
+The survey is shot-noise dominated, and the fractional photon noise 
 ${\rm N}$ scales as the inverse root of the photon flux received from any 
@@
 both planet radii and stellar properties.
-There are errors in $N_{{\rm s,a}}(\pp\a,\ps\a)$ because an apparently 
-searchable point on the sky might include two searchable stars.
+There are errors in $N_{{\rm s,a}}(\pp\a,\ps\a)$ because a 
+searchable point on the sky might be two searchable stars.
 There are errors in $p_{\rm tra}(\pp\a,\ps\a)$ because stars in binaries may 
@@
 which all planets have identical properties, and all stars have identical 
-properties except that some are in binaries.
+properties except that some are in binary systems.
 The straightforward thought-experiments of Sec.~\ref{sec:simplest} are then 
@@
         {\it Top:} At an apparent radius $r\a=r\p$,
-        the observer searched twin binaries out to a larger         
-        distance, $\sqrt{2}\times$ that of single stars.
+        the observer searched twin binaries out to a
+        distance $\sqrt{2}\times$ that of single stars.
         Because of dilution, there are no planets in twin binaries with 
@@
         {\it Middle:} At an apparent radius $r\a=r\p/\sqrt{2}$, the 
-        searched volumes are half those at $r\a=r\p$. 
+        maximum searchable distances are half those at $r\a=r\p$. 
         The only detected planets with $r\a=r\p/\sqrt{2}$ orbit twin binaries.
@@
 If the true planet radius is $r=r\p$, then planets in singles will be 
-detected with the identical apparent radii: $r\a = r\p$.
+detected with identical apparent radii: $r\a = r\p$.
 Conversely, all detections in twin binaries will have apparent radii 
@@
 between the number of searchable binary systems and the number of searchable 
-singles at a given $r\a$.
+singles at any $r\a$.
 This quantity is useful because although $N\s^{\rm b}$ and $N\s^0$ vary
@@
         radius, for a model with identical stars, identical planets, and twin 
-        binaries.
+        binaries (same as Fig.~\ref{fig:model_1_volumes}).
         We assume a twin binary fraction of ${\rm BF}=0.1$, and that all 
@@
         If the true planet radius is $r\p$, all planets detected in binaries 
-        will have apparent radii $r\a = r\p/\sqrt{2}$ (see 
-        Eq.~\ref{eq:model_1_apparent_rate_density}).
+        will have apparent radii $r\a = r\p/\sqrt{2}$;
+        Eq.~\ref{eq:model_1_apparent_rate_density} gives the normalizations.
         The rate and rate density are related by $\Lambda|_a^b = 
@@
 Consider now a universe that is the same in every respect to that of 
-Sec.~\ref{sec:model_1}, except now half of planets have radii $r\p$, while 
+Sec.~\ref{sec:model_1}, except that half of planets have radii $r\p$, while 
 the other half have $r\p/\sqrt{2}$.
@@
 \end{equation}
-where as always $i=0$ corresponds to singles, $i=1$ to primaries, and $i=2$ to 
+where as before $i=0$ corresponds to singles, $i=1$ to primaries, and $i=2$ to 
 secondaries, and the $Z_i$'s are the number of planets per star of each type.
 
-Following an identical line of reasoning as before, the apparent rate density 
-can be written
+Following an identical line of reasoning as in Sec.~\ref{sec:model_1}, the 
+apparent rate density can be written
 \begin{align}
@@
 
-To generalize the procedure of Sec.~\ref{sec:simplest}, we consider a SNR 
+To generalize the procedure of Sec.~\ref{sec:simplest}, we consider an SNR 
 limited transit survey in which all the primaries and single stars have 
@@
 \end{equation}
-
 If $\mathrm{BF}$ is independent of $q$, $L \propto M^\alpha$, and $f(q) 
@@
         \citet{raghavan_survey_2010}'s Fig.~16.
-        At a given observed depth, the searchable binaries in a transit survey 
-        are magnitude-limited.
+        At a given observed transit depth, the searchable binaries in a 
+        transit survey are magnitude-limited.
     }
@@
 \end{equation}
-where as awlays, $i=0$ corresponds to single stars, $i=1$ to primaries of 
+where as always, $i=0$ corresponds to single stars, $i=1$ to primaries of 
 binaries, and $i=2$ to secondaries of binaries.
@@
 
-This study presented simple models for the effects of binarity on occurrence 
+This study presented simple models for how binarity affects occurrence 
 rates measured by transit surveys.
 The simplest of these models (Sec.~\ref{sec:simplest}) provided an 
-order-of-magnitude estimate for how much binarity might affect occurrence 
-rates: by no more than $\sim$factors of two.
+order-of-magnitude estimate that showed we would need very high twin binary 
+fractions for binarity to affect apparent occurrence rates by more than 
+$\sim$factors of two.
 
@@
 \end{enumerate}
-
 Allowing for these conditions, many results follow:
@@
 imaging.
-This will likely become an important consideration for precise measurements of 
-the depth, width, and slope of .
 %

### 2017-12-21 paper/main.tex
add discussion of companion fraction uptick

@@
 
+Further, Fig.~\ref{fig:frac_model_3} shows that going from apparent 
+radii of $2r_\oplus$ to $\approx 1.4r_\oplus$, the fraction of detected 
+planets with binary companions increases by $\approx 6-12\%$, depending on the 
+assumed value of $Z_2/Z_0$.
+Let the fraction of detected planets from primaries at a given apparent radius 
+be $F_1(r\a)$.
+In the planet-less secondaries case, one can then see by analyzing 
+Eqs~\ref{eq:n_det_0} and~\ref{eq:n_det_1} semi-analytically that 
+$F_1(2r_\oplus)/F_1(2r_\oplus/\sqrt{2}) \approx 1.19$.
+%check_companion_fractions.py, and LB's notes 2017/12/21.0
+More intuitively, this ``shift'' is a feature of any radius distribution that 
+declines at large radii, and flattens below some cutoff $r_c$.
+Thinking only about dilution from primaries is simplest:
+at apparent radii $r\a < r_c/\sqrt{2}$, relatively more planets will be 
+``diluted'' into the given $r\a$, since there are more planets in 
+the undiluted distribution from $r\a$ to $\sqrt{2}r\a$.
+This prediction is compared against current measurements in 
+Sec.~\ref{sec:discussion}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 systems, this might bias the rates low.
+
+\paragraph{Fraction of detected planets with binary companions vs. apparent 
+radius}
+A prediction of Fig.~\ref{fig:frac_model_3} is that the fraction of detected 
+planets with binary companions increases by $\approx 6-12\%$ going from 
+$2r_\oplus$ to $\approx 1.4r_\oplus$.
+In \citet{ziegler_robo-ao_2017}'s recent summary of the Robo-AO KOI survey, 
+they reported the nearby star fraction rates for planet candidates binned by 
+Earths ($r\a < 1.6r_\oplus$), Neptunes ($1.6r_\oplus < r\a < 3.9 r_\oplus$), 
+Saturns ($3.9r_\oplus < r\a < 9 r_\oplus$), and Jupiters ($r\a > 9r_\oplus$).
+The nearby star rates and their $1\sigma$ uncertainties 
+(following~\cite{burgasser_binarity_2003}'s procedure) are as
+follows:
+\begin{itemize}
+    \item Earths: $16.3 \pm 1.0\%$, from 1480 systems.
+    \item Neptunes: $13.0 \pm 0.8\%$, from 2058 systems.
+    \item Saturns: $13.6 \pm 2.0\%$, from 338 systems.
+    \item Jupiters: $19.0 \pm 2.8\%$, from 247 systems.
+\end{itemize} 
+where the absolute normalization of the rates are less than those typical for 
+Sun-like stars at least in part because of Robo-AO's sensitivity 
+(see~\citealt{ziegler_robo-ao_2017}'s Fig.~2).
+The uptick in the companion rate for Jupiters is likely tied to a large 
+astrophysical false positive rate~\citep{santerne_sophie_2012}.
+Although the data do not support as large of an uptick in companion rate 
+as our Fig.~\ref{fig:frac_model_3} suggests, going from Neptunes to Earths,
+there is still a weak increase in the detected planet companion fraction.
 

### 2017-12-21 src/check_companion_fractions.py

@@ -1,0 +1,20 @@
+from __future__ import division
+import numpy as np
+from scipy.integrate import trapz
+
+α = 3.5
+β = 0
+δ = -2.92
+
+q = np.arange(0,1+1e-6,1e-6)
+
+A = (1 + q**α)**(-1/2)
+
+int1 = trapz( q**β * A**(-δ-4), q )
+int2 = trapz( q**β * A**(-4), q )
+
+BF = 0.44
+
+frac = (1 + (BF/(1-BF)*int1)**(-1)) / (1 + (BF/(1-BF)*int2)**(-1) )
+
+print(frac)

### 2017-12-21 src/plot_ndet_apparent_vs_radius.py

@@ -110,6 +110,8 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
                     label='$n_{\mathrm{det}}^2(r_{\mathrm{a}})$'+ndetstr+Zstr,
                     c=colors[ind], linestyle=':')
 
+            print(Z_2, min(y_1/y_a), max(y_1/y_a), max(y_1/y_a)/min(y_1/y_a))
+
 
     if many_Zs:
         box = ax.get_position()

### 2017-12-21 paper/main.tex
add KM comments

@@
 To generalize the procedure of Sec.~\ref{sec:simplest}, we consider an SNR 
-limited transit survey in which all the primaries and single stars have 
-identical properties.
-For example, they might all be solar analogs, roughly similar to 
-the stars that {\it Kepler} surveyed~\citep{batalha_selection_2010}.
+limited transit survey in which the true masses of all the singles and 
+primaries are known by the observer.
 We let the properties of the secondaries vary, and assume that there are some 
@@
 terms of its mass.
-We then allow for an arbitrary volume-limited mass ratio distribution 
-$f(q)$, and also for arbitrary true rate densities for singles, primaries, 
+We then allow for a volume-limited mass ratio distribution $f(q)$, which is 
+assumed to be independent of the primary's mass.
+We also allow arbitrary true rate densities for singles, primaries, 
 and doubles ($\Gamma_0, \Gamma_1, \Gamma_2$).
@@
 \begin{equation}
-\Gamma_i(r) = \frac{{\rm d}\Lambda_i}{{\rm d}r} = Z_i f_i(r),
-\quad {\rm for\ }i\in\{0,1,2\},
+\Gamma_i(r) = Z_i f_i(r), \quad {\rm for\ }i\in\{0,1,2\},
 \end{equation}
@@
         bins) as a function of planet radius for the distribution specified by 
-        Eq.~\ref{eq:model3_radius_distribution}. This model has identical 
-        primaries and single stars, and varying secondaries. We use an 
-        arbitrary normalization of $Z_0=0.5$ throughout.}
+        Eq.~\ref{eq:model3_radius_distribution}. 
+        This model assumes that the true properties of all the singles and 
+        primaries are known to the observer, and that the volume-limited mass 
+        ratios of secondaries are drawn from a uniform distribution. We use an 
+        arbitrary normalization of $Z_0=0.5$ throughout.
+        The rate (left) and rate density (right) are related by $\Lambda|_a^b 
+        = \int_{a}^{b}\Gamma\,{\rm d}r$.
+    }
     \label{fig:occ_rate_model_3_log}
@@
 \end{align}
-As before, all single and primary stars in this model have identical 
-properties. The secondaries have masses, radii, and luminosities that vary 
-between systems: $R \propto M \propto L^{\frac{1}{\alpha}}$.
+As before, we assume that the observers know the true properties of all 
+singles and primaries. The secondaries have masses, radii, and luminosities 
+that vary between systems: $R \propto M \propto L^{\frac{1}{\alpha}}$.
 Our ``nominal model'' remains the same: 
@@
 assumed value of $Z_2/Z_0$.
-Let the fraction of detected planets from primaries at a given apparent radius 
-be $F_1(r\a)$.
-In the planet-less secondaries case, one can then see by analyzing 
-Eqs~\ref{eq:n_det_0} and~\ref{eq:n_det_1} semi-analytically that 
-$F_1(2r_\oplus)/F_1(2r_\oplus/\sqrt{2}) \approx 1.19$.
+Let the fraction of total detected planets from primaries at a given 
+apparent radius be $F_1(r\a)$, and from secondaries let it be $F_2(r\a)$.
+In the planet-less secondaries case ($F_2(r\a)=0$), one can 
+analyze Eqs~\ref{eq:n_det_0} and~\ref{eq:n_det_1} semi-analytically and show 
+that $F_1(2r_\oplus)/F_1(2r_\oplus/\sqrt{2}) \approx 1.19$.
 %check_companion_fractions.py, and LB's notes 2017/12/21.0
 More intuitively, this ``shift'' is a feature of any radius distribution that 
-declines at large radii, and flattens below some cutoff $r_c$.
-Thinking only about dilution from primaries is simplest:
-at apparent radii $r\a < r_c/\sqrt{2}$, relatively more planets will be 
+declines at large radii, and flattens below some cutoff $r_{\rm c}$.
+This is because (for dilution about primaries)
+at apparent radii $r\a < r_{\rm c}/\sqrt{2}$, relatively more planets will be 
 ``diluted'' into the given $r\a$, since there are more planets in 
@@
         (Eq.~\ref{eq:model4_radius_distribution}).
-        Similar to Fig.~\protect\ref{fig:occ_rate_model_3_log}, this model has 
-        fixed primaries and single stars, but varying secondaries.
+        Other than the intrinsic radius distribution, this model has the same 
+        assumptions as Fig.~\protect\ref{fig:occ_rate_model_3_log}.
     }
@@
 step function in SNR.
-The detection efficiencies of real transit surveys are smooth functions in 
-SNR; see for example the injection \& recovery simulations performed on {\it 
-    Kepler}\ data by~\citet{christiansen_measuring_2016}, and the resulting 
-smooth 
-functional form adopted by~\citet{fulton_california-_2017}.
+The detection efficiencies of real transit survey pipelines are smooth 
+functions in SNR; see for example the injection \& recovery simulations 
+performed by~\citet{christiansen_measuring_2016} on {\it Kepler}\ data, 
+and the resulting smooth functional form adopted 
+by~\citet{fulton_california-_2017}.
 If we were to take a smooth detection probability in SNR, we would need to 
@@
 Eq.~\ref{eq:defn_apparent_rate_density} to inversely weight for planets 
-that had low probabilities of being detected.
+with low probabilities of being detected.
 
@@
 finite detection efficiency is to raise the SNR floor, to {\it e.g.,} 
-${\rm SNR} \approx 12$ in \citet{fulton_california-_2017}'s Fig 5.
-To a good approximation, this allows one to discuss stars that are 
+${\rm SNR} \approx 12$ for {\it Kepler} 
+(\citealt{fulton_california-_2017}, Fig.~5).
+To a good approximation, this allows one to use the boolean distinctions 
 ``searchable'' and ``not searchable'' for signals of an observed depth (at 
 fixed orbital period).
-For {\it Kepler} specifically, coupled with high resolution imaging of a
-comparison sample of non-KOI host stars, this would facilitate the process 
-of directly comparing the observed KOI distribution of apparent radii with the 
-distributions discussed in this study.
-
+This also makes the survey strictly SNR-limited, rather than ``fuzzily 
+SNR-limited''.
+Since this threshold is set in an arbitrary manner anyway\footnote{For 
+example, {\it Kepler}'s threshold of ${\rm SNR}=7.1$ was set for there to be 
+no more than one statistical false alarm across the full {\it Kepler} 
+campaign~\citep{jenkins_tests_2002}. Equally valid would have been to insist 
+on no more than $10^{-3}$ false alarms per survey, raising the detection floor.
+}, this simplification would put occurrence rate studies on 
+clearer conceptual 
+ground, and facilitate the process of converting the observed distributions
+of apparent radii into true radius distributions.
+
+\begin{comment}
 If one insists on using a smooth detection efficiency, then life probably 
@@
 some complicated deconvolution might be required.
+\end{comment}
 
@@
 \end{itemize} 
-where the absolute normalization of the rates are less than those typical for 
+where the values of the rates are less than the $\sim 45\%$ typical for 
 Sun-like stars at least in part because of Robo-AO's sensitivity 
-(see~\citealt{ziegler_robo-ao_2017}'s Fig.~2).
+(\citealt{ziegler_robo-ao_2017}'s Fig.~2;~\citealt{raghavan_survey_2010}).
 The uptick in the companion rate for Jupiters is likely tied to a large 
 astrophysical false positive rate~\citep{santerne_sophie_2012}.
-Although the data do not support as large of an uptick in companion rate 
-as our Fig.~\ref{fig:frac_model_3} suggests, going from Neptunes to Earths,
-there is still a weak increase in the detected planet companion fraction.
+Going from Neptunes to Earths, the data suggest a weak increase in the 
+detected planet companion fraction, perhaps of a few percent.
 
@@
     \item the transit survey is SNR limited;
-    \item all the primaries and single stars have identical properties;
-    \item the properties of the secondaries can vary, but there are known 
-    functions $L(M)$ and $R(M)$ that specify a star's luminosity and radius in 
-    terms of its mass;
-    \item the binarity-ignoring observers assume that binaries have the same 
-    properties as the primaries.
+    \item the true properties of all the singles and primaries are known to 
+    the observer;
+    \item the observers assume that binaries have the same properties as the 
+    primaries;
+    \item there are functions $L(M)$ and $R(M)$ that specify a star's 
+    luminosity and radius in terms of its mass.
 \end{enumerate}

### 2017-12-22 paper/main.tex
fix typo
KM comment on Sec 3

@@
 \frac{{\rm BF}}{1 - {\rm BF}}
-\left[ \int {\mathrm{d}q \over \mathcal{A}^4}\,f(q)\,\Gamma_1\left({r\a\over 
-    \mathcal{A}}, 
+\left[ \int \mathrm{d}q \,
+       \frac{f(q)}{\mathcal{A}^3}\cdot
+       \frac{1}{\mathcal{A}} \Gamma_1\left({r\a\over \mathcal{A}}, 
 M\a\right)\,
@@
 & \quad\quad\quad\quad\quad \left.\left.
-+\int {q \mathrm{d}q \over 
-    {\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma_2\left({r\a\over 
-    \mathcal{B}}, 
-qM\a\right)\,
++\int {\rm d}q\, \frac{f(q)}{\mathcal{A}^3}\cdot \frac{q}{\mathcal{B}}
+    \Gamma_2\left({r\a\over \mathcal{B}}, qM\a\right)\cdot
 {R(qM\a) \over R(M\a)}
@@
 \end{align}
-where 
+where ${\rm BF}$ is the volume-limited binary fraction, and $\mathcal{A}$ 
+($\mathcal{B}$) is the dilution term for primaries (secondaries).
+The dilution terms can be written
 \begin{equation}
 \mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}
+= (1+q^\alpha)^{-1/2},
 \end{equation}
@@
             sys}(M\a, q)} }
-\end{equation}
-are the dilution terms appropriate to primaries and secondaries, and as before 
-${\rm BF}$ is the volume-limited binary fraction.
+= q^{-1} (1+q^{-\alpha})^{-1/2}
+\end{equation}
+where the latter equalities assume $L\propto M^\alpha \propto R^\alpha$ (the 
+former are more general).
 
@@
 planets with $(r\a, M\a)$ are associated with 
-systems of many different planetary and stellar properties.
-This means that $n_{\rm det}(r\a, M\a)$ is given by a convolution of the 
-true rate density, $\Gamma(r, M)$, and the number per unit $(r\a, M\a)$ of 
-searchable stars that give $(r\a, M\a)$  when the true system actually has 
-$(r, M)$.
-This convolution has been evaluated, leaving only a dependence on the mass 
-ratio distribution.
-Finally, the latter term in the apparent rate density of secondaries comes 
-from a correction for the overestimated transit probability.
+systems of different planetary and stellar properties, as determined
+by the mass ratio $q$ of each binary.
+This corresponds to true planet radii and stellar masses 
+$(r\a/\mathcal{A},M\a)$ for primaries, and $(r\a/\mathcal{B},qM\a)$ for 
+secondaries.
+These contributions are then integrated over the mass ratio distribution 
+including the effect of Malmquist bias, $f(q)/\mathcal{A}^3$, discussed 
+further below. Finally, the latter term in the apparent rate density of 
+secondaries comes from a correction for the overestimated transit probability.
 
@@
         arbitrary normalization of $Z_0=0.5$ throughout.
-        The rate (left) and rate density (right) are related by $\Lambda|_a^b 
+        The rate and rate density are related by $\Lambda|_a^b 
         = \int_{a}^{b}\Gamma\,{\rm d}r$.

### 2017-12-22 src/integrate_for_apparent_rate_density.py
fix math error: q^{5/3} --> q^{2/3} in Γ_2
per `annoying_q_factor_dec_22.pdf`, derived by Kento!

@@ -258,8 +258,8 @@ def run_unit_tests(
         if Z_0 == Z_1 == Z_2:
             assert np.isclose(
                     np.mean(X_num[(r_a>r_pl) & (r_a<=r_pu)]),
-                    1/(1+μ) * (1 + 1/norm_q * BF/(1-BF) * (1.41425)),
-                    rtol=1e-6
+                    1/(1+μ) * (1 + 1/norm_q * BF/(1-BF) * (1.50249)),
+                    rtol=5e-6
                     )
 
         ##################################################################
@@ -387,7 +387,7 @@ def run_unit_tests(
         μ = get_mu(BF, model_number)
         assert np.isclose(
                 np.mean(X_num[(r_a>1) & (r_a<=r_pu/2**(1/2))]),
-                1/(1+μ) * (1 + 1/norm_q * BF/(1-BF) * (1.41425)),
+                1/(1+μ) * (1 + 1/norm_q * BF/(1-BF) * (1.50249)),
                 rtol=1e-6
                 )
 
@@ -441,7 +441,8 @@ def Gamma_a(r_a, M_a, f_q, q, A_q, B_q, μ, norm_r=None, norm_q=None,
             norm_r=norm_r,
             gaussianparams=gaussianparams)
 
-    I_2 = trapz((q**(5/3)) * \
+    #NOTE: q^{5/3} vs q^{2/3} requires some thought.
+    I_2 = trapz((q**(2/3)) * \
                 f_q * \
                 (A_q**(-3)) * \
                 (B_q**(-1)) * \
@@ -584,14 +585,19 @@ def get_apparent_rate_density(r_a_grid, M_a_grid, model_number):
     B_q = B(q)
 
     Γ_a, Γ_0, ndet_a0, ndet_a1, ndet_a2 = [], [], [], [], []
+
     print('ind/max_ind, rvalue')
+
     for r_a_ind, r_a in enumerate(r_a_grid):
         for M_a in M_a_grid:
+
             if r_a_ind % max(1,len(r_a_grid)//10) == 0:
                 print('{:d}/{:d}, {:.2f}'.format(r_a_ind,len(r_a_grid),r_a))
+
             _0, _1, _2, _3, _4 = Gamma_a(r_a, M_a, f_q, q, A_q, B_q, μ,
                     norm_r=norm_r, norm_q=norm_q,
                     gaussianparams=gaussianparams)
+
             Γ_a.append(_0)
             Γ_0.append(_1)
             ndet_a0.append(_2)

### 2017-12-22 src/plot_ndet_apparent_vs_radius.py

@@ -163,7 +163,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
         ax.set_xlim([-0.3,5.3])
 
     if many_Zs and logx:
-        ax.set_xlim([0.5,22])
+        ax.set_xlim([0.2,22])
 
     if model_number == 3 or model_number==7:
 

### 2017-12-22 paper/main.tex
update paper with q^{2/3} results

@@
 
-Using Eq.~\ref{eq:general_Gamma_a}, we can show that when $Z_0=Z_1=Z_2$,
+We are mostly interested in the apparent rate density's radius dependence.
+Marginalizing Eq.~\ref{eq:general_Gamma_a} over apparent stellar mass, we find
+that when $Z_0=Z_1=Z_2$,
 \begin{align}
-X_\Gamma &\equiv \left. \frac{\Gamma\a(r\a,M\a)}{\Gamma_0(r,M)} 
-\right|_{r\a\rightarrow r,\ M\a\rightarrow M} \\
+X_\Gamma &\equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
+\right|_{r\a\rightarrow r} \\
 &=
@@
 \left.\left.
-\int {\rm d}q\,q^{\beta+\gamma+\delta+\frac{8}{3}} 
+\int {\rm d}q\,q^{\beta+\gamma+\delta+\frac{5}{3}} 
 (1+q^\alpha)^{\frac{3}{2}}
@@
 summed integrals in Eq.~\ref{eq:powerlaw_vary_binary} give $(\ldots)\approx 
-1.41425$. %171211_model_integrals.nb
-For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.014$; the
-apparent rate density is higher than the rate density around singles by 1.4\%.
-To summarize, this model suggests that for a power-law radius distribution 
+1.50249$. %171211_model_integrals.nb
+For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$; the
+apparent rate density is higher than the rate density around singles by 4.8\%.
+In summary, this model suggests that for a power-law radius distribution 
 ($2r_\oplus \lesssim r\a \lesssim 17r_\oplus$) in which there are the same 
@@
 For $r\a < 2r_\oplus$, the equations are quite tedious, though still tractable.
-To compute $\Gamma\a(r\a)$, we simply insert 
-Eq.~\ref{eq:model3_radius_distribution} into Eq.~\ref{eq:general_Gamma_a}, and 
-integrate using a computer program.
-We refer the interested reader to our online 
+We insert Eq.~\ref{eq:model3_radius_distribution} into 
+Eq.~\ref{eq:general_Gamma_a}, and integrate using a computer 
+program. We refer the interested reader to our online 
 implementation\footnote{\url{https://github.com/lgbouma/binary_biases}}.
@@
 secondaries (Eqs.~\ref{eq:n_det_0},~\ref{eq:n_det_1}, and~\ref{eq:n_det_2}).
+
+In short, the answer to our question is ``it depends on the number of planets 
+orbiting secondaries, and also on the apparent radius of the detected planet''.
 In the scenario that high-resolution imaging finds a system with $r\a > 
-2r_\oplus$ in a binary, of order $\sim 3\times$ more detected planets orbit 
+2r_\oplus$ in a binary, roughly $\sim 2.5\times$ more detected planets orbit 
 primaries than secondaries, for the $Z_2/Z_0=1$ case.
-For the $Z_2/Z_0=0.5$ case, of order $\sim 7\times$ more detected planet 
+For the $Z_2/Z_0=0.5$ case, $\sim 5\times$ more detected planet 
 planets orbit primaries than secondaries.
-At $r\a < 2r_\oplus$, the ratios are $\sim 1.6 \times$ and $\sim 3.1 \times$ 
-as many detected planets orbiting primaries than secondaries for the same 
-$Z_2/Z_0$ values.
+So, for ``large'' apparent radii (relative to the cutoff in the 
+intrinsic rate density), yes, detected planets in binaries are more 
+likely to orbit the primary.
+
+The situation for $r\a < 2r_\oplus$ is more nuanced.
+For the $Z_2=0$ and $Z_2/Z_0=0.5$ cases, detected planets in binaries are 
+still always more likely to orbit the primary.
+However, if there are as many planets orbiting the secondaries as the 
+primaries, there is actually a turn-over radius, $\approx 0.4r_\oplus$, 
+beyond which more of the detected planets in binaries come from secondaries: 
+they have all been ``diluted down'' from larger true planetary radii!
+Although this (apparent) radius is at the limit of current sensitivities, this 
+effect will be interesting for future instruments to investigate.
 
@@
 as singles, in which case
-$\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 0.84$
+$\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 0.81$.
+%int_rate_density_vs_radius_model_7_withtext*manyZs.pdf
 For the case when no hot Jupiters orbit secondaries, $\Lambda_{{\rm HJ},0} 
@@
 In \citet{ziegler_robo-ao_2017}'s recent summary of the Robo-AO KOI survey, 
-they reported the nearby star fraction rates for planet candidates binned by 
-Earths ($r\a < 1.6r_\oplus$), Neptunes ($1.6r_\oplus < r\a < 3.9 r_\oplus$), 
-Saturns ($3.9r_\oplus < r\a < 9 r_\oplus$), and Jupiters ($r\a > 9r_\oplus$).
-The nearby star rates and their $1\sigma$ uncertainties 
-(following~\cite{burgasser_binarity_2003}'s procedure) are as
-follows:
+they reported the fraction of planet-hosting stars with Robo-AO detected 
+companion stars, binning by Earths ($r\a < 1.6r_\oplus$), Neptunes 
+($1.6r_\oplus < r\a < 3.9 r_\oplus$), Saturns ($3.9r_\oplus < r\a < 9 
+r_\oplus$), and Jupiters ($r\a > 9r_\oplus$).
+The reported nearby star rates and their $1\sigma$ uncertainties are:
 \begin{itemize}
@@
 \end{itemize} 
-where the values of the rates are less than the $\sim 45\%$ typical for 
+where the uncertainties were calculated 
+following~\citet{burgasser_binarity_2003}.
+The absolute values of the rates are less than the $\sim 45\%$ typical for 
 Sun-like stars at least in part because of Robo-AO's sensitivity 
 (\citealt{ziegler_robo-ao_2017}'s Fig.~2;~\citealt{raghavan_survey_2010}).
+Another reason for the lower measured companion rates could be that planetary 
+systems are less likely to have 
+binary companions (as~\citealt{kraus_impact_2016} argued for close binary 
+companions).
 The uptick in the companion rate for Jupiters is likely tied to a large 
@@
 Fig.~\ref{fig:frac_model_3} that assuming a detected planet has equal 
-probability of orbiting the primary or secondary leads to an overestimate of
-binarity's population-level effects.
+probability of orbiting the primary or secondary probably is rarely correct.
 A planet orbiting the secondary does lead to extreme corrections.
 However, at $r\a \gtrsim 2r_\oplus$, these cases are rare outliers.
-At $r\a \lesssim 2r_\oplus$, for all of the trial values of $Z_2/Z_0$ assumed 
-in Fig.~\ref{fig:frac_model_3}, a detected planet is always more likely to 
-orbit the primary than the secondary.
+At $r_\oplus \lesssim r\a \lesssim 2r_\oplus$, for all of the trial values of 
+$Z_2/Z_0$ assumed in Fig.~\ref{fig:frac_model_3}, a detected planet is always 
+more likely to orbit the primary than the secondary.
+Only at very small apparent radii, $r\a \approx 0.5r_\oplus$, and only if 
+secondaries host as many planets as singles and primaries, does this norm 
+break down.
 

### 2017-12-22 paper/figures/collect_results.sh
add cleanup scripts for paper figures

@@ -1,0 +1,7 @@
+cp ../../results/ndet_vs_radius_logx_model_3_fraclines_rpu_22.5_manyZs.pdf .
+cp ../../results/int_rate_density_vs_radius_model_7_rpu_22.5_manyZs.pdf .
+cp ../../results/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf .
+cp ../../results/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf .
+cp ../../results/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf .
+cp ../../results/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf .
+cp ../../results/occ_rate_vs_radius_model_1_brokenx.pdf .

### 2018-01-04 paper/main.tex
paper: formatting fix
fix typo
paper: text improvements

@@
 to occurrence rate measurements.
-Particular attention is paid to dilution of observed planet radii, errors in 
+We pay particular attention to dilution of observed planet radii, errors in 
 star counts, and treatment of detection efficiencies.
-Given a somewhat restrictive set of assumptions, we derive a general formula 
-for the apparent rate density, for which the free parameters include the true 
+Given a plausible set of assumptions, we derive a general formula 
+for the apparent rate density, which depends on the true 
 planet radius distribution, and also the relative numbers of planets 
@@
 From this formalism, we suggest that for most of the observed radius 
-distribution (apparent planet radii $>2r_\oplus$), ignoring binarity only 
+distribution (apparent planet radii $>2r_\oplus$), ignoring binarity 
 leads to errors in inferred occurrence rates at the $\lesssim 10\%$ level.
-One corollary is that binarity seems unlikely to strongly influence the HJ 
-rate discrepancy.
+One corollary is that binarity seems unlikely to strongly influence any 
+discrepancy between transit survey and RV survey hot Jupiter rates.
 The errors created by ignoring binarity at smaller apparent radii might be 
 larger: for instance, the absolute occurrence of Earth-sized planets could be 
-overestimated by up to $\approx 50\%$.
-A final point is that our formalism provides a quantitative argument for why
-whenever high-resolution imaging follow-up discovers stellar neighbors of 
-detected planets, the planet is more likely to orbit the primary. 
+overestimated by $\lesssim 50\%$.
+Under our formalism, we also show that if high-resolution imaging reveals 
+stellar neighbors of detected planets, the planet is usually more likely to 
+orbit the primary. We explore how this statement depends on the
+apparent radius of the detected planet.
 %
@@
 about primaries, and about secondaries~\citep[{\it 
-e.g},][]{wang_occurrence_2015}.
+e.g.},][]{wang_occurrence_2015}.
 
@@
 Binarity might also affect the observers' ability to correctly select 
-searchable stars (but see Sec.~\ref{sec:discussion} for discussion of this 
-issue).
+searchable stars.
 
@@
 luminous.
-While this is what biases detectability, separate effects bias interpretation:
-ignoring binarity, the (apparent) radii assigned to planets in binaries will 
-typically be smaller than the true radii.
-The apparent and true radii differ because of diluting flux, and possibly 
-because the planet is assumed to orbit the wrong 
-star.
+A separate effect is that the apparent radii assigned to planets in binaries 
+will typically be smaller than the true radii.
+Correcting for ``radius dilution'' requires knowing both the amount flux 
+contributed by each source in a photometric aperture, and which star the 
+planet orbits.
 
@@
 properties except that some are in binary systems.
-The straightforward thought-experiments of Sec.~\ref{sec:simplest} are then 
-generalized in Sec.~\ref{sec:general_formula} to allow for varying populations 
-of secondaries, and for varying intrinsic occurrence rate distributions.
-Sec.~\ref{sec:more_complicated} investigates questions of interest, 
-including (a) measurements of $\eta_\oplus$, (b) the ``hot Jupiter rate 
-discrepancy'', and (c) \citet{fulton_california-_2017}'s 
-recently discovered ``valley''.
-We discuss what our models suggest about binarity's biasing effects in 
-Sec.~\ref{sec:discussion}, and conclude in Sec.~\ref{sec:conclusion}.
+We generalize these thought-experiments in 
+Sec.~\ref{sec:general_formula} to allow for realistic stellar populations with 
+arbitrary occurrence rate distributions.
+Sec.~\ref{sec:more_complicated} explores the implications for
+(a) measurements of $\eta_\oplus$,
+(b) the ``hot Jupiter rate discrepancy'', and 
+(c) \citet{fulton_california-_2017}'s recently discovered ``valley''.
+We discuss what our models suggest about the importance of binarity's biases 
+in Sec.~\ref{sec:discussion}, and conclude in Sec.~\ref{sec:conclusion}.
 
@@
 The observers, with no a priori knowledge of the distance to a system, would 
-measure a flux, assume a stellar mass $M\a=M_1$, and estimate both a stellar 
+measure a flux, assume a stellar mass $M\a=M_1$, and estimate a stellar 
 radius $R\a = R(M\a)$ and an under-luminous system luminosity of $L_{\rm 
@@
 0.05$-$0.1$. 
-For the latter, we take $Z_0=Z_1=Z_2=0.5$, and plot the resulting occurrence 
-rates as a function of planet radius in Fig.~\ref{fig:occ_rate_model_1}.
+For the true number of planets per star, we take $Z_0=Z_1=Z_2=0.5$, and plot 
+the resulting occurrence rates as a function of planet radius in 
+Fig.~\ref{fig:occ_rate_model_1}.
 
@@
 \end{equation}
-We can define a rate density ``correction factor'', $X_\Gamma$, as the ratio 
+We define a rate density ``correction factor'', $X_\Gamma$, as the ratio 
 of the apparent to single star rate density,
@@
 Continuing in the assumption that the number of planets per single, primary, 
-and secondary star are equal, we find a rate density 
-correction factor at the true planet radius of $1/(1+\mu)$.
+and secondary star are equal, then the rate density 
+correction factor at the true planet radius is $1/(1+\mu)$.
 This yields a correction of 0.76 if ${\rm BF}=0.1$, and 0.87 if ${\rm 
@@
 While it seems unlikely that secondaries are planet-less, 
-it is worth noting that $\Gamma\a/\Gamma$ is sensitive to the relative number 
-of planets per single, primary, and secondary.
+the fact that $\Gamma\a/\Gamma$ is sensitive to the relative number 
+of planets per single, primary, and secondary will become important as we 
+proceed.
 
@@
 Consider now a universe that is the same in every respect to that of 
-Sec.~\ref{sec:model_1}, except that half of planets have radii $r\p$, while 
-the other half have $r\p/\sqrt{2}$.
+Sec.~\ref{sec:model_1}, except that half of planets have true radii $r\p$, 
+while the other half have true radii $r\p/\sqrt{2}$.
 The true rate densities are
@@
 
-To generalize the procedure of Sec.~\ref{sec:simplest}, we consider an SNR 
-limited transit survey in which the true masses of all the singles and 
-primaries are known by the observer.
-We let the properties of the secondaries vary, and assume that there are some 
-functions $L(M)$ and $R(M)$ that specify a star's luminosity and radius in 
-terms of its mass.
-We then allow for a volume-limited mass ratio distribution $f(q)$, which is 
-assumed to be independent of the primary's mass.
+To generalize the procedure of Sec.~\ref{sec:simplest}, we consider an 
+SNR-limited transit survey in which the singles and primaries can have 
+arbitrary properties, but their true masses are known by the observer.
+We assume that there are some functions $L(M)$ and $R(M)$ that specify a 
+star's luminosity and radius in terms of its mass, and that the volume-limited 
+binary mass ratio distribution, $f(q)$, is independent of the primary's mass.
 We also allow arbitrary true rate densities for singles, primaries, 
-and doubles ($\Gamma_0, \Gamma_1, \Gamma_2$).
-Since the properties of the secondaries vary, we must consider not only the 
-dependence of the rate densities on planet radius, but also on stellar mass.
+and secondaries ($\Gamma_0, \Gamma_1, \Gamma_2$).
 We presume that the observers always take the properties of a binary system to 
@@
 former are more general).
+The rate densities depend on both apparent radius and mass 
+because even if the primaries and singles were to have fixed
+mass, the mass of secondaries would vary, and so this dependence cannot be 
+immediately omitted.
 
@@
 \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
-f(q)\mathrm{d}q.
+f(q)\,\mathrm{d}q.
 \label{eq:mu_general}
@@
 If $\mathrm{BF}$ is independent of $q$, $L \propto M^\alpha$, and $f(q) 
-\propto q^\beta$, this reduces to
+\propto q^\beta$, this simplifies to
 \begin{equation}
 \mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 
-\left(1+q^\alpha\right)^{3/2} q^\beta\mathrm{d}q,
+\left(1+q^\alpha\right)^{3/2} q^\beta \,\mathrm{d}q,
 \label{eq:mu_power_laws}
@@
 In particular, the sample of searchable binaries is magnitude-limited.
-Given a searchable binary, the probability it having a mass ratio $q$ 
+Given a searchable binary, the probability that it has a mass ratio $q$ 
 scales as
@@
 where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
-ratio $q$, and the first term is the Malmquist bias.
+ratio $q$, and the first term is the Malmquist bias when $L\propto M^\alpha$.
 We show this magnitude-limited mass ratio distribution for the $\beta=0$ case 
@@
 The following section applies our general equation for the apparent rate 
-density (Eq.~\ref{eq:general_Gamma_a}) to study binarity's effects in more 
-realistic regimes.
+density (Eq.~\ref{eq:general_Gamma_a}) to study binarity's effects in regimes 
+of observational interest.
 In general, we will write the rate density for each type of star, 
@@
 binary, fixed-planet case (Eq.~\ref{eq:model_1_apparent_rate_density}), except 
-that the radius dependence and normalization are slightly different:
+for a slightly different radius dependence and normalization:
 \begin{equation}
@@
 If the $Z_i$'s are equal, the ``correction factor'' relative to the rate 
-density for singles then becomes quite simple:
+density for singles becomes quite simple:
 \begin{align}
@@
 Note though that it could change if the $Z_i$'s are not equal.
-Also, a power law radius distribution $f(r) \propto r^\delta$ diverges for 
+Also, the power law radius distribution $f(r) \propto r^\delta$ diverges for 
 $\delta < 0$; \citet{howard_planet_2012}'s results indicate that this
@@
 
-To confirm the intuition that non-twin binaries do not affect 
-the above result, we now assume $f(q) = q^\beta/\mathcal{N}_q$, for 
-$\mathcal{N}_q$ the normalization.
-This changes $\mu$ (Eq.~\ref{eq:mu_general} becomes 
+To check whether non-twin binaries change the above result, we now assume 
+$f(q) = q^\beta/\mathcal{N}_q$, for $\mathcal{N}_q$ the normalization.
+This changes $\mu$ (Eq.~\ref{eq:mu_general} simplifies to 
 Eq.~\ref{eq:mu_power_laws}).
-It may also affect the rate density, which could be a function of the stellar 
-mass, which is now varying for secondaries (we assume that singles and 
-primaries have the same mass).
+It may also affect the rate density, which could be a function of the 
+(varying) stellar mass.
 Absorbing this dependence into a power law as well,
@@
 For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$; the
-apparent rate density is higher than the rate density around singles by 4.8\%.
-In summary, this model suggests that for a power-law radius distribution 
+relative difference between the apparent rate density and the rate density 
+around singles is 4.8\%.
+This indicates that considering only twin binaries gave us correct 
+intuition: for a power-law radius distribution 
 ($2r_\oplus \lesssim r\a \lesssim 17r_\oplus$) in which there are the same 
@@
         ratios of secondaries are drawn from a uniform distribution. We use an 
-        arbitrary normalization of $Z_0=0.5$ throughout.
+        arbitrary normalization of $Z_0=Z_1=0.5$ throughout.
         The rate and rate density are related by $\Lambda|_a^b 
@@
 
-Though the details of the radius distribution $\Gamma_i(r)$ at $r<2r_\oplus$ 
-are still an active topic of research, we can consider how binarity effects
-this regime under various reasonable assumptions.
-For instance, we can assume that the true radius shape function is
+Though the details of the true radius distribution $\Gamma_i(r)$ at 
+$r<2r_\oplus$ are currently an active topic of research, we can consider how 
+binarity affects this regime under various reasonable assumptions.
+For instance, assume that the true radius shape function is
 \begin{align}
@@
 \end{align}
-As before, we assume that the observers know the true properties of all 
-singles and primaries. The secondaries have masses, radii, and luminosities 
-that vary between systems: $R \propto M \propto L^{\frac{1}{\alpha}}$.
+As in the previous model, we assume that the observers know the true 
+properties of all singles and primaries. The masses, radii, 
+and luminosities of stars vary as $R \propto M \propto L^{\frac{1}{\alpha}}$.
 Our ``nominal model'' remains the same: 
@@
 those from Sec.~\ref{sub:powerlaw_varying_binaries}.
-For $r\a < 2r_\oplus$, the equations are quite tedious, though still tractable.
-We insert Eq.~\ref{eq:model3_radius_distribution} into 
+For $r\a < 2r_\oplus$, the equations are tedious, but still tractable.
+For simplicity, we insert Eq.~\ref{eq:model3_radius_distribution} into 
 Eq.~\ref{eq:general_Gamma_a}, and integrate using a computer 
@@
 \paragraph{The rate of Earth analogs}
-The most immediately arresting result there is a ``bump'' in the apparent rate 
+The immediately arresting result there is a ``bump'' in the apparent rate 
 density at $r\a < 2r_\oplus$: the true rate for singles is less than the 
@@
 The ``bump'' exists even for the $Z_2/Z_0=0$ case as a $\approx 10\%$ effect.
+Evidently, the magnitude of this error depends strongly on the prevalence of 
+planets around secondaries.
 
@@
 %occ_rate_vs_radius_model_3_withtext_Zsub2_0.00_rpu_22.5.pdf
-If $Z_2/Z_0>0$, binarity affects this value less: when $Z_2/Z_0=0.5$, 
-we find $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 1.06$
+If $Z_2/Z_0>0$, binarity affects the apparent hot Jupiter rate less: when 
+$Z_2/Z_0=0.5$, we find $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 1.06$
 
@@
 
-It would be nice to get some intuition for how much the secondaries matter.
-From Fig.~\ref{fig:model_1_volumes}, we have the intuition that for a given 
-true planet radius, secondaries have a much smaller searchable volume than 
-primaries or singles.
+It would be nice to improve our intuition for how much the secondaries matter.
+We have the understanding that for a given true planet radius, secondaries 
+have a much smaller searchable volume than primaries or singles.
 Does this necessarily imply that if we are given a detected planet with some 
@@
 primaries than secondaries, for the $Z_2/Z_0=1$ case.
-For the $Z_2/Z_0=0.5$ case, $\sim 5\times$ more detected planet 
+For the $Z_2/Z_0=0.5$ case, $\sim 5\times$ more detected 
 planets orbit primaries than secondaries.
-So, for ``large'' apparent radii (relative to the cutoff in the 
-intrinsic rate density), yes, detected planets in binaries are more 
-likely to orbit the primary.
+So, relative to the cutoff in the intrinsic rate density, detected planets in 
+binaries with large apparent radii are more likely to orbit the primary.
 
@@
 However, if there are as many planets orbiting the secondaries as the 
-primaries, there is actually a turn-over radius, $\approx 0.4r_\oplus$, 
+primaries, then there is a turn-over radius, $\approx 0.4r_\oplus$, 
 beyond which more of the detected planets in binaries come from secondaries: 
 they have all been ``diluted down'' from larger true planetary radii!
-Although this (apparent) radius is at the limit of current sensitivities, this 
-effect will be interesting for future instruments to investigate.
+Although this (apparent) radius is at the limit of current detection 
+sensitivities, this effect will be interesting for future instruments to 
+investigate.
 
@@
 %check_companion_fractions.py, and LB's notes 2017/12/21.0
-More intuitively, this ``shift'' is a feature of any radius distribution that 
-declines at large radii, and flattens below some cutoff $r_{\rm c}$.
+Intuitively speaking, this ``shift'' is a feature of any radius distribution 
+that declines at large radii, and flattens below some cutoff $r_{\rm c}$.
 This is because (for dilution about primaries)
@@
 
-In particular,~\citet{fulton_california-_2017} recently reported a ``gap'' in 
+\begin{figure}[!t]
+    \centering
+    \epsscale{1.15}
+    \plottwo{figures/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf}
+    \caption{
+        {\it Left:} rate density and {\it right:} rate (over $0.25r_\oplus$ 
+        bins) as a function of planet radius in a model with a radius gap 
+        (Eq.~\ref{eq:model4_radius_distribution}).
+        Other than the intrinsic radius distribution, this model has the same 
+        assumptions as Fig.~\protect\ref{fig:occ_rate_model_3_log}.
+    }
+    \label{fig:model_4}
+\end{figure}
+
+In particular,~\citet{fulton_california-_2017} reported a ``gap'' in 
 the radius-period 
@@
 
-\begin{figure}[!t]
-    \centering
-    \epsscale{1.15}
-    \plottwo{figures/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf}
-    \caption{
-        {\it Left:} rate density and {\it right:} rate (over $0.25r_\oplus$ 
-        bins) as a function of planet radius in a model with a radius gap 
-        (Eq.~\ref{eq:model4_radius_distribution}).
-        Other than the intrinsic radius distribution, this model has the same 
-        assumptions as Fig.~\protect\ref{fig:occ_rate_model_3_log}.
-    }
-    \label{fig:model_4}
-\end{figure}
-
 \paragraph{Alternative models for the HJ distribution}
@@
 power law distribution.
-Consider instead a Gaussian radius shape function,
+This means that the apparent HJ rates computed in 
+Sec.~\ref{sec:model_3} are probably inaccurate.
+If we instead consider a Gaussian radius shape function,
 \begin{equation}
@@
 \begin{enumerate}
-    \item the transit survey is SNR limited;
+    \item the transit survey is SNR-limited;
     \item the true properties of all the singles and primaries are known to 

### 2018-01-04 paper/main.tex
paper: improve discussion

@@
 The last item we need to write down the apparent rate density $\Gamma\a(r\a)$ 
-is the number of unresolved point-sources on sky, $N_{\rm s,a}$.
+is the number of unresolved point-sources on sky that the observer thinks are 
+searchable, $N_{\rm s,a}$.
 Assuming that the apparent stellar radius is fixed, then given the 
@@
 
-To check whether non-twin binaries change the above result, we now assume 
+To check whether non-twin binaries change the preceding result, we now assume 
 $f(q) = q^\beta/\mathcal{N}_q$, for $\mathcal{N}_q$ the normalization.
@@
 
-In short, the answer to our question is ``it depends on the number of planets 
-orbiting secondaries, and also on the apparent radius of the detected planet''.
+In short, the detected planet usually is more likely to orbit the primary, but 
+it depends on the number of planets orbiting secondaries, and also on the 
+apparent radius of the detected planet.
 In the scenario that high-resolution imaging finds a system with $r\a > 
-2r_\oplus$ in a binary, roughly $\sim 2.5\times$ more detected planets orbit 
+2r_\oplus$ in a binary, roughly $\sim\! 2.5\times$ more detected planets orbit 
 primaries than secondaries, for the $Z_2/Z_0=1$ case.
-For the $Z_2/Z_0=0.5$ case, $\sim 5\times$ more detected 
+For the $Z_2/Z_0=0.5$ case, $\sim\! 5\times$ more detected 
 planets orbit primaries than secondaries.
-So, relative to the cutoff in the intrinsic rate density, detected planets in 
-binaries with large apparent radii are more likely to orbit the primary.
+So detected planets in binaries with large apparent radii (relative to the 
+cutoff in the intrinsic rate density) are more likely to orbit the primary.
 
@@
 
-\paragraph{How has binarity been considered in occurrence rate measurements?}
+\paragraph{How bad is ignoring binarity?}
 This study has shown that under a reasonable set of simplifying assumptions, 
 ignoring binarity introduces systematic errors to star and planet counts in 
-transit surveys, which then bias derived occurrence rates.
-Thus far, real-world occurrence rate calculations\footnote{
+transit surveys, which then biases derived occurrence rates.
+Thus far, occurrence rate calculations\footnote{
     A list of occurrence rate papers is maintained at 
@@
 thereof.
-While we do not resolve the problem, we do suggest the approximate scale of 
-the possible errors in a survey-independent manner.
-
-Of course, on a system-by-system level stellar multiplicity affects the 
-interpretation of planet candidates. High resolution imaging 
-campaigns have measured the multiplicities of almost all {\it Kepler}\ Objects 
-of Interest 
-\citep{howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
-    horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
-    law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
-    wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016,ziegler_robo-ao_2017}.
-The results of these programs have been collected 
-by~\citet{furlan_kepler_2017}, and they represent an important advance in 
-understanding the KOI 
-sample's multiplicity statistics.
-In particular, they can be immediately applied to rectify binarity's effects 
-on the mass-radius diagram~\citep{furlan_densities_2017}.
-
-This high resolution imaging campaign is also beginning to connect with
-occurrence rate calculations.
-The most recent rate studies have used~\citet{furlan_kepler_2017}'s 
-catalog to test the effects of removing KOI hosts with known companions, which 
-helps reduce contamination in the ``numerator'' of 
-the occurrence rate (\citealt{fulton_california-_2017}; 
-\citealt{petigura_CKS_2017}).
-However, without an understanding of the multiplicity statistics of the 
-non-KOI stars, the true number of searchable stars, and thus the true 
-occurrence rates, will remain biased.
-
-\paragraph{Practical effects: smooth detection efficiencies; finite SNR floors}
-To interpret whether the results of this study are of any help for removing 
-binarity's effects from the {\it Kepler}\ planet sample, a few practical 
-concerns become pressing.
-
-First, our calculations have ignored the fact that any given transit survey's 
-finite SNR floor might censor the apparent rate density.
-If the surveyed stars all have the same size, this is equivalent to 
-saying that there might be a cutoff in apparent planet radii, below which no 
-planets are detected.
-The effects on our main results (e.g., 
-Figs.~\ref{fig:occ_rate_model_3_log},~\ref{fig:frac_model_3}, 
-and~\ref{fig:gaussian_HJ}) would be that the apparent rate density 
-below the cutoff in apparent radius would simply drop to zero.
-
-A second assumption we used is that the detection efficiency is a 
-step function in SNR.
-The detection efficiencies of real transit survey pipelines are smooth 
-functions in SNR; see for example the injection \& recovery simulations 
-performed by~\citet{christiansen_measuring_2016} on {\it Kepler}\ data, 
-and the resulting smooth functional form adopted 
-by~\citet{fulton_california-_2017}.
-If we were to take a smooth detection probability in SNR, we would need to 
-include a detection efficiency term in 
-Eq.~\ref{eq:defn_apparent_rate_density} to inversely weight for planets 
-with low probabilities of being detected.
-
-The simplest way to avoid the conceptual complications of accounting for 
-finite detection efficiency is to raise the SNR floor, to {\it e.g.,} 
-${\rm SNR} \approx 12$ for {\it Kepler} 
-(\citealt{fulton_california-_2017}, Fig.~5).
-To a good approximation, this allows one to use the boolean distinctions 
-``searchable'' and ``not searchable'' for signals of an observed depth (at 
-fixed orbital period).
-This also makes the survey strictly SNR-limited, rather than ``fuzzily 
-SNR-limited''.
-Since this threshold is set in an arbitrary manner anyway\footnote{For 
-example, {\it Kepler}'s threshold of ${\rm SNR}=7.1$ was set for there to be 
-no more than one statistical false alarm across the full {\it Kepler} 
-campaign~\citep{jenkins_tests_2002}. Equally valid would have been to insist 
-on no more than $10^{-3}$ false alarms per survey, raising the detection floor.
-}, this simplification would put occurrence rate studies on 
-clearer conceptual 
-ground, and facilitate the process of converting the observed distributions
-of apparent radii into true radius distributions.
-
-\begin{comment}
-If one insists on using a smooth detection efficiency, then life probably 
-becomes more complicated.
-It might then be necessary to model the detection pipeline's efficiency while 
-somehow marginalizing over binarity.
-Since the relative number of detections (at fixed $\delta_{\rm obs}$) coming 
-from singles, primaries, and secondaries changes as a function of the 
-intrinsic distribution of planet parameters (Fig.~\ref{fig:frac_model_3}), 
-some complicated deconvolution might be required.
-\end{comment}
+Although this study does not resolve the problem, it does suggest the 
+approximate scale of the possible errors, in a survey-independent manner.
+The suggestion of Sec.~\ref{sec:model_2} is that for $r\a \gtrsim 2r_\oplus$, 
+binarity can be ignored down to the $\sim$few percent precision level.
+For apparent radii $\lesssim 2r_\oplus$, the picture is less forgiving:
+Sec.~\ref{sec:model_3} suggests that relative errors between apparent rates 
+and true rates around singles could easily reach $\sim\! 50\%$.
 
 \paragraph{The rate of Earth analogs}
-Per {\it Kepler}'s primary science objective, the rate of Earth-like planets 
-orbiting Sun-like stars has been independently measured by 
+In line with {\it Kepler}'s primary science goal, the rate of Earth-like 
+planets orbiting Sun-like stars has been independently measured by 
 \citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
     foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
-These efforts have found that the one-year terrestrial planet occurrence rate 
-varies between $\approx 0.03$ and $\approx 1$ per Sun-like star, depending on 
-assumptions that are made when retrieving the rate 
+These efforts revealed that the one-year terrestrial planet occurrence rate 
+is between $\approx\! 0.03$ and $\approx\!1$ per Sun-like star,
+depending on assumptions that are made when calculating the rate 
 (\citealt{burke_terrestrial_2015}'s Fig.~17).
-In the power law model of Sec.~\ref{sec:model_3}, we noted that the inferred 
-rate can be up to 50\% higher than the true rate around single stars.
-Though this bias seems large, it is currently small compared to the other 
+In Sec.~\ref{sec:model_3}, our power law model indicates that when singles and 
+secondaries host the same number of planets, the apparent rate is 50\% higher 
+than the true rate around single stars.
+Though this bias seems large, it is currently smaller than the other 
 systematic factors that dominate the dispersion in $\eta_\oplus$ 
 measurements.
-If a future analyses determine absolute values of $\eta_\oplus$ to 
-better than a factor of two, binarity might merit closer attention.
-
-One relevant caveat to our assessment of binarity's importance for 
+If future analyses determine absolute values of $\eta_\oplus$ to 
+better than a factor of two, binarity will likely merit closer attention.
+
+One caveat to this assessment of binarity's importance for 
 $\eta_\oplus$ measurements is that none of our models 
@@
     kraus_impact_2016}.
-This effect might further affect transit survey measurements of $\eta_\oplus$
-beyond our rough estimate.
-
-\paragraph{The hot Jupiter rate discrepancy}
-There is at least one context in which ignoring binarity has been suggested as 
-a possible source of discrepant occurrence rate measurements.
-Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
-marginally lower than those found by radial velocity surveys ($\approx 1\%$; 
-see Table~\ref{tab:hj_rates}).
+This might affect transit survey measurements of $\eta_\oplus$ beyond our 
+rough estimate.
+
+\paragraph{Hot Jupiter rate discrepancy}
+While binarity may appreciably affect $\eta_\oplus$ measurements, our analysis
+suggests that it is unlikely to influence the hot Jupiter rate discrepancy.
+The context of this disagreement is that hot Jupiter occurrence rates measured 
+by transit surveys ($\approx 0.5\%$) are marginally lower than those found by 
+radial velocity surveys ($\approx 1\%$; see Table~\ref{tab:hj_rates}).
 Though the discrepancy has weak statistical significance ($<3\sigma$),
@@
     \citet{petigura_CKS_2017} recently found $\beta = 3.4^{0.9}_{-0.8}$.
-This gives an $\approx 25\%$ relative difference, indicating metallicity could 
+    This gives an $\approx 25\%$ relative difference, indicating metallicity 
+    could 
     account for about half of the ``hot Jupiter rate discrepancy''.
@@
 
-Aside from surveying stars of varying metallicities, radial velocity and 
-transit surveys differ in how they treat binarity.
+The hypothesis that binarity might matter is grounded in the fact that radial 
+velocity and transit surveys treat binarity differently.
 Radial velocity surveys typically reject both visual and spectroscopic binaries
 \citep[\textit{e.g.},][]{wright_frequency_2012}.
-Transit surveys typically observe binaries, but the question of whether they 
+Transit surveys observe binaries, but the question of whether they 
 were searchable to begin with is left for later interpretation.
 In spectroscopic follow-up of candidate transiting planets, the prevalence of 
-astrophysical false-positives may also lead to a bias against confirmation of 
+astrophysical false-positives may also lead to a tendency against confirming 
 transiting planets in binary systems.
 
-Ignoring these complications, in this work we showed that
-binarity biases transit survey occurrence rates through its effects on 
-star counts and the apparent radii of detected planets.
-Our results from Sec.~\ref{sec:model_3} indicate that binarity 
+Ignoring these complications, in this work we concentrated on binarity's 
+effects on star counts and the apparent radii of detected planets.
+Assuming a power-law radius distribution, and that no secondaries host HJs,
+our results from Sec.~\ref{sec:model_3} indicate that binarity 
 could lead to underestimated HJ rates relative to singles by a multiplicative 
-factor of at most $\approx 1.13$ (assuming a power-law radius distribution, 
-and that no secondaries host HJs).
+factor of at most $\approx 1.13$.
 We later pointed out in Sec.~\ref{sec:further_models} that assuming a 
 power-law radius distribution is probably wrong if one wishes to study the HJ 
-rate discrepancy. If we instead assumed a 
-Gaussian radius distribution~\citep[following][]{petigura_CKS_2017}, apparent 
-HJ rates are actually {\it greater} 
-than the true rate around singles.
+rate discrepancy.
+If we instead assumed a Gaussian radius 
+distribution~\citep[following][]{petigura_CKS_2017}, apparent 
+HJ rates are {\it greater} than the true rate around singles: the effect goes 
+the wrong way.
 \begin{comment}
@@
 \end{comment}
-This means that assuming a Gaussian similar to that reported 
-by~\citet{petigura_CKS_2017}, binarity is unlikely to resolve the HJ rate 
-discrepancy.
-Of course, such calculations can be at most suggestive~--~a true resolution 
+The ``hot Jupiter island'' reported by~\citet{petigura_CKS_2017} cannot 
+possibly be part of a continuous power law. 
+Thus binarity is unlikely to resolve the HJ rate discrepancy.
+
+Of course, such calculations are only suggestive; a conclusive resolution 
 of binarity's effects may require a detailed understanding of the 
@@
 systems, this might bias the rates low.
+Alternatively, {\it TESS}\ is expected to discover over $10^4$ 
+giant planets~\citep{ricker_transiting_2014,sullivan_transiting_2015}.
+Though they will be difficult to distinguish from false positives, one 
+possible use of this sample will to measure an occurrence rate of 
+short-period giant planets with minimal error from counting statistics.
+Our models suggest that binarity will only become an appreciable fraction of 
+the error budget at the $\approx 10\%$ precision level.
+This should be sufficient for a rate measurement precise enough to indicate a 
+preference between $\approx 0.5\%$ and $\approx 1\%$ of Sun-like stars hosting 
+hot Jupiters.
+
+\paragraph{Practical effects: smooth detection efficiencies; finite SNR floors}
+To relate this study's results to {\it Kepler}\ and other transit surveys, a 
+few practical concerns become pressing.
+
+First, our calculations have ignored the fact that any given transit survey's 
+finite SNR floor might censor the apparent rate density.
+If the surveyed stars all have the same size, this is equivalent to 
+saying that there might be a cutoff in apparent planet radii, below which no 
+planets are detected.
+The effects on our main results (e.g., 
+Figs.~\ref{fig:occ_rate_model_3_log},~\ref{fig:frac_model_3}, 
+and~\ref{fig:gaussian_HJ}) would be that the apparent rate density 
+below the cutoff in apparent radius would simply drop to zero.
+
+A second assumption we used is that the detection efficiency is a 
+step function in SNR.
+The detection efficiencies of real transit survey pipelines are smooth 
+functions in SNR; see for example the injection \& recovery simulations 
+performed by~\citet{christiansen_measuring_2016} on {\it Kepler}\ data, 
+and the resulting smooth functional form adopted 
+by~\citet{fulton_california-_2017}.
+If we were to take a smooth detection probability in SNR, we would need to 
+include a detection efficiency term in 
+Eq.~\ref{eq:defn_apparent_rate_density} to inversely weight for planets 
+with low probabilities of being detected.
+
+The simplest way to avoid the conceptual complications of accounting for 
+finite detection efficiency is to raise the SNR floor, to {\it e.g.,} 
+${\rm SNR} \approx 12$ for {\it Kepler} 
+(\citealt{fulton_california-_2017}, Fig.~5).
+To a good approximation, this allows one to use the boolean distinctions 
+``searchable'' and ``not searchable'' for signals of an observed depth (at 
+fixed orbital period).
+This also makes the survey strictly SNR-limited, rather than ``fuzzily 
+SNR-limited''.
+Since this threshold is set in an arbitrary manner anyway\footnote{For 
+    example, {\it Kepler}'s threshold of ${\rm SNR}=7.1$ was set for there to 
+    be 
+    no more than one statistical false alarm across the full {\it Kepler} 
+    campaign~\citep{jenkins_tests_2002}. Equally valid would have been to 
+    insist 
+    on no more than $10^{-3}$ false alarms per survey, raising the detection 
+    floor.
+}, this simplification would put occurrence rate studies on 
+clearer conceptual 
+ground, and facilitate the process of converting the observed distributions
+of apparent radii into true radius distributions.
+
+\begin{comment}
+If one insists on using a smooth detection efficiency, then life probably 
+becomes more complicated.
+It might then be necessary to model the detection pipeline's efficiency while 
+somehow marginalizing over binarity.
+Since the relative number of detections (at fixed $\delta_{\rm obs}$) coming 
+from singles, primaries, and secondaries changes as a function of the 
+intrinsic distribution of planet parameters (Fig.~\ref{fig:frac_model_3}), 
+some complicated deconvolution might be required.
+\end{comment}
+
+\paragraph{Connecting high resolution imaging to occurrence rates}
+A direct reason to address stellar multiplicity in transit surveys is that it 
+changes the interpretation of planet candidates on a system-by-system level.
+Consequently, high resolution imaging 
+campaigns have measured the multiplicities of almost all {\it Kepler}\ Objects 
+of Interest 
+\citep{howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
+    horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
+    law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
+    wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016,ziegler_robo-ao_2017}.
+The results of these programs have been collected 
+by~\citet{furlan_kepler_2017}, and they represent an important advance in 
+understanding the KOI 
+sample's multiplicity statistics.
+In particular, they can be immediately applied to rectify binarity's effects 
+on the mass-radius diagram~\citep{furlan_densities_2017}.
+
+These high resolution imaging campaigns are also beginning to connect with
+occurrence rate calculations.
+The most recent rate studies have used~\citet{furlan_kepler_2017}'s 
+catalog to test the effects of removing KOI hosts with known companions, which 
+helps reduce contamination in the ``numerator'' of 
+the occurrence rate (\citealt{fulton_california-_2017}; 
+\citealt{petigura_CKS_2017}).
+However, without an understanding of the multiplicity statistics of the 
+non-KOI stars, the true number of searchable stars, and thus the true 
+occurrence rates, will remain biased.
+
+\paragraph{Does a detected planet orbit the primary or secondary?}
+One important step towards rectifying binarity's effects is identifying the 
+host star for any detected planets in binaries.
+The current 
+wisdom is that nothing substantive can be said about the 
+likelihood of a planet orbiting the primary vs. the 
+secondary~\citep[\textit{e.g.},][]{ciardi_understanding_2015,ziegler_robo-ao_2017}.
+This of course ignores cases when planets can be confirmed to orbit either 
+component by analyzing the transit durations or centroids.
+
+\begin{comment}
+\citet{ciardi_understanding_2015} studied the effects of stellar multiplicity 
+on the planet radii derived from transit surveys.
+They modeled the problem for {\it Kepler}\ objects of interest by matching a 
+population of binary and tertiary companions to KOI stars, 
+under the assumption that the KIC-listed stars were the primaries.
+They then computed planet radius correction factors assuming that {\it 
+    Kepler}-detected planets orbited the primary or companion stars
+with equal probability (their Sec.~5).
+Under these assumptions, they found that any given planet's radius is on 
+average underestimated by a multiplicative factor of $\approx\! 1.5$.
+\citet{ziegler_robo-ao_2017} recently reported a similar mean radius 
+correction factor for the multiple systems observed by the Robo-AO KOI survey, 
+using the same assumption that detected planets are as likely to orbit the 
+primary and the secondary.
+\end{comment}
+
+Assuming a broken power-law radius distribution, we showed in 
+Fig.~\ref{fig:frac_model_3} that there are many cases where a detected planet 
+is much more likely to orbit the primary.
+A planet orbiting the secondary does lead to extreme corrections.
+However, at $r\a \gtrsim 2r_\oplus$, these cases are rare outliers.
+At $r_\oplus \lesssim r\a \lesssim 2r_\oplus$, for all of the trial values of 
+$Z_2/Z_0$ assumed in Fig.~\ref{fig:frac_model_3}, a detected planet is always 
+more likely to orbit the primary than the secondary.
+Only at very small apparent radii, $r\a \approx 0.5r_\oplus$, and only if 
+secondaries host as many planets as singles and primaries, does this ``rule'' 
+break down.
+
+Of course, our model's assumptions (see the list in Sec.~\ref{sec:conclusion}) 
+might not apply to the {\it Kepler}\ dataset.
+However if they are applicable, then for the $56\%$ of ``\texttt{CONFIRMED}'' 
+KOIs\footnote{Exoplanet Archive; \cite{akeson_nasa_2013}; 
+    \url{exoplanetarchive.ipac.caltech.edu}} with 
+apparent radii $>2r_\oplus$, 
+whenever high-resolution imaging 
+discovers a binary companion in 
+a system that hosts a detected transiting planet, the planet is much
+more likely to orbit the primary.
 
@@
 radius}
-A prediction of Fig.~\ref{fig:frac_model_3} is that the fraction of detected 
-planets with binary companions increases by $\approx 6-12\%$ going from 
-$2r_\oplus$ to $\approx 1.4r_\oplus$.
+One further prediction of Fig.~\ref{fig:frac_model_3} is that the fraction of 
+detected planets with binary companions increases by $\approx 6-12\%$ going 
+from $2r_\oplus$ to $\approx\! 1.4r_\oplus$.
 In \citet{ziegler_robo-ao_2017}'s recent summary of the Robo-AO KOI survey, 
@@
 following~\citet{burgasser_binarity_2003}.
-The absolute values of the rates are less than the $\sim 45\%$ typical for 
+The absolute values of the rates are less than the $\sim\! 45\%$ typical for 
 Sun-like stars at least in part because of Robo-AO's sensitivity 
@@
 detected planet companion fraction, perhaps of a few percent.
-
-\paragraph{Does a detected planet orbit the primary or secondary?}
-\citet{ciardi_understanding_2015} studied the effects of stellar multiplicity 
-on the planet radii derived from transit surveys.
-They modeled the problem for {\it Kepler}\ objects of interest by matching a 
-population of binary and tertiary companions to KOI stars, 
-under the assumption that the KIC-listed stars were the primaries.
-They then computed planet radius correction factors assuming that {\it 
-    Kepler}-detected planets orbited the primary or companion stars
-with equal probability (their Sec.~5).
-Under these assumptions, they found that any given planet's radius is on 
-average underestimated by a multiplicative factor of $\approx\! 1.5$.
-\citet{ziegler_robo-ao_2017} recently reported a similar mean radius 
-correction factor for the multiple systems observed by the Robo-AO KOI survey, 
-using the same assumption that detected planets are as likely to orbit the 
-primary and the secondary.
-
-Assuming a broken power-law radius distribution, we showed in 
-Fig.~\ref{fig:frac_model_3} that assuming a detected planet has equal 
-probability of orbiting the primary or secondary probably is rarely correct.
-A planet orbiting the secondary does lead to extreme corrections.
-However, at $r\a \gtrsim 2r_\oplus$, these cases are rare outliers.
-At $r_\oplus \lesssim r\a \lesssim 2r_\oplus$, for all of the trial values of 
-$Z_2/Z_0$ assumed in Fig.~\ref{fig:frac_model_3}, a detected planet is always 
-more likely to orbit the primary than the secondary.
-Only at very small apparent radii, $r\a \approx 0.5r_\oplus$, and only if 
-secondaries host as many planets as singles and primaries, does this norm 
-break down.
-
-Of course, our model's assumptions (see the list in Sec.~\ref{sec:conclusion}) 
-might not apply to the {\it Kepler}\ dataset.
-If they do, then for the $56\%$ of ``\texttt{CONFIRMED}'' 
-KOIs\footnote{Exoplanet Archive; \cite{akeson_nasa_2013}; 
-\url{exoplanetarchive.ipac.caltech.edu}} with 
-apparent radii $>2r_\oplus$, 
-whenever high-resolution imaging 
-discovers a binary companion in 
-a system that hosts a detected transiting planet, the planet is much
-more likely to orbit the primary.
-This statement is independent of the fact that planets are often confirmed to 
-orbit the primary by inferring the stellar density from the transit duration.
-
-\paragraph{Utility in future occurrence rate measurements}
-{\it TESS}\ is expected to discover over $10^4$ giant 
-planets~\citep{ricker_transiting_2014,sullivan_transiting_2015}.
-Though they will be difficult to distinguish from false positives, one 
-possible use of this large sample will to measure an occurrence rate of 
-short-period giant planets with minimal error from counting statistics.
-Our models suggest that binarity will only become an appreciable fraction of 
-the error budget at the $\approx 10\%$ precision level.
-This should be sufficient for a rate measurement precise enough to indicate a 
-preference between $\approx 0.5\%$ and $\approx 1\%$ of Sun-like stars hosting 
-hot Jupiters.
+It will be interesting to see whether this effect is borne out by further 
+observations.
 
@@
 As input, this equation requires a volume-limited mass ratio distribution 
-$f(q)$, and also the true rate densities for planets around singles, 
+$f(q)$, and the true rate densities for planets around singles, 
 primaries, and secondaries.
@@
 by~\citet{petigura_CKS_2017}.
+%
+\item Detected planets with $r\a \gtrsim 0.5r_\oplus$ that are revealed by 
+high resolution imaging surveys to exist in binaries are more likely to orbit 
+the primary (Fig.~\ref{fig:frac_model_3}).
+%
+\item Near the ``break'' in the true rate distribution ($\approx 2r_\oplus$), 
+the fraction of detected planets with binary companions increases
+(Fig.~\ref{fig:frac_model_3}).
 \end{itemize}
@@
 \label{sec:appendix}
-Recall our definition of apparent rate density 
+
+In this appendix, we derive Eq.~\ref{eq:general_Gamma_a}.
+First, recall our definition of apparent rate density 
 (Eq.~\ref{eq:defn_apparent_rate_density}).

### 2018-01-08 paper/main.tex
paper: incorporate KM comments

@@
 searchable point on the sky might be two searchable stars.
-There are errors in $p_{\rm tra}(\pp\a,\ps\a)$ because stars in binaries may 
-have different masses and radii than assumed in the single-star case.
-Binarity might also affect the observers' ability to correctly select 
-searchable stars.
+Finally, there are errors in $p_{\rm tra}(\pp\a,\ps\a)$ because stars in 
+binaries may have different masses and radii than assumed in the single-star 
+case.
 
@@
 of stars that are searchable for a given observed transit depth is greater 
-than that the multiplicity fraction in a volume limited sample.
+than the multiplicity fraction in a volume limited sample.
 This is the familiar Malmquist bias: at a fixed $\delta_{\rm obs}$, binaries 
@@
 The observers, with no a priori knowledge of the distance to a system, would 
-measure a flux, assume a stellar mass $M\a=M_1$, and estimate a stellar 
-radius $R\a = R(M\a)$ and an under-luminous system luminosity of $L_{\rm 
+measure a flux, and estimate a stellar mass $M\a=M_1$, a stellar 
+radius $R\a = R(M\a)$, and an under-estimated system luminosity of $L_{\rm 
 sys,a}(M\a) = L(M\a)$.
@@
 \frac{{\rm BF}}{1 - {\rm BF}}
-\left[ \int \mathrm{d}q \,
+\left[ \int_0^1 \mathrm{d}q \,
        \frac{f(q)}{\mathcal{A}^3}\cdot
@@
 & \quad\quad\quad\quad\quad \left.\left.
-+\int {\rm d}q\, \frac{f(q)}{\mathcal{A}^3}\cdot \frac{q}{\mathcal{B}}
++\int_0^1 {\rm d}q\, \frac{f(q)}{\mathcal{A}^3}\cdot \frac{q}{\mathcal{B}}
     \Gamma_2\left({r\a\over \mathcal{B}}, qM\a\right)\cdot
@@
 \end{align}
-where ${\rm BF}$ is the volume-limited binary fraction, and $\mathcal{A}$ 
-($\mathcal{B}$) is the dilution term for primaries (secondaries).
+where ${\rm BF}$ is the volume-limited binary fraction, 
+and $\mathcal{A}(q,M\a)$ [$\mathcal{B}(q,M\a)$] are the dilution terms for 
+primaries [secondaries], whose functional dependences are omitted for 
+notational simplicity.
 The dilution terms can be written
@@
 A derivation of Eq.~\ref{eq:general_Gamma_a} is given in the 
-\hyperref[sec:appendix]{Appendix}; here we highlight its qualitative 
-features.
+\hyperref[sec:appendix]{Appendix}; its qualitative features are as follows.
 The terms inside the curly braces $\{ \ldots \}$ are the sum of 
@@
 depth, for singles and primaries with the same luminosity, binaries are 
-searchable to a greater distance.
+searchable to a greater distance;
 In particular, the sample of searchable binaries is magnitude-limited.
@@
 \left(
-\int {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}} +
+\int_0^1 {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}} +
 \right.
@@
 \left.\left.
-\int {\rm d}q\,q^{\beta+\gamma+\delta+\frac{5}{3}} 
+\int_0^1 {\rm d}q\,q^{\beta+\delta+\frac{5}{3}} 
 (1+q^\alpha)^{\frac{3}{2}}
 (1+q^{-\alpha})^{\frac{\delta+1}{2}}
-\right)\right].
+\right)\right],
 \label{eq:powerlaw_vary_binary}
 \end{align}
-
+where $\gamma$ does not appear because of the marginalization over $M\a$.
 For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the 
@@
 If $Z_2/Z_0>0$, binarity affects the apparent hot Jupiter rate less: when 
-$Z_2/Z_0=0.5$, we find $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 1.06$
+$Z_2/Z_0=0.5$, we find $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 1.06$.
 
@@
 Let the fraction of total detected planets from primaries at a given 
-apparent radius be $F_1(r\a)$, and from secondaries let it be $F_2(r\a)$.
+apparent radius be $F_1(r\a)$, so $F_1(r\a) \equiv n_{\rm det}^1(r\a)/n_{\rm 
+det}^{\rm tot}$.
+Let the analogous quantity for secondaries be $F_2(r\a)$.
 In the planet-less secondaries case ($F_2(r\a)=0$), one can 
 analyze Eqs~\ref{eq:n_det_0} and~\ref{eq:n_det_1} semi-analytically and show 
-that $F_1(2r_\oplus)/F_1(2r_\oplus/\sqrt{2}) \approx 1.19$.
+that $F_1(2r_\oplus/\sqrt{2})/F_1(2r_\oplus) \approx 1.19$.
 %check_companion_fractions.py, and LB's notes 2017/12/21.0
@@
 Sec.~\ref{sec:model_3} are probably inaccurate.
-If we instead consider a Gaussian radius shape function,
+Instead, let us consider a Gaussian radius shape function,
 \begin{equation}
@@
 We then compute $\Gamma\a(r\a)$, and plot it in Fig.~\ref{fig:gaussian_HJ}.
-Integrating to find hot Jupiter rates,
+Integrating for $r\a > 8r_\oplus$ to find hot Jupiter rates,
 we find the opposite effect as in the power law model.
@@
 \approx \Lambda_{\rm HJ,a}$ to within one percent.
+Qualitatively, the apparent HJ rate can be greater than the true rate for 
+singles because binary systems can have an extra star that yields 
+hot Jupiter detections.
 
@@
 (\citealt{burke_terrestrial_2015}'s Fig.~17).
-In Sec.~\ref{sec:model_3}, our power law model indicates that when singles and 
-secondaries host the same number of planets, the apparent rate is 50\% higher 
-than the true rate around single stars.
+In Sec.~\ref{sec:model_3}, our power law model indicates that when primaries, 
+singles, and secondaries host the same number of planets, the apparent rate is 
+50\% higher than the true rate around single stars.
 Though this bias seems large, it is currently smaller than the other 
@@
     \citet{petigura_CKS_2017} recently found $\beta = 3.4^{0.9}_{-0.8}$.
-    This gives an $\approx 25\%$ relative difference, indicating metallicity 
+    This gives a $\approx 25\%$ relative difference, indicating metallicity 
     could 
@@
 Though they will be difficult to distinguish from false positives, one 
-possible use of this sample will to measure an occurrence rate of 
+possible use of this sample will be to measure an occurrence rate of 
 short-period giant planets with minimal error from counting statistics.
@@
 \begin{align}
-n_{\rm det}(r_a, M_a) &=
-\sum_i n_{\rm det}^i(r_a, M_a) \\
+n_{\rm det}(r_a, M\a) &=
+\sum_i n_{\rm det}^i(r_a, M\a) \\
 &=
 \sum_i \int \mathrm{d}r \mathrm{d}M \,
-\mathcal{N}_{\rm s}^i(r_a,M_a; r,M)
+\mathcal{N}_{\rm s}^i(r_a,M\a; r,M)
 \cdot\Gamma_i(r,M) \cdot p_{\rm tra}(r,M),
@@
 \paragraph{Primaries in binaries}
-The number of primaries with apparent parameters $(r_a,M_a)$ given the 
+The number of primaries with apparent parameters $(r_a,M\a)$ given the 
 true parameters $(r,M)$ is
 \begin{equation}
-\mathcal{N}_{\rm s}^1(r_a, M_a; r, M)
-=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r_a, M_a, q; r, M),
+\mathcal{N}_{\rm s}^1(r_a, M\a; r, M)
+=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r_a, M\a, q; r, M),
 \label{eq:fancyN_s_1}
@@
 \begin{equation}
-\mathcal{N}_{{\rm s},q}^1(r_a, M_a, q; r, M) \propto \delta(M_a-M).
+\mathcal{N}_{{\rm s},q}^1(r_a, M\a, q; r, M) \propto \delta(M\a-M).
 \end{equation}
@@
 \delta_{\rm obs}
-= \left[{r\over R(M_a)}\right]^2\times {L(M_a) \over L_{\rm sys}(M_a, q)}
-\equiv \left[{r\over R(M_a)}\right]^2\times \mathcal{A}(q,M\a)^2
+= \left[{r\over R(M\a)}\right]^2\times {L(M\a) \over L_{\rm sys}(M\a, q)}
+\equiv \left[{r\over R(M\a)}\right]^2\times \mathcal{A}(q,M\a)^2,
 \label{eq:delta_obs_primaries} 
+\end{equation}
+where
+\begin{equation}
+\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}.
 \end{equation}
@@
 N_{\rm s}^0(\delta_{\rm obs}, 
-L(M_a))\cdot
-{n_b\over n_s}\left[L_{\rm sys}(M_a, q) \over L(M\a)\right]^{3/2}
-=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))
+L(M\a))\cdot
+{n_b\over n_s}\left[L_{\rm sys}(M\a, q) \over L(M\a)\right]^{3/2}
+=N_{\rm s}^0(\delta_{\rm obs}, L(M\a))
 \cdot \frac{{\rm BF}}{1 - {\rm BF}} \cdot {1 \over \mathcal{A}(q,M\a)^3}.
@@
 \end{equation}
-
 Thus,
@@
 \notag
-\mathcal{N}_{{\rm s}, q}^1(r_a, M_a, q; r, M)
-&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))
+\mathcal{N}_{{\rm s}, q}^1(r_a, M\a, q; r, M)
+&=N_{\rm s}^0(\delta_{\rm obs}, L(M\a))
 \cdot \frac{{\rm BF}}{1 - {\rm BF}} \cdot {1 \over \mathcal{A}(q,M\a)^3}\\
-&\times\delta \left[r_a-r\mathcal{A}(q,M\a)\right]\delta(M_a-M).
-%&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))\cdot\mu(\mathrm{BF},M_a)\\
-%&\times\delta \left(r_a-r\sqrt{{L(M_a) \over L_{\rm sys}(M_a, 
-%q)}}\right)\delta(M_a-M).
+&\times\delta \left[r_a-r\mathcal{A}(q,M\a)\right]\delta(M\a-M).
 \label{eq:N_s_1}
@@
 \paragraph{Secondaries in binaries}
-In this case, $M=qM_1=qM_a$, so
-\begin{equation}
-\mathcal{N}_{{\rm s},q}^2(r_a, M_a, q; r, M)
-\propto \delta\left(M_a-{M\over q}\right).
+In this case, $M=qM_1=qM\a$, so
+\begin{equation}
+\mathcal{N}_{{\rm s},q}^2(r_a, M\a, q; r, M)
+\propto \delta\left(M\a-{M\over q}\right).
 \label{eq:fancyN_s_2_prop}
@@
 \begin{equation}
-\delta_{\rm obs} = \left[{r\over R(qM_a)}\right]^2 \times {L(qM_a) 
-    \over L_{\rm sys}(M_a, q)}.
+\delta_{\rm obs} = \left[{r\over R(qM\a)}\right]^2 \times {L(qM\a) 
+    \over L_{\rm sys}(M\a, q)}
+    \equiv \left[{r\over R(M\a)}\right]^2\times \mathcal{B}(q,M\a)^2,
+\end{equation}
+where
+\begin{equation}
+\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
+            sys}(M\a, q)} }.
 \end{equation}
 The normalization remains the same as the previous case (we are counting the 
-searchable stars at a given observed depth $\delta_{\rm obs}$, total 
+searchable stars at a given observed depth $\delta_{\rm obs}$, and the total 
 luminosity of the binary is the same).
@@
 \begin{equation}
-\mathcal{N}_{\rm s}^2(r_a, M_a; r, M)
-=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r_a, M_a, q; r, M),
+\mathcal{N}_{\rm s}^2(r_a, M\a; r, M)
+=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r_a, M\a, q; r, M),
 \end{equation}
@@
 \notag
-\mathcal{N}_{\rm s}^2(r_a, M_a; r, M; q)
-&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a)) \cdot \frac{{\rm BF}}{1 - {\rm BF}} 
+\mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
+&=N_{\rm s}^0(\delta_{\rm obs}, L(M\a)) \cdot \frac{{\rm BF}}{1 - {\rm BF}} 
 \cdot {1 \over \mathcal{A}(q,M\a)^3}\\
-&\times \delta \left(r_a-r\sqrt{ \left[{R(M_a)\over R(qM_a)}\right]^2 
-    {L(qM_a) 
-        \over L_{\rm sys}(M_a, q)} }\right)\delta\left(M_a-{M\over q}\right).
+&\times 
+	\delta \left[r_a-r\mathcal{B}(q,M\a)\right]
+	\delta\left(M\a-{M\over q}\right).
 \label{eq:mathcal_N_s_2}
@@
 One might worry in Eq.~\ref{eq:mathcal_N_s_2} that we opt to write 
-$\mathcal{N}\s^2 \propto \delta(M_a - M/q)$, rather than $\propto \delta(M_a q 
+$\mathcal{N}\s^2 \propto \delta(M\a - M/q)$, rather than $\propto \delta(M\a q 
 - M)$ or some other delta function with the same functional dependence, 
@@
 {\mathrm{BF}\over{1-\mathrm{BF}}} \int {\mathrm{d}q \over 
-    \mathcal{A}^4}\,f(q)\,\Gamma_1\left({r_a\over\mathcal{A}}, M\a\right),
+    \mathcal{A}^4}\,f(q)\,\Gamma_1\left({r_a\over\mathcal{A}}, M\a\right).
 \label{eq:n_det_1}
 \end{align}
-where
-\begin{equation}
-\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}.
-\end{equation}
 Finally,
@@
 n_{\rm det}^2(r\a, M\a)
+\notag
 &=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^2(r\a, M\a; r, M)
@@
 \int {q \mathrm{d}q \over 
-{\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma_2(r_a/\mathcal{B}, 
-qM\a)\,p_{\rm 
-    tra}(qM\a),
+{\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma_2\left({r_a\over\mathcal{B}}, 
+qM\a\right)\,p_{\rm 
+    tra}(qM\a).
 \label{eq:n_det_2}
 \end{align}
-where
-\begin{equation}
-\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
-            sys}(M\a, q)} }.
-\end{equation}
 
 \paragraph{General formula for apparent occurrence rate}
-Using the results above, the apparent rate density,
+Using the above results, the apparent rate density,
 \begin{align}
@@
 q^{-1/3} \right]	\right\}.
+\label{eq:final_formula}
 \end{align}
@@
 
+Noting the definition of $\mu$ in Eq.~\ref{eq:mu_general},
+Eq.~\ref{eq:final_formula} can also be expressed as
+\begin{align}
+\notag
+\notag
+\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)} \cdot
+   \left[ \Gamma_0(r\a, M\a)\phantom{\tilde \Gamma}\right.&\\
+   &\left.+\mu(\mathrm{BF}, M\a)\cdot
+   %\tilde\Gamma_1(r\a, M\a)
+   \left\langle {1 \over \mathcal{A}}\cdot\Gamma_1\left({r\a\over\mathcal{A}}, M\a\right)
+   +%\tilde\Gamma_2(r\a, M\a)
+   {q \over \mathcal{B}}\cdot\Gamma_2\left({r\a\over\mathcal{B}}, qM\a\right) \cdot {R(qM\a) \over R(M\a)}q^{-1/3}\right\rangle
+   \right],
+\end{align}
+where the angle brackets denote averaging over $f(q)/\mathcal{A}^3$. This form
+shows that the fraction $\mu$ and mass ratio distribution 
+$f(q)/\mathcal{A}^3$ of binaries {\it in the searchable volume} are enough to 
+describe the contributions from binaries to $\Gamma\a$.
+The fraction $\mu$ gives the relative contributions from singles and binaries,
+and $f(q)/\mathcal{A}^3$ weights the contributions from binaries with various 
+mass ratios.
+The apparent rate density at each mass ratio ({\it i.e.}, the terms in
+the angle brackets) is the rate density of systems that give the apparent
+$(r\a, M\a)$, corrected for the overestimated transit probability around
+secondaries.
+
 \newpage

### 2018-01-12 paper/main.tex
add RV bias note

@@
 were searchable to begin with is left for later interpretation.
-In spectroscopic follow-up of candidate transiting planets, the prevalence of 
+In spectroscopic follow-up of transiting planet candidates, the prevalence of 
 astrophysical false-positives may also lead to a tendency against confirming 
 transiting planets in binary systems.
+A separate observational bias is that the RV surveys typically observe 
+chromospherically ``quiet'' stars, which may bias their detection probability 
+high~\citep{bastien_radial_2014}.
 
@@
 %
-\item Near the ``break'' in the true rate distribution ($\approx 2r_\oplus$), 
-the fraction of detected planets with binary companions increases
-(Fig.~\ref{fig:frac_model_3}).
+\item Near the ``break'' in the rate distribution ($\approx 2r_\oplus$), 
+the fraction of detected planets with binary companions increases by 
+$\approx 5-10\%$ (Fig.~\ref{fig:frac_model_3}).
 \end{itemize}
@@
 \acknowledgements{
-It was a pleasure sharing discussions about this study with F. Dai and T. 
-Barclay.
+It was a pleasure sharing discussions about this study with T. Barclay, W. 
+Bhatti, and F. Dai.
 This work made use of NASA's Astrophysics Data System Bibliographic Services.

### 2018-01-30 paper/main.tex
incorporate JNW edits

@@
 %
-This study develops simplified models of signal-to-noise limited transit 
-surveys, in order to clarify the biases that stellar binarity introduces
-to occurrence rate measurements.
-We pay particular attention to dilution of observed planet radii, errors in 
-star counts, and treatment of detection efficiencies.
-Given a plausible set of assumptions, we derive a general formula 
-for the apparent rate density, which depends on the true 
-planet radius distribution, and also the relative numbers of planets 
-orbiting secondaries, primaries, and single stars.
-From this formalism, we suggest that for most of the observed radius 
-distribution (apparent planet radii $>2r_\oplus$), ignoring binarity 
-leads to errors in inferred occurrence rates at the $\lesssim 10\%$ level.
-One corollary is that binarity seems unlikely to strongly influence any 
-discrepancy between transit survey and RV survey hot Jupiter rates.
-The errors created by ignoring binarity at smaller apparent radii might be 
-larger: for instance, the absolute occurrence of Earth-sized planets could be 
-overestimated by $\lesssim 50\%$.
-Under our formalism, we also show that if high-resolution imaging reveals 
-stellar neighbors of detected planets, the planet is usually more likely to 
-orbit the primary. We explore how this statement depends on the
-apparent radius of the detected planet.
+Wide-field surveys for transiting planets, such as the NASA {\it Kepler}
+and {\it TESS} missions, are usually conducted without knowing which stars
+are actually binaries. Unresolved and unrecognized binary stars give rise to 
+systematic errors in planet occurrence rates, including misclassified planets 
+and miscounts in the number of searched stars. The individual errors can have 
+different signs, making it difficult to anticipate the net effect on planet 
+occurrence rates. Here we use simplified models of signal-to-noise limited 
+transit surveys to try and clarify the situation. We derive a formula for the 
+apparent occurrence rate density measured by an observer who falsely assumes 
+all stars are single. The formula depends on the binary fraction; the 
+mass function of the secondary stars; and the true occurrence of planets 
+around primaries, secondaries, and single stars. It also takes into account 
+the Malmquist bias by which binaries are over-represented in flux-limited 
+samples. Application of the formula to an idealized {\it Kepler}-like survey 
+shows that for planets larger than $2r_\oplus$, the net systematic error is of 
+order 10\%. For smaller planets the errors are potentially larger: the 
+occurrence of Earth-sized planets could be overestimated by as much as a 
+factor of two. One consequence is that unrecognized binaries cannot account 
+for the apparent discrepancy between the hot Jupiter occurrence rates measured 
+by transit and RV surveys. We also demonstrate that if high-resolution imaging 
+reveals a transit host star to be a binary, the planet is usually more likely 
+to orbit the primary star than the secondary star.
 %
@@
 
-A group of binarity-ignoring astronomers wants to measure the mean number of 
-planets of a certain type per star of a certain type.
-They perform a wide-field photometric search for planets that transit, and 
-discover all for which
-\begin{equation}
-\left(\frac{{\rm S}}{{\rm N}}\right)
-= ({\rm const}) \cdot \delta_{\rm obs} L_{\rm sys}^{1/2} d^{-1}
-> \left(\frac{{\rm S}}{{\rm N}}\right)_{\rm floor}.
+One of the goals of exoplanetary science is to establish how common,
+or rare, are planets of various types.  Knowledge of planet occurrence
+rates is helpful for inspiring and testing theories of planet
+formation, designing the next generation of planet-finding surveys,
+and simply satisfying our curiosity about other worlds.  One method
+for measuring occurrence rates is to monitor the brightnesses of many
+stars over a wide field, seeking evidence for planetary transits.
+Measuring occurrence rates using this method was the highest priority
+of the NASA {\it Kepler} mission.  Great strides have been made in the
+analysis of {\it Kepler} data, including
+progress toward the goal of determining the fraction of
+Sun-like stars that harbor Earth-like 
+planets~\citep{
+    youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
+    foreman-mackey_exoplanet_2014,burke_terrestrial_2015}
+
+A lingering concern in occurrence rate studies is that in most cases,
+investigators have assumed that all of the sources of light that were
+monitored are single 
+stars~\citep[\textit{e.g.},][]{
+    howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,
+    dressing_occurrence_2015,burke_terrestrial_2015}. In reality many of them 
+are unresolved multiple-star systems, especially binaries.  Unrecognized
+binaries cause numerous systematic errors in the planetary occurrence
+rates.  For example, when there is a transiting planet around a star
+in a binary, the additive constant light from the second star reduces
+the fractional loss of light due to the planet.  
+This ``flux dilution'' makes transit signals harder to detect and lowers the 
+number of detections.  On the other hand, in a binary there two opportunities
+to detect transiting planets, which could increase the overall number
+of detections.
+
+At the outset of this study it was not clear to us whether the neglect
+of binaries was a serious issue at all, or even whether the net effect
+of all the errors is positive or negative.  The goal of this study was
+to clarify the various sources of error and provide a framework for
+dealing with these issues.  In this spirit, most of our models are
+idealized and analytic, and we do not attempt a detailed correction of
+the results from {\it Kepler} or any other real transit survey.
+However we can estimate the order of magnitude of the effects,
+assuming the survey is signal-to-noise limited and given a model for
+the true planet occurrence rate.
+
+This paper is organized as follows.  The next section enumerates the
+various errors that arise from unrecognized binaries.  Then, in 
+Section~\ref{sec:simplest}, we develop an idealized model of a transit
+survey in which all planets 
+have identical properties, and all stars are identical
+except that some fraction are in binary systems.  This simple 
+model motivates the
+derivation of a general formula, given in
+Section~\ref{sec:general_formula}, that allows for more realistic
+stellar and planetary populations.  We use this formula in
+Section~\ref{sec:more_complicated} to explore more complicated but
+nevertheless still analytic models.  In Section~\ref{sec:discussion}
+we discuss the errors due to unrecognized binaries for some specific
+cases of current interest: the occurrence of Earth-like planets; the
+apparent discrepancy between hot-Jupiter occurrence rates in different
+surveys; and the shape of the ``evaporation valley'' in the radius
+distribution of planets that was brought to light by
+\citet{fulton_california-_2017}.  We review all the results in
+Section~\ref{sec:conclusion}.
+
+\section{Understanding the errors}
+\label{sec:concept}
+
+Imagine a group of astronomers that wants to measure the mean number of
+planets of a certain type per star of a certain type.  They perform a
+wide-field photometric search for planets that transit, and discover
+all for which
+\begin{equation}
+\frac{\delta_{\rm obs}}{\sigma}
+  = ({\rm constant}) \cdot \delta_{\rm obs} L_{\rm sys}^{1/2} d^{-1}
+> \left(\frac{{\rm S}}{{\rm N}}\right)_{\rm min}.
 \label{eq:S_N_thresh}
 \end{equation}
-The observed transit depth per unit stellar flux $\delta_{\rm obs}$ 
-constitutes the signal, ${\rm S}$.
-The survey is shot-noise dominated, and the fractional photon noise 
-${\rm N}$ scales as the inverse root of the photon flux received from any 
-stellar system, ${\rm N} \propto (L_{\rm sys}/d^2)^{-1/2}$, for $L_{\rm sys}$ 
-the system luminosity and $d$ its distance.
-The solid angle coverage, telescope area, and survey duration are part of the 
-``const'' term of Eq.~\ref{eq:S_N_thresh}. The transit duration also 
-affects detectability, but we omit it in this work for brevity.
-
-To compute an occurrence, at every planetary and stellar property the 
-astronomers choose the stars around which the planets of interest appeared to 
-be searchable.
-Correcting for the geometric transit probability $p_{\rm tra}$, they report an 
-apparent rate density,
-\begin{equation}
-\Gamma\a(\pp\a, \ps\a) = \frac{n_{\rm det}(\pp\a, \ps\a)}{N_{\rm s,a}(\pp\a, 
-    \ps\a)} \times \frac{1}{p_{\rm tra}(\pp\a, \ps\a)}.
-\label{eq:defn_apparent_rate_density}
-\end{equation}
-where $\pp\a$, $\ps\a$ are the apparent planetary and stellar parameters.
-The quantity $N_{\rm s,a}(\pp\a, \ps\a)$ is the number of unresolved 
-point-sources on the sky that appear to be searchable, and
-$n_{\rm det}(\pp\a, \ps\a)$ is the number of detected planets, per unit 
-$\pp\a$ and $\ps\a$.
-
-There are many potential pitfalls.  Some genuine transit signals can be missed
-by the detection pipeline.  Some apparent transit signals are spurious, from
-noise fluctuations, failures of `detrending', or instrumental effects.  Stars
-and planets can be misclassified due to statistical and systematic errors in
-the measurements of their properties.  Poor angular resolution causes false
-positives due to blends with background eclipsing binaries. {\it Et cetera}.
-
-Here we focus on problems that arise from the fact that many stars exist in 
-multiple star systems.
-For simplicity, we consider only binaries, and we assume that they are all 
-bound and spatially unresolved.
-
-An immediate complication is that, due to dynamical stability or some 
-aspect of planet formation, the occurrence rate of planets might differ 
-between binary and single-star systems.
-In an observed sample of stars that contains both singles and binaries, the 
-detected planets would then be drawn from different intrinsic 
-distributions for the occurrence rates in single star systems, 
-about primaries, and about secondaries~\citep[{\it 
-e.g.},][]{wang_occurrence_2015}.
-
-Outside of astrophysical differences, every term in 
-Eq.~\ref{eq:defn_apparent_rate_density} is observationally-biased.
-There are errors in $n_{\rm det}(\pp\a,\ps\a)$ due to misclassification of 
-both planet radii and stellar properties.
-There are errors in $N_{{\rm s,a}}(\pp\a,\ps\a)$ because a 
-searchable point on the sky might be two searchable stars.
-Finally, there are errors in $p_{\rm tra}(\pp\a,\ps\a)$ because stars in 
-binaries may have different masses and radii than assumed in the single-star 
-case.
-
-Correcting for binarity's observational biases is non-trivial.
-For instance, in counting the number of searchable stars, even after realizing 
-that binaries count as two stars, one must note that the multiplicity fraction 
-of stars that are searchable for a given observed transit depth is greater 
-than the multiplicity fraction in a volume limited sample.
-This is the familiar Malmquist bias: at a fixed $\delta_{\rm obs}$, binaries 
-are searchable out to larger distances than single stars because they are more 
-luminous.
-A separate effect is that the apparent radii assigned to planets in binaries 
-will typically be smaller than the true radii.
-Correcting for ``radius dilution'' requires knowing both the amount flux 
-contributed by each source in a photometric aperture, and which star the 
-planet orbits.
-
-To gain intuition for the many observational biases at play,
-we consider a set of idealized transit surveys.
-First, we discuss the simplest possible cases (Sec.~\ref{sec:simplest}), in 
-which all planets have identical properties, and all stars have identical 
-properties except that some are in binary systems.
-We generalize these thought-experiments in 
-Sec.~\ref{sec:general_formula} to allow for realistic stellar populations with 
-arbitrary occurrence rate distributions.
-Sec.~\ref{sec:more_complicated} explores the implications for
-(a) measurements of $\eta_\oplus$,
-(b) the ``hot Jupiter rate discrepancy'', and 
-(c) \citet{fulton_california-_2017}'s recently discovered ``valley''.
-We discuss what our models suggest about the importance of binarity's biases 
-in Sec.~\ref{sec:discussion}, and conclude in Sec.~\ref{sec:conclusion}.
+Here the signal S is the observed transit depth $\delta_{\rm obs}$, in
+units of relative flux.
+%LB: we don't introduce r or R because they are system-specific.
+%For single stars, $\delta_{\rm obs} \approx (r/R)^2$; for binaries,
+%flux dilution $\mathcal{D}$ lowers the observed depth to
+%$\delta_{\rm obs} \approx \mathcal{D} (r/R)^2$. 
+The noise N is the uncertainty in the
+determination of the flux ratio of the star inside and outside of
+transits.  Throughout this paper we will assume the photometric
+uncertainty to scale as the inverse square root of the number of
+photons collected from the source, {\it i.e.}, the dependence on
+stellar properties is $\sigma \propto (L_{\rm sys}/d^2)^{-1/2}$, where
+$L_{\rm sys}$ is the luminosity of the stellar system and $d$ is its
+distance from Earth.
+% The solid angle coverage, telescope area, and
+% survey duration are in the ``constant'' term of
+% Equation~\ref{eq:S_N_thresh}.  The transit duration also affects
+% detectability, but we omit it in this work for brevity.
+
+The astronomers then assume that all stars are single.  In particular
+they do not have accurate enough parallaxes to tell that some of the
+stars are apparently overluminous. 
+They want to compute the number of planets with size $r$ per star of mass $M$.
+If the total number of such stars for which the planets could be detected
+($N_\star$) and the number of detected planets ($N_{\rm det}$) are both 
+large, then the astronomers' estimate for the occurrence rate ($\Lambda$) is 
+simply
+\begin{equation}
+\Lambda(r,M) = \frac{N_{\rm det}(r,M)}{N_\star(r,M)}
+                    \times \frac{1}{p_{\rm tra}(r,M)},
+\label{eq:occ_rate_simple}
+\end{equation}
+where $p_{\rm tra}$ is the geometric transit probability, needed to
+account for the fact that most planetary orbits are not aligned close
+enough with our line of sight to produce transits.
+
+There are many potential pitfalls in this calculation.  Some genuine
+transit signals are missed even if they formally exceed the
+signal-to-noise threshold, because of the probabilistic nature of
+transit detection.  Planets can be misclassified due to statistical
+and systematic errors in the catalogued properties of the stars.  Some
+apparent transit signals are spurious, arising from noise fluctuations
+or failures of ``detrending'' the astrophysical or instrumental
+variations in the photometric signal.  Poor angular resolution leads
+to blends between eclipsing binary stars and other stars along nearly
+the same line of sight, producing signals that mimic those of
+transiting planets.
+
+We will focus exclusively on the subset of problems that arise from
+the fact that many stars exist in gravitationally bound binary
+systems.  Even with this narrow focus, there are numerous sources of
+error.  All three of the quantities in
+Equation~\ref{eq:occ_rate_simple} are subject to
+observational bias:
+\begin{enumerate}
+%    
+    \item The number of detections, $N_{\det}$, is actually the number of 
+    detected planets that {\it appear} to have size $r$, orbiting stars that 
+    {\it appear} to have mass $M$.
+    Whenever the planet-hosting star is part of a binary,
+%    
+    \begin{itemize}
+        \item the planet's size will be misclassified because of the reduction
+        in the amplitude of the photometric signal;
+%        
+        \item the host star's properties could be misclassified because its 
+        light is combined with a second star of a different spectral type.
+%        
+    \end{itemize}
+%    
+    \item The apparent number of stars that were searched, $N_\star$,
+    is biased
+%    
+    \begin{itemize}
+%        
+        \item toward lower values, because it does not include all of the
+        secondary stars that were searched for transiting planets.
+%        
+        \item toward higher values, because some of the stars that
+        appeared to be suitably small and bright to detect the desired
+        type of planet are in fact binaries for which the amplitude of
+        the photometric signal would be reduced to an undetectable
+        level.
+%        
+    \end{itemize}
+%    
+    \item The transit probability $p_{\rm tra}$, which scales with the
+    stellar mean density as $\rho^{-1/3}$, is biased because the
+    planet-hosting star could be misclassified.
+%    
+\end{enumerate}
+
+Two other problems that may arise are not represented in
+Equation~\ref{eq:occ_rate_simple}.  One is astrophysical:
+the true occurrence rate of the desired type of planet may depend on
+whether the host is a single star, the primary star of a binary, or
+the secondary star of a binary.  Such differences could be caused by
+the requirement for long-term dynamical stability, or differences in
+the planet formation process.  When the search sample includes both
+singles and binaries, the detected planets are thereby drawn from
+different occurrence distributions~\citep[see,
+{\it e.g.},][]{wang_occurrence_2015}.
+
+The other problem is an observational effect.  Even after the
+astronomers learn about binaries and attempt to correct for their
+presence, they must realize that the ratio of binaries to single stars
+in the sample will differ from that in a volume-limited sample due to
+a type of Malmquist bias.  Binaries have a higher total luminosity
+than either the primary or secondary star would have on its own.  This
+means that the binaries are searchable for transit signals of a given
+amplitude at greater distances from the Earth.  The binaries in a
+sample of apparently searchable stars are therefore drawn from a
+larger search volume than the single stars.
+
+% JNW: Let's remember, when discussing Kepler, to point out that it's
+% not really a SNR or flux limited survey, because of the
+% preselection. This would need to be dealt with in a realistic
+% treatment.
+
+% JNW: Let's also remember to say somewhere that we do not deal with
+% period distributions none of these effects mess up the period.
+
+Planet occurrence rates are often presented as two-dimensional density
+functions in the space of planet radius and orbital period.
+Thankfully none of the errors we have enumerated lead to errors in the
+period distribution.  When more than one transit is detected (as is
+usually required by the surveyors), the orbital periods can be
+measured without ambiguity regardless of whether the host star is
+single or one member of a binary.  Hence in what follows, we focus on
+the radius distribution and assume the periods are measured without
+significant uncertainty.
+
+Given all of the confusing and opposing sources of error, we will
+proceed in stages. We will start from a barebones model in which
+everything can be written down on the back of a napkin, and build up
+to an analytic model allowing for generality in the distribution of
+the binaries and the planets they host.  We consider only the
+corrections to the occurrence as a function of planetary radius, and
+not the orbital period (the other key variable in transit studies),
+because when multiple transits are detected the period can be directly
+measured regardless of whether the host star is single or part of a
+binary.
 
@@
 
-\section{The simplest possible transit survey models}
+\section{Simple models}
 \label{sec:simplest}
 
-\subsection{Twin binaries, identical stars, identical planets}
+\subsection{One type of star, one type of planet}
 \label{sec:model_1}
+
+Since the effects of binarity are most pronounced when the two
+components are similar, we begin by considering a universe in which
+all stars are identical, with mass $M$, radius $R$, and luminosity
+$L$.  Some fraction of them exist in twin binaries.
+All planets have size $r\p$.
+Our goal is to compare the occurrence inferred by observers who
+ignore binarity with the true occurrence in single star systems.
+
+To clarify our terminology, we define an ``apparent planet radius'', $r\a$, as 
+the radius that one would infer from a transit signal under the assumption 
+that the host star is single.
+The observed transit depth is given by the ratio of the apparent planet
+radius and the apparent stellar radius, $R\a$:
+\begin{equation}
+\delta_{\rm obs}
+= \left(\frac{r\a}{R\a}\right)^2
+= \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over L_{\rm 
+        sys}},
+\label{eq:delta_obs_general} 
+\end{equation}
+where $r$ is the planet radius, $R_{\rm host}$ ($L_{\rm host}$) is the 
+host star's radius (luminosity), and $L_{\rm sys}$ is the 
+entire system's luminosity.
+For the example at hand, $R_{\rm host} = R$, since all stars have the same 
+size. In single star systems we have $r=r\a=r\p$. In twin binaries, 
+$r\a=r\p/\sqrt{2}$, since $L_{\rm sys}=2L$.
+
+We can now understand that the observers are unwittingly
+reporting an {\it apparent} occurrence rate $\Lambda\a(r\a)$ as
+a function of apparent radius.
+The apparent occurrence rate is the same as the {\it true} occurrence rate for 
+transit signals of 
+amplitude $\delta_{\rm obs} = (r\a/R\a)^2$, \textit{i.e.}, the number of 
+detections ($N_{\rm det}$) of signals of amplitude $\delta_{\rm obs}$, divided 
+by the number of sources $N_\star$ from which such a signal could be detected.
+
+Finally, it is helpful to introduce an apparent rate density 
+$\Gamma\a$, the average number of planets per star per unit apparent planet 
+radius. Analogous to Equation~\ref{eq:occ_rate_simple},  
+\begin{equation}
+\Gamma\a(r\a) = \frac{n_{\rm det}(r\a)}{N_\star(r\a)}
+\times \frac{1}{p_{\rm tra}(r\a)},
+\label{eq:apparent_rate_density}
+\end{equation}
+where $n_{\rm det}={\rm d}N_{\rm det}/{\rm d}r\a$ is the number  
+of detected planets, per unit $r\a$, with apparent radius $r\a$.
+In Equation~\ref{eq:apparent_rate_density}, we neglect the dependence on 
+stellar mass since all stars in this model have the same properties.
+
+To compute the number of detected planets, we consider the volumes within 
+which a given signal could be detected. At a fixed signal-to-noise floor, 
+there is a maximum searchable 
+distance~\citep{pepper_using_2003,pepper_searching_2005}.
+From Equation~\ref{eq:S_N_thresh}, this maximum searchable distance scales as
+\begin{equation}
+d \propto \delta_{\rm obs} \cdot L_{\rm 
+    sys}^{1/2}.
+\end{equation}
+Assuming that stars are uniformly distributed in space, the number 
+of searchable stars $N_\star$ is then proportional to
+\begin{equation}
+N_\star \propto n \delta_{\rm obs}^3 L_{\rm 
+    sys}^{3/2},
+\label{eq:N_searchable_prop}
+\end{equation}
+where $n$ is the number per unit volume of {\it e.g.}, single star, or binary 
+systems.
+We neglect the dependence of $n$ on stellar type.
 
@@
     \caption{
-        Cartoon of the searchable volumes for single stars ({\it left}), and 
-        twin binaries ({\it right}).
-        This model assumes all stars have equal mass and luminosity, and 
-        all planets have the same true radius $r=r\p$.
+        Searchable volumes for single stars ({\it left}) and 
+        twin binaries ({\it right}), assuming that all stars have the 
+        same mass, radius, and luminosity, and that all planets have the same 
+        radius $r=r\p$.
         {\it Top:} At an apparent radius $r\a=r\p$,
@@
         $r\a=r\p$.
-        {\it Middle:} At an apparent radius $r\a=r\p/\sqrt{2}$, the 
+        {\it Middle:} At $r\a=r\p/\sqrt{2}$, the 
         maximum searchable distances are half those at $r\a=r\p$. 
@@
 
-Since the effects of binarity are most pronounced when the two components are 
-similar, we begin by considering a universe in which all planets are 
-identical, and all stars are identical except that some fraction of them exist 
-in binaries. The goal of this thought experiment is to compare the occurrence 
-inferred by observers ignoring binarity with the true occurrence in single 
-star systems.
-
-First, what are the possible apparent radii of detected planets?
-If the true planet radius is $r=r\p$, then planets in singles will be 
-detected with identical apparent radii: $r\a = r\p$.
-Conversely, all detections in twin binaries will have apparent radii 
-$r\a=r\p/\sqrt{2}$, because they are diluted.
-For an unresolved point-source,
-\begin{equation}
-\delta_{\rm obs}
-= \left(\frac{r\a}{R\a}\right)^2
-= \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over L_{\rm 
-        sys}(M_1, q)},
-\label{eq:delta_obs_general} 
-\end{equation}
-where $R_{\rm host}$ ($L_{\rm host}$) is the planet-host's stellar radius 
-(luminosity), $R\a$ is the apparent stellar radius, $L_{\rm sys}=L_1+L_2 = 
-L(M_1) + L(qM_1)$ is the system luminosity, and $q=M_2/M_1$ is the binary mass 
-ratio.
-We assume that the stellar radius and luminosity are uniquely related to the 
-stellar mass.
-The observers, with no a priori knowledge of the distance to a system, would 
-measure a flux, and estimate a stellar mass $M\a=M_1$, a stellar 
-radius $R\a = R(M\a)$, and an under-estimated system luminosity of $L_{\rm 
-sys,a}(M\a) = L(M\a)$.
-
-The planets will be detected if and only if their host stars are searchable.
-For a fixed signal-to-noise floor, there is a maximum searchable 
-distance~\citep{pepper_using_2003,pepper_searching_2005}.
-From Eq.~\ref{eq:S_N_thresh}, this maximum searchable distance scales as
-\begin{equation}
-d(\delta_{\rm obs}, L_{\rm sys}) \propto \delta_{\rm obs} \cdot L_{\rm 
-    sys}^{1/2}.
-\end{equation}
-Assuming that stars are uniformly distributed in space, the number 
-of searchable stars $N\s$ is then proportional to
-\begin{equation}
-N\s(\delta_{\rm obs}, L_{\rm sys}) \propto n \delta_{\rm obs}^3 L_{\rm 
-    sys}^{3/2},
-\label{eq:N_searchable_prop}
-\end{equation}
-where $n$ is the number per unit volume of {\it e.g.}, single star, or binary 
-systems.
-We neglect the dependence of $n$ on stellar type.
-
-The searchable volumes for our thought experiment are illustrated 
-in Fig.~\ref{fig:model_1_volumes}.
+The searchable volumes for this example are illustrated in 
+Figure~\ref{fig:model_1_volumes}.
 At an apparent radius equal to the true radius ($r\a=r\p$), single stars 
@@
 Binaries with $r\a=r\p$ are also searchable, out to $\sqrt{2}d_0$. 
-However, in this model no such systems exist; all planets in twin binaries 
+However, in this example no such systems exist; all planets in twin binaries 
 have true radii $r=r\p$, and so are observed with apparent radii 
@@
 At an apparent radius of $r\a=r\p/\sqrt{2}$, there could also be planets with 
-true radii $r=r\p/\sqrt{2}$ orbiting singles~---~however none of these exist 
+true radii $r=r\p/\sqrt{2}$ orbiting singles, but there are no such systems 
 in this model.
@@
 How many planets are detected?
-If we assume that there are $N\s^0(r\a)$ singles that are searchable for 
+If we assume that there are $N_\star^0(r\a)$ singles that are searchable for 
 planets with $r\a$, and that there are $Z_0$ planets per single, then 
@@
 \begin{equation}
-n_{\rm det}^0(r\a) = N\s^0(r\a) Z_0 p_{\rm tra} \cdot \delta(r\a - r_p)
-\end{equation}
-planet detections (per unit $r\a$), where $\delta$ is the Dirac delta function.
+n_{\rm det}^0(r\a) = N_\star^0(r\a) Z_0 p_{\rm tra} \cdot \delta(r\a - r_p)
+\end{equation}
+planet detections (per unit $r\a$), for $\delta$ the Dirac delta function.
 
 We can write similar equations for the binaries.
-First though, we define a ratio $\mu \equiv N\s^{\rm b}(r\a) / N\s^0(r\a)$ 
+First though, we define a ratio $\mu \equiv N_\star^{\rm b}(r\a) / 
+N_\star^0(r\a)$ 
 between the number of searchable binary systems and the number of searchable 
 singles at any $r\a$.
-This quantity is useful because although $N\s^{\rm b}$ and $N\s^0$ vary
+This quantity is useful because although $N_\star^{\rm b}$ and $N_\star^0$ vary
 as a function of the observed transit depth, $\mu$ remains fixed.
@@
 n_{\rm det}^1(r\a) =
-\mu N\s^0(r\a) Z_1 p_{\rm tra}
+\mu N_\star^0(r\a) Z_1 p_{\rm tra}
 \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right),
@@
 n_{\rm det}^2(r\a) = 
-\mu N\s^0(r\a) Z_2 p_{\rm tra}
+\mu N_\star^0(r\a) Z_2 p_{\rm tra}
 \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right),
@@
 planets per secondary, and $p_{\rm tra}$ is the same for identical stars.
-In the case of twin binaries, Eq.~\ref{eq:N_searchable_prop} gives $\mu = 
-2^{3/2} n_{\rm b}/n_{\rm s} = 2^{3/2} {\rm BF}/(1-{\rm BF})$, for ${\rm BF}$ 
-the binary fraction\footnote{The binary fraction is the fraction of systems in 
-a volume-limited sample that are binary. It is equivalent to the multiplicity 
-fraction if there are no triple, quadruple, or higher order multiples.
-}.
+For twin binaries, Equation~\ref{eq:N_searchable_prop} gives $\mu = 
+2^{3/2} n_{\rm b}/n_{\rm s}$, where $n_{\rm b}$ is the number density of 
+binaries in a volume-limited sample.
 
@@
 is the number of unresolved point-sources on sky that the observer thinks are 
-searchable, $N_{\rm s,a}$.
-Assuming that the apparent stellar radius is fixed, then given the 
-apparent planet radius $r\a$,
-\begin{equation}
-N_{\rm s,a}(r\a) = N\s^0(r\a) \times (1 + \mu)
+searchable, $N_\star$.
+From the definition of $\mu$,
+\begin{equation}
+N_\star(r\a) = N_\star^0(r\a) \times (1 + \mu)
 \label{eq:apparentlysearchable_to_searchable}
@@
 From the discussion above, it should be clear that there are in fact
-$N\s^0(r\a)\times (1 + 2\mu)$ searchable stars at any given $r\a$; the 
+$N_\star^0(r\a)\times (1 + 2\mu)$ searchable stars at any given $r\a$; the 
 observers are under-counting.
 
-Using Eq.~\ref{eq:defn_apparent_rate_density}, the apparent rate density 
-computed without considering binarity is
+Using Equation~\ref{eq:apparent_rate_density}, the apparent rate density 
+computed when ignoring binarity is
 \begin{align}
@@
 The number of searchable singles at a given apparent radius, 
-$N\s^0(r\a)$, makes no appearance.
-The observer's errors in Eq.~\ref{eq:model_1_apparent_rate_density} are 
-(A) under-counting the number of searchable stars at any apparent radius;
-and
-(B) inferring radii in binary systems that are all $\sqrt{2}$ too small.
+$N_\star^0(r\a)$, makes no appearance.
+The observer has erred in Equation~\ref{eq:model_1_apparent_rate_density} by 
+under-counting the number of searchable stars at any apparent radius, and by
+inferring incorrect planet radii in binary systems.
 
@@
     \caption{
-        Inferred occurrence rates over $0.01r_\oplus$ bins in planet 
-        radius, for a model with identical stars, identical planets, and twin 
-        binaries (same as Fig.~\ref{fig:model_1_volumes}).
-        We assume a twin binary fraction of ${\rm BF}=0.1$, and that all 
-        stars (single, primary, and secondary) host planets at equal 
+        Apparent occurrence rate $\Lambda\a$, and occurrence rate for singles 
+        $\Lambda_0$, for a model with one type of star, one type of planet, 
+        and twin binaries (same as Figure~\ref{fig:model_1_volumes}).
+        We assume a twin binary fraction of $0.1$, and that
+        single, primary, and secondary stars host planets at equal 
         rates.
@@
         will have apparent radii $r\a = r\p/\sqrt{2}$;
-        Eq.~\ref{eq:model_1_apparent_rate_density} gives the normalizations.
-        The rate and rate density are related by $\Lambda|_a^b = 
-        \int_{a}^{b}\Gamma\,{\rm d}r$.
+        Equation~\ref{eq:model_1_apparent_rate_density} gives the 
+        normalizations.
     }
@@
 
-To assess the severity of these errors, we need to assume a binary fraction, 
-and to know the true number of planets per single, primary, and secondary star 
-($Z_0,Z_1,$ and $Z_2$).
-For the former,
-\citet{raghavan_survey_2010} found a multiplicity 
-fraction of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$, 
-which we take as a binary fraction. 
-``Twin binaries'' are perhaps 10-20\% of the binaries in a volume-limited 
-sample, depending on how ``twin'' is defined.
-Thus a representative twin binary fraction for this model is ${\rm BF}\approx 
-0.05$-$0.1$. 
-For the true number of planets per star, we take $Z_0=Z_1=Z_2=0.5$, and plot 
-the resulting occurrence rates as a function of planet radius in 
-Fig.~\ref{fig:occ_rate_model_1}.
-
-Our point for comparison is the rate density for single stars,
-\begin{equation}
-\Gamma_0(r) = Z_0 \cdot \delta(r-r\p).
-\end{equation}
-We define a rate density ``correction factor'', $X_\Gamma$, as the ratio 
-of the apparent to single star rate density,
-\begin{equation}
-X_\Gamma(r) \equiv \left. \frac{\Gamma_a(r\a)}{\Gamma_0(r)} \right|_{r\a 
-    \rightarrow r}.
-\end{equation}
-Continuing in the assumption that the number of planets per single, primary, 
-and secondary star are equal, then the rate density 
-correction factor at the true planet radius is $1/(1+\mu)$.
-This yields a correction of 0.76 if ${\rm BF}=0.1$, and 0.87 if ${\rm 
-    BF}=0.05$. Rephrasing the result, if the twin binary fraction were 
-$(2^{3/2}+1)^{-1}\approx 0.26$, then the apparent rate at $r\a=r\p$ would be 
-half the true rate at $r=r\p$.
-For most stellar types, the twin binary fraction is not that high.
+To assess the severity of these errors, we must assume both a binary fraction, 
+and also the true number of planets per single, primary, and secondary star 
+($Z_0,Z_1,Z_2$).
+For the former,~\citet{raghavan_survey_2010} found a multiplicity 
+fraction of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$.
+By multiplicity fraction, they meant ``fraction of systems in a volume-limited 
+sample that are multiple'', which we simplistically take to be fraction of 
+systems in a volume-limited sample that are binaries:
+\begin{equation}
+{\rm binary\ fraction} \equiv \frac{n_b}{n_s + n_b} = 0.44,
+\end{equation}
+Of course not all of these are binaries are close to being ``twin'' binaries 
+as we have assumed in our simple calculation.
+Perhaps only a tenth of them have pairs of stars close enough
+in their basic properties to produce errors as significant as those
+we have been considering.  Thus, an appropriate estimate
+for the binary fraction is of order $0.05$.
+The ratio of the apparent to single star rate densities,
+\begin{equation}
+X_\Gamma(r) \equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} \right|_{r\a 
+    \rightarrow r},
+\end{equation}
+can then be thought of as a ``correction factor''.
+At the true planet radius, $X_\Gamma(r\p)=1/(1+\mu)$.
+This yields a correction $X_\Gamma$ of 0.87~(0.76) if the binary fraction is 
+0.05~(0.10).
+All together the various effects produce biases of order 10\% in the
+occurrence rates.  We will see that this level of error is characteristic
+of many of our more complicated models, as well.
 
@@
 case, $Z_0=Z_1$, and $Z_2=0$. The correction to the rate density at the true 
-planet radius becomes $(1+2\mu)/(1+\mu)^2$.
-This evaluates to 0.94 if ${\rm BF}=0.1$, and 0.98 if ${\rm BF}=0.05$.
-While it seems unlikely that secondaries are planet-less, 
-the fact that $\Gamma\a/\Gamma$ is sensitive to the relative number 
+planet radius becomes $X_\Gamma(r\p) = (1+2\mu)/(1+\mu)^2$.
+This gives a correction of 0.98~(0.94) if the binary fraction is 0.05~(0.10).
+While the secondaries certainly do have planets, 
+the fact that $\Gamma\a/\Gamma_0$ is sensitive to the relative number 
 of planets per single, primary, and secondary will become important as we 
@@
 
-\subsection{Twin binaries, identical stars, two planet sizes}
+\subsection{One type of star, two types of planets}
 
@@
 Consider now a universe that is the same in every respect to that of 
-Sec.~\ref{sec:model_1}, except that half of planets have true radii $r\p$, 
+Section~\ref{sec:model_1}, except that half of planets have true radii $r\p$, 
 while the other half have true radii $r\p/\sqrt{2}$.
@@
 
-Following an identical line of reasoning as in Sec.~\ref{sec:model_1}, the 
+Following an identical line of reasoning as in Section~\ref{sec:model_1}, the 
 apparent rate density can be written
@@
 Both populations are detected out to the same maximum searchable distance.
-Just as with Eq.~\ref{eq:apparentlysearchable_to_searchable}, we will have a 
-cancellation of $N\s^0(r\a)$ terms, leaving only the $\mu$ weights.
+Just as with Equation~\ref{eq:apparentlysearchable_to_searchable}, we benefit 
+from a cancellation of $N_\star^0(r\a)$ terms, leaving only the $\mu$ weights.
 
@@
 
-To generalize the procedure of Sec.~\ref{sec:simplest}, we consider an 
+To generalize the procedure of Section~\ref{sec:simplest}, we consider an 
 SNR-limited transit survey in which the singles and primaries can have 
@@
 
-A derivation of Eq.~\ref{eq:general_Gamma_a} is given in the 
+A derivation of Equation~\ref{eq:general_Gamma_a} is given in the 
 \hyperref[sec:appendix]{Appendix}; its qualitative features are as follows.
@@
 obs}\cdot [L(M\a)+L(qM\a)]^{1/2}$.
-Applying Eq.~\ref{eq:N_searchable_prop},
+Applying Equation~\ref{eq:N_searchable_prop},
 \begin{equation}
 \mu({\rm BF},M\a) = 
-\frac{N\s^{\rm b}(r_a)}{N_s^0(r\a)}=
+\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
 \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
@@
         binary stars, in which the underlying volume-limited distribution is 
-        uniform, qualitatively similar to {\it e.g.}, 
-        \citet{raghavan_survey_2010}'s Fig.~16.
+        uniform, qualitatively similar to
+        Figure~16 of \citet{raghavan_survey_2010}.
         At a given observed transit depth, the searchable binaries in a 
@@
 We show this magnitude-limited mass ratio distribution for the $\beta=0$ case 
-in Fig.~\ref{fig:q_distribn_mag_limited}.
+in Figure~\ref{fig:q_distribn_mag_limited}.
 In Monte Carlo simulations of transit surveys, it is 
@@
 
-\section{More complicated transit survey models}
+\section{Realistic Star and Planet Distributions}
 \label{sec:more_complicated}
 The following section applies our general equation for the apparent rate 
-density (Eq.~\ref{eq:general_Gamma_a}) to study binarity's effects in regimes 
+density (Equation~\ref{eq:general_Gamma_a}) to study binarity's effects in 
+regimes 
 of observational interest.
@@
 The resulting apparent rate density is quite similar to that of the twin 
-binary, fixed-planet case (Eq.~\ref{eq:model_1_apparent_rate_density}), except 
+binary, fixed-planet case (Equation~\ref{eq:model_1_apparent_rate_density}), 
+except 
 for a slightly different radius dependence and normalization:
@@
 \end{equation}
-As in Sec.~\ref{sec:model_1}, $\mu = 2^{3/2} {\rm BF}/(1-{\rm BF})$.
+As in Section~\ref{sec:model_1}, $\mu = 2^{3/2} {\rm BF}/(1-{\rm BF})$.
 If the $Z_i$'s are equal, the ``correction factor'' relative to the rate 
@@
 models for hot Jupiter occurrence rates that we will discuss in 
-Sec.~\ref{sec:further_models}.
+Section~\ref{sec:further_models}.
 If the assumptions behind this model (listed in 
-Sec.~\ref{sec:general_formula}) are at all applicable in real transit surveys, 
+Section~\ref{sec:general_formula}) are at all applicable in real transit surveys, 
 this suggests that for $2r_\oplus \lesssim r\a \lesssim 17r_\oplus$, 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Varying binaries}
+\subsubsection{Binaries with power law mass ratio distribution}
 \label{sub:powerlaw_varying_binaries}
@@
 $f(q) = q^\beta/\mathcal{N}_q$, for $\mathcal{N}_q$ the normalization.
-This changes $\mu$ (Eq.~\ref{eq:mu_general} simplifies to 
-Eq.~\ref{eq:mu_power_laws}).
+This changes $\mu$ (Equation~\ref{eq:mu_general} simplifies to 
+Equation~\ref{eq:mu_power_laws}).
 It may also affect the rate density, which could be a function of the 
@@
 We are mostly interested in the apparent rate density's radius dependence.
-Marginalizing Eq.~\ref{eq:general_Gamma_a} over apparent stellar mass, we find
+Marginalizing Equation~\ref{eq:general_Gamma_a} over apparent stellar mass, we 
+find
 that when $Z_0=Z_1=Z_2$,
@@
 For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the 
-summed integrals in Eq.~\ref{eq:powerlaw_vary_binary} give $(\ldots)\approx 
+summed integrals in Equation~\ref{eq:powerlaw_vary_binary} give 
+$(\ldots)\approx 
 1.50249$. %171211_model_integrals.nb
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fixed primaries, varying secondaries, broken power-law planets}
+\subsection{Varying stars; broken power-law planet radius distribution}
 \label{sec:model_3}
@@
     \caption{
-        {\it Left:} rate density and {\it right:} rate (over $0.5r_\oplus$ 
-        bins) as a function of planet radius for the distribution specified by 
-        Eq.~\ref{eq:model3_radius_distribution}. 
-        This model assumes that the true properties of all the singles and 
-        primaries are known to the observer, and that the volume-limited mass 
-        ratios of secondaries are drawn from a uniform distribution. We use an 
-        arbitrary normalization of $Z_0=Z_1=0.5$ throughout.
+        {\it Left:} apparent rate density ($\Gamma\a$) and single star rate 
+        density ($\Gamma_0$). {\it Right:} apparent occurrence rate 
+        ($\Lambda\a$) and single star occurrence rate ($\Lambda_0$), over 
+        $0.5r_\oplus$ bins.
+        The true planet radius distribution is specified by 
+        Equation~\ref{eq:model3_radius_distribution}. 
+        This model assumes that the observer knows the true properties of all 
+        the singles and primaries, and that the volume-limited mass 
+        ratios of secondaries are drawn from a uniform distribution. Further, 
+        we take $Z_0=Z_1=0.5$ throughout; $Z_0,Z_1,Z_2$ are the number of 
+        planets per single, primary, and secondary star.
         The rate and rate density are related by $\Lambda|_a^b 
@@
 $r<2r_\oplus$ are currently an active topic of research, we can consider how 
-binarity affects this regime under various reasonable assumptions.
+binarity affects this regime under different plausible assumptions.
 For instance, assume that the true radius shape function is
@@
 At apparent radii $r\a > 2r_\oplus$, the results of this model are the same as 
-those from Sec.~\ref{sub:powerlaw_varying_binaries}.
+those from Section~\ref{sub:powerlaw_varying_binaries}.
 For $r\a < 2r_\oplus$, the equations are tedious, but still tractable.
-For simplicity, we insert Eq.~\ref{eq:model3_radius_distribution} into 
-Eq.~\ref{eq:general_Gamma_a}, and integrate using a computer 
+For simplicity, we insert Equation~\ref{eq:model3_radius_distribution} into 
+Equation~\ref{eq:general_Gamma_a}, and integrate using a computer 
 program. We refer the interested reader to our online 
@@
 2r_\oplus$ and the $r\a < 2r_\oplus/\sqrt{2}$ regimes, and is plotted in
-Fig.~\ref{fig:occ_rate_model_3_log}.
+Figure~\ref{fig:occ_rate_model_3_log}.
 
@@
 \paragraph{Hot Jupiter occurrence rates}
-Taking Fig.~\ref{fig:occ_rate_model_3_log} and integrating the rate density, 
+Taking Figure~\ref{fig:occ_rate_model_3_log} and integrating the rate density, 
 we can compare the apparent hot Jupiter 
@@
         The assumed true planet radius distribution is a broken power-law
-        (Eq.~\ref{eq:model3_radius_distribution}; same as 
-        Fig.~\ref{fig:occ_rate_model_3_log}).
+        (Equation~\ref{eq:model3_radius_distribution}; same as 
+        Figure~\ref{fig:occ_rate_model_3_log}).
     }
@@
 
-We explore this quantitatively in Fig.~\ref{fig:frac_model_3}.
+We explore this quantitatively in Figure~\ref{fig:frac_model_3}.
 The lines in this figure are computed using the expressions given in the 
@@
 
-Further, Fig.~\ref{fig:frac_model_3} shows that going from apparent 
+Further, Figure~\ref{fig:frac_model_3} shows that going from apparent 
 radii of $2r_\oplus$ to $\approx 1.4r_\oplus$, the fraction of detected 
@@
 This prediction is compared against current measurements in 
-Sec.~\ref{sec:discussion}.
+Section~\ref{sec:discussion}.
 
@@
 
-The radius distribution specified by Eq.~\ref{eq:model3_radius_distribution} 
+The radius distribution specified by 
+Equation~\ref{eq:model3_radius_distribution} 
 misses some important features recently reported by state of the art 
@@
         bins) as a function of planet radius in a model with a radius gap 
-        (Eq.~\ref{eq:model4_radius_distribution}).
+        (Equation~\ref{eq:model4_radius_distribution}).
         Other than the intrinsic radius distribution, this model has the same 
-        assumptions as Fig.~\protect\ref{fig:occ_rate_model_3_log}.
+        assumptions as Figure~\protect\ref{fig:occ_rate_model_3_log}.
     }
@@
 To illustrate binarity's role in this problem, we make identical assumptions 
-as in Sec.~\ref{sec:model_3}, but instead assume an intrinsic radius 
+as in Section~\ref{sec:model_3}, but instead assume an intrinsic radius 
 distribution
@@
 \end{align}
-The resulting true and inferred rates are shown in Fig.~\ref{fig:model_4}.
+The resulting true and inferred rates are shown in Figure~\ref{fig:model_4}.
 If left uncorrected, binarity makes the gap appear more shallow, and flattens 
@@
 This means that the apparent HJ rates computed in 
-Sec.~\ref{sec:model_3} are probably inaccurate.
+Section~\ref{sec:model_3} are probably inaccurate.
 Instead, let us consider a Gaussian radius shape function,
@@
 As always, $\Gamma_i(r) = Z_i f(r)$.
-We then compute $\Gamma\a(r\a)$, and plot it in Fig.~\ref{fig:gaussian_HJ}.
+We then compute $\Gamma\a(r\a)$, and plot it in Figure~\ref{fig:gaussian_HJ}.
 Integrating for $r\a > 8r_\oplus$ to find hot Jupiter rates,
@@
         Rate density for a population of planets with true radii $r$ drawn from
-        $\mathcal{N}(14r_\oplus,2r_\oplus)$.
+        a Gaussian with mean $14r_\oplus$ and standard deviation $2r_\oplus$.
         This is similar to the hot Jupiter distribution presented 
@@
 Although this study does not resolve the problem, it does suggest the 
-approximate scale of the possible errors, in a survey-independent manner.
-The suggestion of Sec.~\ref{sec:model_2} is that for $r\a \gtrsim 2r_\oplus$, 
+approximate scale of the possible errors in a survey-independent manner.
+The suggestion of Section~\ref{sec:model_2} is that for $r\a \gtrsim 2r_\oplus$, 
 binarity can be ignored down to the $\sim$few percent precision level.
 For apparent radii $\lesssim 2r_\oplus$, the picture is less forgiving:
-Sec.~\ref{sec:model_3} suggests that relative errors between apparent rates 
+Section~\ref{sec:model_3} suggests that relative errors between apparent rates 
 and true rates around singles could easily reach $\sim\! 50\%$.
@@
     foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
-These efforts revealed that the one-year terrestrial planet occurrence rate 
+These efforts found that the one-year terrestrial planet occurrence rate 
 is between $\approx\! 0.03$ and $\approx\!1$ per Sun-like star,
-depending on assumptions that are made when calculating the rate 
-(\citealt{burke_terrestrial_2015}'s Fig.~17).
-In Sec.~\ref{sec:model_3}, our power law model indicates that when primaries, 
+depending on assumptions that are made when calculating the
+rate~\citep[see][, Figure~17]{burke_terrestrial_2015}.
+In Section~\ref{sec:model_3}, our power law model indicates that when primaries, 
 singles, and secondaries host the same number of planets, the apparent rate is 
@@
 Assuming a power-law radius distribution, and that no secondaries host HJs,
-our results from Sec.~\ref{sec:model_3} indicate that binarity 
+our results from Section~\ref{sec:model_3} indicate that binarity 
 could lead to underestimated HJ rates relative to singles by a multiplicative 
 factor of at most $\approx 1.13$.
-We later pointed out in Sec.~\ref{sec:further_models} that assuming a 
+We later pointed out in Section~\ref{sec:further_models} that assuming a 
 power-law radius distribution is probably wrong if one wishes to study the HJ 
@@
 \paragraph{Practical effects: smooth detection efficiencies; finite SNR floors}
-To relate this study's results to {\it Kepler}\ and other transit surveys, a 
-few practical concerns become pressing.
-
-First, our calculations have ignored the fact that any given transit survey's 
-finite SNR floor might censor the apparent rate density.
+To apply this study to {\it Kepler}\ and other real
+transit surveys, a few practical concerns become pressing.
+One concern is that space-based missions with telemetric requirements
+are often required to select target stars.
+Even if the selection process is aimed at creating an SNR-limited
+survey, as~\citet{batalha_selection_2010} did for {\it Kepler},
+uncertainties about stellar parameters and on-sky instrument performance
+can lead to deviations away from an SNR-limited stellar sample.
+
+Further, in most transit surveys the detection efficiency is not
+a step function in SNR.
+Transit survey pipeline detection efficiencies are usually smooth
+functions in SNR; see for example the injection \& recovery 
+simulations 
+performed by~\citet{christiansen_measuring_2016} on {\it Kepler}\ data, 
+and the resulting smooth functional form adopted 
+by~\citet{fulton_california-_2017}.
+If we were to take a smooth detection probability in SNR, we would need to 
+include a detection efficiency term in 
+Equation~\ref{eq:apparent_rate_density} to inversely weight for planets 
+with low probabilities of being detected.
+
+The simplest way to avoid the conceptual complications of accounting for 
+finite detection efficiency is to raise the SNR floor, to {\it e.g.,} 
+${\rm SNR} \approx 12$ for {\it Kepler} 
+(\citealt{fulton_california-_2017}, Figure~5).
+To a good approximation, this allows one to use the boolean distinctions 
+``searchable'' and ``not searchable'' for signals of an observed depth (at 
+fixed orbital period).
+This also makes the survey strictly SNR-limited, rather than ``fuzzily 
+SNR-limited''.
+Since the minimum SNR for detection is set in an arbitrary manner 
+anyway\footnote{For example, {\it Kepler}'s threshold of ${\rm SNR}=7.1$ was 
+set for there to be no more than one statistical false alarm across the full 
+{\it Kepler} campaign~\citep{jenkins_tests_2002}. Equally valid would have 
+been to insist on no more than $10^{-3}$ false alarms per survey, raising the 
+detection floor.
+}, this simplification would put occurrence rate studies on 
+clearer conceptual 
+ground, and facilitate the process of converting the observed distributions
+of apparent radii into true radius distributions.
+
+Finally, our calculations have ignored the fact that any given transit 
+survey's finite SNR floor might censor the apparent rate density.
 If the surveyed stars all have the same size, this is equivalent to 
@@
 
-A second assumption we used is that the detection efficiency is a 
-step function in SNR.
-The detection efficiencies of real transit survey pipelines are smooth 
-functions in SNR; see for example the injection \& recovery simulations 
-performed by~\citet{christiansen_measuring_2016} on {\it Kepler}\ data, 
-and the resulting smooth functional form adopted 
-by~\citet{fulton_california-_2017}.
-If we were to take a smooth detection probability in SNR, we would need to 
-include a detection efficiency term in 
-Eq.~\ref{eq:defn_apparent_rate_density} to inversely weight for planets 
-with low probabilities of being detected.
-
-The simplest way to avoid the conceptual complications of accounting for 
-finite detection efficiency is to raise the SNR floor, to {\it e.g.,} 
-${\rm SNR} \approx 12$ for {\it Kepler} 
-(\citealt{fulton_california-_2017}, Fig.~5).
-To a good approximation, this allows one to use the boolean distinctions 
-``searchable'' and ``not searchable'' for signals of an observed depth (at 
-fixed orbital period).
-This also makes the survey strictly SNR-limited, rather than ``fuzzily 
-SNR-limited''.
-Since this threshold is set in an arbitrary manner anyway\footnote{For 
-    example, {\it Kepler}'s threshold of ${\rm SNR}=7.1$ was set for there to 
-    be 
-    no more than one statistical false alarm across the full {\it Kepler} 
-    campaign~\citep{jenkins_tests_2002}. Equally valid would have been to 
-    insist 
-    on no more than $10^{-3}$ false alarms per survey, raising the detection 
-    floor.
-}, this simplification would put occurrence rate studies on 
-clearer conceptual 
-ground, and facilitate the process of converting the observed distributions
-of apparent radii into true radius distributions.
-
 \begin{comment}
@@
 from singles, primaries, and secondaries changes as a function of the 
-intrinsic distribution of planet parameters (Fig.~\ref{fig:frac_model_3}), 
+intrinsic distribution of planet parameters (Figure~\ref{fig:frac_model_3}), 
 some complicated deconvolution might be required.
@@
     Kepler}-detected planets orbited the primary or companion stars
-with equal probability (their Sec.~5).
+with equal probability (their Section~5).
 Under these assumptions, they found that any given planet's radius is on 
@@
 Assuming a broken power-law radius distribution, we showed in 
-Fig.~\ref{fig:frac_model_3} that there are many cases where a detected planet 
+Figure~\ref{fig:frac_model_3} that there are many cases where a detected 
+planet 
 is much more likely to orbit the primary.
@@
 At $r_\oplus \lesssim r\a \lesssim 2r_\oplus$, for all of the trial values of 
-$Z_2/Z_0$ assumed in Fig.~\ref{fig:frac_model_3}, a detected planet is always 
+$Z_2/Z_0$ assumed in Figure~\ref{fig:frac_model_3}, a detected planet is 
+always 
 more likely to orbit the primary than the secondary.
@@
 
-Of course, our model's assumptions (see the list in Sec.~\ref{sec:conclusion}) 
+Of course, our model's assumptions (see the list in Section~\ref{sec:conclusion}) 
 might not apply to the {\it Kepler}\ dataset.
@@
 radius}
-One further prediction of Fig.~\ref{fig:frac_model_3} is that the fraction of 
+One further prediction of Figure~\ref{fig:frac_model_3} is that the fraction 
+of 
 detected planets with binary companions increases by $\approx 6-12\%$ going 
@@
 Sun-like stars at least in part because of Robo-AO's sensitivity 
-(\citealt{ziegler_robo-ao_2017}'s Fig.~2;~\citealt{raghavan_survey_2010}).
+(\citealt{ziegler_robo-ao_2017}'s Figure~2;~\citealt{raghavan_survey_2010}).
 Another reason for the lower measured companion rates could be that planetary 
@@
 rates measured by transit surveys.
-The simplest of these models (Sec.~\ref{sec:simplest}) provided an 
-order-of-magnitude estimate that showed we would need very high twin binary 
-fractions for binarity to affect apparent occurrence rates by more than 
-$\sim$factors of two.
-
-We then gave a general formula for the apparent rate density inferred by an 
-observer ignoring binarity (Eq.~\ref{eq:general_Gamma_a}).
+The simplest of these models (Section~\ref{sec:simplest}) provided an 
+order-of-magnitude estimate that suggested we would need implausibly high twin 
+binary fractions for binarity to affect apparent occurrence rates by more than 
+factors of two.
+
+We then derived a general formula for the apparent rate density inferred by an 
+observer ignoring binarity (Equation~\ref{eq:general_Gamma_a}).
 As input, this equation requires a volume-limited mass ratio distribution 
@@
 $\sim$few percent level from radii $2r_\oplus \lesssim r\a \lesssim 
-17r_\oplus$ (Sec.~\ref{sec:model_2}).
+17r_\oplus$ (Section~\ref{sec:model_2}).
 %
@@
 |\Gamma_0 - \Gamma\a|/\Gamma_0$ of at most $\approx 50\%$ 
-(Fig.~\ref{fig:occ_rate_model_3_log}).
+(Figure~\ref{fig:occ_rate_model_3_log}).
 Although this is smaller than current systematic uncertainties on the 
@@
 \item Binarity ``fills in'' gaps in the radius distribution 
-(Fig.~\ref{fig:model_4}), by an amount that could affect precise measurements 
+(Figure~\ref{fig:model_4}), by an amount that could affect precise 
+measurements 
 of the depth, width, and slope of \citet{fulton_california-_2017}'s radius 
@@
 \item Binarity does not lead to smaller apparent HJ occurrence rates 
-(Fig.~\ref{fig:gaussian_HJ}).
+(Figure~\ref{fig:gaussian_HJ}).
 This assumes a Gaussian planet radius distribution, similar to that reported 
@@
 high resolution imaging surveys to exist in binaries are more likely to orbit 
-the primary (Fig.~\ref{fig:frac_model_3}).
+the primary (Figure~\ref{fig:frac_model_3}).
 %
@@
 the fraction of detected planets with binary companions increases by 
-$\approx 5-10\%$ (Fig.~\ref{fig:frac_model_3}).
+$\approx 5-10\%$ (Figure~\ref{fig:frac_model_3}).
 \end{itemize}
@@
 Otherwise, while it is only suggestive, our approach still provides 
-helpful hints at how stellar binarity influences transit survey occurrence 
-rates.
+helpful hints at how ignoring stellar binarity influences transit survey
+occurrence rates.
 
@@
 
-In this appendix, we derive Eq.~\ref{eq:general_Gamma_a}.
+In this appendix, we derive Equation~\ref{eq:general_Gamma_a}.
 First, recall our definition of apparent rate density 
-(Eq.~\ref{eq:defn_apparent_rate_density}).
-Let us explicitly write $\pp=r$ and $\ps=M$; $R$ and $L$ are uniquely 
-determined from the assumed stellar mass--radius--luminosity relation. We 
-neglect the dependence on planetary orbital period.
+(Equation~\ref{eq:apparent_rate_density}).
+We assume that $R$ and $L$ are uniquely determined from the assumed 
+stellar mass--radius--luminosity relation, and neglect the dependence on 
+planetary orbital period.
 The planets with $(r\a, M\a)$ are associated with 
@@
 det}(r\a, M\a)$ is given by the convolution of the true rate density, 
-$\Gamma(r, M)$, and $\mathcal{N}(r\a, M\a; r, M)$, the number (per 
+$\Gamma(r, M)$, and $\mathcal{N}_\star(r\a, M\a; r, M)$, the number (per 
 unit $(r\a, M\a)$) of searchable stars that give $(r\a, M\a)$  when 
@@
 \begin{align}
-n_{\rm det}(r_a, M\a) &=
-\sum_i n_{\rm det}^i(r_a, M\a) \\
+n_{\rm det}(r\a, M\a) &=
+\sum_i n_{\rm det}^i(r\a, M\a) \\
 &=
 \sum_i \int \mathrm{d}r \mathrm{d}M \,
-\mathcal{N}_{\rm s}^i(r_a,M\a; r,M)
+\mathcal{N}_\star^i(r\a,M\a; r,M)
 \cdot\Gamma_i(r,M) \cdot p_{\rm tra}(r,M),
@@
 \begin{equation}
-\mathcal{N}_{\rm s}^i(\pp\a,\ps\a; \pp, \ps)
+\mathcal{N}_\star^i(\pp\a,\ps\a; \pp, \ps)
 \end{equation}
@@
 \begin{equation}
-\mathcal{N}_{\rm s}^0(r\a,M\a; r,M)
-=\delta(r\a-r)\delta(M\a-M) N\s^0(r,M),
+\mathcal{N}_\star^0(r\a,M\a; r,M)
+=\delta(r\a-r)\delta(M\a-M) N_\star^0(r,M),
 \end{equation}
@@
 \begin{equation}
-n_{\rm det}^0(r\a, M\a)=N\s^0(r\a,M\a)\cdot \Gamma_0(r\a, 
+n_{\rm det}^0(r\a, M\a)=N_\star^0(r\a,M\a)\cdot \Gamma_0(r\a, 
 M\a) \cdot p_{\rm tra}(r\a, M\a).
@@
 \paragraph{Primaries in binaries}
-The number of primaries with apparent parameters $(r_a,M\a)$ given the 
+The number of primaries with apparent parameters $(r\a,M\a)$ given the 
 true parameters $(r,M)$ is
 \begin{equation}
-\mathcal{N}_{\rm s}^1(r_a, M\a; r, M)
-=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r_a, M\a, q; r, M),
+\mathcal{N}_\star^1(r\a, M\a; r, M)
+=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M),
 \label{eq:fancyN_s_1}
@@
 \begin{equation}
-\mathcal{N}_{{\rm s},q}^1(r_a, M\a, q; r, M) \propto \delta(M\a-M).
+\mathcal{N}_{{\rm s},q}^1(r\a, M\a, q; r, M) \propto \delta(M\a-M).
 \end{equation}
 In this case, $\mathcal{N}_{{\rm s},q}^1$ is non-zero only at 
-$r_a=R_a\sqrt{\delta_{\rm obs}}$, 
+$r\a=R_a\sqrt{\delta_{\rm obs}}$, 
 and the observed depth is
@@
 \begin{equation}
-N_{\rm s}^0(\delta_{\rm obs}, 
+N_\star^0(\delta_{\rm obs}, 
 L(M\a))\cdot
 {n_b\over n_s}\left[L_{\rm sys}(M\a, q) \over L(M\a)\right]^{3/2}
-=N_{\rm s}^0(\delta_{\rm obs}, L(M\a))
+=N_\star^0(\delta_{\rm obs}, L(M\a))
 \cdot \frac{{\rm BF}}{1 - {\rm BF}} \cdot {1 \over \mathcal{A}(q,M\a)^3}.
@@
 \notag
-\mathcal{N}_{{\rm s}, q}^1(r_a, M\a, q; r, M)
-&=N_{\rm s}^0(\delta_{\rm obs}, L(M\a))
+\mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M)
+&=N_\star^0(\delta_{\rm obs}, L(M\a))
 \cdot \frac{{\rm BF}}{1 - {\rm BF}} \cdot {1 \over \mathcal{A}(q,M\a)^3}\\
-&\times\delta \left[r_a-r\mathcal{A}(q,M\a)\right]\delta(M\a-M).
+&\times\delta \left[r\a-r\mathcal{A}(q,M\a)\right]\delta(M\a-M).
 \label{eq:N_s_1}
@@
 \begin{equation}
-\mathcal{N}_{{\rm s},q}^2(r_a, M\a, q; r, M)
+\mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
 \propto \delta\left(M\a-{M\over q}\right).
@@
 \end{equation}
-Again $\mathcal{N}_{\rm s}^2$ is non-zero only at $r_a=R_a\sqrt{\delta_{\rm 
+Again $\mathcal{N}_\star^2$ is non-zero only at $r\a=R_a\sqrt{\delta_{\rm 
         obs}}$, but this 
@@
 \begin{equation}
-\mathcal{N}_{\rm s}^2(r_a, M\a; r, M)
-=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r_a, M\a, q; r, M),
+\mathcal{N}_\star^2(r\a, M\a; r, M)
+=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r\a, M\a, q; r, M),
 \end{equation}
@@
 \mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
-&=N_{\rm s}^0(\delta_{\rm obs}, L(M\a)) \cdot \frac{{\rm BF}}{1 - {\rm BF}} 
+&=N_\star^0(\delta_{\rm obs}, L(M\a)) \cdot \frac{{\rm BF}}{1 - {\rm BF}} 
 \cdot {1 \over \mathcal{A}(q,M\a)^3}\\
 &\times 
-	\delta \left[r_a-r\mathcal{B}(q,M\a)\right]
+	\delta \left[r\a-r\mathcal{B}(q,M\a)\right]
 	\delta\left(M\a-{M\over q}\right).
@@
 
-One might worry in Eq.~\ref{eq:mathcal_N_s_2} that we opt to write 
+One might worry in Equation~\ref{eq:mathcal_N_s_2} that we opt to write 
 $\mathcal{N}\s^2 \propto \delta(M\a - M/q)$, rather than $\propto \delta(M\a q 
@@
 but a different normalization once integrated.
-We do this because the delta function in Eq.~\ref{eq:mathcal_N_s_2} is 
+We do this because the delta function in Equation~\ref{eq:mathcal_N_s_2} is 
 defined with respect to the measure ${\rm d}M\a$, not ${\rm d}M$.
@@
 \paragraph{Number of detected planets}
-Marginalizing per Eq.~\ref{eq:n_det}, we find
+Marginalizing per Equation~\ref{eq:n_det}, we find
 \begin{align}
@@
 n_{\rm det}^0(r\a, M\a)
-&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^0(r\a, M\a; r, M)
+&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_\star^0(r\a, M\a; r, M)
 \cdot\Gamma_0(r, M) \cdot p_{\rm tra}(M)\\
-&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot\Gamma_0(r\a, M\a) \cdot p_{\rm 
+&=N_\star^0(\delta_{\rm obs}, L(M\a))\cdot\Gamma_0(r\a, M\a) \cdot p_{\rm 
     tra}(M\a),
@@
 n_{\rm det}^1(r\a, M\a)
-&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^1(r\a, M\a; r, M)
+&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_\star^1(r\a, M\a; r, M)
 \cdot\Gamma_1(r, M) \cdot p_{\rm tra}(M)\\
-&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
+&=N_\star^0(\delta_{\rm obs}, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
 {\mathrm{BF}\over{1-\mathrm{BF}}} \int {\mathrm{d}q \over 
-    \mathcal{A}^4}\,f(q)\,\Gamma_1\left({r_a\over\mathcal{A}}, M\a\right).
+    \mathcal{A}^4}\,f(q)\,\Gamma_1\left({r\a\over\mathcal{A}}, M\a\right).
 \label{eq:n_det_1}
@@
 \notag
-&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^2(r\a, M\a; r, M)
+&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_\star^2(r\a, M\a; r, M)
 \cdot\Gamma_2(r, M) \cdot p_{\rm tra}(M)\\
 &=
-N\s^0(\delta_{\rm obs}, L(M\a))\cdot \frac{{\rm BF}}{1 - {\rm BF}}
+N_\star^0(\delta_{\rm obs}, L(M\a))\cdot \frac{{\rm BF}}{1 - {\rm BF}}
 \int {q \mathrm{d}q \over 
-{\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma_2\left({r_a\over\mathcal{B}}, 
+{\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma_2\left({r\a\over\mathcal{B}}, 
 qM\a\right)\,p_{\rm 
@@
 \Gamma\a(r\a,M\a) &= 
-\frac{1}{N_{\rm s,a}(r\a,M\a) p_{\rm tra}(r\a,M\a)} \times
+\frac{1}{N_\star(r\a,M\a) p_{\rm tra}(r\a,M\a)} \times
 \sum_i n_{\rm det}^i (r\a,M\a),
@@
 It is validated in limits in which it is possible to write down the answer 
-(e.g., Eq.~\ref{eq:model_1_apparent_rate_density}), and also against a Monte 
+(e.g., Equation~\ref{eq:model_1_apparent_rate_density}), and also against a 
+Monte 
 Carlo realization of the twin binary models (Secs.~\ref{sec:model_1} 
@@
 
-Noting the definition of $\mu$ in Eq.~\ref{eq:mu_general},
-Eq.~\ref{eq:final_formula} can also be expressed as
+Noting the definition of $\mu$ in Equation~\ref{eq:mu_general},
+Equation~\ref{eq:final_formula} can also be expressed as
 \begin{align}

### 2018-01-30 paper/main.tex
minor text edits

@@
 \renewcommand{\d}{_{\rm d}}
+\renewcommand{\b}{_{\rm b}}
 \begin{document}
@@
 for the apparent discrepancy between the hot Jupiter occurrence rates measured 
-by transit and RV surveys. We also demonstrate that if high-resolution imaging 
+by transit and RV surveys. We also show that if high-resolution imaging 
 reveals a transit host star to be a binary, the planet is usually more likely 
@@
 of the NASA {\it Kepler} mission.  Great strides have been made in the
-analysis of {\it Kepler} data, including
-progress toward the goal of determining the fraction of
-Sun-like stars that harbor Earth-like 
+analysis of {\it Kepler} data, including progress toward the goal of
+determining the fraction of Sun-like stars that harbor Earth-like
 planets~\citep{
@@
 investigators have assumed that all of the sources of light that were
-monitored are single 
-stars~\citep[\textit{e.g.},][]{
+monitored are single stars~\citep[\textit{e.g.},][]{
   howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,
-    dressing_occurrence_2015,burke_terrestrial_2015}. In reality many of them 
-are unresolved multiple-star systems, especially binaries.  Unrecognized
-binaries cause numerous systematic errors in the planetary occurrence
-rates.  For example, when there is a transiting planet around a star
-in a binary, the additive constant light from the second star reduces
-the fractional loss of light due to the planet.  
-This ``flux dilution'' makes transit signals harder to detect and lowers the 
-number of detections.  On the other hand, in a binary there two opportunities
-to detect transiting planets, which could increase the overall number
-of detections.
+  dressing_occurrence_2015,burke_terrestrial_2015}. In reality many of
+them are unresolved multiple-star systems, especially binaries.
+Unrecognized binaries cause numerous systematic errors in the
+planetary occurrence rates.  For example, when there is a transiting
+planet around a star in a binary, the additive constant light from the
+second star reduces the fractional loss of light due to the planet.
+This ``flux dilution'' makes transit signals harder to detect and
+lowers the number of detections.  On the other hand, in a binary there
+two opportunities to detect transiting planets, which could increase
+the overall number of detections.
 
@@
 Section~\ref{sec:simplest}, we develop an idealized model of a transit
-survey in which all planets 
-have identical properties, and all stars are identical
-except that some fraction are in binary systems.  This simple 
-model motivates the
-derivation of a general formula, given in
+survey in which all planets have identical properties, and all stars
+are identical except that some fraction are in binary systems.  This
+simple model motivates the derivation of a general formula, given in
 Section~\ref{sec:general_formula}, that allows for more realistic
@@
 
-To clarify our terminology, we define an ``apparent planet radius'', $r\a$, as 
-the radius that one would infer from a transit signal under the assumption 
-that the host star is single.
+To clarify our terminology, we define ``apparent properties'' as the 
+properties that one would infer about a system under the assumption that the 
+host star is single. For instance, the  ``apparent planet radius'', $r\a$, is
+the planet radius that one would infer from a transit signal, 
+assuming that the host star is single.
 The observed transit depth is given by the ratio of the apparent planet
@@
 \end{equation}
-where $r$ is the planet radius, $R_{\rm host}$ ($L_{\rm host}$) is the 
-host star's radius (luminosity), and $L_{\rm sys}$ is the 
+for $r$ the planet radius, $R_{\rm host}$ ($L_{\rm host}$) the 
+host star's radius (luminosity), and $L_{\rm sys}$ the 
 entire system's luminosity.
-For the example at hand, $R_{\rm host} = R$, since all stars have the same 
-size. In single star systems we have $r=r\a=r\p$. In twin binaries, 
+In the example at hand, $R_{\rm host} =R\a = R$, since all stars have the same 
+size. For single star systems we have $r=r\a=r\p$. In twin binaries, 
 $r\a=r\p/\sqrt{2}$, since $L_{\rm sys}=2L$.
@@
 
-We can write similar equations for the binaries.
+We can similarly compute the number of planet detections from binaries.
 First though, we define a ratio $\mu \equiv N_\star^{\rm b}(r\a) / 
@@
 \begin{equation}
-{\rm binary\ fraction} \equiv \frac{n_b}{n_s + n_b} = 0.44,
+{\rm binary\ fraction} \equiv \frac{n\b}{n\s + n\b} = 0.44,
 \end{equation}
@@
 An alternative assumption is that secondaries do not host planets. In that 
-case, $Z_0=Z_1$, and $Z_2=0$. The correction to the rate density at the true 
-planet radius becomes $X_\Gamma(r\p) = (1+2\mu)/(1+\mu)^2$.
+case, the correction to the rate density at the true planet radius becomes 
+$X_\Gamma(r\p) = (1+2\mu)/(1+\mu)^2$.
 This gives a correction of 0.98~(0.94) if the binary fraction is 0.05~(0.10).
-While the secondaries certainly do have planets, 
+Although the secondaries certainly should have planets, 
 the fact that $\Gamma\a/\Gamma_0$ is sensitive to the relative number 
-of planets per single, primary, and secondary will become important as we 
-proceed.
+of planets per single, primary, and secondary will also become
+important as we proceed.
 
@@
 
-A simple extension to the previous example will help us further distinguish 
-the detected populations.
-Consider now a universe that is the same in every respect to that of 
-Section~\ref{sec:model_1}, except that half of planets have true radii $r\p$, 
-while the other half have true radii $r\p/\sqrt{2}$.
-The true rate densities are
+A simple extension to the previous example helps distinguish 
+between the apparent and underlying planet populations.
+Consider now a universe that is the same as that of 
+Section~\ref{sec:model_1}, except that half of planets have radii $r\p$, 
+while the other half have radii $r\p/\sqrt{2}$.
+The rate densities are
 \begin{equation}
@@
 \end{align}
-The important qualitative point of this equation is that at $r\a = 
+There are now three different sizes of detected planets.
+The important qualitative point is that at $r\a = 
 r\p/\sqrt{2}$, two populations contribute.
@@
 from a cancellation of $N_\star^0(r\a)$ terms, leaving only the $\mu$ weights.
+Generally, at any given apparent radius, there will be contributions
+from both single, primaries, and secondaries~---~but the relative weights
+between these contributions will depend on the underlying occurrence rates.
 
@@
 \end{align}
-where ${\rm BF}$ is the volume-limited binary fraction, 
+where ${\rm BF}=n\b/(n\s+n\b)$ is the volume-limited binary fraction, 
 and $\mathcal{A}(q,M\a)$ [$\mathcal{B}(q,M\a)$] are the dilution terms for 
@@
 \end{equation}
-which may be written in a closed form using the hypergeometric function.
+which can also be rewritten using the hypergeometric function.
 
@@
 \label{sec:more_complicated}
-The following section applies our general equation for the apparent rate 
+This section applies our general equation for the apparent rate 
 density (Equation~\ref{eq:general_Gamma_a}) to study binarity's effects in 
-regimes 
-of observational interest.
-In general, we will write the rate density for each type of star, 
+regimes of observational interest.
+In what follows, we will write the rate density for each type of star, 
 $\Gamma_i(r)$, as the product of a shape function and a constant:
@@
 \end{equation}
-where as always, $i=0$ corresponds to single stars, $i=1$ to primaries of 
+where $i=0$ corresponds to single stars, $i=1$ to primaries of 
 binaries, and $i=2$ to secondaries of binaries.
@@
 single, primary, or secondary star.
-This section will consider the effects of varying both $f_i(r)$ and also the
+We want to consider the effects of varying not only $f_i(r)$ but also the
 relative values of the $Z_i$'s.
@@
 We begin introducing realism by keeping all binaries as twins, but letting the 
-radius distribution of planets vary.
+planet radius distributions vary.
 Specifically, we take
@@
 normalization.
-The resulting apparent rate density is quite similar to that of the twin 
-binary, fixed-planet case (Equation~\ref{eq:model_1_apparent_rate_density}), 
-except 
-for a slightly different radius dependence and normalization:
+The resulting apparent rate density is 
 \begin{equation}
@@
 \right)
-\right].
+\right],
 \label{eq:model5_apparent_rate_density}
 \end{equation}
-As in Section~\ref{sec:model_1}, $\mu = 2^{3/2} {\rm BF}/(1-{\rm BF})$.
+which is quite similar to the twin binary, fixed-planet case 
+(Equation~\ref{eq:model_1_apparent_rate_density}), 
+except for the radius dependence and normalization.
+As in Section~\ref{sec:model_1}, $\mu = 2^{3/2} n\b/n\s$.
 If the $Z_i$'s are equal, the ``correction factor'' relative to the rate 
@@
 \end{align}
-For the case of ${\rm BF}=0.1$, $\mu\approx 0.153$. Taking $\delta=-2.92$ from 
+If the binary fraction $0.1$, $\mu\approx 0.15$. Taking $\delta=-2.92$ from 
 \citet{howard_planet_2012},  we get a correction factor $\Gamma\a/\Gamma_0 = 
@@
 \frac{1}{1+\mu}
-\left[1 + \frac{1}{\mathcal{N}_q} \frac{{\rm BF}}{1-{\rm BF}}\times 
+\left[1 + \frac{1}{\mathcal{N}_q} \frac{n\b}{n\s}\times 
 \left(
@@
 1.50249$. %171211_model_integrals.nb
-For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$; the
+For $n\b / (n\b + n\s)=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$; the
 relative difference between the apparent rate density and the rate density 
@@
 
-In the recent work by~\citet{petigura_CKS_2017}, hot Jupiters appear as an 
+In the recent study by~\citet{petigura_CKS_2017}, hot Jupiters appear as an 
 island in period-radius space, rather than as a continuous component of a 
@@
 L(M\a))\cdot
-{n_b\over n_s}\left[L_{\rm sys}(M\a, q) \over L(M\a)\right]^{3/2}
+{n\b\over n\s}\left[L_{\rm sys}(M\a, q) \over L(M\a)\right]^{3/2}
 =N_\star^0(\delta_{\rm obs}, L(M\a))

### 2018-01-30 paper/main.tex
minor edits

@@
 \paragraph{Ratio of searchable binaries to singles}
-We must also specify the exact form of $\mu({\rm BF},M\a)$, the ratio of 
+We must also specify the exact form of $\mu$, the ratio of 
 the number of searchable binary systems to singles.
@@
 \end{equation}
-If $\mathrm{BF}$ is independent of $q$, $L \propto M^\alpha$, and $f(q) 
+If the binary fraction is independent of $q$, $L \propto M^\alpha$, and $f(q) 
 \propto q^\beta$, this simplifies to
@@
 \mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 
-\left(1+q^\alpha\right)^{3/2} q^\beta \,\mathrm{d}q,
+\left(1+q^\alpha\right)^{3/2} q^\beta \,\mathrm{d}q.
 \label{eq:mu_power_laws}
 \end{equation}
-which can also be rewritten using the hypergeometric function.
-
+%which can also be rewritten using the hypergeometric function.
 \begin{figure}[!tb]
@@
 \end{figure}
-
 This can be understood as a Malmquist bias: at fixed observed transit 
@@
 \label{sec:more_complicated}
-This section applies our general equation for the apparent rate 
+We now apply our general equation for the apparent rate 
 density (Equation~\ref{eq:general_Gamma_a}) to study binarity's effects in 
@@
 planet radius distributions vary.
-Specifically, we take
+First, we assume a power law,
 \begin{equation}
@@
 (Equation~\ref{eq:model_1_apparent_rate_density}), 
-except for the radius dependence and normalization.
+except that the radius dependence and normalization are different.
 As in Section~\ref{sec:model_1}, $\mu = 2^{3/2} n\b/n\s$.
@@
 \end{align}
-If the binary fraction $0.1$, $\mu\approx 0.15$. Taking $\delta=-2.92$ from 
+If the binary fraction is $0.1$, $\mu\approx 0.15$. Taking $\delta=-2.92$ from 
 \citet{howard_planet_2012},  we get a correction factor $\Gamma\a/\Gamma_0 = 
@@
 This is quite a small effect!
-Note though that it could change if the $Z_i$'s are not equal.
-Also, the power law radius distribution $f(r) \propto r^\delta$ diverges for 
-$\delta < 0$; \citet{howard_planet_2012}'s results indicate that this
-approximation is good for $r\a\gtrsim 2r_\oplus$.
-Similarly, it is nonsensical for $f(r)$ to be finite above some upper radius 
-limit $r_u$, perhaps around $\approx 24r_\oplus$, based on the most inflated 
-hot Jupiters.
-An upper cut-off of $r_u$ would lead to smaller values of $\Gamma(r\a)$ 
-down to $r_u/\sqrt{2}$, compared to an intrinsic power law without the cut-off.
-We are not particularly interested in this effect; there are better 
+Clearly though, it cannot apply at small radii, since $f(r) \propto r^\delta$ 
+diverges; \citet{howard_planet_2012}'s 
+results indicate that the power law planet radius distribution holds for 
+$r\a\gtrsim 2r_\oplus$.
+It is similarly nonsensical for $f(r)$ to be finite above some upper radius 
+limit $r_{\rm u}$, perhaps around $\approx 24r_\oplus$, based on the most 
+inflated hot Jupiters.
+An upper cut-off of $r_{\rm u}$ would lead to smaller values of $\Gamma(r\a)$ 
+down to $r_{\rm u}/\sqrt{2}$, compared to an intrinsic power law without the 
+cut-off.
+We are not particularly interested in this effect because there are better 
 models for hot Jupiter occurrence rates that we will discuss in 
 Section~\ref{sec:further_models}.
-If the assumptions behind this model (listed in 
-Section~\ref{sec:general_formula}) are at all applicable in real transit surveys, 
-this suggests that for $2r_\oplus \lesssim r\a \lesssim 17r_\oplus$, 
-binarity's impact on derived occurrence rates is quite small.
+If the assumptions behind this model are at all applicable to real transit 
+surveys, Equation~\ref{eq:power_law_correction} suggests that for $2r_\oplus 
+\lesssim r\a \lesssim 17r_\oplus$, binarity's impact on apparent occurrence 
+rates is quite small.
 
@@
 It may also affect the rate density, which could be a function of the 
-(varying) stellar mass.
+varying stellar mass.
 Absorbing this dependence into a power law as well,
@@
 This indicates that considering only twin binaries gave us correct 
-intuition: for a power-law radius distribution 
+intuition: for a power law radius distribution 
 ($2r_\oplus \lesssim r\a \lesssim 17r_\oplus$) in which there are the same 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Varying stars; broken power-law planet radius distribution}
+\subsection{Varying stars; broken power law planet radius distribution}
 \label{sec:model_3}
@@
 
-Though the details of the true radius distribution $\Gamma_i(r)$ at 
+Though the details of the planet radius distribution $\Gamma_i(r)$ at 
 $r<2r_\oplus$ are currently an active topic of research, we can consider how 
@@
 \end{align}
-As in the previous model, we assume that the observers know the true 
+As in the previous model, we presume that the observers know the true 
 properties of all singles and primaries. The masses, radii, 
@@
         (orange), $0$ (green).
-        The assumed true planet radius distribution is a broken power-law
+        The assumed true planet radius distribution is a broken power law
         (Equation~\ref{eq:model3_radius_distribution}; same as 
@@
 depending on assumptions that are made when calculating the
-rate~\citep[see][, Figure~17]{burke_terrestrial_2015}.
-In Section~\ref{sec:model_3}, our power law model indicates that when primaries, 
+rate~\citep[see][Figure~17]{burke_terrestrial_2015}.
+In Section~\ref{sec:model_3}, our power law model indicates that when 
+primaries, 
 singles, and secondaries host the same number of planets, the apparent rate is 
@@
 effects on star counts and the apparent radii of detected planets.
-Assuming a power-law radius distribution, and that no secondaries host HJs,
+Assuming a power law radius distribution, and that no secondaries host HJs,
 our results from Section~\ref{sec:model_3} indicate that binarity 
@@
 We later pointed out in Section~\ref{sec:further_models} that assuming a 
-power-law radius distribution is probably wrong if one wishes to study the HJ 
+power law radius distribution is probably wrong if one wishes to study the HJ 
 rate discrepancy.
@@
 \begin{comment}
-If we believe the assumed power-law radius distribution, we can ask whether 
+If we believe the assumed power law radius distribution, we can ask whether 
 this ``correction factor'' might help resolve the discrepancy.
@@
 This suggestion should be taken with caution, because it (likely incorrectly) 
-assumes a power-law radius distribution.
+assumes a power law radius distribution.
 \end{comment}
@@
 \paragraph{Practical effects: smooth detection efficiencies; finite SNR floors}
-To apply this study to {\it Kepler}\ and other real
-transit surveys, a few practical concerns become pressing.
+To apply this study to real transit surveys, a few practical concerns become 
+pressing.
 One concern is that space-based missions with telemetric requirements
@@
 survey, as~\citet{batalha_selection_2010} did for {\it Kepler},
-uncertainties about stellar parameters and on-sky instrument performance
+uncertainties in stellar parameters and the modeled instrument performance
 can lead to deviations away from an SNR-limited stellar sample.
@@
 Transit survey pipeline detection efficiencies are usually smooth
-functions in SNR; see for example the injection \& recovery 
+functions in SNR; see for example the injection-recovery 
 simulations 
 performed by~\citet{christiansen_measuring_2016} on {\it Kepler}\ data, 
-and the resulting smooth functional form adopted 
+and the resulting smooth detection efficiency adopted 
 by~\citet{fulton_california-_2017}.
-If we were to take a smooth detection probability in SNR, we would need to 
+If we were to assume a smooth detection probability in SNR, we would need to 
 include a detection efficiency term in 
@@
 fixed orbital period).
-This also makes the survey strictly SNR-limited, rather than ``fuzzily 
-SNR-limited''.
+By making the survey strictly SNR-limited, rather than ``fuzzily 
+SNR-limited'', binarity's effects become much easier to model.
 Since the minimum SNR for detection is set in an arbitrary manner 
@@
 
-Finally, our calculations have ignored the fact that any given transit 
+Finally, our calculations also ignore the fact that any given transit 
 survey's finite SNR floor might censor the apparent rate density.
@@
 
-Assuming a broken power-law radius distribution, we showed in 
+Assuming a broken power law radius distribution, we showed in 
 Figure~\ref{fig:frac_model_3} that there are many cases where a detected 
@@
 %
-\item Assuming a power-law planet radius distribution, and that the same 
+\item Assuming a power law planet radius distribution, and that the same 
 number of planets orbit singles, primaries, and secondaries, binarity 

### 2018-01-30 paper/main.tex
further minor edits

@@
 
-\title{ The effects of binarity on planet occurrence rates measured by transit 
-surveys}
+\title{ The effects of binarity on planet occurrence rates measured by
+transit surveys}
 %
@@
 %
-Wide-field surveys for transiting planets, such as the NASA {\it Kepler}
-and {\it TESS} missions, are usually conducted without knowing which stars
-are actually binaries. Unresolved and unrecognized binary stars give rise to 
-systematic errors in planet occurrence rates, including misclassified planets 
-and miscounts in the number of searched stars. The individual errors can have 
-different signs, making it difficult to anticipate the net effect on planet 
-occurrence rates. Here we use simplified models of signal-to-noise limited 
-transit surveys to try and clarify the situation. We derive a formula for the 
-apparent occurrence rate density measured by an observer who falsely assumes 
-all stars are single. The formula depends on the binary fraction; the 
-mass function of the secondary stars; and the true occurrence of planets 
-around primaries, secondaries, and single stars. It also takes into account 
-the Malmquist bias by which binaries are over-represented in flux-limited 
-samples. Application of the formula to an idealized {\it Kepler}-like survey 
-shows that for planets larger than $2r_\oplus$, the net systematic error is of 
-order 10\%. For smaller planets the errors are potentially larger: the 
-occurrence of Earth-sized planets could be overestimated by as much as a 
-factor of two. One consequence is that unrecognized binaries cannot account 
-for the apparent discrepancy between the hot Jupiter occurrence rates measured 
-by transit and RV surveys. We also show that if high-resolution imaging 
-reveals a transit host star to be a binary, the planet is usually more likely 
-to orbit the primary star than the secondary star.
+
+Wide-field surveys for transiting planets, such as the NASA
+{\it Kepler} and {\it TESS} missions, are usually conducted without
+knowing which stars are binaries. Unresolved and unrecognized binary
+stars give rise to systematic errors in planet occurrence rates,
+including misclassified planets and miscounts in the number of
+searched stars. The individual errors can have different signs,
+making it difficult to anticipate the net effect on inferred
+occurrence rates. Here we use simplified models of signal-to-noise
+limited transit surveys to try and clarify the situation. We derive
+a formula for the apparent occurrence rate density measured by an
+observer who falsely assumes all stars are single. The formula
+depends on the binary fraction; the mass function of the secondary
+stars; and the true occurrence of planets around primaries,
+secondaries, and single stars. It also takes into account the
+Malmquist bias by which binaries are over-represented in
+flux-limited samples. Application of the formula to an idealized
+{\it Kepler}-like survey shows that for planets larger than
+$2r_\oplus$, the net systematic error is of order 10\%. For smaller
+planets the errors are potentially larger: the occurrence of
+Earth-sized planets could be overestimated by as much as a factor of
+two. One consequence is that unrecognized binaries cannot account
+for the apparent discrepancy between hot Jupiter occurrence
+rates measured by transit and RV surveys. We also show that if
+high-resolution imaging reveals a transit host star to be a binary,
+the planet is usually more likely to orbit the primary star than the
+secondary star.
 %
@@
 of the NASA {\it Kepler} mission.  Great strides have been made in the
-analysis of {\it Kepler} data, including progress toward the goal of
-determining the fraction of Sun-like stars that harbor Earth-like
-planets~\citep{
+analysis of {\it Kepler} data, including progress towards measuring
+the fraction of Sun-like stars that harbor Earth-like planets~\citep{
   youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
@@
 monitored are single stars~\citep[\textit{e.g.},][]{
-  howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,
+  howard_planet_2012,fressin_false_2013,
   dressing_occurrence_2015,burke_terrestrial_2015}. In reality many of
@@
 the results from {\it Kepler} or any other real transit survey.
-However we can estimate the order of magnitude of the effects,
-assuming the survey is signal-to-noise limited and given a model for
-the true planet occurrence rate.
+Our goal is to estimate the order of magnitude of the effects,
+assuming the survey is signal-to-noise limited, and given the true
+underlying planet occurrence rates.
 
@@
 nevertheless still analytic models.  In Section~\ref{sec:discussion}
-we discuss the errors due to unrecognized binaries for some specific
-cases of current interest: the occurrence of Earth-like planets; the
-apparent discrepancy between hot-Jupiter occurrence rates in different
-surveys; and the shape of the ``evaporation valley'' in the radius
-distribution of planets that was brought to light by
+we discuss the errors due to unrecognized binaries for specific cases
+of current interest: the occurrence of Earth-like planets; the
+apparent discrepancy between hot Jupiter occurrence rates in different
+surveys; and the shape of the ``evaporation valley'' in the planet
+radius distribution that was brought to light by
 \citet{fulton_california-_2017}.  We review all the results in
@@
 They want to compute the number of planets with size $r$ per star of mass $M$.
-If the total number of such stars for which the planets could be detected
+If the total number of stars for which such planets could be detected
 ($N_\star$) and the number of detected planets ($N_{\rm det}$) are both 
@@
 %    
-    \item The number of detections, $N_{\det}$, is actually the number of 
+    \item The number of planets, $N_{\det}$, is actually the number of 
     detected planets that {\it appear} to have size $r$, orbiting stars that 
@@
         \item toward lower values, because it does not include all of the
-        secondary stars that were searched for transiting planets.
+        secondary stars that were searched for transiting planets;
 %        
@@
 presence, they must realize that the ratio of binaries to single stars
-in the sample will differ from that in a volume-limited sample due to
-a type of Malmquist bias.  Binaries have a higher total luminosity
-than either the primary or secondary star would have on its own.  This
-means that the binaries are searchable for transit signals of a given
-amplitude at greater distances from the Earth.  The binaries in a
-sample of apparently searchable stars are therefore drawn from a
-larger search volume than the single stars.
-
-% JNW: Let's remember, when discussing Kepler, to point out that it's
-% not really a SNR or flux limited survey, because of the
-% preselection. This would need to be dealt with in a realistic
-% treatment.
-
-% JNW: Let's also remember to say somewhere that we do not deal with
-% period distributions none of these effects mess up the period.
+in the searched sample will differ from that in a volume-limited
+sample due to a type of Malmquist bias.  Binaries have a higher total
+luminosity than either the primary or secondary star would have on its
+own.  This means that the binaries are searchable for transit signals
+of a given amplitude at greater distances from the Earth.  The
+binaries in a sample of apparently searchable stars are therefore
+drawn from a larger search volume than the single stars.
 
@@
 Given all of the confusing and opposing sources of error, we will
-proceed in stages. We will start from a barebones model in which
-everything can be written down on the back of a napkin, and build up
-to an analytic model allowing for generality in the distribution of
-the binaries and the planets they host.  We consider only the
-corrections to the occurrence as a function of planetary radius, and
-not the orbital period (the other key variable in transit studies),
-because when multiple transits are detected the period can be directly
-measured regardless of whether the host star is single or part of a
-binary.
+proceed in stages. We start from a barebones model in which everything
+can be written down on the back of a napkin, and build up to an
+analytic model allowing for generality in the distribution of the
+binaries and the planets they host.  We consider only corrections to
+the occurrence as a function of planetary radius, and not orbital
+period (the other key variable in transit studies), because when
+multiple transits are detected the period can be directly measured
+regardless of whether the host star is single or part of a binary.
 
@@
 all stars are identical, with mass $M$, radius $R$, and luminosity
-$L$.  Some fraction of them exist in twin binaries.
-All planets have size $r\p$.
-Our goal is to compare the occurrence inferred by observers who
-ignore binarity with the true occurrence in single star systems.
+$L$.  Some fraction of them exist in twin binaries.  All planets have
+size $r\p$.  Our goal is to compare the occurrence inferred by
+observers who ignore binarity with the true occurrence in single star
+systems.
 
@@
 
-We can now understand that the observers are unwittingly
-reporting an {\it apparent} occurrence rate $\Lambda\a(r\a)$ as
-a function of apparent radius.
-The apparent occurrence rate is the same as the {\it true} occurrence rate for 
-transit signals of 
-amplitude $\delta_{\rm obs} = (r\a/R\a)^2$, \textit{i.e.}, the number of 
-detections ($N_{\rm det}$) of signals of amplitude $\delta_{\rm obs}$, divided 
-by the number of sources $N_\star$ from which such a signal could be detected.
+We can now understand that the observers are unwittingly reporting an
+{\it apparent} occurrence rate $\Lambda\a(r\a)$, a function of
+apparent radii.  The apparent occurrence rate is the same as the {\it
+true} occurrence rate for transit signals of amplitude $\delta_{\rm
+obs} = (r\a/R\a)^2$, but this latter quantity is typically not what
+observers are interested in studying.
 
@@
 To compute the number of detected planets, we consider the volumes within 
-which a given signal could be detected. At a fixed signal-to-noise floor, 
+which a signal of a given depth could be detected. At a fixed signal-to-noise floor, 
 there is a maximum searchable 
@@
 At an apparent radius equal to the true radius ($r\a=r\p$), single stars 
-with $d<d_0$ are searchable.
+with $d<d_0$ are by definition searchable.
 Binaries with $r\a=r\p$ are also searchable, out to $\sqrt{2}d_0$. 
@@
 \end{equation}
-relates the number of apparently searchable point-sources to the number of 
+relates the number of apparently searchable point-sources and the number of 
 searchable singles.
-From the discussion above, it should be clear that there are in fact
-$N_\star^0(r\a)\times (1 + 2\mu)$ searchable stars at any given $r\a$; the 
-observers are under-counting.
+There are in fact $N_\star^0(r\a)\times (1 + 2\mu)$ searchable stars
+at any given $r\a$; the observers are under-counting.
 
 Using Equation~\ref{eq:apparent_rate_density}, the apparent rate density 
-computed when ignoring binarity is
+reported when ignoring binarity is
 \begin{align}
@@
 \end{align}
+The first term is from singles, and the second is from binaries.
 The number of searchable singles at a given apparent radius, 
@@
 By multiplicity fraction, they meant ``fraction of systems in a volume-limited 
-sample that are multiple'', which we simplistically take to be fraction of 
-systems in a volume-limited sample that are binaries:
+sample that are multiple'', which we simplistically conflate with the
+fraction of systems in a volume-limited sample that are binaries:
 \begin{equation}
@@
 \end{equation}
-can then be thought of as a ``correction factor''.
+can then be evaluated as a ``correction factor''.
 At the true planet radius, $X_\Gamma(r\p)=1/(1+\mu)$.
@@
 Although the secondaries certainly should have planets, 
-the fact that $\Gamma\a/\Gamma_0$ is sensitive to the relative number 
-of planets per single, primary, and secondary will also become
-important as we proceed.
+the sensitivity of $\Gamma\a/\Gamma_0$ to the relative number of
+planets per single, primary, and secondary will also become important
+as we proceed.
 
@@
 between the apparent and underlying planet populations.
-Consider now a universe that is the same as that of 
+Consider now a universe that is the same as in
 Section~\ref{sec:model_1}, except that half of planets have radii $r\p$, 
@@
 \end{equation}
-where as before $i=0$ corresponds to singles, $i=1$ to primaries, and $i=2$ to 
-secondaries, and the $Z_i$'s are the number of planets per star of each type.
+where $i=0$ corresponds to singles, $i=1$ to primaries, and $i=2$ to
+secondaries, and the $Z_i$'s are the number of planets per star of
+each type.
 
@@
 \end{align}
-There are now three different sizes of detected planets.
-The important qualitative point is that at $r\a = 
-r\p/\sqrt{2}$, two populations contribute.
-The first population is singles with $r=r\p/\sqrt{2}$, and the second is twin 
+Just as in Equation~\ref{eq:model_1_apparent_rate_density}, the
+$N_\star^0(r\a)$ terms cancel, leaving only the $\mu$ weights.
+However, there are now three detected planet sizes.
+Also different is that two populations contribute at $r\a = 
+r\p/\sqrt{2}$:
+the first population is singles with $r=r\p/\sqrt{2}$, and the second is twin 
 binaries with $r=r\p$.
 Both populations are detected out to the same maximum searchable distance.
-Just as with Equation~\ref{eq:apparentlysearchable_to_searchable}, we benefit 
-from a cancellation of $N_\star^0(r\a)$ terms, leaving only the $\mu$ weights.
-Generally, at any given apparent radius, there will be contributions
-from both single, primaries, and secondaries~---~but the relative weights
+More generally, at any given apparent radius, there will be contributions
+from both singles, primaries, and secondaries~---~but the relative weights
 between these contributions will depend on the underlying occurrence rates.
@@
 A derivation of Equation~\ref{eq:general_Gamma_a} is given in the 
-\hyperref[sec:appendix]{Appendix}; its qualitative features are as follows.
+\hyperref[sec:appendix]{Appendix}; its qualitative features are the same as 
+from our simple model (Equation~\ref{eq:model_1_apparent_rate_density}).
 The terms inside the curly braces $\{ \ldots \}$ are the sum of 
@@
 Given the observed signal $\delta_{\rm obs}$ and apparent stellar mass $M\a$, 
-recall that the maximum searchable distance for singles and binaries are 
+recall that the maximum searchable distances for singles and binaries are 
 proportional to $\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm 
@@
 depth, for singles and primaries with the same luminosity, binaries are 
-searchable to a greater distance;
-In particular, the sample of searchable binaries is magnitude-limited.
+searchable to a greater distance.
+Specifically, the sample of searchable binaries is magnitude-limited.
 Given a searchable binary, the probability that it has a mass ratio $q$ 
@@
 \label{sec:more_complicated}
-We now apply our general equation for the apparent rate 
+We will now apply our general equation for the apparent rate 
 density (Equation~\ref{eq:general_Gamma_a}) to study binarity's effects in 
 regimes of observational interest.
-In what follows, we will write the rate density for each type of star, 
+In the following, we write the rate density for each type of star, 
 $\Gamma_i(r)$, as the product of a shape function and a constant:
@@
 planet radius distributions vary.
-First, we assume a power law,
+First, we assume a power law planet radius distribution,
 \begin{equation}
@@
 (Equation~\ref{eq:model_1_apparent_rate_density}), 
-except that the radius dependence and normalization are different.
+except for in the radius dependence and normalization.
 As in Section~\ref{sec:model_1}, $\mu = 2^{3/2} n\b/n\s$.
@@
 If the binary fraction is $0.1$, $\mu\approx 0.15$. Taking $\delta=-2.92$ from 
-\citet{howard_planet_2012},  we get a correction factor $\Gamma\a/\Gamma_0 = 
+\citet{howard_planet_2012},  we find $\Gamma\a/\Gamma_0 = 
 1.004$.
@@
 the rate density of single stars, with a relative difference $\delta \Gamma_0 
-= |\Gamma_0 - \Gamma\a | / \Gamma_0$ of 0.4\%.
+= |\Gamma_0~-~\Gamma\a|/\Gamma_0$ of 0.4\%.
 This is quite a small effect!
@@
 inflated hot Jupiters.
-An upper cut-off of $r_{\rm u}$ would lead to smaller values of $\Gamma(r\a)$ 
+Imposing an upper cut-off of $r_{\rm u}$ would lead to smaller values of 
+$\Gamma(r\a)$ 
 down to $r_{\rm u}/\sqrt{2}$, compared to an intrinsic power law without the 
@@
 The ``bump'' exists even for the $Z_2/Z_0=0$ case as a $\approx 10\%$ effect.
-Evidently, the magnitude of this error depends strongly on the prevalence of 
+The magnitude of this evidently error depends strongly on the prevalence of 
 planets around secondaries.
@@
 $Z_2/Z_0=0.5$, we find $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 1.06$.
+We discuss this issue further in Section~\ref{sec:further_models}.
 
@@
 We explore this quantitatively in Figure~\ref{fig:frac_model_3}.
-The lines in this figure are computed using the expressions given in the 
+The lines in this figure are computed using expressions given in the 
 appendix for the number of detections coming from singles, primaries, and 
@@
 In short, the detected planet usually is more likely to orbit the primary, but 
-it depends on the number of planets orbiting secondaries, and also on the 
-apparent radius of the detected planet.
+this statement depends on the number of planets orbiting secondaries, and also 
+on the apparent radius of the detected planet.
 In the scenario that high-resolution imaging finds a system with $r\a > 
@@
 planets with binary companions increases by $\approx 6-12\%$, depending on the 
-assumed value of $Z_2/Z_0$.
-Let the fraction of total detected planets from primaries at a given 
-apparent radius be $F_1(r\a)$, so $F_1(r\a) \equiv n_{\rm det}^1(r\a)/n_{\rm 
-det}^{\rm tot}$.
-Let the analogous quantity for secondaries be $F_2(r\a)$.
-In the planet-less secondaries case ($F_2(r\a)=0$), one can 
-analyze Eqs~\ref{eq:n_det_0} and~\ref{eq:n_det_1} semi-analytically and show 
-that $F_1(2r_\oplus/\sqrt{2})/F_1(2r_\oplus) \approx 1.19$.
+assumed value of $Z_2/Z_0$. %~\footnote{
+%The increase can be derived analytically.
+%Let the fraction of total detected planets from primaries at a given 
+%apparent radius be $F_1(r\a)$, so $F_1(r\a) \equiv n_{\rm det}^1(r\a)/n_{\rm 
+%    det}^{\rm tot}$.
+%Let the analogous quantity for secondaries be $F_2(r\a)$.
+%In the planet-less secondaries case ($F_2(r\a)=0$), one can 
+%analyze Eqs~\ref{eq:n_det_0} and~\ref{eq:n_det_1} semi-analytically and show 
+%that $F_1(2r_\oplus/\sqrt{2})/F_1(2r_\oplus) \approx 1.19$.
 %check_companion_fractions.py, and LB's notes 2017/12/21.0
+%}.
 Intuitively speaking, this ``shift'' is a feature of any radius distribution 
@@
 the undiluted distribution from $r\a$ to $\sqrt{2}r\a$.
-This prediction is compared against current measurements in 
+We compare this prediction with recent observations in 
 Section~\ref{sec:discussion}.
@@
 Equation~\ref{eq:model3_radius_distribution} 
-misses some important features recently reported by state of the art 
-occurrence rate studies.
+misses some important features reported in state of the art 
+studies of planetary occurrence.
 
@@
 
-In particular,~\citet{fulton_california-_2017} reported a ``gap'' in 
+\citet{fulton_california-_2017} recently reported a ``gap'' in 
 the radius-period 
@@
 \end{align}
-The resulting true and inferred rates are shown in Figure~\ref{fig:model_4}.
+The resulting true and apparent rates are shown in Figure~\ref{fig:model_4}.
 If left uncorrected, binarity makes the gap appear more shallow, and flattens 
@@
 \citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.
-This means that any study measuring the gap's width or depth in the face of 
+This means that any study measuring the gap's width or depth while accounting 
+for 
 binarity must either perform tests at fixed orbital period, or else 
@@
 \approx \Lambda_{\rm HJ,a}$ to within one percent.
-Qualitatively, the apparent HJ rate can be greater than the true rate for 
-singles because binary systems can have an extra star that yields 
+Qualitatively, the apparent HJ rate is greater than the true rate for 
+singles because binary systems can have an extra uncounted star that yields 
 hot Jupiter detections.
@@
 The suggestion of Section~\ref{sec:model_2} is that for $r\a \gtrsim 2r_\oplus$, 
-binarity can be ignored down to the $\sim$few percent precision level.
+binarity can be ignored down to a precision of a few percent.
 For apparent radii $\lesssim 2r_\oplus$, the picture is less forgiving:
-Section~\ref{sec:model_3} suggests that relative errors between apparent rates 
+Section~\ref{sec:model_3} suggests that relative differences between apparent 
+rates 
 and true rates around singles could easily reach $\sim\! 50\%$.
@@
 
-One caveat to this assessment of binarity's importance for 
+One caveat to our assessment of binarity's relevance for 
 $\eta_\oplus$ measurements is that none of our models 
-included the rate density's period-dependence. However, close binaries usually
-provoke dynamical instabilities, leading to fewer long-period planets per 
+included the rate density's period-dependence. However, binaries with 
+separations $\lesssim 10\,{\rm AU}$ could
+provoke dynamical instabilities, leading to fewer Earth-like planets per 
 star~\citep[\textit{e.g.},][]{holman_long-term_1999,wang_influence_2014,
     kraus_impact_2016}.
-This might affect transit survey measurements of $\eta_\oplus$ beyond our 
+This would affect transit survey measurements of $\eta_\oplus$ beyond our 
 rough estimate.
@@
 account for a $\approx 20\%$ relative difference in the measured rates between 
-the CKS and {\it Kepler}\ samples~--~not a factor of two\footnote{
+the CKS and {\it Kepler}\ samples~--~not a 50\% relative difference\footnote{
     \citet{petigura_CKS_2017} recently found $\beta = 3.4^{0.9}_{-0.8}$.
@@
 
-Ignoring these complications, in this work we concentrated on binarity's 
+Ignoring these complications, we concentrated in this work on binarity's 
 effects on star counts and the apparent radii of detected planets.
 Assuming a power law radius distribution, and that no secondaries host HJs,
-our results from Section~\ref{sec:model_3} indicate that binarity 
+we found in Section~\ref{sec:model_3} that binarity 
 could lead to underestimated HJ rates relative to singles by a multiplicative 
-factor of at most $\approx 1.13$.
-We later pointed out in Section~\ref{sec:further_models} that assuming a 
+factor of $\approx 1.13$.
+We then pointed out in Section~\ref{sec:further_models} that assuming a 
 power law radius distribution is probably wrong if one wishes to study the HJ 
 rate discrepancy.
-If we instead assumed a Gaussian radius 
+If we instead assume a Gaussian radius 
 distribution~\citep[following][]{petigura_CKS_2017}, apparent 
@@
 
+\begin{comment}
 Of course, such calculations are only suggestive; a conclusive resolution 
@@
 hot Jupiters.
+\end{comment}
 
@@
 pressing.
-One concern is that space-based missions with telemetric requirements
+One issue is that space-based missions with telemetric requirements
 are often required to select target stars.
@@
 
-Further, in most transit surveys the detection efficiency is not
+Another concern is that in most transit surveys the detection efficiency is not
 a step function in SNR.
 Transit survey pipeline detection efficiencies are usually smooth
-functions in SNR; see for example the injection-recovery 
+functions~--~see for example the injection-recovery 
 simulations 
 performed by~\citet{christiansen_measuring_2016} on {\it Kepler}\ data, 
-and the resulting smooth detection efficiency adopted 
+and the resulting detection efficiency adopted 
 by~\citet{fulton_california-_2017}.
@@
 \paragraph{Connecting high resolution imaging to occurrence rates}
-A direct reason to address stellar multiplicity in transit surveys is that it 
+One reason to address stellar multiplicity in transit surveys is that it 
 changes the interpretation of planet candidates on a system-by-system level.
@@
 
-These high resolution imaging campaigns are also beginning to connect with
-occurrence rate calculations.
-The most recent rate studies have used~\citet{furlan_kepler_2017}'s 
-catalog to test the effects of removing KOI hosts with known companions, which 
-helps reduce contamination in the ``numerator'' of 
+These high resolution imaging campaigns are beginning to connect with
+occurrence rate calculations: using~\citet{furlan_kepler_2017}'s 
+catalog, recent studies tested the effects of removing KOI hosts with known 
+companions, reducing contamination in the ``numerator'' of 
 the occurrence rate (\citealt{fulton_california-_2017}; 
 \citealt{petigura_CKS_2017}).
-However, without an understanding of the multiplicity statistics of the 
-non-KOI stars, the true number of searchable stars, and thus the true 
-occurrence rates, will remain biased.
+While this is a good first step, the denominator remains uncorrected.
+To count the number of stars that were searched, further work on
+understanding the multiplicity statistics of KOI and non-KOI stars is 
+necessary. It may be possible to perform through a non-KOI star 
+high-resolution imaging effort, or perhaps by combining
+{\it Gaia} parallaxes with measured photometric fluxes to identify binary 
+systems.
 
 \paragraph{Does a detected planet orbit the primary or secondary?}
-One important step towards rectifying binarity's effects is identifying the 
-host star for any detected planets in binaries.
+A separate important step towards rectifying binarity's effects is identifying 
+the transit host star for detected planets in binaries.
 The current 
-wisdom is that nothing substantive can be said about the 
+wisdom is that, unless the planet can be confirmed to orbit either 
+component through analysis of the transit durations or centroids, nothing 
+substantive can be said about the 
 likelihood of a planet orbiting the primary vs. the 
 secondary~\citep[\textit{e.g.},][]{ciardi_understanding_2015,ziegler_robo-ao_2017}.
-This of course ignores cases when planets can be confirmed to orbit either 
-component by analyzing the transit durations or centroids.
 
@@
 Assuming a broken power law radius distribution, we showed in 
-Figure~\ref{fig:frac_model_3} that there are many cases where a detected 
-planet 
-is much more likely to orbit the primary.
+Figure~\ref{fig:frac_model_3} that detected 
+planets in binary systems are usually more likely to orbit the primary.
 A planet orbiting the secondary does lead to extreme corrections.
@@
 This work made use of NASA's Astrophysics Data System Bibliographic Services.
-
+%
+\newline
+%
 \software{\texttt{numpy}~\citep{walt_numpy_2011}, 

### 2018-01-30 paper/main.tex
cleaning up tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{introduction}
 
@@
 %$\delta_{\rm obs} \approx \mathcal{D} (r/R)^2$. 
-The noise N is the uncertainty in the
-determination of the flux ratio of the star inside and outside of
-transits.  Throughout this paper we will assume the photometric
-uncertainty to scale as the inverse square root of the number of
-photons collected from the source, {\it i.e.}, the dependence on
-stellar properties is $\sigma \propto (L_{\rm sys}/d^2)^{-1/2}$, where
-$L_{\rm sys}$ is the luminosity of the stellar system and $d$ is its
-distance from Earth.
+The noise N is the uncertainty in the determination of the flux ratio
+of the star inside and outside of transits.  Throughout this paper we
+will assume the photometric uncertainty to scale as the inverse square
+root of the number of photons collected from the source, {\it i.e.},
+the dependence on stellar properties is $\sigma \propto (L_{\rm
+sys}/d^2)^{-1/2}$, where $L_{\rm sys}$ is the luminosity of the
+stellar system and $d$ is its distance from Earth.
 % The solid angle coverage, telescope area, and
@@
 they do not have accurate enough parallaxes to tell that some of the
-stars are apparently overluminous. 
-They want to compute the number of planets with size $r$ per star of mass $M$.
-If the total number of stars for which such planets could be detected
-($N_\star$) and the number of detected planets ($N_{\rm det}$) are both 
-large, then the astronomers' estimate for the occurrence rate ($\Lambda$) is 
-simply
+stars are apparently overluminous.  They want to compute the number of
+planets with size $r$ per star of mass $M$.  If the total number of
+stars for which such planets could be detected ($N_\star$) and the
+number of detected planets ($N_{\rm det}$) are both large, then the
+astronomers' estimate for the occurrence rate ($\Lambda$) is simply
 \begin{equation}
@@
 error.  All three of the quantities in
-Equation~\ref{eq:occ_rate_simple} are subject to
-observational bias:
+Equation~\ref{eq:occ_rate_simple} are subject to observational bias:
 \begin{enumerate}
@@
     \item The number of planets, $N_{\det}$, is actually the number of
-    detected planets that {\it appear} to have size $r$, orbiting stars that 
-    {\it appear} to have mass $M$.
-    Whenever the planet-hosting star is part of a binary,
+      detected planets that {\it appear} to have size $r$, orbiting
+      stars that {\it appear} to have mass $M$.  Whenever the
+      planet-hosting star is part of a binary,
 %    
     \begin{itemize}
-        \item the planet's size will be misclassified because of the reduction
-        in the amplitude of the photometric signal;
-%        
-        \item the host star's properties could be misclassified because its 
-        light is combined with a second star of a different spectral type.
+        \item the planet's size will be misclassified because of the
+          reduction in the amplitude of the photometric signal;
+%        
+        \item the host star's properties could be misclassified
+          because its light is combined with a second star of a
+          different spectral type.
 %        
@@
 %        
-        \item toward lower values, because it does not include all of the
-        secondary stars that were searched for transiting planets;
+        \item toward lower values, because it does not include all of
+          the secondary stars that were searched for transiting
+          planets;
 %        
         \item toward higher values, because some of the stars that
-        appeared to be suitably small and bright to detect the desired
-        type of planet are in fact binaries for which the amplitude of
-        the photometric signal would be reduced to an undetectable
-        level.
+          appeared to be suitably small and bright to detect the
+          desired type of planet are in fact binaries for which the
+          amplitude of the photometric signal would be reduced to an
+          undetectable level.
 %        
@@
 Two other problems that may arise are not represented in
-Equation~\ref{eq:occ_rate_simple}.  One is astrophysical:
-the true occurrence rate of the desired type of planet may depend on
-whether the host is a single star, the primary star of a binary, or
-the secondary star of a binary.  Such differences could be caused by
-the requirement for long-term dynamical stability, or differences in
-the planet formation process.  When the search sample includes both
+Equation~\ref{eq:occ_rate_simple}.  One is astrophysical: the true
+occurrence rate of the desired type of planet may depend on whether
+the host is a single star, the primary star of a binary, or the
+secondary star of a binary.  Such differences could be caused by the
+requirement for long-term dynamical stability, or differences in the
+planet formation process.  When the search sample includes both
 singles and binaries, the detected planets are thereby drawn from
-different occurrence distributions~\citep[see,
-{\it e.g.},][]{wang_occurrence_2015}.
+different occurrence distributions~\citep[see, {\it
+e.g.},][]{wang_occurrence_2015}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{methods}
 
@@
 To clarify our terminology, we define ``apparent properties'' as the
-properties that one would infer about a system under the assumption that the 
-host star is single. For instance, the  ``apparent planet radius'', $r\a$, is
-the planet radius that one would infer from a transit signal, 
-assuming that the host star is single.
-The observed transit depth is given by the ratio of the apparent planet
-radius and the apparent stellar radius, $R\a$:
+properties that one would infer about a system under the assumption
+that the host star is single. For instance, the  ``apparent planet
+radius'', $r\a$, is the planet radius that one would infer from a
+transit signal, assuming that the host star is single.  The observed
+transit depth is given by the ratio of the apparent planet radius and
+the apparent stellar radius, $R\a$:
 \begin{equation}
@@
   = \left(\frac{r\a}{R\a}\right)^2
-= \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over L_{\rm 
-        sys}},
+  = \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over
+          L_{\rm sys}},
   \label{eq:delta_obs_general} 
 \end{equation}
-for $r$ the planet radius, $R_{\rm host}$ ($L_{\rm host}$) the 
-host star's radius (luminosity), and $L_{\rm sys}$ the 
-entire system's luminosity.
-In the example at hand, $R_{\rm host} =R\a = R$, since all stars have the same 
-size. For single star systems we have $r=r\a=r\p$. In twin binaries, 
-$r\a=r\p/\sqrt{2}$, since $L_{\rm sys}=2L$.
+for $r$ the planet radius, $R_{\rm host}$ ($L_{\rm host}$) the host
+star's radius (luminosity), and $L_{\rm sys}$ the entire system's
+luminosity.  In the example at hand, $R_{\rm host} =R\a = R$, since
+all stars have the same size. For single star systems we have
+$r=r\a=r\p$. In twin binaries, $r\a=r\p/\sqrt{2}$, since $L_{\rm
+sys}=2L$.
 
@@
 Finally, it is helpful to introduce an apparent rate density
-$\Gamma\a$, the average number of planets per star per unit apparent planet 
-radius. Analogous to Equation~\ref{eq:occ_rate_simple},  
+$\Gamma\a$, the average number of planets per star per unit apparent
+planet radius. Analogous to Equation~\ref{eq:occ_rate_simple},  
 \begin{equation}
@@
 \end{equation}
-where $n_{\rm det}={\rm d}N_{\rm det}/{\rm d}r\a$ is the number  
-of detected planets, per unit $r\a$, with apparent radius $r\a$.
-In Equation~\ref{eq:apparent_rate_density}, we neglect the dependence on 
+where $n_{\rm det}={\rm d}N_{\rm det}/{\rm d}r\a$ is the number  of
+detected planets, per unit $r\a$, with apparent radius $r\a$.  In
+Equation~\ref{eq:apparent_rate_density}, we neglect the dependence on
 stellar mass since all stars in this model have the same properties.
 
-To compute the number of detected planets, we consider the volumes within 
-which a signal of a given depth could be detected. At a fixed signal-to-noise floor, 
-there is a maximum searchable 
-distance~\citep{pepper_using_2003,pepper_searching_2005}.
-From Equation~\ref{eq:S_N_thresh}, this maximum searchable distance scales as
-\begin{equation}
-d \propto \delta_{\rm obs} \cdot L_{\rm 
-    sys}^{1/2}.
-\end{equation}
-Assuming that stars are uniformly distributed in space, the number 
-of searchable stars $N_\star$ is then proportional to
-\begin{equation}
-N_\star \propto n \delta_{\rm obs}^3 L_{\rm 
-    sys}^{3/2},
+To compute the number of detected planets, we consider the volumes
+within which a signal of a given depth could be detected. At a fixed
+signal-to-noise floor, there is a maximum searchable
+distance~\citep{pepper_using_2003,pepper_searching_2005}.  From
+Equation~\ref{eq:S_N_thresh}, this maximum searchable distance scales
+as
+\begin{equation}
+    d \propto \delta_{\rm obs} \cdot L_{\rm sys}^{1/2}.
+\end{equation}
+Assuming that stars are uniformly distributed in space, the number of
+searchable stars $N_\star$ is then proportional to
+\begin{equation}
+    N_\star \propto n \delta_{\rm obs}^3 L_{\rm sys}^{3/2},
 \label{eq:N_searchable_prop}
 \end{equation}
-where $n$ is the number per unit volume of {\it e.g.}, single star, or binary 
-systems.
-We neglect the dependence of $n$ on stellar type.
+where $n$ is the number per unit volume of {\it e.g.}, single star, or
+binary systems.  We neglect the dependence of $n$ on stellar type.
 
@@
     \caption{
-        Searchable volumes for single stars ({\it left}) and 
-        twin binaries ({\it right}), assuming that all stars have the 
-        same mass, radius, and luminosity, and that all planets have the same 
-        radius $r=r\p$.
-        {\it Top:} At an apparent radius $r\a=r\p$,
-        the observer searched twin binaries out to a
-        distance $\sqrt{2}\times$ that of single stars.
-        Because of dilution, there are no planets in twin binaries with 
-        $r\a=r\p$.
-        {\it Middle:} At $r\a=r\p/\sqrt{2}$, the 
-        maximum searchable distances are half those at $r\a=r\p$. 
-        The only detected planets with $r\a=r\p/\sqrt{2}$ orbit twin binaries.
-        {\it Bottom:} Planets with a true radius $r=r\p$ are searchable to 
-        a maximum distance $d_0$ around singles, and $d_0/\sqrt{2}$ around 
-        twin binaries.
+        Searchable volumes for single stars ({\it left}) and twin
+        binaries ({\it right}), assuming that all stars have the same
+        mass, radius, and luminosity, and that all planets have the
+        same radius $r=r\p$.
+        {\it Top:} At an apparent radius $r\a=r\p$, the observer
+        searched twin binaries out to a distance $\sqrt{2}\times$ that
+        of single stars.  Because of dilution, there are no planets in
+        twin binaries with $r\a=r\p$.
+        {\it Middle:} At $r\a=r\p/\sqrt{2}$, the maximum searchable
+        distances are half those at $r\a=r\p$.  The only detected
+        planets with $r\a=r\p/\sqrt{2}$ orbit twin binaries.
+        {\it Bottom:} Planets with a true radius $r=r\p$ are
+        searchable to a maximum distance $d_0$ around singles, and
+        $d_0/\sqrt{2}$ around twin binaries.
     }
@@
 The searchable volumes for this example are illustrated in
-Figure~\ref{fig:model_1_volumes}.
-At an apparent radius equal to the true radius ($r\a=r\p$), single stars 
-with $d<d_0$ are by definition searchable.
-Binaries with $r\a=r\p$ are also searchable, out to $\sqrt{2}d_0$. 
-However, in this example no such systems exist; all planets in twin binaries 
-have true radii $r=r\p$, and so are observed with apparent radii 
-$r\a=r\p/\sqrt{2}$, out to $d_0/\sqrt{2}$.
-At an apparent radius of $r\a=r\p/\sqrt{2}$, there could also be planets with 
-true radii $r=r\p/\sqrt{2}$ orbiting singles, but there are no such systems 
-in this model.
-
-How many planets are detected?
-If we assume that there are $N_\star^0(r\a)$ singles that are searchable for 
-planets with $r\a$, and that there are $Z_0$ planets per single, then 
-single stars contribute
-\begin{equation}
-n_{\rm det}^0(r\a) = N_\star^0(r\a) Z_0 p_{\rm tra} \cdot \delta(r\a - r_p)
-\end{equation}
-planet detections (per unit $r\a$), for $\delta$ the Dirac delta function.
-
-We can similarly compute the number of planet detections from binaries.
-First though, we define a ratio $\mu \equiv N_\star^{\rm b}(r\a) / 
-N_\star^0(r\a)$ 
-between the number of searchable binary systems and the number of searchable 
-singles at any $r\a$.
-This quantity is useful because although $N_\star^{\rm b}$ and $N_\star^0$ vary
-as a function of the observed transit depth, $\mu$ remains fixed.
-Applying this definition, at $r\a=r\p/\sqrt{2}$, some detections will come 
-from primaries,
+Figure~\ref{fig:model_1_volumes}.  At an apparent radius equal to the
+true radius ($r\a=r\p$), single stars with $d<d_0$ are by definition
+searchable.  Binaries with $r\a=r\p$ are also searchable, out to
+$\sqrt{2}d_0$.  However, in this example no such systems exist; all
+planets in twin binaries have true radii $r=r\p$, and so are observed
+with apparent radii $r\a=r\p/\sqrt{2}$, out to $d_0/\sqrt{2}$.  At an
+apparent radius of $r\a=r\p/\sqrt{2}$, there could also be planets
+with true radii $r=r\p/\sqrt{2}$ orbiting singles, but there are no
+such systems in this model.
+
+How many planets are detected?  If we assume that there are
+$N_\star^0(r\a)$ singles that are searchable for planets with $r\a$,
+and that there are $Z_0$ planets per single, then single stars
+contribute
+\begin{equation}
+n_{\rm det}^0(r\a) = 
+  N_\star^0(r\a) Z_0 p_{\rm tra} \cdot \delta(r\a - r_p)
+\end{equation}
+planet detections (per unit $r\a$), for $\delta$ the Dirac delta
+function.
+
+We can similarly compute the number of planet detections from
+binaries.  First though, we define a ratio $\mu \equiv N_\star^{\rm
+b}(r\a) / N_\star^0(r\a)$ between the number of searchable binary
+systems and the number of searchable singles at any $r\a$.  This
+quantity is useful because although $N_\star^{\rm b}$ and $N_\star^0$
+vary as a function of the observed transit depth, $\mu$ remains fixed.
+Applying this definition, at $r\a=r\p/\sqrt{2}$, some detections will
+come from primaries,
 \begin{equation}
@@
 \end{equation}
-where $Z_1$ is the number of planets per primary, $Z_2$ is the number of 
-planets per secondary, and $p_{\rm tra}$ is the same for identical stars.
-For twin binaries, Equation~\ref{eq:N_searchable_prop} gives $\mu = 
-2^{3/2} n_{\rm b}/n_{\rm s}$, where $n_{\rm b}$ is the number density of 
-binaries in a volume-limited sample.
-
-The last item we need to write down the apparent rate density $\Gamma\a(r\a)$ 
-is the number of unresolved point-sources on sky that the observer thinks are 
-searchable, $N_\star$.
-From the definition of $\mu$,
+where $Z_1$ is the number of planets per primary, $Z_2$ is the number
+of planets per secondary, and $p_{\rm tra}$ is the same for identical
+stars.  For twin binaries, Equation~\ref{eq:N_searchable_prop} gives
+$\mu = 2^{3/2} n_{\rm b}/n_{\rm s}$, where $n_{\rm b}$ is the number
+density of binaries in a volume-limited sample.
+
+The last item we need to write down the apparent rate density
+$\Gamma\a(r\a)$ is the number of unresolved point-sources on sky that
+the observer thinks are searchable, $N_\star$.  From the definition of
+$\mu$,
 \begin{equation}
@@
 \end{equation}
-relates the number of apparently searchable point-sources and the number of 
-searchable singles.
-There are in fact $N_\star^0(r\a)\times (1 + 2\mu)$ searchable stars
-at any given $r\a$; the observers are under-counting.
-
-Using Equation~\ref{eq:apparent_rate_density}, the apparent rate density 
-reported when ignoring binarity is
+relates the number of apparently searchable point-sources and the
+number of searchable singles.  There are in fact $N_\star^0(r\a)\times
+(1 + 2\mu)$ searchable stars at any given $r\a$; the observers are
+under-counting.
+
+Using Equation~\ref{eq:apparent_rate_density}, the apparent rate
+density reported when ignoring binarity is
 \begin{align}
@@
 \end{align}
-The first term is from singles, and the second is from binaries.
-The number of searchable singles at a given apparent radius, 
-$N_\star^0(r\a)$, makes no appearance.
-The observer has erred in Equation~\ref{eq:model_1_apparent_rate_density} by 
-under-counting the number of searchable stars at any apparent radius, and by
-inferring incorrect planet radii in binary systems.
+The first term is from singles, and the second is from binaries.  The
+number of searchable singles at a given apparent radius,
+$N_\star^0(r\a)$, makes no appearance.  The observer has erred in
+Equation~\ref{eq:model_1_apparent_rate_density} by under-counting the
+number of searchable stars at any apparent radius, and by inferring
+incorrect planet radii in binary systems.
 
@@
     \caption{
-        Apparent occurrence rate $\Lambda\a$, and occurrence rate for singles 
-        $\Lambda_0$, for a model with one type of star, one type of planet, 
-        and twin binaries (same as Figure~\ref{fig:model_1_volumes}).
-        We assume a twin binary fraction of $0.1$, and that
-        single, primary, and secondary stars host planets at equal 
-        rates.
-        If the true planet radius is $r\p$, all planets detected in binaries 
-        will have apparent radii $r\a = r\p/\sqrt{2}$;
+        Apparent occurrence rate $\Lambda\a$, and occurrence rate for
+        singles $\Lambda_0$, for a model with one type of star, one
+        type of planet, and twin binaries (same as
+        Figure~\ref{fig:model_1_volumes}).  We assume a twin binary
+        fraction of $0.1$, and that single, primary, and secondary
+        stars host planets at equal rates.  If the true planet radius
+        is $r\p$, all planets detected in binaries will have apparent
+        radii $r\a = r\p/\sqrt{2}$;
         Equation~\ref{eq:model_1_apparent_rate_density} gives the
@@
 
-To assess the severity of these errors, we must assume both a binary fraction, 
-and also the true number of planets per single, primary, and secondary star 
-($Z_0,Z_1,Z_2$).
-For the former,~\citet{raghavan_survey_2010} found a multiplicity 
-fraction of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$.
-By multiplicity fraction, they meant ``fraction of systems in a volume-limited 
-sample that are multiple'', which we simplistically conflate with the
-fraction of systems in a volume-limited sample that are binaries:
+To assess the severity of these errors, we must assume both a binary
+fraction, and also the true number of planets per single, primary, and
+secondary star ($Z_0,Z_1,Z_2$).  For the
+former,~\citet{raghavan_survey_2010} found a multiplicity fraction of
+0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$.  By
+multiplicity fraction, they meant ``fraction of systems in a
+volume-limited sample that are multiple'', which we simplistically
+conflate with the fraction of systems in a volume-limited sample that
+are binaries:
 \begin{equation}
@@
 \end{equation}
-Of course not all of these are binaries are close to being ``twin'' binaries 
-as we have assumed in our simple calculation.
-Perhaps only a tenth of them have pairs of stars close enough
-in their basic properties to produce errors as significant as those
-we have been considering.  Thus, an appropriate estimate
-for the binary fraction is of order $0.05$.
-The ratio of the apparent to single star rate densities,
-\begin{equation}
-X_\Gamma(r) \equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} \right|_{r\a 
-    \rightarrow r},
-\end{equation}
-can then be evaluated as a ``correction factor''.
-At the true planet radius, $X_\Gamma(r\p)=1/(1+\mu)$.
-This yields a correction $X_\Gamma$ of 0.87~(0.76) if the binary fraction is 
-0.05~(0.10).
-All together the various effects produce biases of order 10\% in the
-occurrence rates.  We will see that this level of error is characteristic
-of many of our more complicated models, as well.
-
-An alternative assumption is that secondaries do not host planets. In that 
-case, the correction to the rate density at the true planet radius becomes 
-$X_\Gamma(r\p) = (1+2\mu)/(1+\mu)^2$.
-This gives a correction of 0.98~(0.94) if the binary fraction is 0.05~(0.10).
-Although the secondaries certainly should have planets, 
-the sensitivity of $\Gamma\a/\Gamma_0$ to the relative number of
-planets per single, primary, and secondary will also become important
-as we proceed.
+Of course not all of these are binaries are close to being ``twin''
+binaries as we have assumed in our simple calculation.  Perhaps only a
+tenth of them have pairs of stars close enough in their basic
+properties to produce errors as significant as those we have been
+considering.  Thus, an appropriate estimate for the binary fraction is
+of order $0.05$.  The ratio of the apparent to single star rate
+densities,
+\begin{equation}
+    X_\Gamma(r) \equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)}
+      \right|_{r\a \rightarrow r},
+\end{equation}
+can then be evaluated as a ``correction factor''.  At the true planet
+radius, $X_\Gamma(r\p)=1/(1+\mu)$.  This yields a correction
+$X_\Gamma$ of 0.87~(0.76) if the binary fraction is 0.05~(0.10).  All
+together the various effects produce biases of order 10\% in the
+occurrence rates.  We will see that this level of error is
+characteristic of many of our more complicated models, as well.
+
+An alternative assumption is that secondaries do not host planets. In
+that case, the correction to the rate density at the true planet
+radius becomes $X_\Gamma(r\p) = (1+2\mu)/(1+\mu)^2$.  This gives a
+correction of 0.98~(0.94) if the binary fraction is 0.05~(0.10).
+Although the secondaries certainly should have planets, the
+sensitivity of $\Gamma\a/\Gamma_0$ to the relative number of planets
+per single, primary, and secondary will also become important as we
+proceed.
 
@@
 
-A simple extension to the previous example helps distinguish 
-between the apparent and underlying planet populations.
-Consider now a universe that is the same as in
-Section~\ref{sec:model_1}, except that half of planets have radii $r\p$, 
-while the other half have radii $r\p/\sqrt{2}$.
-The rate densities are
+A simple extension to the previous example helps distinguish between
+the apparent and underlying planet populations.  Consider now a
+universe that is the same as in Section~\ref{sec:model_1}, except that
+half of planets have radii $r\p$, while the other half have radii
+$r\p/\sqrt{2}$.  The rate densities are
 \begin{equation}
@@
 
-Following an identical line of reasoning as in Section~\ref{sec:model_1}, the 
-apparent rate density can be written
+Following an identical line of reasoning as in
+Section~\ref{sec:model_1}, the apparent rate density can be written
 \begin{align}
@@
 $N_\star^0(r\a)$ terms cancel, leaving only the $\mu$ weights.
-However, there are now three detected planet sizes.
-Also different is that two populations contribute at $r\a = 
-r\p/\sqrt{2}$:
-the first population is singles with $r=r\p/\sqrt{2}$, and the second is twin 
-binaries with $r=r\p$.
-Both populations are detected out to the same maximum searchable distance.
-More generally, at any given apparent radius, there will be contributions
-from both singles, primaries, and secondaries~---~but the relative weights
-between these contributions will depend on the underlying occurrence rates.
+However, there are now three detected planet sizes.  Also different is
+that two populations contribute at $r\a = r\p/\sqrt{2}$: the first
+population is singles with $r=r\p/\sqrt{2}$, and the second is twin
+binaries with $r=r\p$.  Both populations are detected out to the same
+maximum searchable distance.  More generally, at any given apparent
+radius, there will be contributions from both singles, primaries, and
+secondaries~---~but the relative weights between these contributions
+will depend on the underlying occurrence rates.
 
@@
 
-To generalize the procedure of Section~\ref{sec:simplest}, we consider an 
-SNR-limited transit survey in which the singles and primaries can have 
-arbitrary properties, but their true masses are known by the observer.
-We assume that there are some functions $L(M)$ and $R(M)$ that specify a 
-star's luminosity and radius in terms of its mass, and that the volume-limited 
-binary mass ratio distribution, $f(q)$, is independent of the primary's mass.
-We also allow arbitrary true rate densities for singles, primaries, 
-and secondaries ($\Gamma_0, \Gamma_1, \Gamma_2$).
-We presume that the observers always take the properties of a binary system to 
-be those of the primary.
-
-Given this laundry-list of assumptions, a general formula for the apparent 
-rate density follows:
+To generalize the procedure of Section~\ref{sec:simplest}, we consider
+an SNR-limited transit survey in which the singles and primaries can
+have arbitrary properties, but their true masses are known by the
+observer.  We assume that there are some functions $L(M)$ and $R(M)$
+that specify a star's luminosity and radius in terms of its mass, and
+that the volume-limited binary mass ratio distribution, $f(q)$, is
+independent of the primary's mass.  We also allow arbitrary true rate
+densities for singles, primaries, and secondaries ($\Gamma_0,
+\Gamma_1, \Gamma_2$).  We presume that the observers always take the
+properties of a binary system to be those of the primary.
+
+Given this laundry-list of assumptions, a general formula for the
+apparent rate density follows:
 \begin{align}
@@
     & \quad\quad\quad\quad\quad \left.\left.
-+\int_0^1 {\rm d}q\, \frac{f(q)}{\mathcal{A}^3}\cdot \frac{q}{\mathcal{B}}
+    +\int_0^1 {\rm d}q\, 
+         \frac{f(q)}{\mathcal{A}^3}\cdot \frac{q}{\mathcal{B}}
         \Gamma_2\left({r\a\over \mathcal{B}}, qM\a\right)\cdot
@@
 where ${\rm BF}=n\b/(n\s+n\b)$ is the volume-limited binary fraction,
-and $\mathcal{A}(q,M\a)$ [$\mathcal{B}(q,M\a)$] are the dilution terms for 
-primaries [secondaries], whose functional dependences are omitted for 
-notational simplicity.
-The dilution terms can be written
-\begin{equation}
-\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}
+and $\mathcal{A}(q,M\a)$ [$\mathcal{B}(q,M\a)$] are the dilution terms
+for primaries [secondaries], whose functional dependences are omitted
+for notational simplicity.  The dilution terms can be written
+\begin{equation}
+    \mathcal{A}(q, M\a)
+    = \sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}
     = (1+q^\alpha)^{-1/2},
@@
 \begin{equation}
-\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
-            sys}(M\a, q)} }
+  \mathcal{B}(q, M\a)
+  = {R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm sys}(M\a, q)} }
   = q^{-1} (1+q^{-\alpha})^{-1/2}
 \end{equation}
-where the latter equalities assume $L\propto M^\alpha \propto R^\alpha$ (the 
-former are more general).
-The rate densities depend on both apparent radius and mass 
-because even if the primaries and singles were to have fixed
-mass, the mass of secondaries would vary, and so this dependence cannot be 
-immediately omitted.
+where the latter equalities assume $L\propto M^\alpha \propto
+R^\alpha$ (the former are more general).  The rate densities depend on
+both apparent radius and mass because even if the primaries and
+singles were to have fixed mass, the mass of secondaries would vary,
+and so this dependence cannot be immediately omitted.
 
 A derivation of Equation~\ref{eq:general_Gamma_a} is given in the
-\hyperref[sec:appendix]{Appendix}; its qualitative features are the same as 
-from our simple model (Equation~\ref{eq:model_1_apparent_rate_density}).
-The terms inside the curly braces $\{ \ldots \}$ are the sum of 
-the apparent rate densities from singles, primaries, and secondaries.
-The contribution from singles is not affected by binarity.
-In the contributions from primaries and secondaries,
-planets with $(r\a, M\a)$ are associated with 
-systems of different planetary and stellar properties, as determined
-by the mass ratio $q$ of each binary.
-This corresponds to true planet radii and stellar masses 
-$(r\a/\mathcal{A},M\a)$ for primaries, and $(r\a/\mathcal{B},qM\a)$ for 
-secondaries.
-These contributions are then integrated over the mass ratio distribution 
-including the effect of Malmquist bias, $f(q)/\mathcal{A}^3$, discussed 
-further below. Finally, the latter term in the apparent rate density of 
-secondaries comes from a correction for the overestimated transit probability.
+\hyperref[sec:appendix]{Appendix}; its qualitative features are the
+same as from our simple model
+(Equation~\ref{eq:model_1_apparent_rate_density}).  The terms inside
+the curly braces $\{ \ldots \}$ are the sum of the apparent rate
+densities from singles, primaries, and secondaries.  The contribution
+from singles is not affected by binarity.  In the contributions from
+primaries and secondaries, planets with $(r\a, M\a)$ are associated
+with systems of different planetary and stellar properties, as
+determined by the mass ratio $q$ of each binary.  This corresponds to
+true planet radii and stellar masses $(r\a/\mathcal{A},M\a)$ for
+primaries, and $(r\a/\mathcal{B},qM\a)$ for secondaries.  These
+contributions are then integrated over the mass ratio distribution
+including the effect of Malmquist bias, $f(q)/\mathcal{A}^3$,
+discussed further below. Finally, the latter term in the apparent rate
+density of secondaries comes from a correction for the overestimated
+transit probability.
 
 \paragraph{Ratio of searchable binaries to singles}
-We must also specify the exact form of $\mu$, the ratio of 
-the number of searchable binary systems to singles.
-Given the observed signal $\delta_{\rm obs}$ and apparent stellar mass $M\a$, 
-recall that the maximum searchable distances for singles and binaries are 
-proportional to $\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm 
-obs}\cdot [L(M\a)+L(qM\a)]^{1/2}$.
-Applying Equation~\ref{eq:N_searchable_prop},
-\begin{equation}
-\mu({\rm BF},M\a) = 
-\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
-\int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
-f(q)\,\mathrm{d}q.
+
+We must also specify the exact form of $\mu$, the ratio of the number
+of searchable binary systems to singles.  Given the observed signal
+$\delta_{\rm obs}$ and apparent stellar mass $M\a$, recall that the
+maximum searchable distances for singles and binaries are proportional
+to $\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm obs}\cdot
+[L(M\a)+L(qM\a)]^{1/2}$.  Applying
+Equation~\ref{eq:N_searchable_prop},
+\begin{equation}
+    \mu({\rm BF},M\a)
+    = 
+    \frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}
+    =
+    \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over
+        L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
     \label{eq:mu_general}
 \end{equation}
-If the binary fraction is independent of $q$, $L \propto M^\alpha$, and $f(q) 
-\propto q^\beta$, this simplifies to
+If the binary fraction is independent of $q$, $L \propto M^\alpha$,
+and $f(q) \propto q^\beta$, this simplifies to
 \begin{equation}
@@
         The mass ratio distribution for a magnitude-limited sample of
-        binary stars, in which the underlying volume-limited distribution is 
-        uniform, qualitatively similar to
-        Figure~16 of \citet{raghavan_survey_2010}.
-        At a given observed transit depth, the searchable binaries in a 
-        transit survey are magnitude-limited.
+        binary stars, in which the underlying volume-limited
+        distribution is uniform, qualitatively similar to Figure~16 of
+        \citet{raghavan_survey_2010}.  At a given observed transit
+        depth, the searchable binaries in a transit survey are
+        magnitude-limited.
     }
@@
 This can be understood as a Malmquist bias: at fixed observed transit
-depth, for singles and primaries with the same luminosity, binaries are 
-searchable to a greater distance.
-Specifically, the sample of searchable binaries is magnitude-limited.
-Given a searchable binary, the probability that it has a mass ratio $q$ 
-scales as
+depth, for singles and primaries with the same luminosity, binaries
+are searchable to a greater distance.  Specifically, the sample of
+searchable binaries is magnitude-limited.  Given a searchable binary,
+the probability that it has a mass ratio $q$ scales as
 \begin{equation}
@@
 \end{equation}
-where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
-ratio $q$, and the first term is the Malmquist bias when $L\propto M^\alpha$.
-We show this magnitude-limited mass ratio distribution for the $\beta=0$ case 
-in Figure~\ref{fig:q_distribn_mag_limited}.
-In Monte Carlo simulations of transit surveys, it is 
-important to draw binaries from a correctly biased mass-ratio distribution 
-\citep[\textit{e.g.},][]{bakos_hatsouth:_2013,sullivan_transiting_2015,
-    gunther_new_2017}.
+where $q^\beta$ is the volume-limited probability of drawing a binary
+of mass ratio $q$, and the first term is the Malmquist bias when
+$L\propto M^\alpha$.  We show this magnitude-limited mass ratio
+distribution for the $\beta=0$ case in
+Figure~\ref{fig:q_distribn_mag_limited}.  In Monte Carlo simulations
+of transit surveys, it is important to draw binaries from a correctly
+biased mass-ratio distribution~\citep[\textit{e.g.},][]{
+  bakos_hatsouth:_2013,sullivan_transiting_2015, gunther_new_2017}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{results}
 
@@
 \label{sec:more_complicated}
-We will now apply our general equation for the apparent rate 
-density (Equation~\ref{eq:general_Gamma_a}) to study binarity's effects in 
-regimes of observational interest.
-In the following, we write the rate density for each type of star, 
-$\Gamma_i(r)$, as the product of a shape function and a constant:
+
+We will now apply our general equation for the apparent rate density
+(Equation~\ref{eq:general_Gamma_a}) to study binarity's effects in
+regimes of observational interest.  In the following, we write the
+rate density for each type of star, $\Gamma_i(r)$, as the product of a
+shape function and a constant:
 \begin{equation}
@@
 where $i=0$ corresponds to single stars, $i=1$ to primaries of
-binaries, and $i=2$ to secondaries of binaries.
-The shape function is normalized to unity.
-The $Z_i$'s are each system type's occurrence rate $\Lambda_i$, integrated 
-over all planetary radii. In other words, they are number of planets per 
-single, primary, or secondary star.
-We want to consider the effects of varying not only $f_i(r)$ but also the
+binaries, and $i=2$ to secondaries of binaries.  The shape function is
+normalized to unity.  The $Z_i$'s are each system type's occurrence
+rate $\Lambda_i$, integrated over all planetary radii. In other words,
+they are number of planets per single, primary, or secondary star.  We
+want to consider the effects of varying not only $f_i(r)$ but also the
 relative values of the $Z_i$'s.
@@
 \subsubsection{Twin binaries}
-We begin introducing realism by keeping all binaries as twins, but letting the 
-planet radius distributions vary.
-First, we assume a power law planet radius distribution,
+We begin introducing realism by keeping all binaries as twins, but
+letting the planet radius distributions vary.  First, we assume a
+power law planet radius distribution,
 \begin{equation}
@@
 \end{equation}
-for $f(r)$ the radius shape function, and $\mathcal{N}_r$ the shape function's 
-normalization.
-The resulting apparent rate density is 
+for $f(r)$ the radius shape function, and $\mathcal{N}_r$ the shape
+function's normalization.  The resulting apparent rate density is 
 \begin{equation}
@@
 which is quite similar to the twin binary, fixed-planet case
-(Equation~\ref{eq:model_1_apparent_rate_density}), 
-except for in the radius dependence and normalization.
-As in Section~\ref{sec:model_1}, $\mu = 2^{3/2} n\b/n\s$.
-If the $Z_i$'s are equal, the ``correction factor'' relative to the rate 
-density for singles becomes quite simple:
+(Equation~\ref{eq:model_1_apparent_rate_density}), except for in the
+radius dependence and normalization.  As in Section~\ref{sec:model_1},
+$\mu = 2^{3/2} n\b/n\s$.  If the $Z_i$'s are equal, the ``correction
+factor'' relative to the rate density for singles becomes quite
+simple:
 \begin{align}
@@
 \end{align}
-If the binary fraction is $0.1$, $\mu\approx 0.15$. Taking $\delta=-2.92$ from 
-\citet{howard_planet_2012},  we find $\Gamma\a/\Gamma_0 = 
-1.004$.
-In other words, the apparent rate density is an {\it over}estimate compared to 
-the rate density of single stars, with a relative difference $\delta \Gamma_0 
-= |\Gamma_0~-~\Gamma\a|/\Gamma_0$ of 0.4\%.
-This is quite a small effect!
-Clearly though, it cannot apply at small radii, since $f(r) \propto r^\delta$ 
-diverges; \citet{howard_planet_2012}'s 
-results indicate that the power law planet radius distribution holds for 
-$r\a\gtrsim 2r_\oplus$.
-It is similarly nonsensical for $f(r)$ to be finite above some upper radius 
-limit $r_{\rm u}$, perhaps around $\approx 24r_\oplus$, based on the most 
-inflated hot Jupiters.
-Imposing an upper cut-off of $r_{\rm u}$ would lead to smaller values of 
-$\Gamma(r\a)$ 
-down to $r_{\rm u}/\sqrt{2}$, compared to an intrinsic power law without the 
-cut-off.
-We are not particularly interested in this effect because there are better 
-models for hot Jupiter occurrence rates that we will discuss in 
-Section~\ref{sec:further_models}.
-If the assumptions behind this model are at all applicable to real transit 
-surveys, Equation~\ref{eq:power_law_correction} suggests that for $2r_\oplus 
-\lesssim r\a \lesssim 17r_\oplus$, binarity's impact on apparent occurrence 
-rates is quite small.
+If the binary fraction is $0.1$, $\mu\approx 0.15$. Taking
+$\delta=-2.92$ from \citet{howard_planet_2012},  we find
+$\Gamma\a/\Gamma_0 = 1.004$.  In other words, the apparent rate
+density is an {\it over}estimate compared to the rate density of
+single stars, with a relative difference $\delta \Gamma_0 =
+|\Gamma_0~-~\Gamma\a|/\Gamma_0$ of 0.4\%.  This is quite a small
+effect!  Clearly though, it cannot apply at small radii, since $f(r)
+\propto r^\delta$ diverges; \citet{howard_planet_2012}'s results
+indicate that the power law planet radius distribution holds for
+$r\a\gtrsim 2r_\oplus$.  It is similarly nonsensical for $f(r)$ to be
+finite above some upper radius limit $r_{\rm u}$, perhaps around
+$\approx 24r_\oplus$, based on the most inflated hot Jupiters.
+Imposing an upper cut-off of $r_{\rm u}$ would lead to smaller values
+of $\Gamma(r\a)$ down to $r_{\rm u}/\sqrt{2}$, compared to an
+intrinsic power law without the cut-off.  We are not particularly
+interested in this effect because there are better models for hot
+Jupiter occurrence rates that we will discuss in
+Section~\ref{sec:further_models}.  If the assumptions behind this
+model are at all applicable to real transit surveys,
+Equation~\ref{eq:power_law_correction} suggests that for $2r_\oplus
+\lesssim r\a \lesssim 17r_\oplus$, binarity's impact on apparent
+occurrence rates is quite small.
 
@@
 
-To check whether non-twin binaries change the preceding result, we now assume 
-$f(q) = q^\beta/\mathcal{N}_q$, for $\mathcal{N}_q$ the normalization.
-This changes $\mu$ (Equation~\ref{eq:mu_general} simplifies to 
-Equation~\ref{eq:mu_power_laws}).
-It may also affect the rate density, which could be a function of the 
-varying stellar mass.
-Absorbing this dependence into a power law as well,
+To check whether non-twin binaries change the preceding result, we now
+assume $f(q) = q^\beta/\mathcal{N}_q$, for $\mathcal{N}_q$ the
+normalization.  This changes $\mu$ (Equation~\ref{eq:mu_general}
+simplifies to Equation~\ref{eq:mu_power_laws}).  It may also affect
+the rate density, which could be a function of the varying stellar
+mass.  Absorbing this dependence into a power law as well,
 \begin{equation}
@@
 where $Z_i$ is dimensionless, and the normalization constants carry
-the units (each side has units $[r^{-1} M^{-1}]$).
-We assume that stars are a one-parameter family, given by $R \propto M \propto 
-L^{\frac{1}{\alpha}}$, so that a given value of $q$ determines everything 
-about a secondary.
-
-We are mostly interested in the apparent rate density's radius dependence.
-Marginalizing Equation~\ref{eq:general_Gamma_a} over apparent stellar mass, we 
-find
-that when $Z_0=Z_1=Z_2$,
+the units (each side has units $[r^{-1} M^{-1}]$).  We assume that
+stars are a one-parameter family, given by $R \propto M \propto
+L^{\frac{1}{\alpha}}$, so that a given value of $q$ determines
+everything about a secondary.
+
+We are mostly interested in the apparent rate density's radius
+dependence.  Marginalizing Equation~\ref{eq:general_Gamma_a} over
+apparent stellar mass, we find that when $Z_0=Z_1=Z_2$,
 \begin{align}
@@
     \right. \\
+    %isn't latex great?
     &\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
@@
 \end{align}
-where $\gamma$ does not appear because of the marginalization over $M\a$.
-For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the 
+where $\gamma$ does not appear because of the marginalization over
+$M\a$.  For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the
 summed integrals in Equation~\ref{eq:powerlaw_vary_binary} give
-$(\ldots)\approx 
-1.50249$. %171211_model_integrals.nb
-For $n\b / (n\b + n\s)=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$; the
-relative difference between the apparent rate density and the rate density 
-around singles is 4.8\%.
-This indicates that considering only twin binaries gave us correct 
-intuition: for a power law radius distribution 
-($2r_\oplus \lesssim r\a \lesssim 17r_\oplus$) in which there are the same 
-number of planets orbiting singles, primaries, and secondaries, binarity 
-influences apparent planet occurrence rates around Sun-like stars at the 
-$\sim$few percent level.
+$(\ldots)\approx 1.50249$. %171211_model_integrals.nb
+For $n\b / (n\b + n\s)=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$;
+the relative difference between the apparent rate density and the rate
+density around singles is 4.8\%.  This indicates that considering only
+twin binaries gave us correct intuition: for a power law radius
+distribution ($2r_\oplus \lesssim r\a \lesssim 17r_\oplus$) in which
+there are the same number of planets orbiting singles, primaries, and
+secondaries, binarity influences apparent planet occurrence rates
+around Sun-like stars at the $\sim$few percent level.
 
@@
     \caption{
-        {\it Left:} apparent rate density ($\Gamma\a$) and single star rate 
-        density ($\Gamma_0$). {\it Right:} apparent occurrence rate 
-        ($\Lambda\a$) and single star occurrence rate ($\Lambda_0$), over 
-        $0.5r_\oplus$ bins.
-        The true planet radius distribution is specified by 
-        Equation~\ref{eq:model3_radius_distribution}. 
-        This model assumes that the observer knows the true properties of all 
-        the singles and primaries, and that the volume-limited mass 
-        ratios of secondaries are drawn from a uniform distribution. Further, 
-        we take $Z_0=Z_1=0.5$ throughout; $Z_0,Z_1,Z_2$ are the number of 
-        planets per single, primary, and secondary star.
-        The rate and rate density are related by $\Lambda|_a^b 
-        = \int_{a}^{b}\Gamma\,{\rm d}r$.
+        {\it Left:} apparent rate density ($\Gamma\a$) and single star
+        rate density ($\Gamma_0$). {\it Right:} apparent occurrence
+        rate ($\Lambda\a$) and single star occurrence rate
+        ($\Lambda_0$), over $0.5r_\oplus$ bins.  The true planet
+        radius distribution is specified by
+        Equation~\ref{eq:model3_radius_distribution}.  This model
+        assumes that the observer knows the true properties of all the
+        singles and primaries, and that the volume-limited mass ratios
+        of secondaries are drawn from a uniform distribution. Further,
+        we take $Z_0=Z_1=0.5$ throughout; $Z_0,Z_1,Z_2$ are the number
+        of planets per single, primary, and secondary star.  The rate
+        and rate density are related by $\Lambda|_a^b =
+        \int_{a}^{b}\Gamma\,{\rm d}r$.
     }
@@
 Though the details of the planet radius distribution $\Gamma_i(r)$ at
-$r<2r_\oplus$ are currently an active topic of research, we can consider how 
-binarity affects this regime under different plausible assumptions.
-For instance, assume that the true radius shape function is
+$r<2r_\oplus$ are currently an active topic of research, we can
+consider how binarity affects this regime under different plausible
+assumptions.  For instance, assume that the true radius shape function
+is
 \begin{align}
@@
 As in the previous model, we presume that the observers know the true
-properties of all singles and primaries. The masses, radii, 
-and luminosities of stars vary as $R \propto M \propto L^{\frac{1}{\alpha}}$.
-Our ``nominal model'' remains the same: 
+properties of all singles and primaries. The masses, radii, and
+luminosities of stars vary as $R \propto M \propto
+L^{\frac{1}{\alpha}}$.  Our ``nominal model'' remains the same:
 $\alpha=3.5$, $\beta=\gamma=0$, $\delta=-2.92$.
 
-At apparent radii $r\a > 2r_\oplus$, the results of this model are the same as 
-those from Section~\ref{sub:powerlaw_varying_binaries}.
-For $r\a < 2r_\oplus$, the equations are tedious, but still tractable.
-For simplicity, we insert Equation~\ref{eq:model3_radius_distribution} into 
-Equation~\ref{eq:general_Gamma_a}, and integrate using a computer 
+At apparent radii $r\a > 2r_\oplus$, the results of this model are the
+same as those from Section~\ref{sub:powerlaw_varying_binaries}.  For
+$r\a < 2r_\oplus$, the equations are tedious, but still tractable.
+For simplicity, we insert Equation~\ref{eq:model3_radius_distribution}
+into Equation~\ref{eq:general_Gamma_a}, and integrate using a computer
 program. We refer the interested reader to our online
@@
 The output is validated against analytic predictions in the $r\a >
-2r_\oplus$ and the $r\a < 2r_\oplus/\sqrt{2}$ regimes, and is plotted in
-Figure~\ref{fig:occ_rate_model_3_log}.
-
-\paragraph{The rate of Earth analogs}
-The immediately arresting result there is a ``bump'' in the apparent rate 
-density at $r\a < 2r_\oplus$: the true rate for singles is less than the 
-inferred rate.
-For the case in which secondaries host as many (half as many) planets as 
-single stars, this means an overestimate of the absolute occurrence rate by 
-$\approx 50\%$ ($\approx 25\%$).
-The ``bump'' exists even for the $Z_2/Z_0=0$ case as a $\approx 10\%$ effect.
-The magnitude of this evidently error depends strongly on the prevalence of 
-planets around secondaries.
-
-\paragraph{Hot Jupiter occurrence rates}
-Taking Figure~\ref{fig:occ_rate_model_3_log} and integrating the rate density, 
-we can compare the apparent hot Jupiter 
-occurrence rate with the true rate for singles.
-In the most extreme case of $Z_2/Z_0=0$, we find that $\Lambda_{{\rm 
-HJ},0}/\Lambda_{\rm HJ,a} = 1.13$, where
-\begin{equation}
-\Lambda_{\rm HJ,a} = \int_{8r_\oplus}^{\infty} \Gamma\a(r)\,{\rm d}r,
+2r_\oplus$ and the $r\a < 2r_\oplus/\sqrt{2}$ regimes, and is plotted
+in Figure~\ref{fig:occ_rate_model_3_log}.
+
+\paragraph{The rate of Earth analogs} The immediately arresting result
+there is a ``bump'' in the apparent rate density at $r\a < 2r_\oplus$:
+the true rate for singles is less than the inferred rate.  For the
+case in which secondaries host as many (half as many) planets as
+single stars, this means an overestimate of the absolute occurrence
+rate by $\approx 50\%$ ($\approx 25\%$).  The ``bump'' exists even for
+the $Z_2/Z_0=0$ case as a $\approx 10\%$ effect.  The magnitude of
+this evidently error depends strongly on the prevalence of planets
+around secondaries.
+
+\paragraph{Hot Jupiter occurrence rates} Taking
+Figure~\ref{fig:occ_rate_model_3_log} and integrating the rate
+density, we can compare the apparent hot Jupiter occurrence rate with
+the true rate for singles.  In the most extreme case of $Z_2/Z_0=0$,
+we find that $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 1.13$, where
+\begin{equation}
+    \Lambda_{\rm HJ,a} =
+      \int_{8r_\oplus}^{\infty} \Gamma\a(r)\,{\rm d}r,
 \end{equation}
@@
 %occ_rate_vs_radius_model_3_withtext_Zsub2_0.00_rpu_22.5.pdf
-If $Z_2/Z_0>0$, binarity affects the apparent hot Jupiter rate less: when 
-$Z_2/Z_0=0.5$, we find $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 1.06$.
-We discuss this issue further in Section~\ref{sec:further_models}.
+If $Z_2/Z_0>0$, binarity affects the apparent hot Jupiter rate less:
+when $Z_2/Z_0=0.5$, we find $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} =
+1.06$.  We discuss this issue further in
+Section~\ref{sec:further_models}.
 
@@
     \caption{
-        Fraction of detected planet at a given apparent planet radius coming 
-        from singles (solid lines), primaries (dashed lines), and secondaries 
-        (dotted lines).
-        Three different values for $Z_2/Z_0$ are selected: $1$ (blue), $0.5$ 
-        (orange), $0$ (green).
-        The assumed true planet radius distribution is a broken power law
+        Fraction of detected planet at a given apparent planet radius
+        coming from singles (solid lines), primaries (dashed lines),
+        and secondaries (dotted lines).  Three different values for
+        $Z_2/Z_0$ are selected: $1$ (blue), $0.5$ (orange), $0$
+        (green).  The assumed true planet radius distribution is a
+        broken power law
         (Equation~\ref{eq:model3_radius_distribution}; same as
@@
 
-It would be nice to improve our intuition for how much the secondaries matter.
-We have the understanding that for a given true planet radius, secondaries 
-have a much smaller searchable volume than primaries or singles.
-Does this necessarily imply that if we are given a detected planet with some 
-apparent radius $r\a$, which is then observed by high-resolution imaging to 
-exist in a binary, that the planet probably orbits the primary?
-
-We explore this quantitatively in Figure~\ref{fig:frac_model_3}.
-The lines in this figure are computed using expressions given in the 
-appendix for the number of detections coming from singles, primaries, and 
-secondaries (Eqs.~\ref{eq:n_det_0},~\ref{eq:n_det_1}, and~\ref{eq:n_det_2}).
-
-In short, the detected planet usually is more likely to orbit the primary, but 
-this statement depends on the number of planets orbiting secondaries, and also 
-on the apparent radius of the detected planet.
-In the scenario that high-resolution imaging finds a system with $r\a > 
-2r_\oplus$ in a binary, roughly $\sim\! 2.5\times$ more detected planets orbit 
-primaries than secondaries, for the $Z_2/Z_0=1$ case.
-For the $Z_2/Z_0=0.5$ case, $\sim\! 5\times$ more detected 
-planets orbit primaries than secondaries.
-So detected planets in binaries with large apparent radii (relative to the 
-cutoff in the intrinsic rate density) are more likely to orbit the primary.
-
-The situation for $r\a < 2r_\oplus$ is more nuanced.
-For the $Z_2=0$ and $Z_2/Z_0=0.5$ cases, detected planets in binaries are 
-still always more likely to orbit the primary.
-However, if there are as many planets orbiting the secondaries as the 
-primaries, then there is a turn-over radius, $\approx 0.4r_\oplus$, 
-beyond which more of the detected planets in binaries come from secondaries: 
-they have all been ``diluted down'' from larger true planetary radii!
-Although this (apparent) radius is at the limit of current detection 
-sensitivities, this effect will be interesting for future instruments to 
-investigate.
+It would be nice to improve our intuition for how much the secondaries
+matter.  We have the understanding that for a given true planet
+radius, secondaries have a much smaller searchable volume than
+primaries or singles.  Does this necessarily imply that if we are
+given a detected planet with some apparent radius $r\a$, which is then
+observed by high-resolution imaging to exist in a binary, that the
+planet probably orbits the primary?
+
+We explore this quantitatively in Figure~\ref{fig:frac_model_3}.  The
+lines in this figure are computed using expressions given in the
+appendix for the number of detections coming from singles, primaries,
+and secondaries (Eqs.~\ref{eq:n_det_0},~\ref{eq:n_det_1},
+and~\ref{eq:n_det_2}).
+
+In short, the detected planet usually is more likely to orbit the
+primary, but this statement depends on the number of planets orbiting
+secondaries, and also on the apparent radius of the detected planet.
+In the scenario that high-resolution imaging finds a system with $r\a
+> 2r_\oplus$ in a binary, roughly $\sim\! 2.5\times$ more detected
+planets orbit primaries than secondaries, for the $Z_2/Z_0=1$ case.
+For the $Z_2/Z_0=0.5$ case, $\sim\! 5\times$ more detected planets
+orbit primaries than secondaries.  So detected planets in binaries
+with large apparent radii (relative to the cutoff in the intrinsic
+rate density) are more likely to orbit the primary.
+
+The situation for $r\a < 2r_\oplus$ is more nuanced.  For the $Z_2=0$
+and $Z_2/Z_0=0.5$ cases, detected planets in binaries are still always
+more likely to orbit the primary.  However, if there are as many
+planets orbiting the secondaries as the primaries, then there is a
+turn-over radius, $\approx 0.4r_\oplus$, beyond which more of the
+detected planets in binaries come from secondaries: they have all been
+``diluted down'' from larger true planetary radii!  Although this
+(apparent) radius is at the limit of current detection sensitivities,
+this effect will be interesting for future instruments to investigate.
 
 Further, Figure~\ref{fig:frac_model_3} shows that going from apparent
-radii of $2r_\oplus$ to $\approx 1.4r_\oplus$, the fraction of detected 
-planets with binary companions increases by $\approx 6-12\%$, depending on the 
-assumed value of $Z_2/Z_0$. %~\footnote{
-%The increase can be derived analytically.
-%Let the fraction of total detected planets from primaries at a given 
-%apparent radius be $F_1(r\a)$, so $F_1(r\a) \equiv n_{\rm det}^1(r\a)/n_{\rm 
-%    det}^{\rm tot}$.
-%Let the analogous quantity for secondaries be $F_2(r\a)$.
-%In the planet-less secondaries case ($F_2(r\a)=0$), one can 
-%analyze Eqs~\ref{eq:n_det_0} and~\ref{eq:n_det_1} semi-analytically and show 
+radii of $2r_\oplus$ to $\approx 1.4r_\oplus$, the fraction of
+detected planets with binary companions increases by $\approx 6-12\%$,
+depending on the assumed value of $Z_2/Z_0$. %~\footnote{
+%The increase can be derived analytically.  Let the fraction of total
+%detected planets from primaries at a given apparent radius be
+%$F_1(r\a)$, so $F_1(r\a) \equiv n_{\rm det}^1(r\a)/n_{\rm det}^{\rm
+%tot}$.  Let the analogous quantity for secondaries be $F_2(r\a)$.  In
+%the planet-less secondaries case ($F_2(r\a)=0$), one can analyze
+%Eqs~\ref{eq:n_det_0} and~\ref{eq:n_det_1} semi-analytically and show
 %that $F_1(2r_\oplus/\sqrt{2})/F_1(2r_\oplus) \approx 1.19$.
-%check_companion_fractions.py, and LB's notes 2017/12/21.0
-%}.
-Intuitively speaking, this ``shift'' is a feature of any radius distribution 
-that declines at large radii, and flattens below some cutoff $r_{\rm c}$.
-This is because (for dilution about primaries)
-at apparent radii $r\a < r_{\rm c}/\sqrt{2}$, relatively more planets will be 
-``diluted'' into the given $r\a$, since there are more planets in 
-the undiluted distribution from $r\a$ to $\sqrt{2}r\a$.
-We compare this prediction with recent observations in 
+%check_companion_fractions.py, and LB's notes 2017/12/21.0 }.
+Intuitively speaking, this ``shift'' is a feature of any radius
+distribution that declines at large radii, and flattens below some
+cutoff $r_{\rm c}$.  This is because (for dilution about primaries) at
+apparent radii $r\a < r_{\rm c}/\sqrt{2}$, relatively more planets
+will be ``diluted'' into the given $r\a$, since there are more planets
+in the undiluted distribution from $r\a$ to $\sqrt{2}r\a$.  We compare
+this prediction with recent observations in
 Section~\ref{sec:discussion}.
@@
 The radius distribution specified by
-Equation~\ref{eq:model3_radius_distribution} 
-misses some important features reported in state of the art 
-studies of planetary occurrence.
+Equation~\ref{eq:model3_radius_distribution} misses some important
+features reported in state of the art studies of planetary occurrence.
 
@@
     \caption{
-        {\it Left:} rate density and {\it right:} rate (over $0.25r_\oplus$ 
-        bins) as a function of planet radius in a model with a radius gap 
-        (Equation~\ref{eq:model4_radius_distribution}).
-        Other than the intrinsic radius distribution, this model has the same 
+        {\it Left:} rate density and {\it right:} rate (over
+        $0.25r_\oplus$ bins) as a function of planet radius in a model
+        with a radius gap
+        (Equation~\ref{eq:model4_radius_distribution}).  Other than
+        the intrinsic radius distribution, this model has the same
         assumptions as Figure~\protect\ref{fig:occ_rate_model_3_log}.
@@
 
-\citet{fulton_california-_2017} recently reported a ``gap'' in 
-the radius-period 
+\citet{fulton_california-_2017} recently reported a ``gap'' in the
+radius-period
 plane~\citep{petigura_california-kepler_2017,johnson_california-kepler_2017}.
-The existence of the gap has been independently corroborated from a sample of 
-KOIs with asteroseismically-determined stellar 
-parameters~\citep{van_eylen_asteroseismic_2017}.
-Precise measurement of the gap's features, in particular its width, 
-depth, and shape, will require accurate occurrence rates.
-To illustrate binarity's role in this problem, we make identical assumptions 
-as in Section~\ref{sec:model_3}, but instead assume an intrinsic radius 
+The existence of the gap has been independently corroborated from a
+sample of KOIs with asteroseismically-determined stellar
+parameters~\citep{van_eylen_asteroseismic_2017}.  Precise measurement
+of the gap's features, in particular its width, depth, and shape, will
+require accurate occurrence rates.  To illustrate binarity's role in
+this problem, we make identical assumptions as in
+Section~\ref{sec:model_3}, but instead assume an intrinsic radius
 distribution
@@
 \end{align}
-The resulting true and apparent rates are shown in Figure~\ref{fig:model_4}.
-If left uncorrected, binarity makes the gap appear more shallow, and flattens 
-the step-function edges.
-Of course, other effects could also ``blur'' the gap in the planet radius 
-dimension. 
-In particular, the valley's period-dependence is almost certainly not flat
-\citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.
-This means that any study measuring the gap's width or depth while accounting 
-for 
-binarity must either perform tests at fixed orbital period, or else 
-marginalize over period and account for the associated blurring in the planet 
-radius dimension.
+The resulting true and apparent rates are shown in
+Figure~\ref{fig:model_4}.  If left uncorrected, binarity makes the gap
+appear more shallow, and flattens the step-function edges.  Of course,
+other effects could also ``blur'' the gap in the planet radius
+dimension.  In particular, the valley's period-dependence is almost
+certainly not flat
+\citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.  This
+means that any study measuring the gap's width or depth while
+accounting for binarity must either perform tests at fixed orbital
+period, or else marginalize over period and account for the associated
+blurring in the planet radius dimension.
 
@@
 
-In the recent study by~\citet{petigura_CKS_2017}, hot Jupiters appear as an 
-island in period-radius space, rather than as a continuous component of a 
-power law distribution.
-This means that the apparent HJ rates computed in 
-Section~\ref{sec:model_3} are probably inaccurate.
-Instead, let us consider a Gaussian radius shape function,
+In the recent study by~\citet{petigura_CKS_2017}, hot Jupiters appear
+as an island in period-radius space, rather than as a continuous
+component of a power law distribution.  This means that the apparent
+HJ rates computed in Section~\ref{sec:model_3} are probably
+inaccurate.  Instead, let us consider a Gaussian radius shape
+function,
 \begin{equation}
@@
 \end{equation}
-with $\bar{r} = 14r_\oplus$ and $\sigma = 2r_\oplus$.
-As always, $\Gamma_i(r) = Z_i f(r)$.
-We then compute $\Gamma\a(r\a)$, and plot it in Figure~\ref{fig:gaussian_HJ}.
-Integrating for $r\a > 8r_\oplus$ to find hot Jupiter rates,
-we find the opposite effect as in the power law model.
-For $Z_2/Z_0>0$, 
-the apparent HJ rate is {\it greater} than the true rate for singles.
-The effect is maximal when there are as many hot Jupiters orbiting secondaries 
-as singles, in which case
+with $\bar{r} = 14r_\oplus$ and $\sigma = 2r_\oplus$.  As always,
+$\Gamma_i(r) = Z_i f(r)$.  We then compute $\Gamma\a(r\a)$, and plot
+it in Figure~\ref{fig:gaussian_HJ}.  Integrating for $r\a > 8r_\oplus$
+to find hot Jupiter rates, we find the opposite effect as in the power
+law model.  For $Z_2/Z_0>0$, the apparent HJ rate is {\it greater}
+than the true rate for singles.  The effect is maximal when there are
+as many hot Jupiters orbiting secondaries as singles, in which case
 $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 0.81$.
 %int_rate_density_vs_radius_model_7_withtext*manyZs.pdf
-For the case when no hot Jupiters orbit secondaries, $\Lambda_{{\rm HJ},0} 
-\approx \Lambda_{\rm HJ,a}$ to within one percent.
+For the case when no hot Jupiters orbit secondaries, $\Lambda_{{\rm
+HJ},0} \approx \Lambda_{\rm HJ,a}$ to within one percent.
 Qualitatively, the apparent HJ rate is greater than the true rate for
-singles because binary systems can have an extra uncounted star that yields 
-hot Jupiter detections.
+singles because binary systems can have an extra uncounted star that
+yields hot Jupiter detections.
 
@@
     \caption{
-        Rate density for a population of planets with true radii $r$ drawn from
-        a Gaussian with mean $14r_\oplus$ and standard deviation $2r_\oplus$.
-        This is similar to the hot Jupiter distribution presented 
-        by~\citet{petigura_CKS_2017}.
+        Rate density for a population of planets with true radii $r$
+        drawn from a Gaussian with mean $14r_\oplus$ and standard
+        deviation $2r_\oplus$.  This is similar to the hot Jupiter
+        distribution presented by~\citet{petigura_CKS_2017}.
     }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{discussion}
 
@@
 \paragraph{How bad is ignoring binarity?}
-This study has shown that under a reasonable set of simplifying assumptions, 
-ignoring binarity introduces systematic errors to star and planet counts in 
-transit surveys, which then biases derived occurrence rates.
-Thus far, occurrence rate calculations\footnote{
-    A list of occurrence rate papers is maintained at 
+This study has shown that under a reasonable set of simplifying
+assumptions, ignoring binarity introduces systematic errors to star
+and planet counts in transit surveys, which then biases derived
+occurrence rates.  Thus far, occurrence rate calculations\footnote{ A
+list of occurrence rate papers is maintained at
 \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
@@
 multiplicity~\citep[\textit{e.g.},][]{howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,dressing_occurrence_2015,burke_terrestrial_2015}.
-For {\it Kepler} occurrence rates specifically, 
-it seems that no one has yet carefully assessed binarity's importance, or lack 
-thereof.
+For {\it Kepler} occurrence rates specifically, it seems that no one
+has yet carefully assessed binarity's importance, or lack thereof.
 Although this study does not resolve the problem, it does suggest the
-approximate scale of the possible errors in a survey-independent manner.
-The suggestion of Section~\ref{sec:model_2} is that for $r\a \gtrsim 2r_\oplus$, 
-binarity can be ignored down to a precision of a few percent.
-For apparent radii $\lesssim 2r_\oplus$, the picture is less forgiving:
-Section~\ref{sec:model_3} suggests that relative differences between apparent 
-rates 
-and true rates around singles could easily reach $\sim\! 50\%$.
+approximate scale of the possible errors in a survey-independent
+manner.  The suggestion of Section~\ref{sec:model_2} is that for $r\a
+\gtrsim 2r_\oplus$, binarity can be ignored down to a precision of a
+few percent.  For apparent radii $\lesssim 2r_\oplus$, the picture is
+less forgiving: Section~\ref{sec:model_3} suggests that relative
+differences between apparent rates and true rates around singles could
+easily reach $\sim\! 50\%$.
 
 \paragraph{The rate of Earth analogs}
-In line with {\it Kepler}'s primary science goal, the rate of Earth-like 
-planets orbiting Sun-like stars has been independently measured by 
+In line with {\it Kepler}'s primary science goal, the rate of
+Earth-like planets orbiting Sun-like stars has been independently
+measured by
 \citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
 foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
-These efforts found that the one-year terrestrial planet occurrence rate 
-is between $\approx\! 0.03$ and $\approx\!1$ per Sun-like star,
+These efforts found that the one-year terrestrial planet occurrence
+rate is between $\approx\! 0.03$ and $\approx\!1$ per Sun-like star,
 depending on assumptions that are made when calculating the
-rate~\citep[see][Figure~17]{burke_terrestrial_2015}.
-In Section~\ref{sec:model_3}, our power law model indicates that when 
-primaries, 
-singles, and secondaries host the same number of planets, the apparent rate is 
-50\% higher than the true rate around single stars.
-Though this bias seems large, it is currently smaller than the other 
-systematic factors that dominate the dispersion in $\eta_\oplus$ 
-measurements.
-If future analyses determine absolute values of $\eta_\oplus$ to 
-better than a factor of two, binarity will likely merit closer attention.
-
-One caveat to our assessment of binarity's relevance for 
-$\eta_\oplus$ measurements is that none of our models 
-included the rate density's period-dependence. However, binaries with 
-separations $\lesssim 10\,{\rm AU}$ could
-provoke dynamical instabilities, leading to fewer Earth-like planets per 
+rate~\citep[see][Figure~17]{burke_terrestrial_2015}.  In
+Section~\ref{sec:model_3}, our power law model indicates that when
+primaries, singles, and secondaries host the same number of planets,
+the apparent rate is 50\% higher than the true rate around single
+stars.  Though this bias seems large, it is currently smaller than the
+other systematic factors that dominate the dispersion in $\eta_\oplus$
+measurements.  If future analyses determine absolute values of
+$\eta_\oplus$ to better than a factor of two, binarity will likely
+merit closer attention.
+
+One caveat to our assessment of binarity's relevance for $\eta_\oplus$
+measurements is that none of our models included the rate density's
+period-dependence. However, binaries with separations $\lesssim
+10\,{\rm AU}$ could provoke dynamical instabilities, leading to fewer
+Earth-like planets per
 star~\citep[\textit{e.g.},][]{holman_long-term_1999,wang_influence_2014,
-    kraus_impact_2016}.
-This would affect transit survey measurements of $\eta_\oplus$ beyond our 
-rough estimate.
+kraus_impact_2016}.  This would affect transit survey measurements of
+$\eta_\oplus$ beyond our rough estimate.
 
 \paragraph{Hot Jupiter rate discrepancy}
-While binarity may appreciably affect $\eta_\oplus$ measurements, our analysis
-suggests that it is unlikely to influence the hot Jupiter rate discrepancy.
-The context of this disagreement is that hot Jupiter occurrence rates measured 
-by transit surveys ($\approx 0.5\%$) are marginally lower than those found by 
-radial velocity surveys ($\approx 1\%$; see Table~\ref{tab:hj_rates}).
-Though the discrepancy has weak statistical significance ($<3\sigma$),
-one reason to expect a difference is that the corresponding stellar 
-populations have distinct metallicities.
-As argued by \citet{gould_frequency_2006}, the RV sample is biased towards 
-metal-rich stars, which have been measured by RV surveys to preferentially 
-host more giant 
+While binarity may appreciably affect $\eta_\oplus$ measurements, our
+analysis suggests that it is unlikely to influence the hot Jupiter
+rate discrepancy.  The context of this disagreement is that hot
+Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$)
+are marginally lower than those found by radial velocity surveys
+($\approx 1\%$; see Table~\ref{tab:hj_rates}).  Though the discrepancy
+has weak statistical significance ($<3\sigma$), one reason to expect a
+difference is that the corresponding stellar populations have distinct
+metallicities.  As argued by \citet{gould_frequency_2006}, the RV
+sample is biased towards metal-rich stars, which have been measured by
+RV surveys to preferentially host more giant
 planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005}.
 Investigating the discrepancy from the metallicty
-angle,~\citet{guo_metallicity_2017} measured the
-{\it Kepler} field's mean metallicity to be $[{\rm M/H}]_{\rm Kepler}= 
--0.045\pm0.009$, which is lower than the California Planet Search's mean of 
-$[{\rm M/H}]_{\rm CPS}= -0.005\pm0.006$.
-The former value agrees with that measured by \citet{dong_metallicities_2014}.
-Refitting for the metallicity exponent in $\Lambda_{\rm HJ} \propto 10^{\beta 
-    [{\rm M/H}] }$, \citeauthor{guo_metallicity_2017}\! found $\beta = 2.1\pm 
-0.7$, and noted that this would imply that the metallicity difference could 
-account for a $\approx 20\%$ relative difference in the measured rates between 
-the CKS and {\it Kepler}\ samples~--~not a 50\% relative difference\footnote{
-    \citet{petigura_CKS_2017} recently found $\beta = 3.4^{0.9}_{-0.8}$.
-    This gives a $\approx 25\%$ relative difference, indicating metallicity 
-    could 
-    account for about half of the ``hot Jupiter rate discrepancy''.
-}.
-\citeauthor{guo_metallicity_2017}\! concluded that ``other factors, such as 
-binary contamination and imperfect stellar properties'' must also be at play.
-
-The hypothesis that binarity might matter is grounded in the fact that radial 
-velocity and transit surveys treat binarity differently.
-Radial velocity surveys typically reject both visual and spectroscopic binaries
-\citep[\textit{e.g.},][]{wright_frequency_2012}.
-Transit surveys observe binaries, but the question of whether they 
-were searchable to begin with is left for later interpretation.
-In spectroscopic follow-up of transiting planet candidates, the prevalence of 
-astrophysical false-positives may also lead to a tendency against confirming 
-transiting planets in binary systems.
-A separate observational bias is that the RV surveys typically observe 
-chromospherically ``quiet'' stars, which may bias their detection probability 
-high~\citep{bastien_radial_2014}.
-
-Ignoring these complications, we concentrated in this work on binarity's 
-effects on star counts and the apparent radii of detected planets.
-Assuming a power law radius distribution, and that no secondaries host HJs,
-we found in Section~\ref{sec:model_3} that binarity 
-could lead to underestimated HJ rates relative to singles by a multiplicative 
-factor of $\approx 1.13$.
-We then pointed out in Section~\ref{sec:further_models} that assuming a 
-power law radius distribution is probably wrong if one wishes to study the HJ 
-rate discrepancy.
-If we instead assume a Gaussian radius 
-distribution~\citep[following][]{petigura_CKS_2017}, apparent 
-HJ rates are {\it greater} than the true rate around singles: the effect goes 
+angle,~\citet{guo_metallicity_2017} measured the {\it Kepler} field's
+mean metallicity to be $[{\rm M/H}]_{\rm Kepler}= -0.045\pm0.009$,
+which is lower than the California Planet Search's mean of $[{\rm
+M/H}]_{\rm CPS}= -0.005\pm0.006$.  The former value agrees with that
+measured by \citet{dong_metallicities_2014}.  Refitting for the
+metallicity exponent in $\Lambda_{\rm HJ} \propto 10^{\beta [{\rm
+M/H}] }$, \citeauthor{guo_metallicity_2017}\! found $\beta = 2.1\pm
+0.7$, and noted that this would imply that the metallicity difference
+could account for a $\approx 20\%$ relative difference in the measured
+rates between the CKS and {\it Kepler}\ samples~--~not a 50\% relative
+difference\footnote{ \citet{petigura_CKS_2017} recently found $\beta =
+3.4^{0.9}_{-0.8}$.  This gives a $\approx 25\%$ relative difference,
+indicating metallicity could account for about half of the ``hot
+Jupiter rate discrepancy''.  }.  \citeauthor{guo_metallicity_2017}\!
+concluded that ``other factors, such as binary contamination and
+imperfect stellar properties'' must also be at play.
+
+The hypothesis that binarity might matter is grounded in the fact that
+radial velocity and transit surveys treat binarity differently.
+Radial velocity surveys typically reject both visual and spectroscopic
+binaries \citep[\textit{e.g.},][]{wright_frequency_2012}.  Transit
+surveys observe binaries, but the question of whether they were
+searchable to begin with is left for later interpretation.  In
+spectroscopic follow-up of transiting planet candidates, the
+prevalence of astrophysical false-positives may also lead to a
+tendency against confirming transiting planets in binary systems.  A
+separate observational bias is that the RV surveys typically observe
+chromospherically ``quiet'' stars, which may bias their detection
+probability high~\citep{bastien_radial_2014}.
+
+Ignoring these complications, we concentrated in this work on
+binarity's effects on star counts and the apparent radii of detected
+planets.  Assuming a power law radius distribution, and that no
+secondaries host HJs, we found in Section~\ref{sec:model_3} that
+binarity could lead to underestimated HJ rates relative to singles by
+a multiplicative factor of $\approx 1.13$.  We then pointed out in
+Section~\ref{sec:further_models} that assuming a power law radius
+distribution is probably wrong if one wishes to study the HJ rate
+discrepancy.  If we instead assume a Gaussian radius
+distribution~\citep[following][]{petigura_CKS_2017}, apparent HJ rates
+are {\it greater} than the true rate around singles: the effect goes
 the wrong way.
 \begin{comment}
-If we believe the assumed power law radius distribution, we can ask whether 
-this ``correction factor'' might help resolve the discrepancy.
-Explicitly, we ask: what is the probability of \citet{wright_frequency_2012}'s 
-result, given a rate drawn from the stated bounds of~\citet{petigura_CKS_2017}?
-In other words, we first take the true HJ rate per thousand stars as 
-$\Lambda_{\rm HJ} = 5.7 \pm 1.3$, with Gaussian uncertainties. 
-We then draw from a Poisson distribution and compute the probability of 
-detecting at least 10 hot Jupiters in a sample of 836 stars.
-Without accounting for binarity or metallicity, only 4\% of RV surveys would 
-detect at least 10 hot Jupiters.
-If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account 
-for~\citet{guo_metallicity_2017}'s measured metallicity difference between the 
-{\it Kepler}\ field and the local solar neighborhood, 9\% of RV surveys would 
-detect at least 10 hot Jupiters.
-If we multiply once more by $1.13$ to account for binarity's supposed bias, we 
-find that 14\% of RV surveys would detect at least 10 hot Jupiters, still 
-suggesting a weak discrepancy.
-
-This suggestion should be taken with caution, because it (likely incorrectly) 
-assumes a power law radius distribution.
+  If we believe the assumed power law radius distribution, we can ask
+  whether this ``correction factor'' might help resolve the
+  discrepancy.  Explicitly, we ask: what is the probability of
+  \citet{wright_frequency_2012}'s result, given a rate drawn from the
+  stated bounds of~\citet{petigura_CKS_2017}?  In other words, we
+  first take the true HJ rate per thousand stars as $\Lambda_{\rm HJ}
+  = 5.7 \pm 1.3$, with Gaussian uncertainties.  We then draw from a
+  Poisson distribution and compute the probability of detecting at
+  least 10 hot Jupiters in a sample of 836 stars.  Without accounting
+  for binarity or metallicity, only 4\% of RV surveys would detect at
+  least 10 hot Jupiters.  If we multiply $\Lambda_{\rm HJ}$ by $1.2$
+  to account for~\citet{guo_metallicity_2017}'s measured metallicity
+  difference between the {\it Kepler}\ field and the local solar
+  neighborhood, 9\% of RV surveys would detect at least 10 hot
+  Jupiters.  If we multiply once more by $1.13$ to account for
+  binarity's supposed bias, we find that 14\% of RV surveys would
+  detect at least 10 hot Jupiters, still suggesting a weak
+  discrepancy.  This suggestion should be taken with caution, because
+  it (incorrectly) assumes a power law radius distribution.
 \end{comment}
-The ``hot Jupiter island'' reported by~\citet{petigura_CKS_2017} cannot 
-possibly be part of a continuous power law. 
-Thus binarity is unlikely to resolve the HJ rate discrepancy.
+The ``hot Jupiter island'' reported by~\citet{petigura_CKS_2017}
+cannot possibly be part of a continuous power law.  Thus binarity is
+unlikely to resolve the HJ rate discrepancy.
 
 \begin{comment}
-Of course, such calculations are only suggestive; a conclusive resolution 
-of binarity's effects may require a detailed understanding of the 
-{\it Kepler}\ field's multiplicity statistics, and the mission's completeness 
-(both for candidate detection and follow-up).
-For instance, if hot Jupiters are less likely to be confirmed in binary 
-systems, this might bias the rates low.
-Alternatively, {\it TESS}\ is expected to discover over $10^4$ 
-giant planets~\citep{ricker_transiting_2014,sullivan_transiting_2015}.
-Though they will be difficult to distinguish from false positives, one 
-possible use of this sample will be to measure an occurrence rate of 
-short-period giant planets with minimal error from counting statistics.
-Our models suggest that binarity will only become an appreciable fraction of 
-the error budget at the $\approx 10\%$ precision level.
-This should be sufficient for a rate measurement precise enough to indicate a 
-preference between $\approx 0.5\%$ and $\approx 1\%$ of Sun-like stars hosting 
-hot Jupiters.
+  Of course, such calculations are only suggestive; a conclusive
+  resolution of binarity's effects may require a detailed
+  understanding of the {\it Kepler}\ field's multiplicity statistics,
+  and the mission's completeness (both for candidate detection and
+  follow-up).  For instance, if hot Jupiters are less likely to be
+  confirmed in binary systems, this might bias the rates low.
+  Alternatively, {\it TESS}\ is expected to discover over $10^4$ giant
+  planets~\citep{ricker_transiting_2014,sullivan_transiting_2015}.
+  Though they will be difficult to distinguish from false positives,
+  one possible use of this sample will be to measure an occurrence
+  rate of short-period giant planets with minimal error from counting
+  statistics.  Our models suggest that binarity will only become an
+  appreciable fraction of the error budget at the $\approx 10\%$
+  precision level.  This should be sufficient for a rate measurement
+  precise enough to indicate a preference between $\approx 0.5\%$ and
+  $\approx 1\%$ of Sun-like stars hosting hot Jupiters.
 \end{comment}
@@
 \paragraph{Practical effects: smooth detection efficiencies; finite SNR floors}
-To apply this study to real transit surveys, a few practical concerns become 
-pressing.
-One issue is that space-based missions with telemetric requirements
-are often required to select target stars.
+To apply this study to real transit surveys, a few practical concerns
+become pressing.  One issue is that space-based missions with
+telemetric requirements are often required to select target stars.
 Even if the selection process is aimed at creating an SNR-limited
 survey, as~\citet{batalha_selection_2010} did for {\it Kepler},
-uncertainties in stellar parameters and the modeled instrument performance
-can lead to deviations away from an SNR-limited stellar sample.
-
-Another concern is that in most transit surveys the detection efficiency is not
-a step function in SNR.
-Transit survey pipeline detection efficiencies are usually smooth
-functions~--~see for example the injection-recovery 
-simulations 
-performed by~\citet{christiansen_measuring_2016} on {\it Kepler}\ data, 
-and the resulting detection efficiency adopted 
-by~\citet{fulton_california-_2017}.
-If we were to assume a smooth detection probability in SNR, we would need to 
-include a detection efficiency term in 
-Equation~\ref{eq:apparent_rate_density} to inversely weight for planets 
-with low probabilities of being detected.
-
-The simplest way to avoid the conceptual complications of accounting for 
-finite detection efficiency is to raise the SNR floor, to {\it e.g.,} 
-${\rm SNR} \approx 12$ for {\it Kepler} 
-(\citealt{fulton_california-_2017}, Figure~5).
-To a good approximation, this allows one to use the boolean distinctions 
-``searchable'' and ``not searchable'' for signals of an observed depth (at 
-fixed orbital period).
-By making the survey strictly SNR-limited, rather than ``fuzzily 
-SNR-limited'', binarity's effects become much easier to model.
-Since the minimum SNR for detection is set in an arbitrary manner 
-anyway\footnote{For example, {\it Kepler}'s threshold of ${\rm SNR}=7.1$ was 
-set for there to be no more than one statistical false alarm across the full 
-{\it Kepler} campaign~\citep{jenkins_tests_2002}. Equally valid would have 
-been to insist on no more than $10^{-3}$ false alarms per survey, raising the 
-detection floor.
-}, this simplification would put occurrence rate studies on 
-clearer conceptual 
-ground, and facilitate the process of converting the observed distributions
-of apparent radii into true radius distributions.
+uncertainties in stellar parameters and the modeled instrument
+performance can lead to deviations away from an SNR-limited stellar
+sample.
+
+Another concern is that in most transit surveys the detection
+efficiency is not a step function in SNR.  Transit survey pipeline
+detection efficiencies are usually smooth functions~--~see for example
+the injection-recovery simulations performed
+by~\citet{christiansen_measuring_2016} on {\it Kepler}\ data, and the
+resulting detection efficiency adopted
+by~\citet{fulton_california-_2017}.  If we were to assume a smooth
+detection probability in SNR, we would need to include a detection
+efficiency term in Equation~\ref{eq:apparent_rate_density} to
+inversely weight for planets with low probabilities of being detected.
+
+The simplest way to avoid the conceptual complications of accounting
+for finite detection efficiency is to raise the SNR floor, to {\it
+e.g.,} ${\rm SNR} \approx 12$ for {\it Kepler}
+(\citealt{fulton_california-_2017}, Figure~5).  To a good
+approximation, this allows one to use the boolean distinctions
+``searchable'' and ``not searchable'' for signals of an observed depth
+(at fixed orbital period).  By making the survey strictly SNR-limited,
+rather than ``fuzzily SNR-limited'', binarity's effects become much
+easier to model.  Since the minimum SNR for detection is set in an
+arbitrary manner anyway\footnote{For example, {\it Kepler}'s threshold
+of ${\rm SNR}=7.1$ was set for there to be no more than one
+statistical false alarm across the full {\it Kepler}
+campaign~\citep{jenkins_tests_2002}. Equally valid would have been to
+insist on no more than $10^{-3}$ false alarms per survey, raising the
+detection floor.  }, this simplification would put occurrence rate
+studies on clearer conceptual ground, and facilitate the process of
+converting the observed distributions of apparent radii into true
+radius distributions.
 
 Finally, our calculations also ignore the fact that any given transit
-survey's finite SNR floor might censor the apparent rate density.
-If the surveyed stars all have the same size, this is equivalent to 
-saying that there might be a cutoff in apparent planet radii, below which no 
-planets are detected.
-The effects on our main results (e.g., 
+survey's finite SNR floor might censor the apparent rate density.  If
+the surveyed stars all have the same size, this is equivalent to
+saying that there might be a cutoff in apparent planet radii, below
+which no planets are detected.  The effects on our main results (e.g.,
 Figs.~\ref{fig:occ_rate_model_3_log},~\ref{fig:frac_model_3},
@@
 \begin{comment}
-If one insists on using a smooth detection efficiency, then life probably 
-becomes more complicated.
-It might then be necessary to model the detection pipeline's efficiency while 
-somehow marginalizing over binarity.
-Since the relative number of detections (at fixed $\delta_{\rm obs}$) coming 
-from singles, primaries, and secondaries changes as a function of the 
-intrinsic distribution of planet parameters (Figure~\ref{fig:frac_model_3}), 
+  If one insists on using a smooth detection efficiency, then life
+  probably becomes more complicated.  It might then be necessary to
+  model the detection pipeline's efficiency while somehow
+  marginalizing over binarity.  Since the relative number of
+  detections (at fixed $\delta_{\rm obs}$) coming from singles,
+  primaries, and secondaries changes as a function of the intrinsic
+  distribution of planet parameters (Figure~\ref{fig:frac_model_3}),
   some complicated deconvolution might be required.
@@
 \paragraph{Connecting high resolution imaging to occurrence rates}
-One reason to address stellar multiplicity in transit surveys is that it 
-changes the interpretation of planet candidates on a system-by-system level.
-Consequently, high resolution imaging 
-campaigns have measured the multiplicities of almost all {\it Kepler}\ Objects 
-of Interest 
-\citep{howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
+One reason to address stellar multiplicity in transit surveys is that
+it changes the interpretation of planet candidates on a
+system-by-system level.  Consequently, high resolution imaging
+campaigns have measured the multiplicities of almost all {\it Kepler}\
+Objects of Interest~\citep{
+  howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
   horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
@@
 The results of these programs have been collected
-by~\citet{furlan_kepler_2017}, and they represent an important advance in 
-understanding the KOI 
-sample's multiplicity statistics.
-In particular, they can be immediately applied to rectify binarity's effects 
-on the mass-radius diagram~\citep{furlan_densities_2017}.
+by~\citet{furlan_kepler_2017}, and they represent an important advance
+in understanding the KOI sample's multiplicity statistics.  In
+particular, they can be immediately applied to rectify binarity's
+effects on the mass-radius diagram~\citep{furlan_densities_2017}.
 
@@
 occurrence rate calculations: using~\citet{furlan_kepler_2017}'s
-catalog, recent studies tested the effects of removing KOI hosts with known 
-companions, reducing contamination in the ``numerator'' of 
-the occurrence rate (\citealt{fulton_california-_2017}; 
-\citealt{petigura_CKS_2017}).
-While this is a good first step, the denominator remains uncorrected.
-To count the number of stars that were searched, further work on
-understanding the multiplicity statistics of KOI and non-KOI stars is 
-necessary. It may be possible to perform through a non-KOI star 
-high-resolution imaging effort, or perhaps by combining
-{\it Gaia} parallaxes with measured photometric fluxes to identify binary 
-systems.
+catalog, recent studies tested the effects of removing KOI hosts with
+known companions, reducing contamination in the ``numerator'' of the
+occurrence rate (\citealt{fulton_california-_2017};
+\citealt{petigura_CKS_2017}).  While this is a good first step, the
+denominator remains uncorrected.  To count the number of stars that
+were searched, further work on understanding the multiplicity
+statistics of KOI and non-KOI stars is necessary. It may be possible
+to perform through a non-KOI star high-resolution imaging effort, or
+perhaps by combining {\it Gaia} parallaxes with measured photometric
+fluxes to identify binary systems.
 
 \paragraph{Does a detected planet orbit the primary or secondary?}
-A separate important step towards rectifying binarity's effects is identifying 
-the transit host star for detected planets in binaries.
-The current 
-wisdom is that, unless the planet can be confirmed to orbit either 
-component through analysis of the transit durations or centroids, nothing 
-substantive can be said about the 
-likelihood of a planet orbiting the primary vs. the 
+A separate important step towards rectifying binarity's effects is
+identifying the transit host star for detected planets in binaries.
+The current wisdom is that, unless the planet can be confirmed to
+orbit either component through analysis of the transit durations or
+centroids, nothing substantive can be said about the likelihood of a
+planet orbiting the primary vs. the
 secondary~\citep[\textit{e.g.},][]{ciardi_understanding_2015,ziegler_robo-ao_2017}.
@@
 \begin{comment}
-\citet{ciardi_understanding_2015} studied the effects of stellar multiplicity 
-on the planet radii derived from transit surveys.
-They modeled the problem for {\it Kepler}\ objects of interest by matching a 
-population of binary and tertiary companions to KOI stars, 
-under the assumption that the KIC-listed stars were the primaries.
-They then computed planet radius correction factors assuming that {\it 
-    Kepler}-detected planets orbited the primary or companion stars
-with equal probability (their Section~5).
-Under these assumptions, they found that any given planet's radius is on 
-average underestimated by a multiplicative factor of $\approx\! 1.5$.
-\citet{ziegler_robo-ao_2017} recently reported a similar mean radius 
-correction factor for the multiple systems observed by the Robo-AO KOI survey, 
-using the same assumption that detected planets are as likely to orbit the 
-primary and the secondary.
+  \citet{ciardi_understanding_2015} studied the effects of stellar
+  multiplicity on the planet radii derived from transit surveys.  They
+  modeled the problem for {\it Kepler}\ objects of interest by
+  matching a population of binary and tertiary companions to KOI
+  stars, under the assumption that the KIC-listed stars were the
+  primaries.  They then computed planet radius correction factors
+  assuming that {\it Kepler}-detected planets orbited the primary or
+  companion stars with equal probability (their Section~5).  Under
+  these assumptions, they found that any given planet's radius is on
+  average underestimated by a multiplicative factor of $\approx\!
+  1.5$.  \citet{ziegler_robo-ao_2017} recently reported a similar mean
+  radius correction factor for the multiple systems observed by the
+  Robo-AO KOI survey, using the same assumption that detected planets
+  are as likely to orbit the primary and the secondary.
 \end{comment}
@@
 Assuming a broken power law radius distribution, we showed in
-Figure~\ref{fig:frac_model_3} that detected 
-planets in binary systems are usually more likely to orbit the primary.
-A planet orbiting the secondary does lead to extreme corrections.
-However, at $r\a \gtrsim 2r_\oplus$, these cases are rare outliers.
-At $r_\oplus \lesssim r\a \lesssim 2r_\oplus$, for all of the trial values of 
-$Z_2/Z_0$ assumed in Figure~\ref{fig:frac_model_3}, a detected planet is 
-always 
-more likely to orbit the primary than the secondary.
-Only at very small apparent radii, $r\a \approx 0.5r_\oplus$, and only if 
-secondaries host as many planets as singles and primaries, does this ``rule'' 
+Figure~\ref{fig:frac_model_3} that detected planets in binary systems
+are usually more likely to orbit the primary.  A planet orbiting the
+secondary does lead to extreme corrections.  However, at $r\a \gtrsim
+2r_\oplus$, these cases are rare outliers.  At $r_\oplus \lesssim r\a
+\lesssim 2r_\oplus$, for all of the trial values of $Z_2/Z_0$ assumed
+in Figure~\ref{fig:frac_model_3}, a detected planet is always more
+likely to orbit the primary than the secondary.  Only at very small
+apparent radii, $r\a \approx 0.5r_\oplus$, and only if secondaries
+host as many planets as singles and primaries, does this ``rule''
 break down.
 
-Of course, our model's assumptions (see the list in Section~\ref{sec:conclusion}) 
-might not apply to the {\it Kepler}\ dataset.
-However if they are applicable, then for the $56\%$ of ``\texttt{CONFIRMED}'' 
-KOIs\footnote{Exoplanet Archive; \cite{akeson_nasa_2013}; 
-    \url{exoplanetarchive.ipac.caltech.edu}} with 
-apparent radii $>2r_\oplus$, 
-whenever high-resolution imaging 
-discovers a binary companion in 
-a system that hosts a detected transiting planet, the planet is much
-more likely to orbit the primary.
+Of course, our model's assumptions (see the list in
+Section~\ref{sec:conclusion}) might not apply to the {\it Kepler}\
+dataset.  However if they are applicable, then for the $56\%$ of
+``\texttt{CONFIRMED}'' KOIs\footnote{Exoplanet Archive;
+\cite{akeson_nasa_2013}; \url{exoplanetarchive.ipac.caltech.edu}} with
+apparent radii $>2r_\oplus$, whenever high-resolution imaging
+discovers a binary companion in a system that hosts a detected
+transiting planet, the planet is much more likely to orbit the
+primary.
 
@@
 radius}
-One further prediction of Figure~\ref{fig:frac_model_3} is that the fraction 
-of 
-detected planets with binary companions increases by $\approx 6-12\%$ going 
-from $2r_\oplus$ to $\approx\! 1.4r_\oplus$.
-In \citet{ziegler_robo-ao_2017}'s recent summary of the Robo-AO KOI survey, 
-they reported the fraction of planet-hosting stars with Robo-AO detected 
-companion stars, binning by Earths ($r\a < 1.6r_\oplus$), Neptunes 
-($1.6r_\oplus < r\a < 3.9 r_\oplus$), Saturns ($3.9r_\oplus < r\a < 9 
-r_\oplus$), and Jupiters ($r\a > 9r_\oplus$).
+One further prediction of Figure~\ref{fig:frac_model_3} is that the
+fraction of detected planets with binary companions increases by
+$\approx 6-12\%$ going from $2r_\oplus$ to $\approx\! 1.4r_\oplus$.
+In \citet{ziegler_robo-ao_2017}'s recent summary of the Robo-AO KOI
+survey, they reported the fraction of planet-hosting stars with
+Robo-AO detected companion stars, binning by Earths ($r\a <
+1.6r_\oplus$), Neptunes ($1.6r_\oplus < r\a < 3.9 r_\oplus$), Saturns
+($3.9r_\oplus < r\a < 9 r_\oplus$), and Jupiters ($r\a > 9r_\oplus$).
 The reported nearby star rates and their $1\sigma$ uncertainties are:
@@
 where the uncertainties were calculated
-following~\citet{burgasser_binarity_2003}.
-The absolute values of the rates are less than the $\sim\! 45\%$ typical for 
-Sun-like stars at least in part because of Robo-AO's sensitivity 
-(\citealt{ziegler_robo-ao_2017}'s Figure~2;~\citealt{raghavan_survey_2010}).
-Another reason for the lower measured companion rates could be that planetary 
-systems are less likely to have 
-binary companions (as~\citealt{kraus_impact_2016} argued for close binary 
-companions).
-The uptick in the companion rate for Jupiters is likely tied to a large 
-astrophysical false positive rate~\citep{santerne_sophie_2012}.
-Going from Neptunes to Earths, the data suggest a weak increase in the 
-detected planet companion fraction, perhaps of a few percent.
-It will be interesting to see whether this effect is borne out by further 
-observations.
+following~\citet{burgasser_binarity_2003}.  The absolute values of the
+rates are less than the $\sim\! 45\%$ typical for Sun-like stars at
+least in part because of Robo-AO's sensitivity
+(\citealt{ziegler_robo-ao_2017}'s
+Figure~2;~\citealt{raghavan_survey_2010}).  Another reason for the
+lower measured companion rates could be that planetary systems are
+less likely to have binary companions (as~\citealt{kraus_impact_2016}
+argued for close binary companions).  The uptick in the companion rate
+for Jupiters is likely tied to a large astrophysical false positive
+rate~\citep{santerne_sophie_2012}.  Going from Neptunes to Earths, the
+data suggest a weak increase in the detected planet companion
+fraction, perhaps of a few percent.  It will be interesting to see
+whether this effect is borne out by further observations.
 
@@
   \paragraph{Independent approaches for estimating binarity's effects}
-T. Barclay et al.\! (in preparation) have performed the exercise of taking 
-stars selected by the {\it Kepler}\ team, pairing them with a population of 
-secondaries, injecting a realistic distribution of planet radii, 
-and then comparing the inferred occurrence rates with the true ones.
-In their model, they find that binarity leads to an inferred rate of 
-Earth-sized planets $\approx 10\%$ less than the true rate.
-In our Model \#3, if all $Z_i$'s are equal (a plausible assumption in 
-the lack of evidence to the contrary), the underestimate is by a comparable 
-16\%.
+  T. Barclay et al.\! (in preparation) have performed the exercise of
+  taking stars selected by the {\it Kepler}\ team, pairing them with a
+  population of secondaries, injecting a realistic distribution of
+  planet radii, and then comparing the inferred occurrence rates with
+  the true ones.  In their model, they find that binarity leads to an
+  inferred rate of Earth-sized planets $\approx 10\%$ less than the
+  true rate.  In our Model \#3, if all $Z_i$'s are equal (a plausible
+  assumption in the lack of evidence to the contrary), the
+  underestimate is by a comparable 16\%.
 \end{comment}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{conclusion}
 
@@
 This study presented simple models for how binarity affects occurrence
-rates measured by transit surveys.
-The simplest of these models (Section~\ref{sec:simplest}) provided an 
-order-of-magnitude estimate that suggested we would need implausibly high twin 
-binary fractions for binarity to affect apparent occurrence rates by more than 
-factors of two.
-
-We then derived a general formula for the apparent rate density inferred by an 
-observer ignoring binarity (Equation~\ref{eq:general_Gamma_a}).
-As input, this equation requires a volume-limited mass ratio distribution 
-$f(q)$, and the true rate densities for planets around singles, 
-primaries, and secondaries.
-The assumptions that make the model tractable are:
+rates measured by transit surveys.  The simplest of these models
+(Section~\ref{sec:simplest}) provided an order-of-magnitude estimate
+that suggested we would need implausibly high twin binary fractions
+for binarity to affect apparent occurrence rates by more than factors
+of two.
+
+We then derived a general formula for the apparent rate density
+inferred by an observer ignoring binarity
+(Equation~\ref{eq:general_Gamma_a}).  As input, this equation requires
+a volume-limited mass ratio distribution $f(q)$, and the true rate
+densities for planets around singles, primaries, and secondaries.  The
+assumptions that make the model tractable are:
 \begin{enumerate}
     \item the transit survey is SNR-limited;
-    \item the true properties of all the singles and primaries are known to 
-    the observer;
-    \item the observers assume that binaries have the same properties as the 
-    primaries;
+    \item the true properties of all the singles and primaries are
+      known to the observer;
+    \item the observers assume that binaries have the same properties
+      as the primaries;
     \item there are functions $L(M)$ and $R(M)$ that specify a star's
@@
 %
-\item Assuming a power law planet radius distribution, and that the same 
-number of planets orbit singles, primaries, and secondaries, binarity 
-influences apparent planet occurrence rates around Sun-like stars at the 
-$\sim$few percent level from radii $2r_\oplus \lesssim r\a \lesssim 
-17r_\oplus$ (Section~\ref{sec:model_2}).
+\item Assuming a power law planet radius distribution, and that the
+  same number of planets orbit singles, primaries, and secondaries,
+    binarity influences apparent planet occurrence rates around
+    Sun-like stars at the $\sim$few percent level from radii
+    $2r_\oplus \lesssim r\a \lesssim 17r_\oplus$
+    (Section~\ref{sec:model_2}).
 %
 \item Assuming a broken-power law planet radius distribution, with
-\citet{howard_planet_2012}'s exponent at $r > 2r_\oplus$ and a constant 
-occurrence at $r < 2r_\oplus$, there is a ``bump'' in the apparent rate 
-density at $r\a < 2r_\oplus$, leading to a relative error $\delta \Gamma_0 = 
-|\Gamma_0 - \Gamma\a|/\Gamma_0$ of at most $\approx 50\%$ 
-(Figure~\ref{fig:occ_rate_model_3_log}).
-Although this is smaller than current systematic uncertainties on the 
-occurrence rates of Earth-sized planets, this means that binarity could
-eventually become an important component of the $\eta_\oplus$ error budget.
+  \citet{howard_planet_2012}'s exponent at $r > 2r_\oplus$ and a
+    constant occurrence at $r < 2r_\oplus$, there is a ``bump'' in the
+    apparent rate density at $r\a < 2r_\oplus$, leading to a relative
+    error $\delta \Gamma_0 = |\Gamma_0 - \Gamma\a|/\Gamma_0$ of at
+    most $\approx 50\%$ (Figure~\ref{fig:occ_rate_model_3_log}).
+    Although this is smaller than current systematic uncertainties on
+    the occurrence rates of Earth-sized planets, this means that
+    binarity could eventually become an important component of the
+    $\eta_\oplus$ error budget.
 %
@@
   (Figure~\ref{fig:model_4}), by an amount that could affect precise
-measurements 
-of the depth, width, and slope of \citet{fulton_california-_2017}'s radius 
-gap, in the event that planets are not carefully vetted with high resolution 
-imaging.
+    measurements of the depth, width, and slope of
+    \citet{fulton_california-_2017}'s radius gap, in the event that
+    planets are not carefully vetted with high resolution imaging.
 %
 \item Binarity does not lead to smaller apparent HJ occurrence rates
-(Figure~\ref{fig:gaussian_HJ}).
-This assumes a Gaussian planet radius distribution, similar to that reported 
+  (Figure~\ref{fig:gaussian_HJ}).  This assumes a Gaussian planet
+    radius distribution, similar to that reported
     by~\citet{petigura_CKS_2017}.
 %
-\item Detected planets with $r\a \gtrsim 0.5r_\oplus$ that are revealed by 
-high resolution imaging surveys to exist in binaries are more likely to orbit 
-the primary (Figure~\ref{fig:frac_model_3}).
-%
-\item Near the ``break'' in the rate distribution ($\approx 2r_\oplus$), 
-the fraction of detected planets with binary companions increases by 
-$\approx 5-10\%$ (Figure~\ref{fig:frac_model_3}).
+\item Detected planets with $r\a \gtrsim 0.5r_\oplus$ that are
+  revealed by high resolution imaging surveys to exist in binaries are
+    more likely to orbit the primary (Figure~\ref{fig:frac_model_3}).
+%
+\item Near the ``break'' in the rate distribution ($\approx
+  2r_\oplus$), the fraction of detected planets with binary companions
+    increases by $\approx 5-10\%$ (Figure~\ref{fig:frac_model_3}).
 \end{itemize}
 
-All of these results should be understood as only being strictly applicable 
-when the assumptions listed above are met.
-Otherwise, while it is only suggestive, our approach still provides 
-helpful hints at how ignoring stellar binarity influences transit survey
-occurrence rates.
+All of these results should be understood as only being strictly
+applicable when the assumptions listed above are met.  Otherwise,
+while it is only suggestive, our approach still provides helpful hints
+at how ignoring stellar binarity influences transit survey occurrence
+rates.
 
 \acknowledgements{
-It was a pleasure sharing discussions about this study with T. Barclay, W. 
-Bhatti, and F. Dai.
-This work made use of NASA's Astrophysics Data System Bibliographic Services.
+It was a pleasure sharing discussions about this study with T.
+Barclay, W.  Bhatti, and F. Dai.  This work made use of NASA's
+Astrophysics Data System Bibliographic Services.
 %
@@
 
-In this appendix, we derive Equation~\ref{eq:general_Gamma_a}.
-First, recall our definition of apparent rate density 
-(Equation~\ref{eq:apparent_rate_density}).
-We assume that $R$ and $L$ are uniquely determined from the assumed 
-stellar mass--radius--luminosity relation, and neglect the dependence on 
-planetary orbital period.
-The planets with $(r\a, M\a)$ are associated with 
-systems of many different planetary and stellar properties, so $n_{\rm 
-det}(r\a, M\a)$ is given by the convolution of the true rate density, 
-$\Gamma(r, M)$, and $\mathcal{N}_\star(r\a, M\a; r, M)$, the number (per 
-unit $(r\a, M\a)$) of searchable stars that give $(r\a, M\a)$  when 
-the true system actually has $(r, M)$. Mathematically,
+In this appendix, we derive Equation~\ref{eq:general_Gamma_a}.  First,
+recall our definition of apparent rate density
+(Equation~\ref{eq:apparent_rate_density}).  We assume that $R$ and $L$
+are uniquely determined from the assumed stellar
+mass--radius--luminosity relation, and neglect the dependence on
+planetary orbital period.  The planets with $(r\a, M\a)$ are
+associated with systems of many different planetary and stellar
+properties, so $n_{\rm det}(r\a, M\a)$ is given by the convolution of
+the true rate density, $\Gamma(r, M)$, and $\mathcal{N}_\star(r\a,
+M\a; r, M)$, the number (per unit $(r\a, M\a)$) of searchable stars
+that give $(r\a, M\a)$  when the true system actually has $(r, M)$.
+Mathematically,
 \begin{align}
@@
 \end{align}
-where $i$ specifies the type of true host stars (0: single, 1: primary, 2: 
-secondary).
-The problem reduces to the evaluation of
+where $i$ specifies the type of true host stars (0: single, 1:
+primary, 2: secondary).  The problem reduces to the evaluation of
 \begin{equation}
@@
 \end{equation}
-for planets around single stars, primaries in binaries, and secondaries in 
-binaries.
+for planets around single stars, primaries in binaries, and
+secondaries in binaries.
 
@@
     \mathcal{N}_\star^1(r\a, M\a; r, M)
-=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M),
+    = \int 
+      \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M),
     \label{eq:fancyN_s_1}
@@
 \begin{equation}
-\mathcal{N}_{{\rm s},q}^1(r\a, M\a, q; r, M) \propto \delta(M\a-M).
+    \mathcal{N}_{{\rm s},q}^1(r\a, M\a, q; r, M)
+    \propto
+    \delta(M\a-M).
 \end{equation}
 In this case, $\mathcal{N}_{{\rm s},q}^1$ is non-zero only at
-$r\a=R_a\sqrt{\delta_{\rm obs}}$, 
-and the observed depth is
+$r\a=R_a\sqrt{\delta_{\rm obs}}$, and the observed depth is
 \begin{equation}
@@
 \end{equation}
-The normalization of $\mathcal{N}_{{\rm s},q}^1$ is given by the number of 
-binaries that are searchable for a signal $\delta_{\rm obs}$ and that have the 
-mass ratio $q$:
+The normalization of $\mathcal{N}_{{\rm s},q}^1$ is given by the
+number of binaries that are searchable for a signal $\delta_{\rm obs}$
+and that have the mass ratio $q$:
 \begin{equation}
@@
 \end{equation}
-Again $\mathcal{N}_\star^2$ is non-zero only at $r\a=R_a\sqrt{\delta_{\rm 
-        obs}}$, but this 
-time
+Again $\mathcal{N}_\star^2$ is non-zero only at
+$r\a=R_a\sqrt{\delta_{\rm obs}}$, but this time
 \begin{equation}
@@
 \begin{equation}
-\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
-            sys}(M\a, q)} }.
-\end{equation}
-The normalization remains the same as the previous case (we are counting the 
-searchable stars at a given observed depth $\delta_{\rm obs}$, and the total 
-luminosity of the binary is the same).
-Thus,
+    \mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over
+    L_{\rm sys}(M\a, q)} }.
+\end{equation}
+The normalization remains the same as the previous case (we are
+counting the searchable stars at a given observed depth $\delta_{\rm
+obs}$, and the total luminosity of the binary is the same).  Thus,
 \begin{equation}
@@
 
-One might worry in Equation~\ref{eq:mathcal_N_s_2} that we opt to write 
-$\mathcal{N}\s^2 \propto \delta(M\a - M/q)$, rather than $\propto \delta(M\a q 
-- M)$ or some other delta function with the same functional dependence, 
-but a different normalization once integrated.
-We do this because the delta function in Equation~\ref{eq:mathcal_N_s_2} is 
-defined with respect to the measure ${\rm d}M\a$, not ${\rm d}M$.
-This is because $\mathcal{N}\s^2$ is defined as a number per $r\a$, per $M\a$.
+One might worry in Equation~\ref{eq:mathcal_N_s_2} that we opt to
+write $\mathcal{N}\s^2 \propto \delta(M\a - M/q)$, rather than
+$\propto \delta(M\a q - M)$ or some other delta function with the same
+functional dependence, but a different normalization once integrated.
+We do this because the delta function in
+Equation~\ref{eq:mathcal_N_s_2} is defined with respect to the measure
+${\rm d}M\a$, not ${\rm d}M$.  This is because $\mathcal{N}\s^2$ is
+defined as a number per $r\a$, per $M\a$.
 
@@
 \end{align}
-This equation is used to derive Eqs.~\ref{eq:model5_apparent_rate_density} 
-and~\ref{eq:powerlaw_vary_binary}, and is numerically integrated to create 
-Figs.~\ref{fig:occ_rate_model_3_log},~\ref{fig:model_4}, 
-and~\ref{fig:gaussian_HJ}.
-It is validated in limits in which it is possible to write down the answer 
-(e.g., Equation~\ref{eq:model_1_apparent_rate_density}), and also against a 
-Monte 
-Carlo realization of the twin binary models (Secs.~\ref{sec:model_1} 
-and~\ref{sec:model_2}).
+This equation is used to derive
+Eqs.~\ref{eq:model5_apparent_rate_density}
+and~\ref{eq:powerlaw_vary_binary}, and is numerically integrated to
+create Figs.~\ref{fig:occ_rate_model_3_log},~\ref{fig:model_4},
+and~\ref{fig:gaussian_HJ}.  It is validated in limits in which it is
+possible to write down the answer (e.g.,
+Equation~\ref{eq:model_1_apparent_rate_density}), and also against a
+Monte Carlo realization of the twin binary models
+(Secs.~\ref{sec:model_1} and~\ref{sec:model_2}).
 
@@
 \end{align}
-where the angle brackets denote averaging over $f(q)/\mathcal{A}^3$. This form
-shows that the fraction $\mu$ and mass ratio distribution 
-$f(q)/\mathcal{A}^3$ of binaries {\it in the searchable volume} are enough to 
-describe the contributions from binaries to $\Gamma\a$.
-The fraction $\mu$ gives the relative contributions from singles and binaries,
-and $f(q)/\mathcal{A}^3$ weights the contributions from binaries with various 
-mass ratios.
-The apparent rate density at each mass ratio ({\it i.e.}, the terms in
-the angle brackets) is the rate density of systems that give the apparent
-$(r\a, M\a)$, corrected for the overestimated transit probability around
-secondaries.
+where the angle brackets denote averaging over $f(q)/\mathcal{A}^3$.
+This form shows that the fraction $\mu$ and mass ratio distribution
+$f(q)/\mathcal{A}^3$ of binaries {\it in the searchable volume} are
+enough to describe the contributions from binaries to $\Gamma\a$.  The
+fraction $\mu$ gives the relative contributions from singles and
+binaries, and $f(q)/\mathcal{A}^3$ weights the contributions from
+binaries with various mass ratios.  The apparent rate density at each
+mass ratio ({\it i.e.}, the terms in the angle brackets) is the rate
+density of systems that give the apparent $(r\a, M\a)$, corrected for
+the overestimated transit probability around secondaries.
 

### 2018-02-04 paper/main.tex
cite Hirsch 2017

@@
 This paper is organized as follows.  The next section enumerates the
-various errors that arise from unrecognized binaries.  Then, in
+various errors that arise from unrecognized binaries.  Then in
 Section~\ref{sec:simplest}, we develop an idealized model of a transit
@@
 singles and binaries, the detected planets are thereby drawn from
-different occurrence distributions~\citep[see, {\it
-e.g.},][]{wang_occurrence_2015}.
+different occurrence 
+distributions~\citep[{\it e.g.},][]{
+    wang_occurrence_2015,kraus_impact_2016}.
 
@@
 true} occurrence rate for transit signals of amplitude $\delta_{\rm
-obs} = (r\a/R\a)^2$, but this latter quantity is typically not what
-observers are interested in studying.
+obs} = (r\a/R\a)^2$, but this latter quantity is less astrophysically
+significant.
 
@@
 
-The hypothesis that binarity might matter is grounded in the fact that
-radial velocity and transit surveys treat binarity differently.
+Binarity might affect the inferred occurrence rates because 
+radial velocity and transit surveys treat binaries differently.
 Radial velocity surveys typically reject both visual and spectroscopic
@@
 One reason to address stellar multiplicity in transit surveys is that
-it changes the interpretation of planet candidates on a
+it can radically alter the interpretation of planet candidates on a
 system-by-system level.  Consequently, high resolution imaging
@@
 by~\citet{furlan_kepler_2017}, and they represent an important advance
-in understanding the KOI sample's multiplicity statistics.  In
-particular, they can be immediately applied to rectify binarity's
-effects on the mass-radius diagram~\citep{furlan_densities_2017}.
-
-These high resolution imaging campaigns are beginning to connect with
+in understanding the KOI sample's multiplicity statistics.  
+An immediate application is to reassess the radii of detected planets.
+Doing so, \citet{hirsch_assessing_2017} find that for their sample of KOIs
+in binaries, the planet radii are underestimated by factors $r/r\a = 1.17$
+if all planets orbit primaries, and $r/r\a = 1.65$ if detected
+planets are equally likely to orbit primaries and singles.
+%In particular, they can be immediately applied to rectify binarity's
+%effects on the mass-radius diagram~\citep{furlan_densities_2017}.
+
+These results are beginning to connect with
 occurrence rate calculations: using~\citet{furlan_kepler_2017}'s
-catalog, recent studies tested the effects of removing KOI hosts with
+catalog, recent studies have tested the effects of removing KOI hosts with
 known companions, reducing contamination in the ``numerator'' of the
 occurrence rate (\citealt{fulton_california-_2017};
-\citealt{petigura_CKS_2017}).  While this is a good first step, the
+\citealt{petigura_CKS_2017}).  
+While these are good first steps, the
 denominator remains uncorrected.  To count the number of stars that
 were searched, further work on understanding the multiplicity
-statistics of KOI and non-KOI stars is necessary. It may be possible
-to perform through a non-KOI star high-resolution imaging effort, or
-perhaps by combining {\it Gaia} parallaxes with measured photometric
-fluxes to identify binary systems.
+statistics of KOI and non-KOI stars is necessary. In particular,
+a non-KOI star high-resolution imaging effort could help estimate
+the systematic errors incurred by assuming all surveyed stars are
+single.
+An alternate approach would be to combine {\it Gaia}
+parallaxes with measured photometric fluxes and identify binary systems
+as those that are 
+overluminous~\citep[\textit{e.g.},][]{widmark_inferring_2018}.
 
 \paragraph{Does a detected planet orbit the primary or secondary?}
-A separate important step towards rectifying binarity's effects is
+An important step towards rectifying binarity's effects is
 identifying the transit host star for detected planets in binaries.
@@
 orbit either component through analysis of the transit durations or
-centroids, nothing substantive can be said about the likelihood of a
+centroids, little can be said about the likelihood of a
 planet orbiting the primary vs. the
-secondary~\citep[\textit{e.g.},][]{ciardi_understanding_2015,ziegler_robo-ao_2017}.
+secondary~\citep[\textit{e.g.},][but see~\citealt{hirsch_assessing_2017}'s 
+approach to weighting radius corrections by planet 
+occurrence]{ciardi_understanding_2015,ziegler_robo-ao_2017}.
 
@@
 \acknowledgements{
-It was a pleasure sharing discussions about this study with T.
+It was a pleasure discussing this study with T.
 Barclay, W.  Bhatti, and F. Dai.  This work made use of NASA's

### 2018-02-09 src/model1_numbers.py
update model 1 plot for bf=0.05

@@ -1,0 +1,9 @@
+BF = 0.05
+nb_by_ns = 1 / ( (1/BF) - 1 )
+
+Λa_by_Λ_at_r = (1 + 2**(3/2)*nb_by_ns)**(-1)
+
+Λa_by_Λ_at_rbyrt2 = 2**(5/2)*nb_by_ns / (1 + 2**(3/2)*nb_by_ns)
+
+print(Λa_by_Λ_at_r, Λa_by_Λ_at_r*0.5)
+print(Λa_by_Λ_at_rbyrt2, Λa_by_Λ_at_rbyrt2*0.5)

### 2018-02-09 src/plot_occrates_vs_radius.py

@@ -4,9 +4,9 @@ This script plots the output of the Monte Carlo simulation.
 first, for models 1,2,3,4:
 >>> python numerical_models.py
 then:
->>> python plot_rate_densities_vs_radius.py
+>>> python plot_occrates_vs_radius.py
 
-makes plots for paper
+makes plot for Model # 1 of paper
 '''
 # -*- coding: utf-8 -*-
 from __future__ import division, print_function
@@ -222,33 +222,33 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
 
 if __name__ == '__main__':
 
-    for r_pu, model_number in zip([1, 1, 22.5], [1,2,3]):
+    # for r_pu, model_number in zip([1, 1, 22.5], [1,2,3]):
 
-        make_plot(model_number, Z_2=0.5, r_pu=r_pu)
+    #     make_plot(model_number, Z_2=0.5, r_pu=r_pu)
 
     make_plot(1, brokenx=True, Z_2=0.5, r_pu=1)
-    make_plot(2, logy=True, Z_2=0.5, r_pu=1)
-    make_plot(3, logy=True, Z_2=0.5, r_pu=22.5)
-    make_plot(3, withtext=True, stdout=True, Z_2=0.5, r_pu=22.5)
+    # make_plot(2, logy=True, Z_2=0.5, r_pu=1)
+    # make_plot(3, logy=True, Z_2=0.5, r_pu=22.5)
+    # make_plot(3, withtext=True, stdout=True, Z_2=0.5, r_pu=22.5)
 
-    make_plot(4, Z_2=0.5, r_pu=22.5)
-    make_plot(4, xcut=True, Z_2=0.5, r_pu=22.5)
+    # make_plot(4, Z_2=0.5, r_pu=22.5)
+    # make_plot(4, xcut=True, Z_2=0.5, r_pu=22.5)
 
-    # Change as a function of Z_2/Z_0
-    for Z_2 in [0, 0.25]:
-        make_plot(3, Z_2=Z_2, r_pu=22.5)
-        make_plot(3, logy=True, Z_2=Z_2, r_pu=22.5)
-        make_plot(3, withtext=True, stdout=True, Z_2=Z_2, r_pu=22.5)
+    # # Change as a function of Z_2/Z_0
+    # for Z_2 in [0, 0.25]:
+    #     make_plot(3, Z_2=Z_2, r_pu=22.5)
[…]

### 2018-02-09 paper/main.tex
commented another possible Γ_a for model 1
incorporate KM's edits
"one star, one planet" section starts by focusing on apparent occurrence
rates.

then, in the next subsection it does rate densities.

then we ease into the general formula, presenting a pseudo-derivation.

@@
 \begin{equation}
-\Lambda(r,M) = \frac{N_{\rm det}(r,M)}{N_\star(r,M)}
-                    \times \frac{1}{p_{\rm tra}(r,M)},
+\Lambda = \frac{N_{\rm det}}{N_\star}
+                    \times \frac{1}{p_{\rm tra}},
 \label{eq:occ_rate_simple}
@@
 \label{sec:model_1}
-
-Since the effects of binarity are most pronounced when the two
-components are similar, we begin by considering a universe in which
-all stars are identical, with mass $M$, radius $R$, and luminosity
-$L$.  Some fraction of them exist in twin binaries.  All planets have
-size $r\p$.  Our goal is to compare the occurrence inferred by
-observers who ignore binarity with the true occurrence in single star
-systems.
-
-To clarify our terminology, we define ``apparent properties'' as the
-properties that one would infer about a system under the assumption
-that the host star is single. For instance, the  ``apparent planet
-radius'', $r\a$, is the planet radius that one would infer from a
-transit signal, assuming that the host star is single.  The observed
-transit depth is given by the ratio of the apparent planet radius and
-the apparent stellar radius, $R\a$:
-\begin{equation}
-  \delta_{\rm obs}
-  = \left(\frac{r\a}{R\a}\right)^2
-  = \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over
-          L_{\rm sys}},
-  \label{eq:delta_obs_general} 
-\end{equation}
-for $r$ the planet radius, $R_{\rm host}$ ($L_{\rm host}$) the host
-star's radius (luminosity), and $L_{\rm sys}$ the entire system's
-luminosity.  In the example at hand, $R_{\rm host} =R\a = R$, since
-all stars have the same size. For single star systems we have
-$r=r\a=r\p$. In twin binaries, $r\a=r\p/\sqrt{2}$, since $L_{\rm
-sys}=2L$.
-
-We can now understand that the observers are unwittingly reporting an
-{\it apparent} occurrence rate $\Lambda\a(r\a)$, a function of
-apparent radii.  The apparent occurrence rate is the same as the {\it
-true} occurrence rate for transit signals of amplitude $\delta_{\rm
-obs} = (r\a/R\a)^2$, but this latter quantity is less astrophysically
-significant.
-
-Finally, it is helpful to introduce an apparent rate density
-$\Gamma\a$, the average number of planets per star per unit apparent
-planet radius. Analogous to Equation~\ref{eq:occ_rate_simple},  
-\begin{equation}
-  \Gamma\a(r\a) = \frac{n_{\rm det}(r\a)}{N_\star(r\a)}
-      \times \frac{1}{p_{\rm tra}(r\a)},
-\label{eq:apparent_rate_density}
-\end{equation}
-where $n_{\rm det}={\rm d}N_{\rm det}/{\rm d}r\a$ is the number  of
-detected planets, per unit $r\a$, with apparent radius $r\a$.  In
-Equation~\ref{eq:apparent_rate_density}, we neglect the dependence on
-stellar mass since all stars in this model have the same properties.
-
-To compute the number of detected planets, we consider the volumes
-within which a signal of a given depth could be detected. At a fixed
-signal-to-noise floor, there is a maximum searchable
-distance~\citep{pepper_using_2003,pepper_searching_2005}.  From
-Equation~\ref{eq:S_N_thresh}, this maximum searchable distance scales
-as
-\begin{equation}
-    d \propto \delta_{\rm obs} \cdot L_{\rm sys}^{1/2}.
-\end{equation}
-Assuming that stars are uniformly distributed in space, the number of
-searchable stars $N_\star$ is then proportional to
-\begin{equation}
-    N_\star \propto n \delta_{\rm obs}^3 L_{\rm sys}^{3/2},
-\label{eq:N_searchable_prop}
-\end{equation}
-where $n$ is the number per unit volume of {\it e.g.}, single star, or
-binary systems.  We neglect the dependence of $n$ on stellar type.
 
@@
 
-The searchable volumes for this example are illustrated in
-Figure~\ref{fig:model_1_volumes}.  At an apparent radius equal to the
-true radius ($r\a=r\p$), single stars with $d<d_0$ are by definition
-searchable.  Binaries with $r\a=r\p$ are also searchable, out to
-$\sqrt{2}d_0$.  However, in this example no such systems exist; all
-planets in twin binaries have true radii $r=r\p$, and so are observed
-with apparent radii $r\a=r\p/\sqrt{2}$, out to $d_0/\sqrt{2}$.  At an
-apparent radius of $r\a=r\p/\sqrt{2}$, there could also be planets
-with true radii $r=r\p/\sqrt{2}$ orbiting singles, but there are no
-such systems in this model.
-
-How many planets are detected?  If we assume that there are
-$N_\star^0(r\a)$ singles that are searchable for planets with $r\a$,
-and that there are $Z_0$ planets per single, then single stars
-contribute
-\begin{equation}
-n_{\rm det}^0(r\a) = 
-  N_\star^0(r\a) Z_0 p_{\rm tra} \cdot \delta(r\a - r_p)
-\end{equation}
-planet detections (per unit $r\a$), for $\delta$ the Dirac delta
-function.
-
-We can similarly compute the number of planet detections from
-binaries.  First though, we define a ratio $\mu \equiv N_\star^{\rm
-b}(r\a) / N_\star^0(r\a)$ between the number of searchable binary
-systems and the number of searchable singles at any $r\a$.  This
-quantity is useful because although $N_\star^{\rm b}$ and $N_\star^0$
-vary as a function of the observed transit depth, $\mu$ remains fixed.
-Applying this definition, at $r\a=r\p/\sqrt{2}$, some detections will
-come from primaries,
-\begin{equation}
-n_{\rm det}^1(r\a) =
-    \mu N_\star^0(r\a) Z_1 p_{\rm tra}
-    \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right),
-\end{equation}
-and some from secondaries,
-\begin{equation}
-n_{\rm det}^2(r\a) = 
-    \mu N_\star^0(r\a) Z_2 p_{\rm tra}
-    \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right),
-\end{equation}
-where $Z_1$ is the number of planets per primary, $Z_2$ is the number
-of planets per secondary, and $p_{\rm tra}$ is the same for identical
-stars.  For twin binaries, Equation~\ref{eq:N_searchable_prop} gives
-$\mu = 2^{3/2} n_{\rm b}/n_{\rm s}$, where $n_{\rm b}$ is the number
-density of binaries in a volume-limited sample.
-
-The last item we need to write down the apparent rate density
-$\Gamma\a(r\a)$ is the number of unresolved point-sources on sky that
-the observer thinks are searchable, $N_\star$.  From the definition of
-$\mu$,
-\begin{equation}
-    N_\star(r\a) = N_\star^0(r\a) \times (1 + \mu)
-    \label{eq:apparentlysearchable_to_searchable}
-\end{equation}
-relates the number of apparently searchable point-sources and the
-number of searchable singles.  There are in fact $N_\star^0(r\a)\times
-(1 + 2\mu)$ searchable stars at any given $r\a$; the observers are
-under-counting.
-
-Using Equation~\ref{eq:apparent_rate_density}, the apparent rate
-density reported when ignoring binarity is
-\begin{align}
-    \Gamma\a(r\a) = 
-    \frac{1}{1+\mu} Z_0 \cdot
-    \delta(r\a-r\p)  +
-    \frac{\mu}{1+\mu} (Z_1 + Z_2) \cdot
-    \delta\left(r\a-\frac{r\p}{\sqrt{2}} \right).
-    \label{eq:model_1_apparent_rate_density}
-\end{align}
-The first term is from singles, and the second is from binaries.  The
-number of searchable singles at a given apparent radius,
-$N_\star^0(r\a)$, makes no appearance.  The observer has erred in
-Equation~\ref{eq:model_1_apparent_rate_density} by under-counting the
-number of searchable stars at any apparent radius, and by inferring
-incorrect planet radii in binary systems.
+Since the effects of binarity are most pronounced when the two
+components are similar, we begin by considering a universe in which
+all stars are identical, with mass $M$, radius $R$, and luminosity
+$L$.  Some fraction of them exist in twin binaries. All planets have
+size $r\p$.  In this scenario, stars are never misclassified because
+the combined light of a binary has the same color and spectrum as a
+single star.  We further assume that planets occur around single stars
+and members of binaries at the same rate, $\Lambda(r\p)$.
+
+The only type of planet in this universe produces a transit signal of
+amplitude $\delta_{\rm obs} = (r\p/R)^2$ when the host is a single
+star.  Our naive observers try to measure the occurrence rate of these
+planets.  They identify all the ``stars'' in their sample that appear
+to be searchable for such a signal, given the size of their telescope.
+These transits are detected within a certain maximum 
+distance~\citep[see][]{pepper_using_2003,pepper_searching_2005}, which from
+Equation~\ref{eq:S_N_thresh} scales as
+\begin{equation}
+  d_{\rm max} \propto \delta_{\rm obs} \cdot L_{\rm sys}^{1/2}.
+  \label{eq:dmax}
+\end{equation}
+Assuming that stars are uniformly distributed in space, the number of
+searchable stars $N_\star$ is then proportional to
+\begin{equation}
+    N_\star \propto n_i \delta_{\rm obs}^3 L_{\rm sys}^{3/2},
+\label{eq:N_searchable_prop}
+\end{equation}
+where $n_i$ is the number per unit volume of single stars, or
+binary systems.
+
+This selection process inadvertently admits some binaries.  Since the
+binaries are twice as luminous as singles, they are included out to a
+distance that is larger by a factor of $\sqrt{2}$, and if they have
+transiting planets then the signals have an amplitude of
+$(r\p/R)^2/2$.  To detect this half-strength signal, the observers
+need the noise level to be lower by a factor of two, which means the
+flux must be four times higher than that of a single star at distance
+$d_0$.  This is true of single stars within a distance $d_0/2$, and
+binaries within a distance $d_0\sqrt{2}/2$.
+Furthermore the observers will consider any such shrunken signals to
+represent planets of a different type, smaller in radius by a factor
+of $\sqrt{2}$. These searchable volumes are illustrated in 
+Figure~\ref{fig:model_1_volumes}.
+
+Putting it all together, the {\it apparent} occurrence rate of planets
+of radius $r\p$ will be
+\begin{equation}
+    \Lambda\a(r\p) = 
+        \frac{\Lambda(r\p)~n\s d_0^3}
+        {n\s d_0^3 + n\b (d_0\sqrt{2})^3}
+\end{equation}
+where $n\s$ and $n\b$ are the number densities of single stars and
+binary stars, respectively, in the local neighborhood.  This apparent
+rate is larger than the true rate by a factor
+\begin{equation}
+    \frac{\Lambda\a(r\p)}{\Lambda(r\p)} = 
+        \frac{1}{1 + 2^{3/2}(n\b/n\s)}.
+    \label{eq:correction_rp}
+\end{equation}
+The observers will also claim to have discovered a new type of planet
+with radius $r\p/\sqrt{2}$ and an occurrence rate given by
+\begin{equation}
+\label{eq:correction_diluted_rp}
+    \frac{\Lambda\a(r\p/\sqrt{2})}{\Lambda(r\p)}
+    =
+    \frac{2n\b (d_0\sqrt{2}/2)^3}
+      {n\s (d_0/2)^3 + n\b (d_0\sqrt{2}/2)^3}
+    =
+    \frac{2\cdot2^{3/2}(n\b/n\s)}{1 + 2^{3/2}
+    (n\b/n\s)}.
+\end{equation}
 
@@
         Figure~\ref{fig:model_1_volumes}).  We assume a twin binary
-        fraction of $0.1$, and that single, primary, and secondary
+        fraction of $0.05$, and that single, primary, and secondary
         stars host planets at equal rates.  If the true planet radius
         is $r\p$, all planets detected in binaries will have apparent
-        radii $r\a = r\p/\sqrt{2}$;
-        Equation~\ref{eq:model_1_apparent_rate_density} gives the
+        radii $r\a = r\p/\sqrt{2}$; Equation~\ref{eq:ratios} gives the
         normalizations.
@@
 
-To assess the severity of these errors, we must assume both a binary
-fraction, and also the true number of planets per single, primary, and
-secondary star ($Z_0,Z_1,Z_2$).  For the
-former,~\citet{raghavan_survey_2010} found a multiplicity fraction of
-0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$.  By
-multiplicity fraction, they meant ``fraction of systems in a
-volume-limited sample that are multiple'', which we simplistically
-conflate with the fraction of systems in a volume-limited sample that
-are binaries:
-\begin{equation}
-    {\rm binary\ fraction} \equiv \frac{n\b}{n\s + n\b} = 0.44,
-\end{equation}
-Of course not all of these are binaries are close to being ``twin''
-binaries as we have assumed in our simple calculation.  Perhaps only a
-tenth of them have pairs of stars close enough in their basic
-properties to produce errors as significant as those we have been
-considering.  Thus, an appropriate estimate for the binary fraction is
-of order $0.05$.  The ratio of the apparent to single star rate
+We can now assess the severity of these errors, given the
+binary-to-single ratio $n\b/n\s$. For stars with masses from 0.7 to
+1.3~$M_\odot$, \citet{raghavan_survey_2010} found the multiplicity
+fraction to be 0.44, where multiplicity fraction is defined as
+the fraction of systems in a volume-limited sample that are multiple.
+Since we assume all multiple systems are binaries, this implies
+\begin{equation}
+    \frac{n\b}{n\s + n\b} \approx 0.44,
+\end{equation}
+which corresponds to a specific $n\b/n\s$.  Of course not all of these
+binaries are close to being ``twin'' binaries as we have assumed in
+our simple calculation. Perhaps only a tenth of them have pairs of
+stars close enough in their basic properties to produce errors as
+significant as those we have been considering.  Thus, an appropriate
+estimate for $n\b/(n\s+n\b)$ is of order $0.05$, leading to
+\begin{equation}
+    \frac{\Lambda\a(r\p)}{\Lambda(r\p)} = 0.87,~~
+    \frac{\Lambda\a(r\p/\sqrt{2})}{\Lambda(r\p)} = 0.26.
+    \label{eq:ratios}
+\end{equation}
+All together the various effects produce biases of order 10\% in the
+occurrence rates.  We will see that this level of error is
+characteristic of many of our more complicated models, as well.
+
+\subsection{Formula Based on Apparent Rate Density}
+\label{sec:model_1_density}
+
+There is a different way to conceptualize the preceding results that
+will be useful in the subsequent discussion.  Here we broaden the
+discussion to consider a spectrum of planet sizes, by introducing the
+occurrence rate density
+\begin{equation}
+    \Gamma(r) \equiv \frac{d\Lambda}{dr},
+\end{equation}
+the average number of planets per star per unit planet radius.
+
+To clarify our terminology, we define ``apparent properties'' as the
+properties that one would infer about a system under the assumption
+that the host star is single. For instance, the  ``apparent planet
+radius'', $r\a$, is the planet radius that one would infer from a
+transit signal, assuming that the host star is single.  The observed
+transit depth is given by the ratio of the apparent planet radius and
+the apparent stellar radius, $R\a$:
+\begin{equation}
+  \delta_{\rm obs}
+  = \left(\frac{r\a}{R\a}\right)^2
+  = \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over
+          L_{\rm sys}},
+  \label{eq:delta_obs_general} 
+\end{equation}
+for $r$ the planet radius, $R_{\rm host}$ ($L_{\rm host}$) the host
+star's radius (luminosity), and $L_{\rm sys}$ the entire system's
+luminosity. This gives $r\a=r\p/\sqrt{2}$ in our ``twin binary''
+model.
+
+With this definition we may say that naive observers are measuring
+$\Gamma\a(r\a)$, the apparent occurrence rate density of planets with
+an apparent radius of $r\a$.  Analogous to
+Equation~\ref{eq:occ_rate_simple},  
+\begin{equation}
+  \Gamma\a(r\a) = \frac{n_{\rm det}(r\a)}{N_\star(r\a)}
+      \times \frac{1}{p_{\rm tra}},
+\label{eq:apparent_rate_density}
+\end{equation}
+where $n_{\rm det}$ is the number of detected planets, per unit $r\a$,
+with apparent radius $r\a$.  In
+Equation~\ref{eq:apparent_rate_density}, we neglect the dependence on
+stellar mass since all stars in this model have the same properties.
+Since $\delta_{\rm obs}$ and $r\a$ are related by $R\a$, which is
+simply assumed by an observer, measuring $\Gamma\a(r\a)$ is equivalent
+to measuring the true occurrence rate density of {\it transit signals}
+of amplitude $\delta_{\rm obs}$.
+
+Let us evaluate the contributions to $n_{\rm det}$ from singles and
+binaries.  As in the previous subsection, for each apparent planet
+radius $r\a$, the observers select $N_\star(r\a)$ unresolved
+point-sources on sky, based on Equation \ref{eq:dmax}.  If we let $\mu
+\equiv N\star^{\rm b}(r\a)/N_\star^0(r\a)$ be the ratio of the number
+of searchable binary systems to single systems, then the number of
+single and binary point-sources thought to be searchable are
+\begin{equation}
+  \frac{N_\star(r\a)}{1+\mu}~~{\rm and}~~\frac{\mu N_\star(r\a)}{1+\mu},
+\end{equation}
+respectively.  Earlier we showed that due to Malmquist bias, $\mu =
+2^{3/2}(n\b/n\s)$.
+
+We further stipulate that the true occurrence rate densities for
+planets around single stars, primaries, and secondaries are
+$\Gamma_0(r)$, $\Gamma_1(r)$, and $\Gamma_2(r)$, respectively.  
+Then single stars contribute
+\begin{equation}
+  n_{\rm det}^0(r\a) = 
+    {N_\star(r\a) \over {1+\mu}} p_{\rm tra} \Gamma_0(r\a)
+  \label{eq:n0}
+\end{equation}
+planet detections per unit $r\a$.  We can similarly compute the number
+of planet detections from binaries.  Since $r\p=\sqrt{2}r\a$ for
+planets in twin binaries, 
+\begin{equation}
+  n_{\rm det}^1(r\a)\mathrm{d}r\a =
+      {\mu N_\star(r\a) \over {1+\mu}} p_{\rm tra}
+      \Gamma_1(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
+	\label{eq:n1}
+\end{equation}
+detections come from primaries, and
+\begin{equation}
+  n_{\rm det}^2(r\a)\mathrm{d}r\a =
+      {\mu N_\star(r\a) \over {1+\mu}} p_{\rm tra}
+      \Gamma_2(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
+	\label{eq:n2}
+\end{equation}
+from secondaries.  Here the transit probability $p_{\rm tra}$ is the
+same in all three cases because the stars are all identical.
+
+Using Equation~\ref{eq:apparent_rate_density}, the apparent rate
+density reported when ignoring binarity is
+\begin{equation}
+	\label{eq:formula_twin_binary}
+  \Gamma\a(r\a) =
+    \frac{1}{1+\mu}\,\Gamma_0(r\a) +
+    \frac{\mu}{1+\mu}\,\sqrt{2}\,\Gamma_1(\sqrt{2}r\a) +
+    \frac{\mu}{1+\mu}\,\sqrt{2}\,\Gamma_2(\sqrt{2}r\a).
+\end{equation}
+If we further assume 
+\begin{equation}
+	\Gamma_i=Z \cdot \delta(r\a-r\p)
+\end{equation} 
+as we did in the previous ``one planet" example,
+the above apparent rate density reduces to
+\begin{align}
+    \Gamma\a(r\a) &= Z \left[
+    \frac{1}{1+\mu} \cdot
+    \delta(r\a-r\p)  +
+    \frac{2\mu}{1+\mu} \cdot
+    \delta\left(r\a-\frac{r\p}{\sqrt{2}} \right) \right].
+    \label{eq:model_1_apparent_rate_density}
+\end{align}
+Integrating over $r\a$, this yields
+\begin{equation}
+	\Lambda\a(r_{\rm p})=\frac{Z}{1+\mu},\quad
+	\Lambda\a(r_{\rm p}/\sqrt{2})=\frac{2\mu Z}{1+\mu},
+\end{equation}
+which reproduce Equations~\ref{eq:correction_rp}
+and~\ref{eq:correction_diluted_rp}.
+
+\begin{comment}
+    The ratio of the apparent to single star rate
     densities,
@@
     \end{equation}
-can then be evaluated as a ``correction factor''.  At the true planet
-radius, $X_\Gamma(r\p)=1/(1+\mu)$.  This yields a correction
-$X_\Gamma$ of 0.87~(0.76) if the binary fraction is 0.05~(0.10).  All
-together the various effects produce biases of order 10\% in the
-occurrence rates.  We will see that this level of error is
-characteristic of many of our more complicated models, as well.
-
-An alternative assumption is that secondaries do not host planets. In
-that case, the correction to the rate density at the true planet
-radius becomes $X_\Gamma(r\p) = (1+2\mu)/(1+\mu)^2$.  This gives a
-correction of 0.98~(0.94) if the binary fraction is 0.05~(0.10).
-Although the secondaries certainly should have planets, the
-sensitivity of $\Gamma\a/\Gamma_0$ to the relative number of planets
-per single, primary, and secondary will also become important as we
-proceed.
-
+    can then be evaluated as a ``correction factor''.  At the true and
+    diluted planet radii, $X_\Gamma(r\p)=1/(1+\mu)$ and
+    $X_\Gamma(r\p/\sqrt{2})=2\mu/(1+\mu)$.  This yields a correction
+    $X_\Gamma$ of 0.87~(0.76) if the binary fraction is 0.05~(0.10).
+    All together the various effects produce biases of order 10\% in the
+    occurrence rates.  
+\end{comment}
+
+\begin{comment}
     \subsection{One type of star, two types of planets}
@@
     will depend on the underlying occurrence rates.
+\end{comment}
 
@@
 
-To generalize the procedure of Section~\ref{sec:simplest}, we consider
-an SNR-limited transit survey in which the singles and primaries can
-have arbitrary properties, but their true masses are known by the
-observer.  We assume that there are some functions $L(M)$ and $R(M)$
-that specify a star's luminosity and radius in terms of its mass, and
-that the volume-limited binary mass ratio distribution, $f(q)$, is
-independent of the primary's mass.  We also allow arbitrary true rate
-densities for singles, primaries, and secondaries ($\Gamma_0,
-\Gamma_1, \Gamma_2$).  We presume that the observers always take the
-properties of a binary system to be those of the primary.
-
-Given this laundry-list of assumptions, a general formula for the
-apparent rate density follows:
-\begin{align}
-    \notag
-    \Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
-    \left\{ \Gamma_0(r\a, M\a)+ 
-    \frac{{\rm BF}}{1 - {\rm BF}}
-    \left[ \int_0^1 \mathrm{d}q \,
-           \frac{f(q)}{\mathcal{A}^3}\cdot
-           \frac{1}{\mathcal{A}} \Gamma_1\left({r\a\over \mathcal{A}},
-    M\a\right)\,
-    \right.   
-    \right. \\
-    & \quad\quad\quad\quad\quad \left.\left.
-    +\int_0^1 {\rm d}q\, 
-         \frac{f(q)}{\mathcal{A}^3}\cdot \frac{q}{\mathcal{B}}
-        \Gamma_2\left({r\a\over \mathcal{B}}, qM\a\right)\cdot
-    {R(qM\a) \over R(M\a)}
-    q^{-1/3} \right]	\right\},
-    \label{eq:general_Gamma_a}
-\end{align}
-where ${\rm BF}=n\b/(n\s+n\b)$ is the volume-limited binary fraction,
-and $\mathcal{A}(q,M\a)$ [$\mathcal{B}(q,M\a)$] are the dilution terms
-for primaries [secondaries], whose functional dependences are omitted
-for notational simplicity.  The dilution terms can be written
-\begin{equation}
-    \mathcal{A}(q, M\a)
-    = \sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}
-    = (1+q^\alpha)^{-1/2},
-\end{equation}
-and
-\begin{equation}
-  \mathcal{B}(q, M\a)
-  = {R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm sys}(M\a, q)} }
-  = q^{-1} (1+q^{-\alpha})^{-1/2}
-\end{equation}
-where the latter equalities assume $L\propto M^\alpha \propto
-R^\alpha$ (the former are more general).  The rate densities depend on
-both apparent radius and mass because even if the primaries and
-singles were to have fixed mass, the mass of secondaries would vary,
-and so this dependence cannot be immediately omitted.
-
-A derivation of Equation~\ref{eq:general_Gamma_a} is given in the
-\hyperref[sec:appendix]{Appendix}; its qualitative features are the
-same as from our simple model
-(Equation~\ref{eq:model_1_apparent_rate_density}).  The terms inside
-the curly braces $\{ \ldots \}$ are the sum of the apparent rate
-densities from singles, primaries, and secondaries.  The contribution
-from singles is not affected by binarity.  In the contributions from
-primaries and secondaries, planets with $(r\a, M\a)$ are associated
-with systems of different planetary and stellar properties, as
-determined by the mass ratio $q$ of each binary.  This corresponds to
-true planet radii and stellar masses $(r\a/\mathcal{A},M\a)$ for
-primaries, and $(r\a/\mathcal{B},qM\a)$ for secondaries.  These
-contributions are then integrated over the mass ratio distribution
-including the effect of Malmquist bias, $f(q)/\mathcal{A}^3$,
-discussed further below. Finally, the latter term in the apparent rate
-density of secondaries comes from a correction for the overestimated
-transit probability.
-
-\paragraph{Ratio of searchable binaries to singles}
-
-We must also specify the exact form of $\mu$, the ratio of the number
-of searchable binary systems to singles.  Given the observed signal
-$\delta_{\rm obs}$ and apparent stellar mass $M\a$, recall that the
-maximum searchable distances for singles and binaries are proportional
-to $\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm obs}\cdot
-[L(M\a)+L(qM\a)]^{1/2}$.  Applying
-Equation~\ref{eq:N_searchable_prop},
-\begin{equation}
-    \mu({\rm BF},M\a)
-    = 
-    \frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}
-    =
-    \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over
-        L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
+To generalize the procedure of Section~\ref{sec:model_1_density} to binaries
+with varying mass ratios, we consider an SNR-limited transit survey in which
+stars can have arbitrary properties.  We assume that there are some functions
+$L(M)$ and $R(M)$ that specify a star's luminosity and radius in terms of its
+mass, and that the volume-limited binary mass ratio distribution, $f(q)$, is
+independent of the primary's mass.  We also allow arbitrary true rate densities
+for singles, primaries, and secondaries ($\Gamma_0, \Gamma_1, \Gamma_2$).  We
+presume that the observers always know the true masses of singles and
+primaries, and that they take the primary's properties to be those of an
+unresolved binary.
+
+Due to the varying mass ratios, we need the following modifications to Equation
+\ref{eq:formula_twin_binary}:
+\begin{enumerate}
+%
+  \item The number of binary systems with mass ratio $(q,
+  q+\mathrm{d}q)$ in the selected sample is now
+  (Equation~\ref{eq:dmax}):
+  \begin{equation}
+      {N_\star(r\a)\over{1+\mu}}\times {n_{\rm b}\over n_{\rm s}}
+      \left[{L_{\rm sys}(M\a, q) \over L(M\a)}\right]^{3/2}
+      f(q)\,\mathrm{d}q,
+  \end{equation}
+  where
+  \begin{equation}
+      \mu({\rm BF},M\a)= 
+      %\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
+      \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L_{\rm sys}(M\a, q)
+      \over L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
       \label{eq:mu_general}
   \end{equation}
-If the binary fraction is independent of $q$, $L \propto M^\alpha$,
-and $f(q) \propto q^\beta$, this simplifies to
-\begin{equation}
-    \mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1
-    \left(1+q^\alpha\right)^{3/2} q^\beta \,\mathrm{d}q.
-    \label{eq:mu_power_laws}
-\end{equation}
-%which can also be rewritten using the hypergeometric function.
+  These should replace ${\mu N_\star(r\a)/(1+\mu)}$ in Equations
+  \ref{eq:n0}--\ref{eq:n2}. Then the result needs to be integrated
+  over $q$.
+
   \begin{figure}[!tb]
@@
           depth, the searchable binaries in a transit survey are
-        magnitude-limited.
+          magnitude-limited. For this figure, we assume $L\propto
+          M^{3.5}$
       }
@@
   \end{figure}
-This can be understood as a Malmquist bias: at fixed observed transit
-depth, for singles and primaries with the same luminosity, binaries
-are searchable to a greater distance.  Specifically, the sample of
-searchable binaries is magnitude-limited.  Given a searchable binary,
-the probability that it has a mass ratio $q$ scales as
-\begin{equation}
-    p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto
-    (1+q^\alpha)^{3/2} q^\beta 
-    \label{eq:Malmquist_bias}
-\end{equation}
-where $q^\beta$ is the volume-limited probability of drawing a binary
-of mass ratio $q$, and the first term is the Malmquist bias when
-$L\propto M^\alpha$.  We show this magnitude-limited mass ratio
-distribution for the $\beta=0$ case in
-Figure~\ref{fig:q_distribn_mag_limited}.  In Monte Carlo simulations
-of transit surveys, it is important to draw binaries from a correctly
-biased mass-ratio distribution~\citep[\textit{e.g.},][]{
-  bakos_hatsouth:_2013,sullivan_transiting_2015, gunther_new_2017}.
+
+  As we showed earlier, this can be understood as a Malmquist bias: in
+  the magnitude-limited sample of searchable binaries, those with
+  larger mass ratios are overrepresented by a factor or
+  $\left[{L_{\rm sys}(M\a, q)/L(M\a)}\right]^{3/2}$ because they are
+  brighter. We show this magnitude-limited mass ratio distribution
+  for the flat $f(q)$ in Figure~\ref{fig:q_distribn_mag_limited}.  In
+  Monte Carlo simulations of transit surveys, it is important to
+  draw binaries from an appropriately biased mass-ratio
+  distribution~\citep[\textit{e.g.},][]{
+    bakos_hatsouth:_2013,sullivan_transiting_2015,
+    gunther_new_2017}.
+%
+  \item The relationship between $r\a$ and $r$ are different.  From
+    Equation~\ref{eq:delta_obs_general}, $r=\mathcal{D}_{1/2}r\a$ for
+    primaries and secondaries, where
+  \begin{equation}
+      \mathcal{D}_1(q, M\a)
+      = \sqrt{L_{\rm sys}(M\a, q) \over L(M\a) }
+      = (1+q^\alpha)^{1/2},
+  \end{equation}
+  and
+  \begin{equation}
+    \mathcal{D}_2(q, M\a)
+    = {R(qM\a)\over R(M\a)}\sqrt{L_{\rm sys}(M\a, q) \over L(qM\a)} 
+    = q (1+q^{-\alpha})^{1/2}.
+  \end{equation}
+  So $\sqrt{2}r\a$ in Equations~\ref{eq:n1} and~\ref{eq:n2} needs to be
+  replaced with $\mathcal{D}_1r\a$ and $\mathcal{D}_2r\a$, respectively.
+
+  \item The transit probability around secondaries are smaller than
+  that around primaries, the latter of which is the same as
+  primaries under our assumption. At a fixed orbital period, this
+  changes $p_{\rm tra}$ in Equation~\ref{eq:n2} by a factor of
+  \begin{equation}
+    {R(qM\a) \over R(M\a)}q^{-1/3}.
+  \end{equation}
+
+\end{enumerate}
+
+Taking these modifications into account, a general formula for the
+apparent rate density follows:
+\begin{align}
+    \notag
+    \Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
+    \left\{ \Gamma_0(r\a, M\a)+ 
+    \frac{n\b}{n\s}
+    \left[ \int_0^1 \mathrm{d}q \,
+           \mathcal{D}_1^3 f(q)\cdot
+          \mathcal{D}_1 \Gamma_1\left(\mathcal{D}_1r\a,
+    M\a\right)\,
+    \right.   
+    \right. \\
+    & \quad\quad\quad\quad\quad \left.\left.
+    +\int_0^1 {\rm d}q\, 
+         \mathcal{D}_1^3 f(q)\cdot \mathcal{D}_2 q
+        \Gamma_2\left(\mathcal{D}_2r\a, qM\a\right)\cdot
+    {R(qM\a) \over R(M\a)}
+    q^{-1/3} \right] \right\}.
+    \label{eq:general_Gamma_a}
+\end{align}
+We also give a more formal derivation in the
+\hyperref[sec:appendix]{Appendix}.
+With the definition of $\mu$ in Equation~\ref{eq:mu_general},
+Equation~\ref{eq:general_Gamma_a} can also be expressed as
+\begin{align}
+    \notag
+    \notag
+    \Gamma\a(r\a,M\a)
+    &= 
+    {1\over 1+\mu(\mathrm{BF}, M\a)} \cdot
+    \left[
+       \Gamma_0(r\a, M\a)\phantom{\tilde \Gamma}\right.&\\
+       &\left.+\mu(\mathrm{BF}, M\a)\cdot
+       \left\langle
+       \mathcal{D}_1\cdot\Gamma_1\left(\mathcal{D}_1r\a, M\a\right)
+       +
+       {q \mathcal{D}_2}\cdot\Gamma_2\left(\mathcal{D}_2r\a,
+       qM\a\right) \cdot {R(qM\a) \over R(M\a)}q^{-1/3}
+       \right\rangle
+    \right],
+\end{align}
+where the angle brackets denote averaging over $\mathcal{D}_1^3f(q)$.
+This form shows that the fraction $\mu$ and mass ratio distribution
+$\mathcal{D}_1^3f(q)$ of binaries {\it in the searchable volume} are
+enough to describe the contributions from binaries to $\Gamma\a$.  The
+fraction $\mu$ gives the relative contributions from singles and
+binaries, and $\mathcal{D}_1^3 f(q)$ weights the contributions from
+binaries with various mass ratios.  The apparent rate density at each
+mass ratio ({\it i.e.}, the terms in the angle brackets) is the rate
+density of systems that give the apparent $(r\a, M\a)$, corrected for
+the overestimated transit probability around secondaries.
 
@@
     \caption{
-        Fraction of detected planet at a given apparent planet radius
+        Fraction of detected planets at a given apparent planet radius
         coming from singles (solid lines), primaries (dashed lines),
@@
 Radial velocity surveys typically reject both visual and spectroscopic
-binaries \citep[\textit{e.g.},][]{wright_frequency_2012}.  Transit
+binaries \citep{wright_frequency_2012}.  Transit
 surveys observe binaries, but the question of whether they were
@@
 telemetric requirements are often required to select target stars.
-Even if the selection process is aimed at creating an SNR-limited
+Even if the selection process aims to create an SNR-limited
 survey, as~\citet{batalha_selection_2010} did for {\it Kepler},
@@
 saying that there might be a cutoff in apparent planet radii, below
-which no planets are detected.  The effects on our main results (e.g.,
-Figs.~\ref{fig:occ_rate_model_3_log},~\ref{fig:frac_model_3},
-and~\ref{fig:gaussian_HJ}) would be that the apparent rate density
+which no planets are detected.  The effects on 
+Figures~\ref{fig:occ_rate_model_3_log},~\ref{fig:frac_model_3},
+and~\ref{fig:gaussian_HJ} would be that the apparent rate density
 below the cutoff in apparent radius would simply drop to zero.
@@
 denominator remains uncorrected.  To count the number of stars that
-were searched, further work on understanding the multiplicity
-statistics of KOI and non-KOI stars is necessary. In particular,
+were searched, further effort to understand the multiplicity
+statistics of KOI vs.~non-KOI stars is necessary. In particular,
 a non-KOI star high-resolution imaging effort could help estimate
@@
 centroids, little can be said about the likelihood of a
-planet orbiting the primary vs. the
-secondary~\citep[\textit{e.g.},][but see~\citealt{hirsch_assessing_2017}'s 
-approach to weighting radius corrections by planet 
+planet orbiting the primary vs.~the
+secondary~\citep[\textit{e.g.},][though~\citealt{hirsch_assessing_2017}'s 
+do weight radius corrections by planet 
 occurrence]{ciardi_understanding_2015,ziegler_robo-ao_2017}.
@@
 \acknowledgements{
-It was a pleasure discussing this study with T.
-Barclay, W.  Bhatti, and F. Dai.  This work made use of NASA's
-Astrophysics Data System Bibliographic Services.
+It was a pleasure discussing this study with T.~Barclay, W.~Bhatti,
+J.~Christiansen and F.~Dai.  This work made use of NASA's Astrophysics
+Data System Bibliographic Services.
 %
@@
 
-In this appendix, we derive Equation~\ref{eq:general_Gamma_a}.  First,
+This appendix derives Equation~\ref{eq:general_Gamma_a} in a more
+rigorous manner than in Section~\ref{sec:general_formula}.  First,
 recall our definition of apparent rate density
@@
 In this case, $\mathcal{N}_{{\rm s},q}^1$ is non-zero only at
-$r\a=R_a\sqrt{\delta_{\rm obs}}$, and the observed depth is
+$r\a=R\a\sqrt{\delta_{\rm obs}}$, and the observed depth is
 \begin{equation}
@@
 Again $\mathcal{N}_\star^2$ is non-zero only at
-$r\a=R_a\sqrt{\delta_{\rm obs}}$, but this time
+$r\a=R\a\sqrt{\delta_{\rm obs}}$, but this time
 \begin{equation}
@@
 This equation is used to derive
-Eqs.~\ref{eq:model5_apparent_rate_density}
+Equations~\ref{eq:model5_apparent_rate_density}
 and~\ref{eq:powerlaw_vary_binary}, and is numerically integrated to
@@
 
-Noting the definition of $\mu$ in Equation~\ref{eq:mu_general},
-Equation~\ref{eq:final_formula} can also be expressed as
-\begin{align}
-    \notag
-    \notag
-    \Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)} \cdot
-       \left[ \Gamma_0(r\a, M\a)\phantom{\tilde \Gamma}\right.&\\
-       &\left.+\mu(\mathrm{BF}, M\a)\cdot
-       %\tilde\Gamma_1(r\a, M\a)
-       \left\langle {1 \over \mathcal{A}}\cdot\Gamma_1\left({r\a\over\mathcal{A}}, M\a\right)
-       +%\tilde\Gamma_2(r\a, M\a)
-       {q \over \mathcal{B}}\cdot\Gamma_2\left({r\a\over\mathcal{B}}, qM\a\right) \cdot {R(qM\a) \over R(M\a)}q^{-1/3}\right\rangle
-       \right],
-\end{align}
-where the angle brackets denote averaging over $f(q)/\mathcal{A}^3$.
-This form shows that the fraction $\mu$ and mass ratio distribution
-$f(q)/\mathcal{A}^3$ of binaries {\it in the searchable volume} are
-enough to describe the contributions from binaries to $\Gamma\a$.  The
-fraction $\mu$ gives the relative contributions from singles and
-binaries, and $f(q)/\mathcal{A}^3$ weights the contributions from
-binaries with various mass ratios.  The apparent rate density at each
-mass ratio ({\it i.e.}, the terms in the angle brackets) is the rate
-density of systems that give the apparent $(r\a, M\a)$, corrected for
-the overestimated transit probability around secondaries.
-
 \newpage

### 2018-02-10 src/plot_visualize_volumes.py
visualize volumes plot to 2row

@@ -1,8 +1,8 @@
-# -*- coding: utf-8 -*-
 '''
 visualize the selected and searchable volumes for single stars and twin
 binaries.
 '''
+# -*- coding: utf-8 -*-
 from __future__ import division, print_function
 from matplotlib import rc
 rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
@@ -54,10 +54,7 @@ def make_sphere(radius, txt, ax, ind):
     x1, y1, _ = proj3d.proj_transform(-2**(-3/2)*radius, 2**(-3/2)*radius, 0,
                                       ax.get_proj())
     #beginning of arrow
-    if ind == 2: #nb top-right
-        prefactor = 1
-    else:
-        prefactor = 1
+    prefactor = 0.9 if ind==2 else 1
     x2, y2, _ = proj3d.proj_transform(-prefactor*radius, 1*radius, 1*radius, ax.get_proj())
 
     ann = ax.annotate(
@@ -77,16 +74,15 @@ def make_sphere(radius, txt, ax, ind):
     ax.patch.set_alpha(0.) # make background transparent
 
 
-fig = plt.figure(figsize=(4,5.5))
+fig = plt.figure(figsize=(4,4))
 
-inds = [1,2,3,4,5,6]
-radii = [1, 2**(1/2), 1/2, 2**(-1/2), 1, 2**(-1/2)]
-txts = ['$d_0$', '$\sqrt{2}d_0$', '$d_0/2$',
-        '$d_0/\sqrt{2}$', '$d_0$', '$d_0/\sqrt{2}$']
+inds = [1,2,3,4]
+radii = [1, 2**(1/2), 1, 2**(-1/2)]
+txts = ['$d_0$', '$\sqrt{2}d_0$', '$d_0$', '$d_0/\sqrt{2}$']
 
 for ind, r, txt in zip(inds, radii, txts):
 
-    ax = fig.add_subplot(3,2,ind,projection='3d')
+    ax = fig.add_subplot(2,2,ind,projection='3d')
 
     make_sphere(r, txt, ax, ind)
 
@@ -97,12 +93,10 @@ ax.text2D(.3, .05, 'single stars', transform=fig.transFigure,
      fontsize='large', va='bottom', ha='center')
 ax.text2D(.7, .05, 'twin binaries', transform=fig.transFigure,
      fontsize='large', va='bottom', ha='center')
[…]

### 2018-02-10 paper/main.tex
clarifications based on KM suggestions

@@
         twin binaries with $r\a=r\p$.
-        {\it Middle:} At $r\a=r\p/\sqrt{2}$, the maximum searchable
+        {\it Bottom:} At $r\a=r\p/\sqrt{2}$, the maximum searchable
         distances are half those at $r\a=r\p$.  The only detected
         planets with $r\a=r\p/\sqrt{2}$ orbit twin binaries.
-        {\it Bottom:} Planets with a true radius $r=r\p$ are
-        searchable to a maximum distance $d_0$ around singles, and
-        $d_0/\sqrt{2}$ around twin binaries.
     }
@@
 point-sources on sky, based on Equation \ref{eq:dmax}.  If we let $\mu
-\equiv N\star^{\rm b}(r\a)/N_\star^0(r\a)$ be the ratio of the number
+\equiv N_\star^{\rm b}(r\a)/N_\star^0(r\a)$ be the ratio of the number
 of searchable binary systems to single systems, then the number of
@@
 rate density for each type of star, $\Gamma_i(r)$, as the product of a
-shape function and a constant:
+shape function, normalized to unity, and a constant:
 \begin{equation}
@@
 where $i=0$ corresponds to single stars, $i=1$ to primaries of
-binaries, and $i=2$ to secondaries of binaries.  The shape function is
-normalized to unity.  The $Z_i$'s are each system type's occurrence
+binaries, and $i=2$ to secondaries of binaries.
+The $Z_i$'s are each system type's occurrence
 rate $\Lambda_i$, integrated over all planetary radii. In other words,
-they are number of planets per single, primary, or secondary star.  We
-want to consider the effects of varying not only $f_i(r)$ but also the
-relative values of the $Z_i$'s.
+they are number of planets per single, primary, or secondary star.
+While our main interest is in varying the radius shape function
+and the relative values of integrated occurrence rates, we 
+will also briefly discuss shape functions in stellar mass.
+To keep things analytically simple, we will assume throughout this
+section that stars are a one-parameter family, given by 
+$L \propto M^\alpha \propto R^\alpha$, so that a given value 
+of $q$ determines everything about a secondary.
 
@@
 \subsubsection{Twin binaries}
-We begin introducing realism by keeping all binaries as twins, but
-letting the planet radius distributions vary.  First, we assume a
+As a first step, we keep all binaries as twins, but
+let the planet radius distribution vary.  If we take a
 power law planet radius distribution,
@@
 \end{equation}
-for $f(r)$ the radius shape function, and $\mathcal{N}_r$ the shape
-function's normalization.  The resulting apparent rate density is 
+for $\mathcal{N}_r$ the shape function's normalization, then
+Equation~\ref{eq:general_Gamma_a} gives the resulting apparent rate density,
 \begin{equation}
@@
     \right)
-    \right],
+    \right].
     \label{eq:model5_apparent_rate_density}
 \end{equation}
-which is quite similar to the twin binary, fixed-planet case
-(Equation~\ref{eq:model_1_apparent_rate_density}), except for in the
+This is similar to the twin binary, fixed-planet case
+(Equation~\ref{eq:model_1_apparent_rate_density}), except for the
 radius dependence and normalization.  As in Section~\ref{sec:model_1},
 $\mu = 2^{3/2} n\b/n\s$.  If the $Z_i$'s are equal, the ``correction
-factor'' relative to the rate density for singles becomes quite
-simple:
+factor'' relative to the rate density for singles becomes simple:
 \begin{align}
@@
 assume $f(q) = q^\beta/\mathcal{N}_q$, for $\mathcal{N}_q$ the
-normalization.  This changes $\mu$ (Equation~\ref{eq:mu_general}
-simplifies to Equation~\ref{eq:mu_power_laws}).  It may also affect
-the rate density, which could be a function of the varying stellar
-mass.  Absorbing this dependence into a power law as well,
+normalization.
+This changes $\mu$: taking the volume-limited binary mass ratio
+distribution to be $f(q) \propto q^\beta$, Equation~\ref{eq:mu_general} 
+simplifies to
+\begin{equation}
+    \mu = \frac{n\b}{n\s} \frac{1}{1+\beta}
+    \int_0^1 (1+q^\alpha)^{3/2}q^\beta\,{\rm d}q.
+    \label{eq:mu_power_law_q}
+\end{equation}
+ The rate density might now also vary with 
+host star mass.  We can absorb this dependence into a power
+law,
 \begin{equation}
@@
 where $Z_i$ is dimensionless, and the normalization constants carry
-the units (each side has units $[r^{-1} M^{-1}]$).  We assume that
-stars are a one-parameter family, given by $R \propto M \propto
-L^{\frac{1}{\alpha}}$, so that a given value of $q$ determines
-everything about a secondary.
+the units (each side has units $[r^{-1} M^{-1}]$).
 
@@
 dependence.  Marginalizing Equation~\ref{eq:general_Gamma_a} over
-apparent stellar mass, we find that when $Z_0=Z_1=Z_2$,
+apparent stellar mass, we find that when all stars host the same number
+of planets ($Z_0=Z_1=Z_2$),
 \begin{align}
-    X_\Gamma &\equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
-    \right|_{r\a\rightarrow r} \\
+    \notag
+    \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
+    \right|_{r\a\rightarrow r}
     &=
-    \notag
     \frac{1}{1+\mu}
@@
     %isn't latex great?
-    &\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
+    &\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
     \left.\left.
@@
 summed integrals in Equation~\ref{eq:powerlaw_vary_binary} give
-$(\ldots)\approx 1.50249$. %171211_model_integrals.nb
+$(\ldots)\approx 1.503$. %171211_model_integrals.nb
 For $n\b / (n\b + n\s)=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$;
@@
 secondaries, binarity influences apparent planet occurrence rates
-around Sun-like stars at the $\sim$few percent level.
+around Sun-like stars at the few percent level.
 
@@
 $r<2r_\oplus$ are currently an active topic of research, we can
-consider how binarity affects this regime under different plausible
-assumptions.  For instance, assume that the true radius shape function
-is
+investigate how binarity affects this regime by making plausible
+assumptions.  For instance, we can assume a broken power-law:
 \begin{align}
@@
 \end{align}
-As in the previous model, we presume that the observers know the true
-properties of all singles and primaries. The masses, radii, and
-luminosities of stars vary as $R \propto M \propto
-L^{\frac{1}{\alpha}}$.  Our ``nominal model'' remains the same:
+Our ``nominal model'' remains the same:
+$L\propto M^\alpha \propto R^\alpha$, and
 $\alpha=3.5$, $\beta=\gamma=0$, $\delta=-2.92$.
 
-At apparent radii $r\a > 2r_\oplus$, the results of this model are the
-same as those from Section~\ref{sub:powerlaw_varying_binaries}.  For
+At apparent radii $r\a > 2r_\oplus$, the apparent rate density in
+this model is the same as from
+Section~\ref{sub:powerlaw_varying_binaries}.  For
 $r\a < 2r_\oplus$, the equations are tedious, but still tractable.
@@
 case in which secondaries host as many (half as many) planets as
-single stars, this means an overestimate of the absolute occurrence
+single stars, this means an overestimate of the occurrence
 rate by $\approx 50\%$ ($\approx 25\%$).  The ``bump'' exists even for
 the $Z_2/Z_0=0$ case as a $\approx 10\%$ effect.  The magnitude of
-this evidently error depends strongly on the prevalence of planets
+this error evidently depends strongly on the prevalence of planets
 around secondaries.
@@
     \Lambda_{\rm HJ,a} =
-      \int_{8r_\oplus}^{\infty} \Gamma\a(r)\,{\rm d}r,
+      \int_{8r_\oplus}^{\infty} \Gamma\a(r\a)\,{\rm d}r\a,
 \end{equation}

### 2018-02-14 paper/main.tex
improve text
substantially

@@
 
-Wide-field surveys for transiting planets, such as the NASA
-{\it Kepler} and {\it TESS} missions, are usually conducted without
-knowing which stars are binaries. Unresolved and unrecognized binary
-stars give rise to systematic errors in planet occurrence rates,
-including misclassified planets and miscounts in the number of
-searched stars. The individual errors can have different signs,
-making it difficult to anticipate the net effect on inferred
-occurrence rates. Here we use simplified models of signal-to-noise
-limited transit surveys to try and clarify the situation. We derive
-a formula for the apparent occurrence rate density measured by an
-observer who falsely assumes all stars are single. The formula
-depends on the binary fraction; the mass function of the secondary
-stars; and the true occurrence of planets around primaries,
-secondaries, and single stars. It also takes into account the
-Malmquist bias by which binaries are over-represented in
-flux-limited samples. Application of the formula to an idealized
+Wide-field surveys for transiting planets, such as the NASA {\it
+Kepler} and {\it TESS} missions, are usually conducted without knowing
+which stars are binaries. Unresolved and unrecognized binary stars
+give rise to systematic errors in planet occurrence rates, including
+misclassified planets and miscounts in the number of searched stars.
+The individual errors can have different signs, making it difficult to
+anticipate the net effect on inferred occurrence rates. Here we use
+simplified models of signal-to-noise limited transit surveys to try
+and clarify the situation. We derive a formula for the apparent
+occurrence rate density measured by an observer who falsely assumes
+all stars are single. The formula depends on the binary fraction; the
+mass function of the secondary stars; and the true occurrence of
+planets around primaries, secondaries, and single stars. It also takes
+into account the Malmquist bias by which binaries are over-represented
+in flux-limited samples. Application of the formula to an idealized
 {\it Kepler}-like survey shows that for planets larger than
-$2r_\oplus$, the net systematic error is of order 10\%. For smaller
-planets the errors are potentially larger: the occurrence of
-Earth-sized planets could be overestimated by as much as a factor of
-two. One consequence is that unrecognized binaries cannot account
-for the apparent discrepancy between hot Jupiter occurrence
-rates measured by transit and RV surveys. We also show that if
+$2r_\oplus$, the net systematic error is of order 10\%.  One
+consequence is that unrecognized binaries cannot account for the
+apparent discrepancy between hot Jupiter occurrence rates measured by
+transit and RV surveys.  For smaller planets the errors are
+potentially larger: the occurrence of Earth-sized planets could be
+overestimated by as much as a factor of two. We also show that if
 high-resolution imaging reveals a transit host star to be a binary,
@@
   howard_planet_2012,fressin_false_2013,
-  dressing_occurrence_2015,burke_terrestrial_2015}. In reality many of
-them are unresolved multiple-star systems, especially binaries.
-Unrecognized binaries cause numerous systematic errors in the
-planetary occurrence rates.  For example, when there is a transiting
-planet around a star in a binary, the additive constant light from the
-second star reduces the fractional loss of light due to the planet.
-This ``flux dilution'' makes transit signals harder to detect and
-lowers the number of detections.  On the other hand, in a binary there
-two opportunities to detect transiting planets, which could increase
-the overall number of detections.
+  dressing_occurrence_2015,burke_terrestrial_2015}. 
+In reality, many of the point sources seen in a transit survey are
+unresolved multiple-star systems, especially binaries.  Unrecognized
+binaries cause numerous systematic errors in the planetary occurrence
+rates.  For example, when there is a transiting planet around a star
+in a binary, the additive constant light from the second star reduces
+the fractional loss of light due to the planet.  This makes transit
+signals harder to detect and lowers the number of detections.  On the
+other hand, in a binary there are two opportunities to detect
+transiting planets, which could increase the overall number of
+detections.
 
@@
 of binaries was a serious issue at all, or even whether the net effect
-of all the errors is positive or negative.  The goal of this study was
-to clarify the various sources of error and provide a framework for
-dealing with these issues.  In this spirit, most of our models are
-idealized and analytic, and we do not attempt a detailed correction of
-the results from {\it Kepler} or any other real transit survey.
-Our goal is to estimate the order of magnitude of the effects,
-assuming the survey is signal-to-noise limited, and given the true
-underlying planet occurrence rates.
+of all the errors is positive or negative.  The goals of this study
+were to provide a framework for dealing with these issues, and to
+calculate a leading-order estimate for the net systematic effects.  In
+this spirit, our models are idealized and analytic, and we do not
+attempt a detailed correction of the results from {\it Kepler} or any
+other real transit survey.
 
@@
 \begin{equation}
-\frac{\delta_{\rm obs}}{\sigma}
-  = ({\rm constant}) \cdot \delta_{\rm obs} L_{\rm sys}^{1/2} d^{-1}
-> \left(\frac{{\rm S}}{{\rm N}}\right)_{\rm min}.
+  \frac{\delta}{\sigma}
+  >
+  \left(\frac{{\rm S}}{{\rm N}}\right)_{\rm min}.
 \label{eq:S_N_thresh}
 \end{equation}
-Here the signal S is the observed transit depth $\delta_{\rm obs}$, in
-units of relative flux.
-%LB: we don't introduce r or R because they are system-specific.
-%For single stars, $\delta_{\rm obs} \approx (r/R)^2$; for binaries,
-%flux dilution $\mathcal{D}$ lowers the observed depth to
-%$\delta_{\rm obs} \approx \mathcal{D} (r/R)^2$. 
-The noise N is the uncertainty in the determination of the flux ratio
-of the star inside and outside of transits.  Throughout this paper we
-will assume the photometric uncertainty to scale as the inverse square
-root of the number of photons collected from the source, {\it i.e.},
-the dependence on stellar properties is $\sigma \propto (L_{\rm
-sys}/d^2)^{-1/2}$, where $L_{\rm sys}$ is the luminosity of the
-stellar system and $d$ is its distance from Earth.
-% The solid angle coverage, telescope area, and
-% survey duration are in the ``constant'' term of
-% Equation~\ref{eq:S_N_thresh}.  The transit duration also affects
-% detectability, but we omit it in this work for brevity.
-
-The astronomers then assume that all stars are single.  In particular
-they do not have accurate enough parallaxes to tell that some of the
-stars are apparently overluminous.  They want to compute the number of
-planets with size $r$ per star of mass $M$.  If the total number of
-stars for which such planets could be detected ($N_\star$) and the
-number of detected planets ($N_{\rm det}$) are both large, then the
-astronomers' estimate for the occurrence rate ($\Lambda$) is simply
+Here the signal S is the observed transit depth $\delta$, in units of
+relative flux.  The noise N is the uncertainty in the determination of
+the flux ratio of the star inside and outside of transits.  The
+minimum signal-to-noise for detection, $({\rm S}/{\rm N})_{\rm min}$,
+depends on the properties of the telescope.  We will assume throughout
+this paper that the photometric uncertainty scales as the inverse
+square root of the number of photons collected from the source, {\it
+i.e.}, the dependence on stellar properties is $\sigma \propto (L_{\rm
+tot}/d^2)^{-1/2}$, where $L_{\rm tot}$ is the total luminosity of the
+stellar system and $d$ is its distance from Earth.  The observed
+signal amplitude $\delta$ depends on the fraction of the total
+luminosity that comes from the planet-hosting star, since light from
+unresolved stellar companions is not affected by the planet's transit.
+% The transit duration also affects detectability, but we omit it in
+% this work for brevity.
+
+The astronomers analyze their data assuming that all stars are
+single.  In particular they do not have accurate enough parallaxes to
+tell that some of the stars are apparently overluminous.  They want to
+compute the number of planets with size $r$ per star of mass $M$.  If
+the total number of stars for which such planets could be detected
+($N_\star$) and the number of detected planets ($N_{\rm det}$) are
+both large, then the astronomers' estimate for the occurrence rate
+($\Lambda$) is simply
 \begin{equation}
@@
 \end{equation}
-where $p_{\rm tra}$ is the geometric transit probability, needed to
-account for the fact that most planetary orbits are not aligned close
-enough with our line of sight to produce transits.
+where the geometric transit probability, $p_{\rm tra}$, accounts for
+the fact that most planetary orbits are not aligned close enough with
+our line of sight to produce transits.
 
@@
 
-We will focus exclusively on the subset of problems that arise from
-the fact that many stars exist in gravitationally bound binary
-systems.  Even with this narrow focus, there are numerous sources of
-error.  All three of the quantities in
-Equation~\ref{eq:occ_rate_simple} are subject to observational bias:
+We will focus exclusively on problems that arise from the fact that
+many stars exist in gravitationally bound binary systems.  Even with
+this narrow focus, there are numerous sources of error.  All three of
+the quantities in Equation~\ref{eq:occ_rate_simple} are subject to
+observational bias:
 \begin{enumerate}
 %    
-    \item The number of planets, $N_{\det}$, is actually the number of
-      detected planets that {\it appear} to have size $r$, orbiting
-      stars that {\it appear} to have mass $M$.  Whenever the
+    \item The detected planet count, $N_{\det}$, is actually the
+      number of detected planets that {\it appear} to have size $r$,
+      orbiting stars that {\it appear} to have mass $M$.  Whenever the
       planet-hosting star is part of a binary,
@@
 different occurrence 
-distributions~\citep[{\it e.g.},][]{
+distributions~\citep[see][]{
     wang_occurrence_2015,kraus_impact_2016}.
 
-The other problem is an observational effect.  Even after the
-astronomers learn about binaries and attempt to correct for their
-presence, they must realize that the ratio of binaries to single stars
-in the searched sample will differ from that in a volume-limited
-sample due to a type of Malmquist bias.  Binaries have a higher total
-luminosity than either the primary or secondary star would have on its
-own.  This means that the binaries are searchable for transit signals
-of a given amplitude at greater distances from the Earth.  The
-binaries in a sample of apparently searchable stars are therefore
-drawn from a larger search volume than the single stars.
+The other problem is an observational effect. In the searched sample,
+the ratio between the number of binary and single stars will differ
+from that in a volume-limited sample due to a type of Malmquist bias.
+The total luminosity of a binary is larger than the luminosity of
+either the primary or secondary star.  This means that for transit
+signals of a given amplitude, the binaries are searchable at greater
+distances from the Earth.  Thus for any planet and star pair, adding a
+stellar companion both helps and hinders transit detection: the extra
+photons help by lowering the noise, and hinder by diminishing the
+observed transit depth.
+% Accounting for each effect requires some care.
 
@@
 analytic model allowing for generality in the distribution of the
-binaries and the planets they host.  We consider only corrections to
-the occurrence as a function of planetary radius, and not orbital
-period (the other key variable in transit studies), because when
-multiple transits are detected the period can be directly measured
-regardless of whether the host star is single or part of a binary.
+binaries and the planets they host.
 
@@
         mass, radius, and luminosity, and that all planets have the
-        same radius $r=r\p$.
-        {\it Top:} At an apparent radius $r\a=r\p$, the observer
-        searched twin binaries out to a distance $\sqrt{2}\times$ that
-        of single stars.  Because of dilution, there are no planets in
-        twin binaries with $r\a=r\p$.
-        {\it Bottom:} At $r\a=r\p/\sqrt{2}$, the maximum searchable
-        distances are half those at $r\a=r\p$.  The only detected
-        planets with $r\a=r\p/\sqrt{2}$ orbit twin binaries.
+        same radius $r\p$.
+        {\it Top:} At an apparent radius $r\a=r\p$, the
+        binarity-ignoring observers search twin binaries out to a
+        distance $\sqrt{2}$ times greater than they search single
+        stars.  Because the transit depths are diluted, there are no 
+        planets in twin binaries with $r\a=r\p$.
+        {\it Bottom:} At $r\a=r\p/\sqrt{2}$, the observed transit
+        depths are smaller by a factor of two, so the maximum
+        searchable distances are half those at $r\a=r\p$.  The only
+        detected planets with $r\a=r\p/\sqrt{2}$ orbit twin binaries.
     }
@@
 
-Since the effects of binarity are most pronounced when the two
+Since the effects of binarity are most pronounced when the two stellar
 components are similar, we begin by considering a universe in which
@@
 $L$.  Some fraction of them exist in twin binaries. All planets have
-size $r\p$.  In this scenario, stars are never misclassified because
-the combined light of a binary has the same color and spectrum as a
-single star.  We further assume that planets occur around single stars
-and members of binaries at the same rate, $\Lambda(r\p)$.
-
-The only type of planet in this universe produces a transit signal of
-amplitude $\delta_{\rm obs} = (r\p/R)^2$ when the host is a single
-star.  Our naive observers try to measure the occurrence rate of these
-planets.  They identify all the ``stars'' in their sample that appear
-to be searchable for such a signal, given the size of their telescope.
-These transits are detected within a certain maximum 
-distance~\citep[see][]{pepper_using_2003,pepper_searching_2005}, which from
-Equation~\ref{eq:S_N_thresh} scales as
-\begin{equation}
-  d_{\rm max} \propto \delta_{\rm obs} \cdot L_{\rm sys}^{1/2}.
+size $r\p$.  In this scenario, stellar radii are never misclassified
+because the combined light of a binary has the same color and spectrum
+as a single star.  We further assume that planets occur around single
+stars and members of binaries at the same rate, $\Lambda(r\p)$.
+
+Our naive observers detect transiting planets with two different
+depths. Since 
+\begin{equation}
+    \delta = \left(\frac{r\p}{R}\right)^2 \frac{L}{L_{\rm tot}},
+    \label{eq:delta_obs_general} 
+\end{equation}
+one class of transit signal, with depth $(r\p/R)^2$, occurs in single
+star systems. The other class, with half the depth, occurs in twin
+binary systems, leading to apparent planet radii $\sqrt{2}$ smaller
+than the true radii.
+
+To calculate the occurrence rate of each planet type, our observers
+identify the ``stars'' from their survey that appear to have been
+searched for signals of each depth.  These transits are detected
+within a certain maximum
+distance~\citep[see][]{pepper_using_2003,pepper_searching_2005}, which
+from Equation~\ref{eq:S_N_thresh} scales as
+\begin{equation}
+  d_{\rm max} \propto \delta \cdot L_{\rm tot}^{1/2}.
   \label{eq:dmax}
@@
 Assuming that stars are uniformly distributed in space, the number of
-searchable stars $N_\star$ is then proportional to
-\begin{equation}
-    N_\star \propto n_i \delta_{\rm obs}^3 L_{\rm sys}^{3/2},
+searchable stars $N_\star$ is proportional to
+\begin{equation}
+    N_\star \propto n \delta^3 L_{\rm tot}^{3/2},
 \label{eq:N_searchable_prop}
 \end{equation}
-where $n_i$ is the number per unit volume of single stars, or
-binary systems.
-
-This selection process inadvertently admits some binaries.  Since the
-binaries are twice as luminous as singles, they are included out to a
-distance that is larger by a factor of $\sqrt{2}$, and if they have
-transiting planets then the signals have an amplitude of
-$(r\p/R)^2/2$.  To detect this half-strength signal, the observers
-need the noise level to be lower by a factor of two, which means the
-flux must be four times higher than that of a single star at distance
-$d_0$.  This is true of single stars within a distance $d_0/2$, and
-binaries within a distance $d_0\sqrt{2}/2$.
-Furthermore the observers will consider any such shrunken signals to
-represent planets of a different type, smaller in radius by a factor
-of $\sqrt{2}$. These searchable volumes are illustrated in 
+where $n$ is the number per unit volume of single or binary star
+systems.
+
+When selecting sources that appear to have been searched, the
+observers admit some binaries.  Since the binaries are twice as
+luminous as singles, at fixed $\delta$ they are included out to a
+distance that is larger by a factor of $\sqrt{2}$.  To detect the
+half-strength signal, the observers need the noise level to be lower
+by a factor of two, which means the flux must be four times higher
+than that of a single star at distance $d_0$.  This is true of single
+stars within a distance $d_0/2$, and binaries within a distance
+$d_0\sqrt{2}/2$.  The searchable volumes are illustrated in
 Figure~\ref{fig:model_1_volumes}.
 
-Putting it all together, the {\it apparent} occurrence rate of planets
-of radius $r\p$ will be
+Putting it all together, the {\it apparent} occurrence rate
+$\Lambda\a$ of planets of radius $r\p$ will be
 \begin{equation}
     \Lambda\a(r\p) = 
-        \frac{\Lambda(r\p)~n\s d_0^3}
+        \frac{\Lambda(r\p) \, n\s d_0^3}
         {n\s d_0^3 + n\b (d_0\sqrt{2})^3}
-\end{equation}
-where $n\s$ and $n\b$ are the number densities of single stars and
-binary stars, respectively, in the local neighborhood.  This apparent
-rate is larger than the true rate by a factor
+    \label{eq:rate_at_rp}
+\end{equation}
+where $n\s$ and $n\b$ are the number densities of single and binary
+star systems, respectively.  This apparent rate is larger than the
+true rate by a factor
 \begin{equation}
@@
 \end{equation}
-The observers will also claim to have discovered a new type of planet
+The observers will also claim to have discovered a class of planet
 with radius $r\p/\sqrt{2}$ and an occurrence rate given by
 \begin{equation}
-\label{eq:correction_diluted_rp}
     \frac{\Lambda\a(r\p/\sqrt{2})}{\Lambda(r\p)}
@@
     (n\b/n\s)}.
+    \label{eq:correction_diluted_rp}
 \end{equation}
@@
 1.3~$M_\odot$, \citet{raghavan_survey_2010} found the multiplicity
-fraction to be 0.44, where multiplicity fraction is defined as
-the fraction of systems in a volume-limited sample that are multiple.
-Since we assume all multiple systems are binaries, this implies
-\begin{equation}
-    \frac{n\b}{n\s + n\b} \approx 0.44,
-\end{equation}
-which corresponds to a specific $n\b/n\s$.  Of course not all of these
-binaries are close to being ``twin'' binaries as we have assumed in
-our simple calculation. Perhaps only a tenth of them have pairs of
-stars close enough in their basic properties to produce errors as
-significant as those we have been considering.  Thus, an appropriate
-estimate for $n\b/(n\s+n\b)$ is of order $0.05$, leading to
+fraction~--~the fraction of systems in a volume-limited sample that
+are multiple~--~to be 0.44.  Assuming all multiple systems are
+binaries, this means
+\begin{equation}
+    \frac{n\b}{n\s + n\b} \approx 0.44.
+\end{equation}
+Of course not all of these binaries are ``twin'' binaries as we have
+assumed in our simple calculation. Perhaps only a tenth of the
+binaries have pairs of stars close enough in their basic properties to
+produce errors as significant as those we have been considering. In
+detail, this fraction depends on the binary mass ratio distribution
+and stellar mass-luminosity relation (see
+Section~\ref{sec:general_formula}).  Taking a leading-order estimate
+of $n\b/(n\s+n\b)\approx0.05$, we find
 \begin{equation}
@@
 \end{equation}
-All together the various effects produce biases of order 10\% in the
+All together, the various effects produce biases of order 10\% in the
 occurrence rates.  We will see that this level of error is
-characteristic of many of our more complicated models, as well.
+characteristic of many of our more complicated models as well.
 
@@
 There is a different way to conceptualize the preceding results that
-will be useful in the subsequent discussion.  Here we broaden the
-discussion to consider a spectrum of planet sizes, by introducing the
-occurrence rate density
-\begin{equation}
-    \Gamma(r) \equiv \frac{d\Lambda}{dr},
-\end{equation}
-the average number of planets per star per unit planet radius.
-
-To clarify our terminology, we define ``apparent properties'' as the
-properties that one would infer about a system under the assumption
-that the host star is single. For instance, the  ``apparent planet
-radius'', $r\a$, is the planet radius that one would infer from a
-transit signal, assuming that the host star is single.  The observed
-transit depth is given by the ratio of the apparent planet radius and
-the apparent stellar radius, $R\a$:
-\begin{equation}
-  \delta_{\rm obs}
-  = \left(\frac{r\a}{R\a}\right)^2
-  = \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over
-          L_{\rm sys}},
-  \label{eq:delta_obs_general} 
-\end{equation}
-for $r$ the planet radius, $R_{\rm host}$ ($L_{\rm host}$) the host
-star's radius (luminosity), and $L_{\rm sys}$ the entire system's
-luminosity. This gives $r\a=r\p/\sqrt{2}$ in our ``twin binary''
-model.
-
-With this definition we may say that naive observers are measuring
-$\Gamma\a(r\a)$, the apparent occurrence rate density of planets with
-an apparent radius of $r\a$.  Analogous to
-Equation~\ref{eq:occ_rate_simple},  
-\begin{equation}
-  \Gamma\a(r\a) = \frac{n_{\rm det}(r\a)}{N_\star(r\a)}
-      \times \frac{1}{p_{\rm tra}},
-\label{eq:apparent_rate_density}
-\end{equation}
-where $n_{\rm det}$ is the number of detected planets, per unit $r\a$,
-with apparent radius $r\a$.  In
-Equation~\ref{eq:apparent_rate_density}, we neglect the dependence on
-stellar mass since all stars in this model have the same properties.
-Since $\delta_{\rm obs}$ and $r\a$ are related by $R\a$, which is
-simply assumed by an observer, measuring $\Gamma\a(r\a)$ is equivalent
-to measuring the true occurrence rate density of {\it transit signals}
-of amplitude $\delta_{\rm obs}$.
-
-Let us evaluate the contributions to $n_{\rm det}$ from singles and
-binaries.  As in the previous subsection, for each apparent planet
-radius $r\a$, the observers select $N_\star(r\a)$ unresolved
-point-sources on sky, based on Equation \ref{eq:dmax}.  If we let $\mu
-\equiv N_\star^{\rm b}(r\a)/N_\star^0(r\a)$ be the ratio of the number
-of searchable binary systems to single systems, then the number of
-single and binary point-sources thought to be searchable are
+will be useful in the upcoming discussion. We now consider a spectrum
+of planet sizes, $r$, and introduce the occurrence rate density
+\begin{equation}
+    \Gamma(r) \equiv \frac{{\rm d}\Lambda}{{\rm d}r},
+    \label{eq:rate_density_defn}
+\end{equation}
+the number of planets per star per unit planet radius.
+
+The naive observers are in fact measuring $\Gamma\a(r\a)$, the {\it
+apparent} occurrence rate density~--~the number of planets per star
+per unit apparent radius $r\a$.  The ``apparent planet radius'' is the
+radius inferred from the transit depth under the assumption that the
+host star is single. The ``apparent stellar radius'' $R\a$ is
+analogous.  The observed transit depth can be written $\delta =
+(r\a/R\a)^2$, which from Equation~\ref{eq:delta_obs_general} gives
+$r\a=r\p/\sqrt{2}$ for planets in twin binaries.  $\Gamma\a(r\a)$ is
+the same as the {\it true} rate density of transit signals of
+amplitude $\delta$.
+
+We will now calculate the apparent rate density by evaluating the star
+and planet counts for signals coming from single stars, primary stars
+in binaries, and secondary stars in binaries.  Let $\mu$ be the ratio
+between the number of searchable binary systems and the number of
+searchable single systems at a particular transit depth. The number of
+single and binary sources in the searched sample are then
 \begin{equation}
   \frac{N_\star(r\a)}{1+\mu}~~{\rm and}~~\frac{\mu N_\star(r\a)}{1+\mu},
+  \label{eq:N_searched}
 \end{equation}
@@
 
-We further stipulate that the true occurrence rate densities for
-planets around single stars, primaries, and secondaries are
-$\Gamma_0(r)$, $\Gamma_1(r)$, and $\Gamma_2(r)$, respectively.  
-Then single stars contribute
-\begin{equation}
-  n_{\rm det}^0(r\a) = 
-    {N_\star(r\a) \over {1+\mu}} p_{\rm tra} \Gamma_0(r\a)
-  \label{eq:n0}
-\end{equation}
-planet detections per unit $r\a$.  We can similarly compute the number
-of planet detections from binaries.  Since $r\p=\sqrt{2}r\a$ for
-planets in twin binaries, 
-\begin{equation}
-  n_{\rm det}^1(r\a)\mathrm{d}r\a =
-      {\mu N_\star(r\a) \over {1+\mu}} p_{\rm tra}
+Suppose the occurrence rate densities for planets around
+single stars, primaries, and secondaries are $\Gamma_0(r),
+\Gamma_1(r)$, and $\Gamma_2(r)$, respectively. For a single planet
+size,
+\begin{equation}
+    \Gamma_i(r) = \Lambda(r\p) \cdot \hat{\delta}(r-r\p),~~{\rm for}
+    \ i\in\{0,1,2\},
+    \label{eq:one_planet}
+\end{equation} 
+where $\hat{\delta}$ is the Dirac delta function.
+The number of planets detected from singles, primaries, and
+secondaries are then
+\begin{align}
+  n_{\rm det}^0(r\a)\mathrm{d}r\a &= 
+      \frac{N_\star(r\a)}{1+\mu} p_{\rm tra}
+      \Gamma_0(r\a)\mathrm{d}r\a,
+  \label{eq:n0} \\
+  n_{\rm det}^1(r\a)\mathrm{d}r\a &= 
+      \frac{\mu N_\star(r\a)}{1+\mu} p_{\rm tra}
       \Gamma_1(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
-	\label{eq:n1}
-\end{equation}
-detections come from primaries, and
-\begin{equation}
-  n_{\rm det}^2(r\a)\mathrm{d}r\a =
-      {\mu N_\star(r\a) \over {1+\mu}} p_{\rm tra}
+	\label{eq:n1} \\
+  n_{\rm det}^2(r\a)\mathrm{d}r\a &=
+      \frac{\mu N_\star(r\a)}{1+\mu} p_{\rm tra}
       \Gamma_2(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
 	\label{eq:n2}
-\end{equation}
-from secondaries.  Here the transit probability $p_{\rm tra}$ is the
-same in all three cases because the stars are all identical.
-
-Using Equation~\ref{eq:apparent_rate_density}, the apparent rate
-density reported when ignoring binarity is
-\begin{equation}
-	\label{eq:formula_twin_binary}
+\end{align}
+where $n_{\rm det}^i$ is the number of detections per unit apparent
+radius for each respective type of star.
+
+Dividing the number of detections by the number of sources,
+the apparent rate density reported when ignoring binarity is
+\begin{equation}
   \Gamma\a(r\a) =
@@
     \frac{\mu}{1+\mu}\,\sqrt{2}\,\Gamma_2(\sqrt{2}r\a).
-\end{equation}
-If we further assume 
-\begin{equation}
-	\Gamma_i=Z \cdot \delta(r\a-r\p)
-\end{equation} 
-as we did in the previous ``one planet" example,
-the above apparent rate density reduces to
+	\label{eq:formula_twin_binary}
+\end{equation}
+If we insert Equation~\ref{eq:one_planet} and integrate over
+apparent radius, this reproduces Equations~\ref{eq:rate_at_rp}
+and~\ref{eq:correction_diluted_rp}.
+
+\begin{comment}
+  and inputting Equation~\ref{eq:one_planet}, we find
   \begin{align}
-    \Gamma\a(r\a) &= Z \left[
+      \Gamma\a(r\a) &= \Lambda(r\p) \left[
       \frac{1}{1+\mu} \cdot
-    \delta(r\a-r\p)  +
+      \hat{\delta}(r\a-r\p)  +
       \frac{2\mu}{1+\mu} \cdot
@@
   and~\ref{eq:correction_diluted_rp}.
+\end{comment}
 
@@
         X_\Gamma(r) \equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)}
-          \right|_{r\a \rightarrow r},
+          \right|_{r\a = r},
     \end{equation}
@@
         \Gamma_i(r) = \frac{Z_i}{2} \left[
-        \delta(r-r\p) + \delta\left(r-\frac{r\p}{\sqrt{2}}\right)
+        \hat{\delta}(r-r\p) + \delta\left(r-\frac{r\p}{\sqrt{2}}\right)
         \right], \quad {\rm for}\  i \in \{ 0,1,2 \},
@@
         \frac{1}{2(1+\mu)} \left[
-        Z_0 \cdot \delta(r\a - r\p)
+        Z_0 \cdot \hat{\delta}(r\a - r\p)
         +
@@
 
-To generalize the procedure of Section~\ref{sec:model_1_density} to binaries
-with varying mass ratios, we consider an SNR-limited transit survey in which
-stars can have arbitrary properties.  We assume that there are some functions
-$L(M)$ and $R(M)$ that specify a star's luminosity and radius in terms of its
-mass, and that the volume-limited binary mass ratio distribution, $f(q)$, is
-independent of the primary's mass.  We also allow arbitrary true rate densities
-for singles, primaries, and secondaries ($\Gamma_0, \Gamma_1, \Gamma_2$).  We
-presume that the observers always know the true masses of singles and
-primaries, and that they take the primary's properties to be those of an
-unresolved binary.
-
-Due to the varying mass ratios, we need the following modifications to Equation
-\ref{eq:formula_twin_binary}:
+To generalize the procedure of Section~\ref{sec:model_1_density} for
+binaries with varying light ratios, we consider an SNR-limited survey
+in which stars can have arbitrary properties.  We assume that there
+are some functions $L(M)$ and $R(M)$ that specify a star's luminosity
+and radius in terms of its mass. We also presume that the observers
+know the masses of every single and primary star, and that they assign
+each binary system the properties of its primary.  Finally, we take
+the volume-limited distribution of binary mass ratios, $f(q)$, to be
+independent of the primary star's mass.
+
+We want an equation for $\Gamma\a(r\a,M\a)$, the apparent rate density
+at each apparent planet radius and apparent stellar mass\footnote{By
+assumption, the apparent stellar mass for single star systems is the
+true mass. For binary systems, the apparent mass is the mass of the
+primary.}.
+Similar to Equation~\ref{eq:rate_density_defn}, we define
+$\Gamma(r,M)$ as the number of planets per star, per unit planet radius,
+per unit stellar mass.  Due to the varying binary mass ratios, we need
+the following modifications to Equation~\ref{eq:formula_twin_binary}:
+%
 \begin{enumerate}
 %
-  \item The number of binary systems with mass ratio $(q,
-  q+\mathrm{d}q)$ in the selected sample is now
-  (Equation~\ref{eq:dmax}):
+\item The Malmquist bias is different. The ratio between the number of
+binary and single systems for which a transit of depth $\delta$ is
+detectable, $\mu$, has changed.  At any $(r\a,M\a)$ pair, the number
+of binary systems in the searchable volume with mass ratio $(q,
+q+\mathrm{d}q)$ is now
 \begin{equation}
     {N_\star(r\a)\over{1+\mu}}\times {n_{\rm b}\over n_{\rm s}}
-      \left[{L_{\rm sys}(M\a, q) \over L(M\a)}\right]^{3/2}
+    \left[{L_{\rm tot}(M\a, q) \over L(M\a)}\right]^{3/2}
     f(q)\,\mathrm{d}q,
-  \end{equation}
-  where
-  \begin{equation}
-      \mu({\rm BF},M\a)= 
+    \label{eq:N_binaries}
+\end{equation}
+where $\mu$ is given by
+\begin{equation}
+    \mu= 
     %\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
-      \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L_{\rm sys}(M\a, q)
+    \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L_{\rm tot}(M\a, q)
     \over L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
@@
 \end{equation}
-  These should replace ${\mu N_\star(r\a)/(1+\mu)}$ in Equations
-  \ref{eq:n0}--\ref{eq:n2}. Then the result needs to be integrated
-  over $q$.
+Binaries with larger mass ratios are overrepresented by a factor of
+$\left[{L_{\rm tot}(M\a, q)/L(M\a)}\right]^{3/2}$ because the
+sample of searchable binaries is magnitude-limited.  To obtain
+the number of binary systems searched at each $(r\a,M\a)$ pair,
+Equation~\ref{eq:N_binaries} needs to be integrated over $q$.  It
+can then replace ${\mu N_\star(r\a)/(1+\mu)}$ in
+Equations~\ref{eq:n1} and~\ref{eq:n2}.
+
+\item The apparent radius of a planet in a binary system now depends
+on whether the host star is the primary or the secondary. When the host
+is the primary, we write
+$r=\mathcal{D}_1 r\a$, where
+\begin{equation}
+    \mathcal{D}_1
+    = \left( \frac{ L_{\rm tot}(M\a, q)}{ L(M\a) } \right)^{1/2}.
+    \label{eq:dil_1}
+\end{equation}
+When the host is the secondary, $r=\mathcal{D}_2 r\a$, and the
+ratio between the assumed and true stellar radii must be included:
+\begin{equation}
+  \mathcal{D}_2
+  = \frac{R(qM\a)}{R(M\a)}
+    \left( \frac{L_{\rm tot}(M\a, q)}{L(qM\a)} \right)^{1/2}.
+  \label{eq:dil_2}
+\end{equation}
+
+\item Since the observers assign binaries the properties of the
+primary, the transit probability for planets orbiting secondaries is
+over-estimated. At a fixed orbital period, this changes
+$p_{\rm tra}$ in Equation~\ref{eq:n2} by a factor of
+\begin{equation}
+  {R(qM\a) \over R(M\a)}q^{-1/3}.
+\end{equation}
+
+\end{enumerate}
+
+Taking these modifications into account, a general formula for the
+apparent rate density follows:
+\begin{align}
+    \notag
+    \Gamma\a(r\a,M\a) &= \frac{1}{1+\mu} \cdot
+    \left\{ \Gamma_0(r\a, M\a)+ 
+    \frac{n\b}{n\s}
+    \left[ \int_0^1 \mathrm{d}q \,
+           \mathcal{D}_1^3 f(q)\cdot
+           \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a, M\a)\,
+    \right.   
+    \right. \\
+    & \quad\quad\quad\quad\quad \left.\left.
+    +\int_0^1 {\rm d}q\, 
+         \mathcal{D}_1^3 f(q)\cdot q \mathcal{D}_2
+         \Gamma_2(\mathcal{D}_2r\a, qM\a)\cdot
+         \frac{R(qM\a)}{R(M\a)} q^{-1/3}
+    \right] \right\}.
+    \label{eq:general_Gamma_a}
+\end{align}
+We give an alternative derivation in the
+\hyperref[sec:appendix]{Appendix}.
+With the definition of $\mu$ in Equation~\ref{eq:mu_general},
+Equation~\ref{eq:general_Gamma_a} can also be expressed as
+\begin{align}
+    \notag
+    \notag
+    \Gamma\a(r\a,M\a)
+    &= 
+    {1\over 1+\mu} \cdot
+    \left[
+       \Gamma_0(r\a, M\a)\phantom{\tilde \Gamma}\right.&\\
+       &\left.+\mu\cdot
+       \left\langle
+       \mathcal{D}_1\cdot\Gamma_1\left(\mathcal{D}_1r\a, M\a\right)
+       +
+       {q \mathcal{D}_2}\cdot\Gamma_2\left(\mathcal{D}_2r\a,
+       qM\a\right) \cdot {R(qM\a) \over R(M\a)}q^{-1/3}
+       \right\rangle
+    \right],
+\end{align}
+where the angle brackets denote averaging over $\mathcal{D}_1^3f(q)$.
+Summarized, the apparent rate density is a weighted sum of the rate
+densities from singles, primaries, and secondaries.  The weights are
+determined by the fraction $\mu$ and mass ratio distribution
+$\mathcal{D}_1^3f(q)$ of binaries {\it in the searchable volume}.  The
+fraction $\mu$ gives the relative contributions from singles and
+binaries, and $\mathcal{D}_1^3 f(q)$ applies a Malmquist bias for
+binaries that are brighter.  A final correction for secondaries
+accounts for the overestimated transit probability.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Realistic Star and Planet Distributions}
+\label{sec:more_complicated}
+
+We will now apply our general equation for the apparent rate density
+(Equation~\ref{eq:general_Gamma_a}) to study the impact of
+unrecognized binaries in regimes of observational interest.  In the
+following, we write the rate density for each type of star,
+$\Gamma_i(r)$, as the product of a shape function, normalized to
+unity, and a constant:
+\begin{equation}
+    \Gamma_i(r) = Z_i f_i(r), \quad {\rm for\ }i\in\{0,1,2\},
+\end{equation}
+where the respective indices correspond to single stars, primaries of
+binaries, and secondaries of binaries.  The normalizations $Z_i$ are
+each system type's occurrence rate $\Lambda_i$, integrated over all
+planetary radii. In other words, they are number of planets per
+single, primary, or secondary star.  Our main interest is in
+varying the radius shape function and the relative values of the
+integrated occurrence rates. We will also briefly mention shape
+functions in stellar mass.  For analytic simplicity, we will assume
+throughout this section that stars are a one-parameter family, given
+by $L \propto M^\alpha \propto R^\alpha$.  Applying these power laws
+to Equations~\ref{eq:dil_1} and~\ref{eq:dil_2}, we find
+\begin{equation}
+  \mathcal{D}_1
+  =  (1+q^\alpha)^{1/2}~~{\rm and}~~\mathcal{D}_2
+  = q(1+q^{-\alpha})^{1/2}
+\end{equation}
+for the radius dilution prefactors.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Power law planet radius distribution}
+\label{sec:model_2}
+
+\subsubsection{Twin binaries}
+As a first step, we return to the case where all binaries are twins.
+However, we now let the planet radius distribution be a power law,
+\begin{equation}
+    \Gamma_i(r) = Z_i f(r) = Z_i r^\gamma/\mathcal{N}_r,
+\end{equation}
+for $\mathcal{N}_r$ the shape function's normalization.  Applying
+Equation~\ref{eq:general_Gamma_a} gives the resulting apparent rate
+density,
+\begin{equation}
+    \Gamma\a(r\a) = \frac{r\a^{\gamma}}{\mathcal{N}_r} \left[
+    \frac{Z_0}{1+\mu}
+    +
+    2^{\frac{\gamma+1}{2} } \frac{\mu}{1+\mu} \left(Z_1 + Z_2
+    \right)
+    \right].
+    \label{eq:model5_apparent_rate_density}
+\end{equation}
+Under these assumptions, twin binaries simply shift the apparent
+radius distribution: $\Gamma\a(r\a) \propto r\a^\gamma$.  As in
+Section~\ref{sec:model_1}, $\mu = 2^{3/2} n\b/n\s$.  If planet
+occurrence is independent of system multiplicity, the ``correction
+factor'' relative to the rate density for singles is
+\begin{align}
+    \frac{\left. \Gamma\a(r\a)\right|_{r\a= r}}{\Gamma_0(r)} 
+    &=
+    \frac{1 + 2^{\frac{\gamma+3}{2}}\mu}{1 + \mu}.
+    \label{eq:power_law_correction}
+\end{align}
+For a binary fraction of $0.1$, $\mu\approx 0.15$. Taking
+$\gamma=-2.92$ from \citet{howard_planet_2012},  we find that the
+apparent rate density is a mere 0.4\% larger than the rate density of
+single stars.
+%relative difference $\Delta \Gamma_0 = |\Gamma_0~-~\Gamma\a|/\Gamma_0$
+Fortuitously, the exponent of the radius distribution is close to
+$-3$, and the errors from neglecting binaries almost entirely
+cancel out.
+
+The above estimate cannot apply at small radii, since the shape
+function diverges. \citet{howard_planet_2012}'s results indicate that
+a single power law fits the planet radius distribution for radii
+greater than $2r_\oplus$.  Similarly, there should be an upper radius
+limit, $r_{\rm u}$, to the radius distribution, perhaps around
+$24r_\oplus$ based on the most inflated hot Jupiters.  Imposing an
+upper cut-off of $r_{\rm u}$ would lead to smaller values of the
+apparent rate density down to $r_{\rm u}/\sqrt{2}$, compared to a
+power law without the cut-off.  We are not particularly interested in
+this effect because hot Jupiter occurrence rates are poorly described
+by a power law (see Section~\ref{sec:further_models}).  All told, if
+our assumptions are applicable to real transit surveys,
+Equation~\ref{eq:power_law_correction} suggests that for apparent
+radii from $2r_\oplus$~to~$17r_\oplus$, unrecognized binaries are a
+minor source of systematic error.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Binaries with power law mass ratio distribution}
+\label{sub:powerlaw_varying_binaries}
 
@@
         magnitude-limited. For this figure, we assume $L\propto
-          M^{3.5}$
+        M^{3.5}$.
     }
@@
 
-  As we showed earlier, this can be understood as a Malmquist bias: in
-  the magnitude-limited sample of searchable binaries, those with
-  larger mass ratios are overrepresented by a factor or
-  $\left[{L_{\rm sys}(M\a, q)/L(M\a)}\right]^{3/2}$ because they are
-  brighter. We show this magnitude-limited mass ratio distribution
-  for the flat $f(q)$ in Figure~\ref{fig:q_distribn_mag_limited}.  In
-  Monte Carlo simulations of transit surveys, it is important to
-  draw binaries from an appropriately biased mass-ratio
-  distribution~\citep[\textit{e.g.},][]{
-    bakos_hatsouth:_2013,sullivan_transiting_2015,
-    gunther_new_2017}.
-%
-  \item The relationship between $r\a$ and $r$ are different.  From
-    Equation~\ref{eq:delta_obs_general}, $r=\mathcal{D}_{1/2}r\a$ for
-    primaries and secondaries, where
-  \begin{equation}
-      \mathcal{D}_1(q, M\a)
-      = \sqrt{L_{\rm sys}(M\a, q) \over L(M\a) }
-      = (1+q^\alpha)^{1/2},
-  \end{equation}
-  and
-  \begin{equation}
-    \mathcal{D}_2(q, M\a)
-    = {R(qM\a)\over R(M\a)}\sqrt{L_{\rm sys}(M\a, q) \over L(qM\a)} 
-    = q (1+q^{-\alpha})^{1/2}.
-  \end{equation}
-  So $\sqrt{2}r\a$ in Equations~\ref{eq:n1} and~\ref{eq:n2} needs to be
-  replaced with $\mathcal{D}_1r\a$ and $\mathcal{D}_2r\a$, respectively.
-
-  \item The transit probability around secondaries are smaller than
-  that around primaries, the latter of which is the same as
-  primaries under our assumption. At a fixed orbital period, this
-  changes $p_{\rm tra}$ in Equation~\ref{eq:n2} by a factor of
-  \begin{equation}
-    {R(qM\a) \over R(M\a)}q^{-1/3}.
-  \end{equation}
-
-\end{enumerate}
-
-Taking these modifications into account, a general formula for the
-apparent rate density follows:
-\begin{align}
-    \notag
-    \Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
-    \left\{ \Gamma_0(r\a, M\a)+ 
-    \frac{n\b}{n\s}
-    \left[ \int_0^1 \mathrm{d}q \,
-           \mathcal{D}_1^3 f(q)\cdot
-          \mathcal{D}_1 \Gamma_1\left(\mathcal{D}_1r\a,
-    M\a\right)\,
-    \right.   
-    \right. \\
-    & \quad\quad\quad\quad\quad \left.\left.
-    +\int_0^1 {\rm d}q\, 
-         \mathcal{D}_1^3 f(q)\cdot \mathcal{D}_2 q
-        \Gamma_2\left(\mathcal{D}_2r\a, qM\a\right)\cdot
-    {R(qM\a) \over R(M\a)}
-    q^{-1/3} \right] \right\}.
-    \label{eq:general_Gamma_a}
-\end{align}
-We also give a more formal derivation in the
-\hyperref[sec:appendix]{Appendix}.
-With the definition of $\mu$ in Equation~\ref{eq:mu_general},
-Equation~\ref{eq:general_Gamma_a} can also be expressed as
-\begin{align}
-    \notag
-    \notag
-    \Gamma\a(r\a,M\a)
-    &= 
-    {1\over 1+\mu(\mathrm{BF}, M\a)} \cdot
-    \left[
-       \Gamma_0(r\a, M\a)\phantom{\tilde \Gamma}\right.&\\
-       &\left.+\mu(\mathrm{BF}, M\a)\cdot
-       \left\langle
-       \mathcal{D}_1\cdot\Gamma_1\left(\mathcal{D}_1r\a, M\a\right)
-       +
-       {q \mathcal{D}_2}\cdot\Gamma_2\left(\mathcal{D}_2r\a,
-       qM\a\right) \cdot {R(qM\a) \over R(M\a)}q^{-1/3}
-       \right\rangle
-    \right],
-\end{align}
-where the angle brackets denote averaging over $\mathcal{D}_1^3f(q)$.
-This form shows that the fraction $\mu$ and mass ratio distribution
-$\mathcal{D}_1^3f(q)$ of binaries {\it in the searchable volume} are
-enough to describe the contributions from binaries to $\Gamma\a$.  The
-fraction $\mu$ gives the relative contributions from singles and
-binaries, and $\mathcal{D}_1^3 f(q)$ weights the contributions from
-binaries with various mass ratios.  The apparent rate density at each
-mass ratio ({\it i.e.}, the terms in the angle brackets) is the rate
-density of systems that give the apparent $(r\a, M\a)$, corrected for
-the overestimated transit probability around secondaries.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Realistic Star and Planet Distributions}
-\label{sec:more_complicated}
-
-We will now apply our general equation for the apparent rate density
-(Equation~\ref{eq:general_Gamma_a}) to study binarity's effects in
-regimes of observational interest.  In the following, we write the
-rate density for each type of star, $\Gamma_i(r)$, as the product of a
-shape function, normalized to unity, and a constant:
-\begin{equation}
-    \Gamma_i(r) = Z_i f_i(r), \quad {\rm for\ }i\in\{0,1,2\},
-\end{equation}
-where $i=0$ corresponds to single stars, $i=1$ to primaries of
-binaries, and $i=2$ to secondaries of binaries.
-The $Z_i$'s are each system type's occurrence
-rate $\Lambda_i$, integrated over all planetary radii. In other words,
-they are number of planets per single, primary, or secondary star.
-While our main interest is in varying the radius shape function
-and the relative values of integrated occurrence rates, we 
-will also briefly discuss shape functions in stellar mass.
-To keep things analytically simple, we will assume throughout this
-section that stars are a one-parameter family, given by 
-$L \propto M^\alpha \propto R^\alpha$, so that a given value 
-of $q$ determines everything about a secondary.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Power law planet radius distributions}
-\label{sec:model_2}
-
-\subsubsection{Twin binaries}
-As a first step, we keep all binaries as twins, but
-let the planet radius distribution vary.  If we take a
-power law planet radius distribution,
-\begin{equation}
-    \Gamma_i(r) = Z_i f(r) = Z_i r^\delta/\mathcal{N}_r,
-\end{equation}
-for $\mathcal{N}_r$ the shape function's normalization, then
-Equation~\ref{eq:general_Gamma_a} gives the resulting apparent rate density,
-\begin{equation}
-    \Gamma\a(r\a) = \frac{r\a^\delta}{\mathcal{N}_r} \left[
-    \frac{Z_0}{1+\mu}
-    +
-    2^{\frac{\delta+1}{2} } \frac{\mu}{1+\mu} \left(Z_1 + Z_2
-    \right)
-    \right].
-    \label{eq:model5_apparent_rate_density}
-\end{equation}
-This is similar to the twin binary, fixed-planet case
-(Equation~\ref{eq:model_1_apparent_rate_density}), except for the
-radius dependence and normalization.  As in Section~\ref{sec:model_1},
-$\mu = 2^{3/2} n\b/n\s$.  If the $Z_i$'s are equal, the ``correction
-factor'' relative to the rate density for singles becomes simple:
-\begin{align}
-    \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
-    \right|_{r\a\rightarrow r}
-    &=
-    \frac{1 + 2^{\frac{\delta+3}{2}}\mu}{1 + \mu}.
-    \label{eq:power_law_correction}
-\end{align}
-If the binary fraction is $0.1$, $\mu\approx 0.15$. Taking
-$\delta=-2.92$ from \citet{howard_planet_2012},  we find
-$\Gamma\a/\Gamma_0 = 1.004$.  In other words, the apparent rate
-density is an {\it over}estimate compared to the rate density of
-single stars, with a relative difference $\delta \Gamma_0 =
-|\Gamma_0~-~\Gamma\a|/\Gamma_0$ of 0.4\%.  This is quite a small
-effect!  Clearly though, it cannot apply at small radii, since $f(r)
-\propto r^\delta$ diverges; \citet{howard_planet_2012}'s results
-indicate that the power law planet radius distribution holds for
-$r\a\gtrsim 2r_\oplus$.  It is similarly nonsensical for $f(r)$ to be
-finite above some upper radius limit $r_{\rm u}$, perhaps around
-$\approx 24r_\oplus$, based on the most inflated hot Jupiters.
-Imposing an upper cut-off of $r_{\rm u}$ would lead to smaller values
-of $\Gamma(r\a)$ down to $r_{\rm u}/\sqrt{2}$, compared to an
-intrinsic power law without the cut-off.  We are not particularly
-interested in this effect because there are better models for hot
-Jupiter occurrence rates that we will discuss in
-Section~\ref{sec:further_models}.  If the assumptions behind this
-model are at all applicable to real transit surveys,
-Equation~\ref{eq:power_law_correction} suggests that for $2r_\oplus
-\lesssim r\a \lesssim 17r_\oplus$, binarity's impact on apparent
-occurrence rates is quite small.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Binaries with power law mass ratio distribution}
-\label{sub:powerlaw_varying_binaries}
-
 To check whether non-twin binaries change the preceding result, we now
-assume $f(q) = q^\beta/\mathcal{N}_q$, for $\mathcal{N}_q$ the
-normalization.
-This changes $\mu$: taking the volume-limited binary mass ratio
-distribution to be $f(q) \propto q^\beta$, Equation~\ref{eq:mu_general} 
-simplifies to
+consider a distribution of binary mass ratios.  Specifically, we take
+$f(q) = q^\beta/\mathcal{N}_q$, for $\mathcal{N}_q$ the normalization.
+This changes $\mu$ from the twin binary case;
+Equation~\ref{eq:mu_general} simplifies to
 \begin{equation}
@@
 \end{equation}
- The rate density might now also vary with 
-host star mass.  We can absorb this dependence into a power
-law,
-\begin{equation}
-    \Gamma_i(r,M) = Z_i \times \frac{r^\delta}{\mathcal{N}_r} \times
-    \frac{M^\gamma}{\mathcal{N}_M},
+For the $\beta=0$ case, this equation means there will be more
+twin-like binaries than faint binaries in the sample of stars
+that are searched at any transit depth
+(Figure~\ref{fig:q_distribn_mag_limited}).
+
+The rate density now varies not only with planet radius, but also
+host star mass.  We can absorb this dependence into a power law,
+\begin{equation}
+    \Gamma_i(r,M) = Z_i \times \frac{r^\gamma}{\mathcal{N}_r} \times
+    \frac{M^\zeta}{\mathcal{N}_M},
 \end{equation}
 where $Z_i$ is dimensionless, and the normalization constants carry
-the units (each side has units $[r^{-1} M^{-1}]$).
-
-We are mostly interested in the apparent rate density's radius
+the units.% (each side has units $[r^{-1} M^{-1}]$).
+
+Our main interest is in the apparent rate density's radius
 dependence.  Marginalizing Equation~\ref{eq:general_Gamma_a} over
@@
 \begin{align}
+    %see annoying_q_factor_dec22.pdf for derivation
     \notag
-    \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
-    \right|_{r\a\rightarrow r}
+    \frac{\left.\Gamma\a(r\a)\right|_{r\a= r}}{\Gamma_0(r)} 
     &=
     \frac{1}{1+\mu}
-    \left[1 + \frac{1}{\mathcal{N}_q} \frac{n\b}{n\s}\times 
+    \left[
+      1 + \frac{1}{\mathcal{N}_q} \frac{n\b}{n\s}\times 
     \left(
-    \int_0^1 {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}} +
+      \int_0^1 {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\gamma+4}{2}} +
       \right.
@@
       \left.\left.
-    \int_0^1 {\rm d}q\,q^{\beta+\delta+\frac{5}{3}} 
+      \int_0^1 {\rm d}q\,q^{\beta+\gamma+\frac{5}{3}} 
       (1+q^\alpha)^{\frac{3}{2}}
-    (1+q^{-\alpha})^{\frac{\delta+1}{2}}
-    \right)\right],
+      (1+q^{-\alpha})^{\frac{\gamma+1}{2}}
+    \right)
+    \right],
     \label{eq:powerlaw_vary_binary}
 \end{align}
-where $\gamma$ does not appear because of the marginalization over
-$M\a$.  For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the
+where $\zeta$ does not appear because of the marginalization over
+$M\a$.  For $\alpha = 3.5$, $\beta=0$, $\gamma=-2.92$, the
 summed integrals in Equation~\ref{eq:powerlaw_vary_binary} give
 $(\ldots)\approx 1.503$. %171211_model_integrals.nb
-For $n\b / (n\b + n\s)=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$;
-the relative difference between the apparent rate density and the rate
-density around singles is 4.8\%.  This indicates that considering only
-twin binaries gave us correct intuition: for a power law radius
-distribution ($2r_\oplus \lesssim r\a \lesssim 17r_\oplus$) in which
-there are the same number of planets orbiting singles, primaries, and
-secondaries, binarity influences apparent planet occurrence rates
-around Sun-like stars at the few percent level.
+For $n\b / (n\b + n\s)=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$.
+The apparent rate density is 4.8\% larger than the rate density around
+singles.  Considering only twin binaries gave us good intuition: for
+apparent radii from $2r_\oplus$ to $17r_\oplus$, binarity influences
+apparent planet occurrence rates around Sun-like stars at the level of
+a few percent.
 
@@
 Though the details of the planet radius distribution $\Gamma_i(r)$ at
-$r<2r_\oplus$ are currently an active topic of research, we can
-investigate how binarity affects this regime by making plausible
-assumptions.  For instance, we can assume a broken power-law:
+$r<2r_\oplus$ are currently an active topic of research, by making
+plausible assumptions we can investigate how neglecting binarity might
+bias measurements in this regime.  For instance, consider a broken
+power-law:
 \begin{align}
@@
     \begin{cases}
-        r^\delta & \text{for } r\geq 2r_\oplus \\
+        r^\gamma & \text{for } r\geq 2r_\oplus \\
         {\rm constant} & \text{for } r\leq2r_\oplus.
@@
 \end{align}
-Our ``nominal model'' remains the same:
-$L\propto M^\alpha \propto R^\alpha$, and
-$\alpha=3.5$, $\beta=\gamma=0$, $\delta=-2.92$.
-
 At apparent radii $r\a > 2r_\oplus$, the apparent rate density in
-this model is the same as from
-Section~\ref{sub:powerlaw_varying_binaries}.  For
-$r\a < 2r_\oplus$, the equations are tedious, but still tractable.
+this model is the same as that in
+Section~\ref{sub:powerlaw_varying_binaries}.  At smaller apparaent
+radii the equations are tedious, but still tractable.
 For simplicity, we insert Equation~\ref{eq:model3_radius_distribution}
@@
 implementation\footnote{\url{https://github.com/lgbouma/binary_biases}}.
-The output is validated against analytic predictions in the $r\a >
-2r_\oplus$ and the $r\a < 2r_\oplus/\sqrt{2}$ regimes, and is plotted
-in Figure~\ref{fig:occ_rate_model_3_log}.
+As before, $L\propto M^\alpha \propto R^\alpha$, and $\alpha=3.5$,
+$\beta=0$, $\gamma=-2.92$.  The output, shown in
+Figure~\ref{fig:occ_rate_model_3_log}, is validated using analytic
+predictions in the $r\a > 2r_\oplus$ and the $r\a <
+2r_\oplus/\sqrt{2}$ regimes.
 
 \paragraph{The rate of Earth analogs} The immediately arresting result
-there is a ``bump'' in the apparent rate density at $r\a < 2r_\oplus$:
-the true rate for singles is less than the inferred rate.  For the
-case in which secondaries host as many (half as many) planets as
-single stars, this means an overestimate of the occurrence
-rate by $\approx 50\%$ ($\approx 25\%$).  The ``bump'' exists even for
-the $Z_2/Z_0=0$ case as a $\approx 10\%$ effect.  The magnitude of
-this error evidently depends strongly on the prevalence of planets
-around secondaries.
-
-\paragraph{Hot Jupiter occurrence rates} Taking
-Figure~\ref{fig:occ_rate_model_3_log} and integrating the rate
-density, we can compare the apparent hot Jupiter occurrence rate with
-the true rate for singles.  In the most extreme case of $Z_2/Z_0=0$,
-we find that $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 1.13$, where
+is a ``bump'' in the apparent rate density at apparent radii below
+$2r_\oplus$: the true rate for singles is less than the apparent rate.
+If secondaries host as many planets as single stars, the occurrence of
+these small planets is overestimated by $\approx 50\%$.  The magnitude
+of the systematic error decreases if there are fewer planets around
+secondaries; if secondaries host no planets at all, the apparent rate
+is overestimated by only $\approx 10\%$.
+
+\paragraph{Hot Jupiter occurrence rates}
+By integrating the rate density from
+Figure~\ref{fig:occ_rate_model_3_log}, we can compare the apparent hot
+Jupiter occurrence rate with the true rate for singles.  The
+difference between the rates is largest when secondaries host no
+planets. In that case, we find $\Lambda_{{\rm HJ},0}/\Lambda_{\rm
+HJ,a} = 1.13$, where
 \begin{equation}
     \Lambda_{\rm HJ,a} =
-      \int_{8r_\oplus}^{\infty} \Gamma\a(r\a)\,{\rm d}r\a,
-\end{equation}
-and similarly for $\Lambda_{\rm HJ,0}$.
+      \int_{8r_\oplus}^{\infty} \Gamma\a(r\a)\,{\rm d}r\a,~~{\rm
+      and}~~
+    \Lambda_{\rm HJ,0} =
+      \int_{8r_\oplus}^{\infty} \Gamma_0(r)\,{\rm d}r.
+\end{equation}
 %occ_rate_vs_radius_model_3_withtext_Zsub2_0.00_rpu_22.5.pdf
-If $Z_2/Z_0>0$, binarity affects the apparent hot Jupiter rate less:
-when $Z_2/Z_0=0.5$, we find $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} =
-1.06$.  We discuss this issue further in
+If secondaries host half as many planets as single stars, then
+$\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 1.06$.  We pay further
+attention to the issue of hot Jupiter occurrence rates in
 Section~\ref{sec:further_models}.
@@
         Fraction of detected planets at a given apparent planet radius
-        coming from singles (solid lines), primaries (dashed lines),
-        and secondaries (dotted lines).  Three different values for
-        $Z_2/Z_0$ are selected: $1$ (blue), $0.5$ (orange), $0$
-        (green).  The assumed true planet radius distribution is a
-        broken power law
-        (Equation~\ref{eq:model3_radius_distribution}; same as
-        Figure~\ref{fig:occ_rate_model_3_log}).
+        that orbit single stars (solid lines), primaries of binaries
+        (dashed lines), and secondaries of binaries (dotted lines).
+        We assume that single stars and primaries have the same number
+        of planets per star, and that the true planet radius
+        distribution is a broken power law
+        (same as Figure~\ref{fig:occ_rate_model_3_log}).
     }
@@
 
-It would be nice to improve our intuition for how much the secondaries
-matter.  We have the understanding that for a given true planet
-radius, secondaries have a much smaller searchable volume than
-primaries or singles.  Does this necessarily imply that if we are
-given a detected planet with some apparent radius $r\a$, which is then
-observed by high-resolution imaging to exist in a binary, that the
-planet probably orbits the primary?
-
-We explore this quantitatively in Figure~\ref{fig:frac_model_3}.  The
-lines in this figure are computed using expressions given in the
-appendix for the number of detections coming from singles, primaries,
-and secondaries (Eqs.~\ref{eq:n_det_0},~\ref{eq:n_det_1},
-and~\ref{eq:n_det_2}).
-
-In short, the detected planet usually is more likely to orbit the
-primary, but this statement depends on the number of planets orbiting
-secondaries, and also on the apparent radius of the detected planet.
-In the scenario that high-resolution imaging finds a system with $r\a
-> 2r_\oplus$ in a binary, roughly $\sim\! 2.5\times$ more detected
-planets orbit primaries than secondaries, for the $Z_2/Z_0=1$ case.
-For the $Z_2/Z_0=0.5$ case, $\sim\! 5\times$ more detected planets
-orbit primaries than secondaries.  So detected planets in binaries
-with large apparent radii (relative to the cutoff in the intrinsic
-rate density) are more likely to orbit the primary.
-
-The situation for $r\a < 2r_\oplus$ is more nuanced.  For the $Z_2=0$
-and $Z_2/Z_0=0.5$ cases, detected planets in binaries are still always
-more likely to orbit the primary.  However, if there are as many
-planets orbiting the secondaries as the primaries, then there is a
-turn-over radius, $\approx 0.4r_\oplus$, beyond which more of the
-detected planets in binaries come from secondaries: they have all been
-``diluted down'' from larger true planetary radii!  Although this
-(apparent) radius is at the limit of current detection sensitivities,
-this effect will be interesting for future instruments to investigate.
-
-Further, Figure~\ref{fig:frac_model_3} shows that going from apparent
-radii of $2r_\oplus$ to $\approx 1.4r_\oplus$, the fraction of
-detected planets with binary companions increases by $\approx 6-12\%$,
-depending on the assumed value of $Z_2/Z_0$. %~\footnote{
+A common situation during transit survey follow-up is for
+high-resolution imaging to reveal multiple stars in a system that
+shows planetary transits.  It is often impossible to rule which star
+hosts the detected planet.  Intuitively, one would expect that the
+primary star would be the more likely host because at fixed
+planet size, planetary transits around secondaries have smaller
+amplitudes (Equations~\ref{eq:dil_1} and~\ref{eq:dil_2} imply
+$\mathcal{D}_2>\mathcal{D}_1$, if $\alpha=3.5$).  However, this
+reasoning is qualitative, and its assumptions might not always
+hold.
+
+Our formalism lets us calculate the relative probability that a
+detected planet orbits a single, primary, or secondary star in a more
+general manner.  To perform the calculation, we use expressions given
+in the appendix for the number of detections coming from each type of
+system (Equations~\ref{eq:n_det_0},~\ref{eq:n_det_1},
+and~\ref{eq:n_det_2}).  We then divide out by the total number of
+detections at each apparent radius.  Figure~\ref{fig:frac_model_3}
+shows the result: if high-resolution imaging reveals a source with
+transits to be a binary system, the detected planet does usually orbit
+the primary.
+
+If the apparent radius of the system is above $2r_\oplus$, and planets
+exist about primaries and secondaries at equal rates, then the planet
+is $\approx\!3$ times more likely to orbit the primary than the
+secondary.  If secondaries host half as many planets as primaries,
+then a detected planet is $\approx\!5$ times more likely to orbit the
+primary.
+
+The situation for apparent radii below $2r_\oplus$ is more nuanced.
+For the two cases in which secondaries host fewer planets than
+primaries, detected planets in binaries are still always more likely
+to orbit the primary.  However, if planets exist at the same rate in
+primaries and secondaries, then there is a turn-over radius,
+$\approx\!0.4r_\oplus$, below which more of the detected planets in
+binaries come from secondaries~--~they have all been ``diluted down''
+from larger true planetary radii!  Rephrased, going from apparent
+radii of $2r_\oplus$ to $1.4r_\oplus$, the fraction of detected
+planets with binary companions increases by anywhere from $6\%$ to
+$12\%$, depending on the relative occurrence of planets about
+primaries and secondaries.  We compare this prediction with recent
+observations in Section~\ref{sec:discussion}.
+%~\footnote{
 %The increase can be derived analytically.  Let the fraction of total
@@
 %check_companion_fractions.py, and LB's notes 2017/12/21.0 }.
-Intuitively speaking, this ``shift'' is a feature of any radius
-distribution that declines at large radii, and flattens below some
-cutoff $r_{\rm c}$.  This is because (for dilution about primaries) at
-apparent radii $r\a < r_{\rm c}/\sqrt{2}$, relatively more planets
-will be ``diluted'' into the given $r\a$, since there are more planets
-in the undiluted distribution from $r\a$ to $\sqrt{2}r\a$.  We compare
-this prediction with recent observations in
-Section~\ref{sec:discussion}.
+%This effect will appear in any radius distribution that declines at
+%large radii, and flattens below some cutoff radius, $r_{\rm c}$.  This
+%is because (for dilution about primaries) at apparent radii $r\a <
+%r_{\rm c}/\sqrt{2}$, relatively more planets will be ``diluted'' into
+%the given $r\a$, since there are more planets in the undiluted
+%distribution from $r\a$ to $\sqrt{2}r\a$.
 
@@
 Equation~\ref{eq:model3_radius_distribution} misses some important
-features reported in state of the art studies of planetary occurrence.
+features revealed by state of the art planet occurrence studies.
 
@@
     \caption{
-        {\it Left:} rate density and {\it right:} rate (over
-        $0.25r_\oplus$ bins) as a function of planet radius in a model
-        with a radius gap
+        {\it Left:} rate density and {\it right:} rate as a function
+        of planet radius in a model with a radius gap
         (Equation~\ref{eq:model4_radius_distribution}).  Other than
@@
     \begin{cases}
-        r^\delta & \text{for } r\geq 2r_\oplus, \\
+        r^\gamma & \text{for } r\geq 2r_\oplus, \\
         0 & \text{for } 1.5r_\oplus < r < 2r_\oplus, \\
@@
 \end{align}
-The resulting true and apparent rates are shown in
-Figure~\ref{fig:model_4}.  If left uncorrected, binarity makes the gap
-appear more shallow, and flattens the step-function edges.  Of course,
-other effects could also ``blur'' the gap in the planet radius
-dimension.  In particular, the valley's period-dependence is almost
-certainly not flat
-\citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.  This
+Figure~\ref{fig:model_4} shows the resulting true and apparent rates.
+If left uncorrected, binarity makes the gap appear more shallow, and
+flattens the step-function edges.  Of course, effects unrelated to
+binarity would also ``blur'' the gap in the planet radius dimension.
+In particular, the valley's period-dependence is almost certainly not
+flat \citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.  This
 means that any study measuring the gap's width or depth while
@@
 
-\paragraph{Alternative models for the HJ distribution}
+\paragraph{The HJ distribution is not a power law}
 
@@
 $\Gamma_i(r) = Z_i f(r)$.  We then compute $\Gamma\a(r\a)$, and plot
-it in Figure~\ref{fig:gaussian_HJ}.  Integrating for $r\a > 8r_\oplus$
-to find hot Jupiter rates, we find the opposite effect as in the power
-law model.  For $Z_2/Z_0>0$, the apparent HJ rate is {\it greater}
-than the true rate for singles.  The effect is maximal when there are
-as many hot Jupiters orbiting secondaries as singles, in which case
-$\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 0.81$.
+it in Figure~\ref{fig:gaussian_HJ}.  Integrating over $r\a >
+8r_\oplus$ to find hot Jupiter rates, we find the opposite effect as
+in the power law model.  If secondaries host any planets at all, the
+apparent HJ rate is {\it greater} than the true rate for singles.  For
+instance, if the hot Jupiter rate about secondaries and singles
+is equal, then $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 0.81$.
 %int_rate_density_vs_radius_model_7_withtext*manyZs.pdf
-For the case when no hot Jupiters orbit secondaries, $\Lambda_{{\rm
-HJ},0} \approx \Lambda_{\rm HJ,a}$ to within one percent.
+%For the case when no hot Jupiters orbit secondaries, $\Lambda_{{\rm
+%HJ},0} \approx \Lambda_{\rm HJ,a}$ to within one percent.
 Qualitatively, the apparent HJ rate is greater than the true rate for
-singles because binary systems can have an extra uncounted star that
-yields hot Jupiter detections.
+singles because binary systems have extra uncounted stars that
+yield hot Jupiter detections.
 
@@
 has yet carefully assessed binarity's importance, or lack thereof.
-Although this study does not resolve the problem, it does suggest the
-approximate scale of the possible errors in a survey-independent
-manner.  The suggestion of Section~\ref{sec:model_2} is that for $r\a
-\gtrsim 2r_\oplus$, binarity can be ignored down to a precision of a
-few percent.  For apparent radii $\lesssim 2r_\oplus$, the picture is
-less forgiving: Section~\ref{sec:model_3} suggests that relative
-differences between apparent rates and true rates around singles could
-easily reach $\sim\! 50\%$.
+This study does not resolve the problem; it only suggests the
+approximate scale of the systematic errors.  Section~\ref{sec:model_2}
+suggests that for apparent radii above $2r_\oplus$, binarity can be
+ignored down to a precision of a few percent.  For apparent radii
+below $2r_\oplus$, the picture is less forgiving:
+Section~\ref{sec:model_3} suggests that the apparent rates around
+single stars could be overestimated by as much as 50\%.
 
 \paragraph{The rate of Earth analogs}
-In line with {\it Kepler}'s primary science goal, the rate of
-Earth-like planets orbiting Sun-like stars has been independently
-measured by
-\citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
-foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
-These efforts found that the one-year terrestrial planet occurrence
-rate is between $\approx\! 0.03$ and $\approx\!1$ per Sun-like star,
-depending on assumptions that are made when calculating the
-rate~\citep[see][Figure~17]{burke_terrestrial_2015}.  In
-Section~\ref{sec:model_3}, our power law model indicates that when
-primaries, singles, and secondaries host the same number of planets,
-the apparent rate is 50\% higher than the true rate around single
-stars.  Though this bias seems large, it is currently smaller than the
-other systematic factors that dominate the dispersion in $\eta_\oplus$
-measurements.  If future analyses determine absolute values of
-$\eta_\oplus$ to better than a factor of two, binarity will likely
-merit closer attention.
-
-One caveat to our assessment of binarity's relevance for $\eta_\oplus$
-measurements is that none of our models included the rate density's
+\citet{youdin_exoplanet_2011},~\citet{petigura_prevalence_2013},~\citet{dong_fast_2013},~\citet{foreman-mackey_exoplanet_2014},
+and~\citet{burke_terrestrial_2015} have found that between $0.03$ and
+$1$ Earth-like planets exist per Sun-like star, depending on
+assumptions that are made when calculating the
+rate~\citep[see][Figure~17]{burke_terrestrial_2015}.  Assuming a
+broken power-law, we showed that unrecognized binaries could cause
+overestimates in the rate of Earth analogs of up to 50\%.  This
+systematic effect is smaller than the other factors that currently
+dominate the dispersion in $\eta_\oplus$ measurements.  If future
+analyses determine absolute values of $\eta_\oplus$ to better than a
+factor of two, binarity will likely merit closer attention.
+
+One caveat is that none of our models included the rate density's
 period-dependence. However, binaries with separations $\lesssim
@@
 \paragraph{Hot Jupiter rate discrepancy}
-While binarity may appreciably affect $\eta_\oplus$ measurements, our
-analysis suggests that it is unlikely to influence the hot Jupiter
-rate discrepancy.  The context of this disagreement is that hot
-Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$)
-are marginally lower than those found by radial velocity surveys
-($\approx 1\%$; see Table~\ref{tab:hj_rates}).  Though the discrepancy
-has weak statistical significance ($<3\sigma$), one reason to expect a
-difference is that the corresponding stellar populations have distinct
-metallicities.  As argued by \citet{gould_frequency_2006}, the RV
-sample is biased towards metal-rich stars, which have been measured by
-RV surveys to preferentially host more giant
-planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005}.
+While unresolved binaries may bias $\eta_\oplus$ measurements, our
+approach suggests that they do not influence the hot Jupiter rate
+discrepancy.  The ``discrepancy'' is that hot Jupiter occurrence rates
+measured by transit surveys ($\approx 0.5\%$) are lower than those
+found by radial velocity surveys ($\approx 1\%$; see
+Table~\ref{tab:hj_rates}).
+
+Though the disagreement is only weakly significant ($<3\sigma$), one
+reason to expect a difference is that the RV sample is biased towards
+metal-rich stars, which host more giant
+planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005,gould_frequency_2006}.
 Investigating the discrepancy from the metallicty
@@
 M/H}]_{\rm CPS}= -0.005\pm0.006$.  The former value agrees with that
-measured by \citet{dong_metallicities_2014}.  Refitting for the
+found by \citet{dong_metallicities_2014}.  Refitting for the
 metallicity exponent in $\Lambda_{\rm HJ} \propto 10^{\beta [{\rm
 M/H}] }$, \citeauthor{guo_metallicity_2017}\! found $\beta = 2.1\pm
-0.7$, and noted that this would imply that the metallicity difference
-could account for a $\approx 20\%$ relative difference in the measured
-rates between the CKS and {\it Kepler}\ samples~--~not a 50\% relative
-difference\footnote{ \citet{petigura_CKS_2017} recently found $\beta =
-3.4^{0.9}_{-0.8}$.  This gives a $\approx 25\%$ relative difference,
-indicating metallicity could account for about half of the ``hot
-Jupiter rate discrepancy''.  }.  \citeauthor{guo_metallicity_2017}\!
-concluded that ``other factors, such as binary contamination and
-imperfect stellar properties'' must also be at play.
-
-Binarity might affect the inferred occurrence rates because 
-radial velocity and transit surveys treat binaries differently.
-Radial velocity surveys typically reject both visual and spectroscopic
-binaries \citep{wright_frequency_2012}.  Transit
-surveys observe binaries, but the question of whether they were
-searchable to begin with is left for later interpretation.  In
-spectroscopic follow-up of transiting planet candidates, the
-prevalence of astrophysical false-positives may also lead to a
-tendency against confirming transiting planets in binary systems.  A
-separate observational bias is that the RV surveys typically observe
-chromospherically ``quiet'' stars, which may bias their detection
-probability high~\citep{bastien_radial_2014}.
-
-Ignoring these complications, we concentrated in this work on
-binarity's effects on star counts and the apparent radii of detected
-planets.  Assuming a power law radius distribution, and that no
-secondaries host HJs, we found in Section~\ref{sec:model_3} that
-binarity could lead to underestimated HJ rates relative to singles by
-a multiplicative factor of $\approx 1.13$.  We then pointed out in
-Section~\ref{sec:further_models} that assuming a power law radius
-distribution is probably wrong if one wishes to study the HJ rate
-discrepancy.  If we instead assume a Gaussian radius
-distribution~\citep[following][]{petigura_CKS_2017}, apparent HJ rates
-are {\it greater} than the true rate around singles: the effect goes
-the wrong way.
+0.7$, and noted that the metallicity difference could account for
+0.2\% of the needed 0.5\% difference between the measured CKS
+and {\it Kepler}\ rates\footnote{ \citet{petigura_CKS_2017} recently
+found $\beta = 3.4^{0.9}_{-0.8}$.  If true, this implies that
+metallicity could account for about half of the ``hot Jupiter rate
+discrepancy''.  }.  \citeauthor{guo_metallicity_2017}\!  concluded
+that ``other factors, such as binary contamination and imperfect
+stellar properties'' must also be at play.
+
+Radial velocity surveys usually reject visual and spectroscopic
+binaries~\citep{wright_frequency_2012}, so their hot Jupiter rates are
+closer to the rate for single stars than the rates reported by transit
+surveys.  However, we found in Section~\ref{sec:further_models} that
+when assuming a Gaussian radius distribution, apparent hot Jupiter
+rates are {\it greater} than the true rate around singles: the effect
+goes the wrong way.  There could be other systematic factors behind
+the difference~--~but they are unlikely to be related to binarity.
+
+%in spectroscopic follow-up of transiting planet candidates, the
+%prevalence of astrophysical false-positives may also lead to a
+%tendency against confirming transiting planets in binary systems.  A
+%separate observational bias is that the RV surveys typically observe
+%chromospherically ``quiet'' stars, which may bias their detection
+%probability high~\citep{bastien_radial_2014}.
+
 \begin{comment}
@@
 \end{comment}
-The ``hot Jupiter island'' reported by~\citet{petigura_CKS_2017}
-cannot possibly be part of a continuous power law.  Thus binarity is
-unlikely to resolve the HJ rate discrepancy.
+
+\paragraph{Does a detected planet orbit the primary or secondary?}
+
+A separate reason to address stellar multiplicity in transit surveys
+is that it can radically alter the interpretation of planet candidates
+on a system-by-system level.  To identify and correct for unseen
+stellar companions, high-resolution imaging campaigns have surveyed
+almost all {\it Kepler}\ Objects of Interest~\citep{
+  howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
+  horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
+  law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
+  wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016,ziegler_robo-ao_2017}.
+The results of these programs have been summarized
+by~\citet{furlan_kepler_2017}, and they represent an important advance
+in understanding the KOI sample's multiplicity statistics.
+
+An immediate application is to reassess the radii of detected planets.
+Doing so, \citet{hirsch_assessing_2017} recently found that for their
+sample of KOIs in binaries, the planet radii are underestimated by
+factors $r/r\a = 1.17$ if all planets orbit primaries, and $r/r\a =
+1.65$ if detected planets are equally likely to orbit primaries and
+singles.  This approach makes minimal assumptions about the likelihood
+that a planet orbits the primary vs.~the secondary
+(though~\citealt{hirsch_assessing_2017} do also consider weighting
+radius corrections by planet occurrence).
+
+Our approach provides a suggestion of how to assess the probability
+that a detected planet in a binary system orbits either component.
+The problem requires assuming both the underlying radius distribution,
+and the relative number of planets per primary and secondary star.  We
+found that for a broken power law radius distribution, with equal
+occurrence rates about primaries and secondaries, detected planets in
+binary systems are usually more likely to orbit the primary
+(Figure~\ref{fig:frac_model_3}).  For apparent radii greater than
+$2r_\oplus$, the odds of primary:secondary are 8:3.  The odds increase
+for the planet to orbit the secondary increase at smaller apparent
+radii, and reach 1:1 at $r\a=0.4r_\oplus$.  For {\it Kepler}, this
+suggests that for almost all confirmed KOIs in multiple star systems,
+the planet most likely orbits the primary.
+
+\paragraph{Fraction of detected planets with binary companions}
+A related effect is that some detected planets are more likely to be
+in binary systems than others.  Notably,
+Figure~\ref{fig:frac_model_3} predicts that the fraction of detected
+planets with binary companions should increase by $\approx 6-12\%$
+going from $2r_\oplus$ to $1.4r_\oplus$.
+
+In \citet{ziegler_robo-ao_2017}'s recent summary of the Robo-AO KOI
+survey, they reported the fraction of planet-hosting stars with
+Robo-AO detected companion stars, binned over apparent planet radii.
+The fraction of KOIs with nearby stars and their $1\sigma$
+uncertainties are:
+\begin{itemize}
+    \item Earths ($r\a < 1.6r_\oplus$): $16.3 \pm 1.0\%$, from 1480
+    systems.
+    \item Neptunes ($1.6r_\oplus < r\a < 3.9 r_\oplus$): $13.0 \pm
+    0.8\%$, from 2058 systems.
+    \item Saturns ($3.9r_\oplus < r\a < 9 r_\oplus$): $13.6 \pm 2.0\%$, from 338 systems. 
+    \item Jupiters ($r\a > 9r_\oplus$): $19.0 \pm 2.8\%$, from 247 systems. 
+\end{itemize} 
+The uncertainties were calculated
+following~\citet{burgasser_binarity_2003}.  The absolute values of the
+companion fractions are lower than in the solar neighborhood at
+least in part because of Robo-AO's sensitivity
+(\citealt{ziegler_robo-ao_2017}'s
+Figure~2;~\citealt{raghavan_survey_2010}).
+%Another reason for the lower measured companion fraction could be
+%that planetary systems are more rare in binary systems,
+%as~\citealt{kraus_impact_2016} found for close binary companions).
+The uptick in the companion rate for Jupiters is likely tied to a
+large astrophysical false positive rate~\citep{santerne_sophie_2012}.
+Going from Neptunes to Earths, the data suggest a weak increase in the
+detected planet companion fraction, perhaps of a few percent.  It will
+be interesting to see whether this effect is borne out by further
+observations.
+
+\paragraph{Connecting high-resolution imaging to occurrence rates}
+
+Occurrence rate calculations are beginning to incorporate the results
+of high-resolution imaging surveys.  For example, recent studies have
+reduced contamination in the ``numerator'' of the occurrence rate by
+using~\citet{furlan_kepler_2017}'s catalog to test the effects of
+removing KOI hosts with known companions
+(\citealt{fulton_california-_2017}; \citealt{petigura_CKS_2017}).
+This is a good first step, but the denominator remains uncorrected.
+
+Even if the multiplicity of every star that {\it Kepler} surveyed were
+known, the problem would not be solved. In this scenario, it would be
+possible to tabulate planet occurrence for single and binary star
+systems separately.  The number of planets per single star would thus
+be known.  However the number of planets per primary and secondary
+would still be convolved.  An observational approach to
+separating the two populations might be to analyze the centroids, or the transit
+durations (and thus host star densities)
+for a representative sample of planets in binary systems.
+
+A theory-driven solution might entail probabilistic population
+inference, with a parametrized model for planet populations around
+primary and secondary stars.  Such an approach might find the
+populations to differ, given that secondary stars are less
+massive, and so are perhaps more likely to host smaller
+planets~\citep{dressing_occurrence_2015}.  Given the difficulty of
+writing a correct likelihood function in a survey with systematic
+biases, this might only be feasible by forward-modeling the survey in
+the framework of approximate Bayesian
+computation~\citep[\textit{e.g.},][]{morehead_understanding_2016}.
 
 \begin{comment}
-  Of course, such calculations are only suggestive; a conclusive
-  resolution of binarity's effects may require a detailed
-  understanding of the {\it Kepler}\ field's multiplicity statistics,
-  and the mission's completeness (both for candidate detection and
-  follow-up).  For instance, if hot Jupiters are less likely to be
-  confirmed in binary systems, this might bias the rates low.
-  Alternatively, {\it TESS}\ is expected to discover over $10^4$ giant
-  planets~\citep{ricker_transiting_2014,sullivan_transiting_2015}.
-  Though they will be difficult to distinguish from false positives,
-  one possible use of this sample will be to measure an occurrence
-  rate of short-period giant planets with minimal error from counting
-  statistics.  Our models suggest that binarity will only become an
-  appreciable fraction of the error budget at the $\approx 10\%$
-  precision level.  This should be sufficient for a rate measurement
-  precise enough to indicate a preference between $\approx 0.5\%$ and
-  $\approx 1\%$ of Sun-like stars hosting hot Jupiters.
-\end{comment}
-
-\paragraph{Practical effects: smooth detection efficiencies; finite SNR floors}
+%LB: the below paragraph seems like it is just making caveats for no
+%good reason. We've been explicit throughout that we have a
+%restrictive set of assumptions...
+
+  \paragraph{Practical effects: smooth detection efficiencies and finite SNR floors}
   To apply this study to real transit surveys, a few practical concerns
   become pressing.  One issue is that space-based missions with
-telemetric requirements are often required to select target stars.
-Even if the selection process aims to create an SNR-limited
-survey, as~\citet{batalha_selection_2010} did for {\it Kepler},
-uncertainties in stellar parameters and the modeled instrument
-performance can lead to deviations away from an SNR-limited stellar
-sample.
-
-Another concern is that in most transit surveys the detection
+  telemetric requirements often must select target stars.  Even if the
+  selection process aims to create an SNR-limited survey,
+  as~\citet{batalha_selection_2010} did for {\it Kepler}, uncertainties
+  in stellar parameters and the modeled instrument performance can lead
+  to deviations away from an SNR-limited stellar sample.
+
+  Another concern is that in real transit surveys the detection
   efficiency is not a step function in SNR.  Transit survey pipeline
-detection efficiencies are usually smooth functions~--~see for example
-the injection-recovery simulations performed
-by~\citet{christiansen_measuring_2016} on {\it Kepler}\ data, and the
-resulting detection efficiency adopted
-by~\citet{fulton_california-_2017}.  If we were to assume a smooth
-detection probability in SNR, we would need to include a detection
-efficiency term in Equation~\ref{eq:apparent_rate_density} to
-inversely weight for planets with low probabilities of being detected.
+  detection efficiencies are usually smooth
+  functions~\citep{christiansen_measuring_2016,fulton_california-_2017}.
+  If we were to assume a smooth detection probability in SNR, we would
+  need to appropriately weight our occurrence calculation for planets
+  with low probabilities of being detected.
 
@@
   (\citealt{fulton_california-_2017}, Figure~5).  To a good
-approximation, this allows one to use the boolean distinctions
+  approximation, this allows use of the boolean distinctions
   ``searchable'' and ``not searchable'' for signals of an observed depth
   (at fixed orbital period).  By making the survey strictly SNR-limited,
-rather than ``fuzzily SNR-limited'', binarity's effects become much
-easier to model.  Since the minimum SNR for detection is set in an
-arbitrary manner anyway\footnote{For example, {\it Kepler}'s threshold
-of ${\rm SNR}=7.1$ was set for there to be no more than one
-statistical false alarm across the full {\it Kepler}
+  rather than ``fuzzily SNR-limited'', the effects of unrecognized
+  binaries become much easier to model.  Since the minimum SNR for
+  detection is set arbitrarily\footnote{For example,
+  {\it Kepler}'s threshold of ${\rm SNR}=7.1$ was set for there to be no
+  more than one statistical false alarm across the full {\it Kepler}
   campaign~\citep{jenkins_tests_2002}. Equally valid would have been to
@@
   studies on clearer conceptual ground, and facilitate the process of
-converting the observed distributions of apparent radii into true
-radius distributions.
-
-Finally, our calculations also ignore the fact that any given transit
-survey's finite SNR floor might censor the apparent rate density.  If
-the surveyed stars all have the same size, this is equivalent to
-saying that there might be a cutoff in apparent planet radii, below
-which no planets are detected.  The effects on 
-Figures~\ref{fig:occ_rate_model_3_log},~\ref{fig:frac_model_3},
-and~\ref{fig:gaussian_HJ} would be that the apparent rate density
-below the cutoff in apparent radius would simply drop to zero.
+  converting the apparent radius distributions into true radius
+  distributions.
+
+  Finally, our calculations ignored the fact that a transit survey's
+  finite SNR floor could censor the apparent rate density. This would
+  make planets with smaller apparent radii harder to detect.  Other than
+  moving the small radii regime out of reach for that particular survey,
+  this would not change any of our findings.
+
+\end{comment}
 
 \begin{comment}
-  If one insists on using a smooth detection efficiency, then life
-  probably becomes more complicated.  It might then be necessary to
-  model the detection pipeline's efficiency while somehow
-  marginalizing over binarity.  Since the relative number of
-  detections (at fixed $\delta_{\rm obs}$) coming from singles,
-  primaries, and secondaries changes as a function of the intrinsic
-  distribution of planet parameters (Figure~\ref{fig:frac_model_3}),
-  some complicated deconvolution might be required.
-\end{comment}
-
-\paragraph{Connecting high resolution imaging to occurrence rates}
-One reason to address stellar multiplicity in transit surveys is that
-it can radically alter the interpretation of planet candidates on a
-system-by-system level.  Consequently, high resolution imaging
-campaigns have measured the multiplicities of almost all {\it Kepler}\
-Objects of Interest~\citep{
-  howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
-  horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
-  law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
-  wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016,ziegler_robo-ao_2017}.
-The results of these programs have been collected
-by~\citet{furlan_kepler_2017}, and they represent an important advance
-in understanding the KOI sample's multiplicity statistics.  
-An immediate application is to reassess the radii of detected planets.
-Doing so, \citet{hirsch_assessing_2017} find that for their sample of KOIs
-in binaries, the planet radii are underestimated by factors $r/r\a = 1.17$
-if all planets orbit primaries, and $r/r\a = 1.65$ if detected
-planets are equally likely to orbit primaries and singles.
-%In particular, they can be immediately applied to rectify binarity's
-%effects on the mass-radius diagram~\citep{furlan_densities_2017}.
-
-These results are beginning to connect with
-occurrence rate calculations: using~\citet{furlan_kepler_2017}'s
-catalog, recent studies have tested the effects of removing KOI hosts with
-known companions, reducing contamination in the ``numerator'' of the
-occurrence rate (\citealt{fulton_california-_2017};
-\citealt{petigura_CKS_2017}).  
-While these are good first steps, the
-denominator remains uncorrected.  To count the number of stars that
+%LB: the following are paragraphs from earlier discussion iterations
+
+  To count the number of stars that
   were searched, further effort to understand the multiplicity
-statistics of KOI vs.~non-KOI stars is necessary. In particular,
-a non-KOI star high-resolution imaging effort could help estimate
-the systematic errors incurred by assuming all surveyed stars are
-single.
-An alternate approach would be to combine {\it Gaia}
-parallaxes with measured photometric fluxes and identify binary systems
-as those that are 
-overluminous~\citep[\textit{e.g.},][]{widmark_inferring_2018}.
-
-\paragraph{Does a detected planet orbit the primary or secondary?}
-An important step towards rectifying binarity's effects is
-identifying the transit host star for detected planets in binaries.
-The current wisdom is that, unless the planet can be confirmed to
-orbit either component through analysis of the transit durations or
-centroids, little can be said about the likelihood of a
-planet orbiting the primary vs.~the
-secondary~\citep[\textit{e.g.},][though~\citealt{hirsch_assessing_2017}'s 
-do weight radius corrections by planet 
-occurrence]{ciardi_understanding_2015,ziegler_robo-ao_2017}.
-
-\begin{comment}
+  statistics of KOI vs.~non-KOI stars is necessary. In particular, a
+  non-KOI star high-resolution imaging effort could help estimate the
+  systematic errors incurred by assuming all surveyed stars are single.
+  An alternate approach would be to combine {\it Gaia} parallaxes with
+  measured photometric fluxes and identify binary systems as those that
+  are overluminous~\citep[\textit{e.g.},][]{widmark_inferring_2018}.
+
   \citet{ciardi_understanding_2015} studied the effects of stellar
@@
   are as likely to orbit the primary and the secondary.
-\end{comment}
-
-Assuming a broken power law radius distribution, we showed in
-Figure~\ref{fig:frac_model_3} that detected planets in binary systems
-are usually more likely to orbit the primary.  A planet orbiting the
-secondary does lead to extreme corrections.  However, at $r\a \gtrsim
-2r_\oplus$, these cases are rare outliers.  At $r_\oplus \lesssim r\a
-\lesssim 2r_\oplus$, for all of the trial values of $Z_2/Z_0$ assumed
-in Figure~\ref{fig:frac_model_3}, a detected planet is always more
-likely to orbit the primary than the secondary.  Only at very small
-apparent radii, $r\a \approx 0.5r_\oplus$, and only if secondaries
-host as many planets as singles and primaries, does this ``rule''
-break down.
 
@@
 
-\paragraph{Fraction of detected planets with binary companions vs. apparent 
-radius}
-One further prediction of Figure~\ref{fig:frac_model_3} is that the
-fraction of detected planets with binary companions increases by
-$\approx 6-12\%$ going from $2r_\oplus$ to $\approx\! 1.4r_\oplus$.
-In \citet{ziegler_robo-ao_2017}'s recent summary of the Robo-AO KOI
-survey, they reported the fraction of planet-hosting stars with
-Robo-AO detected companion stars, binning by Earths ($r\a <
-1.6r_\oplus$), Neptunes ($1.6r_\oplus < r\a < 3.9 r_\oplus$), Saturns
-($3.9r_\oplus < r\a < 9 r_\oplus$), and Jupiters ($r\a > 9r_\oplus$).
-The reported nearby star rates and their $1\sigma$ uncertainties are:
-\begin{itemize}
-    \item Earths: $16.3 \pm 1.0\%$, from 1480 systems.
-    \item Neptunes: $13.0 \pm 0.8\%$, from 2058 systems.
-    \item Saturns: $13.6 \pm 2.0\%$, from 338 systems.
-    \item Jupiters: $19.0 \pm 2.8\%$, from 247 systems.
-\end{itemize} 
-where the uncertainties were calculated
-following~\citet{burgasser_binarity_2003}.  The absolute values of the
-rates are less than the $\sim\! 45\%$ typical for Sun-like stars at
-least in part because of Robo-AO's sensitivity
-(\citealt{ziegler_robo-ao_2017}'s
-Figure~2;~\citealt{raghavan_survey_2010}).  Another reason for the
-lower measured companion rates could be that planetary systems are
-less likely to have binary companions (as~\citealt{kraus_impact_2016}
-argued for close binary companions).  The uptick in the companion rate
-for Jupiters is likely tied to a large astrophysical false positive
-rate~\citep{santerne_sophie_2012}.  Going from Neptunes to Earths, the
-data suggest a weak increase in the detected planet companion
-fraction, perhaps of a few percent.  It will be interesting to see
-whether this effect is borne out by further observations.
-
-\begin{comment}
   \paragraph{Independent approaches for estimating binarity's effects}
@@
 
-This study presented simple models for how binarity affects occurrence
-rates measured by transit surveys.  The simplest of these models
-(Section~\ref{sec:simplest}) provided an order-of-magnitude estimate
-that suggested we would need implausibly high twin binary fractions
-for binarity to affect apparent occurrence rates by more than factors
-of two.
+This study presented a framework for estimating the impact of
+unresolved binaries on transit survey occurrence rates. From
+the order-of-magnitude argument presented in
+Section~\ref{sec:simplest}, we showed that for Sun-like stars in the
+local neighborhood, typical twin binary fractions yield apparent
+occurrence rates that are well within a factor of two of the true
+rates for single stars.
 
 We then derived a general formula for the apparent rate density
-inferred by an observer ignoring binarity
+inferred by observers who ignore binarity
 (Equation~\ref{eq:general_Gamma_a}).  As input, this equation requires
-a volume-limited mass ratio distribution $f(q)$, and the true rate
-densities for planets around singles, primaries, and secondaries.  The
-assumptions that make the model tractable are:
+a volume-limited mass ratio distribution, and the true rate densities
+for planets around singles, primaries, and secondaries.  The
+assumptions that enable this approach are as follows.
 \begin{enumerate}
-    \item the transit survey is SNR-limited;
-    \item the true properties of all the singles and primaries are
-      known to the observer;
-    \item the observers assume that binaries have the same properties
-      as the primaries;
-    \item there are functions $L(M)$ and $R(M)$ that specify a star's
-      luminosity and radius in terms of its mass.
+    \item The transit survey is SNR-limited
+        (Equation~\ref{eq:S_N_thresh}).
+    \item The observers know the true properties of the single
+        and primary stars, and assign all unresolved binaries the
+        properties of the primary.
+    \item There are two functions, $L(M)$ and $R(M)$, that specify a
+        star's luminosity and radius in terms of its mass.
 \end{enumerate}
-Allowing for these conditions, many results follow:
+
+The interpretation of Equation~\ref{eq:general_Gamma_a} is that the
+apparent rate density is a weighted sum of the rate densities for
+single, primary, and secondary stars. The weights depend on the
+relative numbers of binary and single stars in the searchable volumes,
+which are affected by both dilution of transit signals and a Malmquist
+bias.  Both effects should be considered in Monte Carlo simulations of
+transit surveys~\citep[\textit{e.g.},][]{
+  bakos_hatsouth:_2013,sullivan_transiting_2015, gunther_new_2017}.
+
+Applying Equation~\ref{eq:general_Gamma_a}, we then showed that:
 \begin{itemize}
 %
-\item Assuming a power law planet radius distribution, and that the
-  same number of planets orbit singles, primaries, and secondaries,
-    binarity influences apparent planet occurrence rates around
-    Sun-like stars at the $\sim$few percent level from radii
-    $2r_\oplus \lesssim r\a \lesssim 17r_\oplus$
-    (Section~\ref{sec:model_2}).
-%
-\item Assuming a broken-power law planet radius distribution, with
-  \citet{howard_planet_2012}'s exponent at $r > 2r_\oplus$ and a
-    constant occurrence at $r < 2r_\oplus$, there is a ``bump'' in the
-    apparent rate density at $r\a < 2r_\oplus$, leading to a relative
-    error $\delta \Gamma_0 = |\Gamma_0 - \Gamma\a|/\Gamma_0$ of at
-    most $\approx 50\%$ (Figure~\ref{fig:occ_rate_model_3_log}).
-    Although this is smaller than current systematic uncertainties on
-    the occurrence rates of Earth-sized planets, this means that
-    binarity could eventually become an important component of the
-    $\eta_\oplus$ error budget.
+\item If single, primary, and secondary stars all host the same number
+  of planets per star, and the planet radius distribution is a power
+    law with the exponent reported by~\citet{howard_planet_2012} at $r
+    > 2r_\oplus$, then binarity influences apparent planet occurrence
+    rates at the few percent level. This applies for apparent radii
+    from $2r_\oplus$ to $17r_\oplus$ (Section~\ref{sec:model_2}).
+%
+\item Assuming a broken-power law planet radius distribution, with the
+  \citet{howard_planet_2012} exponent above $2r_\oplus$ and a constant
+    occurrence below $2r_\oplus$, there is a ``bump'' in the apparent
+    rate density at $r\a < 2r_\oplus$. This can lead to
+    overestimates in occurrence, $\Delta \Gamma_0 = |\Gamma_0 -
+    \Gamma\a|/\Gamma_0$, of roughly $50\%$
+    (Figure~\ref{fig:occ_rate_model_3_log}).  Although this is smaller
+    than current systematic uncertainties on the occurrence rates of
+    Earth-sized planets, this implies that binarity could eventually
+    become an important component of the $\eta_\oplus$ error budget.
 %
 \item Binarity ``fills in'' gaps in the radius distribution
-  (Figure~\ref{fig:model_4}), by an amount that could affect precise
-    measurements of the depth, width, and slope of
-    \citet{fulton_california-_2017}'s radius gap, in the event that
-    planets are not carefully vetted with high resolution imaging.
+  (Figure~\ref{fig:model_4}), to a degree that could affect precise
+    measurements of the depth, width, and slope
+    of~\citet{fulton_california-_2017}'s radius gap, in the event that
+    planets are not carefully vetted with high-resolution imaging.
 %
@@
 \item Detected planets with $r\a \gtrsim 0.5r_\oplus$ that are
-  revealed by high resolution imaging surveys to exist in binaries are
+  revealed by high-resolution imaging surveys to exist in binaries are
     more likely to orbit the primary (Figure~\ref{fig:frac_model_3}).
 %
-\item Near the ``break'' in the rate distribution ($\approx
-  2r_\oplus$), the fraction of detected planets with binary companions
-    increases by $\approx 5-10\%$ (Figure~\ref{fig:frac_model_3}).
+\item Near the ``break'' in occurrence rate as a function of planet
+  radius ($\approx 2r_\oplus$), the fraction of detected planets with
+    binary companions should increase by roughly $5$~-~$10\%$
+    (Figure~\ref{fig:frac_model_3}).
 \end{itemize}
 
-All of these results should be understood as only being strictly
-applicable when the assumptions listed above are met.  Otherwise,
-while it is only suggestive, our approach still provides helpful hints
-at how ignoring stellar binarity influences transit survey occurrence
+These results are only strictly applicable for idealized transit
+surveys meeting the criteria mentioned above.  For real transit
+surveys, although our approach is only suggestive, we hope that it
+provides a rough estimate for the systematic errors that can be
+incurred by ignoring binarity when calculating planetary occurrence
 rates.
@@
 It was a pleasure discussing this study with T.~Barclay, W.~Bhatti,
-J.~Christiansen and F.~Dai.  This work made use of NASA's Astrophysics
-Data System Bibliographic Services.
+J.~Christiansen, F.~Dai, and T.~Morton.  This work made use of NASA's
+Astrophysics Data System Bibliographic Services.
 %
@@
 \appendix
-\section{Derivation of general formula for apparent occurrence rate}
+\section{Alternative derivation of apparent rate density}
 \label{sec:appendix}
 
-This appendix derives Equation~\ref{eq:general_Gamma_a} in a more
-rigorous manner than in Section~\ref{sec:general_formula}.  First,
-recall our definition of apparent rate density
-(Equation~\ref{eq:apparent_rate_density}).  We assume that $R$ and $L$
-are uniquely determined from the assumed stellar
-mass--radius--luminosity relation, and neglect the dependence on
-planetary orbital period.  The planets with $(r\a, M\a)$ are
-associated with systems of many different planetary and stellar
-properties, so $n_{\rm det}(r\a, M\a)$ is given by the convolution of
-the true rate density, $\Gamma(r, M)$, and $\mathcal{N}_\star(r\a,
-M\a; r, M)$, the number (per unit $(r\a, M\a)$) of searchable stars
-that give $(r\a, M\a)$  when the true system actually has $(r, M)$.
+This appendix derives Equation~\ref{eq:general_Gamma_a} through a more
+straight-forward, but also more tedious, method than that presented in
+Section~\ref{sec:general_formula}.   First, note that analogous to
+Equation~\ref{eq:occ_rate_simple}, the apparent rate density $\Gamma\a$ can be
+written
+\begin{equation}
+    \Gamma\a(r\a,M\a) = \frac{n_{\rm det}(r\a,M\a)}{N_\star(r\a,M\a)}
+    \times \frac{1}{p_{\rm tra}(M\a)},
+\label{eq:apparent_rate_density}
+\end{equation}
+where $n_{\rm det}$ is the number of detected planets, per unit
+$(r\a, M\a)$, with apparent radius $r\a$ orbiting stars of
+apparent mass $M\a$.   The planets with $(r\a, M\a)$ are associated
+with systems of many different planetary and stellar properties, so
+$n_{\rm det}(r\a, M\a)$ is given by the convolution of the true rate
+density, $\Gamma(r, M)$, and $\mathcal{N}_\star(r\a, M\a; r, M)$, the
+number of searchable stars per unit $(r\a, M\a)$ that give $(r\a,
+M\a)$  when the true system actually has properties $(r, M)$.
 Mathematically,
@@
 \end{align}
-where $i$ specifies the type of true host stars (0: single, 1:
+where $i$ specifies the type of true host star (0: single, 1:
 primary, 2: secondary).  The problem reduces to the evaluation of
@@
     \mathcal{N}_\star^0(r\a,M\a; r,M)
-    =\delta(r\a-r)\delta(M\a-M) N_\star^0(r,M),
-\end{equation}
-so
+    =\hat{\delta}(r\a-r)\hat{\delta}(M\a-M) N_\star^0(r,M),
+\end{equation}
+where $\hat{\delta}$ is the Dirac delta function, so
 \begin{equation}
@@
 where $f(q)$ is the volume-limited binary mass ratio distribution.
-
-Since we assume $\ps\a=\ps_1$,
+Since we assume that binaries are assigned the mass of the primary,
 \begin{equation}
@@
     \propto
-    \delta(M\a-M).
+    \hat{\delta}(M\a-M).
 \end{equation}
 In this case, $\mathcal{N}_{{\rm s},q}^1$ is non-zero only at
-$r\a=R\a\sqrt{\delta_{\rm obs}}$, and the observed depth is
-\begin{equation}
-    \delta_{\rm obs}
-    = \left[{r\over R(M\a)}\right]^2\times {L(M\a) \over L_{\rm sys}(M\a, q)}
-    \equiv \left[{r\over R(M\a)}\right]^2\times \mathcal{A}(q,M\a)^2,
+$r\a=R\a\sqrt{\delta}$, and the observed depth is
+\begin{equation}
+    \delta
+    = \left[{r\over R(M\a)}\right]^2\times {L(M\a) \over L_{\rm tot}(M\a, q)}
+    \equiv \left[{r\over R(M\a)}\right]^2\times 
+    \frac{1}{\mathcal{D}_1^2}
     \label{eq:delta_obs_primaries} 
@@
 \begin{equation}
-    \mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}.
+    \mathcal{D}_1=\sqrt{L_{\rm tot}(M\a, q) \over L(M\a)}.
 \end{equation}
 The normalization of $\mathcal{N}_{{\rm s},q}^1$ is given by the
-number of binaries that are searchable for a signal $\delta_{\rm obs}$
-and that have the mass ratio $q$:
-\begin{equation}
-    N_\star^0(\delta_{\rm obs}, 
+number of binaries that are searchable for a signal $\delta$
+and that have mass ratio $q$:
+\begin{equation}
+    N_\star^0(\delta, 
     L(M\a))\cdot
-    {n\b\over n\s}\left[L_{\rm sys}(M\a, q) \over L(M\a)\right]^{3/2}
-    =N_\star^0(\delta_{\rm obs}, L(M\a))
-    \cdot \frac{{\rm BF}}{1 - {\rm BF}} \cdot {1 \over \mathcal{A}(q,M\a)^3}.
+    {n\b\over n\s}\left[L_{\rm tot}(M\a, q) \over L(M\a)\right]^{3/2}.
     \label{eq:primary_normalization}
@@
 \begin{align}
-    \notag
     \mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M)
-    &=N_\star^0(\delta_{\rm obs}, L(M\a))
-    \cdot \frac{{\rm BF}}{1 - {\rm BF}} \cdot {1 \over \mathcal{A}(q,M\a)^3}\\
-    &\times\delta \left[r\a-r\mathcal{A}(q,M\a)\right]\delta(M\a-M).
+    &=N_\star^0(\delta, L(M\a))
+    \cdot {n\b\over n\s} \cdot \mathcal{D}_1^3
+    \cdot\hat{\delta} \left[r\a-\frac{r}{\mathcal{D}_1}\right]\hat{\delta}(M\a-M).
     \label{eq:N_s_1}
@@
     \mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
-    \propto \delta\left(M\a-{M\over q}\right).
+    \propto \hat{\delta}\left(M\a-{M\over q}\right).
     \label{eq:fancyN_s_2_prop}
@@
 Again $\mathcal{N}_\star^2$ is non-zero only at
-$r\a=R\a\sqrt{\delta_{\rm obs}}$, but this time
-\begin{equation}
-    \delta_{\rm obs} = \left[{r\over R(qM\a)}\right]^2 \times {L(qM\a) 
-      \over L_{\rm sys}(M\a, q)}
-      \equiv \left[{r\over R(M\a)}\right]^2\times \mathcal{B}(q,M\a)^2,
+$r\a=R\a\sqrt{\delta}$, but this time
+\begin{equation}
+      \delta =
+      \left[{r\over R(qM\a)}\right]^2 \times
+      {L(qM\a) \over L_{\rm tot}(M\a, q)}
+      \equiv
+      \left[{r\over R(M\a)}\right]^2\times
+      \frac{1}{\mathcal{D}_2^2},
 \end{equation}
@@
 \begin{equation}
-    \mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over
-    L_{\rm sys}(M\a, q)} }.
-\end{equation}
-The normalization remains the same as the previous case (we are
-counting the searchable stars at a given observed depth $\delta_{\rm
-obs}$, and the total luminosity of the binary is the same).  Thus,
+  \mathcal{D}_2
+  =
+  \frac{R(qM\a)}{R(M\a)}
+  \sqrt{ \frac{L_{\rm tot}(M\a,q)}{L(qM\a)} }.
+\end{equation}
+The normalization remains the same as the previous case~--~we are
+counting the searchable stars at a given observed depth $\delta$, and
+the total luminosity of the binary is the same.  Thus,
 \begin{equation}
@@
 \begin{align}
-    \notag
     \mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
-    &=N_\star^0(\delta_{\rm obs}, L(M\a)) \cdot \frac{{\rm BF}}{1 - {\rm BF}} 
-    \cdot {1 \over \mathcal{A}(q,M\a)^3}\\
-    &\times 
-      \delta \left[r\a-r\mathcal{B}(q,M\a)\right]
-      \delta\left(M\a-{M\over q}\right).
+    =N_\star^0(\delta, L(M\a)) \cdot \frac{n\b}{n\s} 
+    \cdot \mathcal{D}_1^3
+    \cdot \hat{\delta} \left[r\a-\frac{r}{\mathcal{D}_2}\right]
+    \hat{\delta} \left(M\a-{M\over q}\right).
     \label{eq:mathcal_N_s_2}
@@
 One might worry in Equation~\ref{eq:mathcal_N_s_2} that we opt to
-write $\mathcal{N}\s^2 \propto \delta(M\a - M/q)$, rather than
-$\propto \delta(M\a q - M)$ or some other delta function with the same
+write $\mathcal{N}\s^2 \propto \hat{\delta}(M\a - M/q)$, rather than
+$\propto \hat{\delta}(M\a q - M)$ or some other delta function with the same
 functional dependence, but a different normalization once integrated.
@@
     \cdot\Gamma_0(r, M) \cdot p_{\rm tra}(M)\\
-    &=N_\star^0(\delta_{\rm obs}, L(M\a))\cdot\Gamma_0(r\a, M\a) \cdot p_{\rm 
+    &=N_\star^0(\delta, L(M\a))\cdot\Gamma_0(r\a, M\a) \cdot p_{\rm 
         tra}(M\a),
@@
     \cdot\Gamma_1(r, M) \cdot p_{\rm tra}(M)\\
-    &=N_\star^0(\delta_{\rm obs}, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
-    {\mathrm{BF}\over{1-\mathrm{BF}}} \int {\mathrm{d}q \over 
-        \mathcal{A}^4}\,f(q)\,\Gamma_1\left({r\a\over\mathcal{A}}, M\a\right).
+    &=N_\star^0(\delta, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
+    \frac{n\b}{n\s}
+    \int \mathrm{d}q \,
+         \mathcal{D}_1^3 f(q)\cdot
+         \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a, M\a).
     \label{eq:n_det_1}
@@
     &=
-    N_\star^0(\delta_{\rm obs}, L(M\a))\cdot \frac{{\rm BF}}{1 - {\rm BF}}
-    \int {q \mathrm{d}q \over 
-    {\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma_2\left({r\a\over\mathcal{B}}, 
-    qM\a\right)\,p_{\rm 
-        tra}(qM\a).
+    N_\star^0(\delta, L(M\a))\cdot \frac{n\b}{n\s}
+    +\int {\rm d}q\, 
+         \mathcal{D}_1^3 f(q)\cdot q \mathcal{D}_2
+         \Gamma_2(\mathcal{D}_2r\a, qM\a)\cdot
+         \frac{R(qM\a)}{R(M\a)} q^{-1/3}.
     \label{eq:n_det_2}
@@
 \paragraph{General formula for apparent occurrence rate}
-Using the above results, the apparent rate density,
+Combining the above results with Equation~\ref{eq:N_searched}, the
+apparent rate density,
 \begin{align}
@@
 evaluates to
-
 \begin{align}
     \notag
-    \Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
+    \Gamma\a(r\a,M\a) &= \frac{1}{1+\mu} \cdot
     \left\{ \Gamma_0(r\a, M\a)+ 
-    \frac{{\rm BF}}{1 - {\rm BF}}
-    \left[ \int {\mathrm{d}q \over \mathcal{A}^4}\,f(q)\,\Gamma_1\left({r\a\over 
-        \mathcal{A}}, 
-    M\a\right)\,
+    \frac{n\b}{n\s}
+    \left[ \int_0^1 \mathrm{d}q \,
+           \mathcal{D}_1^3 f(q)\cdot
+           \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a, M\a)\,
     \right.   
@@
     & \quad\quad\quad\quad\quad \left.\left.
-    +\int {q \mathrm{d}q \over 
-        {\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma_2\left({r\a\over 
-        \mathcal{B}}, 
-    qM\a\right)\,
-    {R(qM\a) \over R(M\a)}
-    q^{-1/3} \right]	\right\}.
-    \label{eq:final_formula}
+    +\int_0^1 {\rm d}q\, 
+         \mathcal{D}_1^3 f(q)\cdot q \mathcal{D}_2
+         \Gamma_2(\mathcal{D}_2r\a, qM\a)\cdot
+         \frac{R(qM\a)}{R(M\a)} q^{-1/3}
+    \right] \right\}.
 \end{align}
-This equation is used to derive
-Equations~\ref{eq:model5_apparent_rate_density}
-and~\ref{eq:powerlaw_vary_binary}, and is numerically integrated to
-create Figs.~\ref{fig:occ_rate_model_3_log},~\ref{fig:model_4},
-and~\ref{fig:gaussian_HJ}.  It is validated in limits in which it is
-possible to write down the answer (e.g.,
-Equation~\ref{eq:model_1_apparent_rate_density}), and also against a
-Monte Carlo realization of the twin binary models
-(Secs.~\ref{sec:model_1} and~\ref{sec:model_2}).
+We validate this equation in limits where it is possible to write down
+the answer (e.g., Equation~\ref{eq:formula_twin_binary}), and also
+against a Monte Carlo realization of the twin binary models
+(Sections~\ref{sec:model_1} and~\ref{sec:model_2}).
 

### 2018-02-14 src/plot_mass_ratio_distribution.py

@@ -9,6 +9,7 @@ rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
 rc('text', usetex=True)
 
 import matplotlib.pyplot as plt
+plt.switch_backend('agg')
 import numpy as np
 from scipy.integrate import trapz
 
@@ -28,8 +29,9 @@ ax.plot(q, yvals, label='volume-limited', zorder=1)
 
 ax.legend(loc='best',fontsize='medium')
 
-ax.set_xlabel('$q=M_2/M_1$', fontsize='large')
-ax.set_ylabel('$p(\mathrm{draw\ }q\,|\,\mathrm{system\ is\ binary})$', fontsize='large')
+ax.set_xlabel('binary mass ratio, $q=M_2/M_1$', fontsize='large')
+#ax.set_ylabel('$p(\mathrm{draw\ }q\,|\,\mathrm{system\ is\ binary})$', fontsize='large')
+ax.set_ylabel('relative probability', fontsize='large')
 ax.set_ylim([-0.1,2.3])
 ax.set_xlim([-0.05,1.05])
 

### 2018-02-14 src/plot_visualize_volumes.py

@@ -10,6 +10,7 @@ rc('text', usetex=True)
 
 from mpl_toolkits.mplot3d import Axes3D
 import matplotlib.pyplot as plt
+plt.switch_backend('agg')
 import numpy as np
 from mpl_toolkits.mplot3d import proj3d
 
@@ -74,11 +75,11 @@ def make_sphere(radius, txt, ax, ind):
     ax.patch.set_alpha(0.) # make background transparent
 
 
-fig = plt.figure(figsize=(4,4))
+fig = plt.figure(figsize=(4.1,4))
 
 inds = [1,2,3,4]
-radii = [1, 2**(1/2), 1, 2**(-1/2)]
-txts = ['$d_0$', '$\sqrt{2}d_0$', '$d_0$', '$d_0/\sqrt{2}$']
+radii = [1, 2**(1/2), 1/2, 2**(-1/2)]
+txts = ['$d_0$', '$\sqrt{2}d_0$', '$d_0/2$', '$d_0/\sqrt{2}$']
 
 for ind, r, txt in zip(inds, radii, txts):
 
@@ -93,9 +94,9 @@ ax.text2D(.3, .05, 'single stars', transform=fig.transFigure,
      fontsize='large', va='bottom', ha='center')
 ax.text2D(.7, .05, 'twin binaries', transform=fig.transFigure,
      fontsize='large', va='bottom', ha='center')
-ax.text2D(.05, .3, '$r_{\mathrm{a}}=r_{\mathrm{p}}$', transform=fig.transFigure,
+ax.text2D(.05, .3, '$r_{\mathrm{a}}=r_{\mathrm{p}}/\sqrt{2}$', transform=fig.transFigure,
      fontsize='large', va='center', ha='left', rotation=90)
-ax.text2D(.05, .7, '$r_{\mathrm{a}}=r_{\mathrm{p}}/\sqrt{2}$', transform=fig.transFigure,
+ax.text2D(.05, .7, '$r_{\mathrm{a}}=r_{\mathrm{p}}$', transform=fig.transFigure,
         fontsize='large', va='center', ha='left', rotation=90)
 
 fig.savefig('../results/visualize_volumes.pdf', dpi=300,

### 2018-02-14 paper/main.tex
improve text (minor)

@@
   \Lambda = \frac{N_{\rm det}}{N_\star}
-                    \times \frac{1}{p_{\rm tra}},
+                    \cdot \frac{1}{p_{\rm tra}},
 \label{eq:occ_rate_simple}
@@
 observed transit depth.
-% Accounting for each effect requires some care.
 
@@
 \begin{equation}
-    {N_\star(r\a)\over{1+\mu}}\times {n_{\rm b}\over n_{\rm s}}
+    {N_\star(r\a)\over{1+\mu}}\cdot {n_{\rm b}\over n_{\rm s}}
     \left[{L_{\rm tot}(M\a, q) \over L(M\a)}\right]^{3/2}
@@
 apparent rate density is a mere 0.4\% larger than the rate density of
-single stars.
-%relative difference $\Delta \Gamma_0 = |\Gamma_0~-~\Gamma\a|/\Gamma_0$
-Fortuitously, the exponent of the radius distribution is close to
-$-3$, and the errors from neglecting binaries almost entirely
-cancel out.
+single stars.  Fortuitously, the exponent of the radius distribution
+is close to $-3$, and the errors from neglecting binaries almost
+entirely cancel out.
 
@@
 \begin{equation}
-    \Gamma_i(r,M) = Z_i \times \frac{r^\gamma}{\mathcal{N}_r} \times
+    \Gamma_i(r,M) = Z_i \cdot \frac{r^\gamma}{\mathcal{N}_r} \cdot
     \frac{M^\zeta}{\mathcal{N}_M},
@@
 apparent stellar mass, we find that when all stars host the same number
-of planets ($Z_0=Z_1=Z_2$),
+of planets,
 \begin{align}
@@
     \left[
-      1 + \frac{1}{\mathcal{N}_q} \frac{n\b}{n\s}\times 
+      1 + \frac{1}{\mathcal{N}_q} \frac{n\b}{n\s}
     \left(
@@
 shows planetary transits.  It is often impossible to rule which star
-hosts the detected planet.  Intuitively, one would expect that the
-primary star would be the more likely host because at fixed
-planet size, planetary transits around secondaries have smaller
-amplitudes (Equations~\ref{eq:dil_1} and~\ref{eq:dil_2} imply
+hosts the detected planet.  One would intuitively expect that the
+primary star would be the more likely host because at fixed planet
+size, planetary transits around secondaries have smaller amplitudes
+(Equations~\ref{eq:dil_1} and~\ref{eq:dil_2} imply
 $\mathcal{D}_2>\mathcal{D}_1$, if $\alpha=3.5$).  However, this
-reasoning is qualitative, and its assumptions might not always
-hold.
+reasoning is qualitative, and its assumptions might not always hold.
 
@@
 from larger true planetary radii!  Rephrased, going from apparent
-radii of $2r_\oplus$ to $1.4r_\oplus$, the fraction of detected
-planets with binary companions increases by anywhere from $6\%$ to
-$12\%$, depending on the relative occurrence of planets about
+radii of $2r_\oplus$~to~$1.4r_\oplus$, the fraction of detected
+planets with binary companions increases by anywhere from
+$6\%$~to~$12\%$, depending on the relative occurrence of planets about
 primaries and secondaries.  We compare this prediction with recent
@@
 %check_companion_fractions.py, and LB's notes 2017/12/21.0 }.
-%This effect will appear in any radius distribution that declines at
-%large radii, and flattens below some cutoff radius, $r_{\rm c}$.  This
-%is because (for dilution about primaries) at apparent radii $r\a <
-%r_{\rm c}/\sqrt{2}$, relatively more planets will be ``diluted'' into
-%the given $r\a$, since there are more planets in the undiluted
-%distribution from $r\a$ to $\sqrt{2}r\a$.
 
@@
 %int_rate_density_vs_radius_model_7_withtext*manyZs.pdf
-%For the case when no hot Jupiters orbit secondaries, $\Lambda_{{\rm
-%HJ},0} \approx \Lambda_{\rm HJ,a}$ to within one percent.
 Qualitatively, the apparent HJ rate is greater than the true rate for
@@
 This appendix derives Equation~\ref{eq:general_Gamma_a} through a more
-straight-forward, but also more tedious, method than that presented in
+straight-forward, but also more tedious, procedure than that of
 Section~\ref{sec:general_formula}.   First, note that analogous to
@@
     \Gamma\a(r\a,M\a) = \frac{n_{\rm det}(r\a,M\a)}{N_\star(r\a,M\a)}
-    \times \frac{1}{p_{\rm tra}(M\a)},
+    \cdot \frac{1}{p_{\rm tra}(M\a)},
 \label{eq:apparent_rate_density}
@@
     \delta
-    = \left[{r\over R(M\a)}\right]^2\times {L(M\a) \over L_{\rm tot}(M\a, q)}
-    \equiv \left[{r\over R(M\a)}\right]^2\times 
+    = \left[{r\over R(M\a)}\right]^2\cdot {L(M\a) \over L_{\rm tot}(M\a, q)}
+    \equiv \left[{r\over R(M\a)}\right]^2\cdot 
     \frac{1}{\mathcal{D}_1^2}
@@
 \begin{equation}
-    N_\star^0(\delta, 
-    L(M\a))\cdot
+    N_\star^0(r\a, M\a)\cdot
     {n\b\over n\s}\left[L_{\rm tot}(M\a, q) \over L(M\a)\right]^{3/2}.
@@
 \end{equation}
-Thus,
+where the argument for the number of searchable single stars,
+$N_\star^0$, could also be expressed as $(\delta, L(M\a))$.
+Applying Equation~\ref{eq:primary_normalization},
 \begin{align}
     \mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M)
-    &=N_\star^0(\delta, L(M\a))
+    &=N_\star^0(r\a, M\a)
     \cdot {n\b\over n\s} \cdot \mathcal{D}_1^3
@@
       \delta =
-      \left[{r\over R(qM\a)}\right]^2 \times
+      \left[{r\over R(qM\a)}\right]^2 \cdot
       {L(qM\a) \over L_{\rm tot}(M\a, q)}
       \equiv
-      \left[{r\over R(M\a)}\right]^2\times
+      \left[{r\over R(M\a)}\right]^2\cdot
       \frac{1}{\mathcal{D}_2^2},
@@
     \mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
-    =N_\star^0(\delta, L(M\a)) \cdot \frac{n\b}{n\s} 
+    =N_\star^0(r\a, M\a) \cdot \frac{n\b}{n\s} 
     \cdot \mathcal{D}_1^3
@@
     \cdot\Gamma_0(r, M) \cdot p_{\rm tra}(M)\\
-    &=N_\star^0(\delta, L(M\a))\cdot\Gamma_0(r\a, M\a) \cdot p_{\rm 
+    &=N_\star^0(r\a, M\a)\cdot\Gamma_0(r\a, M\a) \cdot p_{\rm 
         tra}(M\a),
@@
     \cdot\Gamma_1(r, M) \cdot p_{\rm tra}(M)\\
-    &=N_\star^0(\delta, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
+    &=N_\star^0(r\a, M\a)\cdot p_{\rm tra}(M\a) \cdot
     \frac{n\b}{n\s}
@@
     &=
-    N_\star^0(\delta, L(M\a))\cdot \frac{n\b}{n\s}
+    N_\star^0(r\a, M\a)\cdot \frac{n\b}{n\s}
     +\int {\rm d}q\, 
@@
     \Gamma\a(r\a,M\a) &= 
-    \frac{1}{N_\star(r\a,M\a) p_{\rm tra}(r\a,M\a)} \times
+    \frac{1}{N_\star(r\a,M\a) p_{\rm tra}(r\a,M\a)} \cdot
     \sum_i n_{\rm det}^i (r\a,M\a),

### 2018-02-14 paper/main.tex
improve text (minor)

@@
 \shortauthors{Bouma et al.}
-\shorttitle{Binarity and Occurrence Rates}
+\shorttitle{Binary Biases}
 
@@
 \end{equation}
+
+\item The contribution to the apparent rate density from
+secondaries now depends on the mass of the secondary, $qM\a$. The
+associated measure on the right-hand side of
+Equation~\ref{eq:n2} becomes ${\rm d}(qM\a)$, and gives rise to an
+extra multiplicative factor of $q$.
 
@@
 If secondaries host as many planets as single stars, the occurrence of
-these small planets is overestimated by $\approx 50\%$.  The magnitude
+these small planets is overestimated by about $50\%$.  The magnitude
 of the systematic error decreases if there are fewer planets around
 secondaries; if secondaries host no planets at all, the apparent rate
-is overestimated by only $\approx 10\%$.
+is overestimated by only $10\%$.
 
@@
 exist about primaries and secondaries at equal rates, then the planet
-is $\approx\!3$ times more likely to orbit the primary than the
+is $3$ times more likely to orbit the primary than the
 secondary.  If secondaries host half as many planets as primaries,
-then a detected planet is $\approx\!5$ times more likely to orbit the
+then a detected planet is $5$ times more likely to orbit the
 primary.
@@
 to orbit the primary.  However, if planets exist at the same rate in
-primaries and secondaries, then there is a turn-over radius,
-$\approx\!0.4r_\oplus$, below which more of the detected planets in
-binaries come from secondaries~--~they have all been ``diluted down''
-from larger true planetary radii!  Rephrased, going from apparent
-radii of $2r_\oplus$~to~$1.4r_\oplus$, the fraction of detected
-planets with binary companions increases by anywhere from
-$6\%$~to~$12\%$, depending on the relative occurrence of planets about
-primaries and secondaries.  We compare this prediction with recent
-observations in Section~\ref{sec:discussion}.
+primaries and secondaries, then below apparent radii of $0.4r_\oplus$,
+more of the detected planets in binaries come from secondaries~--~they
+have all been diluted down from larger true planetary radii.
+Rephrased, going from apparent radii of $2r_\oplus$~to~$1.4r_\oplus$,
+the fraction of detected planets with binary companions increases by
+anywhere from $6\%$~to~$12\%$, depending on the relative occurrence of
+planets about primaries and secondaries.  We compare this prediction
+with recent observations in Section~\ref{sec:discussion}.
 %~\footnote{
@@
 approach suggests that they do not influence the hot Jupiter rate
-discrepancy.  The ``discrepancy'' is that hot Jupiter occurrence rates
-measured by transit surveys ($\approx 0.5\%$) are lower than those
-found by radial velocity surveys ($\approx 1\%$; see
-Table~\ref{tab:hj_rates}).
+discrepancy.  The ``discrepancy'' is that RV surveys find roughly
+twice as many hot Jupiters per Sun-like star as do transit surveys
+($\approx 1\%$~vs.~$\approx 0.5\%$, respectively).  We summarize hot
+Jupiter rates reported by different surveys in
+Table~\ref{tab:hj_rates}.
 
@@
 found $\beta = 3.4^{0.9}_{-0.8}$.  If true, this implies that
-metallicity could account for about half of the ``hot Jupiter rate
-discrepancy''.  }.  \citeauthor{guo_metallicity_2017}\!  concluded
+metallicity could account for about half of the hot Jupiter rate
+discrepancy.  }.  \citeauthor{guo_metallicity_2017}\!  concluded
 that ``other factors, such as binary contamination and imperfect
@@
 of high-resolution imaging surveys.  For example, recent studies have
-reduced contamination in the ``numerator'' of the occurrence rate by
+reduced contamination in the numerator of the occurrence rate by
 using~\citet{furlan_kepler_2017}'s catalog to test the effects of
@@
   \citet{howard_planet_2012} exponent above $2r_\oplus$ and a constant
-    occurrence below $2r_\oplus$, there is a ``bump'' in the apparent
-    rate density at $r\a < 2r_\oplus$. This can lead to
-    overestimates in occurrence, $\Delta \Gamma_0 = |\Gamma_0 -
-    \Gamma\a|/\Gamma_0$, of roughly $50\%$
+    occurrence below $2r_\oplus$, the rate density for radii below
+    $2r_\oplus$ is overestimated. The overestimate, $\Delta \Gamma_0 =
+    |\Gamma_0 - \Gamma\a|/\Gamma_0$, can easily reach $50\%$
     (Figure~\ref{fig:occ_rate_model_3_log}).  Although this is smaller
@@
 %
-\item Binarity ``fills in'' gaps in the radius distribution
+\item Binarity blurs sharp features in the radius distribution
   (Figure~\ref{fig:model_4}), to a degree that could affect precise
-    measurements of the depth, width, and slope
-    of~\citet{fulton_california-_2017}'s radius gap, in the event that
-    planets are not carefully vetted with high-resolution imaging.
+    measurements of the depth, width, and slope of
+    the~\citet{fulton_california-_2017} radius gap.
+    %in the event that
+    %planets are not carefully vetted with high-resolution imaging.
 %
@@
 %
-\item Near the ``break'' in occurrence rate as a function of planet
+\item Near the break in occurrence rate as a function of planet
   radius ($\approx 2r_\oplus$), the fraction of detected planets with

### 2018-02-14 paper/main.tex
improve text (minor)

@@
 \shortauthors{Bouma et al.}
-\shorttitle{Binary Biases}
+\shorttitle{Binarity's Biases}
 
@@
 implementation\footnote{\url{https://github.com/lgbouma/binary_biases}}.
-As before, $L\propto M^\alpha \propto R^\alpha$, and $\alpha=3.5$,
-$\beta=0$, $\gamma=-2.92$.  The output, shown in
-Figure~\ref{fig:occ_rate_model_3_log}, is validated using analytic
-predictions in the $r\a > 2r_\oplus$ and the $r\a <
-2r_\oplus/\sqrt{2}$ regimes.
+The output, shown in Figure~\ref{fig:occ_rate_model_3_log}, is
+validated using analytic predictions in the $r\a > 2r_\oplus$ and the
+$r\a < 2r_\oplus/\sqrt{2}$ regimes.  As before, $L\propto M^\alpha
+\propto R^\alpha$, and $\alpha=3.5$, $\beta=0$, $\gamma=-2.92$.
 
@@
 twice as many hot Jupiters per Sun-like star as do transit surveys
-($\approx 1\%$~vs.~$\approx 0.5\%$, respectively).  We summarize hot
+(roughly $1\%$~vs.~$0.5\%$, respectively).  We summarize hot
 Jupiter rates reported by different surveys in
@@
 A related effect is that some detected planets are more likely to be
-in binary systems than others.  Notably,
-Figure~\ref{fig:frac_model_3} predicts that the fraction of detected
-planets with binary companions should increase by $\approx 6-12\%$
-going from $2r_\oplus$ to $1.4r_\oplus$.
+in binary systems than others.  Notably, Figure~\ref{fig:frac_model_3}
+predicts that the fraction of detected planets with binary companions
+should increase by $6$~to~$12\%$ going from $2r_\oplus$ to
+$1.4r_\oplus$.
 
@@
 
-\paragraph{Connecting high-resolution imaging to occurrence rates}
+\paragraph{Connection between high-resolution imaging and occurrence rates}
 
@@
 possible to tabulate planet occurrence for single and binary star
-systems separately.  The number of planets per single star would thus
+systems separately.  The number of planets per single star would
 be known.  However the number of planets per primary and secondary
-would still be convolved.  An observational approach to
-separating the two populations might be to analyze the centroids, or the transit
-durations (and thus host star densities)
-for a representative sample of planets in binary systems.
+would still be convolved.  An observational approach to separating the
+two populations might be to analyze the centroids, or the transit
+durations (and thus host star densities) for a representative sample
+of planets in binary systems.
 
@@
 inference, with a parametrized model for planet populations around
-primary and secondary stars.  Such an approach might find the
-populations to differ, given that secondary stars are less
-massive, and so are perhaps more likely to host smaller
-planets~\citep{dressing_occurrence_2015}.  Given the difficulty of
-writing a correct likelihood function in a survey with systematic
-biases, this might only be feasible by forward-modeling the survey in
+primary and secondary stars.  Such an approach might be expected to
+find that the primary and secondary populations are different, since
+single M dwarfs host more small planets than FGK
+dwarfs~\citep{dressing_occurrence_2015}.  Given the difficulty of
+writing a likelihood function in a survey with systematic
+biases, one possible approach might be to forward-model the survey in
 the framework of approximate Bayesian
@@
 %
-\item Near the break in occurrence rate as a function of planet
-  radius ($\approx 2r_\oplus$), the fraction of detected planets with
-    binary companions should increase by roughly $5$~-~$10\%$
+\item Near the break in occurrence as a function of planet
+  radius at $2r_\oplus$, the fraction of detected planets with
+    binary companions should increase by roughly $5$~to~$10\%$
     (Figure~\ref{fig:frac_model_3}).
@@
 surveys, although our approach is only suggestive, we hope that it
-provides a rough estimate for the systematic errors that can be
-incurred by ignoring binarity when calculating planetary occurrence
+provides a useful estimate for the systematic errors that can be
+incurred by ignoring binarity in calculations of planetary occurrence
 rates.

### 2018-02-16 paper/main.tex
improve text (minor)

@@
   of planets per star, and the planet radius distribution is a power
-    law with the exponent reported by~\citet{howard_planet_2012} at $r
-    > 2r_\oplus$, then binarity influences apparent planet occurrence
-    rates at the few percent level. This applies for apparent radii
-    from $2r_\oplus$ to $17r_\oplus$ (Section~\ref{sec:model_2}).
+    law with the exponent reported by~\citet{howard_planet_2012}, then
+    binarity influences apparent planet occurrence rates at the few
+    percent level. This applies for apparent radii from $2r_\oplus$ to
+    $17r_\oplus$ (Section~\ref{sec:model_2}).
 %
@@
     occurrence below $2r_\oplus$, the rate density for radii below
-    $2r_\oplus$ is overestimated. The overestimate, $\Delta \Gamma_0 =
-    |\Gamma_0 - \Gamma\a|/\Gamma_0$, can easily reach $50\%$
-    (Figure~\ref{fig:occ_rate_model_3_log}).  Although this is smaller
-    than current systematic uncertainties on the occurrence rates of
-    Earth-sized planets, this implies that binarity could eventually
-    become an important component of the $\eta_\oplus$ error budget.
+    $2r_\oplus$ is overestimated. The magnitude of the error, $\Delta
+    \Gamma_0 = |\Gamma_0 - \Gamma\a|/\Gamma_0$, can easily reach
+    $50\%$ (Figure~\ref{fig:occ_rate_model_3_log}).  Although this is
+    smaller than current systematic uncertainties on the occurrence
+    rates of Earth-sized planets, this implies that binarity could
+    eventually become an important component of the $\eta_\oplus$
+    error budget.
 %
@@
 %
-\item Detected planets with $r\a \gtrsim 0.5r_\oplus$ that are
-  revealed by high-resolution imaging surveys to exist in binaries are
-    more likely to orbit the primary (Figure~\ref{fig:frac_model_3}).
+\item Detected planets with apparent radii greater than $0.5r_\oplus$
+  that are revealed by high-resolution imaging surveys to exist in
+    binaries are more likely to orbit the primary
+    (Figure~\ref{fig:frac_model_3}).
 %

### 2018-02-19 paper/main.tex
update shortauth
match AAS submission standards

@@
 
-\shortauthors{Bouma et al.}
+\shortauthors{Bouma, Masuda, Winn}
 \shorttitle{Binarity's Biases}
@@
 
-\title{ The effects of binarity on planet occurrence rates measured by
-transit surveys}
+\title{ Binarity's Biases on Transit Survey Occurrence Rates }
 %
@@
 %
-\author{L. G. Bouma}
+\author[0000-0002-0514-5538]{L. G. Bouma}
 \affiliation{
@@
     4 Ivy Lane, Princeton, NJ 08540, USA}
-\author{K. Masuda}
+\author[0000-0003-1298-9699]{K. Masuda}
 \affiliation{
@@
     4 Ivy Lane, Princeton, NJ 08540, USA}
-\author{J. N. Winn}
+\author[0000-0002-4265-047X]{J. N. Winn}
 \affiliation{
@@
   \Lambda = \frac{N_{\rm det}}{N_\star}
-                    \cdot \frac{1}{p_{\rm tra}},
+                    \, \frac{1}{p_{\rm tra}},
 \label{eq:occ_rate_simple}
@@
 \begin{equation}
-  d_{\rm max} \propto \delta \cdot L_{\rm tot}^{1/2}.
+  d_{\rm max} \propto \delta \, L_{\rm tot}^{1/2}.
   \label{eq:dmax}
@@
     \caption{
-        Apparent occurrence rate $\Lambda\a$, and occurrence rate for
-        singles $\Lambda_0$, for a model with one type of star, one
+        Apparent occurrence rate $\Lambda\a$, and occurrence rate $\Lambda$, 
+        for a model with one type of star, one
         type of planet, and twin binaries (same as
@@
 \begin{equation}
-    \Gamma_i(r) = \Lambda(r\p) \cdot \hat{\delta}(r-r\p),~~{\rm for}
+    \Gamma_i(r) = \Lambda(r\p) \, \hat{\delta}(r-r\p),~~{\rm for}
     \ i\in\{0,1,2\},
@@
 \begin{equation}
-    {N_\star(r\a)\over{1+\mu}}\cdot {n_{\rm b}\over n_{\rm s}}
+    {N_\star(r\a)\over{1+\mu}} \, {n_{\rm b}\over n_{\rm s}}
     \left[{L_{\rm tot}(M\a, q) \over L(M\a)}\right]^{3/2}
@@
     \notag
-    \Gamma\a(r\a,M\a) &= \frac{1}{1+\mu} \cdot
+    \Gamma\a(r\a,M\a) &= \frac{1}{1+\mu}
     \left\{ \Gamma_0(r\a, M\a)+ 
@@
     &= 
-    {1\over 1+\mu} \cdot
+    {1\over 1+\mu}
     \left[
-       \Gamma_0(r\a, M\a)\phantom{\tilde \Gamma}\right.&\\
-       &\left.+\mu\cdot
+       \Gamma_0(r\a, M\a) \phantom{\frac{1}{1}}
+       \right.&\\
+       &\quad\quad \left.+\mu
        \left\langle
-       \mathcal{D}_1\cdot\Gamma_1\left(\mathcal{D}_1r\a, M\a\right)
+       \mathcal{D}_1\Gamma_1\left(\mathcal{D}_1r\a, M\a\right)
        +
-       {q \mathcal{D}_2}\cdot\Gamma_2\left(\mathcal{D}_2r\a,
+       {q \mathcal{D}_2}\Gamma_2\left(\mathcal{D}_2r\a,
        qM\a\right) \cdot {R(qM\a) \over R(M\a)}q^{-1/3}
@@
 \begin{equation}
-    \Gamma_i(r,M) = Z_i \cdot \frac{r^\gamma}{\mathcal{N}_r} \cdot
+    \Gamma_i(r,M) = Z_i \, \frac{r^\gamma}{\mathcal{N}_r} \,
     \frac{M^\zeta}{\mathcal{N}_M},
@@
     \caption{
-        {\it Left:} apparent rate density ($\Gamma\a$) and single star
-        rate density ($\Gamma_0$). {\it Right:} apparent occurrence
+        {\it Left:} apparent rate density ($\Gamma\a$) and rate density for 
+        single stars ($\Gamma_0$). {\it Right:} apparent occurrence
         rate ($\Lambda\a$) and single star occurrence rate
@@
 \texttt{matplotlib}~\citep{hunter_matplotlib_2007}, 
-\texttt{pandas}~\citep{mckinney-proc-scipy-2010}
+\texttt{pandas}~\citep{mckinney-proc-scipy-2010},
+\texttt{IPython}~\citep{perez_2007}
 }
@@
     \Gamma\a(r\a,M\a) = \frac{n_{\rm det}(r\a,M\a)}{N_\star(r\a,M\a)}
-    \cdot \frac{1}{p_{\rm tra}(M\a)},
+    \, \frac{1}{p_{\rm tra}(M\a)},
 \label{eq:apparent_rate_density}
@@
     \mathcal{N}_\star^i(r\a,M\a; r,M)
-    \cdot\Gamma_i(r,M) \cdot p_{\rm tra}(r,M),
+    \, \Gamma_i(r,M) \, p_{\rm tra}(r,M),
     \label{eq:n_det}
@@
 \begin{equation}
-    n_{\rm det}^0(r\a, M\a)=N_\star^0(r\a,M\a)\cdot \Gamma_0(r\a, 
-    M\a) \cdot p_{\rm tra}(r\a, M\a).
+    n_{\rm det}^0(r\a, M\a)=N_\star^0(r\a,M\a)\, \Gamma_0(r\a, 
+    M\a) \, p_{\rm tra}(r\a, M\a).
 \end{equation}
@@
     \delta
-    = \left[{r\over R(M\a)}\right]^2\cdot {L(M\a) \over L_{\rm tot}(M\a, q)}
-    \equiv \left[{r\over R(M\a)}\right]^2\cdot 
+    = \left[{r\over R(M\a)}\right]^2\, {L(M\a) \over L_{\rm tot}(M\a, q)}
+    \equiv \left[{r\over R(M\a)}\right]^2\, 
     \frac{1}{\mathcal{D}_1^2}
@@
 \begin{equation}
-    N_\star^0(r\a, M\a)\cdot
+    N_\star^0(r\a, M\a)\,
     {n\b\over n\s}\left[L_{\rm tot}(M\a, q) \over L(M\a)\right]^{3/2}.
@@
     &=N_\star^0(r\a, M\a)
-    \cdot {n\b\over n\s} \cdot \mathcal{D}_1^3
-    \cdot\hat{\delta} \left[r\a-\frac{r}{\mathcal{D}_1}\right]\hat{\delta}(M\a-M).
+    \, {n\b\over n\s} \, \mathcal{D}_1^3
+    \,\hat{\delta} \left(r\a-\frac{r}{\mathcal{D}_1}\right)\hat{\delta}(M\a-M).
     \label{eq:N_s_1}
@@
       \delta =
-      \left[{r\over R(qM\a)}\right]^2 \cdot
+      \left[{r\over R(qM\a)}\right]^2 \,
       {L(qM\a) \over L_{\rm tot}(M\a, q)}
       \equiv
-      \left[{r\over R(M\a)}\right]^2\cdot
+      \left[{r\over R(M\a)}\right]^2\,
       \frac{1}{\mathcal{D}_2^2},
@@
     \mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
-    =N_\star^0(r\a, M\a) \cdot \frac{n\b}{n\s} 
-    \cdot \mathcal{D}_1^3
-    \cdot \hat{\delta} \left[r\a-\frac{r}{\mathcal{D}_2}\right]
+    =N_\star^0(r\a, M\a) \, \frac{n\b}{n\s} 
+    \, \mathcal{D}_1^3
+    \, \hat{\delta} \left(r\a-\frac{r}{\mathcal{D}_2}\right)
     \hat{\delta} \left(M\a-{M\over q}\right).
@@
     &=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_\star^0(r\a, M\a; r, M)
-    \cdot\Gamma_0(r, M) \cdot p_{\rm tra}(M)\\
-    &=N_\star^0(r\a, M\a)\cdot\Gamma_0(r\a, M\a) \cdot p_{\rm 
+    \,\Gamma_0(r, M) \, p_{\rm tra}(M)\\
+    &=N_\star^0(r\a, M\a)\,\Gamma_0(r\a, M\a) \, p_{\rm 
         tra}(M\a),
@@
     &=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_\star^1(r\a, M\a; r, M)
-    \cdot\Gamma_1(r, M) \cdot p_{\rm tra}(M)\\
-    &=N_\star^0(r\a, M\a)\cdot p_{\rm tra}(M\a) \cdot
+    \,\Gamma_1(r, M) \, p_{\rm tra}(M)\\
+    &=N_\star^0(r\a, M\a)\, p_{\rm tra}(M\a) \,
     \frac{n\b}{n\s}
     \int \mathrm{d}q \,
-         \mathcal{D}_1^3 f(q)\cdot
+         \mathcal{D}_1^3 f(q)\,
          \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a, M\a).
@@
     &=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_\star^2(r\a, M\a; r, M)
-    \cdot\Gamma_2(r, M) \cdot p_{\rm tra}(M)\\
+    \,\Gamma_2(r, M) \, p_{\rm tra}(M)\\
     &=
-    N_\star^0(r\a, M\a)\cdot \frac{n\b}{n\s}
-    +\int {\rm d}q\, 
-         \mathcal{D}_1^3 f(q)\cdot q \mathcal{D}_2
-         \Gamma_2(\mathcal{D}_2r\a, qM\a)\cdot
+    N_\star^0(r\a, M\a)\, \frac{n\b}{n\s}
+    \int {\rm d}q\, 
+         \mathcal{D}_1^3 f(q)\, q \mathcal{D}_2
+         \Gamma_2(\mathcal{D}_2r\a, qM\a)\,
          \frac{R(qM\a)}{R(M\a)} q^{-1/3}.
@@
     \Gamma\a(r\a,M\a) &= 
-    \frac{1}{N_\star(r\a,M\a) p_{\rm tra}(r\a,M\a)} \cdot
+    \frac{1}{N_\star(r\a,M\a) p_{\rm tra}(r\a,M\a)} \,
     \sum_i n_{\rm det}^i (r\a,M\a),
@@
     \notag
-    \Gamma\a(r\a,M\a) &= \frac{1}{1+\mu} \cdot
+    \Gamma\a(r\a,M\a) &= \frac{1}{1+\mu} \,
     \left\{ \Gamma_0(r\a, M\a)+ 
@@
     \left[ \int_0^1 \mathrm{d}q \,
-           \mathcal{D}_1^3 f(q)\cdot
+           \mathcal{D}_1^3 f(q)\,
            \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a, M\a)\,
@@
     +\int_0^1 {\rm d}q\, 
-         \mathcal{D}_1^3 f(q)\cdot q \mathcal{D}_2
-         \Gamma_2(\mathcal{D}_2r\a, qM\a)\cdot
+         \mathcal{D}_1^3 f(q)\, q \mathcal{D}_2
+         \Gamma_2(\mathcal{D}_2r\a, qM\a)\,
          \frac{R(qM\a)}{R(M\a)} q^{-1/3}

### 2018-02-19 src/plot_occrates_vs_radius.py

@@ -92,7 +92,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
         #ax.step(xvals, ytrueselected, where='post', label='true (selected)',
         #        c=colors[1])
 
-        ax.step(xvals, ytruesingle, where='post', label='$\Lambda_0(r)$',
+        ax.step(xvals, ytruesingle, where='post', label='$\Lambda(r)$',
                 linestyle='-', c=colors[1])
 
     elif not standardlines:
@@ -115,7 +115,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
     else:
         ax.legend(loc='best',fontsize='medium')
 
-    ax.set_xlabel('planet radius [$r_\oplus$]', fontsize='large')
+    ax.set_xlabel('planet radius [$r_{\mathrm p}$]', fontsize='large')
 
     ax.set_ylabel('number of planets per star', fontsize='large')
 

### 2018-02-19 src/check_companion_fractions.py
remove outdated plots (cleaning up repo)

@@ -1,20 +1,0 @@
-from __future__ import division
-import numpy as np
-from scipy.integrate import trapz
-
-α = 3.5
-β = 0
-δ = -2.92
-
-q = np.arange(0,1+1e-6,1e-6)
-
-A = (1 + q**α)**(-1/2)
-
-int1 = trapz( q**β * A**(-δ-4), q )
-int2 = trapz( q**β * A**(-4), q )
-
-BF = 0.44
-
-frac = (1 + (BF/(1-BF)*int1)**(-1)) / (1 + (BF/(1-BF)*int2)**(-1) )
-
-print(frac)

### 2018-02-19 src/failed_model_3_test.py

@@ -1,63 +1,0 @@
-'''
-This is a test I wrote that fails because my analytics are wrong.
-
-It would be ideal if we could compare the analytic and numeric (apparent)
-Λ_a(r_a) distributions, above r_a ~= 2r_\oplus and below r_pu/sqrt(2).  By
-analogy with the fixed planet radius, variable mass ratio model -- this might
-seemingly work.  However if you think about it more closely, it won't. You can
-derive an analytic result for the f(r)~r^δ case.  But numerically, we have
-finite edge effects. A r=20rearth planet can be diluted to much below
-20rearth/sqrt(2), if it orbits a secondary.  So to make a good analytic
-prediction, you need to include the finite edge effects.  This might be
-possible, but it'd certainly be painful.  We've validated enough other cases
-that the numerics should be trusted (provided they're tested for a variety of
-upper cutoffs on the radius distribution).
-'''
-
-del vals_num, vals_anal
-Λ_a_num = np.array(inferred_dict['Λ'])
-
-q_grid = np.arange(1e-6, 1+1e-6, 1e-6)
-prob_ml_q = q_grid**β * (1+q_grid**α)**(3/2)
-norm_q = trapz(prob_ml_q, q_grid)
-# Derived 2017/11/30.3 (Eqs 70-72 in email to JNW and KM 2017/11/30).
-I_1 = Λ_1/(norm_q*norm_r)*r_a_anal**δ * trapz(
-        q_grid**β * (1+q_grid**α)**(δ/2 + 2), q_grid
-        )
-I_2 = Λ_2/(norm_q*norm_r)*r_a_anal**δ * trapz(
-        q_grid**(β+δ+8/3) * (1+q_grid**α)**(3/2) * (1+q_grid**(-α))**((δ+1)/2),
-        q_grid
-        )
-Γ_0 = Λ_0 * r_a_anal**δ / norm_r
-
-Λ_a_anal = 1/(1+μ) * (
-        Γ_0 + μ * (I_1+I_2)
-        )
-
-vals_num = Λ_a_num[(r_a_anal>3) & (r_a_anal<=r_pu/2**(1/2))]
-
-assert np.allclose(np.diff(inferred_dict['r']),
-                   np.diff(inferred_dict['r'])[0])
-bin_width = np.diff(true_dict['r'])[0]
-
-vals_anal = bin_width * Λ_a_anal[(r_a_anal>3) & (r_a_anal<=r_pu/2**(1/2))]
-
-if debugging:
[…]

### 2018-02-19 src/plot_HJ_correction_vs_Ztwo.py

@@ -1,94 +1,0 @@
-# -*- coding: utf-8 -*-
-'''
-Given that hot Jupiters are thought to be less common around less-massive
-stars, it would be more sensible to consider Λ_2 < Λ_0 , while letting single
-stars and primaries host planets at the same rate.
-
-This plots the rates as a function of Λ_2 /Λ_0.
-'''
-from __future__ import division, print_function
-import matplotlib as mpl
-mpl.use('pgf')
-pgf_with_custom_preamble = {
-    'pgf.texsystem': 'pdflatex', # xelatex is default; i don't have it
-    'font.family': 'serif', # use serif/main font for text elements
-    'text.usetex': True,    # use inline math for ticks
-    'pgf.rcfonts': False,   # don't setup fonts from rc parameters
-    'pgf.preamble': [
-        '\\usepackage{amsmath}',
-        '\\usepackage{amssymb}'
-        ]
-    }
-mpl.rcParams.update(pgf_with_custom_preamble)
-
-import matplotlib.pyplot as plt
-import numpy as np, pandas as pd
-
-if __name__ == '__main__':
-
-    model_number = 3
-
-    Λ_2_arr = np.arange(0, 0.5+0.05, 0.05)
-
-    Λ_HJ_true_arr, Λ_HJ_inferred_arr, Λ_HJ_true_primary_arr = [], [], []
-
-    # compute the HJ correction factors for each Λ_2
-    for Λ_2 in Λ_2_arr:
-
-        savdir = '../data/numerics/'
-        fname = 'results_model_{:d}_Lambda2_{:.2f}.out'.format(
-                model_number, Λ_2)
-        df = pd.read_csv(savdir+fname)
-
-        lower_bound = 8
-        inds = df['bin_left'] > lower_bound
-        Λ_HJ_true = np.sum(df[inds]['true_Λ'])
-        Λ_HJ_inferred = np.sum(df[inds]['inferred_Λ'])
-        Λ_HJ_true_primary = np.sum(df[inds]['true_primary_Λ'])
-
-        Λ_HJ_true_arr.append(float(Λ_HJ_true))
-        Λ_HJ_inferred_arr.append(float(Λ_HJ_inferred))
-        Λ_HJ_true_primary_arr.append(float(Λ_HJ_true_primary))
-
-    Λ_HJ_true_arr = np.array(Λ_HJ_true_arr)
-    Λ_HJ_inferred_arr = np.array(Λ_HJ_inferred_arr)
[…]

### 2018-02-19 src/plot_KOI_radii.py

@@ -1,10 +1,0 @@
-import pandas as pd, numpy as np
-import matplotlib.pyplot as plt
-
-#from NASA exoplanet archive, only KOIs with "CONFIRMED" designation
-df = pd.read_csv('../data/confirmed_KOI_radii.csv', comment='#')
-
-plt.hist(np.log10(df['koi_prad']), bins=20)
-plt.savefig('../results/KOI_radii_log.pdf', bbox_inches='tight')
-
-print(len(df[df['koi_prad']>2])/len(df))

### 2018-02-19 src/plot_errcases_rate_densities_vs_radius.py

@@ -1,235 +1,0 @@
-'''
-OUTDATED: Dec 5, 2017, I opted against plotting/showing "error cases" because
-they're just confusing for no good reason.
-
-first, for models 1,2, 3:
->>> python numerical_models.py
-then:
->>> python plot_absolute_rate_densities_vs_radius.py
-
-makes plots for paper
-'''
-# -*- coding: utf-8 -*-
-from __future__ import division, print_function
-import matplotlib as mpl
-mpl.use('pgf')
-pgf_with_custom_preamble = {
-    'pgf.texsystem': 'pdflatex', # xelatex is default; i don't have it
-    'font.family': 'serif', # use serif/main font for text elements
-    'text.usetex': True,    # use inline math for ticks
-    'pgf.rcfonts': False,   # don't setup fonts from rc parameters
-    'pgf.preamble': [
-        '\\usepackage{amsmath}',
-        '\\usepackage{amssymb}'
-        ]
-    }
-mpl.rcParams.update(pgf_with_custom_preamble)
-
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-
-from brokenaxes import brokenaxes
-
-def make_plot(model_number, logx=None, logy=None, withtext=None,
-        stdout=False, brokenx=None, Λ_2=None, xcut=None):
-
-    # Make summary plot
-    if not brokenx:
-        f, ax = plt.subplots(figsize=(4,4))
-    else:
-        #cf https://github.com/bendichter/brokenaxes/blob/master/brokenaxes.py
-        f = plt.figure(figsize=(4,4))
-        bigax = brokenaxes(
-                xlims=((0.695, .715), (.985, 1.005)),
-                d=0.02,
-                tilt=85,
-                hspace=.05,
-                despine=True)
-        ax=bigax
-
-    if isinstance(Λ_2,float) or isinstance(Λ_2,int):
-        fname = '../data/numerics/results_model_{:d}_Lambda2_{:.2f}.out'.format(
-                model_number, Λ_2)
-    else:
-        fname = '../data/results_model_'+repr(model_number)+'.out'
-
-    df = pd.read_csv(fname)
-
-    if model_number == 3 or model_number == 4:
-        xvals = np.append(0, df['bin_left'])
-        ytrue = np.append(0, df['true_Λ'])
-        yinferred = np.append(0, df['inferred_Λ'])
-    elif model_number == 1 or model_number == 2:
-        xvals = np.append(df['bin_left'],[1,1.1])
[…]

### 2018-02-19 src/plot_print_earth_rate_analog.py

@@ -1,97 +1,0 @@
-'''
-What is the rate correction for earth analogs in Model #3?
-
-Print the result.
-
-Make the plot of rate as a function of Λ_2/Λ_0 as well.
-'''
-# -*- coding: utf-8 -*-
-from __future__ import division, print_function
-import matplotlib as mpl
-mpl.use('pgf')
-pgf_with_custom_preamble = {
-    'pgf.texsystem': 'pdflatex', # xelatex is default; i don't have it
-    'font.family': 'serif', # use serif/main font for text elements
-    'text.usetex': True,    # use inline math for ticks
-    'pgf.rcfonts': False,   # don't setup fonts from rc parameters
-    'pgf.preamble': [
-        '\\usepackage{amsmath}',
-        '\\usepackage{amssymb}'
-        ]
-    }
-mpl.rcParams.update(pgf_with_custom_preamble)
-
-import matplotlib.pyplot as plt
-
-import numpy as np, pandas as pd
-
-if __name__ == '__main__':
-
-    model_number = 3
-
-    Λ_0 = 0.5
-    Λ_2_arr = np.arange(0, 0.5+0.05, 0.05)
-
-    Λ_earth_true_arr, Λ_earth_inferred_arr, Λ_earth_true_primary_arr = [], [], []
-
-    # compute the rate for each Λ_2
-    for Λ_2 in Λ_2_arr:
-
-        savdir = '../data/numerics/'
-        fname = 'results_model_{:d}_Lambda2_{:.2f}.out'.format(
-                model_number, Λ_2)
-        df = pd.read_csv(savdir+fname)
-
-        for ix, bl in enumerate([0.5, 1.0]):
-
-            inds = (df['bin_left'] == bl)
-
-            Λ_earth_true = df[inds]['true_Λ']
-            Λ_earth_inferred = df[inds]['inferred_Λ']
-            Λ_earth_true_primary = df[inds]['true_primary_Λ']
-
-            Λ_earth_true_arr.append(float(Λ_earth_true))
-            Λ_earth_inferred_arr.append(float(Λ_earth_inferred))
-            Λ_earth_true_primary_arr.append(float(Λ_earth_true_primary))
-
-    Λ_earth_true_arr = np.array(Λ_earth_true_arr)
-    Λ_earth_inferred_arr = np.array(Λ_earth_inferred_arr)
[…]

### 2018-02-19 src/numerical_models.py
remove outdated models in Monte Carlo surveys

@@ -1,20 +1,14 @@
 # -*- coding: utf-8 -*-
 '''
-See README.md for full description.
+See monte_carlo_readme.md for a description of what this does.
 
 The models are as follows:
 Model #1: twin binary, same planet
 Model #2: varying q, same planet
-Model #3: varying q, varying r
-Model #4: varying q, r with a gap
-Model #5: twin binary, varying r
 
 Example usage, for each model type:
 >>> python numerical_models.py --modelnumber 1 --ZsubTwo 0.5 --binaryfrac 0.1
 >>> python numerical_models.py --modelnumber 2 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
->>> python numerical_models.py --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
->>> python numerical_models.py --modelnumber 4 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
->>> python numerical_models.py --modelnumber 5 --ZsubTwo 0.5 --binaryfrac 0.1 --upperradiuscutoff 22.5
 
 Alternatively, use a wrapper like `run_numerical_models.py`.
 '''
@@ -40,7 +34,7 @@ def check_inputs(γ, Z_2, model_number, BF, r_pu):
         # File names assume 2 digits of precision for Z_2.
         raise NotImplementedError
 
-    if model_number > 5 or model_number < 1:
+    if model_number > 2 or model_number < 1:
         raise NotImplementedError
 
     if not (BF > 0):
@@ -86,11 +80,11 @@ def make_stellar_population(quickrun, model_number, BF, α, β, γ, δ):
     B = BF / (1-BF) # prefactor in definition of μ
 
     # Get number of selected primaries.
-    if model_number == 1 or model_number == 5:
+    if model_number == 1:
         q = 1
         μ = B * (1 + q**α)**(3/2)
         N_1 = int(N_0 * μ) # number of selected primaries
-    elif model_number == 2 or model_number == 3 or model_number == 4:
+    elif model_number == 2:
         integral = 0.484174086070513 # 17/10/14.2 analytic result
         N_d = N_0 * B * (2**(3/2) - 3*integral)
         N_1 = int(N_d) # number of primaries = number of double star systems
@@ -104,12 +98,12 @@ def make_stellar_population(quickrun, model_number, BF, α, β, γ, δ):
         ), ignore_index=True )
 
[…]

### 2018-02-19 src/plot_integrated_rate_densities_vs_radius.py
cleanup plot script headers

@@ -1,18 +1,8 @@
 # -*- coding: utf-8 -*-
 from __future__ import division, print_function
-import matplotlib as mpl
-mpl.use('pgf')
-pgf_with_custom_preamble = {
-    'pgf.texsystem': 'pdflatex', # xelatex is default; i don't have it
-    'font.family': 'serif', # use serif/main font for text elements
-    'text.usetex': True,    # use inline math for ticks
-    'pgf.rcfonts': False,   # don't setup fonts from rc parameters
-    'pgf.preamble': [
-        '\\usepackage{amsmath}',
-        '\\usepackage{amssymb}'
-        ]
-    }
-mpl.rcParams.update(pgf_with_custom_preamble)
+from matplotlib import rc
+rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('text', usetex=True)
 
 import matplotlib.pyplot as plt, pandas as pd, numpy as np
 from scipy.integrate import trapz

### 2018-02-19 src/plot_mass_ratio_distribution.py

@@ -1,8 +1,8 @@
+# -*- coding: utf-8 -*-
 '''
 plot the mass ratio distribution for a volume-limited sample, and a
 magnitude-limited sample.
 '''
-# -*- coding: utf-8 -*-
 from __future__ import division, print_function
 from matplotlib import rc
 rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})

### 2018-02-19 src/plot_occrates_vs_radius.py

@@ -1,3 +1,4 @@
+# -*- coding: utf-8 -*-
 '''
 This script plots the output of the Monte Carlo simulation.
 
@@ -8,21 +9,10 @@ then:
 
 makes plot for Model # 1 of paper
 '''
-# -*- coding: utf-8 -*-
 from __future__ import division, print_function
-import matplotlib as mpl
-mpl.use('pgf')
-pgf_with_custom_preamble = {
-    'pgf.texsystem': 'pdflatex', # xelatex is default; i don't have it
-    'font.family': 'serif', # use serif/main font for text elements
-    'text.usetex': True,    # use inline math for ticks
-    'pgf.rcfonts': False,   # don't setup fonts from rc parameters
-    'pgf.preamble': [
-        '\\usepackage{amsmath}',
-        '\\usepackage{amssymb}'
-        ]
-    }
-mpl.rcParams.update(pgf_with_custom_preamble)
+from matplotlib import rc
+rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('text', usetex=True)
 
 import matplotlib.pyplot as plt
 import pandas as pd

### 2018-02-19 src/plot_visualize_volumes.py

@@ -1,8 +1,8 @@
+# -*- coding: utf-8 -*-
 '''
 visualize the selected and searchable volumes for single stars and twin
 binaries.
 '''
-# -*- coding: utf-8 -*-
 from __future__ import division, print_function
 from matplotlib import rc
 rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})

### 2018-02-19 src/run_monte_carlo_models.sh
clean up run_monte_carlo_models.sh

@@ -1,16 +1,3 @@
 # "Nominal" models (this just means I arbitrarily decided Z_2 = 0.5)
 python numerical_models.py --modelnumber 1 --ZsubTwo 0.5 --binaryfrac 0.1
 python numerical_models.py --modelnumber 2 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
-python numerical_models.py --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
-python numerical_models.py --modelnumber 4 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
-python numerical_models.py --modelnumber 5 --ZsubTwo 0.5 --binaryfrac 0.1 --upperradiuscutoff 22.5
-
-# Check vs Z_2
-python numerical_models.py --modelnumber 3 --ZsubTwo 0.0 --binaryfrac 0.44 --upperradiuscutoff 22.5
-python numerical_models.py --modelnumber 3 --ZsubTwo 0.25 --binaryfrac 0.44 --upperradiuscutoff 22.5
-
-# Check vs upper radius cutoff
-python numerical_models.py --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 15.0
-python numerical_models.py --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 17.5
-python numerical_models.py --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 20.0
-python numerical_models.py --modelnumber 3 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 25.0

### 2018-02-19 src/integrate_for_apparent_rate_density.py
update docstrings and comments

@@ -26,7 +26,7 @@ optional arguments:
 
 The models are as follows:
 /Model #1: twin binary, same planet
-XModel #2: varying q, same planet (WARNING: not implemented)
+XModel #2: varying q, same planet (NOTE: not implemented)
 /Model #3: varying q, powerlaw+const r
 /Model #4: varying q, r with a gap
 /Model #5: twin binary, powerlaw r
@@ -218,8 +218,9 @@ def run_unit_tests(
     elif model_number == 2:
 
         print('analytic comparison not yet working')
-        import IPython; IPython.embed()
         raise NotImplementedError
+        #NOTE: this is because there is a funky derivative that I never got
+        #around to working out numerically here.
 
         q_grid = np.arange(1e-6, 1+1e-6, 1e-6)
         prob_vl_q = q_grid**β
@@ -393,6 +394,9 @@ def run_unit_tests(
 
 
 def get_mu(BF, model_number):
+    # mu is defined as (number of searchable binary systems)/(number of
+    # searchable single systems). Since each of these scale as (transit
+    # depth)^3, it is independent of apparent planet radius.
 
     if model_number in [1,5]:
         μ = BF/(1-BF) * 2**(3/2)
@@ -540,6 +544,7 @@ def get_apparent_radius_grid(model_number, slowrun=False):
 
 
 def get_q_grid(model_number):
+    # grid of binary mass ratios
 
     if model_number in [1,5]:
         q = np.arange(0.1,1+0.1,0.1)
@@ -562,6 +567,7 @@ def get_apparent_rate_density(r_a_grid, M_a_grid, model_number):
 
     gaussianparams = None if model_number != 7 else [14,2]
 
+    # Get the radius normalization constant, N_r (\mathcal{N}_r in the text)
     if model_number in [5,6]:
         norm_r = trapz(r_a_grid**δ, r_a_grid)
     elif model_number == 3:
@@ -581,6 +587,8 @@ def get_apparent_rate_density(r_a_grid, M_a_grid, model_number):
         prob_r = np.exp(- (r_grid-mean)**2 / (2 * sigma**2) )
         norm_r = trapz(prob_r, r_grid)
 
+    # Compute the dilution factors, A(q) \equiv 1/\mathcal{D}_1, and likewise
+    # for the secondaries B(q) \equiv 1/\mathcal{D}_2.
     A_q = A(q)
     B_q = B(q)
 
[…]

### 2018-02-19 src/model1_numbers.py

@@ -1,3 +1,7 @@
+'''
+calculate the ratios of apparent to true occurrence rates for the
+order-of-magnitude toy model.
+'''
 BF = 0.05
 nb_by_ns = 1 / ( (1/BF) - 1 )
 

### 2018-02-23 paper/main.tex
add git commit
jnw intro edits

@@
 \shortauthors{Bouma, Masuda, Winn}
-\shorttitle{Binarity's Biases}
+\shorttitle{Binarity and planet occurrence rates}
 
@@
 %
-
 Wide-field surveys for transiting planets, such as the NASA {\it
-Kepler} and {\it TESS} missions, are usually conducted without knowing
-which stars are binaries. Unresolved and unrecognized binary stars
-give rise to systematic errors in planet occurrence rates, including
-misclassified planets and miscounts in the number of searched stars.
-The individual errors can have different signs, making it difficult to
-anticipate the net effect on inferred occurrence rates. Here we use
-simplified models of signal-to-noise limited transit surveys to try
-and clarify the situation. We derive a formula for the apparent
-occurrence rate density measured by an observer who falsely assumes
-all stars are single. The formula depends on the binary fraction; the
-mass function of the secondary stars; and the true occurrence of
-planets around primaries, secondaries, and single stars. It also takes
-into account the Malmquist bias by which binaries are over-represented
-in flux-limited samples. Application of the formula to an idealized
-{\it Kepler}-like survey shows that for planets larger than
-$2r_\oplus$, the net systematic error is of order 10\%.  One
-consequence is that unrecognized binaries cannot account for the
-apparent discrepancy between hot Jupiter occurrence rates measured by
-transit and RV surveys.  For smaller planets the errors are
-potentially larger: the occurrence of Earth-sized planets could be
-overestimated by as much as a factor of two. We also show that if
-high-resolution imaging reveals a transit host star to be a binary,
-the planet is usually more likely to orbit the primary star than the
-secondary star.
+  Kepler} and {\it TESS} missions, are usually conducted without
+knowing which stars have binary companions. Unresolved and
+unrecognized binaries give rise to systematic errors in planet
+occurrence rates, including misclassified planets and mistakes in
+completeness corrections.  The individual errors can have different
+signs, making it difficult to anticipate the net effect on inferred
+occurrence rates. Here we use simplified models of signal-to-noise
+limited transit surveys to try and clarify the situation. We derive a
+formula for the apparent occurrence rate density measured by an
+observer who falsely assumes all stars are single. The formula depends
+on the binary fraction; the mass function of the secondary stars; and
+the true occurrence of planets around primaries, secondaries, and
+single stars. It also takes into account the Malmquist bias by which
+binaries are over-represented in flux-limited samples. Application of
+the formula to an idealized {\it Kepler}-like survey shows that for
+planets larger than 2\,$R_\oplus$, the net systematic error is of
+order 5\%.  In particular, unrecognized binaries are unlikely to be
+the reason for the apparent discrepancies between hot Jupiter
+occurrence rates measured in different surveys.  For smaller planets
+the size the errors are potentially larger: the occurrence of
+Earth-sized planets could be overestimated by as much as 50\%. We also
+show that whenever high-resolution imaging reveals a transit host star
+to be a binary, the planet is usually more likely to orbit the primary
+star than the secondary star.
 %
@@
 formation, designing the next generation of planet-finding surveys,
-and simply satisfying our curiosity about other worlds.  One method
-for measuring occurrence rates is to monitor the brightnesses of many
-stars over a wide field, seeking evidence for planetary transits.
-Measuring occurrence rates using this method was the highest priority
-of the NASA {\it Kepler} mission.  Great strides have been made in the
-analysis of {\it Kepler} data, including progress towards measuring
-the fraction of Sun-like stars that harbor Earth-like planets~\citep{
+and simply satisfying our curiosity.  One method for measuring
+occurrence rates is to monitor the brightnesses of many stars over a
+wide field, seeking evidence for planetary transits.  This was the
+highest priority of the NASA {\it Kepler} mission.  Great strides have
+been made in the analysis of {\it Kepler} data, including progress
+towards measuring the fraction of Sun-like stars that harbor
+Earth-like planets~\citep{
   youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
-  foreman-mackey_exoplanet_2014,burke_terrestrial_2015}
-
-A lingering concern in occurrence rate studies is that in most cases,
-investigators have assumed that all of the sources of light that were
-monitored are single stars~\citep[\textit{e.g.},][]{
+  foreman-mackey_exoplanet_2014,burke_terrestrial_2015}.
+
+A lingering concern about these studies is that in most cases,
+investigators have assumed that all of the targets in the survey
+are single stars~\citep[\textit{e.g.},][]{
   howard_planet_2012,fressin_false_2013,
   dressing_occurrence_2015,burke_terrestrial_2015}. 
-In reality, many of the point sources seen in a transit survey are
-unresolved multiple-star systems, especially binaries.  Unrecognized
+In reality, many of the sources that are monitored in a transit survey are
+unresolved multiple-star systems, mainly binaries.  Unrecognized
 binaries cause numerous systematic errors in the planetary occurrence
@@
 signals harder to detect and lowers the number of detections.  On the
-other hand, in a binary there are two opportunities to detect
+other hand, a binary system presents two opportunities to detect
 transiting planets, which could increase the overall number of
@@
 At the outset of this study it was not clear to us whether the neglect
-of binaries was a serious issue at all, or even whether the net effect
-of all the errors is positive or negative.  The goals of this study
-were to provide a framework for dealing with these issues, and to
-calculate a leading-order estimate for the net systematic effects.  In
-this spirit, our models are idealized and analytic, and we do not
-attempt a detailed correction of the results from {\it Kepler} or any
-other real transit survey.
+of binaries is a serious problem, or even whether the net effect of
+the errors is positive or negative.  The goals of this study were to
+provide a framework for dealing with these issues, and to gauge at
+least the order of magnitude of the systematic errors.  In this
+spirit, our models are idealized.  We do not attempt a detailed
+correction of the results from {\it Kepler} or any other real transit
+survey.  We took inspiration from the insightful analytic model for
+transit surveys by~\citet{pepper_using_2003}.
 
@@
 stellar and planetary populations.  We use this formula in
-Section~\ref{sec:more_complicated} to explore more complicated but
-nevertheless still analytic models.  In Section~\ref{sec:discussion}
-we discuss the errors due to unrecognized binaries for specific cases
+Section~\ref{sec:more_complicated} to explore more realistic models.
+We discuss the errors due to unrecognized binaries for specific cases
 of current interest: the occurrence of Earth-like planets; the
-apparent discrepancy between hot Jupiter occurrence rates in different
-surveys; and the shape of the ``evaporation valley'' in the planet
-radius distribution that was brought to light by
-\citet{fulton_california-_2017}.  We review all the results in
-Section~\ref{sec:conclusion}.
+apparent discrepancy between hot Jupiter occurrence rates measured in
+different surveys; and the shape of the ``evaporation valley'' in the
+planet radius distribution that was brought to light by
+\citet{fulton_california-_2017}.  We summarize and discuss all the
+results in Section~\ref{sec:discussion}.
 
@@
 program. We refer the interested reader to our online
-implementation\footnote{\url{https://github.com/lgbouma/binary_biases}}.
+implementation\footnote{\url{https://github.com/lgbouma/binary_biases},
+commit \texttt{6cb920c}}.
 The output, shown in Figure~\ref{fig:occ_rate_model_3_log}, is

### 2018-02-23 paper/main.tex
jnw understanding errors edits

@@
 
-Imagine a group of astronomers that wants to measure the mean number of
-planets of a certain type per star of a certain type.  They perform a
-wide-field photometric search for planets that transit, and discover
-all for which
+Imagine that a group of astronomers wants to measure the mean number
+of planets per star.  They are particularly interested in planets of
+radius $r$ and stars of mass $M$ and radius $R$.  They obtain a time
+series of images of some region of the sky, and prepare light curves
+for a large number of unresolved sources.  Then they search these
+light curves for transit signals and detect all the signals for which
 \begin{equation}
@@
 \end{equation}
-Here the signal S is the observed transit depth $\delta$, in units of
-relative flux.  The noise N is the uncertainty in the determination of
-the flux ratio of the star inside and outside of transits.  The
-minimum signal-to-noise for detection, $({\rm S}/{\rm N})_{\rm min}$,
-depends on the properties of the telescope.  We will assume throughout
-this paper that the photometric uncertainty scales as the inverse
-square root of the number of photons collected from the source, {\it
-i.e.}, the dependence on stellar properties is $\sigma \propto (L_{\rm
-tot}/d^2)^{-1/2}$, where $L_{\rm tot}$ is the total luminosity of the
-stellar system and $d$ is its distance from Earth.  The observed
-signal amplitude $\delta$ depends on the fraction of the total
-luminosity that comes from the planet-hosting star, since light from
-unresolved stellar companions is not affected by the planet's transit.
+Here the signal, $\delta$, is the observed transit depth, the
+dimensionless fraction by which the total light fades during transits.
+Note that although $\delta$ is often equated with $(r/R)^2$, this is
+not true when the host star is a member of an unresolved binary.  In
+those cases, $\delta$ is smaller than $(r/R)^2$ because of the
+constant light from the binary companion, an effect often called the
+``dilution'' of the transit signal.  The noise, $\sigma$, is the
+fractional uncertainty in the determination of the flux of the source,
+which may include multiple stars that are blended together.  The
+threshold signal-to-noise ratio depends on the desired level of
+confidence that the signal is real.
 % The transit duration also affects detectability, but we omit it in
@@
 
-The astronomers analyze their data assuming that all stars are
-single.  In particular they do not have accurate enough parallaxes to
-tell that some of the stars are apparently overluminous.  They want to
-compute the number of planets with size $r$ per star of mass $M$.  If
-the total number of stars for which such planets could be detected
-($N_\star$) and the number of detected planets ($N_{\rm det}$) are
-both large, then the astronomers' estimate for the occurrence rate
-($\Lambda$) is simply
+The astronomers analyze their data assuming that all the sources are
+single stars.  In particular they do not have accurate enough
+parallaxes to tell that some of the stars appear to be overluminous.
+They count the number $N_{\rm det}$ of transit signals that appear to
+be produced by the desired type of planet around the desired type of
+star.  They also count the number $N_\star$ of ``searchable stars'' in
+their survey, i.e., the number of stars of the desired type that are
+bright enough to have allowed for the detection of a transit signal
+with amplitude $(r/R)^2$.  They estimate the occurrence rate to be
 \begin{equation}
@@
 and systematic errors in the catalogued properties of the stars.  Some
-apparent transit signals are spurious, arising from noise fluctuations
-or failures of ``detrending'' the astrophysical or instrumental
+transit-like signals are spurious, arising from noise fluctuations or
+failures of ``detrending'' the astrophysical or instrumental
 variations in the photometric signal.  Poor angular resolution leads
@@
 
-We will focus exclusively on problems that arise from the fact that
-many stars exist in gravitationally bound binary systems.  Even with
-this narrow focus, there are numerous sources of error.  All three of
-the quantities in Equation~\ref{eq:occ_rate_simple} are subject to
-observational bias:
+Here, though, we will focus exclusively on problems that arise from
+the fact that many stars exist in gravitationally bound binary
+systems.  We will also focus on the errors in planet occurrence as a
+function of radius, rather than orbital period. This is because when
+more than one transit is detected (as is usually required by the
+surveyors), the orbital periods can be measured without ambiguity
+regardless of whether the host star is single or one member of a
+binary.  Even with this narrow focus, there are numerous sources of
+error.  All three of the quantities in
+Equation~\ref{eq:occ_rate_simple} are biased:
 \begin{enumerate}
 %    
-    \item The detected planet count, $N_{\det}$, is actually the
+    \item The number of detected planets, $N_{\det}$, is actually the
       number of detected planets that {\it appear} to have size $r$,
@@
     \begin{itemize}
-        \item the planet's size will be misclassified because of the
+        \item the planet's size could be misclassified because of the
           reduction in the amplitude of the photometric signal;
@@
 %    
-    \item The apparent number of stars that were searched, $N_\star$,
-      is biased
+    \item The number of searchable stars, $N_\star$, is biased
 %    
@@
         \item toward lower values, because it does not include all of
-          the secondary stars that were searched for transiting
-          planets;
+          the secondary stars that were inadvertently searched for
+          transiting planets;
 %        
         \item toward higher values, because some of the stars that
-          appeared to be suitably small and bright to detect the
-          desired type of planet are in fact binaries for which the
-          amplitude of the photometric signal would be reduced to an
-          undetectable level.
+          appeared to be searchable are in fact binaries for which the
+          amplitude of the photometric signal would have been reduced
+          to an undetectable level.
 %        
@@
 %    
-    \item The transit probability $p_{\rm tra}$, which scales with the
-      stellar mean density as $\rho^{-1/3}$, is biased because the
-      planet-hosting star could be misclassified.
+    \item The transit probability $p_{\rm tra}$ is biased because the
+      planet-hosting star could be misclassified.  At fixed orbital
+      period, the transit probability is proportional to
+      $\rho^{-1/3}$, where $\rho$ is the stellar mean
+      density~\citep{Winn2010}.  Therefore, any errors in determining
+      the host star's mean density lead to errors in the correction
+      for the transit probability.
 %    
@@
 
-Two other problems that may arise are not represented in
-Equation~\ref{eq:occ_rate_simple}.  One is astrophysical: the true
-occurrence rate of the desired type of planet may depend on whether
-the host is a single star, the primary star of a binary, or the
-secondary star of a binary.  Such differences could be caused by the
-requirement for long-term dynamical stability, or differences in the
-planet formation process.  When the search sample includes both
-singles and binaries, the detected planets are thereby drawn from
-different occurrence 
-distributions~\citep[see][]{
+There are at least two other complications that may arise, which are
+not represented in Equation~\ref{eq:occ_rate_simple}.  The first one
+is an observational effect. Within the sample of apparently searchable
+stars, the ratio between the number of binary and single stars will
+differ from the ratio that would be found in a volume-limited sample.
+This is due to a type of Malmquist bias.  The total luminosity of a
+binary is larger than the luminosity of either the primary or
+secondary star.  This means that for transit signals of a given
+amplitude, sources that are binaries appear to be searchable at
+greater distances from the Earth.  Binaries are therefore
+over-represented in the collection of apparently searchable stars.
+
+The other complication is astrophysical: the true occurrence rate of a
+certain type of planet may depend on whether the host is a single
+star, the primary star of a binary, or the secondary star of a binary.
+The rate might also depend on the characteristics of the binary, such
+as the mass ratio and orbital period.  Such differences could be
+caused by the requirement for long-term dynamical stability, or
+differences in the planet formation process.  When the search sample
+includes both singles and binaries, the detected planets are thereby
+drawn from different occurrence distributions~\citep[see][]{
   wang_occurrence_2015,kraus_impact_2016}.
 
-The other problem is an observational effect. In the searched sample,
-the ratio between the number of binary and single stars will differ
-from that in a volume-limited sample due to a type of Malmquist bias.
-The total luminosity of a binary is larger than the luminosity of
-either the primary or secondary star.  This means that for transit
-signals of a given amplitude, the binaries are searchable at greater
-distances from the Earth.  Thus for any planet and star pair, adding a
-stellar companion both helps and hinders transit detection: the extra
-photons help by lowering the noise, and hinder by diminishing the
-observed transit depth.
-
-Planet occurrence rates are often presented as two-dimensional density
-functions in the space of planet radius and orbital period.
-Thankfully none of the errors we have enumerated lead to errors in the
-period distribution.  When more than one transit is detected (as is
-usually required by the surveyors), the orbital periods can be
-measured without ambiguity regardless of whether the host star is
-single or one member of a binary.  Hence in what follows, we focus on
-the radius distribution and assume the periods are measured without
-significant uncertainty.
-
 Given all of the confusing and opposing sources of error, we will
-proceed in stages. We start from a barebones model in which everything
+proceed in stages.  We start with a model so simple that everything
 can be written down on the back of a napkin, and build up to an
@@
 \label{sec:model_1}
+
+Since the effects of binarity are most pronounced when the two stellar
+components are similar, we begin by considering a universe in which
+all stars are identical, with mass $M$, radius $R$, and luminosity
+$L$.  Some fraction of them exist in twin binaries. All planets have
+size $r\p$.  In this scenario, stellar radii are never misclassified
+because the combined light of a binary has the same color and spectrum
+as a single star.  We further assume that planets occur around single
+stars and members of binaries at the same rate, $\Lambda(r\p)$.
+
+Our naive observers detect transiting planets with two different
+depths. Since 
+\begin{equation}
+    \delta = \left(\frac{r\p}{R}\right)^2 \frac{L}{L_{\rm tot}},
+    \label{eq:delta_obs_general} 
+\end{equation}
+one class of transit signal, with depth $(r\p/R)^2$, occurs in single
+star systems. The other class, with half the depth, occurs in twin
+binary systems, leading to apparent planet radii $\sqrt{2}$ smaller
+than the true radii.
+
+To calculate the occurrence rate of each planet type, our observers
+identify the ``stars'' from their survey that appear to have been
+searched for signals of each depth.  These transits are detected
+within a certain maximum
+distance~\citep[see][]{pepper_using_2003,pepper_searching_2005}, which
+from Equation~\ref{eq:S_N_thresh} scales as
+\begin{equation}
+  d_{\rm max} \propto \delta \, L_{\rm tot}^{1/2}.
+  \label{eq:dmax}
+\end{equation}
+Assuming that stars are uniformly distributed in space, the number of
+searchable stars $N_\star$ is proportional to
+\begin{equation}
+    N_\star \propto n \delta^3 L_{\rm tot}^{3/2},
+\label{eq:N_searchable_prop}
+\end{equation}
+where $n$ is the number per unit volume of single or binary star
+systems.
 
@@
 \end{figure}
-
-Since the effects of binarity are most pronounced when the two stellar
-components are similar, we begin by considering a universe in which
-all stars are identical, with mass $M$, radius $R$, and luminosity
-$L$.  Some fraction of them exist in twin binaries. All planets have
-size $r\p$.  In this scenario, stellar radii are never misclassified
-because the combined light of a binary has the same color and spectrum
-as a single star.  We further assume that planets occur around single
-stars and members of binaries at the same rate, $\Lambda(r\p)$.
-
-Our naive observers detect transiting planets with two different
-depths. Since 
-\begin{equation}
-    \delta = \left(\frac{r\p}{R}\right)^2 \frac{L}{L_{\rm tot}},
-    \label{eq:delta_obs_general} 
-\end{equation}
-one class of transit signal, with depth $(r\p/R)^2$, occurs in single
-star systems. The other class, with half the depth, occurs in twin
-binary systems, leading to apparent planet radii $\sqrt{2}$ smaller
-than the true radii.
-
-To calculate the occurrence rate of each planet type, our observers
-identify the ``stars'' from their survey that appear to have been
-searched for signals of each depth.  These transits are detected
-within a certain maximum
-distance~\citep[see][]{pepper_using_2003,pepper_searching_2005}, which
-from Equation~\ref{eq:S_N_thresh} scales as
-\begin{equation}
-  d_{\rm max} \propto \delta \, L_{\rm tot}^{1/2}.
-  \label{eq:dmax}
-\end{equation}
-Assuming that stars are uniformly distributed in space, the number of
-searchable stars $N_\star$ is proportional to
-\begin{equation}
-    N_\star \propto n \delta^3 L_{\rm tot}^{3/2},
-\label{eq:N_searchable_prop}
-\end{equation}
-where $n$ is the number per unit volume of single or binary star
-systems.
 

### 2018-02-23 paper/main.tex
simple model jnw edits

@@
 all stars are identical, with mass $M$, radius $R$, and luminosity
-$L$.  Some fraction of them exist in twin binaries. All planets have
-size $r\p$.  In this scenario, stellar radii are never misclassified
-because the combined light of a binary has the same color and spectrum
-as a single star.  We further assume that planets occur around single
-stars and members of binaries at the same rate, $\Lambda(r\p)$.
-
-Our naive observers detect transiting planets with two different
-depths. Since 
-\begin{equation}
-    \delta = \left(\frac{r\p}{R}\right)^2 \frac{L}{L_{\rm tot}},
+$L$.  Single stars are uniformly distributed in space with a number
+density of $n\s$ stars per cubic parsec, and binaries are uniformly
+distributed with number density $n\b$.  In this scenario, stars are
+never misclassified because the combined light of a binary has the
+same color and spectrum as a single star.  We further assume that all
+planets have the same radius, $r$, and occur around single stars and
+members of binaries at the same rate, $\Lambda(r)$.
+
+Our naive observers conduct a transit survey. To calculate the
+occurrence rate of planets with radius $r$, they count the number of
+detections of signals with amplitude $(r/R)^2$.  Then they identify
+all the sources that appear to have been searchable for a signal of
+amplitude $(r/R)^2$.  Here and throughout the rest of this paper, we
+assume that the limiting source of noise is the photon-counting noise
+from the source, i.e., $\sigma \propto 1/\sqrt{F}$, where
+where $F$ is the total flux of the source.
+Thus the observers determine the minimum $F_0$ for which detection would have been
+possible, and count the number of sources with $F_{\rm tot}>F_0$. This will
+include all the single stars out to a maximum distance
+\begin{equation}
+  d_0 = \sqrt{\frac{L}{4\pi F_0}}.
+  \label{eq:dmax}
+\end{equation}
+Since binaries are twice as luminous, the condition $F>F_0$ will
+include binaries out to the larger distance of $d_0\sqrt{2}$.
+None of the stars in binaries will
+appear to have a planet of radius $r$, because of the dilution of
+the transit signal.  Thus, the {\it apparent} occurrence rate $\Lambda\a$ of
+planets of radius $r$ is
+\begin{equation}
+    \Lambda\a(r) = 
+        \frac{\Lambda(r) \, n\s d_0^3}
+        {n\s d_0^3 + n\b (d_0\sqrt{2})^3}.
+    \label{eq:rate_at_rp}
+\end{equation}
+This apparent rate is larger than the true rate by a factor
+\begin{equation}
+    \frac{\Lambda\a(r)}{\Lambda(r)} = 
+        \frac{1}{1 + 2^{3/2}(n\b/n\s)}.
+    \label{eq:correction_rp}
+\end{equation}
+
+The observers will also detect some transiting planets around stars
+with binary companions.  The amplitude of these signals is
+\begin{equation}
+  \frac{L(r/R)^2}{L + L} = \frac{1}{2}\left(\frac{r}{R}\right)^2 =
+  \left(\frac{r/\sqrt{2}}{R}\right)^2,
     \label{eq:delta_obs_general} 
 \end{equation}
-one class of transit signal, with depth $(r\p/R)^2$, occurs in single
-star systems. The other class, with half the depth, occurs in twin
-binary systems, leading to apparent planet radii $\sqrt{2}$ smaller
-than the true radii.
-
-To calculate the occurrence rate of each planet type, our observers
-identify the ``stars'' from their survey that appear to have been
-searched for signals of each depth.  These transits are detected
-within a certain maximum
-distance~\citep[see][]{pepper_using_2003,pepper_searching_2005}, which
-from Equation~\ref{eq:S_N_thresh} scales as
-\begin{equation}
-  d_{\rm max} \propto \delta \, L_{\rm tot}^{1/2}.
-  \label{eq:dmax}
-\end{equation}
-Assuming that stars are uniformly distributed in space, the number of
-searchable stars $N_\star$ is proportional to
-\begin{equation}
-    N_\star \propto n \delta^3 L_{\rm tot}^{3/2},
-\label{eq:N_searchable_prop}
-\end{equation}
-where $n$ is the number per unit volume of single or binary star
-systems.
+leading the astronomers to believe they have discovered a population
+of planets with radius $r/\sqrt{2}$.  To calculate the corresponding
+occurrence rate, they count the stars for which this type of signal
+would have been detectable.  The limiting flux for detection in this
+case is $4F_0$, because the signal amplitude hase been reduced by a
+factor of two and the noise level must also be reduced by a factor of
+two.  The condition $F>4F_0$ is met for single stars within a distance
+$d_0/2$, and binaries within a distance $d_0\sqrt{2}/2$.  Therefore,
+the observers will calculate the occurrence rate of this new type of
+planet to be
+\begin{equation}
+    \Lambda\a\left( \frac{r}{\sqrt{2}} \right) = 
+        \frac{2\Lambda(r) \, n\b (d_0\sqrt{2}/2)^3}
+        {n\s (d_0/2)^3 + n\b (d_0\sqrt{2}/2)^3}
+    =
+    \frac{2\Lambda(r)\cdot2^{3/2}(n\b/n\s)}{1 + 2^{3/2} (n\b/n\s)}.
+    \label{eq:correction_diluted_rp}
+\end{equation}
+Figure~\ref{fig:model_1_volumes} illustrates the
+volumes enclosing the apparently searchable single and binary stars.
 
@@
     \end{center}
-    \caption{
-        Searchable volumes for single stars ({\it left}) and twin
-        binaries ({\it right}), assuming that all stars have the same
-        mass, radius, and luminosity, and that all planets have the
-        same radius $r\p$.
-        {\it Top:} At an apparent radius $r\a=r\p$, the
-        binarity-ignoring observers search twin binaries out to a
-        distance $\sqrt{2}$ times greater than they search single
-        stars.  Because the transit depths are diluted, there are no 
-        planets in twin binaries with $r\a=r\p$.
-        {\it Bottom:} At $r\a=r\p/\sqrt{2}$, the observed transit
-        depths are smaller by a factor of two, so the maximum
-        searchable distances are half those at $r\a=r\p$.  The only
-        detected planets with $r\a=r\p/\sqrt{2}$ orbit twin binaries.
-    }
+    \caption{ {\it Top.}---Volumes within which sources appear to be
+      searchable for planets of radius $r$.  Single stars are
+      searchable out to a distance $d_0$, at which point they become
+      too faint to allow the detection of transits.  Binaries
+      are brighter and therefore appear to be searchable out to a
+      larger distance.  {\it Bottom.}---Volumes within which within
+      which stars appear to be searchable for planets of radius
+      $r/\sqrt{2}$.  }
     \label{fig:model_1_volumes}
 \end{figure}
-
-When selecting sources that appear to have been searched, the
-observers admit some binaries.  Since the binaries are twice as
-luminous as singles, at fixed $\delta$ they are included out to a
-distance that is larger by a factor of $\sqrt{2}$.  To detect the
-half-strength signal, the observers need the noise level to be lower
-by a factor of two, which means the flux must be four times higher
-than that of a single star at distance $d_0$.  This is true of single
-stars within a distance $d_0/2$, and binaries within a distance
-$d_0\sqrt{2}/2$.  The searchable volumes are illustrated in
-Figure~\ref{fig:model_1_volumes}.
-
-Putting it all together, the {\it apparent} occurrence rate
-$\Lambda\a$ of planets of radius $r\p$ will be
-\begin{equation}
-    \Lambda\a(r\p) = 
-        \frac{\Lambda(r\p) \, n\s d_0^3}
-        {n\s d_0^3 + n\b (d_0\sqrt{2})^3}
-    \label{eq:rate_at_rp}
-\end{equation}
-where $n\s$ and $n\b$ are the number densities of single and binary
-star systems, respectively.  This apparent rate is larger than the
-true rate by a factor
-\begin{equation}
-    \frac{\Lambda\a(r\p)}{\Lambda(r\p)} = 
-        \frac{1}{1 + 2^{3/2}(n\b/n\s)}.
-    \label{eq:correction_rp}
-\end{equation}
-The observers will also claim to have discovered a class of planet
-with radius $r\p/\sqrt{2}$ and an occurrence rate given by
-\begin{equation}
-    \frac{\Lambda\a(r\p/\sqrt{2})}{\Lambda(r\p)}
-    =
-    \frac{2n\b (d_0\sqrt{2}/2)^3}
-      {n\s (d_0/2)^3 + n\b (d_0\sqrt{2}/2)^3}
-    =
-    \frac{2\cdot2^{3/2}(n\b/n\s)}{1 + 2^{3/2}
-    (n\b/n\s)}.
-    \label{eq:correction_diluted_rp}
-\end{equation}
 
@@
     \vspace{-0.5cm}
-    \caption{
-        Apparent occurrence rate $\Lambda\a$, and occurrence rate $\Lambda$, 
-        for a model with one type of star, one
-        type of planet, and twin binaries (same as
-        Figure~\ref{fig:model_1_volumes}).  We assume a twin binary
-        fraction of $0.05$, and that single, primary, and secondary
-        stars host planets at equal rates.  If the true planet radius
-        is $r\p$, all planets detected in binaries will have apparent
-        radii $r\a = r\p/\sqrt{2}$; Equation~\ref{eq:ratios} gives the
-        normalizations.
-    }
+    \caption{ Apparent occurrence rate $\Lambda\a$, and true
+    occurrence rate $\Lambda$ in a universe with only one type of
+    star, one type of planet (with radius $R_\oplus$), and a number
+    density of binary stars 5\% that of single stars.  The occurrence
+    rate of planets with radius $R_\oplus$ is underestimated, and the
+    occurrence rate of planets with radius
+    $R_\oplus/\sqrt{2}$ is overestimated.}
     \label{fig:occ_rate_model_1}
@@
 
-We can now assess the severity of these errors, given the
+We can now assess the severity of the errors, for a given value of the
 binary-to-single ratio $n\b/n\s$. For stars with masses from 0.7 to
@@
 are multiple~--~to be 0.44.  Assuming all multiple systems are
-binaries, this means
-\begin{equation}
-    \frac{n\b}{n\s + n\b} \approx 0.44.
-\end{equation}
-Of course not all of these binaries are ``twin'' binaries as we have
-assumed in our simple calculation. Perhaps only a tenth of the
-binaries have pairs of stars close enough in their basic properties to
-produce errors as significant as those we have been considering. In
-detail, this fraction depends on the binary mass ratio distribution
-and stellar mass-luminosity relation (see
-Section~\ref{sec:general_formula}).  Taking a leading-order estimate
-of $n\b/(n\s+n\b)\approx0.05$, we find
-\begin{equation}
-    \frac{\Lambda\a(r\p)}{\Lambda(r\p)} = 0.87,~~
-    \frac{\Lambda\a(r\p/\sqrt{2})}{\Lambda(r\p)} = 0.26.
+binaries, this gives a binary fraction
+\begin{equation}
+  \frac{n\b}{n\s + n\b} \approx 0.44,
+\end{equation}
+which implies $n\b/n\s \approx 0.79$.  Of course not all of
+these binaries are ``twin'' binaries as we have assumed in our simple
+calculation.  Later, in Section~\ref{sec:general_formula}, we will
+allow for a continuum of properties for the secondary stars. For now,
+we might guess that only a tenth of the binaries have pairs of stars
+close enough in brightness to produce errors as significant as those
+we have been considering.  Adopting the value $n\b/n\s\approx0.05$, we
+find
+\begin{equation}
+    \frac{\Lambda\a(r\p)}{\Lambda(r\p)} = 0.88,~~
+    \frac{\Lambda\a(r\p/\sqrt{2})}{\Lambda(r\p)} = 0.25.
     \label{eq:ratios}

### 2018-02-23 src/model1_numbers.py
simple model figures+select numbers changes

@@ -2,8 +2,7 @@
 calculate the ratios of apparent to true occurrence rates for the
 order-of-magnitude toy model.
 '''
-BF = 0.05
-nb_by_ns = 1 / ( (1/BF) - 1 )
+nb_by_ns = 0.05
 
 Λa_by_Λ_at_r = (1 + 2**(3/2)*nb_by_ns)**(-1)
 
@@ -11,3 +10,6 @@ nb_by_ns = 1 / ( (1/BF) - 1 )
 
 print(Λa_by_Λ_at_r, Λa_by_Λ_at_r*0.5)
 print(Λa_by_Λ_at_rbyrt2, Λa_by_Λ_at_rbyrt2*0.5)
+
+bf = 1/(1+1/nb_by_ns)
+print(bf)

### 2018-02-23 src/numerical_models.py

@@ -318,7 +318,10 @@ def calculate_true_and_apparent_rates(
 
         if model_number == 1 or model_number == 2:
             rs = np.array(df['r'])
-            assert np.all(rs[np.greater(rs, np.zeros_like(rs))] == rs[0])
+            assert np.all(
+                rs[np.greater(rs, np.zeros_like(rs))] == \
+                rs[np.greater(rs, np.zeros_like(rs))][0]
+            )
             r_p = rs[0]
             N_p_at_r_p_inferred += (len(r_a[r_a == r_p])/Q_g0)
             N_p_at_r_p_true += len(r[r == r_p])

### 2018-02-23 src/plot_occrates_vs_radius.py

@@ -105,7 +105,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
     else:
         ax.legend(loc='best',fontsize='medium')
 
-    ax.set_xlabel('planet radius [$r_{\mathrm p}$]', fontsize='large')
+    ax.set_xlabel('planet radius [$R_{\oplus}$]', fontsize='large')
 
     ax.set_ylabel('number of planets per star', fontsize='large')
 

### 2018-02-23 src/plot_visualize_volumes.py

@@ -94,9 +94,9 @@ ax.text2D(.3, .05, 'single stars', transform=fig.transFigure,
      fontsize='large', va='bottom', ha='center')
 ax.text2D(.7, .05, 'twin binaries', transform=fig.transFigure,
      fontsize='large', va='bottom', ha='center')
-ax.text2D(.05, .3, '$r_{\mathrm{a}}=r_{\mathrm{p}}/\sqrt{2}$', transform=fig.transFigure,
+ax.text2D(.05, .3, '$r_{\mathrm{a}}=r/\sqrt{2}$', transform=fig.transFigure,
      fontsize='large', va='center', ha='left', rotation=90)
-ax.text2D(.05, .7, '$r_{\mathrm{a}}=r_{\mathrm{p}}$', transform=fig.transFigure,
+ax.text2D(.05, .7, '$r_{\mathrm{a}}=r$', transform=fig.transFigure,
         fontsize='large', va='center', ha='left', rotation=90)
 
 fig.savefig('../results/visualize_volumes.pdf', dpi=300,

### 2018-02-23 src/run_monte_carlo_models.sh

@@ -1,3 +1,3 @@
 # "Nominal" models (this just means I arbitrarily decided Z_2 = 0.5)
-python numerical_models.py --modelnumber 1 --ZsubTwo 0.5 --binaryfrac 0.1
-python numerical_models.py --modelnumber 2 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5
+python numerical_models.py --modelnumber 1 --ZsubTwo 0.5 --binaryfrac 0.0476
+#python numerical_models.py --modelnumber 2 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5

### 2018-02-23 paper/main.tex
jnw results edits

@@
       are brighter and therefore appear to be searchable out to a
-      larger distance.  {\it Bottom.}---Volumes within which within
+      larger distance.  {\it Bottom.}---Volumes within
       which stars appear to be searchable for planets of radius
@@
     star, one type of planet (with radius $R_\oplus$), and a number
-    density of binary stars 5\% that of single stars.  The occurrence
+    density of binary stars 5\% the number density of single stars.
+    The occurrence
     rate of planets with radius $R_\oplus$ is underestimated, and the
@@
 \begin{equation}
-    \frac{\Lambda\a(r\p)}{\Lambda(r\p)} = 0.88,~~
-    \frac{\Lambda\a(r\p/\sqrt{2})}{\Lambda(r\p)} = 0.25.
+    \frac{\Lambda\a(r)}{\Lambda(r)} = 0.88,~~
+    \frac{\Lambda\a(r/\sqrt{2})}{\Lambda(r)} = 0.25.
     \label{eq:ratios}
@@
 
-\subsection{Formula Based on Apparent Rate Density}
+\subsection{Planets of different sizes}
 \label{sec:model_1_density}
 
-There is a different way to conceptualize the preceding results that
-will be useful in the upcoming discussion. We now consider a spectrum
-of planet sizes, $r$, and introduce the occurrence rate density
+We will now generalize to allow for a continuum of planet sizes.   We
+introduce the occurrence rate density
 \begin{equation}
@@
 \end{equation}
-the number of planets per star per unit planet radius.
-
-The naive observers are in fact measuring $\Gamma\a(r\a)$, the {\it
-apparent} occurrence rate density~--~the number of planets per star
-per unit apparent radius $r\a$.  The ``apparent planet radius'' is the
-radius inferred from the transit depth under the assumption that the
-host star is single. The ``apparent stellar radius'' $R\a$ is
-analogous.  The observed transit depth can be written $\delta =
-(r\a/R\a)^2$, which from Equation~\ref{eq:delta_obs_general} gives
-$r\a=r\p/\sqrt{2}$ for planets in twin binaries.  $\Gamma\a(r\a)$ is
-the same as the {\it true} rate density of transit signals of
-amplitude $\delta$.
-
-We will now calculate the apparent rate density by evaluating the star
-and planet counts for signals coming from single stars, primary stars
-in binaries, and secondary stars in binaries.  Let $\mu$ be the ratio
-between the number of searchable binary systems and the number of
-searchable single systems at a particular transit depth. The number of
-single and binary sources in the searched sample are then
-\begin{equation}
-  \frac{N_\star(r\a)}{1+\mu}~~{\rm and}~~\frac{\mu N_\star(r\a)}{1+\mu},
-  \label{eq:N_searched}
-\end{equation}
-respectively.  Earlier we showed that due to Malmquist bias, $\mu =
-2^{3/2}(n\b/n\s)$.
-
-Suppose the occurrence rate densities for planets around
-single stars, primaries, and secondaries are $\Gamma_0(r),
-\Gamma_1(r)$, and $\Gamma_2(r)$, respectively. For a single planet
-size,
-\begin{equation}
-    \Gamma_i(r) = \Lambda(r\p) \, \hat{\delta}(r-r\p),~~{\rm for}
-    \ i\in\{0,1,2\},
-    \label{eq:one_planet}
-\end{equation} 
-where $\hat{\delta}$ is the Dirac delta function.
-The number of planets detected from singles, primaries, and
-secondaries are then
+the number of planets per star per unit planet radius.  The naive
+observers are measuring $\Gamma\a(r\a)$, the apparent occurrence rate
+density of planets with an ``apparent radius''
+\begin{equation}
+  r\a = R \sqrt{\delta}.
+\end{equation}
+
+For a given value of $r\a$, the observers assemble the sample of
+$N_\star(r\a)$ sources for which a signal of amplitude $\delta =
+(r\a/R)^2$ could have been detected.  We showed in the previous
+section that when all stars are identical, this sample will contain
+binaries and single stars in the ratio $2^{3/2}(n\b/n\s)$.  Here we
+will denote this ratio by $\mu$, which will be calculated later in a
+more general context.  With this definition, the number of single
+stars is proportional to $1/(1+\mu)$ and the number of binaries is
+proportional to $\mu/(1+\mu)$.
+
+From within this sample of apparently searchable sources, the
+observers sum the number of detections $dN_{\rm det}$ of planets
+with an apparent radius between $r\a$ and $r\a + dr\a$.  There will be
+three contributions to this sum,
 \begin{align}
-  n_{\rm det}^0(r\a)\mathrm{d}r\a &= 
-      \frac{N_\star(r\a)}{1+\mu} p_{\rm tra}
+  dN_{{\rm det},0} &= 
+      \frac{N_\star(r\a) p_{\rm tra}}{1+\mu}
       \Gamma_0(r\a)\mathrm{d}r\a,
   \label{eq:n0} \\
-  n_{\rm det}^1(r\a)\mathrm{d}r\a &= 
-      \frac{\mu N_\star(r\a)}{1+\mu} p_{\rm tra}
+  dN_{{\rm det},1} &= 
+      \frac{\mu N_\star(r\a) p_{\rm tra}}{1+\mu} 
       \Gamma_1(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
 	\label{eq:n1} \\
-  n_{\rm det}^2(r\a)\mathrm{d}r\a &=
-      \frac{\mu N_\star(r\a)}{1+\mu} p_{\rm tra}
-      \Gamma_2(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
+  dN_{{\rm det},2} &=
+      \frac{\mu N_\star(r\a) p_{\rm tra}}{1+\mu} 
+      \Gamma_2(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a).
 	\label{eq:n2}
 \end{align}
-where $n_{\rm det}^i$ is the number of detections per unit apparent
-radius for each respective type of star.
-
-Dividing the number of detections by the number of sources,
-the apparent rate density reported when ignoring binarity is
-\begin{equation}
-  \Gamma\a(r\a) =
-    \frac{1}{1+\mu}\,\Gamma_0(r\a) +
-    \frac{\mu}{1+\mu}\,\sqrt{2}\,\Gamma_1(\sqrt{2}r\a) +
-    \frac{\mu}{1+\mu}\,\sqrt{2}\,\Gamma_2(\sqrt{2}r\a).
+where here and elsewhere, the subscript 0 refers to single stars, 1
+refers to primary stars of binaries, and 2 refers to secondary stars
+of binaries. The apparent occurrence rate density is therefore
+\begin{equation}
+  \Gamma\a(r\a) = \frac{dN_{\rm det}}{dr\a} \frac{1}{N_\star(r\a) p_{\rm tra}} =
+  \frac{\Gamma_0(r\a)}{1+\mu} +
+  \frac{\mu\sqrt{2}\,\Gamma_1(\sqrt{2}r\a)}{1+\mu} +
+  \frac{\mu\sqrt{2}\,\Gamma_2(\sqrt{2}r\a)}{1+\mu}.
 	\label{eq:formula_twin_binary}
 \end{equation}
-If we insert Equation~\ref{eq:one_planet} and integrate over
-apparent radius, this reproduces Equations~\ref{eq:rate_at_rp}
-and~\ref{eq:correction_diluted_rp}.
-
-\begin{comment}
-  and inputting Equation~\ref{eq:one_planet}, we find
-  \begin{align}
-      \Gamma\a(r\a) &= \Lambda(r\p) \left[
-      \frac{1}{1+\mu} \cdot
-      \hat{\delta}(r\a-r\p)  +
-      \frac{2\mu}{1+\mu} \cdot
-      \delta\left(r\a-\frac{r\p}{\sqrt{2}} \right) \right].
-      \label{eq:model_1_apparent_rate_density}
-  \end{align}
-  Integrating over $r\a$, this yields
-  \begin{equation}
-    \Lambda\a(r_{\rm p})=\frac{Z}{1+\mu},\quad
-    \Lambda\a(r_{\rm p}/\sqrt{2})=\frac{2\mu Z}{1+\mu},
-  \end{equation}
-  which reproduce Equations~\ref{eq:correction_rp}
-  and~\ref{eq:correction_diluted_rp}.
-\end{comment}
-
-\begin{comment}
-    The ratio of the apparent to single star rate
-    densities,
-    \begin{equation}
-        X_\Gamma(r) \equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)}
-          \right|_{r\a = r},
-    \end{equation}
-    can then be evaluated as a ``correction factor''.  At the true and
-    diluted planet radii, $X_\Gamma(r\p)=1/(1+\mu)$ and
-    $X_\Gamma(r\p/\sqrt{2})=2\mu/(1+\mu)$.  This yields a correction
-    $X_\Gamma$ of 0.87~(0.76) if the binary fraction is 0.05~(0.10).
-    All together the various effects produce biases of order 10\% in the
-    occurrence rates.  
-\end{comment}
-
-\begin{comment}
-    \subsection{One type of star, two types of planets}
-
-    A simple extension to the previous example helps distinguish between
-    the apparent and underlying planet populations.  Consider now a
-    universe that is the same as in Section~\ref{sec:model_1}, except that
-    half of planets have radii $r\p$, while the other half have radii
-    $r\p/\sqrt{2}$.  The rate densities are
-    \begin{equation}
-        \Gamma_i(r) = \frac{Z_i}{2} \left[
-        \hat{\delta}(r-r\p) + \delta\left(r-\frac{r\p}{\sqrt{2}}\right)
-        \right], \quad {\rm for}\  i \in \{ 0,1,2 \},
-    \end{equation}
-    where $i=0$ corresponds to singles, $i=1$ to primaries, and $i=2$ to
-    secondaries, and the $Z_i$'s are the number of planets per star of
-    each type.
-
-    Following an identical line of reasoning as in
-    Section~\ref{sec:model_1}, the apparent rate density can be written
+Our earlier results, Equations~\ref{eq:rate_at_rp}
+and~\ref{eq:correction_diluted_rp}, are recovered by integrating this formula
+over $r$ after inserting
+\begin{equation}
+  \Gamma_i(r) = \Lambda(r\p)\, \hat{\delta}(r-r\p),~~{\rm for}\ i\in\{0,1,2\}
+\end{equation}
+where $\hat{\delta}$ is the Dirac delta function, and $r\p$ is the
+single planet size considered in Section~\ref{sec:model_1}.
+
+\subsection{Binaries with different mass ratios}
+\label{sec:general_formula}
+
+Next we generalize to allow for a spectrum of different properties for
+the secondary stars.  For simplicity we assume that the stars form a
+one-parameter family specified by the stellar mass $M$.  This is
+approximately the case for main-sequence stars.  The functions $L(M)$
+and $R(M)$ give the luminosity and radius as a function of mass, and
+$f(q)$ is the distribution of binary mass ratios in a volume-limited
+sample.  We also assume that observers perceive all the binaries to be
+isolated stars with the same mass as the primary star, i.e., the light
+from the secondary star is either too faint or too similar to the
+primary star to make a difference in the stellar classification.
+Finally, for clarity of presentation we make the simplifying
+assumption that $\Gamma_0$, $\Gamma_1$ and $\Gamma_2$ do not depend on
+stellar mass, although our formalism can easily accommodate such a
+dependence.
+
+To compute the apparent occurrence rate density, we need to make
+the following modifications to Equation~\ref{eq:formula_twin_binary}:
+%
+\begin{enumerate}
+%
+\item The Malmquist bias is different.  For a given value of $r\a$, the
+  number of binary systems in the searchable sample with mass ratio
+  $(q, q+\mathrm{d}q)$ is
+\begin{equation}
+    {N_\star(r\a)\over{1+\mu}}\cdot {n_{\rm b}\over n_{\rm s}}
+    \left[{L(M) + L(qM) \over L(M)}\right]^{3/2}
+    f(q)\,\mathrm{d}q,
+    \label{eq:N_binaries}
+\end{equation}
+where $\mu$ is given by
+\begin{equation}
+    \mu= 
+    %\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
+    \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L(M) + L(qM)
+    \over L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
+    \label{eq:mu_general}
+\end{equation}
+To obtain the total number of searchable binaries,
+Equation~\ref{eq:N_binaries} needs to be integrated over $q$. The
+result of the integration replaces ${\mu N_\star(r\a)/(1+\mu)}$ in
+Equations~\ref{eq:n1} and~\ref{eq:n2}.
+
+\item The apparent radius of a planet in a binary system now depends
+on whether the host star is the primary or the secondary star. When the host
+is the primary star, we write $r=\mathcal{D}_1 r\a$, where
+\begin{equation}
+    \mathcal{D}_1
+    = \left[ \frac{ L(M) + L(qM) }{ L(M) } \right]^{1/2}
+    \label{eq:dil_1}
+\end{equation}
+is the appropriate dilution factor.
+When the host is the secondary star, a correction must also be made
+to account for the different radius of the secondary star.
+In that case $r=\mathcal{D}_2 r\a$, where
+\begin{equation}
+  \mathcal{D}_2
+  = \frac{R(qM)}{R(M)}
+    \left[ \frac{L(M) + L(qM)}{L(qM)} \right]^{1/2}.
+  \label{eq:dil_2}
+\end{equation}
+
+\item When a transiting planet is detected around a secondary star,
+  the naive observers make the wrong correction for the transit
+  probability.  At a fixed orbital period, $p_{\rm tra}$
+  in Equation~\ref{eq:n2} must be multiplied by a factor of
+\begin{equation}
+  {R(qM) \over R(M)}q^{-1/3}.
+\end{equation}
+
+\end{enumerate}
+
+Taking these modifications into account, a general formula for the
+apparent rate density is
 \begin{align}
     \notag
-        \Gamma\a(r\a) &=
-        \frac{1}{2(1+\mu)} \left[
-        Z_0 \cdot \hat{\delta}(r\a - r\p)
-        +
-        \left[Z_0 + \mu (Z_1 + Z_2)
-        \right] \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right) 
-        \right. \\
-        &\quad\quad\quad\quad\quad\quad\quad\quad+
-        \left.
-        \mu(Z_1 + Z_2) \cdot \delta\left(r\a - \frac{r\p}{2}\right)
-        \right].
-        \label{eq:two_radii_twins}
-    \end{align}
-    Just as in Equation~\ref{eq:model_1_apparent_rate_density}, the
-    $N_\star^0(r\a)$ terms cancel, leaving only the $\mu$ weights.
-    However, there are now three detected planet sizes.  Also different is
-    that two populations contribute at $r\a = r\p/\sqrt{2}$: the first
-    population is singles with $r=r\p/\sqrt{2}$, and the second is twin
-    binaries with $r=r\p$.  Both populations are detected out to the same
-    maximum searchable distance.  More generally, at any given apparent
-    radius, there will be contributions from both singles, primaries, and
-    secondaries~---~but the relative weights between these contributions
-    will depend on the underlying occurrence rates.
-\end{comment}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{General formula for apparent occurrence rate}
-\label{sec:general_formula}
-
-To generalize the procedure of Section~\ref{sec:model_1_density} for
-binaries with varying light ratios, we consider an SNR-limited survey
-in which stars can have arbitrary properties.  We assume that there
-are some functions $L(M)$ and $R(M)$ that specify a star's luminosity
-and radius in terms of its mass. We also presume that the observers
-know the masses of every single and primary star, and that they assign
-each binary system the properties of its primary.  Finally, we take
-the volume-limited distribution of binary mass ratios, $f(q)$, to be
-independent of the primary star's mass.
-
-We want an equation for $\Gamma\a(r\a,M\a)$, the apparent rate density
-at each apparent planet radius and apparent stellar mass\footnote{By
-assumption, the apparent stellar mass for single star systems is the
-true mass. For binary systems, the apparent mass is the mass of the
-primary.}.
-Similar to Equation~\ref{eq:rate_density_defn}, we define
-$\Gamma(r,M)$ as the number of planets per star, per unit planet radius,
-per unit stellar mass.  Due to the varying binary mass ratios, we need
-the following modifications to Equation~\ref{eq:formula_twin_binary}:
-%
-\begin{enumerate}
-%
-\item The Malmquist bias is different. The ratio between the number of
-binary and single systems for which a transit of depth $\delta$ is
-detectable, $\mu$, has changed.  At any $(r\a,M\a)$ pair, the number
-of binary systems in the searchable volume with mass ratio $(q,
-q+\mathrm{d}q)$ is now
-\begin{equation}
-    {N_\star(r\a)\over{1+\mu}} \, {n_{\rm b}\over n_{\rm s}}
-    \left[{L_{\rm tot}(M\a, q) \over L(M\a)}\right]^{3/2}
-    f(q)\,\mathrm{d}q,
-    \label{eq:N_binaries}
-\end{equation}
-where $\mu$ is given by
-\begin{equation}
-    \mu= 
-    %\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
-    \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L_{\rm tot}(M\a, q)
-    \over L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
-    \label{eq:mu_general}
-\end{equation}
-Binaries with larger mass ratios are overrepresented by a factor of
-$\left[{L_{\rm tot}(M\a, q)/L(M\a)}\right]^{3/2}$ because the
-sample of searchable binaries is magnitude-limited.  To obtain
-the number of binary systems searched at each $(r\a,M\a)$ pair,
-Equation~\ref{eq:N_binaries} needs to be integrated over $q$.  It
-can then replace ${\mu N_\star(r\a)/(1+\mu)}$ in
-Equations~\ref{eq:n1} and~\ref{eq:n2}.
-
-\item The apparent radius of a planet in a binary system now depends
-on whether the host star is the primary or the secondary. When the host
-is the primary, we write
-$r=\mathcal{D}_1 r\a$, where
-\begin{equation}
-    \mathcal{D}_1
-    = \left( \frac{ L_{\rm tot}(M\a, q)}{ L(M\a) } \right)^{1/2}.
-    \label{eq:dil_1}
-\end{equation}
-When the host is the secondary, $r=\mathcal{D}_2 r\a$, and the
-ratio between the assumed and true stellar radii must be included:
-\begin{equation}
-  \mathcal{D}_2
-  = \frac{R(qM\a)}{R(M\a)}
-    \left( \frac{L_{\rm tot}(M\a, q)}{L(qM\a)} \right)^{1/2}.
-  \label{eq:dil_2}
-\end{equation}
-
-\item Since the observers assign binaries the properties of the
-primary, the transit probability for planets orbiting secondaries is
-over-estimated. At a fixed orbital period, this changes
-$p_{\rm tra}$ in Equation~\ref{eq:n2} by a factor of
-\begin{equation}
-  {R(qM\a) \over R(M\a)}q^{-1/3}.
-\end{equation}
-
-\item The contribution to the apparent rate density from
-secondaries now depends on the mass of the secondary, $qM\a$. The
-associated measure on the right-hand side of
-Equation~\ref{eq:n2} becomes ${\rm d}(qM\a)$, and gives rise to an
-extra multiplicative factor of $q$.
-
-\end{enumerate}
-
-Taking these modifications into account, a general formula for the
-apparent rate density follows:
-\begin{align}
-    \notag
-    \Gamma\a(r\a,M\a) &= \frac{1}{1+\mu}
-    \left\{ \Gamma_0(r\a, M\a)+ 
+    \Gamma\a(r\a) &= \frac{1}{1+\mu} \,
+    \left\{ \Gamma_0(r\a)+ 
     \frac{n\b}{n\s}
@@
            \mathcal{D}_1^3 f(q)\cdot
-           \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a, M\a)\,
+           \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a)\,
     \right.   
@@
     +\int_0^1 {\rm d}q\, 
-         \mathcal{D}_1^3 f(q)\cdot q \mathcal{D}_2
-         \Gamma_2(\mathcal{D}_2r\a, qM\a)\cdot
-         \frac{R(qM\a)}{R(M\a)} q^{-1/3}
+         \mathcal{D}_1^3 f(q)\cdot \mathcal{D}_2
+         \Gamma_2(\mathcal{D}_2r\a)\cdot
+         \frac{R(qM)}{R(M)} q^{-1/3}
     \right] \right\}.
@@
 \end{align}
-We give an alternative derivation in the
-\hyperref[sec:appendix]{Appendix}.
-With the definition of $\mu$ in Equation~\ref{eq:mu_general},
-Equation~\ref{eq:general_Gamma_a} can also be expressed as
+The \hyperref[sec:appendix]{appendix} gives an alternative derivation
+of this equation.
+
+We note that the combination $\mathcal{D}_1^3f(q)$ is the mass-ratio
+distribution for binaries contained within the searchable sample of
+sources.  With this in mind we may rewrite
+Equation~\ref{eq:general_Gamma_a} as
 \begin{align}
-    \notag
-    \notag
-    \Gamma\a(r\a,M\a)
-    &= 
-    {1\over 1+\mu}
+    %\notag
+    %\notag
+    \Gamma\a(r\a)
+    =%&= 
+    {1\over 1+\mu} \,
     \left[
-       \Gamma_0(r\a, M\a) \phantom{\frac{1}{1}}
-       \right.&\\
-       &\quad\quad \left.+\mu
+       \Gamma_0(r\a)%\phantom{\tilde \Gamma}\right.%&\\
+       %&\left.
+       +\mu\,
        \left\langle
-       \mathcal{D}_1\Gamma_1\left(\mathcal{D}_1r\a, M\a\right)
+       \mathcal{D}_1\cdot\Gamma_1\left(\mathcal{D}_1r\a\right)
        +
-       {q \mathcal{D}_2}\Gamma_2\left(\mathcal{D}_2r\a,
-       qM\a\right) \cdot {R(qM\a) \over R(M\a)}q^{-1/3}
+       {q \mathcal{D}_2}\cdot\Gamma_2\left(\mathcal{D}_2r\a\right)
+       \cdot
+       {R(qM) \over R(M)}q^{-1/3}
        \right\rangle
@@
 \end{align}
-where the angle brackets denote averaging over $\mathcal{D}_1^3f(q)$.
-Summarized, the apparent rate density is a weighted sum of the rate
-densities from singles, primaries, and secondaries.  The weights are
-determined by the fraction $\mu$ and mass ratio distribution
-$\mathcal{D}_1^3f(q)$ of binaries {\it in the searchable volume}.  The
-fraction $\mu$ gives the relative contributions from singles and
-binaries, and $\mathcal{D}_1^3 f(q)$ applies a Malmquist bias for
-binaries that are brighter.  A final correction for secondaries
-accounts for the overestimated transit probability.
+where the angle brackets denote averaging over all the binaries in the
+searchable sample.
 
@@
 
-\section{Realistic Star and Planet Distributions}
+\section{Case Studies}
 \label{sec:more_complicated}
 
-We will now apply our general equation for the apparent rate density
-(Equation~\ref{eq:general_Gamma_a}) to study the impact of
-unrecognized binaries in regimes of observational interest.  In the
-following, we write the rate density for each type of star,
-$\Gamma_i(r)$, as the product of a shape function, normalized to
-unity, and a constant:
-\begin{equation}
-    \Gamma_i(r) = Z_i f_i(r), \quad {\rm for\ }i\in\{0,1,2\},
-\end{equation}
-where the respective indices correspond to single stars, primaries of
-binaries, and secondaries of binaries.  The normalizations $Z_i$ are
-each system type's occurrence rate $\Lambda_i$, integrated over all
-planetary radii. In other words, they are number of planets per
-single, primary, or secondary star.  Our main interest is in
-varying the radius shape function and the relative values of the
-integrated occurrence rates. We will also briefly mention shape
-functions in stellar mass.  For analytic simplicity, we will assume
-throughout this section that stars are a one-parameter family, given
-by $L \propto M^\alpha \propto R^\alpha$.  Applying these power laws
-to Equations~\ref{eq:dil_1} and~\ref{eq:dil_2}, we find
+We can now gauge the size of the systematic errors associated
+with unresolved binaries, for cases of interest.  Throughout this
+section we assume $R\propto M$, and $L \propto M^{\alpha}$ where
+$\alpha = 3.5$, as is roughly the case for main-sequence stars.
+With these assumptions, Equations~\ref{eq:dil_1} and~\ref{eq:dil_2}
+become
 \begin{equation}
@@
   =  (1+q^\alpha)^{1/2}~~{\rm and}~~\mathcal{D}_2
-  = q(1+q^{-\alpha})^{1/2}
-\end{equation}
-for the radius dilution prefactors.
+  = q(1+q^{-\alpha})^{1/2}.
+\end{equation}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Power law planet radius distribution}
+\subsection{Power-law planet radius distribution}
 \label{sec:model_2}
 
-\subsubsection{Twin binaries}
-As a first step, we return to the case where all binaries are twins.
-However, we now let the planet radius distribution be a power law,
-\begin{equation}
-    \Gamma_i(r) = Z_i f(r) = Z_i r^\gamma/\mathcal{N}_r,
-\end{equation}
-for $\mathcal{N}_r$ the shape function's normalization.  Applying
-Equation~\ref{eq:general_Gamma_a} gives the resulting apparent rate
-density,
-\begin{equation}
-    \Gamma\a(r\a) = \frac{r\a^{\gamma}}{\mathcal{N}_r} \left[
-    \frac{Z_0}{1+\mu}
+Based on {\it Kepler} data, \citet{howard_planet_2012} found the
+radius distribution of planets between 2 and 17~$R_\oplus$ orbiting Sun-like
+stars within 0.25\, AU to be consistent with a power law,
+\begin{equation}
+  \Gamma_0(r) \propto r^\gamma,
+\label{eqn:power_law}
+\end{equation}
+with $\gamma=-2.92\pm 0.11$.  Their analysis ignored the effects of
+binarity.  We can use our formalism to estimate the resulting level of
+systematic error.
+
+To warm up we will again consider the case in which all stars are
+identical.  We assume further that the distributions of planets around
+primaries and secondaries differ only by multiplicative factors,
+\begin{equation}
+    \Gamma_1 = Z_1 \Gamma_0,~~\Gamma_2 = Z_2 \Gamma_0.
+\end{equation}
+Application of Equation~\ref{eq:general_Gamma_a} gives
+\begin{equation}
+    \frac{\Gamma\a(r\a)}{\Gamma_0(r\a)} = 
+    \frac{1}{1+\mu}
     +
-    2^{\frac{\gamma+1}{2} } \frac{\mu}{1+\mu} \left(Z_1 + Z_2
-    \right)
-    \right].
+    2^{\frac{\gamma+1}{2} } \frac{\mu}{1+\mu} \left(Z_1 + Z_2\right),
     \label{eq:model5_apparent_rate_density}
 \end{equation}
-Under these assumptions, twin binaries simply shift the apparent
-radius distribution: $\Gamma\a(r\a) \propto r\a^\gamma$.  As in
-Section~\ref{sec:model_1}, $\mu = 2^{3/2} n\b/n\s$.  If planet
-occurrence is independent of system multiplicity, the ``correction
-factor'' relative to the rate density for singles is
-\begin{align}
-    \frac{\left. \Gamma\a(r\a)\right|_{r\a= r}}{\Gamma_0(r)} 
-    &=
+where $\mu = 2^{3/2} n\b/n\s$.  The ratio does not depend on $r\a$ and
+thus, under our assumptions, the effect of twin binaries is simply to
+change the normalization of the radius distribution.  If we further
+assume that planet occurrence is independent of system multiplicity,
+i.e., $Z_1=Z_2=1$, then
+\begin{equation}
+    \frac{\Gamma\a(r\a)}{\Gamma_0(r\a)} = 
     \frac{1 + 2^{\frac{\gamma+3}{2}}\mu}{1 + \mu}.
     \label{eq:power_law_correction}
-\end{align}
-For a binary fraction of $0.1$, $\mu\approx 0.15$. Taking
-$\gamma=-2.92$ from \citet{howard_planet_2012},  we find that the
-apparent rate density is a mere 0.4\% larger than the rate density of
-single stars.  Fortuitously, the exponent of the radius distribution
-is close to $-3$, and the errors from neglecting binaries almost
-entirely cancel out.
-
-The above estimate cannot apply at small radii, since the shape
-function diverges. \citet{howard_planet_2012}'s results indicate that
-a single power law fits the planet radius distribution for radii
-greater than $2r_\oplus$.  Similarly, there should be an upper radius
-limit, $r_{\rm u}$, to the radius distribution, perhaps around
-$24r_\oplus$ based on the most inflated hot Jupiters.  Imposing an
-upper cut-off of $r_{\rm u}$ would lead to smaller values of the
-apparent rate density down to $r_{\rm u}/\sqrt{2}$, compared to a
-power law without the cut-off.  We are not particularly interested in
-this effect because hot Jupiter occurrence rates are poorly described
-by a power law (see Section~\ref{sec:further_models}).  All told, if
-our assumptions are applicable to real transit surveys,
-Equation~\ref{eq:power_law_correction} suggests that for apparent
-radii from $2r_\oplus$~to~$17r_\oplus$, unrecognized binaries are a
-minor source of systematic error.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Binaries with power law mass ratio distribution}
-\label{sub:powerlaw_varying_binaries}
+\end{equation}
+Adopting $\gamma=-2.92$, and a twin binary fraction $n\b/n\s=0.05$, as
+before, we obtain $\mu = 0.14$ and $\Gamma\a/\Gamma_0 = 1.003$.  The
+correction is tiny because, by coincidence, the reported value of
+$\gamma$ is very close to $-3$, the value for which
+Equation~\ref{eq:power_law_correction} reduces to unity and the
+effects of binarity cancel out completely.  This suggests that
+although \citet{howard_planet_2012} derived the occurrence rate
+density under the false assumption that all stars are single, the
+resulting systematic error is negligible.
 
@@
     \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
-    \caption{
-        The mass ratio distribution for a magnitude-limited sample of
-        binary stars, in which the underlying volume-limited
-        distribution is uniform, qualitatively similar to Figure~16 of
-        \citet{raghavan_survey_2010}.  At a given observed transit
-        depth, the searchable binaries in a transit survey are
-        magnitude-limited. For this figure, we assume $L\propto
-        M^{3.5}$.
-    }
+    \caption{ The mass ratio distribution of binaries in a
+      magnitude-limited sample, assuming the underlying volume-limited
+      distribution is uniform and the luminosity-mass relation is
+      $L\propto M^{3.5}$. For transit signals of a given amplitude,
+      the sample of searchable sources is magnitude-limited, causing
+      high mass ratios to be over-represented. }
     \label{fig:q_distribn_mag_limited}
@@
 
-To check whether non-twin binaries change the preceding result, we now
-consider a distribution of binary mass ratios.  Specifically, we take
-$f(q) = q^\beta/\mathcal{N}_q$, for $\mathcal{N}_q$ the normalization.
-This changes $\mu$ from the twin binary case;
-Equation~\ref{eq:mu_general} simplifies to
-\begin{equation}
-    \mu = \frac{n\b}{n\s} \frac{1}{1+\beta}
+For a more accurate analysis we now consider a distribution of binary
+mass ratios.  Studies of binaries in the local neighborhood suggest
+that the distribution of mass ratios is nearly uniform between zero
+and unity~\citep{raghavan_survey_2010}.  We consider the more general
+possibility of a power-law dependence, $f(q) = \mathcal{N}_q q^\beta$,
+where $\mathcal{N}_q$ is a normalization constant.  In this case
+Equation~\ref{eq:mu_general} gives
+\begin{equation}
+    \mu = \frac{1}{\mathcal{N}_q} \frac{n\b}{n\s}
     \int_0^1 (1+q^\alpha)^{3/2}q^\beta\,{\rm d}q.
@@
 \end{equation}
-For the $\beta=0$ case, this equation means there will be more
-twin-like binaries than faint binaries in the sample of stars
-that are searched at any transit depth
-(Figure~\ref{fig:q_distribn_mag_limited}).
-
-The rate density now varies not only with planet radius, but also
-host star mass.  We can absorb this dependence into a power law,
-\begin{equation}
-    \Gamma_i(r,M) = Z_i \, \frac{r^\gamma}{\mathcal{N}_r} \,
-    \frac{M^\zeta}{\mathcal{N}_M},
-\end{equation}
-where $Z_i$ is dimensionless, and the normalization constants carry
-the units.% (each side has units $[r^{-1} M^{-1}]$).
-
-Our main interest is in the apparent rate density's radius
-dependence.  Marginalizing Equation~\ref{eq:general_Gamma_a} over
-apparent stellar mass, we find that when all stars host the same number
-of planets,
+Figure~\ref{fig:q_distribn_mag_limited} illustrates the Malmquist
+bias for the particular case of a flat distribution.
+
+Again assuming $\Gamma_0=\Gamma_1=\Gamma_2$, the apparent occurrence
+rate density is 
 \begin{align}
@@
     \notag
-    \frac{\left.\Gamma\a(r\a)\right|_{r\a= r}}{\Gamma_0(r)} 
+    %\frac{\left.\Gamma\a(r\a)\right|_{r\a= r}}{\Gamma_0(r)} 
+    \frac{\Gamma\a(r\a)}{\Gamma_0(r\a)} 
     &=
@@
 \end{align}
-where $\zeta$ does not appear because of the marginalization over
-$M\a$.  For $\alpha = 3.5$, $\beta=0$, $\gamma=-2.92$, the
-summed integrals in Equation~\ref{eq:powerlaw_vary_binary} give
-$(\ldots)\approx 1.503$. %171211_model_integrals.nb
-For $n\b / (n\b + n\s)=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$.
-The apparent rate density is 4.8\% larger than the rate density around
-singles.  Considering only twin binaries gave us good intuition: for
-apparent radii from $2r_\oplus$ to $17r_\oplus$, binarity influences
-apparent planet occurrence rates around Sun-like stars at the level of
-a few percent.
+Adopting the realistic numerical values $n\b/n\s=0.79$, $\alpha =
+3.5$, $\beta=0$, and $\gamma=-2.92$, the summed integrals in
+Equation~\ref{eq:powerlaw_vary_binary} give $(\ldots)\approx 1.503$,
+and $\Gamma\a/\Gamma_0 = 1.048$.  The apparent occurrence rate density
+is 4.8\% higher than the true value.  We conclude that for planets around
+Sun-like stars with orbits within 0.25\,AU and radii in the range
+2--17\,$R_\oplus$, the systematic errors associated with binarity are
+on the order of a few percent.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Varying stars; broken power law planet radius distribution}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Broken power-law planet radius distribution}
 \label{sec:model_3}
@@
     \plottwo{figures/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf}
-    \caption{
-        {\it Left:} apparent rate density ($\Gamma\a$) and rate density for 
-        single stars ($\Gamma_0$). {\it Right:} apparent occurrence
-        rate ($\Lambda\a$) and single star occurrence rate
-        ($\Lambda_0$), over $0.5r_\oplus$ bins.  The true planet
+    \caption{ {\it Left:} Apparent occurrence rate density
+      ($\Gamma\a$), compared to the true occurrence rate density
+      ($\Gamma_0$) for single stars and primary stars in binaries.
+      Three different cases are plotted, with different choices for
+      the true occurrence rate density for secondary stars relative to
+      that for single stars ($Z_2/Z_0$).
+      {\it Right:} Same, but for apparent occurrence
+      rate ($\Lambda\a$) within $0.5\,R_\oplus$ bins.
+      In both cases the true planet
       radius distribution is specified by
-        Equation~\ref{eq:model3_radius_distribution}.  This model
-        assumes that the observer knows the true properties of all the
-        singles and primaries, and that the volume-limited mass ratios
-        of secondaries are drawn from a uniform distribution. Further,
-        we take $Z_0=Z_1=0.5$ throughout; $Z_0,Z_1,Z_2$ are the number
-        of planets per single, primary, and secondary star.  The rate
-        and rate density are related by $\Lambda|_a^b =
-        \int_{a}^{b}\Gamma\,{\rm d}r$.
+      Equation~\ref{eq:model3_radius_distribution}.
     }
@@
 
-Though the details of the planet radius distribution $\Gamma_i(r)$ at
-$r<2r_\oplus$ are currently an active topic of research, by making
-plausible assumptions we can investigate how neglecting binarity might
-bias measurements in this regime.  For instance, consider a broken
-power-law:
+For planets smaller than 2\,$R_\oplus$, the true occurrence rate
+density is more uncertain because such planets are more difficult to
+detect.  To investigate the systematic errors associated with binarity
+on the inferred occurrence rate of Earth-sized planets, we need to
+make plausible assumptions about the true occurrence rate density.
+Obviously if the rate density continues to vary as $r^{-3}$ down to
+much smaller planet sizes, the results of the preceding section will
+hold.  But there is no particular reason to think this will be the
+case and indeed, some investigators have concluded that the rate
+density begins to level off to a constant value as $r$ decreases below
+$R_\oplus$~\citep{petigura_plateau_2013}.  To investigate the
+implications we consider a broken power-law:
 \begin{align}
@@
     \begin{cases}
-        r^\gamma & \text{for } r\geq 2r_\oplus \\
-        {\rm constant} & \text{for } r\leq2r_\oplus.
+        r^\gamma & \text{for } r\geq 2R_\oplus \\
+        {\rm constant} & \text{for } r\leq2R_\oplus.
     \end{cases}
@@
 \end{align}
-At apparent radii $r\a > 2r_\oplus$, the apparent rate density in
-this model is the same as that in
-Section~\ref{sub:powerlaw_varying_binaries}.  At smaller apparaent
-radii the equations are tedious, but still tractable.
-For simplicity, we insert Equation~\ref{eq:model3_radius_distribution}
-into Equation~\ref{eq:general_Gamma_a}, and integrate using a computer
-program. We refer the interested reader to our online
-implementation\footnote{\url{https://github.com/lgbouma/binary_biases},
-commit \texttt{6cb920c}}.
-The output, shown in Figure~\ref{fig:occ_rate_model_3_log}, is
-validated using analytic predictions in the $r\a > 2r_\oplus$ and the
-$r\a < 2r_\oplus/\sqrt{2}$ regimes.  As before, $L\propto M^\alpha
-\propto R^\alpha$, and $\alpha=3.5$, $\beta=0$, $\gamma=-2.92$.
-
-\paragraph{The rate of Earth analogs} The immediately arresting result
-is a ``bump'' in the apparent rate density at apparent radii below
-$2r_\oplus$: the true rate for singles is less than the apparent rate.
-If secondaries host as many planets as single stars, the occurrence of
-these small planets is overestimated by about $50\%$.  The magnitude
-of the systematic error decreases if there are fewer planets around
+In this case the integrals that appear in
+Equation~\ref{eq:general_Gamma_a} are tedious to work out
+analytically, leading us to evaluate them numerically.\footnote{We
+refer the interested reader to our online code for performing this
+computation: \url{github.com/lgbouma/binary_biases}, commit
+\texttt{6cb920c}.} Figure~\ref{fig:occ_rate_model_3_log} shows the
+results, again for the case $n\b/n\s=0.79$, $\alpha = 3.5$, $\beta=0$,
+and $\gamma=-2.92$.
+
+The most obvious aspect of the results is that the occurrence rate
+density of planets smaller than the breakpoint radius of 2\,$R_\oplus$
+is now substantially overestimated.  If secondary stars have the same
+planet population as the single stars, then the occurrence rate
+density of small planets is overestimated by $50\%$.  The magnitude of
+the systematic error decreases if there are fewer planets around
 secondaries; if secondaries host no planets at all, the apparent rate
@@
 
-\paragraph{Hot Jupiter occurrence rates}
-By integrating the rate density from
-Figure~\ref{fig:occ_rate_model_3_log}, we can compare the apparent hot
-Jupiter occurrence rate with the true rate for singles.  The
-difference between the rates is largest when secondaries host no
-planets. In that case, we find $\Lambda_{{\rm HJ},0}/\Lambda_{\rm
-HJ,a} = 1.13$, where
-\begin{equation}
-    \Lambda_{\rm HJ,a} =
-      \int_{8r_\oplus}^{\infty} \Gamma\a(r\a)\,{\rm d}r\a,~~{\rm
+The effects on larger planets are not as substantial.  To be
+quantitative we consider the occurrence rate of giant planets with
+$r>8\,R_\oplus$, by integrating the occurrence rate density displayed
+in Figure~\ref{fig:occ_rate_model_3_log}:
+\begin{equation}
+    \Lambda_{\rm giant,a} =
+      \int_{8\,R_\oplus}^{\infty} \Gamma\a(r\a)\,{\rm d}r\a,~~{\rm
       and}~~
-    \Lambda_{\rm HJ,0} =
-      \int_{8r_\oplus}^{\infty} \Gamma_0(r)\,{\rm d}r.
-\end{equation}
+    \Lambda_{\rm giant,0} =
+      \int_{8\,R_\oplus}^{\infty} \Gamma_0(r)\,{\rm d}r.
+\end{equation}
+In this case the occurrence rate density is underestimated.  The
+difference between the apparent and true rates is largest when the
+secondary stars do not host any planets, and has a magnitude
+$\Lambda_{{\rm g},0}/\Lambda_{\rm g,a} = 1.13$.
 %occ_rate_vs_radius_model_3_withtext_Zsub2_0.00_rpu_22.5.pdf
-If secondaries host half as many planets as single stars, then
-$\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 1.06$.  We pay further
-attention to the issue of hot Jupiter occurrence rates in
-Section~\ref{sec:further_models}.
-
-\paragraph{Fraction of detected planets from a given source}
-
+If instead the secondary stars have half as many giant planets as single
+stars, then the factor is reduced from 1.13 to 1.06.
+
+\subsection{Which star has the planet?}
+\label{subsec:whichstar}
 \begin{figure}[!t]
@@
     \includegraphics[width=\textwidth]{figures/ndet_vs_radius_logx_model_3_fraclines_rpu_22.5_manyZs.pdf}
-    \caption{
-        Fraction of detected planets at a given apparent planet radius
-        that orbit single stars (solid lines), primaries of binaries
-        (dashed lines), and secondaries of binaries (dotted lines).
-        We assume that single stars and primaries have the same number
-        of planets per star, and that the true planet radius
-        distribution is a broken power law
-        (same as Figure~\ref{fig:occ_rate_model_3_log}).
-    }
+    \caption{ Fraction of detected planets that orbit single stars
+      (solid lines), primary stars of binaries (dashed lines), and
+      secondary stars of binaries (dotted lines), as a function of the
+      apparent radius of the planet.  We assume that single stars and
+      primaries have the same number of planets per star.  Three
+      different cases are plotted, differing in the relative
+      occurrence of planets around secondary stars ($Z_2/Z_0$).  The
+      true radius distribution is given by
+      Equation~\ref{eq:model3_radius_distribution}.}
     \label{fig:frac_model_3}
@@
 
-A common situation during transit survey follow-up is for
-high-resolution imaging to reveal multiple stars in a system that
-shows planetary transits.  It is often impossible to rule which star
-hosts the detected planet.  One would intuitively expect that the
-primary star would be the more likely host because at fixed planet
-size, planetary transits around secondaries have smaller amplitudes
-(Equations~\ref{eq:dil_1} and~\ref{eq:dil_2} imply
-$\mathcal{D}_2>\mathcal{D}_1$, if $\alpha=3.5$).  However, this
-reasoning is qualitative, and its assumptions might not always hold.
-
-Our formalism lets us calculate the relative probability that a
-detected planet orbits a single, primary, or secondary star in a more
-general manner.  To perform the calculation, we use expressions given
-in the appendix for the number of detections coming from each type of
-system (Equations~\ref{eq:n_det_0},~\ref{eq:n_det_1},
-and~\ref{eq:n_det_2}).  We then divide out by the total number of
-detections at each apparent radius.  Figure~\ref{fig:frac_model_3}
-shows the result: if high-resolution imaging reveals a source with
-transits to be a binary system, the detected planet does usually orbit
-the primary.
-
-If the apparent radius of the system is above $2r_\oplus$, and planets
-exist about primaries and secondaries at equal rates, then the planet
-is $3$ times more likely to orbit the primary than the
-secondary.  If secondaries host half as many planets as primaries,
-then a detected planet is $5$ times more likely to orbit the
-primary.
-
-The situation for apparent radii below $2r_\oplus$ is more nuanced.
-For the two cases in which secondaries host fewer planets than
-primaries, detected planets in binaries are still always more likely
-to orbit the primary.  However, if planets exist at the same rate in
-primaries and secondaries, then below apparent radii of $0.4r_\oplus$,
-more of the detected planets in binaries come from secondaries~--~they
-have all been diluted down from larger true planetary radii.
-Rephrased, going from apparent radii of $2r_\oplus$~to~$1.4r_\oplus$,
-the fraction of detected planets with binary companions increases by
-anywhere from $6\%$~to~$12\%$, depending on the relative occurrence of
-planets about primaries and secondaries.  We compare this prediction
-with recent observations in Section~\ref{sec:discussion}.
-%~\footnote{
-%The increase can be derived analytically.  Let the fraction of total
-%detected planets from primaries at a given apparent radius be
-%$F_1(r\a)$, so $F_1(r\a) \equiv n_{\rm det}^1(r\a)/n_{\rm det}^{\rm
-%tot}$.  Let the analogous quantity for secondaries be $F_2(r\a)$.  In
-%the planet-less secondaries case ($F_2(r\a)=0$), one can analyze
-%Eqs~\ref{eq:n_det_0} and~\ref{eq:n_det_1} semi-analytically and show
-%that $F_1(2r_\oplus/\sqrt{2})/F_1(2r_\oplus) \approx 1.19$.
-%check_companion_fractions.py, and LB's notes 2017/12/21.0 }.
+Our formalism also provides a way to calculate the relative
+probability that a detected planet orbits a single star, the primary
+star, or a secondary star.  These can be obtained from the
+generalizations of Equations~\ref{eq:n0}--\ref{eq:n2}, which are
+derived in the \hyperref[sec:appendix]{appendix}.  This information
+can be used to help interpret the results of a transit survey.  It is
+also relevant to the fairly common situation in which transits are
+detected from a source, and subsequent high-resolution imaging reveals
+the source to be a multiple-star system.  The question then arises:
+which star is the host of the detected planet?  Without further
+observations the answer is often unclear.  To illustrate we return to
+the scenario described in the previous section: a broken power-law
+radius distribution with $\gamma=-2.92$, along with the choices
+$n\b/n\s=0.79$, $\alpha = 3.5$, and $\beta=0$.  We also try different
+assumptions for the rate of planets around secondaries, i.e.,
+different choices for $Z_2/Z_0$.  We use
+Equations~\ref{eq:n_det_0}--\ref{eq:n_det_2} to compute the number of
+detections from single stars, primaries, and secondaries, and divide
+by the total number of detections at each apparent radius.
+
+Figure~\ref{fig:frac_model_3} shows the results.  When the apparent
+radius exceeds $2\,R_\oplus$, and planets exist about secondaries at
+the same rate as the primary star ($Z_2/Z_0=1$), then the planet is
+$3$ times more likely to orbit the primary star than the secondary
+star.  If secondaries host half as many planets as primaries
+($Z_2/Z_0=0.5$), then a detected planet is $5$ times more likely to
+orbit the primary star.
+
+The situation for smaller apparent radii is more nuanced.  For
+$Z_2/Z_0=0$ or 0.5, any transit signals from binaries are still always
+more likely to arise from the primary star.  However, if planets exist
+at the same rate in primaries and secondaries ($Z_2/Z_0=1$), then
+below apparent radii of $0.4\,R_\oplus$, more of the detected planets
+in binaries come from secondaries.  They are actually much larger
+planets for which $\delta$ has been substantially reduced by the light
+from the primary star.  As we consider apparent radii ranging from 2
+to 1.4\,$R_\oplus$, the fraction of detected planets with binary
+companions increases by anywhere from $6\%$~to~$12\%$, depending on
+the relative occurrence of planets about primaries and secondaries.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Further models: radius gaps, Gaussian HJ distributions}
+\subsection{A gap in the radius distribution}
 \label{sec:further_models}
-
-The radius distribution specified by
-Equation~\ref{eq:model3_radius_distribution} misses some important
-features revealed by state of the art planet occurrence studies.
-
-\paragraph{Precise features of the radius valley}
 
@@
     \plottwo{figures/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf}
-    \caption{
-        {\it Left:} rate density and {\it right:} rate as a function
-        of planet radius in a model with a radius gap
-        (Equation~\ref{eq:model4_radius_distribution}).  Other than
-        the intrinsic radius distribution, this model has the same
-        assumptions as Figure~\protect\ref{fig:occ_rate_model_3_log}.
-    }
+    \caption{ {\it Left:} True and apparent occurrence rate densities,
+      and {\it right:} occurrence rates, as a function of planet
+      radius, using a model for the radius distribution that exhibits
+      a gap between 1.5 and 2\,$R_\oplus$
+      (Equation~\ref{eq:model4_radius_distribution}). }
     \label{fig:model_4}
@@
 \citet{fulton_california-_2017} recently reported a ``gap'' in the
-radius-period
-plane~\citep{petigura_california-kepler_2017,johnson_california-kepler_2017}.
-The existence of the gap has been independently corroborated from a
-sample of KOIs with asteroseismically-determined stellar
-parameters~\citep{van_eylen_asteroseismic_2017}.  Precise measurement
-of the gap's features, in particular its width, depth, and shape, will
-require accurate occurrence rates.  To illustrate binarity's role in
-this problem, we make identical assumptions as in
-Section~\ref{sec:model_3}, but instead assume an intrinsic radius
-distribution
+radius distribution of close-in planets around Sun-like stars, between
+planet sizes of 1.5 and 2\,$R_\oplus$.  This can also be visualized as
+a ``valley'' in the occurrence rate density as a function of radius
+and period.  The existence of the gap has been independently
+corroborated from a sample of KOIs with asteroseismically-determined
+stellar parameters~\citep{van_eylen_asteroseismic_2017}.  Such a
+feature had been predicted as a consequence of the gradual
+photo-evaporation of the hydrogen-helium atmospheres of small rocky
+planets, during the first 100~Myr of the age of the system when the
+host star produces a higher flux of ultraviolet and X-ray
+radiation~\citep{owen_evaporation_2017}.
+
+The occurrence calculations that led to this discovery, like almost
+all occurrence calculations, did not carefully account for
+unresolved binaries.  Intuitively we expect the effect of unresolved
+binaries to have a blurring effect on the radius distribution, filling
+in any gaps in the radius distribution and making them appear less
+empty than in reality.  To investigate the quantitative effects we
+make identical assumptions as in Section~\ref{sec:model_3}, except
+that the radius distribution is assumed to have a complete absence of
+planets with sizes between 1.5 and 2\,$R_\oplus$:
 \begin{align}
@@
     \begin{cases}
-        r^\gamma & \text{for } r\geq 2r_\oplus, \\
-        0 & \text{for } 1.5r_\oplus < r < 2r_\oplus, \\
-        {\rm constant} & \text{for } r\leq1.5r_\oplus.
+        r^\gamma & \text{for } r\geq 2\,R_\oplus, \\
+        0 & \text{for } 1.5\,R_\oplus < r < 2\,R_\oplus, \\
+        {\rm constant} & \text{for } r\leq 1.5\,R_\oplus.
     \end{cases}
@@
 \end{align}
-Figure~\ref{fig:model_4} shows the resulting true and apparent rates.
-If left uncorrected, binarity makes the gap appear more shallow, and
-flattens the step-function edges.  Of course, effects unrelated to
-binarity would also ``blur'' the gap in the planet radius dimension.
-In particular, the valley's period-dependence is almost certainly not
-flat \citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.  This
-means that any study measuring the gap's width or depth while
-accounting for binarity must either perform tests at fixed orbital
-period, or else marginalize over period and account for the associated
-blurring in the planet radius dimension.
-
-\paragraph{The HJ distribution is not a power law}
-
-In the recent study by~\citet{petigura_CKS_2017}, hot Jupiters appear
-as an island in period-radius space, rather than as a continuous
-component of a power law distribution.  This means that the apparent
-HJ rates computed in Section~\ref{sec:model_3} are probably
-inaccurate.  Instead, let us consider a Gaussian radius shape
-function,
-\begin{equation}
-    f(r) \propto \exp \left( -\frac{(r-\bar{r})^2}{2\sigma^2} \right),
-\end{equation}
-with $\bar{r} = 14r_\oplus$ and $\sigma = 2r_\oplus$.  As always,
-$\Gamma_i(r) = Z_i f(r)$.  We then compute $\Gamma\a(r\a)$, and plot
-it in Figure~\ref{fig:gaussian_HJ}.  Integrating over $r\a >
-8r_\oplus$ to find hot Jupiter rates, we find the opposite effect as
-in the power law model.  If secondaries host any planets at all, the
-apparent HJ rate is {\it greater} than the true rate for singles.  For
-instance, if the hot Jupiter rate about secondaries and singles
-is equal, then $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 0.81$.
+Figure~\ref{fig:model_4} shows the resulting true and apparent occurrence
+rate densities.
+For the case $Z_2/Z_0=1$, unresolved binaries reduces the contrast
+of the gap by nearly a factor of two, while also producing
+spurious features for apparent sizes beneath 1.5\,$R_\oplus$.
+Thus the gap identified by \citet{fulton_california-_2017} may be
+even more devoid of planets than it appears.
+
+%Of course, effects unrelated to
+%binarity would also ``blur'' the gap in the planet radius dimension.
+%In particular, the valley's period-dependence is almost certainly not
+%flat \citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.  This
+%means that any study measuring the gap's width or depth while
+%accounting for binarity must either perform tests at fixed orbital
+%period, or else marginalize over period and account for the associated
+%blurring in the planet radius dimension.
+
+\subsection{Gaussian radius distribution}
+
+The planet population may include some special members with a distinct
+radius distribution.  For example in the recent study
+by~\citet{petigura_CKS_2017}, hot Jupiters appear as an island in
+period-radius space, rather than as a component of a power-law
+distribution extending to smaller planets and longer periods.
+For this reason we test the effects of unresolved binaries
+on a Gaussian radius distribution,
+\begin{equation}
+    f(r) \propto \exp \left[ -\frac{(r-\bar{r})^2}{2\sigma_r^2} \right],
+\end{equation}
+with $\bar{r} = 14\,R_\oplus$ and $\sigma_r = 2\,R_\oplus$.  As before,
+we allow for different normalizations of the planet populations around
+single, primary, and secondary stars: $\Gamma_i(r) = Z_i f(r)$.
+Figure~\ref{fig:gaussian_HJ} shows the results for the apparent radius
+distribution, $\Gamma\a(r\a)$.  As one would expect, the effect is to
+smear the radius distribution toward smaller values, because some of
+the hot Jupiters now appear to be smaller planets.  Less obviously,
+the integrated rate of hot Jupiters is also affected.  We calculate
+the apparent hot Jupiter rate by integrating the apparent rate density
+for $r\a > 8\,R_\oplus$.  If secondaries host any planets at all, the
+apparent rate is {\it greater} than the true rate.  For instance, when
+hot Jupiters are just as common around secondary stars as single or primary
+stars, then $\Lambda_{\rm HJ,a}/\Lambda_{{\rm HJ},0} = 1.23$.
 %int_rate_density_vs_radius_model_7_withtext*manyZs.pdf
-Qualitatively, the apparent HJ rate is greater than the true rate for
-singles because binary systems have extra uncounted stars that
-yield hot Jupiter detections.
+The apparent rate is higher because a larger number of stars were
+searched than are accounted for in the rate calculation.
 
@@
     \includegraphics[width=.6\textwidth]{figures/int_rate_density_vs_radius_model_7_rpu_22.5_manyZs.pdf}
-    \caption{
-        Rate density for a population of planets with true radii $r$
-        drawn from a Gaussian with mean $14r_\oplus$ and standard
-        deviation $2r_\oplus$.  This is similar to the hot Jupiter
-        distribution presented by~\citet{petigura_CKS_2017}.
-    }
+    \caption{ True and apparent occurrence rate densities, for a
+      population of planets with true radii $r$ drawn from a Gaussian distribution
+      with mean $14\,R_\oplus$ and standard deviation $2\,R_\oplus$.  This
+      is similar to the hot Jupiter distribution presented
+      by~\citet{petigura_CKS_2017}.  }
     \label{fig:gaussian_HJ}

### 2018-02-23 paper/main.tex
jnw discussion edits

@@
 \begin{equation}
-    {N_\star(r\a)\over{1+\mu}}\cdot {n_{\rm b}\over n_{\rm s}}
+    {N_\star(r\a)\over{1+\mu}}\, {n_{\rm b}\over n_{\rm s}}
     \left[{L(M) + L(qM) \over L(M)}\right]^{3/2}
@@
 
-\section{Discussion}
+\section{Summary and Discussion}
 \label{sec:discussion}
 
-\paragraph{How bad is ignoring binarity?}
-This study has shown that under a reasonable set of simplifying
-assumptions, ignoring binarity introduces systematic errors to star
-and planet counts in transit surveys, which then biases derived
-occurrence rates.  Thus far, occurrence rate calculations\footnote{ A
-list of occurrence rate papers is maintained at
-\url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
-} using transit survey data have mostly ignored stellar
+Ignoring binarity introduces systematic errors to star and planet
+counts in transit surveys, which in turn lead to biases in the derived
+planet occurrence rates.  Thus far, occurrence rate calculations using
+transit survey data have mostly ignored stellar
 multiplicity~\citep[\textit{e.g.},][]{howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,dressing_occurrence_2015,burke_terrestrial_2015}.
-For {\it Kepler} occurrence rates specifically, it seems that no one
-has yet carefully assessed binarity's importance, or lack thereof.
-This study does not resolve the problem; it only suggests the
-approximate scale of the systematic errors.  Section~\ref{sec:model_2}
-suggests that for apparent radii above $2r_\oplus$, binarity can be
-ignored down to a precision of a few percent.  For apparent radii
-below $2r_\oplus$, the picture is less forgiving:
-Section~\ref{sec:model_3} suggests that the apparent rates around
-single stars could be overestimated by as much as 50\%.
-
-\paragraph{The rate of Earth analogs}
+We do not claim to have solved this problem. Our aim was to clarify
+the various effects and assess the size of the errors in various
+situations. We hope that our formalism will also be useful to those
+investigators who do attempt more realistic calculations of occurrence
+rates.
+
+The calculations presented in Section~\ref{sec:model_2} suggest that
+for planets around Sun-like stars with periods shorter than a few
+months and apparent radii exceeding $2\,R_\oplus$, binarity can
+basically be ignored.  The errors are only of order a few percent.
+For apparent radii below $2\,R_\oplus$, nature may not be as
+forgiving.  The size of the effect depends on the true radius
+distribution and in particular whether it continues to vary as
+$\sim$$r^{-3}$ down to 1\,$R_\oplus$ and below.  The calculations
+presented in Section~\ref{sec:model_3} suggest that the apparent rates
+could be overestimated by as much as 50\%.
+
+\paragraph{Earth-like planets} For the specific problem of calculating the occurrence rate
+$\eta_\oplus$ of Earth-like planets with periods of order one year,
+even a 50\% systematic error would not be the dominant source of
+uncertainty at the moment.  Estimates by
 \citet{youdin_exoplanet_2011},~\citet{petigura_prevalence_2013},~\citet{dong_fast_2013},~\citet{foreman-mackey_exoplanet_2014},
-and~\citet{burke_terrestrial_2015} have found that between $0.03$ and
-$1$ Earth-like planets exist per Sun-like star, depending on
-assumptions that are made when calculating the
-rate~\citep[see][Figure~17]{burke_terrestrial_2015}.  Assuming a
-broken power-law, we showed that unrecognized binaries could cause
-overestimates in the rate of Earth analogs of up to 50\%.  This
-systematic effect is smaller than the other factors that currently
-dominate the dispersion in $\eta_\oplus$ measurements.  If future
-analyses determine absolute values of $\eta_\oplus$ to better than a
-factor of two, binarity will likely merit closer attention.
-
-One caveat is that none of our models included the rate density's
-period-dependence. However, binaries with separations $\lesssim
-10\,{\rm AU}$ could provoke dynamical instabilities, leading to fewer
-Earth-like planets per
+and~\citet{burke_terrestrial_2015} have found values of $\eta_\oplus$
+ranging from $0.03$ to unity, with the wide variance arising from
+small-number statistics as well as a host of other systematic
+errors~\citep[see][Figure~17]{burke_terrestrial_2015}.  Rapid progress
+is expected soon, though, and binarity will merit closer attention in
+the future.  It may also be worth investigating the possible effects
+of any dependence of occurrence rate densities on the period of the
+binary.  Binaries with separations $\lesssim 10\,{\rm AU}$ could
+provoke dynamical instabilities, leading to fewer Earth-like planets
+per
 star~\citep[\textit{e.g.},][]{holman_long-term_1999,wang_influence_2014,
-kraus_impact_2016}.  This would affect transit survey measurements of
-$\eta_\oplus$ beyond our rough estimate.
-
-\paragraph{Hot Jupiter rate discrepancy}
-While unresolved binaries may bias $\eta_\oplus$ measurements, our
-approach suggests that they do not influence the hot Jupiter rate
-discrepancy.  The ``discrepancy'' is that RV surveys find roughly
-twice as many hot Jupiters per Sun-like star as do transit surveys
-(roughly $1\%$~vs.~$0.5\%$, respectively).  We summarize hot
-Jupiter rates reported by different surveys in
-Table~\ref{tab:hj_rates}.
-
-Though the disagreement is only weakly significant ($<3\sigma$), one
-reason to expect a difference is that the RV sample is biased towards
-metal-rich stars, which host more giant
-planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005,gould_frequency_2006}.
-Investigating the discrepancy from the metallicty
-angle,~\citet{guo_metallicity_2017} measured the {\it Kepler} field's
-mean metallicity to be $[{\rm M/H}]_{\rm Kepler}= -0.045\pm0.009$,
-which is lower than the California Planet Search's mean of $[{\rm
-M/H}]_{\rm CPS}= -0.005\pm0.006$.  The former value agrees with that
-found by \citet{dong_metallicities_2014}.  Refitting for the
-metallicity exponent in $\Lambda_{\rm HJ} \propto 10^{\beta [{\rm
-M/H}] }$, \citeauthor{guo_metallicity_2017}\! found $\beta = 2.1\pm
-0.7$, and noted that the metallicity difference could account for
-0.2\% of the needed 0.5\% difference between the measured CKS
-and {\it Kepler}\ rates\footnote{ \citet{petigura_CKS_2017} recently
-found $\beta = 3.4^{0.9}_{-0.8}$.  If true, this implies that
-metallicity could account for about half of the hot Jupiter rate
-discrepancy.  }.  \citeauthor{guo_metallicity_2017}\!  concluded
-that ``other factors, such as binary contamination and imperfect
-stellar properties'' must also be at play.
-
-Radial velocity surveys usually reject visual and spectroscopic
-binaries~\citep{wright_frequency_2012}, so their hot Jupiter rates are
-closer to the rate for single stars than the rates reported by transit
-surveys.  However, we found in Section~\ref{sec:further_models} that
-when assuming a Gaussian radius distribution, apparent hot Jupiter
-rates are {\it greater} than the true rate around singles: the effect
-goes the wrong way.  There could be other systematic factors behind
-the difference~--~but they are unlikely to be related to binarity.
-
-%in spectroscopic follow-up of transiting planet candidates, the
-%prevalence of astrophysical false-positives may also lead to a
-%tendency against confirming transiting planets in binary systems.  A
-%separate observational bias is that the RV surveys typically observe
-%chromospherically ``quiet'' stars, which may bias their detection
-%probability high~\citep{bastien_radial_2014}.
-
-\begin{comment}
-  If we believe the assumed power law radius distribution, we can ask
-  whether this ``correction factor'' might help resolve the
-  discrepancy.  Explicitly, we ask: what is the probability of
-  \citet{wright_frequency_2012}'s result, given a rate drawn from the
-  stated bounds of~\citet{petigura_CKS_2017}?  In other words, we
-  first take the true HJ rate per thousand stars as $\Lambda_{\rm HJ}
-  = 5.7 \pm 1.3$, with Gaussian uncertainties.  We then draw from a
-  Poisson distribution and compute the probability of detecting at
-  least 10 hot Jupiters in a sample of 836 stars.  Without accounting
-  for binarity or metallicity, only 4\% of RV surveys would detect at
-  least 10 hot Jupiters.  If we multiply $\Lambda_{\rm HJ}$ by $1.2$
-  to account for~\citet{guo_metallicity_2017}'s measured metallicity
-  difference between the {\it Kepler}\ field and the local solar
-  neighborhood, 9\% of RV surveys would detect at least 10 hot
-  Jupiters.  If we multiply once more by $1.13$ to account for
-  binarity's supposed bias, we find that 14\% of RV surveys would
-  detect at least 10 hot Jupiters, still suggesting a weak
-  discrepancy.  This suggestion should be taken with caution, because
-  it (incorrectly) assumes a power law radius distribution.
-\end{comment}
-
-\paragraph{Does a detected planet orbit the primary or secondary?}
-
-A separate reason to address stellar multiplicity in transit surveys
-is that it can radically alter the interpretation of planet candidates
-on a system-by-system level.  To identify and correct for unseen
-stellar companions, high-resolution imaging campaigns have surveyed
-almost all {\it Kepler}\ Objects of Interest~\citep{
+  kraus_impact_2016}.  This would affect transit survey measurements
+of $\eta_\oplus$ beyond our rough estimate.
+
+\paragraph{Hot Jupiters} Another frequently discussed problem
+involving occurrence rates is the discrepancy between the occurrence
+rates of hot Jupiters that have been measured in different surveys, as
+summarized in Table~\ref{tab:hj_rates}.  In particular, the California
+Planet Search (CPS), a Doppler survey, found a higher rate ($12\pm 2$
+per thousand stars) than the {\it Kepler} transit survey
+($5.7^{+1.4}_{-1.2}$).  It has been suggested that unresolved binaries
+in the {\it Kepler} sample might be an important factor, but the
+calculations presented in Section~\ref{sec:further_models} suggest
+that this is not the case.  We found that the effects of unresolved
+binaries are likely to result in an overestimation of the hot-Jupiter
+occurrence rate, which would worsen the discrepancy, rather than
+relieve it. Some other possibilities are errors in stellar
+classification of the {\it Kepler} stars, as well as differences in
+the metallicity of the stars in each survey.  The occurrence rate of
+hot Jupiters is known to vary strongly with stellar metallicity, with
+$\Lambda \propto 10^{3.4{\rm [M/H]}}$ according to a recent
+study~\citep{petigura_CKS_2017}.  \citet{guo_metallicity_2017} found
+the mean metallicity of the {\it Kepler} stars to be [M/H]~$=-0.045\pm
+0.009$, which is only slightly lower than that of the stars in the
+Doppler survey, $-0.005\pm 0.006$.  Nevertheless, given the strong
+dependence of occurrence on metallicity, even a difference of
+$0.04$~dex could account for a factor of $10^{3.4\cdot 0.04} = 1.37$
+in the occurrence rate.  After correcting for metallicity, the
+discrepancy between the {\it Kepler} and CPS occurrence rates is
+reduced to the 1.7$\sigma$ level.
+
+\paragraph{Radius corrections} Another application of our formalism is
+to help in those cases in which it is not clear whether the primary or
+secondary star is the source of a transit signal.  By this point
+almost all of the {\it Kepler}\ Objects of Interest have been examined
+with high resolution imaging~\citep{
   howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
@@
 The results of these programs have been summarized
-by~\citet{furlan_kepler_2017}, and they represent an important advance
-in understanding the KOI sample's multiplicity statistics.
-
-An immediate application is to reassess the radii of detected planets.
-Doing so, \citet{hirsch_assessing_2017} recently found that for their
-sample of KOIs in binaries, the planet radii are underestimated by
-factors $r/r\a = 1.17$ if all planets orbit primaries, and $r/r\a =
-1.65$ if detected planets are equally likely to orbit primaries and
-singles.  This approach makes minimal assumptions about the likelihood
-that a planet orbits the primary vs.~the secondary
-(though~\citealt{hirsch_assessing_2017} do also consider weighting
-radius corrections by planet occurrence).
-
-Our approach provides a suggestion of how to assess the probability
-that a detected planet in a binary system orbits either component.
-The problem requires assuming both the underlying radius distribution,
-and the relative number of planets per primary and secondary star.  We
-found that for a broken power law radius distribution, with equal
-occurrence rates about primaries and secondaries, detected planets in
-binary systems are usually more likely to orbit the primary
-(Figure~\ref{fig:frac_model_3}).  For apparent radii greater than
-$2r_\oplus$, the odds of primary:secondary are 8:3.  The odds increase
-for the planet to orbit the secondary increase at smaller apparent
-radii, and reach 1:1 at $r\a=0.4r_\oplus$.  For {\it Kepler}, this
-suggests that for almost all confirmed KOIs in multiple star systems,
-the planet most likely orbits the primary.
-
-\paragraph{Fraction of detected planets with binary companions}
+by~\citet{furlan_kepler_2017}. Based on this information,
+\citet{hirsch_assessing_2017} re-assessed the radius measurements of
+the {\it Kepler} planets in binaries. They found that planet radii are
+generally underestimated by a factor $r/r\a = 1.17$ if all planets
+orbit primaries, and $r/r\a = 1.65$ if detected planets are equally
+likely to orbit primaries and singles.  Our formalism provides a way
+to assess the relative probabilities that a detected planet orbits the
+primary or secondary star.  The calculations presented in
+\S\,\ref{subsec:whichstar} suggest that in almost all cases the planet
+most likely orbits the primary star.
+
+\begin{comment}
+% JNW: These 2 sections do not seem very interesting.
+  {\paragraph{Fraction of detected planets with binary companions}
 A related effect is that some detected planets are more likely to be
@@
 predicts that the fraction of detected planets with binary companions
-should increase by $6$~to~$12\%$ going from $2r_\oplus$ to
-$1.4r_\oplus$.
+should increase by $6$~to~$12\%$ going from $2R_\oplus$ to
+$1.4R_\oplus$.
 
@@
 \begin{itemize}
-    \item Earths ($r\a < 1.6r_\oplus$): $16.3 \pm 1.0\%$, from 1480
+    \item Earths ($r\a < 1.6R_\oplus$): $16.3 \pm 1.0\%$, from 1480
     systems.
-    \item Neptunes ($1.6r_\oplus < r\a < 3.9 r_\oplus$): $13.0 \pm
+    \item Neptunes ($1.6R_\oplus < r\a < 3.9 R_\oplus$): $13.0 \pm
     0.8\%$, from 2058 systems.
-    \item Saturns ($3.9r_\oplus < r\a < 9 r_\oplus$): $13.6 \pm 2.0\%$, from 338 systems. 
-    \item Jupiters ($r\a > 9r_\oplus$): $19.0 \pm 2.8\%$, from 247 systems. 
+    \item Saturns ($3.9R_\oplus < r\a < 9 R_\oplus$): $13.6 \pm 2.0\%$, from 338 systems. 
+    \item Jupiters ($r\a > 9R_\oplus$): $19.0 \pm 2.8\%$, from 247 systems. 
 \end{itemize} 
@@
 be interesting to see whether this effect is borne out by further
-observations.
+observations.}
 
@@
 computation~\citep[\textit{e.g.},][]{morehead_understanding_2016}.
+
+\end{comment}
 
@@
 
+\begin{comment}
 \section{Conclusion}
-\label{sec:conclusion}
-
+% JNW: Material seems redundant.
   This study presented a framework for estimating the impact of
@@
     binarity influences apparent planet occurrence rates at the few
-    percent level. This applies for apparent radii from $2r_\oplus$ to
-    $17r_\oplus$ (Section~\ref{sec:model_2}).
+    percent level. This applies for apparent radii from $2R_\oplus$ to
+    $17R_\oplus$ (Section~\ref{sec:model_2}).
 %
 \item Assuming a broken-power law planet radius distribution, with the
-  \citet{howard_planet_2012} exponent above $2r_\oplus$ and a constant
-    occurrence below $2r_\oplus$, the rate density for radii below
-    $2r_\oplus$ is overestimated. The magnitude of the error, $\Delta
+  \citet{howard_planet_2012} exponent above $2R_\oplus$ and a constant
+    occurrence below $2R_\oplus$, the rate density for radii below
+    $2R_\oplus$ is overestimated. The magnitude of the error, $\Delta
     \Gamma_0 = |\Gamma_0 - \Gamma\a|/\Gamma_0$, can easily reach
@@
 %
-\item Detected planets with apparent radii greater than $0.5r_\oplus$
+\item Detected planets with apparent radii greater than $0.5R_\oplus$
   that are revealed by high-resolution imaging surveys to exist in
@@
 \item Near the break in occurrence as a function of planet
-  radius at $2r_\oplus$, the fraction of detected planets with
+  radius at $2R_\oplus$, the fraction of detected planets with
     binary companions should increase by roughly $5$~to~$10\%$
@@
 rates.
+\end{comment}
 
@@
 
-This appendix derives Equation~\ref{eq:general_Gamma_a} through a more
-straight-forward, but also more tedious, procedure than that of
-Section~\ref{sec:general_formula}.   First, note that analogous to
-Equation~\ref{eq:occ_rate_simple}, the apparent rate density $\Gamma\a$ can be
-written
+Here we present an alternative derivation of
+Equation~\ref{eq:general_Gamma_a}.  We also generalize a bit further,
+by allowing the occurrence rate density to depend on stellar mass $M$
+as well as planet radius $r$.  We begin by writing the apparent rate
+density $\Gamma\a$ as (in analogy to
+Equation~\ref{eq:occ_rate_simple})
 \begin{equation}
@@
 \end{equation}
-where $n_{\rm det}$ is the number of detected planets, per unit
-$(r\a, M\a)$, with apparent radius $r\a$ orbiting stars of
-apparent mass $M\a$.   The planets with $(r\a, M\a)$ are associated
-with systems of many different planetary and stellar properties, so
-$n_{\rm det}(r\a, M\a)$ is given by the convolution of the true rate
-density, $\Gamma(r, M)$, and $\mathcal{N}_\star(r\a, M\a; r, M)$, the
-number of searchable stars per unit $(r\a, M\a)$ that give $(r\a,
-M\a)$  when the true system actually has properties $(r, M)$.
-Mathematically,
+where $n_{\rm det}(r\a,M\a)$ is the number of detected planets per
+star with radius $r\a$ orbiting stars of apparent mass $M\a$, per unit
+$r\a$ and $M\a$.  This collection of planets with the same apparent
+properties actually includes planets with a variety of true sizes and
+host star masses.  We may write $n_{\rm det}(r\a, M\a)$ as the
+convolution of the true occurrence rate density, $\Gamma(r, M)$; and
+$\mathcal{N}_\star(r\a, M\a; r, M)$, the number of searchable stars
+per unit $(r\a, M\a)$ for which a planet with true properties $(r, M)$
+would appear to be a planet with apparent properties $(r\a, M\a)$:
 \begin{align}
     n_{\rm det}(r\a, M\a) &=
-    \sum_i n_{\rm det}^i(r\a, M\a) \\
+    \sum_{i=0}^2 n_{\rm det}^i(r\a, M\a) \\
     &=
-    \sum_i \int \mathrm{d}r \mathrm{d}M \,
+    \sum_{i=0}^2 \int \mathrm{d}r \int \mathrm{d}M \,
     \mathcal{N}_\star^i(r\a,M\a; r,M)
-    \, \Gamma_i(r,M) \, p_{\rm tra}(r,M),
+    \,\Gamma_i(r,M) \, p_{\rm tra}(M),
     \label{eq:n_det}
 \end{align}
-where $i$ specifies the type of true host star (0: single, 1:
-primary, 2: secondary).  The problem reduces to the evaluation of
-\begin{equation}
-    \mathcal{N}_\star^i(\pp\a,\ps\a; \pp, \ps)
-\end{equation}
-for planets around single stars, primaries in binaries, and
-secondaries in binaries.
-
-\paragraph{Single stars} For $i=0$, 
+where $i$ specifies the true type of host star, with 0 for single
+stars, 1 for primary stars, and 2 for secondary stars.  We now proceed
+to calculate $\mathcal{N}_\star^i(r\a,M\a; r,M)$.
+
+\paragraph{Single stars}
+For single stars,
 \begin{equation}
@@
 \end{equation}
-where $\hat{\delta}$ is the Dirac delta function, so
+where $\hat{\delta}$ is the Dirac delta function.  Therefore,
 \begin{equation}

### 2018-02-24 paper/main.tex
jnw appendix edits

@@
 \begin{align}
-  dN_{{\rm det},0} &= 
+  {\rm d}N_{{\rm det},0} &= 
       \frac{N_\star(r\a) p_{\rm tra}}{1+\mu}
@@
   \label{eq:n0} \\
-  dN_{{\rm det},1} &= 
+  {\rm d}N_{{\rm det},1} &= 
       \frac{\mu N_\star(r\a) p_{\rm tra}}{1+\mu} 
@@
 	\label{eq:n1} \\
-  dN_{{\rm det},2} &=
+  {\rm d}N_{{\rm det},2} &=
       \frac{\mu N_\star(r\a) p_{\rm tra}}{1+\mu} 
@@
 \begin{equation}
-  \Gamma\a(r\a) = \frac{dN_{\rm det}}{dr\a} \frac{1}{N_\star(r\a) p_{\rm tra}} =
+  \Gamma\a(r\a) = \frac{{\rm d}N_{\rm det}}{{\rm d}r\a} \frac{1}{N_\star(r\a) p_{\rm tra}} =
   \frac{\Gamma_0(r\a)}{1+\mu} +
@@
     &=
-    \sum_{i=0}^2 \int \mathrm{d}r \int \mathrm{d}M \,
+    \sum_{i=0}^2 \int \mathrm{d}r \!\int\! \mathrm{d}M \,
     \mathcal{N}_\star^i(r\a,M\a; r,M)
@@
 
-\paragraph{Primaries in binaries}
-The number of primaries with apparent parameters $(r\a,M\a)$ given the
-true parameters $(r,M)$ is
+\paragraph{Primary stars}
+For primary stars in binary systems, 
 \begin{equation}
     \mathcal{N}_\star^1(r\a, M\a; r, M)
-    = \int 
-      \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M),
+    = \int_0^1 
+      \mathrm{d}q\,f(q)\,\mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M),
     \label{eq:fancyN_s_1}
 \end{equation}
-where $f(q)$ is the volume-limited binary mass ratio distribution.
-Since we assume that binaries are assigned the mass of the primary,
+where $f(q)$ is the binary mass ratio distribution in a volume-limited sample
+of stars.  Since we are assuming that the observer will perceive a binary to be a single
+star with the same properties as the primary star,
 \begin{equation}
@@
 In this case, $\mathcal{N}_{{\rm s},q}^1$ is non-zero only at
-$r\a=R\a\sqrt{\delta}$, and the observed depth is
+$r\a=R\a\sqrt{\delta}$, and the observed transit depth is
 \begin{equation}
@@
 \begin{equation}
-    \mathcal{D}_1=\sqrt{L_{\rm tot}(M\a, q) \over L(M\a)}.
+    L_{\rm tot}(M\a,q) = L(M\a) + L(qM\a),~~\mathcal{D}_1=\sqrt{L_{\rm tot}(M\a, q) \over L(M\a)}.
 \end{equation}
@@
 \end{equation}
-where the argument for the number of searchable single stars,
-$N_\star^0$, could also be expressed as $(\delta, L(M\a))$.
+%where the argument for the number of searchable single stars,
+%$N_\star^0$, could also be expressed as $(\delta, L(M\a))$.
 Applying Equation~\ref{eq:primary_normalization},
@@
     \, {n\b\over n\s} \, \mathcal{D}_1^3
-    \,\hat{\delta} \left(r\a-\frac{r}{\mathcal{D}_1}\right)\hat{\delta}(M\a-M).
+    \,\hat{\delta} \left[r\a-\frac{r}{\mathcal{D}_1}\right]\hat{\delta}(M\a-M).
     \label{eq:N_s_1}
@@
 
-\paragraph{Secondaries in binaries}
+\paragraph{Secondary stars}
 In this case, $M=qM_1=qM\a$, so
@@
     \mathcal{N}_\star^2(r\a, M\a; r, M)
-    =\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r\a, M\a, q; r, M),
+    =\int_0^1 \mathrm{d}q~f(q)\,\mathcal{N}_{{\rm s}, q}^2(r\a, M\a, q; r, M),
 \end{equation}
@@
 
-One might worry in Equation~\ref{eq:mathcal_N_s_2} that we opt to
-write $\mathcal{N}\s^2 \propto \hat{\delta}(M\a - M/q)$, rather than
-$\propto \hat{\delta}(M\a q - M)$ or some other delta function with the same
-functional dependence, but a different normalization once integrated.
-We do this because the delta function in
-Equation~\ref{eq:mathcal_N_s_2} is defined with respect to the measure
-${\rm d}M\a$, not ${\rm d}M$.  This is because $\mathcal{N}\s^2$ is
-defined as a number per $r\a$, per $M\a$.
-
 \paragraph{Number of detected planets}
-Marginalizing per Equation~\ref{eq:n_det}, we find
+Inserting the results into Equation~\ref{eq:n_det}, we find
 \begin{align}
@@
     n_{\rm det}^0(r\a, M\a)
-    &=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_\star^0(r\a, M\a; r, M)
-    \,\Gamma_0(r, M) \, p_{\rm tra}(M)\\
-    &=N_\star^0(r\a, M\a)\,\Gamma_0(r\a, M\a) \, p_{\rm 
-        tra}(M\a),
-    \label{eq:n_det_0}
-\end{align}
-and
-\begin{align}
+    &=\int\mathrm{d}r\,\mathrm{d}M~\mathcal{N}_\star^0(r\a, M\a; r, M)
+    \, \Gamma_0(r, M) \, p_{\rm tra}(M)\\
+    &=N_\star^0(r\a, M\a)\, \Gamma_0(r\a, M\a) \, p_{\rm 
+        tra}(M\a),\\
     \notag
     n_{\rm det}^1(r\a, M\a)
-    &=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_\star^1(r\a, M\a; r, M)
-    \,\Gamma_1(r, M) \, p_{\rm tra}(M)\\
+    &=\int\mathrm{d}r\,\mathrm{d}M~\mathcal{N}_\star^1(r\a, M\a; r, M)
+    \, \Gamma_1(r, M) \, p_{\rm tra}(M)\\
     &=N_\star^0(r\a, M\a)\, p_{\rm tra}(M\a) \,
@@
     \int \mathrm{d}q \,
-         \mathcal{D}_1^3 f(q)\,
-         \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a, M\a).
-    \label{eq:n_det_1}
-\end{align}
-Finally,
-\begin{align}
+         \mathcal{D}_1^3 f(q)\cdot
+         \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a, M\a),\\
     n_{\rm det}^2(r\a, M\a)
     \notag
-    &=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_\star^2(r\a, M\a; r, M)
-    \,\Gamma_2(r, M) \, p_{\rm tra}(M)\\
+    &=\int\mathrm{d}r\,\mathrm{d}M~\mathcal{N}_\star^2(r\a, M\a; r, M)
+    \, \Gamma_2(r, M) \, p_{\rm tra}(M)\\
     &=
-    N_\star^0(r\a, M\a)\, \frac{n\b}{n\s}
+    N_\star^0(r\a, M\a)\, p_{\rm tra}(M\a) \, \frac{n\b}{n\s}
     \int {\rm d}q\, 
-         \mathcal{D}_1^3 f(q)\, q \mathcal{D}_2
-         \Gamma_2(\mathcal{D}_2r\a, qM\a)\,
+         \mathcal{D}_1^3 f(q)\cdot q \mathcal{D}_2
+         \Gamma_2(\mathcal{D}_2r\a, qM\a)\cdot
          \frac{R(qM\a)}{R(M\a)} q^{-1/3}.
@@
 
-\paragraph{General formula for apparent occurrence rate}
-Combining the above results with Equation~\ref{eq:N_searched}, the
-apparent rate density,
+Finally, combining these results, the
+apparent occurrence rate density
 \begin{align}
@@
     \frac{1}{N_\star(r\a,M\a) p_{\rm tra}(r\a,M\a)} \,
-    \sum_i n_{\rm det}^i (r\a,M\a),
+    \sum_{i=0}^2 n_{\rm det}^i (r\a,M\a)
 \end{align}
-evaluates to
+becomes
 \begin{align}
@@
     \left[ \int_0^1 \mathrm{d}q \,
-           \mathcal{D}_1^3 f(q)\,
+           \mathcal{D}_1^3 f(q)\cdot
            \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a, M\a)\,
@@
     +\int_0^1 {\rm d}q\, 
-         \mathcal{D}_1^3 f(q)\, q \mathcal{D}_2
-         \Gamma_2(\mathcal{D}_2r\a, qM\a)\,
+         \mathcal{D}_1^3 f(q)\cdot q \mathcal{D}_2
+         \Gamma_2(\mathcal{D}_2r\a, qM\a)\cdot
          \frac{R(qM\a)}{R(M\a)} q^{-1/3}
@@
 \end{align}
-We validate this equation in limits where it is possible to write down
-the answer (e.g., Equation~\ref{eq:formula_twin_binary}), and also
-against a Monte Carlo realization of the twin binary models
-(Sections~\ref{sec:model_1} and~\ref{sec:model_2}).
+%We validate this equation in limits where it is possible to write down
+%the answer (e.g., Equation~\ref{eq:formula_twin_binary}), and also
+%against a Monte Carlo realization of the twin binary models
+%(Sections~\ref{sec:model_1} and~\ref{sec:model_2}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \input{hj_rates.tex}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2018-02-24 paper/figures/collect_results.sh
figure label improvements

@@ -1,7 +1,11 @@
-cp ../../results/ndet_vs_radius_logx_model_3_fraclines_rpu_22.5_manyZs.pdf .
-cp ../../results/int_rate_density_vs_radius_model_7_rpu_22.5_manyZs.pdf .
-cp ../../results/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf .
-cp ../../results/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf .
-cp ../../results/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf .
-cp ../../results/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf .
+#!/usr/bin/env bash
+
+cp ../../results/visualize_volumes.pdf .
 cp ../../results/occ_rate_vs_radius_model_1_brokenx.pdf .
+cp ../../results/mass_ratio_distribution.pdf .
+cp ../../results/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf .
+cp ../../results/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf .
+cp ../../results/ndet_vs_radius_logx_model_3_fraclines_rpu_22.5_manyZs.pdf .
+cp ../../results/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf .
+cp ../../results/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf .
+cp ../../results/int_rate_density_vs_radius_model_7_rpu_22.5_manyZs.pdf .

### 2018-02-24 src/make_all_plots.sh

@@ -1,0 +1,8 @@
+#!/usr/bin/env bash
+
+python plot_visualize_volumes.py
+python plot_occrates_vs_radius.py
+python plot_mass_ratio_distribution.py
+python plot_integrated_rate_densities_vs_radius.py
+python plot_integrated_occrates_vs_radius.py
+python plot_ndet_apparent_vs_radius.py

### 2018-02-24 src/plot_integrated_occrates_vs_radius.py

@@ -87,8 +87,11 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
     if not many_Zs:
         ax.step(xvals, yinferred, label=lambdastr, c=colors[0], where='post')
     else:
-        ax.step(xvals, yinferred, label=lambdastr+', $Z_2/Z_0$={:.1f}'.format(
-            Z_2/Z_0), c=colors[0], where='post')
+        if Z_2/Z_0 == 0.5:
+            labelstr = lambdastr+', $Z_2/Z_0$={:.1f}'.format(Z_2/Z_0)
+        else:
+            labelstr = lambdastr+', $Z_2/Z_0$={:d}'.format(int(Z_2/Z_0))
+        ax.step(xvals, yinferred, label=labelstr, c=colors[0], where='post')
 
     if many_Zs:
         for ind, Z_2 in enumerate([0.25,0]):
@@ -117,8 +120,12 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
             c = ['#4ca8e8', '#85c5f2'] # shades of blue for vs function of Z_2
             ls = ['--', ':'] # shades of blue for vs function of Z_2
 
-            ax.step(xvals, yinferred, label=lambdastr+', $Z_2/Z_0$={:.1f}'.format(
-            Z_2/Z_0), c=c[ind], linestyle=ls[ind], where='post')
+            if Z_2/Z_0 == 0.5:
+                labelstr = lambdastr+', $Z_2/Z_0$={:.1f}'.format(Z_2/Z_0)
+            else:
+                labelstr = lambdastr+', $Z_2/Z_0$={:d}'.format(int(Z_2/Z_0))
+            ax.step(xvals, yinferred, label=labelstr, c=c[ind],
+                    linestyle=ls[ind], where='post')
 
     if standardlines:
 
@@ -126,15 +133,19 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
                 linestyle='-', c=colors[1])
 
     if brokenx:
-        ax.legend(loc='upper left',fontsize='medium')
+        leg = ax.legend(loc='upper left',fontsize='medium')
+        leg.get_frame().set_linewidth(0.)
[…]

### 2018-02-24 src/plot_integrated_rate_densities_vs_radius.py

@@ -68,8 +68,11 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
     if not many_Zs:
         ax.plot(xvals, yinferred, label=gammastr, c=colors[0])
     else:
-        ax.plot(xvals, yinferred, label=gammastr+', $Z_2/Z_0$={:.1f}'.format(
-            Z_2/Z_0), c=colors[0])
+        if Z_2/Z_0 == 0.5:
+            labelstr = gammastr+', $Z_2/Z_0$={:.1f}'.format(Z_2/Z_0)
+        else:
+            labelstr = gammastr+', $Z_2/Z_0$={:d}'.format(int(Z_2/Z_0))
+        ax.plot(xvals, yinferred, label=labelstr, c=colors[0])
 
     if many_Zs:
         for ind, Z_2 in enumerate([0.25,0]):
@@ -84,8 +87,13 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
             c = ['#4ca8e8', '#85c5f2'] # shades of blue for vs function of Z_2
             ls = ['--', ':'] # shades of blue for vs function of Z_2
 
-            ax.plot(xvals, yinferred, label=gammastr+', $Z_2/Z_0$={:.1f}'.format(
-            Z_2/Z_0), c=c[ind], linestyle=ls[ind])
+            if Z_2/Z_0 == 0.5:
+                labelstr = gammastr+', $Z_2/Z_0$={:.1f}'.format(Z_2/Z_0)
+            else:
+                labelstr = gammastr+', $Z_2/Z_0$={:d}'.format(int(Z_2/Z_0))
+
+            ax.plot(xvals, yinferred, label=labelstr, c=c[ind],
+                    linestyle=ls[ind])
 
 
     if standardlines:
@@ -94,15 +102,19 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
                 c=colors[1])
 
     if model_number != 7:
-        ax.legend(loc='best',fontsize='medium')
+        leg = ax.legend(loc='best',fontsize='medium')
+        leg.get_frame().set_linewidth(0.)
+        leg.get_frame().set_facecolor('none')
     elif model_number == 7 and not logy:
-        ax.legend(loc='upper left',fontsize='small')
[…]

### 2018-02-24 src/plot_mass_ratio_distribution.py

@@ -27,7 +27,9 @@ yvals = np.ones_like(q)
 yvals[(q>1)|(q<0)] = 0
 ax.plot(q, yvals, label='volume-limited', zorder=1)
 
-ax.legend(loc='best',fontsize='medium')
+leg = ax.legend(loc='best',fontsize='medium')
+leg.get_frame().set_linewidth(0.)
+leg.get_frame().set_facecolor('none')
 
 ax.set_xlabel('binary mass ratio, $q=M_2/M_1$', fontsize='large')
 #ax.set_ylabel('$p(\mathrm{draw\ }q\,|\,\mathrm{system\ is\ binary})$', fontsize='large')

### 2018-02-24 src/plot_ndet_apparent_vs_radius.py

@@ -89,16 +89,17 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
             c = ['#4ca8e8', '#85c5f2'] # shades of blue for vs function of Z_2
             ls = ['--', ':'] # shades of blue for vs function of Z_2
 
-            Zstr = ', $Z_2/Z_0$={:.1f}'.format(Z_2/Z_0)
-            ax.plot(xvals, y_0/y_a,
-                    label='$n_{\mathrm{det}}^0(r_{\mathrm{a}})$'+ndetstr+Zstr,
-                    c=colors[ind], linestyle='-')
-            ax.plot(xvals, y_1/y_a,
-                    label='$n_{\mathrm{det}}^1(r_{\mathrm{a}})$'+ndetstr+Zstr,
-                    c=colors[ind], linestyle='--')
-            ax.plot(xvals, y_2/y_a,
-                    label='$n_{\mathrm{det}}^2(r_{\mathrm{a}})$'+ndetstr+Zstr,
-                    c=colors[ind], linestyle=':')
+            if Z_2/Z_0 == 0.5:
+                Zstr = '$Z_2/Z_0$={:.1f}'.format(Z_2/Z_0)
+            else:
+                Zstr = '$Z_2/Z_0$={:d}'.format(int(Z_2/Z_0))
+
+            ax.plot(xvals, y_0/y_a, label='single stars, '+Zstr, c=colors[ind],
+                    linestyle='-')
+            ax.plot(xvals, y_1/y_a, label='primaries, '+Zstr, c=colors[ind],
+                    linestyle='--')
+            ax.plot(xvals, y_2/y_a, label='secondaries, '+Zstr, c=colors[ind],
+                    linestyle=':')
 
             print(Z_2, min(y_1/y_a), max(y_1/y_a), max(y_1/y_a)/min(y_1/y_a))
 
@@ -107,7 +108,9 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
         box = ax.get_position()
         ax.set_position([box.x0, box.y0, box.width * 5/5, box.height])
 	# put a legend to the right of the current axis
-        ax.legend(loc='center left', bbox_to_anchor=(1, 0.5))
+        leg = ax.legend(loc='center left', bbox_to_anchor=(1, 0.5))
+        leg.get_frame().set_linewidth(0.)
+        leg.get_frame().set_facecolor('none')
 
[…]

### 2018-02-24 src/plot_occrates_vs_radius.py

@@ -101,7 +101,9 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
                 linestyle='-', c=colors[1])
 
     if brokenx:
-        ax.legend(loc='upper left',fontsize='medium')
+        leg = ax.legend(loc='upper left',fontsize='medium')
+        leg.get_frame().set_linewidth(0.)
+        leg.get_frame().set_facecolor('none')
     else:
         ax.legend(loc='best',fontsize='medium')
 

### 2018-02-24 src/run_monte_carlo_models.sh

@@ -1,3 +1,5 @@
+#!/usr/bin/env bash
+
 # "Nominal" models (this just means I arbitrarily decided Z_2 = 0.5)
 python numerical_models.py --modelnumber 1 --ZsubTwo 0.5 --binaryfrac 0.0476
 #python numerical_models.py --modelnumber 2 --ZsubTwo 0.5 --binaryfrac 0.44 --upperradiuscutoff 22.5

### 2018-02-24 paper/main.tex
aesthetic improvements

@@
 occurrence rates measured in different surveys.  For smaller planets
-the size the errors are potentially larger: the occurrence of
-Earth-sized planets could be overestimated by as much as 50\%. We also
-show that whenever high-resolution imaging reveals a transit host star
-to be a binary, the planet is usually more likely to orbit the primary
-star than the secondary star.
+the errors are potentially larger: the occurrence of Earth-sized
+planets could be overestimated by as much as 50\%. We also show that
+whenever high-resolution imaging reveals a transit host star to be a
+binary, the planet is usually more likely to orbit the primary star
+than the secondary star.
 %
@@
     occurrence rate $\Lambda$ in a universe with only one type of
-    star, one type of planet (with radius $R_\oplus$), and a number
-    density of binary stars 5\% the number density of single stars.
+    star, one type of planet (with radius $R_\oplus$), and 
+    a binary system number density 5\% that of single stars.
     The occurrence
@@
     \plottwo{figures/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf}
-    \caption{ {\it Left:} Apparent occurrence rate density
+    \caption{ {\it Left.}---Apparent occurrence rate density
       ($\Gamma\a$), compared to the true occurrence rate density
@@
       Three different cases are plotted, with different choices for
-      the true occurrence rate density for secondary stars relative to
+      the number of planets per secondary star relative to
       that for single stars ($Z_2/Z_0$).
-      {\it Right:} Same, but for apparent occurrence
+      {\it Right.}---Same, but for apparent occurrence
       rate ($\Lambda\a$) within $0.5\,R_\oplus$ bins.
@@
     \plottwo{figures/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf}
-    \caption{ {\it Left:} True and apparent occurrence rate densities,
-      and {\it right:} occurrence rates, as a function of planet
+    \caption{ {\it Left.}---True and apparent occurrence rate densities,
+      and {\it right.}---occurrence rates, as a function of planet
       radius, using a model for the radius distribution that exhibits
@@
     &=N_\star^0(r\a, M\a)\, \Gamma_0(r\a, M\a) \, p_{\rm 
-        tra}(M\a),\\
+        tra}(M\a),
+    \label{eq:n_det_0}
+    \\
     \notag

### 2018-02-24 src/plot_integrated_occrates_vs_radius.py

@@ -250,6 +250,9 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
     if many_Zs:
         outname += '_manyZs'
 
+    ax.spines['right'].set_visible(False)
+    ax.spines['top'].set_visible(False)
+
     f.savefig(outname+'.pdf', bbox_inches='tight')
 
 

### 2018-02-24 src/plot_integrated_rate_densities_vs_radius.py

@@ -218,6 +218,9 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
     if many_Zs:
         outname += '_manyZs'
 
+    ax.spines['right'].set_visible(False)
+    ax.spines['top'].set_visible(False)
+
     f.savefig(outname+'.pdf', bbox_inches='tight')
 
 

### 2018-02-24 src/plot_mass_ratio_distribution.py

@@ -37,5 +37,8 @@ ax.set_ylabel('relative probability', fontsize='large')
 ax.set_ylim([-0.1,2.3])
 ax.set_xlim([-0.05,1.05])
 
+ax.spines['right'].set_visible(False)
+ax.spines['top'].set_visible(False)
+
 outname = '../results/mass_ratio_distribution'
 f.savefig(outname+'.pdf', bbox_inches='tight')

### 2018-02-24 src/plot_occrates_vs_radius.py

@@ -56,7 +56,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
         bigax = brokenaxes(
                 xlims=((0.695, .715), (.985, 1.005)),
                 d=0.02,
-                tilt=85,
+                tilt=87.5,
                 hspace=.05,
                 despine=True)
         ax=bigax

### 2018-02-24 paper/main.tex
text improvements

@@
 Here, though, we will focus exclusively on problems that arise from
-the fact that many stars exist in gravitationally bound binary
-systems.  We will also focus on the errors in planet occurrence as a
-function of radius, rather than orbital period. This is because when
-more than one transit is detected (as is usually required by the
-surveyors), the orbital periods can be measured without ambiguity
-regardless of whether the host star is single or one member of a
-binary.  Even with this narrow focus, there are numerous sources of
-error.  All three of the quantities in
-Equation~\ref{eq:occ_rate_simple} are biased:
+the fact that many stars exist in unresolved binary systems.  We will
+also focus on the errors in planet occurrence as a function of radius,
+rather than orbital period. This is because when more than one transit
+is detected (as is usually required by the surveyors), the orbital
+periods can be measured without ambiguity regardless of whether the
+host star is single or one member of a binary.  Even with this narrow
+focus, there are numerous sources of error.  All three of the
+quantities in Equation~\ref{eq:occ_rate_simple} are biased:
 \begin{enumerate}
@@
 $L$.  Single stars are uniformly distributed in space with a number
-density of $n\s$ stars per cubic parsec, and binaries are uniformly
-distributed with number density $n\b$.  In this scenario, stars are
-never misclassified because the combined light of a binary has the
-same color and spectrum as a single star.  We further assume that all
-planets have the same radius, $r$, and occur around single stars and
-members of binaries at the same rate, $\Lambda(r)$.
+density of $n\s$ stars per cubic parsec, and binary systems are
+uniformly distributed with number density $n\b$.  In this scenario,
+stars are never misclassified because the combined light of a binary
+has the same color and spectrum as a single star.  We further assume
+that all planets have the same radius, $r$, and occur around single
+stars and members of binaries at the same rate, $\Lambda(r)$.
 
@@
 Thus the observers determine the minimum $F_0$ for which detection would have been
-possible, and count the number of sources with $F_{\rm tot}>F_0$. This will
+possible, and count the number of sources with $F>F_0$. This will
 include all the single stars out to a maximum distance
@@
 would have been detectable.  The limiting flux for detection in this
-case is $4F_0$, because the signal amplitude hase been reduced by a
+case is $4F_0$, because the signal amplitude has been reduced by a
 factor of two and the noise level must also be reduced by a factor of
@@
 From within this sample of apparently searchable sources, the
-observers sum the number of detections $dN_{\rm det}$ of planets
+observers sum the number of detections ${\rm d}N_{\rm det}$ of planets
 with an apparent radius between $r\a$ and $r\a + dr\a$.  There will be
@@
 
-The most obvious aspect of the results is that the occurrence rate
-density of planets smaller than the breakpoint radius of 2\,$R_\oplus$
-is now substantially overestimated.  If secondary stars have the same
-planet population as the single stars, then the occurrence rate
-density of small planets is overestimated by $50\%$.  The magnitude of
-the systematic error decreases if there are fewer planets around
-secondaries; if secondaries host no planets at all, the apparent rate
-is overestimated by only $10\%$.
+The most obvious aspect of the results is that the occurrence rate of
+planets smaller than the breakpoint radius of 2\,$R_\oplus$ is now
+substantially overestimated.  If secondary stars have the same planet
+population as the single stars, then the occurrence rate density of
+small planets is overestimated by $50\%$.  The magnitude of the
+systematic error decreases if there are fewer planets around
+secondaries; if secondaries host no planets at all, the occurrence
+rate is overestimated by only $10\%$.
 
@@
 secondary stars do not host any planets, and has a magnitude
-$\Lambda_{{\rm g},0}/\Lambda_{\rm g,a} = 1.13$.
+$\Lambda_{{\rm giant},0}/\Lambda_{\rm giant,a} = 1.13$.
 %occ_rate_vs_radius_model_3_withtext_Zsub2_0.00_rpu_22.5.pdf
@@
 
-The occurrence calculations that led to this discovery, like almost
-all occurrence calculations, did not carefully account for
-unresolved binaries.  Intuitively we expect the effect of unresolved
-binaries to have a blurring effect on the radius distribution, filling
-in any gaps in the radius distribution and making them appear less
-empty than in reality.  To investigate the quantitative effects we
-make identical assumptions as in Section~\ref{sec:model_3}, except
-that the radius distribution is assumed to have a complete absence of
-planets with sizes between 1.5 and 2\,$R_\oplus$:
+The occurrence rate calculations that led to this discovery did not
+carefully account for unresolved binaries.  Intuitively we expect
+unresolved binaries to have a blurring effect, filling in any gaps in
+the radius distribution and making them appear less empty than in
+reality.  To investigate the quantitative effects we make identical
+assumptions as in Section~\ref{sec:model_3}, except that the radius
+distribution is assumed to have a complete absence of planets with
+sizes between 1.5 and 2\,$R_\oplus$:
 \begin{align}
@@
 the integrated rate of hot Jupiters is also affected.  We calculate
-the apparent hot Jupiter rate by integrating the apparent rate density
-for $r\a > 8\,R_\oplus$.  If secondaries host any planets at all, the
-apparent rate is {\it greater} than the true rate.  For instance, when
-hot Jupiters are just as common around secondary stars as single or primary
-stars, then $\Lambda_{\rm HJ,a}/\Lambda_{{\rm HJ},0} = 1.23$.
+the apparent hot Jupiter rate $\Lambda_{\rm HJ,a}$ by integrating the
+apparent rate density for $r\a > 8\,R_\oplus$.  If secondaries host
+any planets at all, the apparent rate is {\it greater} than the true
+rate.  For instance, when hot Jupiters are just as common around
+secondary stars as single or primary stars, then $\Lambda_{\rm
+HJ,a}/\Lambda_{{\rm HJ},0} = 1.23$.
 %int_rate_density_vs_radius_model_7_withtext*manyZs.pdf

### 2018-02-24 paper/main.tex
update commit hash

@@
 computation: \url{github.com/lgbouma/binary_biases}, commit
-\texttt{6cb920c}.} Figure~\ref{fig:occ_rate_model_3_log} shows the
+\texttt{4e517fe}.} Figure~\ref{fig:occ_rate_model_3_log} shows the
 results, again for the case $n\b/n\s=0.79$, $\alpha = 3.5$, $\beta=0$,

### 2018-02-28 paper/main.tex
remove appendix; change NPPS label; add brokenaxes
Better to not have Lambda(r) since we want discrete labels.

WRT the appendix:
As it was, the calculation that it's doing is roughly the same as what's
done in the main text.  However it tries to be more formal, and in
expanding the definition of "rate density" makes a mistake.

Defining Gamma(r,M) as number of planets per star per unit planet radius
per unit stellar mass is not actually the density function that we want.
This definition of Gamma is ill-defined because of the added measure in
stellar counts (the denominator). This problem is i

@@
     4 Ivy Lane, Princeton, NJ 08540, USA}
+\affiliation{
+    NASA Sagan Fellow}
 \author[0000-0002-4265-047X]{J. N. Winn}
@@
 that all planets have the same radius, $r$, and occur around single
-stars and members of binaries at the same rate, $\Lambda(r)$.
+stars and members of binaries at the same rate, $\Lambda_r$.
 
@@
 assume that the limiting source of noise is the photon-counting noise
-from the source, i.e., $\sigma \propto 1/\sqrt{F}$, where
+from the source, i.e., $\sigma \propto 1/\sqrt{F}$,
 where $F$ is the total flux of the source.
@@
 \begin{equation}
-    \Lambda\a(r) = 
-        \frac{\Lambda(r) \, n\s d_0^3}
+    \Lambda_{{\rm{a}},r} = 
+        \frac{\Lambda_r \, n\s d_0^3}
         {n\s d_0^3 + n\b (d_0\sqrt{2})^3}.
@@
 \end{equation}
-This apparent rate is larger than the true rate by a factor
-\begin{equation}
-    \frac{\Lambda\a(r)}{\Lambda(r)} = 
+This apparent rate is smaller than the true rate by a factor
+\begin{equation}
+    \frac{\Lambda_{{\rm{a}},r}}{\Lambda_r} = 
         \frac{1}{1 + 2^{3/2}(n\b/n\s)}.
@@
 \begin{equation}
-    \Lambda\a\left( \frac{r}{\sqrt{2}} \right) = 
-        \frac{2\Lambda(r) \, n\b (d_0\sqrt{2}/2)^3}
+    \Lambda_{{\rm{a}},r/\sqrt{2}} = 
+        \frac{2\, \Lambda_r \, n\b (d_0\sqrt{2}/2)^3}
         {n\s (d_0/2)^3 + n\b (d_0\sqrt{2}/2)^3}
     =
-    \frac{2\Lambda(r)\cdot2^{3/2}(n\b/n\s)}{1 + 2^{3/2} (n\b/n\s)}.
+    \frac{2\, \Lambda_r \cdot2^{3/2}(n\b/n\s)}{1 + 2^{3/2} (n\b/n\s)}.
     \label{eq:correction_diluted_rp}
@@
     occurrence rate $\Lambda$ in a universe with only one type of
-    star, one type of planet (with radius $R_\oplus$), and 
-    a binary system number density 5\% that of single stars.
+    star, one type of planet (with radius $r$), and
+    $n\b/n\s=0.05$, for $n\b$ the number density of binary
+    systems, and $n\s$ the number density of single stars.
     The occurrence
-    rate of planets with radius $R_\oplus$ is underestimated, and the
+    rate of planets with radius $r$ is underestimated, and the
     occurrence rate of planets with radius
-    $R_\oplus/\sqrt{2}$ is overestimated.}
+    $r/\sqrt{2}$ is overestimated.}
     \label{fig:occ_rate_model_1}
@@
 \begin{equation}
-    \frac{\Lambda\a(r)}{\Lambda(r)} = 0.88,~~
-    \frac{\Lambda\a(r/\sqrt{2})}{\Lambda(r)} = 0.25.
+    \frac{\Lambda_{{\rm{a}},r}}{\Lambda_r} = 0.88,~~
+    \frac{\Lambda_{{\rm{a}},r/\sqrt{2}}}{\Lambda_r} = 0.25.
     \label{eq:ratios}
@@
 We will now generalize to allow for a continuum of planet sizes.   We
-introduce the occurrence rate density
-\begin{equation}
-    \Gamma(r) \equiv \frac{{\rm d}\Lambda}{{\rm d}r},
+introduce the occurrence rate density $\Gamma$,
+the number of planets per star per unit planet radius, so that
+\begin{equation}
+    \Gamma(r) {\rm d}r \equiv \frac{ {\rm d}N_{\rm det} }{N_\star}
+            \, \frac{1}{p_{\rm tra}}.
     \label{eq:rate_density_defn}
 \end{equation}
-the number of planets per star per unit planet radius.  The naive
-observers are measuring $\Gamma\a(r\a)$, the apparent occurrence rate
-density of planets with an ``apparent radius''
+The naive observers are measuring $\Gamma\a(r\a)$, the apparent
+occurrence rate density of planets with an ``apparent radius''
 \begin{equation}
@@
 \begin{equation}
-  \Gamma_i(r) = \Lambda(r\p)\, \hat{\delta}(r-r\p),~~{\rm for}\ i\in\{0,1,2\}
-\end{equation}
-where $\hat{\delta}$ is the Dirac delta function, and $r\p$ is the
-single planet size considered in Section~\ref{sec:model_1}.
+  \Gamma_i(r) = \Lambda_{r\p}\, \hat{\delta}(r-r\p),~~{\rm for}\ i\in\{0,1,2\}
+\end{equation}
+where $\hat{\delta}$ is the Dirac delta function, and $\Lambda_{r\p}$ is the
+number of planets with size $r\p$ per star considered in 
+Section~\ref{sec:model_1}.
 
@@
 \end{equation}
-To obtain the total number of searchable binaries,
-Equation~\ref{eq:N_binaries} needs to be integrated over $q$. The
-result of the integration replaces ${\mu N_\star(r\a)/(1+\mu)}$ in
-Equations~\ref{eq:n1} and~\ref{eq:n2}.
+Equation~\ref{eq:N_binaries} replaces ${\mu N_\star(r\a)/(1+\mu)}$
+in Equations~\ref{eq:n1} and~\ref{eq:n2}.
+The whole equation is then integrated to give the number of
+detected planets.
 
@@
 \end{align}
-The \hyperref[sec:appendix]{appendix} gives an alternative derivation
-of this equation.
-
+%The \hyperref[sec:appendix]{appendix} gives a more formal derivation
+%of this equation.
 We note that the combination $\mathcal{D}_1^3f(q)$ is the mass-ratio
@@
        +
-       {q \mathcal{D}_2}\cdot\Gamma_2\left(\mathcal{D}_2r\a\right)
+       {\mathcal{D}_2}\cdot\Gamma_2\left(\mathcal{D}_2r\a\right)
        \cdot
@@
       that for single stars ($Z_2/Z_0$).
-      {\it Right.}---Same, but for apparent occurrence
-      rate ($\Lambda\a$) within $0.5\,R_\oplus$ bins.
+      {\it Right.}---Same, integrated over $0.5\,R_\oplus$
+      bins to give apparent and true occurrence rates.
       In both cases the true planet
@@
 density begins to level off to a constant value as $r$ decreases below
-$R_\oplus$~\citep{petigura_plateau_2013}.  To investigate the
+$2R_\oplus$~\citep{petigura_plateau_2013}.  To investigate the
 implications we consider a broken power-law:
@@
 probability that a detected planet orbits a single star, the primary
-star, or a secondary star.  These can be obtained from the
-generalizations of Equations~\ref{eq:n0}--\ref{eq:n2}, which are
-derived in the \hyperref[sec:appendix]{appendix}.  This information
-can be used to help interpret the results of a transit survey.  It is
+star, or a secondary star.  
+This information can be used to help interpret the results of
+a transit survey.  It is
 also relevant to the fairly common situation in which transits are
@@
 assumptions for the rate of planets around secondaries, i.e.,
-different choices for $Z_2/Z_0$.  We use
-Equations~\ref{eq:n_det_0}--\ref{eq:n_det_2} to compute the number of
-detections from single stars, primaries, and secondaries, and divide
-by the total number of detections at each apparent radius.
+different choices for $Z_2/Z_0$.  
+Dividing each component of Equation~\ref{eq:general_Gamma_a} by
+the total rate density, we get the fraction of
+detections from single stars, primaries, and secondaries as a function
+of apparent radius.
 
@@
 \begin{equation}
-    f(r) \propto \exp \left[ -\frac{(r-\bar{r})^2}{2\sigma_r^2} \right],
+    f(r) = 
+    \frac{1}{\sqrt{2 \pi \sigma_r^2}} \,
+    \exp \left[ -\frac{(r-\bar{r})^2}{2\sigma_r^2} \right],
 \end{equation}
@@
 Astrophysics Data System Bibliographic Services.
+This work was performed in part under contract with the California Institute 
+of Technology (Caltech)/Jet Propulsion Laboratory (JPL) funded by NASA through 
+the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.
 %
@@
 \newpage
+
+\begin{comment}
 \appendix
@@
 
-Here we present an alternative derivation of
+Here we present a more formal derivation of
 Equation~\ref{eq:general_Gamma_a}.  We also generalize a bit further,
@@
 \end{equation}
-where $\hat{\delta}$ is the Dirac delta function.  Therefore,
-\begin{equation}
-    n_{\rm det}^0(r\a, M\a)=N_\star^0(r\a,M\a)\, \Gamma_0(r\a, 
-    M\a) \, p_{\rm tra}(r\a, M\a).
-\end{equation}
+where $\hat{\delta}$ is the Dirac delta function.
+%Therefore,
+%\begin{equation}
+%    n_{\rm det}^0(r\a, M\a)=N_\star^0(r\a,M\a)\, \Gamma_0(r\a, 
+%    M\a) \, p_{\rm tra}(r\a, M\a).
+%\end{equation}
 
@@
     = \int_0^1 
-      \mathrm{d}q\,f(q)\,\mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M),
+      \mathrm{d}q\,f(q)\,\mathcal{N}_{\star, q}^1(r\a, M\a, q; r, M),
     \label{eq:fancyN_s_1}
@@
 \begin{equation}
-    \mathcal{N}_{{\rm s},q}^1(r\a, M\a, q; r, M)
+    \mathcal{N}_{\star,q}^1(r\a, M\a, q; r, M)
     \propto
@@
 \end{equation}
-In this case, $\mathcal{N}_{{\rm s},q}^1$ is non-zero only at
+In this case, $\mathcal{N}_{\star,q}^1$ is non-zero only at
 $r\a=R\a\sqrt{\delta}$, and the observed transit depth is
@@
     \delta
-    = \left[{r\over R(M\a)}\right]^2\, {L(M\a) \over L_{\rm tot}(M\a, q)}
+    = \left({r\over R(M\a)}\right)^2\, {L(M\a) \over L_{\rm tot}(M\a, q)}
     \equiv \left[{r\over R(M\a)}\right]^2\, 
@@
 \end{equation}
-The normalization of $\mathcal{N}_{{\rm s},q}^1$ is given by the
+The normalization of $\mathcal{N}_{\star,q}^1$ is given by the
 number of binaries that are searchable for a signal $\delta$
@@
 %$N_\star^0$, could also be expressed as $(\delta, L(M\a))$.
-Applying Equation~\ref{eq:primary_normalization},
+Applying the preceding arguments, we find
 \begin{align}
-    \mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M)
+    \mathcal{N}_{\star, q}^1(r\a, M\a, q; r, M)
     &=N_\star^0(r\a, M\a)
     \, {n\b\over n\s} \, \mathcal{D}_1^3
-    \,\hat{\delta} \left[r\a-\frac{r}{\mathcal{D}_1}\right]\hat{\delta}(M\a-M).
+    \,\hat{\delta} \left(r\a-\frac{r}{\mathcal{D}_1}\right)\hat{\delta}(M\a-M).
     \label{eq:N_s_1}
@@
 \begin{equation}
-    \mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
+    \mathcal{N}_{\star,q}^2(r\a, M\a, q; r, M)
     \propto \hat{\delta}\left(M\a-{M\over q}\right).
@@
     \mathcal{N}_\star^2(r\a, M\a; r, M)
-    =\int_0^1 \mathrm{d}q~f(q)\,\mathcal{N}_{{\rm s}, q}^2(r\a, M\a, q; r, M),
+    =\int_0^1 \mathrm{d}q~f(q)\,\mathcal{N}_{\star, q}^2(r\a, M\a, q; r, M),
 \end{equation}
@@
 \begin{align}
-    \mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
+    \mathcal{N}_{\star,q}^2(r\a, M\a, q; r, M)
     =N_\star^0(r\a, M\a) \, \frac{n\b}{n\s} 
@@
 %(Sections~\ref{sec:model_1} and~\ref{sec:model_2}).
+\end{comment}
 

### 2018-02-28 src/brokenaxes.py

@@ -1,0 +1,290 @@
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import matplotlib.ticker as ticker
+from matplotlib import rcParams
+from datetime import timedelta
+
+import numpy as np
+
+__author__ = 'Ben Dichter'
+
+
+class BrokenAxes:
+    def __init__(self, xlims=None, ylims=None, d=.015, tilt=45,
+                 subplot_spec=None, fig=None, despine=True,
+                 *args, **kwargs):
+        """Creates a grid of axes that act like a single broken axes
+
+        Parameters
+        ----------
+        xlims, ylims: (optional) None or tuple of tuples, len 2
+            Define the ranges over which to plot. If `None`, the axis is left
+            unsplit.
+        d: (optional) double
+            Length of diagonal split mark used to indicate broken axes
+        tilt: (optional) double
+            Angle of diagonal split mark
+        subplot_spec: (optional) None or Gridspec.subplot_spec
+            Defines a subplot
+        fig: (optional) None or Figure
+            If no figure is defined, `plt.gcf()` is used
+        despine: (optional) bool
+            Get rid of right and top spines. Default: True
+        wspace, hspace: (optional) bool
+            Change the size of the horizontal or vertical gaps
+        args, kwargs: (optional)
+            Passed to gridspec.GridSpec
+
+        Notes
+        -----
+        The broken axes effect is achieved by creating a number of smaller axes
+        and setting their position and data ranges. A "big_ax" is used for
+        methods that need the position of the entire broken axes object, e.g.
+        `set_xlabel`.
+        """
+
+        self.despine = despine
+        self.d = d
+        self.tilt = tilt
+
+        if fig is None:
+            self.fig = plt.gcf()
+        else:
+            self.fig = fig
+
+        if xlims:
+            width_ratios = [i[1] - i[0] for i in xlims]
+        else:
+            width_ratios = [1]
+
+        # handle datetime xlims
+        if type(width_ratios[0]) == timedelta:
+            width_ratios = [tt.total_seconds() for tt in width_ratios]
+
+        if ylims:
+            height_ratios = [i[1] - i[0] for i in ylims[::-1]]
+        else:
+            height_ratios = [1]
+
+        # handle datetime ylims
+        if type(height_ratios[0]) == timedelta:
[…]

### 2018-02-28 src/plot_integrated_occrates_vs_radius.py

@@ -83,7 +83,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
     colors = ['#1f77b4', '#ff7f0e', '#2ca02c', '#d62728']
     c = ['#4ca8e8', '#85c5f2'] # shades of blue for vs function of Z_2
 
-    lambdastr = r'$\Lambda_{\mathrm{a}}(r_{\mathrm{a}})$'
+    lambdastr = r'$\Gamma_{\mathrm{a}}(r_{\mathrm{a}}) \Delta r_{\mathrm{a}}$'
     if not many_Zs:
         ax.step(xvals, yinferred, label=lambdastr, c=colors[0], where='post')
     else:
@@ -129,7 +129,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
 
     if standardlines:
 
-        ax.step(xvals, ytruesingle, where='post', label='$\Lambda_0(r)$',
+        ax.step(xvals, ytruesingle, where='post', label='$\Gamma_0(r) \Delta r$',
                 linestyle='-', c=colors[1])
 
     if brokenx:

### 2018-02-28 src/plot_occrates_vs_radius.py

@@ -55,9 +55,10 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
         f = plt.figure(figsize=(4,4))
         bigax = brokenaxes(
                 xlims=((0.695, .715), (.985, 1.005)),
-                d=0.02,
+                d=0.0,
+                #d=0.02,
                 tilt=87.5,
-                hspace=.05,
+                hspace=.0,
                 despine=True)
         ax=bigax
 
@@ -74,16 +75,17 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
 
     colors = ['#1f77b4', '#ff7f0e', '#2ca02c', '#d62728']
 
-    lambdastr = r'$\Lambda_{\mathrm{a}}(r_{\mathrm{a}})$'
-    ax.step(xvals, yinferred, where='post', label=lambdastr, c=colors[0])
+    lambdastr = 'apparent' #r'$\Lambda_{\mathrm{a}}(r_{\mathrm{a}})$'
+    ax.step(xvals, yinferred, where='post', label=lambdastr, c=colors[0],
+            zorder=2)
 
     if standardlines:
 
         #ax.step(xvals, ytrueselected, where='post', label='true (selected)',
         #        c=colors[1])
 
-        ax.step(xvals, ytruesingle, where='post', label='$\Lambda(r)$',
-                linestyle='-', c=colors[1])
+        ax.step(xvals, ytruesingle, where='post', label='true',#'$\Lambda(r)$',
+                linestyle='--', c=colors[1], zorder=3)
 
     elif not standardlines:
 
@@ -107,7 +109,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
     else:
         ax.legend(loc='best',fontsize='medium')
 
-    ax.set_xlabel('planet radius [$R_{\oplus}$]', fontsize='large')
+    ax.set_xlabel('planet radius', fontsize='large')
 
     ax.set_ylabel('number of planets per star', fontsize='large')
 

### 2018-02-28 paper/main.tex
tex cleanup

@@
 assume that the limiting source of noise is the photon-counting noise
-from the source, i.e., $\sigma \propto 1/\sqrt{F}$,
-where $F$ is the total flux of the source.
-Thus the observers determine the minimum $F_0$ for which detection would have been
-possible, and count the number of sources with $F>F_0$. This will
-include all the single stars out to a maximum distance
+from the source, i.e., $\sigma \propto 1/\sqrt{F}$, where $F$ is the
+total flux of the source.  Thus the observers determine the minimum
+$F_0$ for which detection would have been possible, and count the
+number of sources with $F>F_0$. This will include all the single stars
+out to a maximum distance
 \begin{equation}
@@
 Since binaries are twice as luminous, the condition $F>F_0$ will
-include binaries out to the larger distance of $d_0\sqrt{2}$.
-None of the stars in binaries will
-appear to have a planet of radius $r$, because of the dilution of
-the transit signal.  Thus, the {\it apparent} occurrence rate $\Lambda\a$ of
-planets of radius $r$ is
+include binaries out to the larger distance of $d_0\sqrt{2}$.  None of
+the stars in binaries will appear to have a planet of radius $r$,
+because of the dilution of the transit signal.  Thus, the {\it
+apparent} occurrence rate $\Lambda\a$ of planets of radius $r$ is
 \begin{equation}
@@
     \caption{ {\it Top.}---Volumes within which sources appear to be
-      searchable for planets of radius $r$.  Single stars are
-      searchable out to a distance $d_0$, at which point they become
-      too faint to allow the detection of transits.  Binaries
-      are brighter and therefore appear to be searchable out to a
-      larger distance.  {\it Bottom.}---Volumes within
-      which stars appear to be searchable for planets of radius
-      $r/\sqrt{2}$.  }
+    searchable for planets of radius $r$.  Single stars are searchable
+    out to a distance $d_0$, at which point they become too faint to
+    allow the detection of transits.  Binaries are brighter and
+    therefore appear to be searchable out to a larger distance.  {\it
+    Bottom.}---Volumes within which stars appear to be searchable for
+    planets of radius $r/\sqrt{2}$.  }
     \label{fig:model_1_volumes}
@@
     occurrence rate $\Lambda$ in a universe with only one type of
-    star, one type of planet (with radius $r$), and
-    $n\b/n\s=0.05$, for $n\b$ the number density of binary
-    systems, and $n\s$ the number density of single stars.
-    The occurrence
-    rate of planets with radius $r$ is underestimated, and the
-    occurrence rate of planets with radius
-    $r/\sqrt{2}$ is overestimated.}
+    star, one type of planet (with radius $r$), and $n\b/n\s=0.05$,
+    for $n\b$ the number density of binary systems, and $n\s$ the
+    number density of single stars.  The occurrence rate of planets
+    with radius $r$ is underestimated, and the occurrence rate of
+    planets with radius $r/\sqrt{2}$ is overestimated.}
     \label{fig:occ_rate_model_1}
@@
 \end{equation}
-which implies $n\b/n\s \approx 0.79$.  Of course not all of
-these binaries are ``twin'' binaries as we have assumed in our simple
+which implies $n\b/n\s \approx 0.79$.  Of course not all of these
+binaries are ``twin'' binaries as we have assumed in our simple
 calculation.  Later, in Section~\ref{sec:general_formula}, we will
@@
 We will now generalize to allow for a continuum of planet sizes.   We
-introduce the occurrence rate density $\Gamma$,
-the number of planets per star per unit planet radius, so that
+introduce the occurrence rate density $\Gamma$, the number of planets
+per star per unit planet radius, so that
 \begin{equation}
@@
 Our earlier results, Equations~\ref{eq:rate_at_rp}
-and~\ref{eq:correction_diluted_rp}, are recovered by integrating this formula
-over $r$ after inserting
+and~\ref{eq:correction_diluted_rp}, are recovered by integrating this
+formula over $r$ after inserting
 \begin{equation}
@@
 \end{equation}
-where $\hat{\delta}$ is the Dirac delta function, and $\Lambda_{r\p}$ is the
-number of planets with size $r\p$ per star considered in 
+where $\hat{\delta}$ is the Dirac delta function, and $\Lambda_{r\p}$
+is the number of planets with size $r\p$ per star considered in
 Section~\ref{sec:model_1}.
@@
     \mu= 
-    %\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
     \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L(M) + L(qM)
@@
 \end{align}
-%The \hyperref[sec:appendix]{appendix} gives a more formal derivation
-%of this equation.
 We note that the combination $\mathcal{D}_1^3f(q)$ is the mass-ratio
@@
 \begin{align}
-    %\notag
-    %\notag
     \Gamma\a(r\a)
-    =%&= 
+    =
     {1\over 1+\mu} \,
     \left[
-       \Gamma_0(r\a)%\phantom{\tilde \Gamma}\right.%&\\
-       %&\left.
+       \Gamma_0(r\a)
        +\mu\,
@@
     distribution is uniform and the luminosity-mass relation is
-      $L\propto M^{3.5}$. For transit signals of a given amplitude,
-      the sample of searchable sources is magnitude-limited, causing
-      high mass ratios to be over-represented. }
+    $L\propto M^{3.5}$. For transit signals of a given amplitude, the
+    sample of searchable sources is magnitude-limited, causing high
+    mass ratios to be over-represented. }
     \label{fig:q_distribn_mag_limited}
@@
 probability that a detected planet orbits a single star, the primary
-star, or a secondary star.  
-This information can be used to help interpret the results of
-a transit survey.  It is
-also relevant to the fairly common situation in which transits are
-detected from a source, and subsequent high-resolution imaging reveals
-the source to be a multiple-star system.  The question then arises:
-which star is the host of the detected planet?  Without further
-observations the answer is often unclear.  To illustrate we return to
-the scenario described in the previous section: a broken power-law
-radius distribution with $\gamma=-2.92$, along with the choices
-$n\b/n\s=0.79$, $\alpha = 3.5$, and $\beta=0$.  We also try different
-assumptions for the rate of planets around secondaries, i.e.,
-different choices for $Z_2/Z_0$.  
-Dividing each component of Equation~\ref{eq:general_Gamma_a} by
-the total rate density, we get the fraction of
-detections from single stars, primaries, and secondaries as a function
-of apparent radius.
+star, or a secondary star.  This information can be used to help
+interpret the results of a transit survey.  It is also relevant to the
+fairly common situation in which transits are detected from a source,
+and subsequent high-resolution imaging reveals the source to be a
+multiple-star system.  The question then arises: which star is the
+host of the detected planet?  Without further observations the answer
+is often unclear.  To illustrate we return to the scenario described
+in the previous section: a broken power-law radius distribution with
+$\gamma=-2.92$, along with the choices $n\b/n\s=0.79$, $\alpha = 3.5$,
+and $\beta=0$.  We also try different assumptions for the rate of
+planets around secondaries, i.e., different choices for $Z_2/Z_0$.
+Dividing each component of Equation~\ref{eq:general_Gamma_a} by the
+total rate density, we get the fraction of detections from single
+stars, primaries, and secondaries as a function of apparent radius.
 
@@
 \end{align}
-Figure~\ref{fig:model_4} shows the resulting true and apparent occurrence
-rate densities.
-For the case $Z_2/Z_0=1$, unresolved binaries reduces the contrast
-of the gap by nearly a factor of two, while also producing
-spurious features for apparent sizes beneath 1.5\,$R_\oplus$.
-Thus the gap identified by \citet{fulton_california-_2017} may be
-even more devoid of planets than it appears.
-
-%Of course, effects unrelated to
-%binarity would also ``blur'' the gap in the planet radius dimension.
-%In particular, the valley's period-dependence is almost certainly not
-%flat \citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.  This
+Figure~\ref{fig:model_4} shows the resulting true and apparent
+occurrence rate densities.  For the case $Z_2/Z_0=1$, unresolved
+binaries reduces the contrast of the gap by nearly a factor of two,
+while also producing spurious features for apparent sizes beneath
+1.5\,$R_\oplus$.  Thus the gap identified by
+\citet{fulton_california-_2017} may be even more devoid of planets
+than it appears.
+
+%Of course, effects unrelated to binarity would also ``blur'' the gap
+%in the planet radius dimension.  In particular, the valley's
+%period-dependence is almost certainly not flat
+%\citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.  This
 %means that any study measuring the gap's width or depth while
 %accounting for binarity must either perform tests at fixed orbital
-%period, or else marginalize over period and account for the associated
-%blurring in the planet radius dimension.
+%period, or else marginalize over period and account for the
+%associated blurring in the planet radius dimension.
 
@@
 period-radius space, rather than as a component of a power-law
-distribution extending to smaller planets and longer periods.
-For this reason we test the effects of unresolved binaries
-on a Gaussian radius distribution,
+distribution extending to smaller planets and longer periods.  For
+this reason we test the effects of unresolved binaries on a Gaussian
+radius distribution,
 \begin{equation}
@@
     \caption{ True and apparent occurrence rate densities, for a
-      population of planets with true radii $r$ drawn from a Gaussian distribution
-      with mean $14\,R_\oplus$ and standard deviation $2\,R_\oplus$.  This
-      is similar to the hot Jupiter distribution presented
-      by~\citet{petigura_CKS_2017}.  }
+    population of planets with true radii $r$ drawn from a Gaussian
+    distribution with mean $14\,R_\oplus$ and standard deviation
+    $2\,R_\oplus$.  This is similar to the hot Jupiter distribution
+    presented by~\citet{petigura_CKS_2017}.  }
     \label{fig:gaussian_HJ}
@@
 
-\paragraph{Earth-like planets} For the specific problem of calculating the occurrence rate
-$\eta_\oplus$ of Earth-like planets with periods of order one year,
-even a 50\% systematic error would not be the dominant source of
-uncertainty at the moment.  Estimates by
+\paragraph{Earth-like planets} For the specific problem of calculating
+the occurrence rate $\eta_\oplus$ of Earth-like planets with periods
+of order one year, even a 50\% systematic error would not be the
+dominant source of uncertainty at the moment.  Estimates by
 \citet{youdin_exoplanet_2011},~\citet{petigura_prevalence_2013},~\citet{dong_fast_2013},~\citet{foreman-mackey_exoplanet_2014},
@@
 star~\citep[\textit{e.g.},][]{holman_long-term_1999,wang_influence_2014,
-  kraus_impact_2016}.  This would affect transit survey measurements
-of $\eta_\oplus$ beyond our rough estimate.
+kraus_impact_2016}.  This would affect transit survey measurements of
+$\eta_\oplus$ beyond our rough estimate.
 
@@
 
-\begin{comment}
-% JNW: These 2 sections do not seem very interesting.
-  {\paragraph{Fraction of detected planets with binary companions}
-A related effect is that some detected planets are more likely to be
-in binary systems than others.  Notably, Figure~\ref{fig:frac_model_3}
-predicts that the fraction of detected planets with binary companions
-should increase by $6$~to~$12\%$ going from $2R_\oplus$ to
-$1.4R_\oplus$.
-
-In \citet{ziegler_robo-ao_2017}'s recent summary of the Robo-AO KOI
-survey, they reported the fraction of planet-hosting stars with
-Robo-AO detected companion stars, binned over apparent planet radii.
-The fraction of KOIs with nearby stars and their $1\sigma$
-uncertainties are:
-\begin{itemize}
-    \item Earths ($r\a < 1.6R_\oplus$): $16.3 \pm 1.0\%$, from 1480
-    systems.
-    \item Neptunes ($1.6R_\oplus < r\a < 3.9 R_\oplus$): $13.0 \pm
-    0.8\%$, from 2058 systems.
-    \item Saturns ($3.9R_\oplus < r\a < 9 R_\oplus$): $13.6 \pm 2.0\%$, from 338 systems. 
-    \item Jupiters ($r\a > 9R_\oplus$): $19.0 \pm 2.8\%$, from 247 systems. 
-\end{itemize} 
-The uncertainties were calculated
-following~\citet{burgasser_binarity_2003}.  The absolute values of the
-companion fractions are lower than in the solar neighborhood at
-least in part because of Robo-AO's sensitivity
-(\citealt{ziegler_robo-ao_2017}'s
-Figure~2;~\citealt{raghavan_survey_2010}).
-%Another reason for the lower measured companion fraction could be
-%that planetary systems are more rare in binary systems,
-%as~\citealt{kraus_impact_2016} found for close binary companions).
-The uptick in the companion rate for Jupiters is likely tied to a
-large astrophysical false positive rate~\citep{santerne_sophie_2012}.
-Going from Neptunes to Earths, the data suggest a weak increase in the
-detected planet companion fraction, perhaps of a few percent.  It will
-be interesting to see whether this effect is borne out by further
-observations.}
-
-\paragraph{Connection between high-resolution imaging and occurrence rates}
-
-Occurrence rate calculations are beginning to incorporate the results
-of high-resolution imaging surveys.  For example, recent studies have
-reduced contamination in the numerator of the occurrence rate by
-using~\citet{furlan_kepler_2017}'s catalog to test the effects of
-removing KOI hosts with known companions
-(\citealt{fulton_california-_2017}; \citealt{petigura_CKS_2017}).
-This is a good first step, but the denominator remains uncorrected.
-
-Even if the multiplicity of every star that {\it Kepler} surveyed were
-known, the problem would not be solved. In this scenario, it would be
-possible to tabulate planet occurrence for single and binary star
-systems separately.  The number of planets per single star would
-be known.  However the number of planets per primary and secondary
-would still be convolved.  An observational approach to separating the
-two populations might be to analyze the centroids, or the transit
-durations (and thus host star densities) for a representative sample
-of planets in binary systems.
-
-A theory-driven solution might entail probabilistic population
-inference, with a parametrized model for planet populations around
-primary and secondary stars.  Such an approach might be expected to
-find that the primary and secondary populations are different, since
-single M dwarfs host more small planets than FGK
-dwarfs~\citep{dressing_occurrence_2015}.  Given the difficulty of
-writing a likelihood function in a survey with systematic
-biases, one possible approach might be to forward-model the survey in
-the framework of approximate Bayesian
-computation~\citep[\textit{e.g.},][]{morehead_understanding_2016}.
-
-\end{comment}
-
-\begin{comment}
-%LB: the below paragraph seems like it is just making caveats for no
-%good reason. We've been explicit throughout that we have a
-%restrictive set of assumptions...
-
-  \paragraph{Practical effects: smooth detection efficiencies and finite SNR floors}
-  To apply this study to real transit surveys, a few practical concerns
-  become pressing.  One issue is that space-based missions with
-  telemetric requirements often must select target stars.  Even if the
-  selection process aims to create an SNR-limited survey,
-  as~\citet{batalha_selection_2010} did for {\it Kepler}, uncertainties
-  in stellar parameters and the modeled instrument performance can lead
-  to deviations away from an SNR-limited stellar sample.
-
-  Another concern is that in real transit surveys the detection
-  efficiency is not a step function in SNR.  Transit survey pipeline
-  detection efficiencies are usually smooth
-  functions~\citep{christiansen_measuring_2016,fulton_california-_2017}.
-  If we were to assume a smooth detection probability in SNR, we would
-  need to appropriately weight our occurrence calculation for planets
-  with low probabilities of being detected.
-
-  The simplest way to avoid the conceptual complications of accounting
-  for finite detection efficiency is to raise the SNR floor, to {\it
-  e.g.,} ${\rm SNR} \approx 12$ for {\it Kepler}
-  (\citealt{fulton_california-_2017}, Figure~5).  To a good
-  approximation, this allows use of the boolean distinctions
-  ``searchable'' and ``not searchable'' for signals of an observed depth
-  (at fixed orbital period).  By making the survey strictly SNR-limited,
-  rather than ``fuzzily SNR-limited'', the effects of unrecognized
-  binaries become much easier to model.  Since the minimum SNR for
-  detection is set arbitrarily\footnote{For example,
-  {\it Kepler}'s threshold of ${\rm SNR}=7.1$ was set for there to be no
-  more than one statistical false alarm across the full {\it Kepler}
-  campaign~\citep{jenkins_tests_2002}. Equally valid would have been to
-  insist on no more than $10^{-3}$ false alarms per survey, raising the
-  detection floor.  }, this simplification would put occurrence rate
-  studies on clearer conceptual ground, and facilitate the process of
-  converting the apparent radius distributions into true radius
-  distributions.
-
-  Finally, our calculations ignored the fact that a transit survey's
-  finite SNR floor could censor the apparent rate density. This would
-  make planets with smaller apparent radii harder to detect.  Other than
-  moving the small radii regime out of reach for that particular survey,
-  this would not change any of our findings.
-
-\end{comment}
-
-\begin{comment}
-%LB: the following are paragraphs from earlier discussion iterations
-
-  To count the number of stars that
-  were searched, further effort to understand the multiplicity
-  statistics of KOI vs.~non-KOI stars is necessary. In particular, a
-  non-KOI star high-resolution imaging effort could help estimate the
-  systematic errors incurred by assuming all surveyed stars are single.
-  An alternate approach would be to combine {\it Gaia} parallaxes with
-  measured photometric fluxes and identify binary systems as those that
-  are overluminous~\citep[\textit{e.g.},][]{widmark_inferring_2018}.
-
-  \citet{ciardi_understanding_2015} studied the effects of stellar
-  multiplicity on the planet radii derived from transit surveys.  They
-  modeled the problem for {\it Kepler}\ objects of interest by
-  matching a population of binary and tertiary companions to KOI
-  stars, under the assumption that the KIC-listed stars were the
-  primaries.  They then computed planet radius correction factors
-  assuming that {\it Kepler}-detected planets orbited the primary or
-  companion stars with equal probability (their Section~5).  Under
-  these assumptions, they found that any given planet's radius is on
-  average underestimated by a multiplicative factor of $\approx\!
-  1.5$.  \citet{ziegler_robo-ao_2017} recently reported a similar mean
-  radius correction factor for the multiple systems observed by the
-  Robo-AO KOI survey, using the same assumption that detected planets
-  are as likely to orbit the primary and the secondary.
-
-  Of course, our model's assumptions (see the list in
-  Section~\ref{sec:conclusion}) might not apply to the {\it Kepler}\
-  dataset.  However if they are applicable, then for the $56\%$ of
-  ``\texttt{CONFIRMED}'' KOIs\footnote{Exoplanet Archive;
-  \cite{akeson_nasa_2013}; \url{exoplanetarchive.ipac.caltech.edu}} with
-  apparent radii $>2r_\oplus$, whenever high-resolution imaging
-  discovers a binary companion in a system that hosts a detected
-  transiting planet, the planet is much more likely to orbit the
-  primary.
-
-  \paragraph{Independent approaches for estimating binarity's effects}
-  T. Barclay et al.\! (in preparation) have performed the exercise of
-  taking stars selected by the {\it Kepler}\ team, pairing them with a
-  population of secondaries, injecting a realistic distribution of
-  planet radii, and then comparing the inferred occurrence rates with
-  the true ones.  In their model, they find that binarity leads to an
-  inferred rate of Earth-sized planets $\approx 10\%$ less than the
-  true rate.  In our Model \#3, if all $Z_i$'s are equal (a plausible
-  assumption in the lack of evidence to the contrary), the
-  underestimate is by a comparable 16\%.
-\end{comment}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{comment}
-\section{Conclusion}
-% JNW: Material seems redundant.
-  This study presented a framework for estimating the impact of
-unresolved binaries on transit survey occurrence rates. From
-the order-of-magnitude argument presented in
-Section~\ref{sec:simplest}, we showed that for Sun-like stars in the
-local neighborhood, typical twin binary fractions yield apparent
-occurrence rates that are well within a factor of two of the true
-rates for single stars.
-
-We then derived a general formula for the apparent rate density
-inferred by observers who ignore binarity
-(Equation~\ref{eq:general_Gamma_a}).  As input, this equation requires
-a volume-limited mass ratio distribution, and the true rate densities
-for planets around singles, primaries, and secondaries.  The
-assumptions that enable this approach are as follows.
-\begin{enumerate}
-    \item The transit survey is SNR-limited
-        (Equation~\ref{eq:S_N_thresh}).
-    \item The observers know the true properties of the single
-        and primary stars, and assign all unresolved binaries the
-        properties of the primary.
-    \item There are two functions, $L(M)$ and $R(M)$, that specify a
-        star's luminosity and radius in terms of its mass.
-\end{enumerate}
-
-The interpretation of Equation~\ref{eq:general_Gamma_a} is that the
-apparent rate density is a weighted sum of the rate densities for
-single, primary, and secondary stars. The weights depend on the
-relative numbers of binary and single stars in the searchable volumes,
-which are affected by both dilution of transit signals and a Malmquist
-bias.  Both effects should be considered in Monte Carlo simulations of
-transit surveys~\citep[\textit{e.g.},][]{
-  bakos_hatsouth:_2013,sullivan_transiting_2015, gunther_new_2017}.
-
-Applying Equation~\ref{eq:general_Gamma_a}, we then showed that:
-\begin{itemize}
-%
-\item If single, primary, and secondary stars all host the same number
-  of planets per star, and the planet radius distribution is a power
-    law with the exponent reported by~\citet{howard_planet_2012}, then
-    binarity influences apparent planet occurrence rates at the few
-    percent level. This applies for apparent radii from $2R_\oplus$ to
-    $17R_\oplus$ (Section~\ref{sec:model_2}).
-%
-\item Assuming a broken-power law planet radius distribution, with the
-  \citet{howard_planet_2012} exponent above $2R_\oplus$ and a constant
-    occurrence below $2R_\oplus$, the rate density for radii below
-    $2R_\oplus$ is overestimated. The magnitude of the error, $\Delta
-    \Gamma_0 = |\Gamma_0 - \Gamma\a|/\Gamma_0$, can easily reach
-    $50\%$ (Figure~\ref{fig:occ_rate_model_3_log}).  Although this is
-    smaller than current systematic uncertainties on the occurrence
-    rates of Earth-sized planets, this implies that binarity could
-    eventually become an important component of the $\eta_\oplus$
-    error budget.
-%
-\item Binarity blurs sharp features in the radius distribution
-  (Figure~\ref{fig:model_4}), to a degree that could affect precise
-    measurements of the depth, width, and slope of
-    the~\citet{fulton_california-_2017} radius gap.
-    %in the event that
-    %planets are not carefully vetted with high-resolution imaging.
-%
-\item Binarity does not lead to smaller apparent HJ occurrence rates
-  (Figure~\ref{fig:gaussian_HJ}).  This assumes a Gaussian planet
-    radius distribution, similar to that reported
-    by~\citet{petigura_CKS_2017}.
-%
-\item Detected planets with apparent radii greater than $0.5R_\oplus$
-  that are revealed by high-resolution imaging surveys to exist in
-    binaries are more likely to orbit the primary
-    (Figure~\ref{fig:frac_model_3}).
-%
-\item Near the break in occurrence as a function of planet
-  radius at $2R_\oplus$, the fraction of detected planets with
-    binary companions should increase by roughly $5$~to~$10\%$
-    (Figure~\ref{fig:frac_model_3}).
-\end{itemize}
-
-These results are only strictly applicable for idealized transit
-surveys meeting the criteria mentioned above.  For real transit
-surveys, although our approach is only suggestive, we hope that it
-provides a useful estimate for the systematic errors that can be
-incurred by ignoring binarity in calculations of planetary occurrence
-rates.
-\end{comment}
-
 \acknowledgements{
@@
 
-\newpage
-
-\begin{comment}
-\appendix
-\section{Alternative derivation of apparent rate density}
-\label{sec:appendix}
-
-Here we present a more formal derivation of
-Equation~\ref{eq:general_Gamma_a}.  We also generalize a bit further,
-by allowing the occurrence rate density to depend on stellar mass $M$
-as well as planet radius $r$.  We begin by writing the apparent rate
-density $\Gamma\a$ as (in analogy to
-Equation~\ref{eq:occ_rate_simple})
-\begin{equation}
-    \Gamma\a(r\a,M\a) = \frac{n_{\rm det}(r\a,M\a)}{N_\star(r\a,M\a)}
-    \, \frac{1}{p_{\rm tra}(M\a)},
-\label{eq:apparent_rate_density}
-\end{equation}
-where $n_{\rm det}(r\a,M\a)$ is the number of detected planets per
-star with radius $r\a$ orbiting stars of apparent mass $M\a$, per unit
-$r\a$ and $M\a$.  This collection of planets with the same apparent
-properties actually includes planets with a variety of true sizes and
-host star masses.  We may write $n_{\rm det}(r\a, M\a)$ as the
-convolution of the true occurrence rate density, $\Gamma(r, M)$; and
-$\mathcal{N}_\star(r\a, M\a; r, M)$, the number of searchable stars
-per unit $(r\a, M\a)$ for which a planet with true properties $(r, M)$
-would appear to be a planet with apparent properties $(r\a, M\a)$:
-\begin{align}
-    n_{\rm det}(r\a, M\a) &=
-    \sum_{i=0}^2 n_{\rm det}^i(r\a, M\a) \\
-    &=
-    \sum_{i=0}^2 \int \mathrm{d}r \!\int\! \mathrm{d}M \,
-    \mathcal{N}_\star^i(r\a,M\a; r,M)
-    \,\Gamma_i(r,M) \, p_{\rm tra}(M),
-    \label{eq:n_det}
-\end{align}
-where $i$ specifies the true type of host star, with 0 for single
-stars, 1 for primary stars, and 2 for secondary stars.  We now proceed
-to calculate $\mathcal{N}_\star^i(r\a,M\a; r,M)$.
-
-\paragraph{Single stars}
-For single stars,
-\begin{equation}
-    \mathcal{N}_\star^0(r\a,M\a; r,M)
-    =\hat{\delta}(r\a-r)\hat{\delta}(M\a-M) N_\star^0(r,M),
-\end{equation}
-where $\hat{\delta}$ is the Dirac delta function.
-%Therefore,
-%\begin{equation}
-%    n_{\rm det}^0(r\a, M\a)=N_\star^0(r\a,M\a)\, \Gamma_0(r\a, 
-%    M\a) \, p_{\rm tra}(r\a, M\a).
-%\end{equation}
-
-\paragraph{Primary stars}
-For primary stars in binary systems, 
-\begin{equation}
-    \mathcal{N}_\star^1(r\a, M\a; r, M)
-    = \int_0^1 
-      \mathrm{d}q\,f(q)\,\mathcal{N}_{\star, q}^1(r\a, M\a, q; r, M),
-    \label{eq:fancyN_s_1}
-\end{equation}
-where $f(q)$ is the binary mass ratio distribution in a volume-limited sample
-of stars.  Since we are assuming that the observer will perceive a binary to be a single
-star with the same properties as the primary star,
-\begin{equation}
-    \mathcal{N}_{\star,q}^1(r\a, M\a, q; r, M)
-    \propto
-    \hat{\delta}(M\a-M).
-\end{equation}
-In this case, $\mathcal{N}_{\star,q}^1$ is non-zero only at
-$r\a=R\a\sqrt{\delta}$, and the observed transit depth is
-\begin{equation}
-    \delta
-    = \left({r\over R(M\a)}\right)^2\, {L(M\a) \over L_{\rm tot}(M\a, q)}
-    \equiv \left[{r\over R(M\a)}\right]^2\, 
-    \frac{1}{\mathcal{D}_1^2}
-    \label{eq:delta_obs_primaries} 
-\end{equation}
-where
-\begin{equation}
-    L_{\rm tot}(M\a,q) = L(M\a) + L(qM\a),~~\mathcal{D}_1=\sqrt{L_{\rm tot}(M\a, q) \over L(M\a)}.
-\end{equation}
-The normalization of $\mathcal{N}_{\star,q}^1$ is given by the
-number of binaries that are searchable for a signal $\delta$
-and that have mass ratio $q$:
-\begin{equation}
-    N_\star^0(r\a, M\a)\,
-    {n\b\over n\s}\left[L_{\rm tot}(M\a, q) \over L(M\a)\right]^{3/2}.
-    \label{eq:primary_normalization}
-\end{equation}
-%where the argument for the number of searchable single stars,
-%$N_\star^0$, could also be expressed as $(\delta, L(M\a))$.
-Applying the preceding arguments, we find
-\begin{align}
-    \mathcal{N}_{\star, q}^1(r\a, M\a, q; r, M)
-    &=N_\star^0(r\a, M\a)
-    \, {n\b\over n\s} \, \mathcal{D}_1^3
-    \,\hat{\delta} \left(r\a-\frac{r}{\mathcal{D}_1}\right)\hat{\delta}(M\a-M).
-    \label{eq:N_s_1}
-\end{align}
-
-\paragraph{Secondary stars}
-In this case, $M=qM_1=qM\a$, so
-\begin{equation}
-    \mathcal{N}_{\star,q}^2(r\a, M\a, q; r, M)
-    \propto \hat{\delta}\left(M\a-{M\over q}\right).
-    \label{eq:fancyN_s_2_prop}
-\end{equation}
-Again $\mathcal{N}_\star^2$ is non-zero only at
-$r\a=R\a\sqrt{\delta}$, but this time
-\begin{equation}
-      \delta =
-      \left[{r\over R(qM\a)}\right]^2 \,
-      {L(qM\a) \over L_{\rm tot}(M\a, q)}
-      \equiv
-      \left[{r\over R(M\a)}\right]^2\,
-      \frac{1}{\mathcal{D}_2^2},
-\end{equation}
-where
-\begin{equation}
-  \mathcal{D}_2
-  =
-  \frac{R(qM\a)}{R(M\a)}
-  \sqrt{ \frac{L_{\rm tot}(M\a,q)}{L(qM\a)} }.
-\end{equation}
-The normalization remains the same as the previous case~--~we are
-counting the searchable stars at a given observed depth $\delta$, and
-the total luminosity of the binary is the same.  Thus,
-\begin{equation}
-    \mathcal{N}_\star^2(r\a, M\a; r, M)
-    =\int_0^1 \mathrm{d}q~f(q)\,\mathcal{N}_{\star, q}^2(r\a, M\a, q; r, M),
-\end{equation}
-where
-\begin{align}
-    \mathcal{N}_{\star,q}^2(r\a, M\a, q; r, M)
-    =N_\star^0(r\a, M\a) \, \frac{n\b}{n\s} 
-    \, \mathcal{D}_1^3
-    \, \hat{\delta} \left(r\a-\frac{r}{\mathcal{D}_2}\right)
-    \hat{\delta} \left(M\a-{M\over q}\right).
-    \label{eq:mathcal_N_s_2}
-\end{align}
-
-\paragraph{Number of detected planets}
-Inserting the results into Equation~\ref{eq:n_det}, we find
-\begin{align}
-    \notag
-    n_{\rm det}^0(r\a, M\a)
-    &=\int\mathrm{d}r\,\mathrm{d}M~\mathcal{N}_\star^0(r\a, M\a; r, M)
-    \, \Gamma_0(r, M) \, p_{\rm tra}(M)\\
-    &=N_\star^0(r\a, M\a)\, \Gamma_0(r\a, M\a) \, p_{\rm 
-        tra}(M\a),
-    \label{eq:n_det_0}
-    \\
-    \notag
-    n_{\rm det}^1(r\a, M\a)
-    &=\int\mathrm{d}r\,\mathrm{d}M~\mathcal{N}_\star^1(r\a, M\a; r, M)
-    \, \Gamma_1(r, M) \, p_{\rm tra}(M)\\
-    &=N_\star^0(r\a, M\a)\, p_{\rm tra}(M\a) \,
-    \frac{n\b}{n\s}
-    \int \mathrm{d}q \,
-         \mathcal{D}_1^3 f(q)\cdot
-         \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a, M\a),\\
-    n_{\rm det}^2(r\a, M\a)
-    \notag
-    &=\int\mathrm{d}r\,\mathrm{d}M~\mathcal{N}_\star^2(r\a, M\a; r, M)
-    \, \Gamma_2(r, M) \, p_{\rm tra}(M)\\
-    &=
-    N_\star^0(r\a, M\a)\, p_{\rm tra}(M\a) \, \frac{n\b}{n\s}
-    \int {\rm d}q\, 
-         \mathcal{D}_1^3 f(q)\cdot q \mathcal{D}_2
-         \Gamma_2(\mathcal{D}_2r\a, qM\a)\cdot
-         \frac{R(qM\a)}{R(M\a)} q^{-1/3}.
-    \label{eq:n_det_2}
-\end{align}
-
-Finally, combining these results, the
-apparent occurrence rate density
-\begin{align}
-    \Gamma\a(r\a,M\a) &= 
-    \frac{1}{N_\star(r\a,M\a) p_{\rm tra}(r\a,M\a)} \,
-    \sum_{i=0}^2 n_{\rm det}^i (r\a,M\a)
-\end{align}
-becomes
-\begin{align}
-    \notag
-    \Gamma\a(r\a,M\a) &= \frac{1}{1+\mu} \,
-    \left\{ \Gamma_0(r\a, M\a)+ 
-    \frac{n\b}{n\s}
-    \left[ \int_0^1 \mathrm{d}q \,
-           \mathcal{D}_1^3 f(q)\cdot
-           \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a, M\a)\,
-    \right.   
-    \right. \\
-    & \quad\quad\quad\quad\quad \left.\left.
-    +\int_0^1 {\rm d}q\, 
-         \mathcal{D}_1^3 f(q)\cdot q \mathcal{D}_2
-         \Gamma_2(\mathcal{D}_2r\a, qM\a)\cdot
-         \frac{R(qM\a)}{R(M\a)} q^{-1/3}
-    \right] \right\}.
-\end{align}
-%We validate this equation in limits where it is possible to write down
-%the answer (e.g., Equation~\ref{eq:formula_twin_binary}), and also
-%against a Monte Carlo realization of the twin binary models
-%(Sections~\ref{sec:model_1} and~\ref{sec:model_2}).
-\end{comment}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-02-28 paper/main.tex
text: minor

@@
 where $\hat{\delta}$ is the Dirac delta function, and $\Lambda_{r\p}$
-is the number of planets with size $r\p$ per star considered in
+is the number of planets per star with size $r\p$ considered in
 Section~\ref{sec:model_1}.
@@
 computation: \url{github.com/lgbouma/binary_biases}, commit
-\texttt{4e517fe}.} Figure~\ref{fig:occ_rate_model_3_log} shows the
+\texttt{74fe7e4}.} Figure~\ref{fig:occ_rate_model_3_log} shows the
 results, again for the case $n\b/n\s=0.79$, $\alpha = 3.5$, $\beta=0$,

### 2018-03-01 paper/main.tex
update title

@@
 
-\title{ Binarity's Biases on Transit Survey Occurrence Rates }
+\title{ Biases in Planet Occurrence Caused by Unresolved Binaries in
+        Transit Surveys }
 %
@@
 provide a framework for dealing with these issues, and to gauge at
-least the order of magnitude of the systematic errors.  In this
+least the order of magnitude of the systematic effects.  In this
 spirit, our models are idealized.  We do not attempt a detailed
@@
 and~\ref{eq:correction_diluted_rp}, are recovered by integrating this
-formula over $r$ after inserting
+formula over $r$ after letting the respective rate densities be
 \begin{equation}
@@
     \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L(M) + L(qM)
-    \over L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
+    \over L(M)}\right]^{3/2} f(q)\,\mathrm{d}q.
     \label{eq:mu_general}
@@
        \left\langle
-       \mathcal{D}_1\cdot\Gamma_1\left(\mathcal{D}_1r\a\right)
+       \mathcal{D}_1 \, \Gamma_1\left(\mathcal{D}_1r\a\right)
        +
-       {\mathcal{D}_2}\cdot\Gamma_2\left(\mathcal{D}_2r\a\right)
-       \cdot
+       {\mathcal{D}_2} \, \Gamma_2\left(\mathcal{D}_2r\a\right)
+       \,
        {R(qM) \over R(M)}q^{-1/3}
@@
 in binaries come from secondaries.  They are actually much larger
-planets for which $\delta$ has been substantially reduced by the light
-from the primary star.  As we consider apparent radii ranging from 2
-to 1.4\,$R_\oplus$, the fraction of detected planets with binary
-companions increases by anywhere from $6\%$~to~$12\%$, depending on
-the relative occurrence of planets about primaries and secondaries.
+planets for which the transit signal amplitude has been substantially
+reduced by the light from the primary star.  As we consider apparent
+radii ranging from 2 to 1.4\,$R_\oplus$, the fraction of detected
+planets with binary companions increases by anywhere from
+$6\%$~to~$12\%$, depending on the relative occurrence of planets about
+primaries and secondaries.
 
@@
 dependence of occurrence on metallicity, even a difference of
-$0.04$~dex could account for a factor of $10^{3.4\cdot 0.04} = 1.37$
+$0.04$~dex could account for a factor of $10^{3.4(0.04)} = 1.37$
 in the occurrence rate.  After correcting for metallicity, the

### 2018-03-01 paper/main.tex
update commit

@@
 computation: \url{github.com/lgbouma/binary_biases}, commit
-\texttt{74fe7e4}.} Figure~\ref{fig:occ_rate_model_3_log} shows the
+\texttt{fd41b4b}.} Figure~\ref{fig:occ_rate_model_3_log} shows the
 results, again for the case $n\b/n\s=0.79$, $\alpha = 3.5$, $\beta=0$,

### 2018-03-01 paper/main.tex
minor conclusion edit
rename figs for aas convention

@@
     \begin{center}
-        \includegraphics[width=0.6\textwidth]{figures/visualize_volumes.pdf}
+        \includegraphics[width=0.6\textwidth]{figures/f1.pdf}
     \end{center}
@@
     \begin{center}
-        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
+        \includegraphics[width=.6\textwidth]{figures/f2.pdf}
     \end{center}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
+    \includegraphics[width=0.6\textwidth]{figures/f3.pdf}
     \caption{ The mass ratio distribution of binaries in a
@@
     \epsscale{1.15}
-    \plottwo{figures/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf}
+    \plottwo{figures/f4a.pdf}{figures/f4b.pdf}
     \caption{ {\it Left.}---Apparent occurrence rate density
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/ndet_vs_radius_logx_model_3_fraclines_rpu_22.5_manyZs.pdf}
+    \includegraphics[width=\textwidth]{figures/f5.pdf}
     \caption{ Fraction of detected planets that orbit single stars
@@
     \epsscale{1.15}
-    \plottwo{figures/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf}
+    \plottwo{figures/f6a.pdf}{figures/f6b.pdf}
     \caption{ {\it Left.}---True and apparent occurrence rate densities,
@@
     \centering
-    \includegraphics[width=.6\textwidth]{figures/int_rate_density_vs_radius_model_7_rpu_22.5_manyZs.pdf}
+    \includegraphics[width=.6\textwidth]{figures/f7.pdf}
     \caption{ True and apparent occurrence rate densities, for a
@@
 \S\,\ref{subsec:whichstar} suggest that in almost all cases the planet
-most likely orbits the primary star.
+most likely orbits the primary star.  Additionally, the fraction of
+detected planets that are actually in unresolved binaries should
+increase towards smaller apparent radii.
 

### 2018-03-01 paper/figures/collect_results.sh

@@ -1,11 +1,11 @@
 #!/usr/bin/env bash
 
-cp ../../results/visualize_volumes.pdf .
-cp ../../results/occ_rate_vs_radius_model_1_brokenx.pdf .
-cp ../../results/mass_ratio_distribution.pdf .
-cp ../../results/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf .
-cp ../../results/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf .
-cp ../../results/ndet_vs_radius_logx_model_3_fraclines_rpu_22.5_manyZs.pdf .
-cp ../../results/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf .
-cp ../../results/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf .
-cp ../../results/int_rate_density_vs_radius_model_7_rpu_22.5_manyZs.pdf .
+cp ../../results/visualize_volumes.pdf f1.pdf
+cp ../../results/occ_rate_vs_radius_model_1_brokenx.pdf f2.pdf
+cp ../../results/mass_ratio_distribution.pdf f3.pdf
+cp ../../results/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf f4a.pdf
+cp ../../results/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf f4b.pdf
+cp ../../results/ndet_vs_radius_logx_model_3_fraclines_rpu_22.5_manyZs.pdf f5.pdf
+cp ../../results/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf f6a.pdf
+cp ../../results/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf f6b.pdf
+cp ../../results/int_rate_density_vs_radius_model_7_rpu_22.5_manyZs.pdf f7.pdf

### 2018-04-13 paper/review/response_1.txt
add response to referee comments

Dear Dr. Sigurdsson,

We thank you for organizing the review of our paper, and the referee
for constructive criticism.  We have considered the referee's remarks
carefully and revised our manuscript accordingly.

Below, we have reproduced the referee's report, along with our
point-by-point responses. A list of changes is also appended to the
manuscript.

Sincerely,

Luke Bouma, Kento Masuda, and Joshua Winn.

********************************************************************************

Referee comment:

Section 2, end of paragraph 2, For each of the 4 points regarding missed
transit signals, how often do they occur? (could add references).

  Response:

  We cannot identify "4 points regarding missed transit signals" in section 2,
  end of paragraph 2.

  Assuming that the referee is referring to points #1, #2, #3, enumerated at
  the end of section 2, paragraph 4:

  We do not know how often each of these effects happen -- the goal of this
  section is simply to introduce the existence of these sources of uncertainty.
  Could the referee please clarify their request, or perhaps give some indication
  of which references we might add?

********************************************************************************

Referee comment:

Section 3.1, first sentence, "Since the effects of binarity are most pronounced
when the two stellar components are similar" <- please also point to the place
in the text where this is explained.

  Response:

  The original idea was that binarity produces the largest errors in inferred
  planetary radii when the two stellar components are similar.  However, this
  is only true if the detected planet orbits the primary.  If it orbits the
  secondary, it is false.

  We have accordingly reworded this sentence.

********************************************************************************

Referee comment:

Section 3.2, following equations 4, you may want to change "stars" to "host
star".

  Response:

  Equation 4 is in Section 3.1, and the word "stars" does not appear around
  that equation in an immediately obvious way.

  Perhaps the referee meant around equation 14 of section 3.2?

  We have not taken any action on this point.

********************************************************************************

Referee comment:

Section 4.1, when exploring the Howard et al. planet radius distribution, how
sensitive are the results to the choice of gamma? Do mathematical artifacts
here make the results insensitive to the choice of the value of gamma?

  Response:

  Consider the cases of γ=-2.5, and γ=-3.5. (Well outside the power laws needed
  to fit Howard et al's results).  Applying Equations 28 and 30, we find:

                   γ=-2.5      γ=-2.92      γ=-3.5
  --------------------------------------------------
  Equation 28
  Γ_a/Γ_0           1.023        1.003      0.980

  Equation 30 
  Γ_a/Γ_0           1.095        1.048      0.993

  We have added a sentence summarizing this result.

********************************************************************************

Referee comment:

Section 4.4, end of paragraph 1, Add Lopez and Fortney citation.

  Response:

  We have corrected this omission.  In addition to referencing the work by
  Lopez & Fortney 2013, we now also refer to that by Owen & Wu 2013.

********************************************************************************

Referee comment:

Section 4.4, paragraph 2, "radius distribution is assumed to have a complete
absence of planets with sizes between 1.5 and 2R_Earth", might clarify that the
"true" radius distribution is assumed to have this feature after fitting the
apparent distribution.

  Response:

  We have clarified the wording in this paragraph, in a manner that should
  clarify the distinction between Fulton+17's apparent distribution, and the true
  distribution that we assume for this numerical experiment.

********************************************************************************

Referee comment:

Section 4.4, paragraph 2, More discussion of the spurious feature below 1.5
R_Earth would be helpful.

  Response:

  The peak in apparent occurrence rate density between 1.3 and 1.5 R_earth
  (solid blue line relative to dotted light blue line) is the contribution from
  secondaries with true radii greater than 2R_earth.

  We have added a comment to this effect in the caption of Figure 6. We have
  also increased the resolution of the grid in planet radius, to emphasize that
  this is a feature, rather than a bug.

  [
  OPTIONAL:
  As an aside, consider the numerical experiment of a single planet size, and a
  distribution of binary light ratios. I.e., imagine the true occurrence rate
  density is a delta function around r_p. The resulting apparent occurrence rate
  density would have contributions from primaries between r_a = r_p/sqrt(2) and
  r_a = r_p.  It would have contributions from secondaries from (roughly) r_a =
  0 up to r_p/sqrt(2). We ran this numerical experiment, and though did not
  mention it in the manuscript, we found that the contribution from secondaries
  peaked at r_a = r_p/sqrt(2).

  This delta function peak is analogous to what is seen in Figure 6.
  ]

********************************************************************************

Referee comment:

Section 4.4, paragraph 2, "may be even more devoid of planets than it appears",
might want to emphasize again here that this conclusion is very dependent on
the true distribution model plugged into the formalism.

  Response:

  We agree that the apparent rate density distribution is very dependent on
  the assumed true rate density distribution. However, we have opted not to
  change our original wording, which we believe accurately states our
  conclusion.

  Our conclusion here is that for an assumed true rate density distribution
  that roughly matches observations, there is no way for binarity to
  cause underestimates of the rate density inside a "dip" of planet occurrence.

  Restated, if there is a "gap" in the true rate density distribution,
  the apparent rate density distribution will always fill it in.

  Thus, if a gap is observed in an apparent distribution, the true distribution
  must have a gap at least as deep, if not deeper.

********************************************************************************

Referee comment:

Section 5, Hot Jupiter paragraph, states that result of this study find that
unresolved binaries likely result in an overestimated of hot-Jupiter occurrence
rates, implied by the Fulton gap model in Section 4.4. Previously, in section
4.2, paragraph 3, it states the occurrence rate density of planets greater than
8 Earth radii are underestimated. The abstract just says net systematic error
of order 5%. It would help to include a table describing the different tests in
this study, and how parameters are varied (how knobs are turned).

  Response:

  In Section 5, Hot Jupiter paragraph, we erroneously referred to Section 4.4;
  this should have been a reference to Section 4.5 (the gaussian radius
  distribution model).  We have corrected the error.

  We have now also added a table summarizing the case studies, as well as
  the parameters that are varied.

********************************************************************************

Referee comment:

- Recommend using the term "uncertainty" instead of "errors" .

  Response:

  We have changed our terminology accordingly in many places throughout the
  manuscript (see list of changes).

********************************************************************************

Referee comment:

- May want to comment on parameterizing the occurrence rate in terms of planet
  radius and insolation flux. The semi major axis will depend on which star in
  the binary the planet orbits.

- May want to comment on paper by Danley Hsu: Occurrence rates from Kepler
  using approximate Bayesian computation. You could speculate on what their
  data generating process would yield when plugged into this formalism.

- May want to comment on the parameter space and telescopes for resolving
  binaries of various separations, etc. and the probability of being able to
  resolve binaries with followup.

  Response:

  We have added a "Caveats and Outlook" paragraph that touches on all three of
  these issues.

### 2018-04-13 paper/case_study_toc.tex
add response to referee comments

%% \begin{deluxetable}{} command tell LaTeX how many columns
%% there are and how to align them.
\begin{deluxetable}{cccc}

%% Keep a portrait orientation

%% Over-ride the default font size
%% Use Default (12pt)

%% Use \tablewidth{?pt} to over-ride the default table width.
%% If you are unhappy with the default look at the end of the
%% *.log file to see what the default was set at before adjusting
%% this value.

%% This is the title of the table.
\caption{Case study table of contents.}
\label{tab:case_study_toc}

%% This command over-rides LaTeX's natural table count
%% and replaces it with this number.  LaTeX will increment 
%% all other tables after this table based on this number
\tablenum{1}

%% The \tablehead gives provides the column headers.  It
%% is currently set up so that the column labels are on the
%% top line and the units surrounded by ()s are in the 
%% bottom line.  You may add more header information by writing
%% another line between these lines. For each column that requries
%% extra information be sure to include a \colhead{text} command
%% and remember to end any extra lines with \\ and include the 
%% correct number of &s.
\tablehead{
  \colhead{Section} &
  \colhead{True rate density} &
  \colhead{Apparent rate density} & 
  \colhead{Applicable where?}
}

%% All data must appear between the \startdata and \enddata commands
\startdata
  \ref{sec:model_2} & power-law & Eqs.~\ref{eq:power_law_correction}
  \&~\ref{eq:powerlaw_vary_binary} & 2-17\,$R_\oplus$; no gap; no HJs
  \\
  \ref{sec:model_3} \& \ref{subsec:whichstar} & broken power-law &
  Fig.~\ref{fig:occ_rate_model_3_log} & 0-17\,$R_\oplus$; 
  no gap; no HJs
  \\
  \ref{sec:further_models} & broken power-law + gap & Fig.~\ref{fig:model_4} & 
  0-17\,$R_\oplus$; has gap; no HJs
  \\
  \ref{sec:hjs} & gaussian & Fig.~\ref{fig:gaussian_HJ} & only hot Jupiters
  \\
\enddata

%% Include any \tablenotetext{key}{text}, \tablerefs{ref list},
%% or \tablecomments{text} between the \enddata and 
%% \end{deluxetable} commands

%% General table comment marker
\tablecomments{
    Aside from varying the true rate density, within each case study we also 
    vary the number of planets orbiting secondary stars, relative to the 
    number orbiting single stars. We use the following notation throughout.
    $\alpha$---power-law exponent in stellar mass-luminosity relation, 
    $L\propto M^\alpha$;
    $\beta$---power-law exponent in volume-limited binary mass-ratio 
    distribution, $f(q)\propto q^\beta$;
    $\gamma$---power-law exponent in true rate density above 2\,$R_\oplus$, 
    $\Gamma(r)\propto r^\gamma$.
}

\end{deluxetable}

### 2018-04-13 paper/main.tex
aj submitted
add response to referee comments

@@
-\documentclass[12pt,modern]{aastex61}
+\documentclass[12pt,modern,trackchanges]{aastex61}
 \usepackage{graphics,graphicx}
@@
 knowing which stars have binary companions. Unresolved and
-unrecognized binaries give rise to systematic errors in planet
+unrecognized binaries give rise to systematic 
+\deleted{errors}\added{uncertainty} in planet
 occurrence rates, including misclassified planets and mistakes in
@@
 unresolved multiple-star systems, mainly binaries.  Unrecognized
-binaries cause numerous systematic errors in the planetary occurrence
+binaries cause numerous systematic \deleted{errors}\added{uncertainties} in 
+the planetary occurrence
 rates.  For example, when there is a transiting planet around a star
@@
 transit detection.  Planets can be misclassified due to statistical
-and systematic errors in the catalogued properties of the stars.  Some
+and systematic \deleted{errors}\added{uncertainties} in the catalogued 
+properties of the stars.  Some
 transit-like signals are spurious, arising from noise fluctuations or
@@
       $\rho^{-1/3}$, where $\rho$ is the stellar mean
-      density~\citep{Winn2010}.  Therefore, any errors in determining
-      the host star's mean density lead to errors in the correction
+      density~\citep{Winn2010}.  Therefore, any 
+      \deleted{errors}\added{uncertainties} in determining
+      the host star's mean density lead to 
+      \deleted{errors}\added{uncertainties} in the correction
       for the transit probability.
@@
 
-Since the effects of binarity are most pronounced when the two stellar
-components are similar, we begin by considering a universe in which
+Since binarity produces \deleted{the largest}\added{large} errors in inferred
+planetary radii when the two stellar components are similar, we
+begin by considering a universe in which
 all stars are identical, with mass $M$, radius $R$, and luminosity
@@
     \begin{center}
-        \includegraphics[width=0.6\textwidth]{figures/f1.pdf}
+        \includegraphics[width=0.6\textwidth]{f1.pdf}
     \end{center}
@@
     \begin{center}
-        \includegraphics[width=.6\textwidth]{figures/f2.pdf}
+        \includegraphics[width=.6\textwidth]{f2.pdf}
     \end{center}
@@
 
-We can now gauge the size of the systematic errors associated
-with unresolved binaries, for cases of interest.  Throughout this
+\input{case_study_toc.tex}
+
+We can now gauge the size of the systematic 
+\deleted{errors}\added{uncertainties} associated
+with unresolved binaries, for \deleted{cases of interest.}\added{the cases of 
+interest listed in Table~\ref{tab:case_study_toc}.}
+Throughout this
 section we assume $R\propto M$, and $L \propto M^{\alpha}$ where
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{figures/f3.pdf}
+    \includegraphics[width=0.6\textwidth]{f3.pdf}
     \caption{ The mass ratio distribution of binaries in a
@@
 and $\Gamma\a/\Gamma_0 = 1.048$.  The apparent occurrence rate density
-is 4.8\% higher than the true value.  We conclude that for planets around
+is 4.8\% higher than the true value.
+\added{Exploring different values for the power-law index,
+we find that $\Gamma\a/\Gamma_0$ lies between $0.99$ and 
+$1.10$, for $\gamma=-3.5$ and $\gamma=-2.5$, respectively.}
+We conclude that for planets around
 Sun-like stars with orbits within 0.25\,AU and radii in the range
-2--17\,$R_\oplus$, the systematic errors associated with binarity are
+2--17\,$R_\oplus$, the systematic \deleted{errors}\added{uncertainties} 
+associated with binarity are
 on the order of a few percent.
@@
     \epsscale{1.15}
-    \plottwo{figures/f4a.pdf}{figures/f4b.pdf}
+    \plottwo{f4a.pdf}{f4b.pdf}
     \caption{ {\it Left.}---Apparent occurrence rate density
@@
 density is more uncertain because such planets are more difficult to
-detect.  To investigate the systematic errors associated with binarity
+detect.  To investigate the systematic \deleted{errors}\added{uncertainties} 
+associated with binarity
 on the inferred occurrence rate of Earth-sized planets, we need to
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/f5.pdf}
+    \includegraphics[width=\textwidth]{f5.pdf}
     \caption{ Fraction of detected planets that orbit single stars
@@
     \epsscale{1.15}
-    \plottwo{figures/f6a.pdf}{figures/f6b.pdf}
+    \plottwo{f6a.pdf}{f6b.pdf}
     \caption{ {\it Left.}---True and apparent occurrence rate densities,
@@
       a gap between 1.5 and 2\,$R_\oplus$
-      (Equation~\ref{eq:model4_radius_distribution}). }
+      (Equation~\ref{eq:model4_radius_distribution}). 
+      \added{The peak in apparent occurrence rate density between 1.3 and 
+      1.5$\,R_\oplus$ (solid dark blue line, relative to dotted light blue 
+      line) is the contribution from secondaries with true radii greater
+      than 2\,$R_\oplus$.}
+    }
     \label{fig:model_4}
@@
 host star produces a higher flux of ultraviolet and X-ray
-radiation~\citep{owen_evaporation_2017}.
-
-The occurrence rate calculations that led to this discovery did not
-carefully account for unresolved binaries.  Intuitively we expect
+radiation\added{~\citep[\textit{e.g.},][]{lopez_role_2013,owen_kepler_2013,owen_evaporation_2017}}.
+
+The occurrence rate calculations that led to this discovery \deleted{did not
+carefully account for}\added{gave only a preliminary accounting for} 
+unresolved binaries.
+Intuitively we expect
 unresolved binaries to have a blurring effect, filling in any gaps in
-the radius distribution and making them appear less empty than in
+the \added{true} radius distribution and making them appear less empty than in
 reality.  To investigate the quantitative effects we make identical
-assumptions as in Section~\ref{sec:model_3}, except that the radius
-distribution is assumed to have a complete absence of planets with
+assumptions as in Section~\ref{sec:model_3}, except that \deleted{the radius
+distribution is assumed to have}\added{in analogy with
+\citet{fulton_california-_2017}'s findings we assume the true radius 
+distribution has} a complete absence of planets with
 sizes between 1.5 and 2\,$R_\oplus$:
@@
 occurrence rate densities.  For the case $Z_2/Z_0=1$, unresolved
-binaries reduces the contrast of the gap by nearly a factor of two,
+binaries reduce the contrast of the gap by nearly a factor of two,
 while also producing spurious features for apparent sizes beneath
@@
 \subsection{Gaussian radius distribution}
+\label{sec:hjs}
 
@@
     \centering
-    \includegraphics[width=.6\textwidth]{figures/f7.pdf}
+    \includegraphics[width=.6\textwidth]{f7.pdf}
     \caption{ True and apparent occurrence rate densities, for a
@@
 We do not claim to have solved this problem. Our aim was to clarify
-the various effects and assess the size of the errors in various
+the various effects and assess the size of the 
+\deleted{errors}\added{uncertainties} in various
 situations. We hope that our formalism will also be useful to those
@@
 small-number statistics as well as a host of other systematic
-errors~\citep[see][Figure~17]{burke_terrestrial_2015}.  Rapid progress
+\deleted{errors}\added{uncertainties}~\citep[see][Figure~17]{burke_terrestrial_2015}.
+  Rapid progress
 is expected soon, though, and binarity will merit closer attention in
@@
 in the {\it Kepler} sample might be an important factor, but the
-calculations presented in Section~\ref{sec:further_models} suggest
+calculations presented in 
+Section~\added{\ref{sec:hjs}}\deleted{\ref{sec:further_models}} suggest
 that this is not the case.  We found that the effects of unresolved
@@
 \S\,\ref{subsec:whichstar} suggest that in almost all cases the planet
-most likely orbits the primary star.  Additionally, the fraction of
-detected planets that are actually in unresolved binaries should
-increase towards smaller apparent radii.
+most likely orbits the primary star.
+
+\added{\paragraph{Caveats \& outlook}
+Unresolved binaries corrupt occurrence rate distributions along
+dimensions other than planet radius. 
+In particular, since binarity can lead to incorrect
+assessment of a planet's host stellar mass, the occurrence
+distributions in semi-major axis and insolation must also be corrected.
+Though we leave consideration of such biases for future work,
+we take solace in the fact that the NASA {\it TESS} mission
+emphasizes stars within a few hundred parsecs.
+Through a combination of high-resolution imaging and 
+{\it Gaia}'s astrometry and spectroscopy, it will be possible
+to characterize the {\it TESS} target stars more thoroughly than
+was possible with {\it Kepler}.
+This is essential for inferring properties of planet populations, since
+a population inference model with parameters controlling both the planet 
+and binary star populations might be necessary to consistently 
+account for binarity.
+Given the difficulty of writing a correct likelihood function for such
+a model, one plausible path might be to
+forward-model transit surveys with likelihood-free 
+techniques~\citep[\textit{e.g.},][]{morehead_understanding_2016,hsu_improving_2018}.
+}
 
@@
 \newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \input{hj_rates.tex}
@@
 
+\listofchanges
 \end{document}

### 2018-04-17 paper/main.tex
add KM's comments

@@
       number of detected planets that {\it appear} to have size $r$,
-      orbiting stars that {\it appear} to have mass $M$.  Whenever the
-      planet-hosting star is part of a binary,
+      orbiting stars that {\it appear} to have mass $M$ \added{and
+      radius $R$}.  Whenever the planet-hosting star is part of a
+      binary,
 %    
@@
 in Equations~\ref{eq:n1} and~\ref{eq:n2}.
-The whole equation is then integrated to give the number of
-detected planets.
+The whole equation is then integrated \added{over $q$} to give the
+number of detected planets.
 
@@
 orbit primaries, and $r/r\a = 1.65$ if detected planets are equally
-likely to orbit primaries and singles.  Our formalism provides a way
-to assess the relative probabilities that a detected planet orbits the
-primary or secondary star.  The calculations presented in
-\S\,\ref{subsec:whichstar} suggest that in almost all cases the planet
-most likely orbits the primary star.
+likely to orbit primaries and \deleted{singles}\added{secondaries}.
+Our formalism provides a way to assess the relative probabilities that
+a detected planet orbits the primary or secondary star.  The
+calculations presented in \S\,\ref{subsec:whichstar} suggest that in
+almost all cases the planet most likely orbits the primary star.
 
@@
 distributions in semi-major axis and insolation must also be corrected.
-Though we leave consideration of such biases for future work,
-we take solace in the fact that the NASA {\it TESS} mission
-emphasizes stars within a few hundred parsecs.
-Through a combination of high-resolution imaging and 
-{\it Gaia}'s astrometry and spectroscopy, it will be possible
-to characterize the {\it TESS} target stars more thoroughly than
-was possible with {\it Kepler}.
-This is essential for inferring properties of planet populations, since
-a population inference model with parameters controlling both the planet 
-and binary star populations might be necessary to consistently 
-account for binarity.
-Given the difficulty of writing a correct likelihood function for such
-a model, one plausible path might be to
+We leave consideration of such biases for future work.}
+
+\added{
+It seems likely that to consistently account for binarity in
+planet occurrence rate calculation, one must stipulate a
+population inference model with parameters controlling both the
+planet and binary star populations.
+Given the difficulty of writing a correct likelihood function
+for such a model, one feasible computational approach might be to
 forward-model transit surveys with likelihood-free 
 techniques~\citep[\textit{e.g.},][]{morehead_understanding_2016,hsu_improving_2018}.
+The NASA {\it TESS} mission should provide ample opportunity
+for such a study.
 }

### 2018-04-17 paper/figures/collect_results.sh
update ylabel on f4b, f6b

@@ -9,3 +9,13 @@ cp ../../results/ndet_vs_radius_logx_model_3_fraclines_rpu_22.5_manyZs.pdf f5.pd
 cp ../../results/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf f6a.pdf
 cp ../../results/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf f6b.pdf
 cp ../../results/int_rate_density_vs_radius_model_7_rpu_22.5_manyZs.pdf f7.pdf
+
+cp ../../results/visualize_volumes.pdf ../f1.pdf
+cp ../../results/occ_rate_vs_radius_model_1_brokenx.pdf ../f2.pdf
+cp ../../results/mass_ratio_distribution.pdf ../f3.pdf
+cp ../../results/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf ../f4a.pdf
+cp ../../results/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf ../f4b.pdf
+cp ../../results/ndet_vs_radius_logx_model_3_fraclines_rpu_22.5_manyZs.pdf ../f5.pdf
+cp ../../results/int_rate_density_vs_radius_model_4_xcut_manyZs.pdf ../f6a.pdf
+cp ../../results/int_occ_rate_vs_radius_model_4_xcut_manyZs.pdf ../f6b.pdf
+cp ../../results/int_rate_density_vs_radius_model_7_rpu_22.5_manyZs.pdf ../f7.pdf

### 2018-04-17 src/integrate_for_apparent_rate_density.py

@@ -532,7 +532,7 @@ def get_apparent_radius_grid(model_number, slowrun=False):
         if not slowrun:
             r_a_grid = np.arange(1e-1,r_pu+1e-1,1e-1)
         elif slowrun:
-            r_a_grid = np.arange(2e-2,r_pu+2e-2,5e-3)
+            r_a_grid = np.arange(2e-2,r_pu+2e-2,2e-2)
 
     elif model_number == 7:
         if not slowrun:
@@ -575,7 +575,7 @@ def get_apparent_rate_density(r_a_grid, M_a_grid, model_number):
         prob_r = np.minimum( r_grid**δ, r_pl**δ )
         norm_r = trapz(prob_r, r_grid)
     elif model_number == 4:
-        r_grid = np.arange(1e-3, r_pu+1e-3, 1e-4)
+        r_grid = np.arange(1e-3, r_pu+1e-3, 1e-3)
         prob_r = np.minimum( r_grid**δ, r_pl**δ )
         prob_r[(r_grid > 1.5) & (r_grid < 2)] = 0
         norm_r = trapz(prob_r, r_grid)

### 2018-04-17 src/plot_integrated_occrates_vs_radius.py

@@ -4,6 +4,8 @@ from matplotlib import rc
 rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
 rc('text', usetex=True)
 
+import matplotlib.pyplot as plt
+plt.switch_backend('agg')
 import matplotlib.pyplot as plt, pandas as pd, numpy as np
 from scipy.integrate import trapz
 
@@ -147,7 +149,7 @@ def make_plot(model_number, logx=None, logy=None, withtext=None,
 
     ax.set_xlabel('planet radius [$R_\oplus$]', fontsize='large')
 
-    ax.set_ylabel('number of planets per star', fontsize='large')
+    ax.set_ylabel('number of planets per star per bin', fontsize='large')
 
     if logx:
         ax.set_xscale('log')

### 2018-04-17 paper/main.tex
add another KM comment
fix typo

@@
 \end{equation}
+\added{The apparent and true rates are illustrated in 
+Figure~\ref{fig:occ_rate_model_1}.}
 All together, the various effects produce biases of order 10\% in the
@@
 \added{
-It seems likely that to consistently account for binarity in
-planet occurrence rate calculation, one must stipulate a
-population inference model with parameters controlling both the
-planet and binary star populations.
+It seems likely that to consistently account for binarity, one
+must use a population inference model with parameters
+controlling both the planet and binary star populations.
 Given the difficulty of writing a correct likelihood function
@@
 techniques~\citep[\textit{e.g.},][]{morehead_understanding_2016,hsu_improving_2018}.
-The NASA {\it TESS} mission should provide ample opportunity
-for such a study.
+The NASA {\it TESS} mission will likely open up this avenue of research,
+since its target stars are close and bright.
 }

### 2018-04-18 paper/review/response_1.txt
update referee response
update response per JNW comments

@@
 
-  We cannot identify "4 points regarding missed transit signals" in section 2,
-  end of paragraph 2.
-
-  Assuming that the referee is referring to points #1, #2, #3, enumerated at
-  the end of section 2, paragraph 4:
-
-  We do not know how often each of these effects happen -- the goal of this
-  section is simply to introduce the existence of these sources of uncertainty.
-  Could the referee please clarify their request, or perhaps give some indication
-  of which references we might add?
+  We assume the referee is referring to paragraph 3.  All of these
+  effects are quite common, both in the Kepler survey and ground-based
+  surveys, though we are not aware of any source that would allow us
+  to estimate the probabilities.  Since these "pitfalls" are not the
+  topic of this paper, we do not want to attempt such a calculation
+  here.
 
@@
 
-  The original idea was that binarity produces the largest errors in inferred
-  planetary radii when the two stellar components are similar.  However, this
-  is only true if the detected planet orbits the primary.  If it orbits the
+  We decided to omit this sentence.  The original idea was that
+  binarity produces the largest errors in inferred planetary radii
+  when the two stellar components are similar.  However, this is only
+  true if the detected planet orbits the primary.  If it orbits the
   secondary, it is false.
-
-  We have accordingly reworded this sentence.
 
@@
 
-  Equation 4 is in Section 3.1, and the word "stars" does not appear around
-  that equation in an immediately obvious way.
-
-  Perhaps the referee meant around equation 14 of section 3.2?
-
-  We have not taken any action on this point.
+  Equation 4 is in Section 3.1 (not Section 3.2) and is not followed
+  by a sentence with the word "stars". Perhaps the referee is
+  referring to equation 14?  We do not understand why it would be an
+  improvement here to replace "stars" with "host star", so we have not
+  taken any action.
 
@@
 
-  Consider the cases of γ=-2.5, and γ=-3.5. (Well outside the power laws needed
-  to fit Howard et al's results).  Applying Equations 28 and 30, we find:
+  We addressed this point by considering the cases of γ=-2.5, and
+  γ=-3.5, which bracket the result from Howard et al. and are well
+  outside the quoted uncertainty range.  Applying Equations 28 and 30,
+  we find:
 
@@
 
-  We have corrected this omission.  In addition to referencing the work by
-  Lopez & Fortney 2013, we now also refer to that by Owen & Wu 2013.
+  We have corrected this omission, and also added a citation to Owen &
+  Wu (2013).
 
@@
 
-Section 4.4, paragraph 2, "radius distribution is assumed to have a complete
-absence of planets with sizes between 1.5 and 2R_Earth", might clarify that the
-"true" radius distribution is assumed to have this feature after fitting the
-apparent distribution.
+Section 4.4, paragraph 2, "radius distribution is assumed to have a
+complete absence of planets with sizes between 1.5 and 2R_Earth",
+might clarify that the "true" radius distribution is assumed to have
+this feature after fitting the apparent distribution.
 
@@
 
-  We have clarified the wording in this paragraph, in a manner that should
-  clarify the distinction between Fulton+17's apparent distribution, and the true
-  distribution that we assume for this numerical experiment.
+  We have tried to clarify this passage, to distinguish between the
+  apparent rate distribution measured by Fulton et al. (2017) and the
+  distribution assumed in our numerical experiment.
 
@@
 
-  The peak in apparent occurrence rate density between 1.3 and 1.5 R_earth
-  (solid blue line relative to dotted light blue line) is the contribution from
-  secondaries with true radii greater than 2R_earth.
-
-  We have added a comment to this effect in the caption of Figure 6. We have
-  also increased the resolution of the grid in planet radius, to emphasize that
-  this is a feature, rather than a bug.
-
-  [
-  OPTIONAL:
-  As an aside, consider the numerical experiment of a single planet size, and a
-  distribution of binary light ratios. I.e., imagine the true occurrence rate
-  density is a delta function around r_p. The resulting apparent occurrence rate
-  density would have contributions from primaries between r_a = r_p/sqrt(2) and
-  r_a = r_p.  It would have contributions from secondaries from (roughly) r_a =
-  0 up to r_p/sqrt(2). We ran this numerical experiment, and though did not
-  mention it in the manuscript, we found that the contribution from secondaries
-  peaked at r_a = r_p/sqrt(2).
-
-  This delta function peak is analogous to what is seen in Figure 6.
-  ]
+  The peak in apparent occurrence rate density between 1.3 and 1.5
+  R_earth (solid blue line relative to dotted light blue line) is the
+  contribution from secondaries with true radii greater than 2R_earth.
+  This is now stated in the caption of Figure 6.  We have also
+  increased the resolution of the grid in planet radius, to emphasize
+  that this is a feature, rather than a bug.
 
@@
 
-  We agree that the apparent rate density distribution is very dependent on
-  the assumed true rate density distribution. However, we have opted not to
-  change our original wording, which we believe accurately states our
-  conclusion.
-
-  Our conclusion here is that for an assumed true rate density distribution
-  that roughly matches observations, there is no way for binarity to
-  cause underestimates of the rate density inside a "dip" of planet occurrence.
-
-  Restated, if there is a "gap" in the true rate density distribution,
-  the apparent rate density distribution will always fill it in.
-
-  Thus, if a gap is observed in an apparent distribution, the true distribution
-  must have a gap at least as deep, if not deeper.
+  We have added a few sentences to make our point more clearly:
+  "The quantitative results of this numerical experiment obviously
+  depend on the input assumptions.  The more general point is that
+  whenever there is a gap-like feature in the true rate density
+  distribution, the effects of binarity will tend to fill it in.  If a
+  gap is observed in an apparent distribution, the true distribution
+  must have a gap at least as deep, if not deeper."
 
@@
 
-  In Section 5, Hot Jupiter paragraph, we erroneously referred to Section 4.4;
-  this should have been a reference to Section 4.5 (the gaussian radius
-  distribution model).  We have corrected the error.
+  We see now that in Section 5 (Hot Jupiter paragraph) we erroneously
+  referred to Section 4.4; this should have been a reference to
+  Section 4.5 (the gaussian radius distribution model).  We have
+  corrected the error.
 
-  We have now also added a table summarizing the case studies, as well as
-  the parameters that are varied.
+  We have also followed the referee's advice and added a table
+  summarizing the case studies, as well as the parameters that are
+  varied.
 
@@
 
-  We have changed our terminology accordingly in many places throughout the
-  manuscript (see list of changes).
+  We appreciate the suggestion but we prefer to leave the text as it
+  is.  The term "systematic error" is in more common use than
+  "systematic uncertainty", by about a factor of 5 according to Google
+  Ngram viewer.
 
@@
 
-- May want to comment on paper by Danley Hsu: Occurrence rates from Kepler
-  using approximate Bayesian computation. You could speculate on what their
-  data generating process would yield when plugged into this formalism.
+  Response: We have added a "Caveats and Outlook" paragraph that
+  touches on all three of these issues.
+
+- May want to comment on paper by Danley Hsu: Occurrence rates from
+  Kepler using approximate Bayesian computation. You could speculate
+  on what their data generating process would yield when plugged into
+  this formalism.
+
+  Response: The work by Hsu et al. does look interesting, but since we
+  lack experience with their technique we do not wish to speculate on
+  how to modify it to accommodate binarity.
 
@@
 
-  Response:
+  Response: Given that there are so many possible approaches and
+  instruments for imaging, RV, and astrometry, a quantitative analysis
+  of this issue would be beyond the scope of this article.  In the
+  revision, we have simply acknowledged that the combination of Gaia
+  and TESS data will lessen the severity of the problem, compared to
+  the situation with Kepler.
 
-  We have added a "Caveats and Outlook" paragraph that touches on all three of
-  these issues.
+********************************************************************************
+
+Other:
+
+* We have changed the ylabel in Figures 4b and 6b from "number of planets per
+  star" to "number of planets per star per bin".
+
+* We now mention Figure 2 in the text (cf. appended List of Changes)

### 2018-04-18 paper/main.tex
update manuscript w/ JNW comments

@@
 Wide-field surveys for transiting planets, such as the NASA {\it
-Kepler} and {\it TESS} missions, are usually conducted without
-knowing which stars have binary companions. Unresolved and
-unrecognized binaries give rise to systematic 
-\deleted{errors}\added{uncertainty} in planet
-occurrence rates, including misclassified planets and mistakes in
-completeness corrections.  The individual errors can have different
-signs, making it difficult to anticipate the net effect on inferred
-occurrence rates. Here we use simplified models of signal-to-noise
-limited transit surveys to try and clarify the situation. We derive a
-formula for the apparent occurrence rate density measured by an
-observer who falsely assumes all stars are single. The formula depends
-on the binary fraction; the mass function of the secondary stars; and
-the true occurrence of planets around primaries, secondaries, and
-single stars. It also takes into account the Malmquist bias by which
-binaries are over-represented in flux-limited samples. Application of
-the formula to an idealized {\it Kepler}-like survey shows that for
+Kepler} and {\it TESS} missions, are usually conducted without knowing
+which stars have binary companions. Unresolved and unrecognized
+binaries give rise to systematic errors in planet occurrence rates,
+including misclassified planets and mistakes in completeness
+corrections.  The individual errors can have different signs, making
+it difficult to anticipate the net effect on inferred occurrence
+rates. Here we use simplified models of signal-to-noise limited
+transit surveys to try and clarify the situation. We derive a formula
+for the apparent occurrence rate density measured by an observer who
+falsely assumes all stars are single. The formula depends on the
+binary fraction; the mass function of the secondary stars; and the
+true occurrence of planets around primaries, secondaries, and single
+stars. It also takes into account the Malmquist bias by which binaries
+are over-represented in flux-limited samples. Application of the
+formula to an idealized {\it Kepler}-like survey shows that for
 planets larger than 2\,$R_\oplus$, the net systematic error is of
@@
 A lingering concern about these studies is that in most cases,
-investigators have assumed that all of the targets in the survey
-are single stars~\citep[\textit{e.g.},][]{
+investigators have assumed that all of the targets in the survey are
+single stars~\citep[\textit{e.g.},][]{
 howard_planet_2012,fressin_false_2013,
-  dressing_occurrence_2015,burke_terrestrial_2015}. 
-In reality, many of the sources that are monitored in a transit survey are
-unresolved multiple-star systems, mainly binaries.  Unrecognized
-binaries cause numerous systematic \deleted{errors}\added{uncertainties} in 
-the planetary occurrence
-rates.  For example, when there is a transiting planet around a star
-in a binary, the additive constant light from the second star reduces
-the fractional loss of light due to the planet.  This makes transit
+dressing_occurrence_2015,burke_terrestrial_2015}.  In reality, many of
+the sources that are monitored in a transit survey are unresolved
+multiple-star systems, mainly binaries.  Unrecognized binaries cause
+numerous systematic errors in the planetary occurrence rates.  For
+example, when there is a transiting planet around a star in a binary,
+the additive constant light from the second star reduces the
+fractional loss of light due to the planet.  This makes transit
 signals harder to detect and lowers the number of detections.  On the
@@
 transit detection.  Planets can be misclassified due to statistical
-and systematic \deleted{errors}\added{uncertainties} in the catalogued 
-properties of the stars.  Some
+and systematic errors in the catalogued properties of the stars.  Some
 transit-like signals are spurious, arising from noise fluctuations or
@@
       $\rho^{-1/3}$, where $\rho$ is the stellar mean
-      density~\citep{Winn2010}.  Therefore, any 
-      \deleted{errors}\added{uncertainties} in determining
-      the host star's mean density lead to 
-      \deleted{errors}\added{uncertainties} in the correction
+      density~\citep{Winn2010}.  Therefore, any errors in determining
+      the host star's mean density lead to errors in the correction
       for the transit probability.
@@
 
-We can now gauge the size of the systematic 
-\deleted{errors}\added{uncertainties} associated
-with unresolved binaries, for \deleted{cases of interest.}\added{the cases of 
-interest listed in Table~\ref{tab:case_study_toc}.}
-Throughout this
+We can now gauge the size of the systematic errors associated with
+unresolved binaries, for \deleted{cases of interest.}\added{the cases
+of interest listed in Table~\ref{tab:case_study_toc}.} Throughout this
 section we assume $R\propto M$, and $L \propto M^{\alpha}$ where
-$\alpha = 3.5$, as is roughly the case for main-sequence stars.
-With these assumptions, Equations~\ref{eq:dil_1} and~\ref{eq:dil_2}
-become
+$\alpha = 3.5$, as is roughly the case for main-sequence stars.  With
+these assumptions, Equations~\ref{eq:dil_1} and~\ref{eq:dil_2} become
 \begin{equation}
@@
 Based on {\it Kepler} data, \citet{howard_planet_2012} found the
-radius distribution of planets between 2 and 17~$R_\oplus$ orbiting Sun-like
-stars within 0.25\, AU to be consistent with a power law,
+radius distribution of planets between 2 and 17~$R_\oplus$ orbiting
+Sun-like stars within 0.25\, AU to be consistent with a power law,
 \begin{equation}
@@
 $1.10$, for $\gamma=-3.5$ and $\gamma=-2.5$, respectively.}
-We conclude that for planets around
-Sun-like stars with orbits within 0.25\,AU and radii in the range
-2--17\,$R_\oplus$, the systematic \deleted{errors}\added{uncertainties} 
-associated with binarity are
-on the order of a few percent.
+We conclude that for planets around Sun-like stars with orbits within
+0.25\,AU and radii in the range 2--17\,$R_\oplus$, the systematic
+errors associated with binarity are on the order of a few percent.
 
@@
 density is more uncertain because such planets are more difficult to
-detect.  To investigate the systematic \deleted{errors}\added{uncertainties} 
-associated with binarity
+detect.  To investigate the systematic errors associated with binarity
 on the inferred occurrence rate of Earth-sized planets, we need to
@@
 while also producing spurious features for apparent sizes beneath
-1.5\,$R_\oplus$.  Thus the gap identified by
-\citet{fulton_california-_2017} may be even more devoid of planets
-than it appears.
+1.5\,$R_\oplus$.
+
+\added{The quantitative results of this numerical experiment obviously
+depend on the input assumptions.  The more general point is that
+whenever there is a gap-like feature in the true rate density
+distribution, the effects of binarity will tend to fill it in.  If a
+gap is observed in an apparent distribution, the true distribution
+must have a gap at least as deep, if not deeper.}  Thus, the gap
+identified by \citet{fulton_california-_2017} may be even more devoid
+of planets than it appears.
 
@@
 We do not claim to have solved this problem. Our aim was to clarify
-the various effects and assess the size of the 
-\deleted{errors}\added{uncertainties} in various
+the various effects and assess the size of the errors in various
 situations. We hope that our formalism will also be useful to those
@@
 small-number statistics as well as a host of other systematic
-\deleted{errors}\added{uncertainties}~\citep[see][Figure~17]{burke_terrestrial_2015}.
-  Rapid progress
+errors~\citep[see][Figure~17]{burke_terrestrial_2015}.  Rapid progress
 is expected soon, though, and binarity will merit closer attention in
@@
 
-\added{\paragraph{Caveats \& outlook}
-Unresolved binaries corrupt occurrence rate distributions along
-dimensions other than planet radius. 
-In particular, since binarity can lead to incorrect
-assessment of a planet's host stellar mass, the occurrence
-distributions in semi-major axis and insolation must also be corrected.
-We leave consideration of such biases for future work.}
-
-\added{
-It seems likely that to consistently account for binarity, one
-must use a population inference model with parameters
-controlling both the planet and binary star populations.
-Given the difficulty of writing a correct likelihood function
-for such a model, one feasible computational approach might be to
-forward-model transit surveys with likelihood-free 
-techniques~\citep[\textit{e.g.},][]{morehead_understanding_2016,hsu_improving_2018}.
-The NASA {\it TESS} mission will likely open up this avenue of research,
-since its target stars are close and bright.
-}
+\added{\paragraph{Caveats \& outlook} In this paper we have focused
+  exclusively on systematic errors in the planet radius distribution.
+  Unresolved binaries will also have other effects on the inferred
+  properties of a distribution of transiting planets.  For example,
+  the combined light of a binary might lead to a mistaken estimate of
+  the mass of the host star.  This would have implications for the
+  occurrence rate as a function of orbital distance and insolation,
+  since the orbital distance is usually calculated from the orbital
+  period and the stellar mass.}
+
+\added{Of course, many problems associated with binarity would
+disappear if we had perfect knowledge about the companions to all
+the stars in a transit survey. Progress toward this ideal is likely
+to come soon, thanks to the combination of data from the ESA {\it
+Gaia} astrometric mission \citep{Gaia2016} and the NASA {\it TESS}
+mission~\citep{ricker_transiting_2014}.  The {\it TESS} transit
+survey will concentrate on stars that are brighter than {\it Kepler}
+stars by a factor of 30--100, and closer to the Earth by a factor of
+5--10.  This will simplify all of the follow-up observations to
+search for companions and measure their properties, with direct
+imaging, Doppler monitoring, and astrometric monitoring.  Meanwhile
+{\it Gaia} will deliver parallaxes, astrometic monitoring data, and
+space-based apparent magnitudes for all of the stars relevant for {\it
+TESS}, all of which will make it easier to identify binaries and other
+multiple star systems.}
 
